### 2014-03-23 manuscript/latitudepaper.tex
Starting to rearrange paper.

\section*{Introduction}

Creating networks describing ecologically important interactions (e.g. food
webs composed of feeding links) provides a powerful way to explore differences
in community structure as networks provide a rich set of metrics that can be
used to compare structure across ecosystems (Williams & Martinez, 2000, Olesen
& Jordano, 2002, Stouffer et al., 2005, Reide et al., 2010). Such comparisons
have revealed that the structure of biological networks is generally tightly
constrained (Riede et al., 2010) and that it may be possible to reduce the
plethora of network variables to a few major descriptive dimensions (Vermaat
et al., 2009). In particular, characteristic changes in structural properties
with species richness and connectance (number of links/number of species2)
have suggested scale-dependence (Riede et al., 2010), which here refers to the
strong dependence of network properties, such as fractions of
species in different trophic groups, on the species richness or connectance of
the networks. Therefore it is likely that much variation in network structure
can be explained by variation in these two properties (Vermaat et al., 2009).

Species-richness in turn depends strongly on latitude via effects of
productivity and temperature (Brown et al., 2004, Cardillo et al., 2005,
Thompson & Townsend, 2005, Davies et al., 2007).  The strength and generality
of this pattern has generated a range of explanatory models (Whittaker et al.,
2001). Higher primary productivity has been shown emprically to affect species
richness at small and large scales  (Thompson & Townsend, 2005; Apellaniz
\emph{et al.}, 2012). Mechanistically, higher solar input (and therefor
higher productivity) may cause higher species richness (Brown et al., 2004,
Davies et al., 2007) by broadening the niche space, lessening competition
(Davies et al., 2007). Some have proposed that species' niches are generally
narrower in the tropics, and this greater specialization is what permits
higher species richness. This hypothesis is only equivocally supported
(Vazquez & Stevens, 2004) but even if niche sizes are similar at all latitudes
an increase in productivity, and by extension niche space, would be expected
to reduce competition and permit diversification. Adaptive radiation in the
tropics may also be facilitated (Cardillo et al., 2005) by the greater genetic
diversity btween populations, as well as between species, that has been
observed (Eo \emph{et al.}, 2008).

In addition to these potential effects of the changing magnitude of solar
radiation and productivity across latitudes,   both temperature (Field et al.,
1998) and primary productivity (Paine, 1966, Huston & Wolverton, 2011) are
more \emph{stable} at the equator than at higher latitudes. This lack of
seasonality in temperature and productivity is associated with lower
extinction rates, and therefore is also a potential mechanism for greater
species richness at lower latitudes (Krug \emph{et al.}, 2009). Less seasonality may also lead to greater specialization, as species do not need to switch food sources througout the year.[but can I support it?]

Due to the strength and generality of associations between biological
processes and environmental variables, variation in network structure may also
be explained by ecological gradients (Baiser et al., 2011). Predictable
changes in species richness (Davies et al., 2007, Schemske et al., 2009),
metabolic rates (Stegen et al., 2012), and rates and intensities of species
interactions (Marquis, 2005, Schemske et al., 2009) along latitudinal
gradients are among the most general and robust ecological patterns that have
been identified.

These explanations for latitudinal gradients in species richness  suggest that
other network properties should also vary over temperature and/or
productivity, independent of species richness. Temperature affects the rate at
which chemical reactions proceed, including metabolic reactions in organisms
(Gillooly et al., 2001). A faster metabolism implies greater energy demands on
an organism and therefore higher rates of herbivory, predation, and
decomposition (Brown et al., 2004, Schemske et al., 2009). This greater
activity tends to result in interactions with more species (Waser et al.,
1996, Bascompte & Jordano, 2007), increasing the number of links per species
and connectance at higher temperatures. Reduced competition due to either
narrower niches or a broader niche space (Davies et al., 2007) could also lead
to higher numbers of links per species and connectance, as species are free to
pursue links with many partners rather than being restricted to the most
profitable links. Specialist consumers tend to be more efficient at ingesting
and assimilating prey (Montoya et al., 2006), suggesting that specialization
is also likely at higher latitudes where productivity is low for much of the
year (Field et al., 1998). Higher productivity is expected to result in longer
food chains by relaxing the upper limits set by the inefficiency of energy
transfer across trophic levels (Brown et al., 2004). This should produce a web
with a lower proportion of basal species and more intermediate and top
predators in food webs. Bitrophic networks should also show more higher-
trophic-level and animal species, since they should experience the same
relaxed productivity in their feeding links, even if those links are not
explicitly considered in the networks used here.

To test whether variability in the network structure of ecological networks
can be reduced to a few ecologically meaningful dimensions, and whether these
dimensions are associated with potential environmental drivers, we preformed
principal components analyses on 97 multitrophic predator-prey (n=52) and
bitrophic parasite-host and mutualist networks (n=45) that range across a
latitudinal gradient from 52.35°S to 81.82°N. We ran additional analyses for
network properties that had been standardized for differences in species
richness and connectance to examine scale-independent variation in network
structure. We hypothesized that, in the analyses of scale-dependent network
properties, species richness and connectance would explain much of the
variation in network structure and that, because of this, temperature and
productivity would be strongly associated with major axes of variation.
Networks were expected to contain more species at higher trophic levels and
feature higher connectance and links per species closer to the equator. We
expected these trends to continue in the standardized network properties, as
many of the explanations for increasing species richness at lower latitudes
should also affect other network properties directly.

\section*{Methods}

We compiled a list of XX published food webs from [database details]. We
included only food webs with a clearly defined study site that did not cover
more than 10 degrees of latitude. Source and sink webs were also excluded as
they are likely to have different food web properties than webs attempting to
describe the entire community of a site. Also excluded were webs with poor
resolution, describing highly modified or artificial ecosystems, or including
humans.

We then converted each web to a trophic-species version by aggregating species
with the same predators and prey. This helps to reduce variation in resolution
across different studies. We then classified them both according to latitude
and ecosystem type (terrestrial, freshwater, marine, estuary). We analysed XX
food-web properties for each web (Table 1).

In our analysis, we first addressed whether the diversity or complexity of our
published food webs varies over latitude (expressed as degrees away from the
equator regardless of direction) or factorial ecosystem type. We also included
year published as in independent variable to control for changing standards
for food web studies over time. We fit independent generalized linear models
for each of the logarithms of species richness, mean links per species, and
connectance.

Second, we analysed the scaling relationships between the remaining XX food-
web parameters and connectance and species richness. We used a series of
generalized linear models with a food-web parameter as the dependent variable
and latitude, ecosystem type, and their interactions with connectance and
species richness as independent variables. (parameter ~
latitude*ecotype*(log10(connectance)+log10(species richness))). For food web
properties that were proportions, we used general linear models with a
binomial distribution. All other food web properties were log-transformed
except for motif frequencies, where many webs had zero frequencies of at least
some motifs. When modelling the standard deviation of generality, this
required the removal of 5 webs, all with 12 or fewer species, which had
standard deviations of generality of 0. These full models were then
systematically reduced using R function dredge \cite{} in package MuMIn
\cite{} in order to isolate the model with the highest AIC.

Significant slopes in the reduced models were taken to indicate scaling
relationships with species richness or connectance. Significant interactions
indicated differences in the scaling relationships over latitude. Different
intercepts indicated differences between ecosystem types.

\section*{Results}

The scaling relationships of many food-web properties changed across latitude.
(need to look up difference between change in slope and change in int.) Mean
trophic level scaled with species but not connectance and had both slope and
intercept effects of latitude and ecotype. Maximum trophic level scaled with
both species-richness and connectance, with the species-richness relationship
having both slope and intercept effects of latitude while the connectance
relationship had both slope and intercept effects of ecotype. Similarly, the
scaling of generality with species-richness has both slope and intercept
effects of latitude, as well as an intercept effect of ecotype.

The scaling of motif frequencies with connectance varied across ecotypes for
most motifs (specifically motifs 102, 108, 110, 14, 238, 46, 74, and 78) with
both intercept and slope effects. Scaling relationships with species-richness
did not change. Latitude had not effect on the scaling relationships of these
motifs. For three motifs (12, 36, and 6), scaling was not associated with
either latitude or ecotype. The frequency of the remaining motif (108) did not
scale with species richness. The scaling of this motif's frequency with
connectance did vary with latitude, although this relationship was not
significant.  Overall, therefore, we conclude that motif structure does not
change across latitude.

[Table of results]

### 2014-03-23 code/Models.R

@@ -24,54 +24,54 @@ conn_min = glm(log10(Connectance)~Ecotype-1+(1|Year_pub))
 ##################################
 ##################################
 
-linkSD_scale=glm(log10(LinkSD)~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
-gen_scale=glm(log10(Gen)~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
+linkSD_scale=glm(log10(LinkSD)~(Latitude*Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
+gen_scale=glm(log10(Gen)~(Latitude*Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
+# 5 (very small) webs with 0 GenSD is messing with this. Eliminating  1  4 30 84 85 for this model.
 Gendata=data[data$GenSD!=0,]
-genSD_scale=glm(log10(GenSD)~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
-vul_scale=glm(log10(Vul)~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
-vulSD_scale=glm(log10(VulSD)~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
-mean_SWTL_scale=glm(log10(mean_SWTL)~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
-max_SWTL_scale=glm(log10(max_SWTL)~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
-path_scale=glm(log10(Path)~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub))
-basal_scale=glm(pBas~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial')
-int_scale=glm(pInt~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial')
-top_scale=glm(pTop~(Latitude+Ecotype)*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial')
[…]

### 2014-06-03 manuscript/latitudepaper.tex
Started fleshing out results.

@@
 
-The scaling relationships of many food-web properties changed across latitude.
-(need to look up difference between change in slope and change in int.) Mean
-trophic level scaled with species but not connectance and had both slope and
-intercept effects of latitude and ecotype. Maximum trophic level scaled with
-both species-richness and connectance, with the species-richness relationship
-having both slope and intercept effects of latitude while the connectance
-relationship had both slope and intercept effects of ecotype. Similarly, the
-scaling of generality with species-richness has both slope and intercept
-effects of latitude, as well as an intercept effect of ecotype.
+Most food-web properties scaled with species-richness and/or connectance, and many of these relationships changed across latitude.
+In the best-fit models, the percentages of species that were top predators, intermediate consumers, basal resources, herbivores, and omnivores did not significantly covary with either species-richness or connectance.
+Mean trophic level scaled with species richness, mean shortest path scaled with connectance, and all other properties scaled with both species richness and connectance.
+
+The strength of the scaling relationship between mean trophic level and species richness decreased with increasing latitude ($\beta=-0.008$,$p<0.001$).
+In addition, different ecosystem types had both different intercept trophic levels (except for lakes, which did not differ from estuaries) and different scaling relationships with species-richness (again except for lakes).
+Scaling of mean trophic level with species richness was strongest for estuarine food webs ($\beta=0.616$,$p<0.001$; intercept) and was progressively weaker for lake webs, stream webs, terrestrial webs, and marine webs.
+
+Mean shortest path length decreased with increasing connectance ($\beta=-1.269$,$p=0.016$), and this relationship did not change with latitude.
+Although path length increased with latitude ($\beta=0.005$,$p=0.045$), the best-fitting model did not include a change to the scaling relationship with latitude.
+Different ecosystems, however, both had different intercept path lengths and different scaling relationships with connectance.
+
+Mean and SD of vulnerability and SD of generality scaled with both species richness and connectance, but none of these scaling relationships varied either with latitude or with ecosystem type.
+
+SD of links per species scaled with both species richness and connectance.
+Neither scaling relationship varied with latitude, and only the relationship with connectance varied across ecosystem types.
+LinkSD increased with increasing connectance ($\beta=0.999$,$p<0.001$), and this relationship was strongest for terrestrial and estuarine webs and weaker for marine, lake, and stream webs.
+
+Similarly, mean links per species did not vary with latitude but did across ecosystem types. Streams had the highest mean L/S, followed by lakes, marine webs, terrestrial webs, and estuaries.
+
+Gen, Max TL.
 

### 2014-06-03 code/Models.R

@@ -57,16 +57,6 @@ x98_scale=glm(X98~(Latitude*Ecotype)*(log10(Connectance)+log10(Species))+(1|Year
 
 #Dredging in now.
 
-# The scaling relationships of many food-web properties changed across latitude.
-# (need to look up difference between change in slope and change in int.) Mean
-# trophic level scaled with species but not connectance and had both slope and
-# intercept effects of latitude and ecotype. Maximum trophic level scaled with
-# both species-richness and connectance, with the species-richness relationship
-# having both slope and intercept effects of latitude while the connectance
-# relationship had both slope and intercept effects of ecotype. Similarly, the
-# scaling of generality with species-richness has both slope and intercept
-# effects of latitude, as well as an intercept effect of ecotype.
-
 mean_SWTL_dredged=glm(log10(mean_SWTL)~(Latitude+Ecotype)*log10(Species)+(1|Year_pub))
 max_SWTL_dredged=glm(log10(max_SWTL)~Latitude*log10(Species)+Ecotype*log10(Connectance)+(1|Year_pub))
 int_dredged=glm(pInt~Latitude*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial')
@@ -107,15 +97,3 @@ x6_dredged=glm(X6~log10(Connectance)+log10(Species)+(1|Year_pub))
 
 #Latitude
 x108_dredged=glm(X108~Latitude*log10(Connectance)+(1|Year_pub))
-
-
-# The scaling of motif frequencies with connectance varied across ecotypes for
-# most motifs (specifically motifs 102, 108, 110, 14, 238, 46, 74, and 78) with
-# both intercept and slope effects. Scaling relationships with species-richness
-# did not change. Latitude had not effect on the scaling relationships of these
-# motifs. For three motifs (12, 36, and 6), scaling was not associated with
-# either latitude or ecotype. The frequency of the remaining motif (108) did not
-# scale with species richness. The scaling of this motif's frequency with
-# connectance did vary with latitude, although this relationship was not
-# significant.  Overall, therefore, we conclude that motif structure does not
-# change across latitude.

### 2014-06-12 manuscript/latitudepaper.tex
Finished results.

--- 2014-03-23 manuscript/latitudepaper.tex
@@
 \section*{Introduction}
+
+[[Shorten this up]]
 
@@
 have revealed that the structure of biological networks is generally tightly
-constrained (Riede et al., 2010) and that it may be possible to reduce the
-plethora of network variables to a few major descriptive dimensions (Vermaat
-et al., 2009). In particular, characteristic changes in structural properties
-with species richness and connectance (number of links/number of species2)
-have suggested scale-dependence (Riede et al., 2010), which here refers to the
+constrained, particularly by relationships between species richness or connectance
+(the proportion of possible links that are realized)
+which suggest scale-depence (Riede et al., 2010), which here refers to the
 strong dependence of network properties, such as fractions of
@@
 properties that were proportions, we used general linear models with a
-binomial distribution. All other food web properties were log-transformed
-except for motif frequencies, where many webs had zero frequencies of at least
-some motifs. When modelling the standard deviation of generality, this
+binomial distribution. All other food web properties were log-transformed.
+When modelling the standard deviation of generality, this
 required the removal of 5 webs, all with 12 or fewer species, which had
@@
 systematically reduced using R function dredge \cite{} in package MuMIn
-\cite{} in order to isolate the model with the highest AIC.
+\cite{} in order to isolate the model with the highest AIC. These best-fitting models were 
+then examined in detail.
 
@@
 
-The scaling relationships of many food-web properties changed across latitude.
-(need to look up difference between change in slope and change in int.) Mean
-trophic level scaled with species but not connectance and had both slope and
-intercept effects of latitude and ecotype. Maximum trophic level scaled with
-both species-richness and connectance, with the species-richness relationship
-having both slope and intercept effects of latitude while the connectance
-relationship had both slope and intercept effects of ecotype. Similarly, the
-scaling of generality with species-richness has both slope and intercept
-effects of latitude, as well as an intercept effect of ecotype.
+In this data set, none of the best fit models for species richness, connectance, or links per species included an 
+effect of latitude, although all three properties varied across ecosystem types. [[Table or something]]
 
-The scaling of motif frequencies with connectance varied across ecotypes for
-most motifs (specifically motifs 102, 108, 110, 14, 238, 46, 74, and 78) with
-both intercept and slope effects. Scaling relationships with species-richness
-did not change. Latitude had not effect on the scaling relationships of these
-motifs. For three motifs (12, 36, and 6), scaling was not associated with
-either latitude or ecotype. The frequency of the remaining motif (108) did not
-scale with species richness. The scaling of this motif's frequency with
-connectance did vary with latitude, although this relationship was not
-significant.  Overall, therefore, we conclude that motif structure does not
-change across latitude.
+The best-fit models for most food-web properties exhibited scaling relationships with species-richness and/or 
+connectance. Notable exceptions were the proportions of basal resources, herbivores, and omnivores, which varied only 
+across year published; and the proportions of top predators and intermediate consumers, which varied with connectance 
+and species richness and connectance (respectively) although not significantly.
 
-[Table of results]
+For the food-web properties that did scale with species-richness or connectance, most of these relationships were 
+constant over latitude. Latitude terms were not included in the best-fit models for vulnerability, SD of generality or 
+SD of links. SD of vulnerability showed a weak negative relationship with latitude ($\Beta$=-0.001, $p$=0.056), 
+and path length increased with increasing 
+latitude ($\Beta$ = 0.005, $p$=0.045) but neither latitude effect affected any scaling with species richness or 
+connectance.
+
+The scaling rules of mean and maximum trophic level and generality varied over latitude. 
+Maximum trophic level increased with 
+latitude ($\Beta=0.011$, $p$=0.011), but this relationship was weakened as species richness increased ($\beta$=-0.008, $
+p$=0.011). Similarly, maximum trophic level increased with species richness ($\beta$=0.430, $p$=0.003) except at very 
+high latitudes. Maximum trophic level decreased with connectance for estuarine food webs ($\beta$=-0.458, $p$=0.021), 
+varied little in lakes ($\beta$=-0.127, $p$=0.192), and increased with connectance in marine, stream, and terrestrial 
+food webs ($\beta$=0.219, $p$=0.005; $\beta$=0.249, $p$<0.001; and $\beta$=0.337, $p$=0.002, respectively). Taken 
+together, these effects resulted in an increase in maximum trophic level with latitude at low species richnesses across 
+all ecotypes and decreasing maximum trophic level with latitude at high species richness across all ecotypes 
+(Fig. \ref{}. At moderate levels of species richness, trophic level increased with latitude for estuarine webs, showed 
+little change for lake webs, and decreased for all other ecotypes.
+
+Qualitatively similar trends were observed for mean trophic level. Mean trophic level increased with latitude 
+($\beta$=0.0109, $p$<0.001) and with species richness ($\beta$=0.616, $p$<0.001), but both trends were weakened by an 
+interaction between latitude and species-richness ($\beta$=-0.008, $p$<0.001). The best-fitting model for mean trophic 
+level did not include a connectance term. The increase in mean trophic level with species richness was highest for 
+estuarine food webs ($\beta$=0.616, $p$<0.001) and lower for lakes ($\beta$=-0.608, $p$=0.232), streams 
+($\beta$=0.238, $p$<0.001), terrestrial food webs ($\beta$=0.217, $p$=0.002), and marine food webs 
+($\beta$=0.133, $p$<0.001).
+
+Generality showed the opposite trend, decreasing with increasing latitude ($\beta$=-0.017, $p$=0.003). This decrease 
+was counteracted by a positive interaction between latitude and species richness ($\beta$=0.013, $p$=0.003), with the net result that generality increased with latitude for most ecotypes and species richnesses (Fig.
+\ref{}).
+The main effect of species richness on generality varied across ecotypes. Generality decreased with increasing species 
+richness for estuarine webs ($\beta$=-0.058, $p$=0.003) and increased for lakes ($\beta$=0.220, $p$=0.245), 
+streams ($\beta$=0.543, $p$<0.001), terrestrial ($\beta$=0.603, $p$=0.005) and marine webs ($\beta$=0.761, $p$<0.001). 
+Generality increased with connectance equally for all ecotypes ($\beta$=0.875, $p$<0.001).
+
+\section*{Discussion}
+
+The tendency of food-web structure to exhibit scaling relationships with both species richness and connectance has been 
+well-established \citep{,,,,}. As species richness in particular is also know to vary systematically over latitude 
+\citep{,,,,}, intuitively one might suspect that the scaling relationships of other food web properties might also vary
+over latitude \citep{}. However, we found that only four of XX food web properties varied significantly over latitude, 
+and that only the scaling relationships of trophic level and generality varied from the tropics to the poles.
+
+A study of plant-animal mutualistic networks found the opposite trend to that observed here, that generality decreased 
+with increasing latitude while increasing with increasing plant diversity \citep{Schleuning2012}. Unfortunately this 
+study did not examine changes in scaling relationships over latitude... Regardless, this may indicate that food webs 
+and mutualistic networks vary differently over latitudinal gradients of productivity, temperature, etc. 
+\citet{Schleuning2012} propose that the latitudinal specialization gradient in mutualists derives from the gradient in 
+plant diversity, as high resource diversity may lead to more generalized consumers. As species richness in the food 
+webs in our dataset did not vary over latitude, it seems unlikely that this is the mechanism driving increased 
+generality in high-latitude food webs. As we also observed an increase in both mean and maximum trophic level with 
+latitude, it is possible that high-trophic level species are also more apt to be generalists. Generalism may be an 
+important strategy for high-level consumers as their prey may be scarce or seasonal \citep{}.
+
+[[other scaling paper]]
+
+The overall consistency of scaling laws over latitude is remarkable and suggests that food webs worldwide assemble 
+along similar ``rules'' regardless of temperature, productivity, or other latitudinal gradients. However, the changing
+scaling laws for generality and trophic level suggest that there are also key differences in the ways that food webs 
+are configured in the tropics and at higher latitudes. Importantly, the opposing trends for generality in food webs 
+and mutualistic networks may suggest that latitude imposes different pressures on mutualistic versus antagonistic 
+interactions between species. [[Need a punchier conclusion]]

### 2014-06-12 manuscript/latitudepaper.tex
Introduction trimmed down.

@@
 
-[[Shorten this up]]
-
-Creating networks describing ecologically important interactions (e.g. food
-webs composed of feeding links) provides a powerful way to explore differences
-in community structure as networks provide a rich set of metrics that can be
-used to compare structure across ecosystems (Williams & Martinez, 2000, Olesen
-& Jordano, 2002, Stouffer et al., 2005, Reide et al., 2010). Such comparisons
+Food webs (networks of feeding links between species) have been used for decades to summarize the structure of ecological communities \citep{Martinez2000,earlierwork}.
+Comparisons of community structure around the world and across ecosystem types 
 have revealed that the structure of biological networks is generally tightly
 constrained, particularly by relationships between species richness or connectance
-(the proportion of possible links that are realized)
-which suggest scale-depence (Riede et al., 2010), which here refers to the
+(the proportion of possible links that are realized) and other food-web properties \citep{Riede2010}.
+These relationships have suggested that the structure of food webs is highly scale-depended which here refers to the
 strong dependence of network properties, such as fractions of
 species in different trophic groups, on the species richness or connectance of
-the networks. Therefore it is likely that much variation in network structure
+the networks \citep{Riede2010}. Therefore it is likely that much variation in network structure
 can be explained by variation in these two properties (Vermaat et al., 2009).
 
-Species-richness in turn depends strongly on latitude via effects of
-productivity and temperature (Brown et al., 2004, Cardillo et al., 2005,
-Thompson & Townsend, 2005, Davies et al., 2007).  The strength and generality
-of this pattern has generated a range of explanatory models (Whittaker et al.,
-2001). Higher primary productivity has been shown emprically to affect species
-richness at small and large scales  (Thompson & Townsend, 2005; Apellaniz
-\emph{et al.}, 2012). Mechanistically, higher solar input (and therefor
-higher productivity) may cause higher species richness (Brown et al., 2004,
-Davies et al., 2007) by broadening the niche space, lessening competition
-(Davies et al., 2007). Some have proposed that species' niches are generally
-narrower in the tropics, and this greater specialization is what permits
-higher species richness. This hypothesis is only equivocally supported
-(Vazquez & Stevens, 2004) but even if niche sizes are similar at all latitudes
-an increase in productivity, and by extension niche space, would be expected
-to reduce competition and permit diversification. Adaptive radiation in the
-tropics may also be facilitated (Cardillo et al., 2005) by the greater genetic
-diversity btween populations, as well as between species, that has been
-observed (Eo \emph{et al.}, 2008).
+As changes in species richness and connectance can explain much of the variation in network structure \citep{Vermaat2009}, 
+it follows that drivers of change in these two properties may also affect other properties. Species richness in particular 
+exhibits a strong latitudinal gradient, believed to be driven by varying productivity and temperature at different latitudes 
+\citep{Brown2004,Cardillo2005,Thompson2005,Davies2007}. An alternative view
+posits that species' niches are narrower in the tropics, 
+reducing competition and permitting greater adaptive radiation \citep{}. Although this view is only equivocally supported 
+\citep{Vazquez2004}, it is also possible that the higher productivity of the tropics \citep{Brown2004} may result in a broader 
+niche space \citep{Davies2007} which could also allow greater diversification even if niche sizes are globally similar.
 
-In addition to these potential effects of the changing magnitude of solar
-radiation and productivity across latitudes,   both temperature (Field et al.,
-1998) and primary productivity (Paine, 1966, Huston & Wolverton, 2011) are
-more \emph{stable} at the equator than at higher latitudes. This lack of
-seasonality in temperature and productivity is associated with lower
-extinction rates, and therefore is also a potential mechanism for greater
-species richness at lower latitudes (Krug \emph{et al.}, 2009).
-Less seasonality may also lead to greater specialization, as species do not need to switch food sources througout the year.[but can I support it?]
+In addition to species richness, there are general and robust latitudinal gradients in metabolic rates \citep{Stegen2012} and 
+rates and intensities of species interactions \citep{Marquis2005,Schemske2009}. These gradients, together with the strength and 
+generality of associations between biological processes and environmental variables, suggest that variation in network structure 
+may also be explained by ecological gradients \citep{Baiser2011}. Importantly, some of these gradients may act directly 
+on food-web properties such that they change over latitude beyond the expected changes due to changing species richness. For 
+example, if niche sizes vary with latitude then generality (mean number of prey per predator), vulnerability (mean number of 
+predators per prey), and mean number of links per species may all vary with latitude beyond variation due to changes in species
+richness.
 
-Due to the strength and generality of associations between biological
-processes and environmental variables, variation in network structure may also
-be explained by ecological gradients (Baiser et al., 2011). Predictable
-changes in species richness (Davies et al., 2007, Schemske et al., 2009),
-metabolic rates (Stegen et al., 2012), and rates and intensities of species
-interactions (Marquis, 2005, Schemske et al., 2009) along latitudinal
-gradients are among the most general and robust ecological patterns that have
-been identified.
+%% Useful for discussion:
+% These explanations for latitudinal gradients in species richness  suggest that
+% other network properties should also vary over temperature and/or
+% productivity, independent of species richness. Temperature affects the rate at
+% which chemical reactions proceed, including metabolic reactions in organisms
+% (Gillooly et al., 2001). A faster metabolism implies greater energy demands on
+% an organism and therefore higher rates of herbivory, predation, and
+% decomposition (Brown et al., 2004, Schemske et al., 2009). This greater
+% activity tends to result in interactions with more species (Waser et al.,
+% 1996, Bascompte & Jordano, 2007), increasing the number of links per species
+% and connectance at higher temperatures. Reduced competition due to either
+% narrower niches or a broader niche space (Davies et al., 2007) could also lead
+% to higher numbers of links per species and connectance, as species are free to
+% pursue links with many partners rather than being restricted to the most
+% profitable links. Specialist consumers tend to be more efficient at ingesting
+% and assimilating prey (Montoya et al., 2006), suggesting that specialization
+% is also likely at higher latitudes where productivity is low for much of the
+% year (Field et al., 1998). Higher productivity is expected to result in longer
+% food chains by relaxing the upper limits set by the inefficiency of energy
+% transfer across trophic levels (Brown et al., 2004). This should produce a web
+% with a lower proportion of basal species and more intermediate and top
+% predators in food webs. Bitrophic networks should also show more higher-
+% trophic-level and animal species, since they should experience the same
+% relaxed productivity in their feeding links, even if those links are not
+% explicitly considered in the networks used here.
 
-These explanations for latitudinal gradients in species richness  suggest that
-other network properties should also vary over temperature and/or
-productivity, independent of species richness. Temperature affects the rate at
-which chemical reactions proceed, including metabolic reactions in organisms
-(Gillooly et al., 2001). A faster metabolism implies greater energy demands on
-an organism and therefore higher rates of herbivory, predation, and
-decomposition (Brown et al., 2004, Schemske et al., 2009). This greater
-activity tends to result in interactions with more species (Waser et al.,
-1996, Bascompte & Jordano, 2007), increasing the number of links per species
-and connectance at higher temperatures. Reduced competition due to either
-narrower niches or a broader niche space (Davies et al., 2007) could also lead
-to higher numbers of links per species and connectance, as species are free to
-pursue links with many partners rather than being restricted to the most
-profitable links. Specialist consumers tend to be more efficient at ingesting
-and assimilating prey (Montoya et al., 2006), suggesting that specialization
-is also likely at higher latitudes where productivity is low for much of the
-year (Field et al., 1998). Higher productivity is expected to result in longer
-food chains by relaxing the upper limits set by the inefficiency of energy
-transfer across trophic levels (Brown et al., 2004). This should produce a web
-with a lower proportion of basal species and more intermediate and top
-predators in food webs. Bitrophic networks should also show more higher-
-trophic-level and animal species, since they should experience the same
-relaxed productivity in their feeding links, even if those links are not
-explicitly considered in the networks used here.
-
-To test whether variability in the network structure of ecological networks
-can be reduced to a few ecologically meaningful dimensions, and whether these
-dimensions are associated with potential environmental drivers, we preformed
-principal components analyses on 97 multitrophic predator-prey (n=52) and
-bitrophic parasite-host and mutualist networks (n=45) that range across a
-latitudinal gradient from 52.35°S to 81.82°N. We ran additional analyses for
-network properties that had been standardized for differences in species
-richness and connectance to examine scale-independent variation in network
-structure. We hypothesized that, in the analyses of scale-dependent network
-properties, species richness and connectance would explain much of the
-variation in network structure and that, because of this, temperature and
-productivity would be strongly associated with major axes of variation.
-Networks were expected to contain more species at higher trophic levels and
-feature higher connectance and links per species closer to the equator. We
-expected these trends to continue in the standardized network properties, as
-many of the explanations for increasing species richness at lower latitudes
-should also affect other network properties directly.
+Here we examine the effect of latitude on food-web structure by examining
+its impact on the scaling relationships of food-web properties with species
+richness and connectance. We expect that food-web structure will scale strongly
+with both species richness and connectance, and that the scaling relationships
+of properties measuring degree of specialization (i.e., generality, vulnerability, and
+links per species) will change over latitude. The scaling relationships of other
+properties (for example the proportions of top, intermediate, and basal resources) may
+be less affected by latitude.
 
@@
 they are likely to have different food web properties than webs attempting to
-describe the entire community of a site. Also excluded were webs with poor
-resolution, describing highly modified or artificial ecosystems, or including
-humans.
+describe the entire community of a site. We also excluded webs describing highly
+modified or artificial ecosystems, and those including humans, as these could also
+have different structural properties to more ``natural'' food webs.
 
@@
 across different studies. We then classified them both according to latitude
-and ecosystem type (terrestrial, freshwater, marine, estuary). We analysed XX
+and ecosystem type (terrestrial, [[stream, lake (lump?)]], marine, estuary). We analysed XX
 food-web properties for each web (Table 1).
 
-In our analysis, we first addressed whether the diversity or complexity of our
-published food webs varies over latitude (expressed as degrees away from the
+In our analysis, we first addressed whether the diversity (S) or complexity (C, L/S) of our
+published food webs varied over latitude (expressed as degrees away from the
 equator regardless of direction) or factorial ecosystem type. We also included
@@
 for each of the logarithms of species richness, mean links per species, and
-connectance.
+connectance. These models were used to determine any latitudinal gradients in the food-web
+properties known to drive scaling relationships with other properties.
 
@@
 properties that were proportions, we used general linear models with a
-binomial distribution. All other food web properties were log-transformed.
+binomial error distribution. All other food web properties were log-transformed with a normal error distribution.
 When modelling the standard deviation of generality, this
@@
 \cite{} in order to isolate the model with the highest AIC. These best-fitting models were 
-then examined in detail.
-
-Significant slopes in the reduced models were taken to indicate scaling
-relationships with species richness or connectance. Significant interactions
-indicated differences in the scaling relationships over latitude. Different
-intercepts indicated differences between ecosystem types.
+then examined in detail. Significant slopes over species-richness or connectance were taken to indicate scaling
+relationships. Significant interactions with latitude indicated that these scaling relationships varied from the tropics
+to the poles. Different intercepts indicated differences between ecosystem types.
 

### 2014-06-13 manuscript/latitudepaper.tex
First draft of manuscript is almost done, bar graphs/tables.

@@
 richness.
-
-%% Useful for discussion:
-% These explanations for latitudinal gradients in species richness  suggest that
-% other network properties should also vary over temperature and/or
-% productivity, independent of species richness. Temperature affects the rate at
-% which chemical reactions proceed, including metabolic reactions in organisms
-% (Gillooly et al., 2001). A faster metabolism implies greater energy demands on
-% an organism and therefore higher rates of herbivory, predation, and
-% decomposition (Brown et al., 2004, Schemske et al., 2009). This greater
-% activity tends to result in interactions with more species (Waser et al.,
-% 1996, Bascompte & Jordano, 2007), increasing the number of links per species
-% and connectance at higher temperatures. Reduced competition due to either
-% narrower niches or a broader niche space (Davies et al., 2007) could also lead
-% to higher numbers of links per species and connectance, as species are free to
-% pursue links with many partners rather than being restricted to the most
-% profitable links. Specialist consumers tend to be more efficient at ingesting
-% and assimilating prey (Montoya et al., 2006), suggesting that specialization
-% is also likely at higher latitudes where productivity is low for much of the
-% year (Field et al., 1998). Higher productivity is expected to result in longer
-% food chains by relaxing the upper limits set by the inefficiency of energy
-% transfer across trophic levels (Brown et al., 2004). This should produce a web
-% with a lower proportion of basal species and more intermediate and top
-% predators in food webs. Bitrophic networks should also show more higher-
-% trophic-level and animal species, since they should experience the same
-% relaxed productivity in their feeding links, even if those links are not
-% explicitly considered in the networks used here.
 
@@
 \citet{Schleuning2012} propose that the latitudinal specialization gradient in mutualists derives from the gradient in 
-plant diversity, as high resource diversity may lead to more generalized consumers. As species richness in the food 
-webs in our dataset did not vary over latitude, it seems unlikely that this is the mechanism driving increased 
-generality in high-latitude food webs. As we also observed an increase in both mean and maximum trophic level with 
+plant diversity, as high resource diversity may lead to more generalized consumers.
+
+A contrary argument was proposed in an earlier study \citep{Vazquez2004}. In this study, it was noted that bipartite 
+networks such as plant-pollinator and host-parasite networks are typically highly nested (specialists interact with 
+subsets of the interaction partners of generalists), and that nestedness tends to increase with network size 
+\citep{Vazquez2004}. Therefore, as the number of species in a community increases the number of extreme specialists in 
+a community should increase and generality should decrease. Importantly, this argument suggests that latitude can 
+affect generality only indirectly via species richnes. As the networks in our dataset did not increase in size towards 
+the tropics, and there was an effect of latitude as well as species richness, it seems unlikely that either of these 
+two arguments holds.
+
+As we also observed an increase in both mean and maximum trophic level with 
 latitude, it is possible that high-trophic level species are also more apt to be generalists. Generalism may be an 
-important strategy for high-level consumers as their prey may be scarce or seasonal \citep{}.
+important strategy for high-level consumers as their prey may be scarce or seasonal \citep{}. These results also 
+suggest that the tropics may indeed have narrower niches \citep{}. Similar increases in geographic range size with 
+latitude (Rapoport's rule) have been found for mammals \citep{Letcher1994}, XX \citep{} and XX \citep{}. Large 
+geographic ranges imply climactic generalization \citep{Letcher1994}, but may also promote dietary generalization 
+(i.e., a species with a wide range may be more likely to eat a variety of different prey depending on what is 
+available). This is supported by the fact tha feeding on many prey within a trophic level (non-omnivorous generality) 
+has been shown to decrease population variability in zooplankton \citep{Romanuk2006}.
 

### 2014-06-13 code/Models.R
Plots now work.

@@ -60,6 +60,7 @@ x98_scale=glm(X98~(Latitude*Ecotype)*(log10(Connectance)+log10(Species))+(1|Year
 mean_SWTL_dredged=glm(log10(mean_SWTL)~(Latitude+Ecotype)*log10(Species)+(1|Year_pub))
 max_SWTL_dredged=glm(log10(max_SWTL)~Latitude*log10(Species)+Ecotype*log10(Connectance)+(1|Year_pub))
 int_dredged=glm(pInt~Latitude*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial')
+
 gen_dredged=glm(log10(Gen)~(Latitude*log10(Species)+Ecotype+Ecotype:log10(Species)+log10(Connectance))+(1|Year_pub))
 
 vulSD_dredged=glm(log10(VulSD)~Latitude+Ecotype+log10(Connectance)+log10(Species)+(1|Year_pub))

### 2014-06-13 code/generality_plots.py

@@ -1,0 +1,195 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText
+
+#Global mins, means, maxes. Doing by ecotype below.
+mean_C=0.1
+min_C=0.025
+max_C=0.25
+
+mean_S=36
+min_S=5
+max_S=109
+
+#Mean dist from centroids
+def linereader(fw_prop):
+  linefile="../mod_data/"+fw_prop+"_coeffs"
+  linetab=open(linefile,'r')
+  lines={}
+  for line in linetab:
+    if len(line.split())==5:
+      effect=line.split()[0][1:-1]
+      beta=float(line.split()[1])
+      lines[effect]=beta
+  return lines
+
+def datareader(fw_prop):
+  datafile="../mod_data/summary-properties.tsv"
+  f=open(datafile,'r')
+  datadict={'estuary':{},'lake':{},'terrestrial':{},'marine':{},'stream':{}}
+  for line in f:
+    if line.split()[0]=='Web':
+      heads=line.split()[1:]
+    else:
+      web=line.split()[0]
+      data=line.split()[1:]
+      Ecotype=line.split()[1]
+      if Ecotype in datadict:
+        datadict[Ecotype][web]={}
+        for term in range(0,len(heads)):
+          if term!='Ecotype':
+            datadict[Ecotype][web][heads[term]]=data[term]
+  return datadict
+
+def plotter(fw_prop,ecotype):
+  datadict=datareader(fw_prop)
+  lines=linereader(fw_prop)
+
+  realdata={}
+  realdata={'Species':[],'Connectance':[],'Latitude':[],fw_prop:[]}
+
+  for web in datadict[ecotype]:
+    for term in realdata:
+      realdata[term].append(float(datadict[ecotype][web][term]))
+
+  mean_C=float(sum(realdata['Connectance']))/len(realdata['Connectance'])
+  min_C=float(sorted(realdata['Connectance'])[1])
+  max_C=float(sorted(realdata['Connectance'])[-1])
+
+  mean_S=float(sum(realdata['Species']))/len(realdata['Species'])
[…]

### 2014-06-13 code/property_plots.py

@@ -138,7 +138,7 @@ def plotter(fw_prop):
       linedata[webtype].append(point)
 
   
-  grace=Grace(colors=ColorBrewerScheme('Spectral'))
+  grace=Grace(colors=ColorBrewerScheme('Paired'))
   graph=grace.add_graph()
 
   for webtype in linedata:
@@ -149,26 +149,27 @@ def plotter(fw_prop):
     data=graph.add_dataset(linedata[webtype],type='xy')
     data.symbol.shape=0
     if webtype=='marine':
-      colo=2
+      colo=3
     elif webtype=='stream':
-      colo=4
+      colo=11
     elif webtype=='estuary':
-      colo=6
+      colo=9
     elif webtype=='lake':
-      colo=8
+      colo=7
     else:
-      colo=10
+      colo=5
     data.legend=webtype
     data.line.configure(color=colo,linewidth=2)
 
     really=graph.add_dataset(realpoints,type='xy')
     really.line.type=0
-    really.symbol.color=colo
+    really.symbol.configure(color=colo,fill_color=colo)
 
 
   graph.world.xmax=90
   graph.world.xmin=0
   graph.world.ymax=int(sorted(realdata['marine'][fw_prop])[-1])+2
+  graph.legend.configure(loc=(1.1,.5),loctype='view')
 
   graph.xaxis.label.configure(text='Degrees from equator',char_size=1)
   graph.xaxis.tick.configure(major=10,major_size=1,minor_size=.7)

### 2014-06-13 code/Models.R
Reorder only.

@@ -59,9 +59,9 @@ x98_scale=glm(X98~(Latitude*Ecotype)*(log10(Connectance)+log10(Species))+(1|Year
 
 mean_SWTL_dredged=glm(log10(mean_SWTL)~(Latitude+Ecotype)*log10(Species)+(1|Year_pub))
 max_SWTL_dredged=glm(log10(max_SWTL)~Latitude*log10(Species)+Ecotype*log10(Connectance)+(1|Year_pub))
-int_dredged=glm(pInt~Latitude*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial')
-
 gen_dredged=glm(log10(Gen)~(Latitude*log10(Species)+Ecotype+Ecotype:log10(Species)+log10(Connectance))+(1|Year_pub))
+
+int_dredged=glm(pInt~Latitude*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial') #No sig. scaling.
 
 vulSD_dredged=glm(log10(VulSD)~Latitude+Ecotype+log10(Connectance)+log10(Species)+(1|Year_pub))
 path_dredged=glm(log10(Path)~Latitude+Ecotype*log10(Connectance)+(1|Year_pub))

### 2014-06-18 manuscript/latitudepaper.tex
Added tables explaining food web properties, full models for S, C, LS.

@@
+\documentclass[12pt]{article}  
+\usepackage{amsmath}
+\usepackage{url}
+\usepackage[dvips]{graphicx}
+\usepackage{multirow}
+\usepackage{geometry}
+\usepackage{pdflscape}
+%\usepackage{rotating}
+% make Figure 1 etc bold
+\usepackage[labelfont=bf]{caption}
+\usepackage{setspace}
+
+\usepackage[running]{lineno}
+
+% let's get some nature formatted citations
+%\usepackage{overcite}
+\usepackage[round]{natbib}
+
+% some cheats to reduce the need to type complicated bits and pieces
+\newcommand{\expect}[1]{\left\langle #1 \right\rangle}
+\newcommand{\etal}{\textit{et al.\ }}
+
+\newcommand{\beginsupplement}{%
+        \setcounter{table}{0}
+        \renewcommand{\thetable}{S\arabic{table}}%
+        \setcounter{figure}{0}
+        \renewcommand{\thefigure}{S\arabic{figure}}%
+     }
+
+% the abstract formatting
+\newenvironment{sciabstract}{%
+\begin{quote} \bf}
+{\end{quote}}
+\renewcommand\refname{References}
+
+% margin sizes`
+\topmargin 0.0cm
+\oddsidemargin 0.2cm
+
+\textwidth 16cm 
+\textheight 21cm
+\footskip 1.0cm
+
+\title{Scaling laws of trophic level and generality vary across latitude}
+\author{Alyssa Cirtwill, Tamara Romanuk?}
+\date{$^1$School of Biological Sciences\\University of Canterbury\\
+Private Bag 4800\\Christchurch 8140, New Zealand}
+
+\begin{document}
+\maketitle
+\baselineskip=8.5mm
+
+\vspace{0.4 in}
+
 \section*{Introduction}
@@
 (the proportion of possible links that are realized) and other food-web properties \citep{Riede2010}.
-These relationships have suggested that the structure of food webs is highly scale-depended which here refers to the
-strong dependence of network properties, such as fractions of
-species in different trophic groups, on the species richness or connectance of
-the networks \citep{Riede2010}. Therefore it is likely that much variation in network structure
-can be explained by variation in these two properties (Vermaat et al., 2009).
+These relationships have suggested that the structure of food webs is highly scale-dependent. 
+Specifically, network properties such as fractions of species in different trophic groups 
+have been shown to strongly depend on the species richness or connectance of
+the networks \citep{Vermaat2009,Riede2010}.
 
@@
 on food-web properties such that they change over latitude beyond the expected changes due to changing species richness. For 
-example, if niche sizes vary with latitude then generality (mean number of prey per predator), vulnerability (mean number of 
-predators per prey), and mean number of links per species may all vary with latitude beyond variation due to changes in species
-richness.
+example, if niche sizes vary with latitude then mean numbers of predators, prey, and links per species may also vary with 
+latitude. Some of this variation may be explained by variation in species richness, but as niche sizes are believed to be 
+related directly to latitude it is reasonable to expect that there may also be latitudinal effects unrelated to those of 
+changing species richness.
 
@@
 
-We compiled a list of XX published food webs from [database details]. We
+We compiled a list of 89 published food webs from the University of Canberra's GlobalWeb database (www.globalwebdb.com) \citep{}. We
 included only food webs with a clearly defined study site that did not cover
@@
 have different structural properties to more ``natural'' food webs.
+Where several food webs were constructed from the same study site, without obvious boundaries between ``sites'' (e.g. three food
+webs from Lake Nyasa), we aggregated the webs to form one summary web for the site. That is, we included all species and
+interactions observed in any of the the original webs for that site in the summary web.
+Similarly, we aggregated food webs created for the same location in different years. Both types of
+aggregation should help to combat a known problem with food webs, namely that infrequent interactions and
+rare species tend to be under-represented.
 
@@
 with the same predators and prey. This helps to reduce variation in resolution
-across different studies. We then classified them both according to latitude
-and ecosystem type (terrestrial, [[stream, lake (lump?)]], marine, estuary). We analysed XX
+across different studies.
+We then classified them both according to latitude
+and ecosystem type (terrestrial, stream, lake, marine, estuary). We then calculated 17
 food-web properties for each web (Table 1).
@@
 
-Second, we analysed the scaling relationships between the remaining XX food-
+Second, we analysed the scaling relationships between the remaining 14 food-
 web parameters and connectance and species richness. We used a series of
@@
 In this data set, none of the best fit models for species richness, connectance, or links per species included an 
-effect of latitude, although all three properties varied across ecosystem types. [[Table or something]]
+effect of latitude, although all three properties varied across ecosystem types (Table 2).
 
@@
 constant over latitude. Latitude terms were not included in the best-fit models for vulnerability, SD of generality or 
-SD of links. SD of vulnerability showed a weak negative relationship with latitude ($\Beta$=-0.001, $p$=0.056), 
+SD of links. SD of vulnerability showed a weak negative relationship with latitude ($\beta$=-0.001, $p$=0.056), 
 and path length increased with increasing 
-latitude ($\Beta$ = 0.005, $p$=0.045) but neither latitude effect affected any scaling with species richness or 
+latitude ($\beta$ = 0.005, $p$=0.045) but neither latitude effect affected any scaling with species richness or 
 connectance.
@@
 Maximum trophic level increased with 
-latitude ($\Beta=0.011$, $p$=0.011), but this relationship was weakened as species richness increased ($\beta$=-0.008, $
-p$=0.011). Similarly, maximum trophic level increased with species richness ($\beta$=0.430, $p$=0.003) except at very 
-high latitudes. Maximum trophic level decreased with connectance for estuarine food webs ($\beta$=-0.458, $p$=0.021), 
-varied little in lakes ($\beta$=-0.127, $p$=0.192), and increased with connectance in marine, stream, and terrestrial 
+latitude ($\beta=0.011$, $p$=0.011), but this relationship weakened as species richness increased 
+($\beta$=-0.008, $p$=0.011). Similarly, maximum trophic level increased with species richness ($\beta$=0.430, $p$=0.003) 
+except at very high latitudes. Maximum trophic level decreased with connectance for estuarine food webs 
+($\beta$=-0.458, $p$=0.021), varied little in lakes ($\beta$=-0.127, $p$=0.192), and increased with connectance in
+marine, stream, and terrestrial 
 food webs ($\beta$=0.219, $p$=0.005; $\beta$=0.249, $p$<0.001; and $\beta$=0.337, $p$=0.002, respectively). Taken 
@@
 all ecotypes and decreasing maximum trophic level with latitude at high species richness across all ecotypes 
-(Fig. \ref{}. At moderate levels of species richness, trophic level increased with latitude for estuarine webs, showed 
+(Fig. \ref{}). At moderate levels of species richness, trophic level increased with latitude for estuarine webs, showed 
 little change for lake webs, and decreased for all other ecotypes.
@@
 Generality showed the opposite trend, decreasing with increasing latitude ($\beta$=-0.017, $p$=0.003). This decrease 
-was counteracted by a positive interaction between latitude and species richness ($\beta$=0.013, $p$=0.003), with the net result that generality increased with latitude for most ecotypes and species richnesses (Fig.
-\ref{}).
+was counteracted by a positive interaction between latitude and species richness ($\beta$=0.013, $p$=0.003), with the net 
+result that generality increased with latitude for most ecotypes and species richnesses (Fig. \ref{}).
 The main effect of species richness on generality varied across ecotypes. Generality decreased with increasing species 
@@
 The tendency of food-web structure to exhibit scaling relationships with both species richness and connectance has been 
-well-established \citep{,,,,}. As species richness in particular is also know to vary systematically over latitude 
+well-established \citep{,,,,}. As species richness in particular is also known to vary systematically over latitude 
 \citep{,,,,}, intuitively one might suspect that the scaling relationships of other food web properties might also vary
-over latitude \citep{}. However, we found that only four of XX food web properties varied significantly over latitude, 
-and that only the scaling relationships of trophic level and generality varied from the tropics to the poles.
+over latitude \citep{}. However, we found that only five of 17 food web properties varied significantly over latitude, 
+and that only, of these, only mean and maximum trophi level and generality showed different scaling laws at different latitudes.
 
-A study of plant-animal mutualistic networks found the opposite trend to that observed here, that generality decreased 
-with increasing latitude while increasing with increasing plant diversity \citep{Schleuning2012}. Unfortunately this 
-study did not examine changes in scaling relationships over latitude... Regardless, this may indicate that food webs 
-and mutualistic networks vary differently over latitudinal gradients of productivity, temperature, etc. 
-\citet{Schleuning2012} propose that the latitudinal specialization gradient in mutualists derives from the gradient in 
-plant diversity, as high resource diversity may lead to more generalized consumers.
-
-A contrary argument was proposed in an earlier study \citep{Vazquez2004}. In this study, it was noted that bipartite 
-networks such as plant-pollinator and host-parasite networks are typically highly nested (specialists interact with 
-subsets of the interaction partners of generalists), and that nestedness tends to increase with network size 
-\citep{Vazquez2004}. Therefore, as the number of species in a community increases the number of extreme specialists in 
-a community should increase and generality should decrease. Importantly, this argument suggests that latitude can 
-affect generality only indirectly via species richnes. As the networks in our dataset did not increase in size towards 
-the tropics, and there was an effect of latitude as well as species richness, it seems unlikely that either of these 
-two arguments holds.
-
-As we also observed an increase in both mean and maximum trophic level with 
-latitude, it is possible that high-trophic level species are also more apt to be generalists. Generalism may be an 
-important strategy for high-level consumers as their prey may be scarce or seasonal \citep{}. These results also 
+The lack of latitudinal gradients in most of the food-web properties considered here may be due to the lack of a latitudinal 
+gradient in species richness in this data set. If so, that strongly implies that the latitudinal gradients that were observed
+were driven by some other factor than latitudinal changes in species richness. As we observed increasing generality away from 
+the equator in conjunction with increasing trophic level, it appears that high-trophic level species are also more apt to be 
+generalists. Generalism may be an important strategy for high-level consumers as their prey may be scarce or 
+seasonal \citep{}. These results also 
 suggest that the tropics may indeed have narrower niches \citep{}. Similar increases in geographic range size with 
-latitude (Rapoport's rule) have been found for mammals \citep{Letcher1994}, XX \citep{} and XX \citep{}. Large 
+latitude (Rapoport's rule) have been found for mammals \citep{Letcher1994}, XX \citep{}, and XX \citep{}. Large 
 geographic ranges imply climactic generalization \citep{Letcher1994}, but may also promote dietary generalization 
@@
 
-[[other scaling paper]]
+This contrasts with an earlier study of plant-animal mutualistic networks which found that generality increased in the tropics
+\citep{Schleuning2012}. That increase in generality was attributed to increasing species richness, as high resource diversity 
+might lead to generalized consumers \citep{Schleuning2012}. Unfortunately, this study did not investigate the scaling 
+relationship of species richness with generality, so it is not clear whether a latitudinal gradient in species richness was 
+responsible for the latitudinal gradient in generality. Regardless, the opposite trends in generality between antagonistic 
+and mutualistic networks may indicate that different types of interactions between species are under different types of pressures
+and hence respond differently to changes in temperature, productivity, or other latitudinally-associated variables.
 
-The overall consistency of scaling laws over latitude is remarkable and suggests that food webs worldwide assemble 
-along similar ``rules'' regardless of temperature, productivity, or other latitudinal gradients. However, the changing
-scaling laws for generality and trophic level suggest that there are also key differences in the ways that food webs 
-are configured in the tropics and at higher latitudes. Importantly, the opposing trends for generality in food webs 
-and mutualistic networks may suggest that latitude imposes different pressures on mutualistic versus antagonistic 
-interactions between species. [[Need a punchier conclusion]]
+% A contrary argument was proposed in an earlier study \citep{Vazquez2004}. In this study, it was noted that bipartite 
+% networks such as plant-pollinator and host-parasite networks are typically highly nested (specialists interact with 
+% subsets of the interaction partners of generalists), and that nestedness tends to increase with network size 
+% \citep{Vazquez2004}. Therefore, as the number of species in a community increases the number of extreme specialists in 
+% a community should increase and generality should decrease. Importantly, this argument suggests that latitude can 
+% affect generality only indirectly via species richnes. As the networks in our dataset did not increase in size towards 
+% the tropics, and there was an effect of latitude as well as species richness, it seems unlikely that either of these 
+% two arguments holds.
+
+\section*{Conclusion}
+
+While the overall consistency of scaling laws between species richness and connectance and other food-web properties is 
+remarkable, there are nonetheless signification variations in the scaling laws of trophic level and generality. These food web 
+properties vary both over latitude and across different network types. [[something punchy]]
+
+\newpage
+
+\section*{Tables}
+
+\begin{center}
+\begin{table}[!h]
+\caption{Symbols for and descriptions of food-web properties.}
+\label{symbols}
+\begin{tabular}{c l l}
+\hline
+Symbol      & Name & Description \\
+\hline
+S & Species richness & Number of trophic species \\
+LS & Links per species & Mean number of links per taxon \\
+C & Connectance & Number of observed links divided by the number of possible links ($L/S^{2}$) \\
+\%Top & \% Top predators & Percentage of taxa without consumers \\
+\%Int & \% Intermediate consumers & Percentage of taxa with both consumers and resources \\
+\%Basal & \% Basal Resources & Percentage of taxa without resources \\
+\%Herb	& \% Herbivores	& Percentage of herbivores and detrivores (taxa that feed on basal taxa) \\
+\%Omni & \%Omnivores & Percentage of omnivores (taxa that feed on ≥2 taxa with different trophic levels) \\
+Gen & Generality & Mean number of resources per taxon \\
+GenSD & SD of generality & Standard deviation of resources per taxon \\
+Vul & Vulnerability & Mean number of consumers per taxon \\
+VulSD & SD of vulnerability & Standard deviation of consumers per taxon \\
+LinkSD & SD of links per species & Standard deviation of links (consumers and resources) per taxon \\
+SWTL & Mean short-weighted trophic level & Short-weighted trophic level averaged across taxa \\
+Path & Path length & Characteristic path length, the mean shortest food chain between species pairs \\
+\hline
+\end{tabular}
+\end{table}
+% NODF & Average Nestedness & Degree to which interactions among specialists are subsets or interactions among generalists \\
+% Chain & Chain length & Mean food chain length \\
+% Cluster & Clustering coefficient & Mean clustering coefficient (probability that two taxa linked to the same taxon are also linked) \\
+
+\begin{center}
+\begin{table}[!h]
+\caption{Full models for S, LS, and C.}
+\label{symbols}
+\begin{tabular}{c c c c c c c}
+\hline
+ & \multicolumn{2}{S} & \multicolumn{2}{C} & \multicolumn{2}{LS} \\
+\hline
+Effect & Estimate & $p$-value & Estimate & $p$-value & Estimate & $p$-value \\
+\hline
+Latitude 			& 0.002  & 0.870  & -0.006 & 0.460  & -0.004 & 0.6115 \\ 
+Estuary 			& 1.078  & 0.018  & -0.809 & 0.008  & 0.269 & 0.363 \\
+Lake 				& 1.351  & 0.002  & -1.069 & <0.001 & 0.282 & 0.315 \\
+Marine 				& 1.127  & <0.001 & -0.761 & <0.001 & 0.366 & 0.012 \\
+Stream 				& 1.319  & <0.001 & -1.260 & <0.001 & 
+Terrestrial 		& 1.097  & <0.001 & -0.919 & <0.001 & 
+Latitude:Lake 		& -0.004 & 0.796  & 0.011  & 0.314  & 
+Latitude:Marine 	& 0.003  & 0.842  & 0.001  & 0.896  & 
+Latitude:Stream 	& 0.004  & 0.780  & 0.009  & 0.310  & 
+Latitude:Terrestrial & 0.001 & 0.920  & 0.003  & 0.712  &
+
+\newpage
+
+\bibliographystyle{jae}%Compile with jae.bst style file
+\bibliography{noISN}
+
+\end{document}

### 2014-06-19 manuscript/latitudepaper.tex
Aggregated lakes and streams as 'freshwaters' for simpler analysis.

@@
 We then classified them both according to latitude
-and ecosystem type (terrestrial, stream, lake, marine, estuary). We then calculated 17
-food-web properties for each web (Table 1).
+and ecosystem type (terrestrial, freshwater, marine, or estuary). We then calculated 17
+food-web properties for each web (Table \ref{symboltable}).
 
@@
 For the food-web properties that did scale with species-richness or connectance, most of these relationships were 
-constant over latitude. Latitude terms were not included in the best-fit models for vulnerability, SD of generality or 
-SD of links. SD of vulnerability showed a weak negative relationship with latitude ($\beta$=-0.001, $p$=0.056), 
-and path length increased with increasing 
-latitude ($\beta$ = 0.005, $p$=0.045) but neither latitude effect affected any scaling with species richness or 
-connectance.
+constant over latitude. Latitude terms were not included in the best-fit models for SD of generality or 
+SD of links. Best-fit models for vulnerability, SD of vulnerability, and path length included latitude terms but showed 
+very weak relationships ($\beta$=3.52 x $10^{-17}$, $p$=0.170; $\beta$=-0.001, $p$=0.050; and $\beta$=0.005, $p$=0.069; 
+respectively). None of the above models included an effect of latitude on scaling with S or C.
 
-The scaling rules of mean and maximum trophic level and generality varied over latitude. 
-Maximum trophic level increased with 
-latitude ($\beta=0.011$, $p$=0.011), but this relationship weakened as species richness increased 
-($\beta$=-0.008, $p$=0.011). Similarly, maximum trophic level increased with species richness ($\beta$=0.430, $p$=0.003) 
-except at very high latitudes. Maximum trophic level decreased with connectance for estuarine food webs 
-($\beta$=-0.458, $p$=0.021), varied little in lakes ($\beta$=-0.127, $p$=0.192), and increased with connectance in
-marine, stream, and terrestrial 
-food webs ($\beta$=0.219, $p$=0.005; $\beta$=0.249, $p$<0.001; and $\beta$=0.337, $p$=0.002, respectively). Taken 
-together, these effects resulted in an increase in maximum trophic level with latitude at low species richnesses across 
-all ecotypes and decreasing maximum trophic level with latitude at high species richness across all ecotypes 
-(Fig. \ref{}). At moderate levels of species richness, trophic level increased with latitude for estuarine webs, showed 
-little change for lake webs, and decreased for all other ecotypes.
+The scaling rules of mean trophic level and generality, however, did vary over latitude. 
+Mean trophic level increased with latitude ($\beta$=0.011, $p$<0.001) and with species richness 
+($\beta$=0.633, $p$<0.001), but both trends were weakened by an interaction between latitude and species-richness 
+($\beta$=-0.008, $p$=0.001). The best-fitting model for mean trophic 
+level did not include a connectance term. The increase in mean trophic level with species richness was highest for 
+estuarine food webs ($\beta$=0.633, $p$<0.001) and lower for freshwater ($\beta$=0.259, $p$=0.002), terrestrial 
+($\beta$=0.234, $p$=0.005), and marine food webs ($\beta$=0.152, $p$<0.001). For food webs with high species richness, 
+trophic level declined with latitude while trophic level in species-poor webs showed the opposite trend 
+(Fig. \ref{TLfig}). The number of species for which the slope of trophic level over latitude changed from negative to 
+positive varied across ecosystem types.
 
-Qualitatively similar trends were observed for mean trophic level. Mean trophic level increased with latitude 
-($\beta$=0.0109, $p$<0.001) and with species richness ($\beta$=0.616, $p$<0.001), but both trends were weakened by an 
-interaction between latitude and species-richness ($\beta$=-0.008, $p$<0.001). The best-fitting model for mean trophic 
-level did not include a connectance term. The increase in mean trophic level with species richness was highest for 
-estuarine food webs ($\beta$=0.616, $p$<0.001) and lower for lakes ($\beta$=-0.608, $p$=0.232), streams 
-($\beta$=0.238, $p$<0.001), terrestrial food webs ($\beta$=0.217, $p$=0.002), and marine food webs 
-($\beta$=0.133, $p$<0.001).
-
-Generality showed the opposite trend, decreasing with increasing latitude ($\beta$=-0.017, $p$=0.003). This decrease 
-was counteracted by a positive interaction between latitude and species richness ($\beta$=0.013, $p$=0.003), with the net 
-result that generality increased with latitude for most ecotypes and species richnesses (Fig. \ref{}).
-The main effect of species richness on generality varied across ecotypes. Generality decreased with increasing species 
-richness for estuarine webs ($\beta$=-0.058, $p$=0.003) and increased for lakes ($\beta$=0.220, $p$=0.245), 
-streams ($\beta$=0.543, $p$<0.001), terrestrial ($\beta$=0.603, $p$=0.005) and marine webs ($\beta$=0.761, $p$<0.001). 
-Generality increased with connectance equally for all ecotypes ($\beta$=0.875, $p$<0.001).
+Generality showed the opposite trend, increasing with latitude for webs with high species richness and decreasing with
+latitude for species-poor webs (Fig. \ref{genfig}).
+This increase was driven by a positive interaction between latitude and species richness ($\beta$=0.014, $p$=0.002), as 
+the main effect of latitude was negative ($\beta$=-0.018, $p$=0.002). Generality also decreased with species richness 
+for estuarine food webs ($\beta$=-0.150, $p$=0.002) but increased with species richness for freshwater, terrestrial, 
+and marine webs ($\beta$=0.453, $p$=0.005; $\beta$=0.523, $p$=0.006; and $\beta$=0.675, $p$=0.001; respectively). 
+Generality increased with connectance equally in all ecotypes and across all latitudes ($\beta$=0.799, $p$<0.001).
 
@@
 
-The lack of latitudinal gradients in most of the food-web properties considered here may be due to the lack of a latitudinal 
-gradient in species richness in this data set. If so, that strongly implies that the latitudinal gradients that were observed
-were driven by some other factor than latitudinal changes in species richness. As we observed increasing generality away from 
-the equator in conjunction with increasing trophic level, it appears that high-trophic level species are also more apt to be 
-generalists. Generalism may be an important strategy for high-level consumers as their prey may be scarce or 
-seasonal \citep{}. These results also 
-suggest that the tropics may indeed have narrower niches \citep{}. Similar increases in geographic range size with 
-latitude (Rapoport's rule) have been found for mammals \citep{Letcher1994}, XX \citep{}, and XX \citep{}. Large 
-geographic ranges imply climactic generalization \citep{Letcher1994}, but may also promote dietary generalization 
-(i.e., a species with a wide range may be more likely to eat a variety of different prey depending on what is 
-available). This is supported by the fact tha feeding on many prey within a trophic level (non-omnivorous generality) 
-has been shown to decrease population variability in zooplankton \citep{Romanuk2006}.
+The lack of latitudinal gradients in most of the food-web properties considered here may be due to the lack of a 
+latitudinal gradient in species richness in this data set. If so, that strongly implies that the latitudinal gradients 
+that were observed were driven by some other factor than latitudinal changes in species richness. As we observed 
+increasing generality away from 
+the equator in conjunction with decreasing trophic level (at least in high-S food webs), it appears that species nearer
+the top of the food web may be feeding on a wider variety of prey at the poles, lowering their trophic levels. 
+As both feeding on many prey within a trophic level (non-omnivorous generality) \citep{Romanuk2006} and feeding on many 
+trophic levels \citep{} have been shown to decrease population variability, high generality at higher latitudes may act 
+as ``insurance'' for upper-level consumers by allowing them to switch prey according to availability.
 
-This contrasts with an earlier study of plant-animal mutualistic networks which found that generality increased in the tropics
-\citep{Schleuning2012}. That increase in generality was attributed to increasing species richness, as high resource diversity 
-might lead to generalized consumers \citep{Schleuning2012}. Unfortunately, this study did not investigate the scaling 
-relationship of species richness with generality, so it is not clear whether a latitudinal gradient in species richness was 
-responsible for the latitudinal gradient in generality. Regardless, the opposite trends in generality between antagonistic 
-and mutualistic networks may indicate that different types of interactions between species are under different types of pressures
-and hence respond differently to changes in temperature, productivity, or other latitudinally-associated variables.
+This contrasts with an earlier study of plant-animal mutualistic networks which found that generality increased in the 
+tropics \citep{Schleuning2012}. That increase in generality was attributed to increasing species richness, as high 
+resource diversity might lead to generalized consumers \citep{Schleuning2012}. While we also found increasing 
+generality with increasing species richness in our dataset, it seems unlikely that higher species richness at the poles 
+is driving the observed trend in generality. This suggests that while mutualistic and antagonistic interactions may
+be similarly affected by species richness, they respond differently to other latitudinally-associated variables.
+
+[[High TL/low generality in species-poor food webs?]]
 
@@
 \caption{Symbols for and descriptions of food-web properties.}
-\label{symbols}
+\label{symboltable}
 \begin{tabular}{c l l}

### 2014-06-19 code/food_web_properties.py

@@ -248,14 +248,19 @@ def websorter(metafile,directory,motifdir):
       webfile='WEB'+str(webno)
       uselist.append(webfile)
       ecotype=items[3]
+      if ecotype in ['lake','stream']:
+        ecotype2='freshwater'
+      else:
+        ecotype2=ecotype
       year=items[6]
       latitude=items[10]
-      info=[ecotype,year,latitude]
+      info=[ecotype,ecotype2,year,latitude]
       infodict[webfile]=info
   f.close()
 
   header=['Web',
           'Ecotype',
+          'Ecotype2',
           'Year_pub',
           'Latitude',
           'Species',

### 2014-06-19 code/freshwater_models.R

@@ -1,0 +1,63 @@
+data=read.table('../mod_data/summary-properties.tsv',sep='\t',header=TRUE)
+attach(data)
+
+##################################
+##################################
+##    Part 1: testing S, C, LS over lat
+##################################
+##################################
+
+#Including year published as a random effect
+
+species_latbytype = glm(log10(Species)~Latitude*(Ecotype2-1)+(1|Year_pub))
+links_latbytype = glm(log10(LS)~Latitude*(Ecotype2-1)+(1|Year_pub))
+conn_latbytype = glm(log10(Connectance)~Latitude*(Ecotype2-1)+(1|Year_pub))
+
+#dredged models:
+species_min = glm(log10(Species)~Ecotype2-1+(1|Year_pub))
+links_min = glm(log10(LS)~Ecotype2-1+(1|Year_pub))
+conn_min = glm(log10(Connectance)~Ecotype2-1+(1|Year_pub))
+
+##################################
+##################################
+##    Part 2: testing scaling relationships
+##################################
+##################################
+
+linkSD_scale=glm(log10(LinkSD)~(Latitude*Ecotype2)*(log10(Connectance)+log10(Species))+(1|Year_pub))
+gen_scale=glm(log10(Gen)~(Latitude*Ecotype2)*(log10(Connectance)+log10(Species))+(1|Year_pub))
+# 5 (very small) webs with 0 GenSD is messing with this. Eliminating  1  4 30 84 85 for this model.
+Gendata=data[data$GenSD!=0,]
+genSD_scale=with(Gendata,glm(log10(GenSD)~(Latitude*Ecotype2)*(log10(Connectance)+log10(Species))+(1|Year_pub)))
+vul_scale=glm(log10(Vul)~(Latitude*Ecotype2)*(log10(Connectance)+log10(Species))+(1|Year_pub))
+vulSD_scale=glm(log10(VulSD)~(Latitude*Ecotype2)*(log10(Connectance)+log10(Species))+(1|Year_pub))
+mean_SWTL_scale=glm(log10(mean_SWTL)~(Latitude*Ecotype2)*(log10(Connectance)+log10(Species))+(1|Year_pub))
[…]

### 2014-06-19 code/freshwater_plots.py

@@ -1,0 +1,231 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText
+
+#Global mins, means, maxes. Doing by ecotype below.
+mean_C=0.1
+min_C=0.025
+max_C=0.25
+
+mean_S=36
+min_S=5
+max_S=109
+
+propnames={'gen':'Gen','vul':'Vul','TL':'mean_SWTL','path':'Path'}
+
+#Mean dist from centroids
+def linereader(fw_prop):
+  linefile="../mod_data/fresh_"+fw_prop+".coeffs"
+  linetab=open(linefile,'r')
+  lines={}
+  for line in linetab:
+    if len(line.split())==5:
+      effect=line.split()[0][1:-1]
+      beta=float(line.split()[1])
+      lines[effect]=beta
+  return lines
+
+def datareader(fw_prop):
+  datafile="../mod_data/summary-properties.tsv"
+  f=open(datafile,'r')
+  datadict={'estuary':{},'freshwater':{},'terrestrial':{},'marine':{}}
+  for line in f:
+    if line.split()[0]=='Web':
+      heads=line.split()[1:]
+    else:
+      web=line.split()[0]
+      data=line.split()[1:]
+      Ecotype=line.split()[1]
+      Ecotype2=line.split()[2]
+      if Ecotype2 in datadict:
+        datadict[Ecotype2][web]={}
+        for term in range(0,len(heads)):
+          if term not in ['Ecotype2','Ecotype']:
+            datadict[Ecotype2][web][heads[term]]=data[term]
+  return datadict
+
+def plotter(fw_prop):
+  lines=linereader(fw_prop)
+  datadict=datareader(fw_prop)
+
+  colors=ColorBrewerScheme('GnBu')
+  colors.add_color(255, 85, 66,"land")
+  colors.add_color(0,204,196,"fresh")
+  colors.add_color(20,167,204,"est")
+  colors.add_color(42,95,153,"marine")
+
+  grace=MultiPanelGrace(colors=colors)
+  grace.add_label_scheme("ecotypes",['terrestrial','freshwater','estuary','marine'])
+  grace.set_label_scheme("ecotypes")
+
[…]

### 2014-06-19 code/freshwater_models.R
.

@@ -45,12 +45,15 @@ omni_scale=glm(pOmni~(Latitude*Ecotype2)*(log10(Connectance)+log10(Species))+(1|
 mean_SWTL_dredged=glm(log10(mean_SWTL)~(Latitude+Ecotype2)*log10(Species)+(1|Year_pub))
 gen_dredged=glm(log10(Gen)~(Latitude*log10(Species)+Ecotype2+Ecotype2:log10(Species)+log10(Connectance))+(1|Year_pub))
 
-int_dredged=glm(pInt~Latitude*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial') #No sig. scaling.
-
+#NS
 vul_dredged=glm(log10(Vul)~Latitude*log10(Species)+log10(Connectance)+(1|Year_pub))
+int_dredged=glm(pInt~Latitude*(log10(Connectance)+log10(Species))+(1|Year_pub),family='binomial') #No sig. scaling.
 vulSD_dredged=glm(log10(VulSD)~Latitude+log10(Species)+log10(Connectance)+Ecotype2+(1|Year_pub))
+
+#Lat sig but doesn't affect scaling.
 path_dredged=glm(log10(Path)~Latitude+Ecotype2*log10(Connectance)+(1|Year_pub))
 
+#Ecoype only
 linkSD_dredged=glm(log10(LinkSD)~Ecotype2*log10(Connectance)+log10(Species)+(1|Year_pub))
 
 genSD_dredged=with(Gendata,glm(GenSD~log10(Connectance)+log10(Species)+(1|Year_pub)))

### 2014-06-23 manuscript/latitudepaper.tex
Try non-linear regressions next week.
Corrected table 2, inserted figures.

@@
 \vspace{0.4 in}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%%    Look into non-linear regressions for all properties (nls?)
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 trophic level declined with latitude while trophic level in species-poor webs showed the opposite trend 
-(Fig. \ref{TLfig}). The number of species for which the slope of trophic level over latitude changed from negative to 
+(Fig. \ref{TL_all}). The number of species for which the slope of trophic level over latitude changed from negative to 
 positive varied across ecosystem types.
@@
 Generality showed the opposite trend, increasing with latitude for webs with high species richness and decreasing with
-latitude for species-poor webs (Fig. \ref{genfig}).
+latitude for species-poor webs (Fig. \ref{gen_all}).
 This increase was driven by a positive interaction between latitude and species richness ($\beta$=0.014, $p$=0.002), as 
@@
 \end{table}
+\end{center}
 % NODF & Average Nestedness & Degree to which interactions among specialists are subsets or interactions among generalists \\
@@
 \hline
- & \multicolumn{2}{S} & \multicolumn{2}{C} & \multicolumn{2}{LS} \\
+ & \multicolumn{2}{c}{S} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{LS} \\
 \hline
@@
 \hline
-Latitude 			& 0.002  & 0.870  & -0.006 & 0.460  & -0.004 & 0.6115 \\ 
-Estuary 			& 1.078  & 0.018  & -0.809 & 0.008  & 0.269 & 0.363 \\
-Lake 				& 1.351  & 0.002  & -1.069 & <0.001 & 0.282 & 0.315 \\
-Marine 				& 1.127  & <0.001 & -0.761 & <0.001 & 0.366 & 0.012 \\
-Stream 				& 1.319  & <0.001 & -1.260 & <0.001 & 
-Terrestrial 		& 1.097  & <0.001 & -0.919 & <0.001 & 
-Latitude:Lake 		& -0.004 & 0.796  & 0.011  & 0.314  & 
-Latitude:Marine 	& 0.003  & 0.842  & 0.001  & 0.896  & 
-Latitude:Stream 	& 0.004  & 0.780  & 0.009  & 0.310  & 
-Latitude:Terrestrial & 0.001 & 0.920  & 0.003  & 0.712  &
+Latitude 			& 0.002  & 0.873  & -0.006 & 0.480  & -0.004 & 0.613 \\ 
+Estuary 			& 1.078  & 0.022  & -0.809 & 0.012  & 0.269 & 0.362 \\
+Freshwater 			& 1.347  & \textless0.001  & -1.229 & \textless0.001 & 0.118 & 0.394 \\
+Marine 				& 1.127  & \textless0.001 & -0.761 & \textless0.001 & 0.366 & 0.012 \\
+Terrestrial 		& 1.097  & \textless0.001 & -0.919 & \textless0.001 & 0.178 & 0.354\\
+Latitude:Freshwater & 0.002  & 0.902  & 0.010  & 0.299  & 0.012 & 0.194\\
+Latitude:Marine 	& 0.003  & 0.847  & 0.001  & 0.902  & 0.004 & 0.662 \\
+Latitude:Terrestrial & 0.001 & 0.923  & 0.003  & 0.724  & 0.005 & 0.597 \\
+\end{tabular}
+\end{table}
+\end{center}
 
 \newpage
+
+\section*{Figures}
+
+\begin{figure}[!h]
+\label{gen_all}
+\includegraphics[width=.9\textwidth]{Figures/gen_all.eps}
+\caption{Relationships between mean generality and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
+\end{figure}
+
+\begin{figure}[!h]
+\label{TL_all}
+\includegraphics[width=.9\textwidth]{Figures/TL_all.eps}
+\caption{Relationships between mean trophic level and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
+\end{figure}
 

### 2014-06-27 manuscript/latitudepaper.tex
Updated data file with labels for each site, new webs to use, locations of new webs.

@@
 
+I want to know: Does latitude affect scaling of generality with species richness?
+
+Considerations: Data quality (S<5 for some webs), model (log, nls, nlme)
+
+2) Add more webs (Riede 2010).
+    - pred-prey components of 7 parasite estuary webs
+    - Baird\&Ulanowicz - will need to be entered by hand (old pdf) - good quant web for concomitant project
+    - Heymans - look carefully at which webs to include, aggregate
+    - 
+3) Gen probably doesn't need to include connectance (LS doesn't, plus I don't actually care)
+5) LS, Gen (to compare more directly w mutualists) first.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Food webs (networks of feeding links between species) have been used for decades to summarize the structure of ecological communities \citep{Martinez2000,earlierwork}.
+Food webs (networks of feeding links between species) have been used for decades to summarize the structure of ecological communities \citep{Williams2000,earlierwork}.
 Comparisons of community structure around the world and across ecosystem types 
@@
 exhibits a strong latitudinal gradient, believed to be driven by varying productivity and temperature at different latitudes 
-\citep{Brown2004,Cardillo2005,Thompson2005,Davies2007}. An alternative view
+\citep{Hawkins2004,Cardillo2005,Thompson2005,Davies2007}. An alternative view
 posits that species' niches are narrower in the tropics, 
@@
 generality of associations between biological processes and environmental variables, suggest that variation in network structure 
-may also be explained by ecological gradients \citep{Baiser2011}. Importantly, some of these gradients may act directly 
+may also be explained by ecological gradients \citep{Baiser2012}. Importantly, some of these gradients may act directly 
 on food-web properties such that they change over latitude beyond the expected changes due to changing species richness. For 
@@
 
-We compiled a list of 89 published food webs from the University of Canberra's GlobalWeb database (www.globalwebdb.com) \citep{}. We
-included only food webs with a clearly defined study site that did not cover
-more than 10 degrees of latitude. Source and sink webs were also excluded as
-they are likely to have different food web properties than webs attempting to
-describe the entire community of a site. We also excluded webs describing highly
+We compiled a list of 345 food webs from the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
+\citep{}. Of these, 302 webs had accessible original sources. 
+18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
+to have different food web properties than webs attempting to
+describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
+competition-focused networks
+\citep{Riede2010}. Of the remaining 230 food webs, we excluded one paleoweb (comprised of probable interactions between 
+extinct species) \citep{Simenstad1978} and five ``generalized schemes'' 
+\citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
+we wished to measure
+directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
+the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
+\citep{Vinogradov1978}, such that it is not clear which site the food web represents. [[[SI table of rejected webs, and why]]] 
+[Explain Thompson, Preston, Amundsen separate from Dunne.]
+This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans. 
+We supplemented these networks with the free-living components of eight high-resolution estuarine food webs \citep{Dunne2013,Thompson2005} and two lake food web \citep{Preston2012,Amundsen2013} that 
+included parasites, as well as XX webs that have been used in previous studies of food-web scaling.
+
+Where the latitude of a study site was not 
+explicitly stated, latitude was inferred based on Google Earth \citep{} coordinates of the described site.
+
+. We also excluded webs describing highly
 modified or artificial ecosystems, and those including humans, as these could also
@@
 \bibliographystyle{jae}%Compile with jae.bst style file
-\bibliography{noISN}
+\bibliography{My_Collection}
 

### 2014-06-27 code/freshwater_models.R

@@ -1,5 +1,32 @@
 data=read.table('../mod_data/summary-properties.tsv',sep='\t',header=TRUE)
 
+###Binary codings for ecotypes
+
+data$Estuary=0
+data$Lake=0
+data$Marine=0
+data$Stream=0
+data$Terr=0
+
+for(i in 1:length(data$Ecotype)){
+  if(data$Ecotype[i]=='estuary'){
+    data$Estuary[i]=1  }}
+
+for(i in 1:length(data$Ecotype)){
+  if(data$Ecotype[i]=='lake'){
+    data$Lake[i]=1  }}
+
+for(i in 1:length(data$Ecotype)){
+  if(data$Ecotype[i]=='marine'){
+    data$Marine[i]=1  }}
+
+for(i in 1:length(data$Ecotype)){
+  if(data$Ecotype[i]=='stream'){
+    data$Stream[i]=1  }}
+
+for(i in 1:length(data$Ecotype)){
+  if(data$Ecotype[i]=='terrestrial'){
+    data$Terr[i]=1  }}
 
 ## Testing which is better for LS, log or nls:
 
@@ -15,13 +42,13 @@ y=data$LS
 
 
 LS_full=with(data,glm(log10(LS)~log10(Species)+log10(Species):Latitude+log10(Species):(Fresh+Marine+Terr)+log10(Species):Latitude:(Fresh+Marine+Terr)+Year_pub))
-LS_min=with(data,glm(log10(LS)~log10(Species)+log10(Species):Fresh+log10(Species):Marine+log10(Species):Latitude+log10(Species):Latitude:Fresh))
+LS_min=with(data,glm(log10(LS)~log10(Species)+log10(Species):Lake+log10(Species):Stream+log10(Species):Marine+log10(Species):Latitude+log10(Species):Latitude:Lake+log10(Species):Latitude:Stream)
 
-Gen_full=with(data,glm(log10(Gen)~log10(Species)+log10(Species):Latitude+log10(Species):(Fresh+Marine+Terr)+log10(Species):Latitude:(Fresh+Marine+Terr)+Year_pub))
-Gen_min=with(data,glm(log10(Gen)~log10(Species)+log10(Species):Fresh+log10(Species):Latitude+log10(Species):Latitude:Fresh+Year_pub))
[…]

### 2014-06-27 manuscript/latitudepaper.tex
Added a to-do list.

@@
 competition-focused networks
-\citep{Riede2010}. Of the remaining 230 food webs, we excluded one paleoweb (comprised of probable interactions between 
-extinct species) \citep{Simenstad1978} and five ``generalized schemes'' 
+\citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
+between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
 \citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 

### 2014-06-27 code/listcreator.py
Listcreator now set up to only do necessary (i.e. new) webs.

@@ -5,85 +5,7 @@ import random
 from decimal import *
 from math import *
 
-def create_aggregated_web(fillist,directory):
-
-  predpreydict={}
-  specieslist=set()
-  for fil in fillist:
-    rowdict={}
-
-    webfile = directory+'/'+fil+'.csv'
-    f=open(webfile,'r')
-    for line in f:
-      newline=line.split('\n')[0] #Trims off extraneous newline
-      items=newline.split(',')
-      if '' not in items[1:]:
-        rowdict[items[0]]=items[1:]
-    f.close()
-
-    for row in rowdict:
-      for item in rowdict[row]:
-        try:
-          item = int(item)
-        except:
-          predators = row
-
-    for item in rowdict[predators]:
-      position = rowdict[predators].index(item)
-      specieslist.add(item)
-      preylist=[]
-      for row in rowdict:
-        specieslist.add(row)
-        if row != predators:
-          try:
-            if rowdict[row][position]!='0':
-              preylist.append(row)
-          except:
-            print fil, row
-            print rowdict[predators][position], position
-          
-      predpreydict[item]=preylist
-
-  numberdict={}
-  i = 1
-  for species in specieslist:
-    numberdict[species]=i
-    i=i+1
-
-  webname=re.findall(r'WEB(\d+)',webfile)[0]
-
-  decodefile=open('Food-web-database/species-keys/agg-webs/'+webname,'w')
-  for species in specieslist:
-    decodefile.write(species+'\t'+str(numberdict[species])+'\n')
-  decodefile.close()  
-
-  g=open('Food-web-database/pred-prey-lists-to-use/WEB'+str(1000+int(webname)),'w')
-  for pred in rowdict[predators]:
-    for prey in predpreydict[pred]:
-      g.write(str(numberdict[pred])+'\t'+str(numberdict[prey])+'\n')
-  g.close()
-
 def create_predprey_list(webfile):
-
-  Ruzicka=['WEB320','WEB321','WEB322','WEB323','WEB324']
-  Fryer=['WEB33','WEB38','WEB39','WEB204']
[…]

### 2014-07-01 manuscript/latitudepaper.tex
Old changes.
Started doing some edits to methods.

@@
 
-. We also excluded webs describing highly
-modified or artificial ecosystems, and those including humans, as these could also
-have different structural properties to more ``natural'' food webs.
-Where several food webs were constructed from the same study site, without obvious boundaries between ``sites'' (e.g. three food
-webs from Lake Nyasa), we aggregated the webs to form one summary web for the site. That is, we included all species and
-interactions observed in any of the the original webs for that site in the summary web.
-Similarly, we aggregated food webs created for the same location in different years. Both types of
-aggregation should help to combat a known problem with food webs, namely that infrequent interactions and
-rare species tend to be under-represented.
-
 We then converted each web to a trophic-species version by aggregating species
 with the same predators and prey. This helps to reduce variation in resolution
-across different studies.
+across different studies \citep{Dunne2013}.
 We then classified them both according to latitude
-and ecosystem type (terrestrial, freshwater, marine, or estuary). We then calculated 17
-food-web properties for each web (Table \ref{symboltable}).
+and ecosystem type (terrestrial, lake, stream, marine, or estuary). For each web, we calculated the 
+number of species (S), number of links (L), mean
+number of links per species (Z = L/S), mean generality (G, number of prey per consumer), and 
+mean vulnerability (V, number of predators per prey).
 
-In our analysis, we first addressed whether the diversity (S) or complexity (C, L/S) of our
-published food webs varied over latitude (expressed as degrees away from the
-equator regardless of direction) or factorial ecosystem type. We also included
-year published as in independent variable to control for changing standards
-for food web studies over time. We fit independent generalized linear models
-for each of the logarithms of species richness, mean links per species, and
-connectance. These models were used to determine any latitudinal gradients in the food-web
-properties known to drive scaling relationships with other properties.
+We were then able to assess the scaling relationships between Z, G, and V with S. Note that although most other food web
+properties scale with both species richness and connectance ($C = L/S^{2}$), Z can be expressed in terms of S
+alone \citep{Riede2010}. This is due to the fact that both C and Z are calculated using the same information. Since G and V are
+closely related to Z, they should also be explored in terms of S rather than S and C.
+
+Given the scaling relationship
+
+\begin{equation}
+
+	p = \alpha S^{\beta} \,,
+
+\end{equation}
+
+two methods of analysis are possible.
+One may analyse the equation on the original scale of measurement, assuming that error is normally and additively distributed.
+Alternatively, one may log-transform the equation to linearize it.
+An additive error term in the log-transformed equation would therefore correspond to a log-normal, multiplicative error term in the original formulation.
+As both types of error are common in biological power laws \citep{Xiao}, and lacking strong intuition about the true error distribution in our data, we fit and compared both types of models.
+
+There are also two possible ways to examine the effect of latitude on food-web properties.
+Latitude might have an effect independent of scaling with species richness, or it might affect the scaling relationship itself.
+The former question is analogous to regressing the residuals of the property against latitude while the latter examines the effect of latitude on the exponent $\beta$.
+In order to assess both possibilites, we examined the model
+
+\begin{equation}
+
+p_{w} = \alpha S_{w}^{\beta + \gamma \Delta_{w}0} + \rho \Delta_{w} + \eta_{w} \.,
+
+\end{equation}
+
+where $\Delta_{w}$ is the absolute latitude of food web $w$.
+
+[Log or normal, based on Xiao.]
 
@@
 latitude*ecotype*(log10(connectance)+log10(species richness))). For food web
-properties that were proportions, we used general linear models with a
+properties that were proportions, we used general linear models with a11111111
 binomial error distribution. All other food web properties were log-transformed with a normal error distribution.
@@
 
+%\end{spacing}
+\newpage
+\bibliographystyle{jae}%Compile with jae.bst style file
+\bibliography{noISN.bib}% your .bib file(s)
+
 \newpage
@@
 
-\bibliographystyle{jae}%Compile with jae.bst style file
-\bibliography{My_Collection}
-
 \end{document}

### 2014-07-04 manuscript/latitudepaper.tex
Fixed food web properties, edited manuscript. New story entirely now.

--- 2014-06-27 manuscript/latitudepaper.tex
@@
 
-I want to know: Does latitude affect scaling of generality with species richness?
-
-Considerations: Data quality (S<5 for some webs), model (log, nls, nlme)
-
-2) Add more webs (Riede 2010).
-    - pred-prey components of 7 parasite estuary webs
-    - Baird\&Ulanowicz - will need to be entered by hand (old pdf) - good quant web for concomitant project
-    - Heymans - look carefully at which webs to include, aggregate
-    - 
-3) Gen probably doesn't need to include connectance (LS doesn't, plus I don't actually care)
-5) LS, Gen (to compare more directly w mutualists) first.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
 Food webs (networks of feeding links between species) have been used for decades to summarize the structure of ecological communities \citep{Williams2000,earlierwork}.
-Comparisons of community structure around the world and across ecosystem types 
-have revealed that the structure of biological networks is generally tightly
-constrained, particularly by relationships between species richness or connectance
-(the proportion of possible links that are realized) and other food-web properties \citep{Riede2010}.
-These relationships have suggested that the structure of food webs is highly scale-dependent. 
-Specifically, network properties such as fractions of species in different trophic groups 
-have been shown to strongly depend on the species richness or connectance of
-the networks \citep{Vermaat2009,Riede2010}.
+One of the earliest goals of constructing food webs was to measure the relationship between the species richness of
+a community and its stability \citep{Dunne2006}, a goal which is still pursued today \citep{robustness studies}.
+Some authors have recognized the potential for environmental effects to influence stability \citep{Shurin2007}, as well as other food web properties such as food chain length \citep{Townsend1998,Thompson2003,2004c,Young2013,Digel2014}.
+Latitude is a particularly intruiging contender for an environmental influence on food web structure \citep{Shurin2007},
+as latitudinal gradients in temperature \citep{}, primary productivity \citep{}, body size \citep{}, and 
+species richness \citep{Schemske2009a} are among the most robust patterns in ecology[[back up from original draft]].
 
-As changes in species richness and connectance can explain much of the variation in network structure \citep{Vermaat2009}, 
-it follows that drivers of change in these two properties may also affect other properties. Species richness in particular 
-exhibits a strong latitudinal gradient, believed to be driven by varying productivity and temperature at different latitudes 
-\citep{Hawkins2004,Cardillo2005,Thompson2005,Davies2007}. An alternative view
-posits that species' niches are narrower in the tropics, 
-reducing competition and permitting greater adaptive radiation \citep{}. Although this view is only equivocally supported 
-\citep{Vazquez2004}, it is also possible that the higher productivity of the tropics \citep{Brown2004} may result in a broader 
+Latitude's strong influence on species richness, however, presents a problem for the analysis of food web structure.
+Although it was initially thought that food-web structure was small-world and scale invariant \citep{}, further 
+analyses with higher-quality data have revealed that most food-web structural properties scale strongly with species 
+richness, connectance (the proportion of possible links that are realized), or both \citep{Riede2010} 
+(see \citet{Dunne2006} for a review of the history of scaling laws in food web theory). This means that relationships
+between latitude and food-web structure must be considered in light of the latitudinal gradient in species richness.
+This is especially true for food-web properties that both scale with species richness and are related to candidate
+explanations for the latitudinal diversity gradient.
+
+% Explain niche space hypothesis, Schemske, Vazquez. Then make clear that niche space suggests opposite gradient to ~S^B.
+%Then give hypotheses.
+Here, we are particularly interested in the potential effects of latitude on scaling relationships for the number of
+links per species, generality (the number of prey per predator), and vulnerability (the number of predators per prey).
+We focus on these properties because they are related to one of leading candidates for a mechanism behind the 
+latitudinal species-richness gradient: namely that species' niches are narrow in the tropics, reducing competition
+and permitting greater adaptive radiation (reviewed in \citet{Vazquez2004}). Alternatively, it is  possible that the
+higher productivity of the tropics \citep{Brown2004} may result in a broader 
 niche space \citep{Davies2007} which could also allow greater diversification even if niche sizes are globally similar.
+In either case, if there is less competition at lower latitudes, there should also be less generality. A higher 
+proportion of non-competing specialists should also result in lower vulnerability.
+Importantly, these trends (lower generality, vulnerability, and hence links per species in the tropics) are opposite
+to those based on the positive scaling relationship between links per species and species richness \citep{Riede2010}.
+If, therefore, there is a latitudinal effect on generality and vulnerability beyond that of the latitudinal diversity
+gradient, the scaling relationships between species richness and links per species, generality, and vulnerability 
+should vary over latitude.
 
-In addition to species richness, there are general and robust latitudinal gradients in metabolic rates \citep{Stegen2012} and 
-rates and intensities of species interactions \citep{Marquis2005,Schemske2009}. These gradients, together with the strength and 
-generality of associations between biological processes and environmental variables, suggest that variation in network structure 
-may also be explained by ecological gradients \citep{Baiser2012}. Importantly, some of these gradients may act directly 
-on food-web properties such that they change over latitude beyond the expected changes due to changing species richness. For 
-example, if niche sizes vary with latitude then mean numbers of predators, prey, and links per species may also vary with 
-latitude. Some of this variation may be explained by variation in species richness, but as niche sizes are believed to be 
-related directly to latitude it is reasonable to expect that there may also be latitudinal effects unrelated to those of 
-changing species richness.
+%Among other things, a constant scaling between S and C implies that species tend to eat the same number of prey regarless of diversity \citep{Dunne2006,Pimm1982} - rephrase a bit more, this is very close.
 
-Here we examine the effect of latitude on food-web structure by examining
-its impact on the scaling relationships of food-web properties with species
-richness and connectance. We expect that food-web structure will scale strongly
-with both species richness and connectance, and that the scaling relationships
-of properties measuring degree of specialization (i.e., generality, vulnerability, and
-links per species) will change over latitude. The scaling relationships of other
-properties (for example the proportions of top, intermediate, and basal resources) may
-be less affected by latitude.
+% In addition to species richness, there are general and robust latitudinal gradients in metabolic rates \citep{Stegen2012} and 
+% rates and intensities of species interactions \citep{Marquis2005,Schemske2009}. These gradients, together with the strength and 
+% generality of associations between biological processes and environmental variables, suggest that variation in network structure 
+% may also be explained by ecological gradients \citep{Baiser2012}. Importantly, some of these gradients may act directly 
+% on food-web properties such that they change over latitude beyond the expected changes due to changing species richness. For 
+% example, if niche sizes vary with latitude then mean numbers of predators, prey, and links per species may also vary with 
+% latitude. Some of this variation may be explained by variation in species richness, but as niche sizes are believed to be 
+% related directly to latitude it is reasonable to expect that there may also be latitudinal effects unrelated to those of 
+% changing species richness.
 

### 2014-07-04 code/food_web_properties.py

@@ -154,7 +154,7 @@ def food_web_properties(directory,item):
     Path=sum(paths)/len(paths)
 
   stroutput=[]
-  outputs = [N,L,C,LS,LinkSD,Gen,GenSD,Vul,VulSD,Path,Clus] 
+  outputs = [int(N),int(L),float(C),float(LS),float(LinkSD),float(Gen),float(GenSD),float(Vul),float(VulSD),float(Path),float(Clus)] 
   for thing in outputs:
     stroutput.append(str(thing))
   return stroutput 
@@ -177,13 +177,15 @@ def websorter(metafile,directory,motifdir):
         webfile=webno+'.web'
       uselist.append(webfile)
       ecotype=items[3]
+      Humans=items[19]
+      Site=items[21]
       if ecotype in ['lake','stream']:
         ecotype2='freshwater'
       else:
         ecotype2=ecotype
       year=items[6]
       latitude=items[10]
-      info=[ecotype,ecotype2,year,latitude]
+      info=[ecotype,ecotype2,year,Humans,Site,latitude]
       infodict[webfile]=info
   f.close()
 

### 2014-07-04 code/freshwater_models.R

@@ -1,115 +1,0 @@
-data=read.table('../mod_data/summary-properties.tsv',sep='\t',header=TRUE)
-
-###Binary codings for ecotypes
-
-data$Estuary=0
-data$Lake=0
-data$Marine=0
-data$Stream=0
-data$Terr=0
-
-for(i in 1:length(data$Ecotype)){
-  if(data$Ecotype[i]=='estuary'){
-    data$Estuary[i]=1  }}
-
-for(i in 1:length(data$Ecotype)){
-  if(data$Ecotype[i]=='lake'){
-    data$Lake[i]=1  }}
-
-for(i in 1:length(data$Ecotype)){
-  if(data$Ecotype[i]=='marine'){
-    data$Marine[i]=1  }}
-
-for(i in 1:length(data$Ecotype)){
-  if(data$Ecotype[i]=='stream'){
-    data$Stream[i]=1  }}
-
-for(i in 1:length(data$Ecotype)){
-  if(data$Ecotype[i]=='terrestrial'){
-    data$Terr[i]=1  }}
-
-## Testing which is better for LS, log or nls:
-
-x=data$Species
-y=data$LS
-
-# power_analysis(x,y) based on http://www.esapubs.org/archive/ecol/E092/160/Sup_2_Guidelines.r
-# log-normal error better supported :)
-
-# For generality, vul: same
-
-# For TL: log-normal on both S and C. 
-
-
-LS_full=with(data,glm(log10(LS)~log10(Species)+log10(Species):Latitude+log10(Species):(Fresh+Marine+Terr)+log10(Species):Latitude:(Fresh+Marine+Terr)+Year_pub))
-LS_min=with(data,glm(log10(LS)~log10(Species)+log10(Species):Lake+log10(Species):Stream+log10(Species):Marine+log10(Species):Latitude+log10(Species):Latitude:Lake+log10(Species):Latitude:Stream)
-
-Gen_full=with(data,glm(log10(Gen)~log10(Species)+log10(Species):Latitude+log10(Species):(Lake+Stream+Marine+Terr)+log10(Species):Latitude:(Lake+Stream+Marine+Terr)+Year_pub))
-Gen_min=with(data,glm(log10(Gen)~log10(Species)+log10(Species):(Lake+Stream)+log10(Species):Latitude+log10(Species):Latitude:(Lake+Stream)+Year_pub))
-
[…]

### 2014-07-07 manuscript/latitudepaper.tex
Finished rebuilding intro, working on methods.

--- 2014-07-04 manuscript/latitudepaper.tex
@@
 
-\title{Scaling laws of trophic level and generality vary across latitude}
-\author{Alyssa Cirtwill, Tamara Romanuk?}
+\title{Generality in food webs scales with species richness, not latitude}
+\author{Alyssa Cirtwill, Tamara Romanuk?, Daniel Stouffer?}
 \date{$^1$School of Biological Sciences\\University of Canterbury\\
@@
 %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
-Food webs (networks of feeding links between species) have been used for decades to summarize the structure of ecological communities \citep{Williams2000,earlierwork}.
+Food webs (networks of feeding links between species) have been used for decades to summarize the structure of 
+ecological communities \citep{Williams2000,earlierwork}.
 One of the earliest goals of constructing food webs was to measure the relationship between the species richness of
 a community and its stability \citep{Dunne2006}, a goal which is still pursued today \citep{robustness studies}.
-Some authors have recognized the potential for environmental effects to influence stability \citep{Shurin2007}, as well as other food web properties such as food chain length \citep{Townsend1998,Thompson2003,2004c,Young2013,Digel2014}.
+Some authors have recognized the potential for environmental effects to influence both stability \citep{Shurin2007} and 
+other food web properties such as food chain length \citep{Townsend1998,Thompson2003,2004c,Young2013,Digel2014}.
 Latitude is a particularly intruiging contender for an environmental influence on food web structure \citep{Shurin2007},
@@
 This is especially true for food-web properties that both scale with species richness and are related to candidate
-explanations for the latitudinal diversity gradient.
+explanations for the latitudinal diversity gradient, such as measures of specialization.
 
@@
 %Then give hypotheses.
-Here, we are particularly interested in the potential effects of latitude on scaling relationships for the number of
-links per species, generality (the number of prey per predator), and vulnerability (the number of predators per prey).
-We focus on these properties because they are related to one of leading candidates for a mechanism behind the 
-latitudinal species-richness gradient: namely that species' niches are narrow in the tropics, reducing competition
-and permitting greater adaptive radiation (reviewed in \citet{Vazquez2004}). Alternatively, it is  possible that the
-higher productivity of the tropics \citep{Brown2004} may result in a broader 
-niche space \citep{Davies2007} which could also allow greater diversification even if niche sizes are globally similar.
-In either case, if there is less competition at lower latitudes, there should also be less generality. A higher 
-proportion of non-competing specialists should also result in lower vulnerability.
-Importantly, these trends (lower generality, vulnerability, and hence links per species in the tropics) are opposite
-to those based on the positive scaling relationship between links per species and species richness \citep{Riede2010}.
-If, therefore, there is a latitudinal effect on generality and vulnerability beyond that of the latitudinal diversity
-gradient, the scaling relationships between species richness and links per species, generality, and vulnerability 
-should vary over latitude.
+A latitudinal gradient in specialization lies behind the ``latitude-niche breadth hypothesis'' \citep{Vazquez2004}.
+This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
+turn should evolve smaller niches \citep{Vazquez2004}. These narrow niches should therefore allow more species to 
+coexist in the tropics than can at higher latitudes. Alternatively, higher productivity of the tropics \citep{Brown2004}
+may result in a broader niche space \citep{Davies2007} which could also allow greater diversification even if niche 
+sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocably 
+supported \citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
+richness \citep{Lappalainen2006,Krasnov2008,Slove2010}.
 
-%Among other things, a constant scaling between S and C implies that species tend to eat the same number of prey regarless of diversity \citep{Dunne2006,Pimm1982} - rephrase a bit more, this is very close.
+Importantly, the expectation of the latitude niche-breadth hypothesis that higher species richness is associated with 
+reduced competition is contary to the expected increase in the mean number of interactions per species (one potential 
+measure of specialization) as species richness increases \citep{Dunne2006,Riede2010}. If, therefore, there is a
+distinct effect of latitude on specialization then this effect should be visible in changing scaling relationships.
+Here, we tested the effect of latitude on scaling relationships between species richness and mean links per species, 
+mean generality (number of prey per predator), and mean vulnerability (number of predators per prey). Together, these
+properties provide a measure a species' biotic specialization - that is, its specialization in terms of interactions 
+with other species.
 
@@
 
-We compiled a list of 345 food webs from the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
-\citep{}. Of these, 302 webs had accessible original sources. 
-18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
-to have different food web properties than webs attempting to
-describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
-competition-focused networks
-\citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
-between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
-\citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
-we wished to measure
-directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
-the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
-\citep{Vinogradov1978}, such that it is not clear which site the food web represents. [[[SI table of rejected webs, and why]]] 
-[Explain Thompson, Preston, Amundsen separate from Dunne.]
-This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans. 
-We supplemented these networks with the free-living components of eight high-resolution estuarine food webs \citep{Dunne2013,Thompson2005} and two lake food web \citep{Preston2012,Amundsen2013} that 
-included parasites, as well as XX webs that have been used in previous studies of food-web scaling.
+\subsection*{Data Set}
+We compiled a list of XX empirical food webs from an online database (GlobalWeb webs \citep{GlobalWeb}), supplemented 
+with XX food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
+and seven food webs used to study the impact of parasites on network structure (ParWebs \citep{Dunne2013}).
+Of the GlobalWeb webs, XX were rejected because their original source could not be found (XX), they were source or sink
+webs rather than descriptions of an entire community (XX), were focused on plant-pollinator, host-parasitoid, or 
+competitive interactions (XX), described inferred interactions in an extinct community (2), were ``generalized 
+schemes'' rather than being based on empirical observation (5), or because it was not clear which of a variety of 
+described sites the published food web represented (1). (See Table S1 for a list of rejected webs and reasons for their
+exclusion.) For three GlobalWeb webs which included parasites as a minor component of the community, as well as the 
+seven ParWebs webs, we included a modified version of each web which included only free-living species and the 
+interactions between them \citep{Dunne2013}. For each of the XXX webs included in the final database, we recorded the
+study site latitude if possible or, where no latitude was given, obtained estimated coordinates of the described
+study site using Google Earth \citep{GoogleEarth}. Webs were also classified according to ecosystem type (terrestrial,
+lake, stream, estuary, or marine), year of publication (to control for changing standards of data collection over time \citep{Dunne2006}), and whether or not humans were included (11 webs included humans).
 
-Where the latitude of a study site was not 
-explicitly stated, latitude was inferred based on Google Earth \citep{} coordinates of the described site.
+We then converted each web to a trophic-species web by aggregating species with identical predator and prey sets.
+Using trophic species webs helps to reduce variation in resolution across different studies and across taxa within
+a study \citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}. The number of species ($S$) and links ($L$) in each 
+trophic species
+web were counted and used to calculate mean links per species ($Z$), generality ($G$), and vulnerability ($V$).
 
-. We also excluded webs describing highly
-modified or artificial ecosystems, and those including humans, as these could also
-have different structural properties to more ``natural'' food webs.
-Where several food webs were constructed from the same study site, without obvious boundaries between ``sites'' (e.g. three food
-webs from Lake Nyasa), we aggregated the webs to form one summary web for the site. That is, we included all species and
-interactions observed in any of the the original webs for that site in the summary web.
-Similarly, we aggregated food webs created for the same location in different years. Both types of
-aggregation should help to combat a known problem with food webs, namely that infrequent interactions and
-rare species tend to be under-represented.
+\subsection*{Scaling Relationships with S}
 
-We then converted each web to a trophic-species version by aggregating species
-with the same predators and prey. This helps to reduce variation in resolution
-across different studies.
-We then classified them both according to latitude
-and ecosystem type (terrestrial, freshwater, marine, or estuary). We then calculated 17
-food-web properties for each web (Table \ref{symboltable}).
+We were then able to examine the form of the scaling relationship between each property ($Z$, $G$, and $V$) and $S$.
+The scaling relationship between $Z$ and $S$ has been shown to be a power law \citep{Riede2010} of the form
 
-In our analysis, we first addressed whether the diversity (S) or complexity (C, L/S) of our
-published food webs varied over latitude (expressed as degrees away from the
-equator regardless of direction) or factorial ecosystem type. We also included
-year published as in independent variable to control for changing standards
-for food web studies over time. We fit independent generalized linear models
-for each of the logarithms of species richness, mean links per species, and
-connectance. These models were used to determine any latitudinal gradients in the food-web
-properties known to drive scaling relationships with other properties.
+\begin{equation}
+\label{Power}
+$Z=\alpha S^{\beta} + \epsilon $ \,,
+\end{equation}
 
-Second, we analysed the scaling relationships between the remaining 14 food-
-web parameters and connectance and species richness. We used a series of
-generalized linear models with a food-web parameter as the dependent variable
-and latitude, ecosystem type, and their interactions with connectance and
-species richness as independent variables. (parameter ~
-latitude*ecotype*(log10(connectance)+log10(species richness))). For food web
-properties that were proportions, we used general linear models with a
-binomial error distribution. All other food web properties were log-transformed with a normal error distribution.
-When modelling the standard deviation of generality, this
-required the removal of 5 webs, all with 12 or fewer species, which had
-standard deviations of generality of 0. These full models were then
-systematically reduced using R function dredge \cite{} in package MuMIn
-\cite{} in order to isolate the model with the highest AIC. These best-fitting models were 
-then examined in detail. Significant slopes over species-richness or connectance were taken to indicate scaling
-relationships. Significant interactions with latitude indicated that these scaling relationships varied from the tropics
-to the poles. Different intercepts indicated differences between ecosystem types.
+which is often re-expreseed in logarithmic form
+
+\begin{equation}
+\label{Loglog}
+$log(Z) = log(\alpha) + \beta log(S) + \epsilon $ \,.
+\end{equation}
+
+However, the two forms of the relationship imply different error structures: normally-distributed, additive error in 
+\ref{Power} and lognormal, multiplicative error in \ref{Loglog}. As there is no intuitive reason to believe that our
+data have one error distribution over another, we follow the recommendations in \citet{Xiao2011} and compared the two
+model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
+data was then used to test for potential effects of latitude.
+
+Although scaling relationships between $S$, $G$, and $V$ have not been explicitly examined (but see scaling 
+relationships for the standard devaitions of each property in \citet{Riede2010}), we expect that they will follow
+power laws similar to that of the relationship between $S$ and $Z$. This is because the links taken into account in
+calculating $G$ and $V$ are subsets of the total links included when calculating $Z$. As with $Z$, we explicitly 
+compared the error distributions of models for $G$ and $V$ using both the power-law and logarithmic formulations.
+
+\subsection*{Effect of Latitude}
+
+Logarithm of a sum is awful:   log(a+c) = log(a) + log(1+b^[log(c)-log(a)]) But can probably feed that into R...
+
+Once the best formulation of the relationship between each property and $S$ had been determined, we then assessed
+the impact of latitude on this relationship. There are two ways that properties might be affected by latitude:
+1) the slope of the scaling relationship with $S$ might vary over latitude or 2) the residuals $\epsilon$ might
+vary over latitude. In order to test both possibilities, we used models of the form
+
+\begin{equation}
+
+$Z=\alpha S^{\beta_{0}+\beta_{1}\delta} + \gamma\delta + \epsilon $ \,,
+
+\end{equation}
+
+where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction), ....
+
+% of  the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
+% \citep{}. Of these, 302 webs had accessible original sources. 
+% 18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
+% to have different food web properties than webs attempting to
+% describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
+% competition-focused networks
+% \citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
+% between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
+% \citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
+% we wished to measure
+% directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
+% the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
+% \citep{Vinogradov1978}, such that it is not clear which site the food web represents. 
+% This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans.
 

### 2014-07-08 manuscript/latitudepaper.tex
Changes to methods.

@@
 
-Logarithm of a sum is awful:   log(a+c) = log(a) + log(1+b^[log(c)-log(a)]) But can probably feed that into R...
+% Logarithm of a sum is awful:   log(a+c) = log(a) + log(1+b^[log(c)-log(a)]) But can probably feed that into R...
 
@@
 1) the slope of the scaling relationship with $S$ might vary over latitude or 2) the residuals $\epsilon$ might
-vary over latitude. In order to test both possibilities, we used models of the form
+vary over latitude. We were primarily interested in the first possibility, and so included a term for the effect of 
+latitude on the scaling exponent $\beta$ in equation \ref{Power}. In addition, as other studies have suggested that 
+food webs in different ecosystem types have characteristic structural differences, we included a dummy variable for 
+each ecosystem type (stream, lake, terrestrial, or marine, with estuary used as the `intercept' ecosystem type). 
+We also considered other trends in the data that could affect relationships between latitude and species richness.
+To account for changing standards in data collection over time \citep{Dunne2006} we included an effect of year of
+publication. As 11 of our XX webs included humans, and therefore might have different properties than other networks,
+we included a factorial effect of the presence of humans. Finally, some of our webs describe the same area in different
+seasons or different years. To account for likely correlation among these webs, we included a random effect of site ID.
+
+We therefore began by considering models of the form:
 
 \begin{equation}
-
-$Z=\alpha S^{\beta_{0}+\beta_{1}\delta} + \gamma\delta + \epsilon $ \,,
+\label{PowerLat}
+$Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\delta_{i}+\beta_{2}\Ecotype+\beta_{X}\delta_{i}\Ecotype}\Year_{i}\Humans_{i} + \epsilon_{i} $ \,,
 
@@
 
-where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction), ....
+where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction), 
+$\beta_{1}$ represents the effect of latitude on the scaling exponent $\beta$ in equation \ref{Power}. If the scaling
+relationship with S for a property suggested that lognormal error was more appropriate, we used the logarithmic re-
+expression:
+
+\begin{equation}
+\label{LogLat}
+$Z_{i}= log(\alpha)+\beta_{0}log(S) + \beta_{1}log(S)\delta_{i} +\beta_{2}log(S)Ecotype + \beta_{X}log(S)\delta_{i}Ecotype +log(year_{i}) +log(Humans_{i})  +\epsilon_{i} $ \,.
+
+\end{equation}
+
+We calculated the AIC of the chosen maximal model, as well as the AIC's of a suite of candidate simplified models.
+Simplified models were obtained by systematically removing all possible combinations of terms from the full model.
+The term for species richness was not removed from a model if any of the terms affecting the exponent $\beta$ were 
+included in the model. The model with the lowest AIC was selected as the best-fitting model. For power-law formulations
+this simplification was performed by hand. For logarithmic formulations, this simplification was performed using the
+R \citep{R} function dredge from package MuMIn \citep{MuMIn}. We then used the R \citep{R} function lmer
+from the package lmerTest \citep{lmerTest} to estimate the standardized effects ($\beta$s) for each fixed effect in the 
+best-fitting models, as well as their corresponding $p$-values.
 
@@
 \section*{Results}
+
+\subsection*{Scaling Relationships with S}
+
+For models of $Z$, $G$, and $V$, the assumption of multiplicative log-normal error was better supported (Table \ref{Errorfits}).
+We therefore use only models with logarithmic form for the remainder of the paper.
+
+\begin{tabular}
+
+\label{Errorfits}
+\caption{AIC's for model \ref{Power}, assuming normal error, and model \ref{Loglog}, assuming lognormal error.}
+\begin{table}{l | l l | c}
+Property & Normal error & Lognormal error & Model selected \\
+\hline
+$Z$ & 1151 &  767 & \ref{Loglog} \\
+$G$ & 1266 & 1037 & \ref{Loglog} \\
+$V$ & 1151 & 767 & \ref{Loglog} \\
+\end{table}
+\end{tabular}
 

### 2014-07-08 code/Models.R

@@ -2,6 +2,7 @@
 ## Power analysis function from http://www.esapubs.org/archive/ecol/E092/160/Sup_2_Guidelines.r
 ## Loading required packages. May need to be installed from CRAN.
 library(nlrwr)
+library(lmerTest)
 library(boot)
 ## Function to carry out the analytical process described in General Guidelines
 ## Input: x - vector, explanatory variable

### 2014-07-09 manuscript/latitudepaper.tex
Roughed out discussion, finished results. Still need to do figures.

@@
 
+\subsection*{Relationships with Latitude}
+
+We first examined simple linear relationships between latitude and $S$, $Z$, $G$, and $V$. We fit models of the form
+
+\begin{equation}
+
+S_{i} = \alpha_{0} + \alpha_{1}\Delta_{i}+\epsilon_{i} \,,
+
+\end{equation}
+
+where $S_{i}$ is the species richness of web $i$, $\Delta_{i}$ its absolute latitude (degrees north or south 
+regardless of direction), and $\epsilon_{i}$ a residual error term.
+These simple linear models, fit using the function lm in R \citep{R} package stats, were used to confirm that there are indeed latitudinal gradients in food-web structure in this data set.
+
 \subsection*{Scaling Relationships with S}
@@
 
-\subsection*{Effect of Latitude}
+\subsection*{Effect of Latitude on Scaling}
 
@@
 1) the slope of the scaling relationship with $S$ might vary over latitude or 2) the residuals $\epsilon$ might
-vary over latitude. We were primarily interested in the first possibility, and so included a term for the effect of 
-latitude on the scaling exponent $\beta$ in equation \ref{Power}. In addition, as other studies have suggested that 
+vary over latitude. To account for both possibilities we included terms for the effect of latitude on the scaling
+exponent $\beta$ in equation \ref{Power} as well as on the residual. In addition, as other studies have suggested that 
 food webs in different ecosystem types have characteristic structural differences, we included a dummy variable for 
@@
 \label{PowerLat}
-$Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\delta_{i}+\beta_{2}\Ecotype+\beta_{X}\delta_{i}\Ecotype}\Year_{i}\Humans_{i} + \epsilon_{i} $ \,,
+$Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\Delta_{i}+\beta_{3}\Sigma_{i} + \beta_{4}\Lambda_{i} + \beta_{5}\Tau_{i} + \beta_{6}\Mu_{i} 
++ \beta_{7}\Delta_{i}\Sigma_{i} + \beta_{8}\Delta_{i}\Lambda_{i} + \beta_{9}\Delta_{i}\Tau_{i} + \beta_{10}\Delta_{i}\Mu_{i}}
++ \rho{1}\Delta_{i} + \rho_{2}\Upsilon_{i} + \rho_{3}\Eta_{i} + P_{i} + \epsilon_{i} $ \,,
+\end{equation}
+
+where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
+$\Sigma_{i}$, $\Lambda_{i}$, $\Tau_{i}$, and $\Mu_{i}$ are 
+factors indicating whether web $i$ is a stream, lake, 
+terrestrial, or marine food web (e.g., $\Sigma_{i}$=1 for 
+a stream food web, 0 otherwise). If $\Sigma_{i}$, $\Lambda_{i}$, $\Tau_{i}$, and $\Mu_{i}$ are all 0, web $i$ 
+describes an estuary food web. $\Upsilon_{i}$ is the year web $i$ was published, $\Eta_{i}=1$ if web $i$ contains humans, 0 otherwise, and $P_{i}$ is a random effect of 
+site ID. Note that all fixed effects $\beta$ refer to factors acting on the scaling exponent between $Z$ and $S$
+while fixed effects $\rho$ refer to factors acting on the residual error.
+
+The logarithmic formulation of this model is:
+
+\begin{equation}
+\label{LogLat}
+$Z_{i}= log(\alpha)+\beta_{0}log(S) + \beta_{1}\Delta_{i}log(S) +\beta_{3}\Sigma_{i}log(S) + \beta_{4}\Lambda_{i}log(S)  + \beta_{5}\Tau_{i}log(S)  + \beta_{6}\Mu_{i}log(S)  
++ \beta_{7}\Delta_{i}\Sigma_{i}log(S)  + \beta_{8}\Delta_{i}\Lambda_{i}log(S)  + \beta_{9}\Delta_{i}\Tau_{i}log(S)  + \beta_{10}\Delta_{i}\Mu_{i}log(S) 
++ \rho_{1}\Delta_{i} + \rho_{2}\Upsilon_{i}) + \rho_{3}\Eta_{i} +\epsilon_{i} $ \,.
 
@@
 
-where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction), 
-$\beta_{1}$ represents the effect of latitude on the scaling exponent $\beta$ in equation \ref{Power}. If the scaling
-relationship with S for a property suggested that lognormal error was more appropriate, we used the logarithmic re-
-expression:
-
-\begin{equation}
-\label{LogLat}
-$Z_{i}= log(\alpha)+\beta_{0}log(S) + \beta_{1}log(S)\delta_{i} +\beta_{2}log(S)Ecotype + \beta_{X}log(S)\delta_{i}Ecotype +log(year_{i}) +log(Humans_{i})  +\epsilon_{i} $ \,.
-
-\end{equation}
+As in the power-law formulation, fixed effects $\beta$ 
+affect the scaling exponent and fixed effects $\rho$ 
+affect the (lognormal) residual.
 
@@
 R \citep{R} function dredge from package MuMIn \citep{MuMIn}. We then used the R \citep{R} function lmer
-from the package lmerTest \citep{lmerTest} to estimate the standardized effects ($\beta$s) for each fixed effect in the 
+from the package lmerTest \citep{lmerTest} to estimate the standardized effects ($\beta$s and $\rho$s) for each fixed effect in the 
 best-fitting models, as well as their corresponding $p$-values.
@@
 \section*{Results}
+
+\subsection*{Relationships with Latitude}
+
+$S$ and $G$ both increased with increasing latitude, contrary to expected latitudinal gradients (Table \ref{Latlms}). $G$ and $V$ were not significantly correlated with latitude.
+
+\begin{tabular}
+
+\label{Latlms}
+\caption{Intercepts and slopes for simple linear regressions of food web properties against absolute latitude.}
+\begin{table}{l | l l l l}
+\multirow{2}Property & \multicolumn{2}{c}{Intercept} & \multicolumn{2}{c}{Slope} \\
+ & $\alpha$ & $p$-value & $\alpha$ & $p$-value \\
+\hline
+$S$ & 23.10 & \textless0.001 & 0.284 & 0.040 \\
+$Z$ & 2.566 & \textless0.001 & 0.020 & 0.180 \\
+$G$ & 3.269 & \textless0.001 & 0.049 & 0.014 \\
+$V$ & 2.566 & \textless0.001 & 0.020 & 0.180 \\
+\end{table}
+\end{tabular}
 
@@
 In this data set, none of the best fit models for species richness, connectance, or links per species included an 
-effect of latitude, although all three properties varied across ecosystem types (Table 2).
-
-The best-fit models for most food-web properties exhibited scaling relationships with species-richness and/or 
-connectance. Notable exceptions were the proportions of basal resources, herbivores, and omnivores, which varied only 
-across year published; and the proportions of top predators and intermediate consumers, which varied with connectance 
-and species richness and connectance (respectively) although not significantly.
-
-For the food-web properties that did scale with species-richness or connectance, most of these relationships were 
-constant over latitude. Latitude terms were not included in the best-fit models for SD of generality or 
-SD of links. Best-fit models for vulnerability, SD of vulnerability, and path length included latitude terms but showed 
-very weak relationships ($\beta$=3.52 x $10^{-17}$, $p$=0.170; $\beta$=-0.001, $p$=0.050; and $\beta$=0.005, $p$=0.069; 
-respectively). None of the above models included an effect of latitude on scaling with S or C.
-
-The scaling rules of mean trophic level and generality, however, did vary over latitude. 
-Mean trophic level increased with latitude ($\beta$=0.011, $p$<0.001) and with species richness 
-($\beta$=0.633, $p$<0.001), but both trends were weakened by an interaction between latitude and species-richness 
-($\beta$=-0.008, $p$=0.001). The best-fitting model for mean trophic 
-level did not include a connectance term. The increase in mean trophic level with species richness was highest for 
-estuarine food webs ($\beta$=0.633, $p$<0.001) and lower for freshwater ($\beta$=0.259, $p$=0.002), terrestrial 
-($\beta$=0.234, $p$=0.005), and marine food webs ($\beta$=0.152, $p$<0.001). For food webs with high species richness, 
-trophic level declined with latitude while trophic level in species-poor webs showed the opposite trend 
-(Fig. \ref{TL_all}). The number of species for which the slope of trophic level over latitude changed from negative to 
-positive varied across ecosystem types.
-
-Generality showed the opposite trend, increasing with latitude for webs with high species richness and decreasing with
-latitude for species-poor webs (Fig. \ref{gen_all}).
-This increase was driven by a positive interaction between latitude and species richness ($\beta$=0.014, $p$=0.002), as 
-the main effect of latitude was negative ($\beta$=-0.018, $p$=0.002). Generality also decreased with species richness 
-for estuarine food webs ($\beta$=-0.150, $p$=0.002) but increased with species richness for freshwater, terrestrial, 
-and marine webs ($\beta$=0.453, $p$=0.005; $\beta$=0.523, $p$=0.006; and $\beta$=0.675, $p$=0.001; respectively). 
-Generality increased with connectance equally in all ecotypes and across all latitudes ($\beta$=0.799, $p$<0.001).
+effect of latitude on either the scaling exponent or residual (Table \ref{bestfits}). 
+$G$ increased slightly in more recent webs ($\rho{2}$=0.005, $p$<0.001), but the best-fit models for $V$ and $Z$ did not include a term for year of publication. 
+In contrast, $Z$ and $V$ were higher in lake food webs ($\beta_{4}$=0.10, $p$<0.001 and $\beta_{4}$=0.10, $p$<0.001, respectively) while the best-fit model for $G$ did not include an effect for any ecosystem type.
 
@@
 
-The tendency of food-web structure to exhibit scaling relationships with both species richness and connectance has been 
-well-established \citep{,,,,}. As species richness in particular is also known to vary systematically over latitude 
-\citep{,,,,}, intuitively one might suspect that the scaling relationships of other food web properties might also vary
-over latitude \citep{}. However, we found that only five of 17 food web properties varied significantly over latitude, 
-and that only, of these, only mean and maximum trophi level and generality showed different scaling laws at different latitudes.
+The tendency of food-web structure to exhibit scaling relationships with both
+species richness and connectance has been  well-established \citep{,,,,}. As
+species richness in particular is also known to vary systematically over
+latitude  \citep{,,,,}, intuitively one might suspect that any relationship
+between food-web properties such as generality might be due to the latitudinal
+gradient in species richness. Here, we found that while there were latitudinal
+gradients in species richness and generality, latitude was not related to
+either the scaling relationship between generality and species richness or the
+residuals of this scaling relationship.
 
-The lack of latitudinal gradients in most of the food-web properties considered here may be due to the lack of a 
-latitudinal gradient in species richness in this data set. If so, that strongly implies that the latitudinal gradients 
-that were observed were driven by some other factor than latitudinal changes in species richness. As we observed 
-increasing generality away from 
-the equator in conjunction with decreasing trophic level (at least in high-S food webs), it appears that species nearer
-the top of the food web may be feeding on a wider variety of prey at the poles, lowering their trophic levels. 
-As both feeding on many prey within a trophic level (non-omnivorous generality) \citep{Romanuk2006} and feeding on many 
-trophic levels \citep{} have been shown to decrease population variability, high generality at higher latitudes may act 
-as ``insurance'' for upper-level consumers by allowing them to switch prey according to availability.
+As the latitudinal gradient in species richness in this data set ran in the
+opposite direction to the general trend for angiosperms \citep{}, mammals
+\citep{}, birds \citep{}, marine organisms? \citep{}, we conclude that it is
+likely an artifact of the data set. Academic institutions have the longest
+history in temperate latitudes, and it may be that communities at these
+latitudes are better understood or more completely sampled. We do not believe
+that our observation of higher species richness at higher latitudes represents
+a true biological trend. As such, it does not seem likely that the increase in
+generality with latitude that we observed is due to an underlying tendency for
+species to pursue a wider variety of prey at higher latitudes. Rather, the
+trend in generality can be more parsimoniously explained by the trend in
+species richness.
 
-This contrasts with an earlier study of plant-animal mutualistic networks which found that generality increased in the 
-tropics \citep{Schleuning2012}. That increase in generality was attributed to increasing species richness, as high 
-resource diversity might lead to generalized consumers \citep{Schleuning2012}. While we also found increasing 
-generality with increasing species richness in our dataset, it seems unlikely that higher species richness at the poles 
-is driving the observed trend in generality. This suggests that while mutualistic and antagonistic interactions may
-be similarly affected by species richness, they respond differently to other latitudinally-associated variables.
+Our findings here add further doubt to the niche-breadth hypothesis, as
+narrower niches in the tropics were associated with lower species richness in
+this data set. It appears instead that, as more species are available, each
+species tends to consume more prey, be consumed by more predators, and have
+more links in general (check with figs). This makes intuitive sense as a more
+species-rich community is likely to have more species with similar behaviour
+and morphology that thereby have overlapping predator or prey sets.
 
-[[High TL/low generality in species-poor food webs?]]
+Parallel increases in generality and species richness across latitude have
+also been noted in studies of plant-pollinator networks (although in that case
+species richness was highest in the tropics) \citep{Schleuning2012}. Although
+the authors of that study do not explicitly examine the relationship between
+specialization and network size, they do cite increasing plant species
+richness as a potential driver for increasing generalization
+\citep{Schleuning2012}. Although the scaling of mutualist network structure
+does not appear to have been explored as systematically as that of unipartite
+food webs, some poperties such as nestedness \citep{Vazquez2004} and XX
+\citep{} have been shown to scale with species richness. As such scaling
+appears to be common to both antagonistic and mutualistic food webs, and
+trends in species richness can explain counterintuitive trends in network
+structure \citep{Schleuning2012}, it seems likely that many latitudinal trends
+in network structure are at least partly due to trends in species richness.
 
-% A contrary argument was proposed in an earlier study \citep{Vazquez2004}. In this study, it was noted that bipartite 
-% networks such as plant-pollinator and host-parasite networks are typically highly nested (specialists interact with 
-% subsets of the interaction partners of generalists), and that nestedness tends to increase with network size 
-% \citep{Vazquez2004}. Therefore, as the number of species in a community increases the number of extreme specialists in 
-% a community should increase and generality should decrease. Importantly, this argument suggests that latitude can 
-% affect generality only indirectly via species richnes. As the networks in our dataset did not increase in size towards 
-% the tropics, and there was an effect of latitude as well as species richness, it seems unlikely that either of these 
-% two arguments holds.
+%Nestedness increases with A+P, increases number of extreme specialists AND number of generalists. Not clear how degree should scale with S according to scaling with nestedness.
 
@@
 
-While the overall consistency of scaling laws between species richness and connectance and other food-web properties is 
-remarkable, there are nonetheless signification variations in the scaling laws of trophic level and generality. These food web 
-properties vary both over latitude and across different network types. [[something punchy]]
+It is not our intention here to question the validity of the wide range of
+studies exploring variation in network structure across changing environments.
+However, if those studies have not taken into account changes in species
+richness over environmental gradients, it is possible that observed changes in
+food-web structure are due only indirectly to the environmental variables of
+interest. Effects of environmental variables on network structure should
+therefore be interpreted with caution unless effects of changing species
+richness are made explicit.
 

### 2014-07-09 manuscript/latitudepaper.tex
Clean enough to pass along.

@@
 Food webs (networks of feeding links between species) have been used for decades to summarize the structure of 
-ecological communities \citep{Williams2000,earlierwork}.
-One of the earliest goals of constructing food webs was to measure the relationship between the species richness of
-a community and its stability \citep{Dunne2006}, a goal which is still pursued today \citep{robustness studies}.
-Some authors have recognized the potential for environmental effects to influence both stability \citep{Shurin2007} and 
-other food web properties such as food chain length \citep{Townsend1998,Thompson2003,2004c,Young2013,Digel2014}.
-Latitude is a particularly intruiging contender for an environmental influence on food web structure \citep{Shurin2007},
-as latitudinal gradients in temperature \citep{}, primary productivity \citep{}, body size \citep{}, and 
-species richness \citep{Schemske2009a} are among the most robust patterns in ecology[[back up from original draft]].
+ecological communities \citep{Williams2000,earlierwork} and to understand how that structure relates to environmental variables 
+such as land use \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, temperature?, latitude?. 
+Latitude is of particular interest as an environmental driver of food-web structure because it entails gradients in 
+temperature \citep{}, primary productivity \citep{}, and seasonality \citep{}. Importantly, there is also a strong
+latitudinal gradient in species richness for most taxa \citep{Schemske2009a}.
 
-Latitude's strong influence on species richness, however, presents a problem for the analysis of food web structure.
+This effect of latitude on species richness, however, presents a problem for the analysis of food web structure.
 Although it was initially thought that food-web structure was small-world and scale invariant \citep{}, further 
@@
 
-S_{i} = \alpha_{0} + \alpha_{1}\Delta_{i}+\epsilon_{i} \,,
+$S_{i} = \alpha_{0} + \alpha_{1}\Delta_{i}+\epsilon_{i}$ \,,
 
@@
 The tendency of food-web structure to exhibit scaling relationships with both
-species richness and connectance has been  well-established \citep{,,,,}. As
+species richness and connectance has been  well-established \citep{}. As
 species richness in particular is also known to vary systematically over
-latitude  \citep{,,,,}, intuitively one might suspect that any relationship
+latitude \citep{}, intuitively one might suspect that any relationship
 between food-web properties such as generality might be due to the latitudinal
@@
 As the latitudinal gradient in species richness in this data set ran in the
-opposite direction to the general trend for angiosperms \citep{}, mammals
-\citep{}, birds \citep{}, marine organisms? \citep{}, we conclude that it is
+opposite direction to the general trend for \citep{}, we conclude that it is
 likely an artifact of the data set. Academic institutions have the longest
 history in temperate latitudes, and it may be that communities at these
-latitudes are better understood or more completely sampled. We do not believe
-that our observation of higher species richness at higher latitudes represents
-a true biological trend. As such, it does not seem likely that the increase in
+latitudes are better understood or more completely sampled. As such, it does not seem likely that the increase in
 generality with latitude that we observed is due to an underlying tendency for

### 2014-07-09 manuscript/latitudepaper.tex
Fixed some of the equation issues.

@@
 
-\begin{equation}
-
-$S_{i} = \alpha_{0} + \alpha_{1}\Delta_{i}+\epsilon_{i}$ \,,
-
-\end{equation}
+\begin{eqnarray}
+S_{i} = \alpha_{0} + \alpha_{1} \Delta_{i} + \epsilon_{i} 
+\end{eqnarray}
 
@@
 \label{Power}
-$Z=\alpha S^{\beta} + \epsilon $ \,,
+Z_{i}=\alpha S_{i}^{\beta} + \epsilon_{i} 
 \end{equation}
@@
 \label{Loglog}
-$log(Z) = log(\alpha) + \beta log(S) + \epsilon $ \,.
+log(Z_{i}) = log(\alpha) + \beta log(S_{i}) + \epsilon_{i}  
 \end{equation}
@@
 \label{PowerLat}
-$Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\Delta_{i}+\beta_{3}\Sigma_{i} + \beta_{4}\Lambda_{i} + \beta_{5}\Tau_{i} + \beta_{6}\Mu_{i} 
-+ \beta_{7}\Delta_{i}\Sigma_{i} + \beta_{8}\Delta_{i}\Lambda_{i} + \beta_{9}\Delta_{i}\Tau_{i} + \beta_{10}\Delta_{i}\Mu_{i}}
-+ \rho{1}\Delta_{i} + \rho_{2}\Upsilon_{i} + \rho_{3}\Eta_{i} + P_{i} + \epsilon_{i} $ \,,
+
+Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\Delta_{i}+\beta_{3}\Sigma_{i} + \beta_{4}\Lambda_{i} + \beta_{5}T_{i} + \beta_{6}M_{i} 
++ \beta_{7}\Delta_{i}\Sigma_{i} + \beta_{8}\Delta_{i}\Lambda_{i} + \beta_{9}\Delta_{i}T_{i} + \beta_{10}\Delta_{i}M_{i}}
++ \rho{1}\Delta_{i} + \rho_{2}\Upsilon_{i} + \rho_{3}H_{i} + P_{i} + \epsilon_{i} 
 \end{equation}
@@
 where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
-$\Sigma_{i}$, $\Lambda_{i}$, $\Tau_{i}$, and $\Mu_{i}$ are 
+$\Sigma_{i}$, $\Lambda_{i}$, $T_{i}$, and $M_{i}$ are 
 factors indicating whether web $i$ is a stream, lake, 
 terrestrial, or marine food web (e.g., $\Sigma_{i}$=1 for 
-a stream food web, 0 otherwise). If $\Sigma_{i}$, $\Lambda_{i}$, $\Tau_{i}$, and $\Mu_{i}$ are all 0, web $i$ 
-describes an estuary food web. $\Upsilon_{i}$ is the year web $i$ was published, $\Eta_{i}=1$ if web $i$ contains humans, 0 otherwise, and $P_{i}$ is a random effect of 
+a stream food web, 0 otherwise). If $\Sigma_{i}$, $\Lambda_{i}$, $T_{i}$, and $M_{i}$ are all 0, web $i$ 
+describes an estuary food web. $\Upsilon_{i}$ is the year web $i$ was published, $H_{i}=1$ if web $i$ contains humans, 0 otherwise, and $P_{i}$ is a random effect of 
 site ID. Note that all fixed effects $\beta$ refer to factors acting on the scaling exponent between $Z$ and $S$
@@
 \label{LogLat}
-$Z_{i}= log(\alpha)+\beta_{0}log(S) + \beta_{1}\Delta_{i}log(S) +\beta_{3}\Sigma_{i}log(S) + \beta_{4}\Lambda_{i}log(S)  + \beta_{5}\Tau_{i}log(S)  + \beta_{6}\Mu_{i}log(S)  
-+ \beta_{7}\Delta_{i}\Sigma_{i}log(S)  + \beta_{8}\Delta_{i}\Lambda_{i}log(S)  + \beta_{9}\Delta_{i}\Tau_{i}log(S)  + \beta_{10}\Delta_{i}\Mu_{i}log(S) 
-+ \rho_{1}\Delta_{i} + \rho_{2}\Upsilon_{i}) + \rho_{3}\Eta_{i} +\epsilon_{i} $ \,.
+Z_{i}= log(\alpha)+\beta_{0}log(S) + \beta_{1}\Delta_{i}log(S) +\beta_{3}\Sigma_{i}log(S) + \beta_{4}\Lambda_{i}log(S)  + \beta_{5}T_{i}log(S)  + \beta_{6}M_{i}log(S)  
++ \beta_{7}\Delta_{i}\Sigma_{i}log(S)  + \beta_{8}\Delta_{i}\Lambda_{i}log(S)  + \beta_{9}\Delta_{i}T_{i}log(S)  + \beta_{10}\Delta_{i}M_{i}log(S) 
++ \rho_{1}\Delta_{i} + \rho_{2}\Upsilon_{i}) + \rho_{3}H_{i} +\epsilon_{i}
 

### 2014-07-11 manuscript/latitudepaper.tex
Forget what I changed.

@@
 Latitude is of particular interest as an environmental driver of food-web structure because it entails gradients in 
-temperature \citep{}, primary productivity \citep{}, and seasonality \citep{}. Importantly, there is also a strong
-latitudinal gradient in species richness for most taxa \citep{Schemske2009a}.
+temperature \citep{}, primary productivity \citep{}, and seasonality \citep{}. Indeed, each of these latitudinal 
+environmental gradients has been put forward as a driver for the latitudinal gradient in species richness, one of
+the most general and robust patterns in ecology \citep{Schemske2009a,,}.
 
-This effect of latitude on species richness, however, presents a problem for the analysis of food web structure.
+This effect of latitude on species richness, however, presents a problem for the analysis of other aspects of food-web structure.
 Although it was initially thought that food-web structure was small-world and scale invariant \citep{}, further 
@@
 
-Importantly, the expectation of the latitude niche-breadth hypothesis that higher species richness is associated with 
+Importantly, the expectation of the latitude-niche breadth hypothesis that higher species richness is associated with 
 reduced competition is contary to the expected increase in the mean number of interactions per species (one potential 
@@
 \subsection*{Data Set}
-We compiled a list of XX empirical food webs from an online database (GlobalWeb webs \citep{GlobalWeb}), supplemented 
-with XX food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
+We compiled a list of 347 empirical food webs from an online database (GlobalWeb webs \citep{GlobalWeb}), supplemented 
+with 31 food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
 and seven food webs used to study the impact of parasites on network structure (ParWebs \citep{Dunne2013}).
-Of the GlobalWeb webs, XX were rejected because their original source could not be found (XX), they were source or sink
-webs rather than descriptions of an entire community (XX), were focused on plant-pollinator, host-parasitoid, or 
-competitive interactions (XX), described inferred interactions in an extinct community (2), were ``generalized 
-schemes'' rather than being based on empirical observation (5), or because it was not clear which of a variety of 
-described sites the published food web represented (1). (See Table S1 for a list of rejected webs and reasons for their
+Of the GlobalWeb webs, 122 were rejected because their original source could not be found or was unpublished (53), they were source or sink
+webs rather than descriptions of an entire community (13), were focused on plant-pollinator, host-parasitoid, or 
+competitive interactions (8+34+2=44), described inferred interactions in an extinct community (2), were ``generalized 
+schemes'' rather than being based on empirical observation (8), or because it was not clear which of a variety of 
+described sites the published food web represented (2). (See Table S1 for a list of rejected webs and reasons for their
 exclusion.) For three GlobalWeb webs which included parasites as a minor component of the community, as well as the 
 seven ParWebs webs, we included a modified version of each web which included only free-living species and the 
-interactions between them \citep{Dunne2013}. For each of the XXX webs included in the final database, we recorded the
+interactions between them \citep{Dunne2013}. For each of the 263 webs included in the final database, we recorded the
 study site latitude if possible or, where no latitude was given, obtained estimated coordinates of the described
@@
 \label{PowerLat}
-
 Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\Delta_{i}+\beta_{3}\Sigma_{i} + \beta_{4}\Lambda_{i} + \beta_{5}T_{i} + \beta_{6}M_{i} 
@@
 factors indicating whether web $i$ is a stream, lake, 
-terrestrial, or marine food web (e.g., $\Sigma_{i}$=1 for 
+terrestrial, or marine food web respectively (e.g., $\Sigma_{i}$=1 for 
 a stream food web, 0 otherwise). If $\Sigma_{i}$, $\Lambda_{i}$, $T_{i}$, and $M_{i}$ are all 0, web $i$ 
@@
 + \rho_{1}\Delta_{i} + \rho_{2}\Upsilon_{i}) + \rho_{3}H_{i} +\epsilon_{i}
-
 \end{equation}
@@
 
-$S$ and $G$ both increased with increasing latitude, contrary to expected latitudinal gradients (Table \ref{Latlms}). $G$ and $V$ were not significantly correlated with latitude.
+$S$ and $G$ both increased with increasing latitude, contrary to expected latitudinal gradients (Table \ref{Latlms}). 
+$G$ and $V$ were not significantly correlated with latitude.
 
-\begin{tabular}
+\begin{table}[!h]
+\caption{Intercepts and slopes for simple linear regressions of food web properties against absolute latitude.}
+\label{Latlms}
+\begin{tabular}{l | l l | l l}
 
-\label{Latlms}
-\caption{Intercepts and slopes for simple linear regressions of food web properties against absolute latitude.}
-\begin{table}{l | l l l l}
-\multirow{2}Property & \multicolumn{2}{c}{Intercept} & \multicolumn{2}{c}{Slope} \\
+\multirow{2}{*}Property & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Slope} \\
                       & $\alpha$ & $p$-value & $\alpha$ & $p$-value \\
@@
 $V$ & 2.566 & \textless0.001 & 0.020 & 0.180 \\
+\end{tabular}
 \end{table}
-\end{tabular}
 
@@
 
-\begin{tabular}
+\begin{table}[!t]
 
+\caption{AIC's for model \ref{Power}, assuming normal error, and model \ref{Loglog}, assuming lognormal error.}
 \label{Errorfits}
-\caption{AIC's for model \ref{Power}, assuming normal error, and model \ref{Loglog}, assuming lognormal error.}
-\begin{table}{l | l l | c}
+\begin{tabular}{l | l l | c}
 Property & Normal error & Lognormal error & Model selected \\
@@
 $V$ & 1151 & 767 & \ref{Loglog} \\
+\end{tabular}
 \end{table}
-\end{tabular}
 
 In this data set, none of the best fit models for species richness, connectance, or links per species included an 
-effect of latitude on either the scaling exponent or residual (Table \ref{bestfits}). 
-$G$ increased slightly in more recent webs ($\rho{2}$=0.005, $p$<0.001), but the best-fit models for $V$ and $Z$ did not include a term for year of publication. 
-In contrast, $Z$ and $V$ were higher in lake food webs ($\beta_{4}$=0.10, $p$<0.001 and $\beta_{4}$=0.10, $p$<0.001, respectively) while the best-fit model for $G$ did not include an effect for any ecosystem type.
+effect of latitude on either the scaling exponent or residual (Table \ref{Bestfits}). 
+$G$ increased slightly in more recent webs ($\rho_{2}$=0.005, $p$\textless0.001), but the best-fit models for $V$ and $Z$ did not include a term for year of publication. 
+In contrast, $Z$ and $V$ were higher in lake food webs ($\beta_{4}$=0.10, $p$\textless0.001 and $\beta_{4}$=0.10, $p$\textless0.001, respectively) while the best-fit model for $G$ did not include an effect for any ecosystem type.
+
+\begin{table}[!h]
+
+\caption{Standard effects and their $p$-values for the best-fitting models of $Z$, $G$, and $V$.}
+\label{Bestfits}
+\begin{tabular}{l | l l | l l | l l | l l }
+\multirow{2}{*}{Property} & \multicolumn{2}{c}{Intercept} & \multicolumn{2}{c}{log(Species)} & \multicolumn{2}{c}{log(Species)$\Lambda$} & \multicolumn{2}{c}{$\Upsilon$} \\
+& $\beta$ & $p$-value &  $\beta$ & $p$-value &  $\beta$ & $p$-value &  $\beta$ & $p$-value  \\
+\hline
+$Z$ & -0.516 & \textless0.001 & 0.662 & \textless0.001 & 0.099 & \textless0.001 & \multicolumn{2}{c}{NA} \\
+$G$ & -9.999 & \textless0.001 & 0.547 & \textless0.001 & \multicolumn{2}{c}{NA} & 0.005 & \textless0.001 \\
+$V$ & -0.516 & \textless0.001 & 0.662 & \textless0.001 & 0.099 & \textless0.001 & \multicolumn{2}{c}{NA} \\
+\end{tabular}
+\end{table}
 

### 2014-07-24 manuscript/latitudepaper.tex
Starting to change things.

@@
 %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
-Food webs (networks of feeding links between species) have been used for decades to summarize the structure of 
+Food webs --networks of feeding links between species-- have been used for over a century to summarize the structure of 
 ecological communities \citep{Williams2000,earlierwork} and to understand how that structure relates to environmental variables 
-such as land use \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, temperature?, latitude?. 
-Latitude is of particular interest as an environmental driver of food-web structure because it entails gradients in 
-temperature \citep{}, primary productivity \citep{}, and seasonality \citep{}. Indeed, each of these latitudinal 
-environmental gradients has been put forward as a driver for the latitudinal gradient in species richness, one of
-the most general and robust patterns in ecology \citep{Schemske2009a,,}.
+such as land use \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, and temperature. The latter
+variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics \citep{}, 
+suggesting that latitude may indirectly affect food-web structure.
+Indeed, these latitudinal environmental gradients have been put forward as potential driverd for the latitudinal gradient in species 
+richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,,}.
 
@@
 richness, connectance (the proportion of possible links that are realized), or both \citep{Riede2010} 
-(see \citet{Dunne2006} for a review of the history of scaling laws in food web theory). This means that relationships
+(see \citet{Dunne2006} for a review of the history of scaling laws in food web theory). This means that any relationship
 between latitude and food-web structure must be considered in light of the latitudinal gradient in species richness.
 This is especially true for food-web properties that both scale with species richness and are related to candidate
-explanations for the latitudinal diversity gradient, such as measures of specialization.
+explanations for the latitudinal diversity gradient, such as measures of specialization [[DBS requests citation, ARC thinks this is the motivation for the paper and isn't aware of a source]].
 
+[[Smoother transition needed here]]
 % Explain niche space hypothesis, Schemske, Vazquez. Then make clear that niche space suggests opposite gradient to ~S^B.
@@
 distinct effect of latitude on specialization then this effect should be visible in changing scaling relationships.
-Here, we tested the effect of latitude on scaling relationships between species richness and mean links per species, 
-mean generality (number of prey per predator), and mean vulnerability (number of predators per prey). Together, these
-properties provide a measure a species' biotic specialization - that is, its specialization in terms of interactions 
-with other species.
+Here, we tested for changes in the scaling of mean links per species, mean generality, and mean vulnerability with species
+richness over latitude. We focused on these three food-web properties --only some of the wide array of metrics that have been
+described (see e.g. \citep{})-- because together they provide a measure a species' biotic specialization, which underlies the 
+``latitude-niche breadth hypothesis''.
 

### 2014-07-29 manuscript/latitudepaper.tex
Daniel corrections.

@@
 \subsection*{Data Set}
-We compiled a list of 347 empirical food webs from an online database (GlobalWeb webs \citep{GlobalWeb}), supplemented 
-with 31 food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
-and seven food webs used to study the impact of parasites on network structure (ParWebs \citep{Dunne2013}).
-Of the GlobalWeb webs, 122 were rejected because their original source could not be found or was unpublished (53), they were source or sink
-webs rather than descriptions of an entire community (13), were focused on plant-pollinator, host-parasitoid, or 
-competitive interactions (8+34+2=44), described inferred interactions in an extinct community (2), were ``generalized 
-schemes'' rather than being based on empirical observation (8), or because it was not clear which of a variety of 
-described sites the published food web represented (2). (See Table S1 for a list of rejected webs and reasons for their
-exclusion.) For three GlobalWeb webs which included parasites as a minor component of the community, as well as the 
-seven ParWebs webs, we included a modified version of each web which included only free-living species and the 
-interactions between them \citep{Dunne2013}. For each of the 263 webs included in the final database, we recorded the
-study site latitude if possible or, where no latitude was given, obtained estimated coordinates of the described
-study site using Google Earth \citep{GoogleEarth}. Webs were also classified according to ecosystem type (terrestrial,
-lake, stream, estuary, or marine), year of publication (to control for changing standards of data collection over time \citep{Dunne2006}), and whether or not humans were included (11 webs included humans).
+
+We compiled a list of 263 empirical food webs from
+multiple sources (see Supplemental Information for web origins and selection
+criteria). We recorded study site latitude from the original source where
+possible or, where study sites were described but exact coordinates were not
+given, obtained estimated coordinates using Google Earth \citep{GoogleEarth}.
+Webs were also classified according to ecosystem type (terrestrial, lake,
+stream, estuary, or marine), year of publication (to control for potential change
+in standards of data collection over time \citep{Dunne2006}), and whether or not
+humans were included.
+
+% [[list in supplemental (347 GlobalWeb webs \citep{GlobalWeb}), supplemented 
+% with 31 food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
+% and seven food webs used to study the impact of parasites on network structure (ParWebs \citep{Dunne2013}).
+% Of the GlobalWeb webs, 122 were rejected because their original source could not be found or was unpublished (53), they were source or sink
+% webs rather than descriptions of an entire community (13), were focused on plant-pollinator, host-parasitoid, or 
+% competitive interactions (8, 34, and 2, respectively), described inferred interactions in an extinct community (2), were ``generalized 
+% schemes'' rather than being based on empirical observation (8), or because it was not clear which of a variety of 
+% described sites the published food web represented (2). (See Table S1 for a list of rejected webs and reasons for their
+% exclusion.) For three GlobalWeb webs which included parasites as a minor component of the community, as well as the 
+% seven ParWebs webs, we included a modified version of each web which included only free-living species and the 
+% interactions between them \citep{Dunne2013}.
 
@@
 \begin{eqnarray}
-S_{i} = \alpha_{0} + \alpha_{1} \Delta_{i} + \epsilon_{i} 
+S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \epsilon_{i} 
 \end{eqnarray}
 
-where $S_{i}$ is the species richness of web $i$, $\Delta_{i}$ its absolute latitude (degrees north or south 
+where $S_{i}$ is the species richness of web $i$, $\Lambda_{i}$ its absolute latitude (degrees north or south 
 regardless of direction), and $\epsilon_{i}$ a residual error term.
@@
 
-However, the two forms of the relationship imply different error structures: normally-distributed, additive error in 
-\ref{Power} and lognormal, multiplicative error in \ref{Loglog}. As there is no intuitive reason to believe that our
-data have one error distribution over another, we follow the recommendations in \citet{Xiao2011} and compared the two
-model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
-data was then used to test for potential effects of latitude.
-
 Although scaling relationships between $S$, $G$, and $V$ have not been explicitly examined (but see scaling 
@@
 
+%%% TO SI
+
+% Note that the two forms of the power-law relationship imply different error structures: normally-distributed, additive error in 
+% \ref{Power} and lognormal, multiplicative error in \ref{Loglog}. As there is no intuitive reason to believe that our
+% data have one error distribution over another, we follow the recommendations in \citet{Xiao2011} and compared the two
+% model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
+% data was then used to test for potential effects of latitude.
+
 \subsection*{Effect of Latitude on Scaling}
@@
 
-Once the best formulation of the relationship between each property and $S$ had been determined, we then assessed
-the impact of latitude on this relationship. There are two ways that properties might be affected by latitude:
-1) the slope of the scaling relationship with $S$ might vary over latitude or 2) the residuals $\epsilon$ might
-vary over latitude. To account for both possibilities we included terms for the effect of latitude on the scaling
-exponent $\beta$ in equation \ref{Power} as well as on the residual. In addition, as other studies have suggested that 
-food webs in different ecosystem types have characteristic structural differences, we included a dummy variable for 
-each ecosystem type (stream, lake, terrestrial, or marine, with estuary used as the `intercept' ecosystem type). 
-We also considered other trends in the data that could affect relationships between latitude and species richness.
-To account for changing standards in data collection over time \citep{Dunne2006} we included an effect of year of
-publication. As 11 of our XX webs included humans, and therefore might have different properties than other networks,
-we included a factorial effect of the presence of humans. Finally, some of our webs describe the same area in different
+We then assessed
+the impact of latitude on this relationship; specifically, the effect of latitude on the scaling exponent $\beta$. 
+In addition to latitude, we included a factorial variable for ecosystem type (stream, lake, terrestrial, marine, or estuary) to account for recognized variation in food web structure across ecosystem types \citep{}.
+% We also considered other trends in the data that could affect relationships between latitude and species richness.
+% To account for changing standards in data collection over time \citep{Dunne2006} we included an effect of year of
+% publication. As 11 of our XX webs included humans, and therefore might have different properties than other networks,
+% we included a factorial effect of the presence of humans. 
+Finally, some of our webs describe the same area in different
 seasons or different years. To account for likely correlation among these webs, we included a random effect of site ID.
@@
 \label{PowerLat}
-Z_{i}=\alpha S^{\beta_{0}+\beta_{1}\Delta_{i}+\beta_{3}\Sigma_{i} + \beta_{4}\Lambda_{i} + \beta_{5}T_{i} + \beta_{6}M_{i} 
-+ \beta_{7}\Delta_{i}\Sigma_{i} + \beta_{8}\Delta_{i}\Lambda_{i} + \beta_{9}\Delta_{i}T_{i} + \beta_{10}\Delta_{i}M_{i}}
-+ \rho{1}\Delta_{i} + \rho_{2}\Upsilon_{i} + \rho_{3}H_{i} + P_{i} + \epsilon_{i} 
+Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{3}E_{i}} + P_{i} + \epsilon_{i} 
 \end{equation}
 
-where $\delta$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
-$\Sigma_{i}$, $\Lambda_{i}$, $T_{i}$, and $M_{i}$ are 
-factors indicating whether web $i$ is a stream, lake, 
-terrestrial, or marine food web respectively (e.g., $\Sigma_{i}$=1 for 
-a stream food web, 0 otherwise). If $\Sigma_{i}$, $\Lambda_{i}$, $T_{i}$, and $M_{i}$ are all 0, web $i$ 
-describes an estuary food web. $\Upsilon_{i}$ is the year web $i$ was published, $H_{i}=1$ if web $i$ contains humans, 0 otherwise, and $P_{i}$ is a random effect of 
-site ID. Note that all fixed effects $\beta$ refer to factors acting on the scaling exponent between $Z$ and $S$
-while fixed effects $\rho$ refer to factors acting on the residual error.
+where $L_{i}$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
+$E_{i}$ indicates the ecosystem type of food web $i$, and $P_{i}$ is a random effect of 
+site ID.
 
@@
 \label{LogLat}
-Z_{i}= log(\alpha)+\beta_{0}log(S) + \beta_{1}\Delta_{i}log(S) +\beta_{3}\Sigma_{i}log(S) + \beta_{4}\Lambda_{i}log(S)  + \beta_{5}T_{i}log(S)  + \beta_{6}M_{i}log(S)  
-+ \beta_{7}\Delta_{i}\Sigma_{i}log(S)  + \beta_{8}\Delta_{i}\Lambda_{i}log(S)  + \beta_{9}\Delta_{i}T_{i}log(S)  + \beta_{10}\Delta_{i}M_{i}log(S) 
-+ \rho_{1}\Delta_{i} + \rho_{2}\Upsilon_{i}) + \rho_{3}H_{i} +\epsilon_{i}
+log(Z_{i})= log(\alpha)+\beta_{0}log(S_{i}) + \beta_{1}L*log(S_{i}) +\beta_{3}E*log(S_{i})+ P_{i} +\epsilon_{i}
 \end{equation}
 
-As in the power-law formulation, fixed effects $\beta$ 
-affect the scaling exponent and fixed effects $\rho$ 
-affect the (lognormal) residual.
-
+We fit equation \ref{LogLat}, as well as similar equations for $G$ and $V$ using R \citep{R} function lmer from package lme4
+\citep{lmerTest}.
 We calculated the AIC of the chosen maximal model, as well as the AIC's of a suite of candidate simplified models.
@@
 The term for species richness was not removed from a model if any of the terms affecting the exponent $\beta$ were 
-included in the model. The model with the lowest AIC was selected as the best-fitting model. For power-law formulations
-this simplification was performed by hand. For logarithmic formulations, this simplification was performed using the
+included in the model. The model with the lowest AIC was selected as the best-fitting model. 
+This simplification was performed using the
 R \citep{R} function dredge from package MuMIn \citep{MuMIn}. We then used the R \citep{R} function lmer
-from the package lmerTest \citep{lmerTest} to estimate the standardized effects ($\beta$s and $\rho$s) for each fixed effect in the 
+from the package lmerTest \citep{lmerTest} to estimate the standardized effects ($\beta$s ) for each fixed effect in the 
 best-fitting models, as well as their corresponding $p$-values.
@@
 
-\multirow{2}{*}Property & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Slope} \\
-                      & $\alpha$ & $p$-value & $\alpha$ & $p$-value \\
+\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Slope} \\
+                      & $\alpha_{0}$ & $p$-value & $\alpha_{1}$ & $p$-value \\
 \hline
@@
 
-For models of $Z$, $G$, and $V$, the assumption of multiplicative log-normal error was better supported (Table \ref{Errorfits}).
+% For models of $Z$, $G$, and $V$, the assumption of multiplicative log-normal error was better supported (Table \ref{Errorfits}).
 We therefore use only models with logarithmic form for the remainder of the paper.
 
-\begin{table}[!t]
+% \begin{table}[!t]
 
-\caption{AIC's for model \ref{Power}, assuming normal error, and model \ref{Loglog}, assuming lognormal error.}
-\label{Errorfits}
-\begin{tabular}{l | l l | c}
-Property & Normal error & Lognormal error & Model selected \\
-\hline
-$Z$ & 1151 &  767 & \ref{Loglog} \\
-$G$ & 1266 & 1037 & \ref{Loglog} \\
-$V$ & 1151 & 767 & \ref{Loglog} \\
-\end{tabular}
-\end{table}
+% \caption{AIC's for model \ref{Power}, assuming normal error, and model \ref{Loglog}, assuming lognormal error.}
+% \label{Errorfits}
+% \begin{tabular}{l | l l | c}
+% Property & Normal error & Lognormal error & Model selected \\
+% \hline
+% $Z$ & 1151 &  767 & \ref{Loglog} \\
+% $G$ & 1266 & 1037 & \ref{Loglog} \\
+% $V$ & 1151 & 767 & \ref{Loglog} \\
+% \end{tabular}
+% \end{table}
 
@@
 $Z$ & -0.516 & \textless0.001 & 0.662 & \textless0.001 & 0.099 & \textless0.001 & \multicolumn{2}{c}{NA} \\
-$G$ & -9.999 & \textless0.001 & 0.547 & \textless0.001 & \multicolumn{2}{c}{NA} & 0.005 & \textless0.001 \\
+$G$ & -9.999 & \textless0.001 & 0.547 & \textless0.001 & \multicolumn{2}{c|}{NA} & 0.005 & \textless0.001 \\
 $V$ & -0.516 & \textless0.001 & 0.662 & \textless0.001 & 0.099 & \textless0.001 & \multicolumn{2}{c}{NA} \\
@@
 
-As the latitudinal gradient in species richness in this data set ran in the
-opposite direction to the general trend for \citep{}, we conclude that it is
-likely an artifact of the data set. Academic institutions have the longest
-history in temperate latitudes, and it may be that communities at these
-latitudes are better understood or more completely sampled. As such, it does not seem likely that the increase in
+The latitudinal gradient in species richness in this data set ran in the opposite 
+direction to the general trends for (list types of taxa). This may be due to the 
+fact that latitudinal gradient in species richness are usually studied within a
+taxonomic or trophic group (e.g., birds, vascular plants), whereas food webs 
+measure many taxa concurrently. It is possible that while many taxa generally increase
+towards the tropics, the number of species across all taxa that co-occur within an 
+study site decreases. Alternatively, it is possible that by using trophic-species versions
+of our food webs, we have artificially reversed the species-richness gradient. [[re-run analyses
+with species-species webs]]. This would imply that, while there may be more species in the tropics,
+many of those species tend to have identical predator and prey sets to co-occuring species. In either
+case, it does not seem likely that the increase in
 generality with latitude that we observed is due to an underlying tendency for
@@
 
-It is not our intention here to question the validity of the wide range of
-studies exploring variation in network structure across changing environments.
+It was not our initial intention to question the validity of the wide range of
+studies exploring variation in network structure across changing environments \citep{}.
 However, if those studies have not taken into account changes in species

### 2015-01-27 manuscript/latitudepaper.tex
unknown changes

--- 2014-07-11 manuscript/latitudepaper.tex
@@
 
-In this data set, none of the best fit models for species richness, connectance, or links per species included an 
+In this data set, the best fit models for species richness and links per species did not include an 
 effect of latitude on either the scaling exponent or residual (Table \ref{Bestfits}). 

### 2015-01-27 manuscript/latitudepaper.tex

--- 2014-07-29 manuscript/latitudepaper.tex
@@
 \title{Generality in food webs scales with species richness, not latitude}
-\author{Alyssa Cirtwill, Tamara Romanuk?, Daniel Stouffer?}
+\author{Alyssa Cirtwill, Daniel Stouffer, Tamara Romanuk}
 \date{$^1$School of Biological Sciences\\University of Canterbury\\

### 2015-01-27 code/Models.R
New results

@@ -4,6 +4,7 @@
 library(nlrwr)
 library(lmerTest)
 library(boot)
+library(MuMIn)
 ## Function to carry out the analytical process described in General Guidelines
 ## Input: x - vector, explanatory variable
 ##        y - vector, response variable
@@ -188,9 +189,6 @@ y=data$Gen
 z=data$Vul         
 
 
-
-
-
 power_analysis(data$Species,data$LS)   #To determine whether scaling of LS~S is more lognormal or nonlinear.
                       #It is lognormal, AIC=766.8 vs 1150.3 with nonlinear.
 power_analysis(data$Species,data$Gen)   #To determine whether scaling of Gen~S is more lognormal or nonlinear.
@@ -199,34 +197,108 @@ power_analysis(data$Species,data$Vul)   #To determine whether scaling of Vul~S i
                       #It is lognormal, AIC=766.9 vs 1150.6
 
 #Therefore using lognormal with confidence for modified models.
-LS_full=with(data,lmer(log10(LS)~log10(Species)
+LS_full=with(data,lm(log10(LS)~log10(Species)
   +log10(Species):Latitude
   +log10(Species):(Stream+Lake+Marine+Terr)
   +log10(Species):Latitude:(Stream+Lake+Marine+Terr)
-  +(1|Site)
   ,na.action=na.fail))
-LS_min =with(data,lmer(log10(LS)~log10(Species)+log10(Species):Lake+(1|Site),na.action=na.fail))
+ls_dredge=dredge(LS_full,rank=AIC)
+LS_min =with(data,lm(log10(LS)~log10(Species)
+  +log10(Species):(Lake+Marine+Stream)
+  +log10(Species):Latitude
+  +log10(Species):Latitude:Lake
+  +log10(Species):Latitude:Stream
+  ,na.action=na.fail))
 
 
-Gen_full=with(data,lmer(log10(Gen)~log10(Species)
+Gen_full=with(data,lm(log10(Gen)~log10(Species)
   +log10(Species):Latitude
   +log10(Species):(Stream+Lake+Marine+Terr)
   +log10(Species):Latitude:(Stream+Lake+Marine+Terr)
-  +(1|Site)
   ,na.action=na.fail))
[…]

### 2015-01-27 manuscript/latitudepaper.tex
updated results

@@
 ecological communities \citep{Williams2000,earlierwork} and to understand how that structure relates to environmental variables 
-such as land use \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, and temperature. The latter
-variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics \citep{}, 
+such as land use \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, and climate\citep{}. The latter
+variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
+climate is more variable at high latitudes \citep{}, 
 suggesting that latitude may indirectly affect food-web structure.
@@
 between latitude and food-web structure must be considered in light of the latitudinal gradient in species richness.
-This is especially true for food-web properties that both scale with species richness and are related to candidate
-explanations for the latitudinal diversity gradient, such as measures of specialization [[DBS requests citation, ARC thinks this is the motivation for the paper and isn't aware of a source]].
+This is especially true for food-web properties such as measures of specialization
+that both scale with species richness \citep{Riede2010} and are related to candidate
+explanations for the latitudinal diversity gradient \citep{Vazquez2004}.
 
@@
 % we included a factorial effect of the presence of humans. 
-Finally, some of our webs describe the same area in different
-seasons or different years. To account for likely correlation among these webs, we included a random effect of site ID.
+Note that some of our webs describe the same area in different
+seasons or different years. [[removed the site-level random effect because I don't want it to steal latitude information.]]
 
@@
 \label{PowerLat}
-Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{3}E_{i}} + P_{i} + \epsilon_{i} 
+Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{3}E_{i}} + \epsilon_{i} 
 \end{equation}
@@
 where $L_{i}$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
-$E_{i}$ indicates the ecosystem type of food web $i$, and $P_{i}$ is a random effect of 
-site ID.
+$E_{i}$ indicates the ecosystem type of food web $i$.
 
@@
 \label{LogLat}
-log(Z_{i})= log(\alpha)+\beta_{0}log(S_{i}) + \beta_{1}L*log(S_{i}) +\beta_{3}E*log(S_{i})+ P_{i} +\epsilon_{i}
+1log(Z_{i})= log(\alpha)+\beta_{0}log(S_{i}) + \beta_{1}L*log(S_{i}) +\beta_{3}E*log(S_{i}) +\epsilon_{i}
 \end{equation}
 
-We fit equation \ref{LogLat}, as well as similar equations for $G$ and $V$ using R \citep{R} function lmer from package lme4
-\citep{lmerTest}.
+We fit equation \ref{LogLat}, as well as similar equations for $G$ and $V$ using R \citep{R} function lm from package stats
+\citep{stats}.
 We calculated the AIC of the chosen maximal model, as well as the AIC's of a suite of candidate simplified models.
@@
 The term for species richness was not removed from a model if any of the terms affecting the exponent $\beta$ were 
-included in the model. The model with the lowest AIC was selected as the best-fitting model. 
+included in the model. The best-fitting model was then determined to be the model with the fewest terms where $\delta$AIC<2.
+
+The model with the lowest AIC was selected as the best-fitting model. 
 This simplification was performed using the
-R \citep{R} function dredge from package MuMIn \citep{MuMIn}. We then used the R \citep{R} function lmer
-from the package lmerTest \citep{lmerTest} to estimate the standardized effects ($\beta$s ) for each fixed effect in the 
+R \citep{R} function dredge from package MuMIn \citep{MuMIn}. We then used the R \citep{R} function lm
+to estimate the standardized effects ($\beta$s ) for each fixed effect in the 
 best-fitting models, as well as their corresponding $p$-values.
@@
 
-\subsection*{Relationships with Latitude}
+\subsection*{Scaling Relationships with S and Latitude}
 
-$S$ and $G$ both increased with increasing latitude, contrary to expected latitudinal gradients (Table \ref{Latlms}). 
+For relationships of $Z$, $G$, and $V$ to S, the assumption of multiplicative log-normal error was better supported
+(Table \ref{Errorfits}). We therefore use only models with logarithmic form for the remainder of the paper.
+
+Contrary to expected latitudinal gradients, $S$ and $G$ both increased with increasing latitude(Table \ref{Latlms}). 
 $G$ and $V$ were not significantly correlated with latitude.
+
+\begin{table}[!t]
+
+\caption{AIC's for model \ref{Power}, assuming normal error, and model \ref{Loglog}, assuming lognormal error.}
+\label{Errorfits}
+\begin{tabular}{l | l l | c}
+Property & Normal error & Lognormal error & Model selected \\
+\hline
+$Z$ & 1151 &  767 & \ref{Loglog} \\
+$G$ & 1266 & 1037 & \ref{Loglog} \\
+$V$ & 1151 & 767 & \ref{Loglog} \\
+\end{tabular}
+\end{table}
 
@@
 
-\subsection*{Scaling Relationships with S}
+\subsection*{Effect of Latitude on Scaling with S}
 
-% For models of $Z$, $G$, and $V$, the assumption of multiplicative log-normal error was better supported (Table \ref{Errorfits}).
-We therefore use only models with logarithmic form for the remainder of the paper.
-
-% \begin{table}[!t]
-
-% \caption{AIC's for model \ref{Power}, assuming normal error, and model \ref{Loglog}, assuming lognormal error.}
-% \label{Errorfits}
-% \begin{tabular}{l | l l | c}
-% Property & Normal error & Lognormal error & Model selected \\
-% \hline
-% $Z$ & 1151 &  767 & \ref{Loglog} \\
-% $G$ & 1266 & 1037 & \ref{Loglog} \\
-% $V$ & 1151 & 767 & \ref{Loglog} \\
-% \end{tabular}
-% \end{table}
-
-In this data set, the best fit models for species richness and links per species did not include an 
-effect of latitude on either the scaling exponent or residual (Table \ref{Bestfits}). 
-$G$ increased slightly in more recent webs ($\rho_{2}$=0.005, $p$\textless0.001), but the best-fit models for $V$ and $Z$ did not include a term for year of publication. 
-In contrast, $Z$ and $V$ were higher in lake food webs ($\beta_{4}$=0.10, $p$\textless0.001 and $\beta_{4}$=0.10, $p$\textless0.001, respectively) while the best-fit model for $G$ did not include an effect for any ecosystem type.
+The effect of latitude on scaling relationships varied across ecosystem types (Table~\ref{Bestfits}). 
+In lakes and streams, the scaling exponent for species richness increased with latitude (although this 
+increase was not significant for lakes and generality). For other types of ecosystems, the scaling 
+exponent for species richness did not change significantly with latitude. 
+[[Some more description after figures.]]
 
@@
 
-\caption{Standard effects and their $p$-values for the best-fitting models of $Z$, $G$, and $V$.}
+\caption{Standard effects and their $p$-values for the best-fitting models of links per species ($Z$), generality ($G$), and vulnerability ($V$).}
 \label{Bestfits}
-\begin{tabular}{l | l l | l l | l l | l l }
-\multirow{2}{*}{Property} & \multicolumn{2}{c}{Intercept} & \multicolumn{2}{c}{log(Species)} & \multicolumn{2}{c}{log(Species)$\Lambda$} & \multicolumn{2}{c}{$\Upsilon$} \\
-& $\beta$ & $p$-value &  $\beta$ & $p$-value &  $\beta$ & $p$-value &  $\beta$ & $p$-value  \\
+\begin{tabular}{l | l l | l l | l l }
+\multirow{2}{*}{Effect} & \multicolumn{2}{c}{$Z$} & \multicolumn{2}{c}{$G$} & \multicolumn{2}{c}{$V$}\\
+                & $\beta$ & $p$-value &  $\beta$ & $p$-value &  $\beta$ & $p$-value & \\
 \hline
-$Z$ & -0.516 & \textless0.001 & 0.662 & \textless0.001 & 0.099 & \textless0.001 & \multicolumn{2}{c}{NA} \\
-$G$ & -9.999 & \textless0.001 & 0.547 & \textless0.001 & \multicolumn{2}{c|}{NA} & 0.005 & \textless0.001 \\
-$V$ & -0.516 & \textless0.001 & 0.662 & \textless0.001 & 0.099 & \textless0.001 & \multicolumn{2}{c}{NA} \\
+Intercept               & -0.561 & \textless0.001 & -0.299 & \textless0.001 & -0.561 & \textless0.001 \\
+log(species)            &  0.733 & \textless0.001 &  0.622 & \textless0.001 &  0.733 & \textless0.001 \\
+log(species):Lake       & -0.118 & 0.047          & -0.115 & 0.078          & -0.118 & 0.047 \\
+log(species):Marine     &  0.051 & 0.040          &  0.120 & \textless0.001 &  0.051 & 0.040 \\
+log(species):Stream     & -0.161 & 0.014          & -0.057 & 0.421          & -0.161 & 0.014 \\
+log(species):Latitude   & -0.001 & 0.081          & -0.001 & 0.273          & -0.001 & 0.081 \\
+log(species):Lat:Lake   &  0.006 & \textless0.001 &  0.006 & \textless0.001 &  0.006 & \textless0.001 \\
+log(species):Lat:Stream &  0.004 & 0.018          &  0.003 & 0.059          &  0.004 & 0.018 \\
+\hline
 \end{tabular}
@@
 
-The tendency of food-web structure to exhibit scaling relationships with both
-species richness and connectance has been  well-established \citep{}. As
-species richness in particular is also known to vary systematically over
-latitude \citep{}, intuitively one might suspect that any relationship
-between food-web properties such as generality might be due to the latitudinal
-gradient in species richness. Here, we found that while there were latitudinal
-gradients in species richness and generality, latitude was not related to
-either the scaling relationship between generality and species richness or the
-residuals of this scaling relationship.
+[[This'll need to be redone]]
+% The tendency of food-web structure to exhibit scaling relationships with both
+% species richness and connectance has been well-established \citep{}. As
+% species richness in particular is also known to vary systematically over
+% latitude \citep{}, intuitively one might suspect that any relationship
+% between food-web properties such as generality might be due to the latitudinal
+% gradient in species richness. Here, we found that while there were latitudinal
+% gradients in species richness and generality, latitude was not related to
+% either the scaling relationship between generality and species richness or the
+% residuals of this scaling relationship.
 
-The latitudinal gradient in species richness in this data set ran in the opposite 
-direction to the general trends for (list types of taxa). This may be due to the 
-fact that latitudinal gradient in species richness are usually studied within a
-taxonomic or trophic group (e.g., birds, vascular plants), whereas food webs 
-measure many taxa concurrently. It is possible that while many taxa generally increase
-towards the tropics, the number of species across all taxa that co-occur within an 
-study site decreases. Alternatively, it is possible that by using trophic-species versions
-of our food webs, we have artificially reversed the species-richness gradient. [[re-run analyses
-with species-species webs]]. This would imply that, while there may be more species in the tropics,
-many of those species tend to have identical predator and prey sets to co-occuring species. In either
-case, it does not seem likely that the increase in
-generality with latitude that we observed is due to an underlying tendency for
-species to pursue a wider variety of prey at higher latitudes. Rather, the
-trend in generality can be more parsimoniously explained by the trend in
-species richness.
+% The latitudinal gradient in species richness in this data set ran in the opposite 
+% direction to the general trends for (list types of taxa). This may be due to the 
+% fact that latitudinal gradient in species richness are usually studied within a
+% taxonomic or trophic group (e.g., birds, vascular plants), whereas food webs 
+% measure many taxa concurrently. It is possible that while many taxa generally increase
+% towards the tropics, the number of species across all taxa that co-occur within an 
+% study site decreases. Alternatively, it is possible that by using trophic-species versions
+% of our food webs, we have artificially reversed the species-richness gradient. [[re-run analyses
+% with species-species webs]]. This would imply that, while there may be more species in the tropics,
+% many of those species tend to have identical predator and prey sets to co-occuring species. In either
+% case, it does not seem likely that the increase in
+% generality with latitude that we observed is due to an underlying tendency for
+% species to pursue a wider variety of prey at higher latitudes. Rather, the
+% trend in generality can be more parsimoniously explained by the trend in
+% species richness.
 
-Our findings here add further doubt to the niche-breadth hypothesis, as
-narrower niches in the tropics were associated with lower species richness in
-this data set. It appears instead that, as more species are available, each
-species tends to consume more prey, be consumed by more predators, and have
-more links in general (check with figs). This makes intuitive sense as a more
-species-rich community is likely to have more species with similar behaviour
-and morphology that thereby have overlapping predator or prey sets.
+% Our findings here add further doubt to the niche-breadth hypothesis, as
+% narrower niches in the tropics were associated with lower species richness in
+% this data set. It appears instead that, as more species are available, each
+% species tends to consume more prey, be consumed by more predators, and have
+% more links in general (check with figs). This makes intuitive sense as a more
+% species-rich community is likely to have more species with similar behaviour
+% and morphology that thereby have overlapping predator or prey sets.
 
-Parallel increases in generality and species richness across latitude have
-also been noted in studies of plant-pollinator networks (although in that case
-species richness was highest in the tropics) \citep{Schleuning2012}. Although
-the authors of that study do not explicitly examine the relationship between
-specialization and network size, they do cite increasing plant species
-richness as a potential driver for increasing generalization
-\citep{Schleuning2012}. Although the scaling of mutualist network structure
-does not appear to have been explored as systematically as that of unipartite
-food webs, some poperties such as nestedness \citep{Vazquez2004} and XX
-\citep{} have been shown to scale with species richness. As such scaling
-appears to be common to both antagonistic and mutualistic food webs, and
-trends in species richness can explain counterintuitive trends in network
-structure \citep{Schleuning2012}, it seems likely that many latitudinal trends
-in network structure are at least partly due to trends in species richness.
+% Parallel increases in generality and species richness across latitude have
+% also been noted in studies of plant-pollinator networks (although in that case
+% species richness was highest in the tropics) \citep{Schleuning2012}. Although
+% the authors of that study do not explicitly examine the relationship between
+% specialization and network size, they do cite increasing plant species
+% richness as a potential driver for increasing generalization
+% \citep{Schleuning2012}. Although the scaling of mutualist network structure
+% does not appear to have been explored as systematically as that of unipartite
+% food webs, some poperties such as nestedness \citep{Vazquez2004} and XX
+% \citep{} have been shown to scale with species richness. As such scaling
+% appears to be common to both antagonistic and mutualistic food webs, and
+% trends in species richness can explain counterintuitive trends in network
+% structure \citep{Schleuning2012}, it seems likely that many latitudinal trends
+% in network structure are at least partly due to trends in species richness.
 
-%Nestedness increases with A+P, increases number of extreme specialists AND number of generalists. Not clear how degree should scale with S according to scaling with nestedness.
+% %Nestedness increases with A+P, increases number of extreme specialists AND number of generalists. Not clear how degree should scale with S according to scaling with nestedness.
 
-\section*{Conclusion}
+% \section*{Conclusion}
 
-It was not our initial intention to question the validity of the wide range of
-studies exploring variation in network structure across changing environments \citep{}.
-However, if those studies have not taken into account changes in species
-richness over environmental gradients, it is possible that observed changes in
-food-web structure are due only indirectly to the environmental variables of
-interest. Effects of environmental variables on network structure should
-therefore be interpreted with caution unless effects of changing species
-richness are made explicit.
+% It was not our initial intention to question the validity of the wide range of
+% studies exploring variation in network structure across changing environments \citep{}.
+% However, if those studies have not taken into account changes in species
+% richness over environmental gradients, it is possible that observed changes in
+% food-web structure are due only indirectly to the environmental variables of
+% interest. Effects of environmental variables on network structure should
+% therefore be interpreted with caution unless effects of changing species
+% richness are made explicit.
 

### 2015-01-27 code/property_plots.py
setting up to make plots

@@ -11,186 +11,77 @@ from PyGrace.dataset import SYMBOLS
 from PyGrace.Extensions.panel import Panel,MultiPanelGrace
 from PyGrace.drawing_objects import DrawText
 
+# Think I want plots of the raw data (S, LS, G, V vs. lat) with slope lines
+# Plus predictions for LS, G, V vs S (with corrected obs.)
 
-mean_C=0.1
-min_C=0.025
-max_C=0.25
+def datareader(rawdatafile):
+  points={'S':{'estuary':[],'lake':[],'marine':[],'stream':[],'terrestrial':[]},
+  'LS':{'estuary':[],'lake':[],'marine':[],'stream':[],'terrestrial':[]},
+  'G':{'estuary':[],'lake':[],'marine':[],'stream':[],'terrestrial':[]},  
+  'V'{'estuary':[],'lake':[],'marine':[],'stream':[],'terrestrial':[]}}
 
-mean_S=36
-min_S=5
-max_S=109
-
-#Mean dist from centroids
-def linereader(fw_prop):
-  linefile="../mod_data/"+fw_prop+"_coeffs"
-  linetab=open(linefile,'r')
-  lines={}
-  for line in linetab:
-    if len(line.split())==5:
-      effect=line.split()[0][1:-1]
-      beta=float(line.split()[1])
-      lines[effect]=beta
-  return lines
-
-def datareader(fw_prop):
-  datafile="../mod_data/summary-properties.tsv"
-  f=open(datafile,'r')
-  datadict={'estuary':{},'lake':{},'terrestrial':{},'marine':{},'stream':{}}
+  f=open(rawdatafile,'r')
   for line in f:
-    if line.split()[0]=='Web':
-      heads=line.split()[1:]
-    else:
-      web=line.split()[0]
-      data=line.split()[1:]
-      Ecotype=line.split()[1]
-      if Ecotype in datadict:
-        datadict[Ecotype][web]={}
-        for term in range(0,len(heads)):
-          if term!='Ecotype':
-            datadict[Ecotype][web][heads[term]]=data[term]
-  return datadict
+    if line.split()[0]!='Web':
+      Latitude=float(line.split()[6])
+      Species=int(line.split()[7])
+      LS=float(line.split()[10])
+      G=float(line.split()[12])
+      V=float(line.split()[14])
+      ecotype=line.split()[1]
 
-def plotter(fw_prop):
-  datadict=datareader(fw_prop)
[…]

### 2015-01-27 manuscript/latitudepaper.tex
to be overwritten

--- 2015-01-27 manuscript/latitudepaper.tex
@@
 
-In this data set, the best fit models for species richness and links per species did not include an 
+In this data set, none of the best fit models for species richness, connectance, or links per species included an 
 effect of latitude on either the scaling exponent or residual (Table \ref{Bestfits}). 
@@
 LS & Links per species & Mean number of links per taxon \\
-C & Connectance & Number of observed links divided by the number of possible links ($L/S^{2}$) \\
-\%Top & \% Top predators & Percentage of taxa without consumers \\
-\%Int & \% Intermediate consumers & Percentage of taxa with both consumers and resources \\
-\%Basal & \% Basal Resources & Percentage of taxa without resources \\
-\%Herb	& \% Herbivores	& Percentage of herbivores and detrivores (taxa that feed on basal taxa) \\
-\%Omni & \%Omnivores & Percentage of omnivores (taxa that feed on ≥2 taxa with different trophic levels) \\
 Gen & Generality & Mean number of resources per taxon \\
-GenSD & SD of generality & Standard deviation of resources per taxon \\
 Vul & Vulnerability & Mean number of consumers per taxon \\
-VulSD & SD of vulnerability & Standard deviation of consumers per taxon \\
-LinkSD & SD of links per species & Standard deviation of links (consumers and resources) per taxon \\
-SWTL & Mean short-weighted trophic level & Short-weighted trophic level averaged across taxa \\
-Path & Path length & Characteristic path length, the mean shortest food chain between species pairs \\
 \hline
@@
 
-\newpage
+% \newpage
 
-\section*{Figures}
+% \section*{Figures}
 
-\begin{figure}[!h]
-\label{gen_all}
-\includegraphics[width=.9\textwidth]{Figures/gen_all.eps}
-\caption{Relationships between mean generality and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
-\end{figure}
+% \begin{figure}[!h]
+% \label{gen_all}
+% \includegraphics[width=.9\textwidth]{Figures/gen_all.eps}
+% \caption{Relationships between mean generality and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
+% \end{figure}
 
-\begin{figure}[!h]
-\label{TL_all}
-\includegraphics[width=.9\textwidth]{Figures/TL_all.eps}
-\caption{Relationships between mean trophic level and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
-\end{figure}
+% \begin{figure}[!h]
+% \label{TL_all}
+% \includegraphics[width=.9\textwidth]{Figures/TL_all.eps}
+% \caption{Relationships between mean trophic level and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
+% \end{figure}
 

### 2015-01-28 code/property_plots.py
Plots!

@@ -53,12 +53,12 @@ def fixed_reader(coefffile):
   f.close()
   return fixed_effects
 
-def correct_raw_obs(rawdatafile,coefffile):
+def heatmappoints(rawdatafile,coefffile):
   # Would probably be more helpful to do a heatmap of observed latitudes.
-  corrected_obs={'Lake':{'tropical':[],'temperate':[],'arctic':[]},
-                'Stream':{'tropical':[],'temperate':[],'arctic':[]},
-                'Marine':{'tropical':[],'temperate':[],'arctic':[]},
-                'other':{'tropical':[],'temperate':[],'arctic':[]}}
+  corrected_obs={'Lake':{},
+                'Stream':{},
+                'Marine':{},
+                'other':{}}
   fixed_effects=fixed_reader(coefffile)
   prop=coefffile.split('/')[-1].split('_')[0]
   f=open(rawdatafile,'r')
@@ -79,23 +79,17 @@ def correct_raw_obs(rawdatafile,coefffile):
       else:
         ecotype='other'
 
-      if Latitude<23.437:
-        corrected_obs[ecotype]['tropical'].append((Species,eval(prop)))
-      elif 23.437<=Latitude<66.563:
-        corrected_obs[ecotype]['temperate'].append((Species,eval(prop)))
-      elif Latitude>=66.563:
-        corrected_obs[ecotype]['arctic'].append((Species,eval(prop)))
-
+      corrected_obs[ecotype][(Species,eval(prop))]=Latitude
   f.close()
   return corrected_obs
 
 def predictionreader(predfile):
   # Add slopelines (separate slopes for each type?)
 
-  predpoints={'Lake':{0:[],45:[],75:[]},
-              'Marine':{0:[],45:[],75:[]},
-              'Stream':{0:[],45:[],75:[]},
-              'other':{0:[],45:[],75:[]}}
+  predpoints={'Lake':{0:[],30:[],60:[]},
+              'Marine':{0:[],30:[],60:[]},
+              'Stream':{0:[],30:[],60:[]},
+              'other':{0:[],30:[],60:[]}}
 
   f=open(predfile,'r')
   for line in f:
@@ -136,24 +130,24 @@ def latplots(rawdatafile):
       # lakedata.line.linestyle=0
       # strdata.line.linestyle=0
 
+      dataset.symbol.configure(shape=1,color=1,fill_color=3,linewidth=.5)
       if ecotype=='estuary':
[…]

### 2015-01-28 manuscript/latitudepaper.tex
updated results

@@
 \begin{eqnarray}
-S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \epsilon_{i} 
+S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} 
 \end{eqnarray}
 
-where $S_{i}$ is the species richness of web $i$, $\Lambda_{i}$ its absolute latitude (degrees north or south 
-regardless of direction), and $\epsilon_{i}$ a residual error term.
-These simple linear models, fit using the function lm in R \citep{R} package stats, were used to confirm that there are indeed latitudinal gradients in food-web structure in this data set.
+where $S_{i}$ is the species richness of web $i$, $\Lambda_{i}$ its absolute
+latitude (degrees north or south  regardless of direction), $E_{i}$ is the
+ecosystem type of network $i$ and $\epsilon_{i}$ a residual error term. If the
+interaction between latitude and ecosystem type was not significant, this term
+was removed and the model re-fit. These simple linear models, fit using the
+function lm in R \citep{R} package stats, were used to determine whether there
+were latitudinal gradients in food-web structure in this data set.
 
@@
 
-Contrary to expected latitudinal gradients, $S$ and $G$ both increased with increasing latitude(Table \ref{Latlms}). 
-$G$ and $V$ were not significantly correlated with latitude.
+Contrary to expected latitudinal gradients, $S$, $Z$, $G$ and $V$ did not vary significantly over latitude, although $S$ and $G$ did vary over ecosystem types (Table~\ref{Latlms}, Fig.~\ref{Latfigs}).
 
@@
 \hline
-$S$ & 23.10 & \textless0.001 & 0.284 & 0.040 \\
-$Z$ & 2.566 & \textless0.001 & 0.020 & 0.180 \\
-$G$ & 3.269 & \textless0.001 & 0.049 & 0.014 \\
-$V$ & 2.566 & \textless0.001 & 0.020 & 0.180 \\
+$S$ & 29.42 & \textless0.001 & 0.188 & 0.167 \\
+$Z$ & 2.724 & 0.002          & 0.017 & 0.283 \\
+$G$ & 3.095 & 0.006          & 0.035 & 0.080 \\
+$V$ & 2.724 & 0.002          & 0.017 & 0.283 \\
 \end{tabular}
@@
 
-The effect of latitude on scaling relationships varied across ecosystem types (Table~\ref{Bestfits}). 
-In lakes and streams, the scaling exponent for species richness increased with latitude (although this 
-increase was not significant for lakes and generality). For other types of ecosystems, the scaling 
-exponent for species richness did not change significantly with latitude. 
-[[Some more description after figures.]]
+The effect of latitude on scaling relationships varied across ecosystem types
+(Table~\ref{Bestfits}, Fig.~\ref{scalingfig}).  In lakes and streams, the
+scaling exponent for species richness increased with latitude (although this
+increase was not significant for lakes and generality). For other types of
+ecosystems, the scaling  exponent for species richness decreased, but not significantly,
+with latitude. Despite these overal trends, the observed networks displayed a great deal
+of variability in each property.
 
@@
 \hline
+$R^{2} (adjusted)$   & \multicolumn{2}{c}{0.706} & \multicolumn{2}{c}{0.658} & \multicolumn{2}{c}{0.706} \\
 \end{tabular}

### 2015-01-28 code/Models.R

@@ -240,10 +240,17 @@ Vul_min=with(data,lm(log10(Vul)~log10(Species)
 
 
 # What's the basic correlation with latitude?
-Sp_latdirect=(with(data,lm(Species~Latitude,na.action=na.fail)))
-LS_latdirect=(with(data,lm(LS~Latitude,na.action=na.fail)))
-Gen_latdirect=(with(data,lm(Gen~Latitude,na.action=na.fail)))
-Vul_latdirect=(with(data,lm(Vul~Latitude,na.action=na.fail)))
+Sp_latdirect=(with(data,lm(Species~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
+LS_latdirect=(with(data,lm(LS~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
+Gen_latdirect=(with(data,lm(Gen~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
+Vul_latdirect=(with(data,lm(Vul~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
+# Latitude x ecotype isn't sig in any of these.
+Sp_latdirect=(with(data,lm(Species~Latitude+(Stream+Lake+Marine+Terr),na.action=na.fail)))
+LS_latdirect=(with(data,lm(LS~Latitude+(Stream+Lake+Marine+Terr),na.action=na.fail)))
+Gen_latdirect=(with(data,lm(Gen~Latitude+(Stream+Lake+Marine+Terr),na.action=na.fail)))
+Vul_latdirect=(with(data,lm(Vul~Latitude+(Stream+Lake+Marine+Terr),na.action=na.fail)))
+
+
 
 
 # Make some predictions for plotting
@@ -256,7 +263,7 @@ Vul_latdirect=(with(data,lm(Vul~Latitude,na.action=na.fail)))
 newdata=matrix(nrow=200*3*4,ncol=5)
 k=1
 for(j in c("Lake","Marine","Stream","Other")){
-  for(latitude in c(0,45,75)){
+  for(latitude in c(0,30,60)){
     for(i in 1:200){
     newdata[k,1]=i
     newdata[k,2]=latitude

### 2015-01-29 manuscript/latitudepaper.tex
using greyscale fig for printoff

@@
 Note that some of our webs describe the same area in different
-seasons or different years. [[removed the site-level random effect because I don't want it to steal latitude information.]]
+seasons or different years. 
+% [[removed the site-level random effect because I don't want it to steal latitude information.]]
 
@@
 
+\subsection*{Effect of Latitude on Scaling with S}
+
+The effect of latitude on scaling relationships varied across ecosystem types
+(Table~\ref{Bestfits}, Fig.~\ref{scalingfig}).  In lakes and streams, the
+scaling exponent for species richness increased with latitude (although this
+increase was not significant for lakes and generality). For other types of
+ecosystems, the scaling  exponent for species richness decreased, but not significantly,
+with latitude. Despite these overal trends, the observed networks displayed a great deal
+of variability in each property.
+
+\section*{Discussion}
+
+The tendency of food-web structure to exhibit scaling relationships with both
+species richness and connectance has been well-established \citep{}. As
+species richness in particular is also known to vary systematically over
+latitude \citep{}, intuitively one might suspect that any relationship
+between food-web properties such as generality might be due to the latitudinal
+gradient in species richness. In this dataset, however, we did not find
+overall latitudinal gradients in species richness, links per species, 
+generality, or vulnerability. This fact notwithstanding, latitude did affect the
+scaling relationships between species richness and the other network properties.
+
+The lack of latitudinal gradients in food-web properties in this dataset contrasts
+strongly with other studies which have found consistent variation in species richness,
+[[other properties]] \citep{}. As numbers of species and links included in a food web
+vary strongly with sampling effort as well as with the underlying diversity of the study
+area, it is possible that the lack of latitudinal trends here is a result of researchers
+tending to expend similar amounts of sampling effort across studies. This could result in
+food webs describing species-rich tropical communities omitting more species and links
+than species-poor arctic communities. While unusual, the lack of association between species richness
+and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
+between species richness and other properties is not being driven by underlying variation in
+species richness, allowing us to more clearly assess effects of latitude on scaling.
+
+Our scaling results provide only equivocal support for the niche-breadth hypothesis.
+In particular, scaling relationships between species richness and links per species,
+generality, or vulnerability strengthened with increasing latitude for lake and stream
+food webs but did not vary significantly with latitude in estuarine, terrestrial, and
+marine communities. In lakes and streams, the niche hypothesis' proposal that niches
+are narrower in the tropics fits the observed scaling patterns. The increase in links
+per species as food-web size increases is much slower in low-latitude communities than
+in their high-latitude counterparts. From this, we can infer a higher proportion of
+specialists with few predators in tropical communities. This echos earlier research [[details]]
+\citep{}. In contrast, temperate and polar communities appear to contain more generalist
+species. As food webs are generally aggregated over space and time, the stronger
+increase in links per species with species richness could be driven by species switching
+between more prey species that are only intermittently available in areas with highly
+variable climates.
+
+\section*{Conclusion}
+
+[[something catchy to sum up]]
+
+%\end{spacing}
+\newpage
+\bibliographystyle{jae}%Compile with jae.bst style file
+\bibliography{noISN.bib}% your .bib file(s)
+
+\newpage
+
+\section*{Tables}
+
+\begin{center}
+\begin{table}[!h]
+\caption{Symbols for and descriptions of food-web properties.}
+\label{symboltable}
+\begin{tabular}{c l l}
+\hline
+Symbol      & Name & Description \\
+\hline
+$S$ & Species richness & Number of trophic species \\
+$Z$ & Links per species & Mean number of links per taxon \\
+$G$ & Generality & Mean number of resources per taxon \\
+$V$ & Vulnerability & Mean number of consumers per taxon \\
+\hline
+\end{tabular}
+\end{table}
+\end{center}
+
 \begin{table}[!t]
@@
 
-\subsection*{Effect of Latitude on Scaling with S}
-
-The effect of latitude on scaling relationships varied across ecosystem types
-(Table~\ref{Bestfits}, Fig.~\ref{scalingfig}).  In lakes and streams, the
-scaling exponent for species richness increased with latitude (although this
-increase was not significant for lakes and generality). For other types of
-ecosystems, the scaling  exponent for species richness decreased, but not significantly,
-with latitude. Despite these overal trends, the observed networks displayed a great deal
-of variability in each property.
-
 \begin{table}[!h]
@@
 \begin{tabular}{l | l l | l l | l l }
-\multirow{2}{*}{Effect} & \multicolumn{2}{c}{$Z$} & \multicolumn{2}{c}{$G$} & \multicolumn{2}{c}{$V$}\\
-                & $\beta$ & $p$-value &  $\beta$ & $p$-value &  $\beta$ & $p$-value & \\
+Effect          & \multicolumn{2}{c|}{$Z$} & \multicolumn{2}{c|}{$G$} & \multicolumn{2}{c}{$V$}\\
+                & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
 \hline
@@
 \hline
-$R^{2} (adjusted)$   & \multicolumn{2}{c}{0.706} & \multicolumn{2}{c}{0.658} & \multicolumn{2}{c}{0.706} \\
+$R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
 \end{tabular}
@@
 
-\section*{Discussion}
-
-[[This'll need to be redone]]
-% The tendency of food-web structure to exhibit scaling relationships with both
-% species richness and connectance has been well-established \citep{}. As
-% species richness in particular is also known to vary systematically over
-% latitude \citep{}, intuitively one might suspect that any relationship
-% between food-web properties such as generality might be due to the latitudinal
-% gradient in species richness. Here, we found that while there were latitudinal
-% gradients in species richness and generality, latitude was not related to
-% either the scaling relationship between generality and species richness or the
-% residuals of this scaling relationship.
-
-% The latitudinal gradient in species richness in this data set ran in the opposite 
-% direction to the general trends for (list types of taxa). This may be due to the 
-% fact that latitudinal gradient in species richness are usually studied within a
-% taxonomic or trophic group (e.g., birds, vascular plants), whereas food webs 
-% measure many taxa concurrently. It is possible that while many taxa generally increase
-% towards the tropics, the number of species across all taxa that co-occur within an 
-% study site decreases. Alternatively, it is possible that by using trophic-species versions
-% of our food webs, we have artificially reversed the species-richness gradient. [[re-run analyses
-% with species-species webs]]. This would imply that, while there may be more species in the tropics,
-% many of those species tend to have identical predator and prey sets to co-occuring species. In either
-% case, it does not seem likely that the increase in
-% generality with latitude that we observed is due to an underlying tendency for
-% species to pursue a wider variety of prey at higher latitudes. Rather, the
-% trend in generality can be more parsimoniously explained by the trend in
-% species richness.
-
-% Our findings here add further doubt to the niche-breadth hypothesis, as
-% narrower niches in the tropics were associated with lower species richness in
-% this data set. It appears instead that, as more species are available, each
-% species tends to consume more prey, be consumed by more predators, and have
-% more links in general (check with figs). This makes intuitive sense as a more
-% species-rich community is likely to have more species with similar behaviour
-% and morphology that thereby have overlapping predator or prey sets.
-
-% Parallel increases in generality and species richness across latitude have
-% also been noted in studies of plant-pollinator networks (although in that case
-% species richness was highest in the tropics) \citep{Schleuning2012}. Although
-% the authors of that study do not explicitly examine the relationship between
-% specialization and network size, they do cite increasing plant species
-% richness as a potential driver for increasing generalization
-% \citep{Schleuning2012}. Although the scaling of mutualist network structure
-% does not appear to have been explored as systematically as that of unipartite
-% food webs, some poperties such as nestedness \citep{Vazquez2004} and XX
-% \citep{} have been shown to scale with species richness. As such scaling
-% appears to be common to both antagonistic and mutualistic food webs, and
-% trends in species richness can explain counterintuitive trends in network
-% structure \citep{Schleuning2012}, it seems likely that many latitudinal trends
-% in network structure are at least partly due to trends in species richness.
-
-% %Nestedness increases with A+P, increases number of extreme specialists AND number of generalists. Not clear how degree should scale with S according to scaling with nestedness.
-
-% \section*{Conclusion}
-
-% It was not our initial intention to question the validity of the wide range of
-% studies exploring variation in network structure across changing environments \citep{}.
-% However, if those studies have not taken into account changes in species
-% richness over environmental gradients, it is possible that observed changes in
-% food-web structure are due only indirectly to the environmental variables of
-% interest. Effects of environmental variables on network structure should
-% therefore be interpreted with caution unless effects of changing species
-% richness are made explicit.
-
-%\end{spacing}
-\newpage
-\bibliographystyle{jae}%Compile with jae.bst style file
-\bibliography{noISN.bib}% your .bib file(s)
-
 \newpage
 
-\section*{Tables}
+\section*{Figures}
 
-\begin{center}
-\begin{table}[!h]
-\caption{Symbols for and descriptions of food-web properties.}
-\label{symboltable}
-\begin{tabular}{c l l}
-\hline
-Symbol      & Name & Description \\
-\hline
-S & Species richness & Number of trophic species \\
-LS & Links per species & Mean number of links per taxon \\
-Gen & Generality & Mean number of resources per taxon \\
-Vul & Vulnerability & Mean number of consumers per taxon \\
-\hline
-\end{tabular}
-\end{table}
-\end{center}
-% NODF & Average Nestedness & Degree to which interactions among specialists are subsets or interactions among generalists \\
-% Chain & Chain length & Mean food chain length \\
-% Cluster & Clustering coefficient & Mean clustering coefficient (probability that two taxa linked to the same taxon are also linked) \\
+\begin{figure}[!h]
+\label{Latfigs}
+\includegraphics[width=.9\textwidth]{Figures/properties_vs_lat.eps}
+\caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability.
+No food web property showed a significant latitudinal gradient in this dataset (N=259 food webs).}
+\end{figure}
 
-\begin{center}
-\begin{table}[!h]
-\caption{Full models for S, LS, and C.}
-\label{symbols}
-\begin{tabular}{c c c c c c c}
-\hline
- & \multicolumn{2}{c}{S} & \multicolumn{2}{c}{C} & \multicolumn{2}{c}{LS} \\
-\hline
-Effect & Estimate & $p$-value & Estimate & $p$-value & Estimate & $p$-value \\
-\hline
-Latitude 			& 0.002  & 0.873  & -0.006 & 0.480  & -0.004 & 0.613 \\ 
-Estuary 			& 1.078  & 0.022  & -0.809 & 0.012  & 0.269 & 0.362 \\
-Freshwater 			& 1.347  & \textless0.001  & -1.229 & \textless0.001 & 0.118 & 0.394 \\
-Marine 				& 1.127  & \textless0.001 & -0.761 & \textless0.001 & 0.366 & 0.012 \\
-Terrestrial 		& 1.097  & \textless0.001 & -0.919 & \textless0.001 & 0.178 & 0.354\\
-Latitude:Freshwater & 0.002  & 0.902  & 0.010  & 0.299  & 0.012 & 0.194\\
-Latitude:Marine 	& 0.003  & 0.847  & 0.001  & 0.902  & 0.004 & 0.662 \\
-Latitude:Terrestrial & 0.001 & 0.923  & 0.003  & 0.724  & 0.005 & 0.597 \\
-\end{tabular}
-\end{table}
-\end{center}
-
-% \newpage
-
-% \section*{Figures}
-
-% \begin{figure}[!h]
-% \label{gen_all}
-% \includegraphics[width=.9\textwidth]{Figures/gen_all.eps}
-% \caption{Relationships between mean generality and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
-% \end{figure}
-
-% \begin{figure}[!h]
-% \label{TL_all}
-% \includegraphics[width=.9\textwidth]{Figures/TL_all.eps}
-% \caption{Relationships between mean trophic level and latitude for food webs with moderate connectance (0.1, mean of empirical webs) at high (S=109, solid line), moderate (S=36, dashed line), and low (S=5, dotted line) species richness.}
-% \end{figure}
+\begin{figure}[!h]
+\label{scalingfig}
+\includegraphics[width=.9\textwidth]{Figures/scaling_with_S_grey.eps}
+\caption{Relationships between species richness and mean links per species, mean generality, and mean vulnerability (N=259 food webs).
+In estuarine, terrestrial, and marine communities the scaling relationship with species-richness did not vary significantly across latitude for any food-web property.
+In lake and stream communities, each food-web property showed stronger scaling with species richness as latitude increased (N=259 food webs).
+}
+\end{figure}
 

### 2015-02-02 manuscript/latitudepaper.tex
half-way through methods

@@
 variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
-climate is more variable at high latitudes \citep{}, 
-suggesting that latitude may indirectly affect food-web structure.
-Indeed, these latitudinal environmental gradients have been put forward as potential driverd for the latitudinal gradient in species 
-richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,,}.
+climate is more variable at high latitudes \citep{}. These variables affect both the resources available and species' 
+metabolisms~\citep{Stegen2012}, and have been proposed as influences on the strength of 
+interspecific interactions~\citep{Marquis2005,Schemske2009}. 
+By shaping interactions between species, latitudinal gradients may also shape food-web structure.
+Indeed, these latitudinal environmental gradients have been put forward as potential driverd for the 
+latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,,}.
 
-This effect of latitude on species richness, however, presents a problem for the analysis of other aspects of food-web structure.
-Although it was initially thought that food-web structure was small-world and scale invariant \citep{}, further 
-analyses with higher-quality data have revealed that most food-web structural properties scale strongly with species 
-richness, connectance (the proportion of possible links that are realized), or both \citep{Riede2010} 
-(see \citet{Dunne2006} for a review of the history of scaling laws in food web theory). This means that any relationship
-between latitude and food-web structure must be considered in light of the latitudinal gradient in species richness.
-This is especially true for food-web properties such as measures of specialization
-that both scale with species richness \citep{Riede2010} and are related to candidate
-explanations for the latitudinal diversity gradient \citep{Vazquez2004}.
+% These gradients, together with the strength and generality of associations between biological processes and environmental variables, suggest that variation in network structure 
+% may also be explained by ecological gradients \citep{Baiser2012}.
 
-[[Smoother transition needed here]]
-% Explain niche space hypothesis, Schemske, Vazquez. Then make clear that niche space suggests opposite gradient to ~S^B.
-%Then give hypotheses.
-A latitudinal gradient in specialization lies behind the ``latitude-niche breadth hypothesis'' \citep{Vazquez2004}.
+One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\citep{,Vazquez2004}. 
 This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
@@
 
-Importantly, the expectation of the latitude-niche breadth hypothesis that higher species richness is associated with 
-reduced competition is contary to the expected increase in the mean number of interactions per species (one potential 
-measure of specialization) as species richness increases \citep{Dunne2006,Riede2010}. If, therefore, there is a
-distinct effect of latitude on specialization then this effect should be visible in changing scaling relationships.
-Here, we tested for changes in the scaling of mean links per species, mean generality, and mean vulnerability with species
-richness over latitude. We focused on these three food-web properties --only some of the wide array of metrics that have been
-described (see e.g. \citep{})-- because together they provide a measure a species' biotic specialization, which underlies the 
-``latitude-niche breadth hypothesis''.
-
-% In addition to species richness, there are general and robust latitudinal gradients in metabolic rates \citep{Stegen2012} and 
-% rates and intensities of species interactions \citep{Marquis2005,Schemske2009}. These gradients, together with the strength and 
-% generality of associations between biological processes and environmental variables, suggest that variation in network structure 
-% may also be explained by ecological gradients \citep{Baiser2012}. Importantly, some of these gradients may act directly 
-% on food-web properties such that they change over latitude beyond the expected changes due to changing species richness. For 
-% example, if niche sizes vary with latitude then mean numbers of predators, prey, and links per species may also vary with 
-% latitude. Some of this variation may be explained by variation in species richness, but as niche sizes are believed to be 
-% related directly to latitude it is reasonable to expect that there may also be latitudinal effects unrelated to those of 
-% changing species richness.
+If decreased seasonality or higher productivity is the cause of higher species-richness in the tropics, then 
+there should be other effects of latitude on food-web structure. Attempts to unravel the effects, however,
+are complicated by known effects of species richness on many other network properties~\citep{Riede2010}. In particular,
+narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,
+average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
+that a latitudinal effect on specialization may be obscured by a latitudinal gradient in species richness. If this is
+the case, it may still be possible to uncover effects of latitude on specialization by examining the shape of the scaling 
+relationship between specialization and species richness over changing latitude. Here, we use three measures of specialization:
+mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
+latitude affects the scaling of each property with species richness, we test effects of latitude on specialization implied by
+the ``latitude-niche breadth hypothesis''.
 
@@
 given, obtained estimated coordinates using Google Earth \citep{GoogleEarth}.
-Webs were also classified according to ecosystem type (terrestrial, lake,
-stream, estuary, or marine), year of publication (to control for potential change
-in standards of data collection over time \citep{Dunne2006}), and whether or not
-humans were included.
 
@@
 
-We then converted each web to a trophic-species web by aggregating species with identical predator and prey sets.
-Using trophic species webs helps to reduce variation in resolution across different studies and across taxa within
-a study \citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}. The number of species ($S$) and links ($L$) in each 
-trophic species
-web were counted and used to calculate mean links per species ($Z$), generality ($G$), and vulnerability ($V$).
+As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
+is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
+Many analyses of food-web structure reduce this variation by aggregating species with identical predator and prey
+sets to form ``trophic species'' webs (e.g. ~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
+is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
+species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
+of the dataset. As the version of the dataset used did not qualitatively change the results, we present only
+the results for the original webs in the main text. In each case, we counted the number of species ($S$) and 
+links in each web and used these to calculate the mean number of links per species ($Z$), mean generality 
+($G$), and mean vulnerability ($V$) of each web.
 
@@
 
-We first examined simple linear relationships between latitude and $S$, $Z$, $G$, and $V$. We fit models of the form
+[[re-run with dredge]]
+To determine whether there were latitudinal gradients in food-web structure,
+we first examined simple linear relationships between latitude and $S$, $Z$, $G$, and $V$. 
+We fit models of the form
 
@@
 
-where $S_{i}$ is the species richness of web $i$, $\Lambda_{i}$ its absolute
+where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
 latitude (degrees north or south  regardless of direction), $E_{i}$ is the
-ecosystem type of network $i$ and $\epsilon_{i}$ a residual error term. If the
-interaction between latitude and ecosystem type was not significant, this term
-was removed and the model re-fit. These simple linear models, fit using the
-function lm in R \citep{R} package stats, were used to determine whether there
-were latitudinal gradients in food-web structure in this data set.
+ecosystem type of network $i$ (comprising terms for stream, marine, lake, and terrestrial networks with estuarine
+networks being the intercept) and $\epsilon_{i}$ a residual error term. 
+We then simplified these maximal models. To do this, we calculated the AIC
+of the chosen maximal model, as well as the AIC's of a suite of candidate simplified models identified
+using R~\citep{R} function dredge from packages MuMIn~\citep{MuMIn}. Simplified models were obtained by
+systematically removing all possible combinations of terms from the full model.
+The best-fitting model was then determined to be the model with the fewest terms where $\delta$AIC<2.
 
@@
 
-We were then able to examine the form of the scaling relationship between each property ($Z$, $G$, and $V$) and $S$.
-The scaling relationship between $Z$ and $S$ has been shown to be a power law \citep{Riede2010} of the form
+Next, we examined the form of the scaling relationship between each 
+property ($Z$, $G$, and $V$) and $S$. The scaling relationship between $Z$ and 
+$S$ has been shown to be a power law \citep{Riede2010} of the form
 
@@
 \label{Power}
-Z_{i}=\alpha S_{i}^{\beta} + \epsilon_{i} 
+Z_{i}~\alpha S_{i}^{\beta}
 \end{equation}
@@
 \label{Loglog}
-log(Z_{i}) = log(\alpha) + \beta log(S_{i}) + \epsilon_{i}  
+\log{Z_{i}} ~ \log{\alpha} + \beta\log{S_{i}}
 \end{equation}
+
+Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
+Specifically,~\ref{Power} implies a normally-distributed, additive error and~\ref{LogLog} a lognormal,
+multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
+over another, we follow the recommendations in \citet{Xiao2011} and compared the two
+model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
+data was then used to test for potential effects of latitude.
 
@@
 compared the error distributions of models for $G$ and $V$ using both the power-law and logarithmic formulations. 
-
-%%% TO SI
-
-% Note that the two forms of the power-law relationship imply different error structures: normally-distributed, additive error in 
-% \ref{Power} and lognormal, multiplicative error in \ref{Loglog}. As there is no intuitive reason to believe that our
-% data have one error distribution over another, we follow the recommendations in \citet{Xiao2011} and compared the two
-% model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
-% data was then used to test for potential effects of latitude.
+In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
+species richness.
 

### 2015-02-03 manuscript/latitudepaper.tex
Up to revising the discussion now

@@
 
-[[re-run with dredge]]
 To determine whether there were latitudinal gradients in food-web structure,
@@
 
-\begin{eqnarray}
+\begin{equation}
+\label{Latfull}
 S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} 
-\end{eqnarray}
+\end{equation}
 
@@
 systematically removing all possible combinations of terms from the full model.
-The best-fitting model was then determined to be the model with the fewest terms where $\delta$AIC<2.
+The best-fitting model was then determined to be the model with the fewest terms 
+where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
+and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
+model.
 
@@
 
-We then assessed
-the impact of latitude on this relationship; specifically, the effect of latitude on the scaling exponent $\beta$. 
-In addition to latitude, we included a factorial variable for ecosystem type (stream, lake, terrestrial, marine, or estuary) to account for recognized variation in food web structure across ecosystem types \citep{}.
-% We also considered other trends in the data that could affect relationships between latitude and species richness.
-% To account for changing standards in data collection over time \citep{Dunne2006} we included an effect of year of
-% publication. As 11 of our XX webs included humans, and therefore might have different properties than other networks,
-% we included a factorial effect of the presence of humans. 
-Note that some of our webs describe the same area in different
-seasons or different years. 
-% [[removed the site-level random effect because I don't want it to steal latitude information.]]
+We then assessed the impact of latitude on the scaling relationships between $Z$, $G$, $V$, and $S$. 
+Even if there is no direct effect of latitude on specialization, perhaps due to contrasting effects
+on species richness as described above, there may still be an effect of latitude on the scaling of
+each property with species richness. In fact, if the species-rich tropics truly have narrower 
+niches~\citep{Brown2004}, then we would expect to see less increase in mean numbers of links, 
+predators, and prey with increasing species richness in the tropics.
+In the context of the scaling relationships above, we wish to determine the effect of latitude on
+the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
+web property directly, we included a factorial variable for ecosystem type (stream, lake, 
+terrestrial, marine, or estuary), as well as interactions between food web type and latitude.
 
@@
 \label{PowerLat}
-Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{3}E_{i}} + \epsilon_{i} 
+Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{2}E_{i}+\beta_{3}LE_{i}} + \epsilon_{i} 
 \end{equation}
 
-where $L_{i}$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
+where $S_{i}$ is the number of species in food web $i$, $L_{i}$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
 $E_{i}$ indicates the ecosystem type of food web $i$.
@@
 \label{LogLat}
-1log(Z_{i})= log(\alpha)+\beta_{0}log(S_{i}) + \beta_{1}L*log(S_{i}) +\beta_{3}E*log(S_{i}) +\epsilon_{i}
+\log{Z_{i}} = \log{\alpha}+\beta_{0}\log{S_{i}} + \beta_{1}L\log{S_{i}} +\beta_{2}E\log{S_{i}} +\beta_{3}LE\log{S_{i}} +\epsilon_{i}
 \end{equation}
 
-We fit equation \ref{LogLat}, as well as similar equations for $G$ and $V$ using R \citep{R} function lm from package stats
-\citep{stats}.
-We calculated the AIC of the chosen maximal model, as well as the AIC's of a suite of candidate simplified models.
-Simplified models were obtained by systematically removing all possible combinations of terms from the full model.
-The term for species richness was not removed from a model if any of the terms affecting the exponent $\beta$ were 
-included in the model. The best-fitting model was then determined to be the model with the fewest terms where $\delta$AIC<2.
-
-The model with the lowest AIC was selected as the best-fitting model. 
-This simplification was performed using the
-R \citep{R} function dredge from package MuMIn \citep{MuMIn}. We then used the R \citep{R} function lm
-to estimate the standardized effects ($\beta$s ) for each fixed effect in the 
-best-fitting models, as well as their corresponding $p$-values.
+For each property in $Z$, $G$, and $V$, we used the form of the equation that was best supported
+when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
+We then simplified the model. As with the models describing the relationships between latitude and food-web
+properties, we calculated the AIC of the maximal and all reduced models, created by systematically removing
+all possible combinations of terms. Note that if an interaction term was included in a reduced model, all
+associated main effects were also retained. $S$ was included in all reduced models. Reduced models were
+identified using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. The best-fitting model
+was then determined to be the model with the fewest terms where $\Delta$AIC<2. Where there were several
+models with the fewest terms where $\Delta$AIC<2, the model with the lowest AIC in this set was chosen as
+the best-fitting model. The best-fitting model was then fit using R~\citep{R} function lm from package stats~\citep{stats}.
 
@@
 
-\subsection*{Scaling Relationships with S and Latitude}
+\subsection*{Scaling Relationships with $S$ and Latitude}
 
-For relationships of $Z$, $G$, and $V$ to S, the assumption of multiplicative log-normal error was better supported
-(Table \ref{Errorfits}). We therefore use only models with logarithmic form for the remainder of the paper.
+For relationships of $Z$, $G$, and $V$ to $S$, equation~\ref{LogLog} had a lower AIC than the corresponding
+equation~\ref{Power}. This indicates that the data support an assumption of multiplicative log-normal
+error better than an assumption of additive normal error. That is, [[but what does it mean?]] . 
+We therefore used logarithmic-form models when assessing the effect of latitude on scaling relationships 
+with $S$.
 
-Contrary to expected latitudinal gradients, $S$, $Z$, $G$ and $V$ did not vary significantly over latitude, although $S$ and $G$ did vary over ecosystem types (Table~\ref{Latlms}, Fig.~\ref{Latfigs}).
+Contrary to the expected latitudinal gradient, the best-fit version of equation~\ref{Latfull} for $S$
+did not include a term for latitude or any of its interactions with ecosystem type. Species richness was
+higher for stream ecosystems ($\alpha_{2:Stream}$=22.4, $p$\textless0.001) than other ecosystem types. 
+Similarly, the best-fit version of equation~\ref{Latfull} for $G$ did not include 
+any terms for latitude or interactions between latitude and ecosystem type. $G$ was lower in terrestrial
+and lake food webs than in other ecosystem types ($\alpha_{2:Terrestrial}$=-3.77, $p$\textless0.001 and 
+$\alpha_{2:Lake}$=-1.98, $p$=0.044). The best-fit models for $Z$ and $V$ did not include any terms for
+latitude, ecosystem type, or their interactions.
+the best-fit version of equation~\ref{Latfull} for $Z$ did not include a term for latitude,
+ecosystem type, or any of their interactions. Food webs tended to contain about 3.53 links per species
+($p$\textless0.001), with the average species being preyed upon by 3.53 predators ($p$\textless0.001).
 
@@
 
-The effect of latitude on scaling relationships varied across ecosystem types
-(Table~\ref{Bestfits}, Fig.~\ref{scalingfig}).  In lakes and streams, the
-scaling exponent for species richness increased with latitude (although this
-increase was not significant for lakes and generality). For other types of
-ecosystems, the scaling  exponent for species richness decreased, but not significantly,
-with latitude. Despite these overal trends, the observed networks displayed a great deal
-of variability in each property.
+The effect of latitude on scaling relationships varied across ecosystem types.
+Overall, specialization in marine and terrestrial food webs increased towards the poles, 
+while specialization in lake food webs increased towards the equator (Fig.~\ref{scalinfig}). 
+In estuarine and stream food webs, there was a great deal of variation, with links per species
+and vulnerability increasing towards the poles and generality increasing towards the equator.
+More specifically, the scaling of mean links per species with species richness increased with
+increasing latitude ($\beta_{Latitude}$=0.004, $p$\textless0.001; Table~\ref{Bestfits}). This
+increase, however, was reversed for marine and terrestrial food webs
+($\beta_{Latitude:Marine}$=-0.005, $p$=0.007 and
+$\beta_{Latitude:Terrestrial}$=-0.005, $p$=0.001). Scaling of mean vulnerability with
+species richness showed the same pattern ($\beta_{Latitude}$=0.004, $p$\textless0.001;
+$\beta_{Latitude:Marine}$=-0.005, $p$=0.007; and $\beta_{Latitude:Terrestrial}$=-0.005, $p$=0.002).
+In contrast, scaling of mean generality with species richnesss increased with latitude 
+for lake food webs ($\beta_{Latitude:Lake}$=0.006, $p$=0.002) but did not vary with latitude for
+other ecosystem types ($\beta_{Latitude}$=-0.001, $p$=0.199).
 
@@
 
-\begin{center}
 \begin{table}[!h]
-\caption{Symbols for and descriptions of food-web properties.}
-\label{symboltable}
-\begin{tabular}{c l l}
+\caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude.
+Note that none
+of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. Each `NA' indicates a term that was not included in the corresponding best-fit model.}
+\label{Latlms}
+\begin{tabular}{l | l l  l l  l l  l l}
+
 \hline
-Symbol      & Name & Description \\
+\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
+& $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
 \hline
-$S$ & Species richness & Number of trophic species \\
-$Z$ & Links per species & Mean number of links per taxon \\
-$G$ & Generality & Mean number of resources per taxon \\
-$V$ & Vulnerability & Mean number of consumers per taxon \\
+Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
+Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
+Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
+Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
 \hline
-\end{tabular}
-\end{table}
-\end{center}
-
-\begin{table}[!t]
-
-\caption{AIC's for model \ref{Power}, assuming normal error, and model \ref{Loglog}, assuming lognormal error.}
-\label{Errorfits}
-\begin{tabular}{l | l l | c}
-Property & Normal error & Lognormal error & Model selected \\
-\hline
-$Z$ & 1151 &  767 & \ref{Loglog} \\
-$G$ & 1266 & 1037 & \ref{Loglog} \\
-$V$ & 1151 & 767 & \ref{Loglog} \\
 \end{tabular}
@@
 \begin{table}[!h]
-\caption{Intercepts and slopes for simple linear regressions of food web properties against absolute latitude.}
+\caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude in trophic-species versions of food webs.
+Note that none
+of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. `NA' a term that was not included in the corresponding best-fit model.}
 \label{Latlms}
-\begin{tabular}{l | l l | l l}
+\begin{tabular}{l | l l  l l  l l  l l}
 
-\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Slope} \\
-                      & $\alpha_{0}$ & $p$-value & $\alpha_{1}$ & $p$-value \\
 \hline
-$S$ & 29.42 & \textless0.001 & 0.188 & 0.167 \\
-$Z$ & 2.724 & 0.002          & 0.017 & 0.283 \\
-$G$ & 3.095 & 0.006          & 0.035 & 0.080 \\
-$V$ & 2.724 & 0.002          & 0.017 & 0.283 \\
+\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
+& $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
+\hline
+Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
+Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
+Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
+Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
+\hline
 \end{tabular}
@@
 \begin{table}[!h]
+\caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness.
+Each `NA' indicates a term that was not included in the corresponding best-fit model.
+These models refer to the original versions of food webs.
+}
+\label{Bestfits}
+\begin{tabular}{l | l l  l l  l l }
+Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
+                & \multicolumn{2}{c}{Vulnerability}\\
+                & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
+\hline
+Intercept               &-0.453 & \textless0.001 & -0.249 & \textless0.001 & -0.453 & \textless0.001 \\
+log(species)            & 0.419 & \textless0.001 &  0.663 & \textless0.001 &  0.419 & \textless0.001 \\
+log(species):Lake       & 0.119 & \textless0.001 & -0.185 & 0.016          &  0.119 & \textless0.001 \\
+log(species):Marine     & 0.255 & \textless0.001 &  0.090 & 0.002          &  0.255 & \textless0.001 \\
+log(species):Terrestrial& 0.207 & 0.002          & -0.122 & \textless0.001 &  0.207 & 0.002 \\
+log(species):Latitude   & 0.004 & \textless0.001 & -0.001 & 0.199          &  0.003 & \textless0.001 \\
+log(species):Latitude:Marine&-0.004 & 0.007      &  NA    &  NA            & -0.005 & 0.007 \\
+log(species):Latitude:Terrestrial&-0.005 & 0.002 &  NA    &  NA            & -0.005 & 0.002 \\
+log(species):Latitude:Lake & NA & NA             &  0.006 & 0.002          &  NA    & NA    \\
+\hline
+$R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
+\hline
+\end{tabular}
+\end{table}
 
-\caption{Standard effects and their $p$-values for the best-fitting models of links per species ($Z$), generality ($G$), and vulnerability ($V$).}
+\begin{table}[!h]
+\caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness.
+Each `NA' indicates a term that was not included in the corresponding best-fit model.
+These models refer to the trophic species versions of food webs.
+}
 \label{Bestfits}
-\begin{tabular}{l | l l | l l | l l }
-Effect          & \multicolumn{2}{c|}{$Z$} & \multicolumn{2}{c|}{$G$} & \multicolumn{2}{c}{$V$}\\
+\begin{tabular}{l | l l  l l  l l }
+Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
+                & \multicolumn{2}{c}{Vulnerability}\\
                 & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
@@
 $R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
+\hline
 \end{tabular}
@@
 
-\begin{figure}[!h]
-\label{Latfigs}
-\includegraphics[width=.9\textwidth]{Figures/properties_vs_lat.eps}
-\caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability.
+% \begin{figure}[!h]
+% \label{Latfigs}
+% \includegraphics[width=.9\textwidth]{Figures/properties_vs_lat.eps}
+% \caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability.
 No food web property showed a significant latitudinal gradient in this dataset (N=259 food webs).}
-\end{figure}
+% \end{figure}
 
@@
 \includegraphics[width=.9\textwidth]{Figures/scaling_with_S_grey.eps}
-\caption{Relationships between species richness and mean links per species, mean generality, and mean vulnerability (N=259 food webs).
-In estuarine, terrestrial, and marine communities the scaling relationship with species-richness did not vary significantly across latitude for any food-web property.
-In lake and stream communities, each food-web property showed stronger scaling with species richness as latitude increased (N=259 food webs).
-}
+\caption{Relationships between species richness and mean links per species, mean generality, and mean 
+vulnerability (N=259 food webs). Scaling of mean links per species and mean vulnerability with species 
+richness strengthened with latitude for estuarine, stream, and lake food webs. This strengthening was
+reversed for marine and terrestrial food webs. Scaling of mean generality with species richness 
+strengthened with latitude for lake food webs, but did not significantly vary with latitude for other
+ecosystem types (N=259 food webs). }
 \end{figure}

### 2015-02-03 code/Models.R

@@ -260,15 +260,20 @@ for(infile in c('../mod_data/summary-properties.tsv','../non_TS/summary-properti
       ,na.action=na.fail))  }
 
   # What's the basic correlation with latitude?
-  Sp_latdirect=(with(data,lm(Species~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
-  LS_latdirect=(with(data,lm(LS~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
-  Gen_latdirect=(with(data,lm(Gen~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
-  Vul_latdirect=(with(data,lm(Vul~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
-  # Latitude x ecotype isn't sig in any of these.
-  Sp_latdirect=(with(data,lm(Species~Latitude+(Stream+Lake+Marine+Terr),na.action=na.fail)))
-  LS_latdirect=(with(data,lm(LS~Latitude+(Stream+Lake+Marine+Terr),na.action=na.fail)))
-  Gen_latdirect=(with(data,lm(Gen~Latitude+(Stream+Lake+Marine+Terr),na.action=na.fail)))
-  Vul_latdirect=(with(data,lm(Vul~Latitude+(Stream+Lake+Marine+Terr),na.action=na.fail)))
+  Sp_latdirect_full=(with(data,lm(Species~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
+  LS_latdirect_full=(with(data,lm(LS~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
+  Gen_latdirect_full=(with(data,lm(Gen~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
+  Vul_latdirect_full=(with(data,lm(Vul~Latitude*(Stream+Lake+Marine+Terr),na.action=na.fail)))
+
+  sld=dredge(Sp_latdirect_full,rank=AIC)
+  lld=dredge(LS_latdirect_full,rank=AIC)
+  gld=dredge(Gen_latdirect_full,rank=AIC)
+  vld=dredge(Vul_latdirect_full,rank=AIC)
+
+  Sp_latdirect=(with(data,lm(Species~Stream),na.action=na.fail))
+  LS_latdirect=(with(data,lm(LS~1),na.action=na.fail))
[…]

### 2015-02-03 code/property_plots.py

@@ -319,7 +319,7 @@ def scaleplots(rawdatafile,colorscheme,webtype):
 
   showbar.autoticky()
   showbar.set_view(1.268,0.3688,1.318,0.889)
-  grace.add_drawing_object(DrawText,text='Degrees from equator', x=1.38, y=.6289, rot=270,char_size=.75,just=2)
+  grace.add_drawing_object(DrawText,text='Latitude (degrees from equator)', x=1.38, y=.6289, rot=270,char_size=.75,just=2)
 
   grace.write_file(outfile1)
   grace.write_file(outfile2) 

### 2015-02-03 manuscript/latitudepaper.tex
ran through the discussion again too.

@@
 
-The tendency of food-web structure to exhibit scaling relationships with both
-species richness and connectance has been well-established \citep{}. As
+The tendency of food-web structure to exhibit scaling relationships with
+species richness has been well-established \citep{Dunne2004,Riede2010}. As
 species richness in particular is also known to vary systematically over
@@
 overall latitudinal gradients in species richness, links per species, 
-generality, or vulnerability. This fact notwithstanding, latitude did affect the
-scaling relationships between species richness and the other network properties.
+generality, or vulnerability.
 
@@
 food webs describing species-rich tropical communities omitting more species and links
-than species-poor arctic communities. While unusual, the lack of association between species richness
+than species-poor arctic communities. In addition, it is worth noting that gradients in
+species richness are generally measured for a single taxonomic group at a time~\citep{}.
+It is possible that these taxa are not well-represented in our food webs and that the
+dominant taxa in them do not have an underlying latitudinal gradient in richness. In
+either case, the lack of association between species richness
 and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
@@
 
-Our scaling results provide only equivocal support for the niche-breadth hypothesis.
-In particular, scaling relationships between species richness and links per species,
-generality, or vulnerability strengthened with increasing latitude for lake and stream
-food webs but did not vary significantly with latitude in estuarine, terrestrial, and
-marine communities. In lakes and streams, the niche hypothesis' proposal that niches
-are narrower in the tropics fits the observed scaling patterns. The increase in links
-per species as food-web size increases is much slower in low-latitude communities than
-in their high-latitude counterparts. From this, we can infer a higher proportion of
-specialists with few predators in tropical communities. This echos earlier research [[details]]
-\citep{}. In contrast, temperate and polar communities appear to contain more generalist
-species. As food webs are generally aggregated over space and time, the stronger
-increase in links per species with species richness could be driven by species switching
-between more prey species that are only intermittently available in areas with highly
-variable climates.
+These effects varied strongly across ecosystem types. In marine and terrestrial food webs,
+scaling of links per species, generality, and vulnerability was not strongly affected by
+latitude. This is consistent with the idea that species' niche breadths do not vary systematically
+with temperature and productivity but that the niche space might be larger in species-rich communities
+~\citep{Davies2007}. In contrast, scaling in of lake, estuarine, and stream was generally stronger
+towards the poles. This means that species in tropical communities gain fewer additional feeding links
+per additional species in the web, supporting the hypothesis that greater stability in the tropics
+leads to narrower niches~\citep{Brown2004} and a higher proportion of specialists~\citep{}. As food webs
+are generally aggregated in space and time, the greater increase in links in high latitude stream, 
+estuarine, and lake food webs might reflect prey switching as different food sources become
+available~\citep{}.
 
@@
 
-[[something catchy to sum up]]
+Our results were consistent with the latitude-niche breadth hypothesis, but only in certain ecosystem
+types. This suggests that different types of food webs respond differently to differences in climate
+driven by latitudinal gradients. [[A sentence or two explaining why this is important.]]
 

### 2015-03-04 manuscript/latitudepaper.tex
Just changed which version of the figure to use
Added Tamara's comments

@@
 
-\section*{Introduction}
+\section*{Introduction} [[Add something about ecosystem type since it's in the methods]]
 
@@
 ecological communities \citep{Williams2000,earlierwork} and to understand how that structure relates to environmental variables 
-such as land use \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, and climate\citep{}. The latter
+such as land use [[lets really consider the three env variables used here.
+there really is not a lot of work on land use....i get why prim prod and climate are included....maybe focus on habitat types since you focus on habitats in the analysis]] \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, and climate\citep{}.
+The latter
 variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
-climate is more variable at high latitudes \citep{}. These variables affect both the resources available and species' 
-metabolisms~\citep{Stegen2012}, and have been proposed as influences on the strength of 
+climate is more variable at high latitudes \citep{}.
+[[maybe climatic regimes?
+the issue is that there really are not a lot of studies that look at these things.....]] These variables affect both the resources available and species'
+metabolisms~\citep{Stegen2012}, and have been proposed as determinants of the strength of 
 interspecific interactions~\citep{Marquis2005,Schemske2009}. 
-By shaping interactions between species, latitudinal gradients may also shape food-web structure.
-Indeed, these latitudinal environmental gradients have been put forward as potential driverd for the 
+By modulating interactions between species, latitudinal gradients may also shape food-web structure.
+Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
 latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,,}.
@@
 turn should evolve smaller niches \citep{Vazquez2004}. These narrow niches should therefore allow more species to 
-coexist in the tropics than can at higher latitudes. Alternatively, higher productivity of the tropics \citep{Brown2004}
+coexist in the tropics than at higher latitudes. Alternatively, higher productivity of the tropics \citep{Brown2004}
 may result in a broader niche space \citep{Davies2007} which could also allow greater diversification even if niche 
@@
 If decreased seasonality or higher productivity is the cause of higher species-richness in the tropics, then 
-there should be other effects of latitude on food-web structure. Attempts to unravel the effects, however,
-are complicated by known effects of species richness on many other network properties~\citep{Riede2010}. In particular,
+there should be other effects of latitudinal gradients on food-web structure. Attempts to unravel these effects, however,
+are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}[[Check that I don't say that richness causes structural effects elsewhere]].
+In particular,
 narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,
@@
 of the dataset. As the version of the dataset used did not qualitatively change the results, we present only
-the results for the original webs in the main text. In each case, we counted the number of species ($S$) and 
+the results for the original webs in the main text.
+[[so what does this suggest?
+i find that in methods when making these statements it helps to go the step beyond and try and infer why trophic species/SR yielded similar results]] In each case, we counted the number of species ($S$) and
 links in each web and used these to calculate the mean number of links per species ($Z$), mean generality 
@@
 ~\citep{Davies2007}. In contrast, scaling in of lake, estuarine, and stream was generally stronger
-towards the poles. This means that species in tropical communities gain fewer additional feeding links
+towards the poles. [[Sentence structure in following?]] This means that species in tropical communities gain fewer additional feeding links
 per additional species in the web, supporting the hypothesis that greater stability in the tropics
@@
 \label{scalingfig}
-\includegraphics[width=.9\textwidth]{Figures/scaling_with_S_grey.eps}
+\includegraphics[width=.9\textwidth]{Figures/nonts_scaling_with_S_grey.eps}
 \caption{Relationships between species richness and mean links per species, mean generality, and mean 

### 2015-03-20 code/TL_latplots.py
Corrected file printing code, made by_TL figures for non-TS webs.

@@ -1,0 +1,293 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+# Think I want plots of the raw data (S, LS, G, V vs. lat) with slope lines
+# Plus predictions for LS, G, V vs S (with corrected obs.)
+
+def datareader(rawdatafile):
+  points={'S':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
+  'LS':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
+  'Gen':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},  
+  'Vul':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
+  'B':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
+  'I':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
+  'T':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]}
+  }
+
+  f=open(rawdatafile,'r')
+  for line in f:
+    if line.split()[0]!='Web':
+      Latitude=float(line.split('\t')[6])
+      Species=int(line.split('\t')[7])
+      LS=float(line.split('\t')[10])
+      G=float(line.split('\t')[12])
+      V=float(line.split('\t')[14])
+      ecotype=line.split('\t')[1]
+      ecotype=ecotype.capitalize()
+      B=float(line.split('\t')[-4])
+      I=float(line.split('\t')[-2])
+      T=float(line.split('\t')[-1])
+
+      points['S'][ecotype].append((Latitude,Species))
+      points['LS'][ecotype].append((Latitude,LS))
[…]

### 2015-03-20 code/TL_scaleplots.py

@@ -1,0 +1,259 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+# Think I want plots of the raw data (S, LS, G, V vs. lat) with slope lines
+# Plus predictions for LS, G, V vs S (with corrected obs.)
+
+from TL_latplots import datareader
+
+def fixed_reader(coefffile):
+  fixed_effects={}
+  f=open(coefffile,'r')
+  for line in f:
+    if line.split('\t')[0]!='"Estimate"':
+      name=line.split('\t')[0][1:-1]
+      beta=float(line.split('\t')[1])
+      fixed_effects[name]=beta
+  f.close()
+  return fixed_effects
+
+def heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat):
+  # Would probably be more helpful to do a heatmap of observed latitudes.
+  obs={'Lake':{},
+              'Stream':{},
+              'Marine':{},
+              'Terrestrial':{},
+              'Estuary':{}}
+  fixed_effects=fixed
+  f=open(rawdatafile,'r')
+  for line in f:
+    if line.split()[0]!='Web':
+      Latitude=float(line.split('\t')[6])
+      S=int(line.split('\t')[7])
+      LS=float(line.split('\t')[10])
+      L=LS
+      G=float(line.split('\t')[12])
+      Gen=G
+      V=float(line.split('\t')[14])
+      Vul=V
+      ecotype=line.split('\t')[1]
+      ecotype=ecotype.capitalize()
+      B=float(line.split('\t')[-4])
+      I=float(line.split('\t')[-2])
+      T=float(line.split('\t')[-1])
+      if Bformat=='numbers':
+        B=B*S
+        I=I*S
+        T=T*S
[…]

### 2015-03-20 code/byTL_Models.R

@@ -11,7 +11,10 @@ library(MuMIn)
 ##############################################################################################
 
 infile='../non_TS/summary-properties.tsv'
-format='proportions'
+# format='proportions'
+# format='numbers'
+
+for(format in c('proportions','numbers')){
 power_analysis=FALSE
 # For proportions and numbers, everything is log-normal.
 
@@ -66,7 +69,11 @@ power_analysis=FALSE
 
   source('recreate_with_subset.R')
 
-  if(format=='proportion'){
+  if(infile=='../mod_data/summary-properties.tsv'){
+    outdir='../mod_data/'  } else {
+      outdir='../non_TS/'     }
+
+  if(format=='proportions'){
     source('property_models_proportions.R')
     save.image(file=paste(outdir,'proportion_Models.RData',sep=''))
 
@@ -91,30 +98,32 @@ power_analysis=FALSE
   # Maybe 3 levels of latitude.
   # Range is 0 - 78 degrees.
   # 0, 45, 75 == equatorial, temperate, arctic
-  newdata=matrix(nrow=200*3*5*3,ncol=7)
+  newdata=matrix(nrow=500*3*5,ncol=7)
   k=1
   for(j in c("Lake","Marine","Stream","Terr","Other")){
     for(latitude in c(0,30,60)){
-      for(proportion in c(0.01,0.5,0.8)){
-        for(i in 1:200){
-        newdata[k,1]=i
-        newdata[k,2]=latitude
+        for(i in 1:500){
+        # newdata[k,1]=i
+        newdata[k,1]=latitude
+        newdata[k,2]=0
         newdata[k,3]=0
         newdata[k,4]=0
         newdata[k,5]=0
-        newdata[k,6]=0
         if(j=="Lake"){
-          newdata[k,3]=1 }
+          newdata[k,2]=1 }
         if(j=="Marine"){
-          newdata[k,4]=1 }
+          newdata[k,3]=1 }
         if(j=="Stream"){
-          newdata[k,5]=1 }
+          newdata[k,4]=1 }
         if(j=="Terr"){
-          newdata[k,6]=1 }
-        newdata[k,7]=proportion
+          newdata[k,5]=1 }
+        newdata[k,6]=i/500
+        newdata[k,7]=(i/500)*200
+
+        proportion
         k=k+1
-  }}}}
[…]

### 2015-03-20 code/recreate_with_subset.R

@@ -70,9 +70,9 @@
   gld=dredge(Gen_latdirect_full,rank=AIC)
   vld=dredge(Vul_latdirect_full,rank=AIC)
 
-  Sp_latdirect=(with(data,lm(Species~Stream),na.action=na.fail))
-  LS_latdirect=(with(data,lm(LS~1),na.action=na.fail))
-  Gen_latdirect=(with(data,lm(Gen~Terr+Lake),na.action=na.fail))
-  Vul_latdirect=(with(data,lm(Vul~1),na.action=na.fail))
+  Sp_latdirect=(with(data,lm(Species~Stream*Latitude+Lake+Marine),na.action=na.fail))
+  LS_latdirect=(with(data,lm(LS~Stream*Latitude+Marine),na.action=na.fail))
+  Gen_latdirect=(with(data,lm(Gen~Marine+Stream),na.action=na.fail))
+  Vul_latdirect=(with(data,lm(Vul~Latitude*Stream+Marine),na.action=na.fail))
 
  

### 2015-03-20 manuscript/latitudepaper.tex
Brief note on scaling of TL's with lat.
Starting to rough out results.

@@
 \vspace{0.4 in}
+
+[[Breaking things down by TL:
+
+  Using proportions in main text following Riede et. al.
+
+  With the subset of webs that actually have >0 BIT, there is a relationship between S, Gen, Vul, B, and T and Lat.
+Looks like this might be driven by outliers though...
+so gotta test that but might get to ignore things again.
+
+]]
 
@@
 
-For relationships of $Z$, $G$, and $V$ to $S$, equation~\ref{LogLog} had a lower AIC than the corresponding
-equation~\ref{Power}. This indicates that the data support an assumption of multiplicative log-normal
-error better than an assumption of additive normal error. That is, [[but what does it mean?]] . 
-We therefore used logarithmic-form models when assessing the effect of latitude on scaling relationships 
-with $S$.
+For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{LogLog} had a
+lower AIC than the corresponding equation~\ref{Power}. This indicates that the
+data support an assumption of multiplicative log-normal error better than an
+assumption of additive normal error. That is, models where $\epsilon$ is
+modelled as an exponent to a multiplicative term (that is, an additive term on
+the logarithmic scale) provide a better description of the data than models
+where $\epsiolon$ is modelled as an additive term on the arithmetic scale
+[[That's what this means... not sure if explaining it actually adds anything
+though]] .  We therefore used logarithmic-form models when assessing the
+effect of latitude on scaling relationships  with $S$.
 
@@
 ($p$\textless0.001), with the average species being preyed upon by 3.53 predators ($p$\textless0.001).
+
+Considering only the subset of webs with at least one basal resource,
+intermediate consumer, and top predator present, $S$, $Z$, and $V$ decreased with
+latitude in stream webs but did not vary with latitude in other ecosystem types.
+However, the relationships with latitude in stream webs [[Are they actually due to outliers?]]
+The proportion of top predators in a food web decreased with increasing latitude in lake and
+stream webs, while the proportion of basal resources increased with latitude in stream webs
+[[Are these robust to outliers?]]
 
@@
 other ecosystem types ($\beta_{Latitude}$=-0.001, $p$=0.199).
+
+\subsection*{Effect of Latitude on Scaling with B, I, and T}
+
+As with scaling relationships with $S$, the effect of latitude on scaling relationships
+with the proportions of basal resources, intermediate consumers, and top predators
+varied across ecosystem types. Scaling of $Z$ with $B$ was stronger towards the equator in terrestrial
+ecosystems, stronger towards the pole in lake, stream, and estuarine ecosystems, and did not vary
+with latitude in Mairne ecosystems. Scaling of $Z$ with $I$ was not affected by latitude in any
+ecosystem type, and scaling of $Z$ with $T$ was stronger towards the equator in stream and terrestrial
+ecosystems but weaker towards the equator in all other ecosystem types. The differences in scaling
+relationships over latitude were most dramatic in stream ecosystems.
+
+Similar to the patterns observed for $Z$, scaling of $G$ with $B$ was stronger towards the poles
+in stream, lake, and estuarine webs while marine and terrestrial webs showed very weak changes
+in scaling relationships over latitude. Scaling of $G$ with $I$ was stronger towards the poles in stream
+webs, but there was little effect of changing latitude on the scaling of $G$ with $I$ in other ecosystem
+types. Scaling of $G$ with $T$ did not vary with latitude.
 

### 2015-03-23 manuscript/latitudepaper.tex
Updated results for by_TL models

--- 2015-03-04 manuscript/latitudepaper.tex
@@
 given, obtained estimated coordinates using Google Earth \citep{GoogleEarth}.
+We then divided the species in each web into basal resources (those species with
+consumers but no prey), top predators (those species with prey but no predators),
+and intermediate consumers (species with both predators and prey, including cannibalistic
+species). For our future analyses, we considered only those webs with at least one basal
+resource, one intermediate consumer, and one top predator. This reduced our dataset to
+163 food webs.
 
@@
 
-For relationships of $Z$, $G$, and $V$ to $S$, equation~\ref{LogLog} had a lower AIC than the corresponding
-equation~\ref{Power}. This indicates that the data support an assumption of multiplicative log-normal
-error better than an assumption of additive normal error. That is, [[but what does it mean?]] . 
-We therefore used logarithmic-form models when assessing the effect of latitude on scaling relationships 
-with $S$.
+For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{LogLog} had a
+lower AIC than the corresponding equation~\ref{Power}. This indicates that the
+data support an assumption of multiplicative log-normal error better than an
+assumption of additive normal error. That is, models where $\epsilon$ is
+modelled as an exponent to a multiplicative term (that is, an additive term on
+the logarithmic scale) provide a better description of the data than models
+where $\epsilon$ is modelled as an additive term on the arithmetic scale
+[[That's what this means... not sure if explaining it actually adds anything
+though]] .  We therefore used logarithmic-form models when assessing the
+effect of latitude on scaling relationships  with $S$.
 
-Contrary to the expected latitudinal gradient, the best-fit version of equation~\ref{Latfull} for $S$
-did not include a term for latitude or any of its interactions with ecosystem type. Species richness was
-higher for stream ecosystems ($\alpha_{2:Stream}$=22.4, $p$\textless0.001) than other ecosystem types. 
-Similarly, the best-fit version of equation~\ref{Latfull} for $G$ did not include 
-any terms for latitude or interactions between latitude and ecosystem type. $G$ was lower in terrestrial
-and lake food webs than in other ecosystem types ($\alpha_{2:Terrestrial}$=-3.77, $p$\textless0.001 and 
-$\alpha_{2:Lake}$=-1.98, $p$=0.044). The best-fit models for $Z$ and $V$ did not include any terms for
-latitude, ecosystem type, or their interactions.
-the best-fit version of equation~\ref{Latfull} for $Z$ did not include a term for latitude,
-ecosystem type, or any of their interactions. Food webs tended to contain about 3.53 links per species
-($p$\textless0.001), with the average species being preyed upon by 3.53 predators ($p$\textless0.001).
+Contrary to the expected latitudinal gradient, the best-fit version of
+equation~\ref{Latfull} for $S$ included a signficant effect of latitude on $S$
+in stream webs only ($\alpha_{Latitude:Stream}$=-1.69, $p$=0.007).  This
+relationship was robust to the removal of three outliers (post-removal
+$\alpha_{Latitude:Stream}$=-1.17, $p$=0.038). The best-fit versions of
+equation~\ref{Latfull} for $Z$ and $V$ also included relatioships with
+latitude in stream webs ($\alpha_{Latitude:Stream}$=-0.179, $p$=0.007 and
+$\alpha_{Latitude:Stream}$=-0.179, $p$=0.007, respectively). However, after
+the removal of three outlying stream webs with very high $Z$ and $V$ (two of
+which also had unusually high $S$) these relationships were no longer
+significant ($\alpha_{Latitude:Stream}$=-0-0.046, $p$=0.373 and
+$\alpha_{Latitude:Stream}$=-0.046, $p$=0.373, respectively). Marine food webs
+had lower $S$, $Z$, $G$, and $V$ than all other web types (post-removal
+$\alpha_{Marine}$=-29.5, $p$\textless0.001, $\alpha_{Marine}$=-1.46,
+$p$=0.035, $\alpha_{Marine}$=-1.74, $p$=0.0612, and $\alpha_{Marine}$=-1.46,
+$p$=0.035, respectively) while stream food webs had higher $G$ than webs from
+other ecosystem types (post-removal $\alpha_{Stream}$=3.51,
+$p$\textless0.001).
 
-\subsection*{Effect of Latitude on Scaling with S}
+As with $S$, $B$ increased slightly with latitude ($\alpha_{Latitude}$=0.001, $p$=0.139). Unlike with $S$, the scaling 
+relationship was stronger in stream food webs ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001). 
+Scaling of $I$ with latitude did not vary with latitude or across
+ecosystem types. 
+As with $S$ and $B$, scaling of $T$ increased slightly with 
+latitude ($\alpha_{Latitude}$=0.001, $p$=0.136). As with $S$,
+this trend was reversed in stream food webs ($\alpha_{Latitude:Stream}$=-0.006, $p$=0.030) and was also reversed in 
+lake food webs ($\alpha_{Latitude:Lake}$=-0.006, $p$=0.001).
+All of the above trends were robust to the removal of outliers.
+
+\subsection*{Effect of Latitude on Scaling with S, B, I, and T}
 
 The effect of latitude on scaling relationships varied across ecosystem types.
-Overall, specialization in marine and terrestrial food webs increased towards the poles, 
-while specialization in lake food webs increased towards the equator (Fig.~\ref{scalinfig}). 
-In estuarine and stream food webs, there was a great deal of variation, with links per species
-and vulnerability increasing towards the poles and generality increasing towards the equator.
-More specifically, the scaling of mean links per species with species richness increased with
-increasing latitude ($\beta_{Latitude}$=0.004, $p$\textless0.001; Table~\ref{Bestfits}). This
-increase, however, was reversed for marine and terrestrial food webs
-($\beta_{Latitude:Marine}$=-0.005, $p$=0.007 and
-$\beta_{Latitude:Terrestrial}$=-0.005, $p$=0.001). Scaling of mean vulnerability with
-species richness showed the same pattern ($\beta_{Latitude}$=0.004, $p$\textless0.001;
-$\beta_{Latitude:Marine}$=-0.005, $p$=0.007; and $\beta_{Latitude:Terrestrial}$=-0.005, $p$=0.002).
-In contrast, scaling of mean generality with species richnesss increased with latitude 
-for lake food webs ($\beta_{Latitude:Lake}$=0.006, $p$=0.002) but did not vary with latitude for
-other ecosystem types ($\beta_{Latitude}$=-0.001, $p$=0.199).
+Specialization in lake food webs decreased towards the poles [[LS, Gen, Vul
+increased]] (Fig.~\ref{}), while in stream food webs $G$ increased towards the
+poles but $Z$ and $V$ were unaffected.  These trends were robust to the
+removal of outliers. [[Scaling of BIT with latitude?]]
+
+[[Makes more sense to go property by property, do BIT with S].]
+
+More specifically, the scaling of $V$ with $S$ was slightly stronger towards
+the equator in estuarine, marine, stream, and terrestrial food webs
+($\alpha_{Latitude}$=-0.001, $p$=0.267) but stronger towards the poles in
+stream food webs ($\alpha_{Latitude:Lake}$=0.005, $p$=0.008; Fig.~\ref{}).
+This scaling relationship was not consistent across different trophic levels.
+Scaling of $V$ with the proportion of basal resources was  stronger towards
+the poles in estuarine, lake, and stream food webs
+($\alpha_{Latitude}$=-0.007, $p$=0.006),  stronger towards the equator in
+terrestrial food webs ($\alpha_{Latitude:Terrestrial}$=0.013, $p$=0.002), and
+nearly neutral in marine food webs ($\alpha_{Latitude:Marine}$=0.009,
+$p$=0.047).  Scaling of $V$ with the proportion of intermediate consumers did
+not vary across latitude for any ecosystem type.  Scaling was weaker in lake
+and stream ecosystems ($\alpha_{Lake}$=-0.170, $p$=0.019 and
+$\alpha_{Stream}$=-0.430, $p$\textless0.001, respectively) than in other
+ecosystem types. Scaling of $V$ with the proportion of top predators generally
+showed a similar pattern to scaling of $V$ with the proportion of basal
+resources. Scaling was slightly stronger towards the equator for lake, marine,
+and estuarine food webs ($\alpha_{Latitude}$=-0.001, $p$=0.52) but stronger
+towards the poles for terrestrial and stream food webs
+($\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067;
+$\alpha_{Latitude:Stream}$=0.015, $p$\textless0.001).
+
+The scaling of $G$ with $S$ folowed a somewhat similar pattern to the scaling
+of $Z$ with $S$.  Scaling was slightly stronger towards the equator in
+estuarine, marine, and terrestrial food webs ($\alpha_{Latitude}$=-0.001,
+$p$=0.363) but stronger towards the poles in lake and stream food webs
+($\alpha_{Latitude:Lake}$=0.005, $p$=0.002 and
+$\alpha_{Latitude:Stream}$=0.007, $p$=0.002).  The scaling of $G$ with the
+proportion of basal resources was stronger towards the poles in estuarine,
+stream, and lake food webs ($\alpha_{Latitude}$=-0.009, $p$=0.002) but this
+trend was reversed for terrestrial and marine webs
+($\alpha_{Latitude:Marine}$=0.011, $p$=0.028;
+$\alpha_{Latitude:Terrestrial}$=0.015, $p$=0.001). Similarly, the scaling of
+$G$ with the proportion of intermediate consumers was stronger towards the
+equator in [[The picture doesn't match the betas... maybe because of - scaling
+with latitude and with ecosystem type?]] Scaling of $G$ with the proportion of
+top predators did not vary across latitude. Scaling was strongest in stream
+ecosystems ($\alpha_{Stream}$=-0.344, $p$\textless0.001) and weakest in marine
+food webs ($\alpha_{Marine}$=0.170, $p$=0.008).
+
+Scaling of $V$ with $S$ was slightly stronger towards the equator
+($\alpha_{Latitude}$=-0.001, $p$=0.267; Fig.~\ref{}) except in lake food webs
+where scaling was stronger towards the poles ($\alpha_{Latitude:Lake}$=0.005,
+$p$=0.008). When scaling was broken up by trophic level, however, lake food
+webs were not so exceptional. Scaling of $V$ with $B$ was stronger towards the
+poles in estuarine, lake and stream food webs ($\alpha_{Latitude}$=-0.007,
+$p$=0.006). This trend was reversed for marine and terrestrial food webs
+($\alpha_{Latitude:Marine}$=0.009, $p$=0.047;
+$\alpha_{Latitude:Terrestrial}$=0.013, $p$=0.002). Scaling of $V$ with $I$ was
+not affected by latitude in any ecosystem type.  Scaling of $V$ with $T$ was
+slightly stronger towards the equator in estuarine, marine, and lake food webs
+($\alpha_{Latitude}$=-0.001, $p$=0.521) but stronger towards the equator in
+stream and terrestrial food webs ($\alpha_{Latitude:Stream}$=0.015,
+$p$\textless0.001; $\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067).
 

### 2015-03-24 manuscript/latitudepaper.tex
Making results more readable

@@
 Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
-Specifically,~\ref{Power} implies a normally-distributed, additive error and~\ref{LogLog} a lognormal,
+Specifically,~\ref{Power} implies a normally-distributed, additive error and~\ref{Loglog} a lognormal,
 multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
@@
 identified using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. The best-fitting model
-was then determined to be the model with the fewest terms where $\Delta$AIC<2. Where there were several
-models with the fewest terms where $\Delta$AIC<2, the model with the lowest AIC in this set was chosen as
+was then determined to be the model with the fewest terms where $\Delta$AIC\textless2. Where there were several
+models with the fewest terms where $\Delta$AIC\textless2, the model with the lowest AIC in this set was chosen as
 the best-fitting model. The best-fitting model was then fit using R~\citep{R} function lm from package stats~\citep{stats}.
@@
 
+\section*{Scaling by Trophic Levels}
+
+We were also interested in the ways that scaling relationships with $S$ might
+be affected by changes to the distribution of species among trophic levels. To
+that end, we repeated all of the above analyses replacing species richness by
+proportion of basal resources $B$, proportion of intermediate consumers $I$,
+and  proportion of top predators $T$ in turn. All model fitting and model
+simplification procedures were identical to those described for species-
+richness.
+
 \section*{Results}
@@
 
-For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{LogLog} had a
+  For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{Loglog} had a
   lower AIC than the corresponding equation~\ref{Power}. This indicates that the
@@
   significant ($\alpha_{Latitude:Stream}$=-0-0.046, $p$=0.373 and
-$\alpha_{Latitude:Stream}$=-0.046, $p$=0.373, respectively). Marine food webs
+  $\alpha_{Latitude:Stream}$=-0.046, $p$=0.373, respectively). The best-fit
+  version of equation~\ref{Latfull} for $G$ did not include any effect of
+  latitude in any ecosystem type. Marine food webs
   had lower $S$, $Z$, $G$, and $V$ than all other web types (post-removal
@@
   other ecosystem types (post-removal $\alpha_{Stream}$=3.51,
-$p$\textless0.001).
+  $p$\textless0.001) [[Check streams in $V$, $Z$ for post-removal models]].
 
-As with $S$, $B$ increased slightly with latitude ($\alpha_{Latitude}$=0.001, $p$=0.139). Unlike with $S$, the scaling 
-relationship was stronger in stream food webs ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001). 
-Scaling of $I$ with latitude did not vary with latitude or across
-ecosystem types. 
-As with $S$ and $B$, scaling of $T$ increased slightly with 
-latitude ($\alpha_{Latitude}$=0.001, $p$=0.136). As with $S$,
-this trend was reversed in stream food webs ($\alpha_{Latitude:Stream}$=-0.006, $p$=0.030) and was also reversed in 
-lake food webs ($\alpha_{Latitude:Lake}$=-0.006, $p$=0.001).
-All of the above trends were robust to the removal of outliers.
+  The relationships between $B$, $I$, and $T$ with latitude were broadly similar
+  to the relationship between $S$ and latitude. $B$ did not vary significantly
+  over latitude except in stream food webs where $B$ increased towards the poles
+  ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001), while $I$ did not vary
+  significantly with latitude in any ecosystem type. Like $S$, $T$ decreased
+  towards the poles in stream food webs ($\alpha_{Latitude}$=0.001, $p$=0.136;
+  $\alpha_{Latitude:Stream}$=-0.006, $p$=0.030) and also decreased towards the
+  poles in lake webs ($\alpha_{Latitude:Lake}$=-0.006, $p$=0.001
+  All of these trends were robust to the removal of outliers.
 
@@
 
-The effect of latitude on scaling relationships varied across ecosystem types.
-Specialization in lake food webs decreased towards the poles [[LS, Gen, Vul
-increased]] (Fig.~\ref{}), while in stream food webs $G$ increased towards the
-poles but $Z$ and $V$ were unaffected.  These trends were robust to the
-removal of outliers. [[Scaling of BIT with latitude?]]
+The effect of latitude on scaling relationships with $S$ varied across
+ecosystem types. The strength of scaling decreased towards the poles for $Z$,
+$G$, and $V$ in lake food webs, while in stream food webs $G$ increased
+towards the poles but $Z$ and $V$ were unaffected (Figs.~\ref{LS,Gen,Vul}).
+In all other ecosystem types, the strength of scaling of $Z$, $G$, and $V$
+with $S$ did not vary over latitude. These trends were all robust to the
+removal of outliers. When scaling relationships were broken down across
+trophic levels, however, the situation was more complex. Scaling relationships
+with $B$, $I$, and $T$ generally did not follow the pattern set by scaling
+relationships with $S$.
 
-[[Makes more sense to go property by property, do BIT with S].]
+[[Need to find a way to express the total effect of all the alphas for a given ecotype...]]
+[[Perhaps with a nice table to refer to?]]
 
-More specifically, the scaling of $V$ with $S$ was slightly stronger towards
-the equator in estuarine, marine, stream, and terrestrial food webs
-($\alpha_{Latitude}$=-0.001, $p$=0.267) but stronger towards the poles in
-stream food webs ($\alpha_{Latitude:Lake}$=0.005, $p$=0.008; Fig.~\ref{}).
-This scaling relationship was not consistent across different trophic levels.
-Scaling of $V$ with the proportion of basal resources was  stronger towards
-the poles in estuarine, lake, and stream food webs
-($\alpha_{Latitude}$=-0.007, $p$=0.006),  stronger towards the equator in
-terrestrial food webs ($\alpha_{Latitude:Terrestrial}$=0.013, $p$=0.002), and
-nearly neutral in marine food webs ($\alpha_{Latitude:Marine}$=0.009,
-$p$=0.047).  Scaling of $V$ with the proportion of intermediate consumers did
-not vary across latitude for any ecosystem type.  Scaling was weaker in lake
-and stream ecosystems ($\alpha_{Lake}$=-0.170, $p$=0.019 and
-$\alpha_{Stream}$=-0.430, $p$\textless0.001, respectively) than in other
-ecosystem types. Scaling of $V$ with the proportion of top predators generally
-showed a similar pattern to scaling of $V$ with the proportion of basal
-resources. Scaling was slightly stronger towards the equator for lake, marine,
-and estuarine food webs ($\alpha_{Latitude}$=-0.001, $p$=0.52) but stronger
-towards the poles for terrestrial and stream food webs
-($\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067;
-$\alpha_{Latitude:Stream}$=0.015, $p$\textless0.001).
+[[redo the other paragraphs something like this]]
+For example, while $V$ increased with $S$ across all ecosystem types, $V$
+tended to decrease with increasing $B$ and $I$ (Fig.~\ref{LS}). The scaling of
+$V$ with $B$ was stronger towards the poles in estuarine, lake, and stream
+food webs ($\alpha_{Latitude}$=-0.007, $p$=0.006), stronger towards the
+equator in terrestrial webs ($\alpha_{Latitude:Terrestrial}$=0.013,
+$p$=0.002), and weakly related to latitude in marine webs
+($\alpha_{Latitude:Marine}$=0.009, $p$=0.047). Scaling of $V$ with $T$ was
+also stronger towards the equator in terrestrial webs
+($\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067,
+$\alpha_{Terrestrial}$=-0.093, $p$0.526), while scaling of $V$ with $T$ did
+not vary significantly over latitude in estuarine, marine or lake webs
+($\alpha_{Latitude}$=-0.001, $p$=0.52). Contrary to the scaling of $V$ with
+$B$, scaling of $V$ with $T$ in streams was stronger towards the equator
+($\alpha_{Latitude:Stream}$=0.015, $p$\textless0.001,
+$\alpha_{Stream}$=-0.822,$p$\textless0.001).
 
@@
 
-\section*{Tables}
+% \section*{Tables}
 
-\begin{table}[!h]
-\caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude.
+% \begin{table}[!h]
+% \caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude.
 Note that none
-of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. Each `NA' indicates a term that was not included in the corresponding best-fit model.}
-\label{Latlms}
-\begin{tabular}{l | l l  l l  l l  l l}
+% of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. Each `NA' indicates a term that was not included in the corresponding best-fit model.}
+% \label{Latlms}
+% \begin{tabular}{l | l l  l l  l l  l l}
 
-\hline
-\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
-& $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
-\hline
-Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
-Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
-Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
-Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
-\hline
-\end{tabular}
-\end{table}
+% \hline
+% \multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
+% & $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
+% \hline
+% Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
+% Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
+% Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
+% Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
+% \hline
+% \end{tabular}
+% \end{table}
 
-\begin{table}[!h]
-\caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude in trophic-species versions of food webs.
+% \begin{table}[!h]
+% \caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude in trophic-species versions of food webs.
 Note that none
-of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. `NA' a term that was not included in the corresponding best-fit model.}
-\label{Latlms}
-\begin{tabular}{l | l l  l l  l l  l l}
+% of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. `NA' a term that was not included in the corresponding best-fit model.}
+% \label{Latlms}
+% \begin{tabular}{l | l l  l l  l l  l l}
 
-\hline
-\multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
-& $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
-\hline
-Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
-Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
-Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
-Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
-\hline
-\end{tabular}
-\end{table}
+% \hline
+% \multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
+% & $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
+% \hline
+% Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
+% Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
+% Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
+% Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
+% \hline
+% \end{tabular}
+% \end{table}
 
-\begin{table}[!h]
-\caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness.
+% \begin{table}[!h]
+% \caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness.
 Each `NA' indicates a term that was not included in the corresponding best-fit model.
@@
 }
-\label{Bestfits}
-\begin{tabular}{l | l l  l l  l l }
-Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
-                & \multicolumn{2}{c}{Vulnerability}\\
-                & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
-\hline
-Intercept               &-0.453 & \textless0.001 & -0.249 & \textless0.001 & -0.453 & \textless0.001 \\
-log(species)            & 0.419 & \textless0.001 &  0.663 & \textless0.001 &  0.419 & \textless0.001 \\
-log(species):Lake       & 0.119 & \textless0.001 & -0.185 & 0.016          &  0.119 & \textless0.001 \\
-log(species):Marine     & 0.255 & \textless0.001 &  0.090 & 0.002          &  0.255 & \textless0.001 \\
-log(species):Terrestrial& 0.207 & 0.002          & -0.122 & \textless0.001 &  0.207 & 0.002 \\
-log(species):Latitude   & 0.004 & \textless0.001 & -0.001 & 0.199          &  0.003 & \textless0.001 \\
-log(species):Latitude:Marine&-0.004 & 0.007      &  NA    &  NA            & -0.005 & 0.007 \\
-log(species):Latitude:Terrestrial&-0.005 & 0.002 &  NA    &  NA            & -0.005 & 0.002 \\
-log(species):Latitude:Lake & NA & NA             &  0.006 & 0.002          &  NA    & NA    \\
-\hline
-$R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
-\hline
-\end{tabular}
-\end{table}
+% \label{Bestfits}
+% \begin{tabular}{l | l l  l l  l l }
+% Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
+%                 & \multicolumn{2}{c}{Vulnerability}\\
+%                 & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
+% \hline
+% Intercept               &-0.453 & \textless0.001 & -0.249 & \textless0.001 & -0.453 & \textless0.001 \\
+% log(species)            & 0.419 & \textless0.001 &  0.663 & \textless0.001 &  0.419 & \textless0.001 \\
+% log(species):Lake       & 0.119 & \textless0.001 & -0.185 & 0.016          &  0.119 & \textless0.001 \\
+% log(species):Marine     & 0.255 & \textless0.001 &  0.090 & 0.002          &  0.255 & \textless0.001 \\
+% log(species):Terrestrial& 0.207 & 0.002          & -0.122 & \textless0.001 &  0.207 & 0.002 \\
+% log(species):Latitude   & 0.004 & \textless0.001 & -0.001 & 0.199          &  0.003 & \textless0.001 \\
+% log(species):Latitude:Marine&-0.004 & 0.007      &  NA    &  NA            & -0.005 & 0.007 \\
+% log(species):Latitude:Terrestrial&-0.005 & 0.002 &  NA    &  NA            & -0.005 & 0.002 \\
+% log(species):Latitude:Lake & NA & NA             &  0.006 & 0.002          &  NA    & NA    \\
+% \hline
+% $R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
+% \hline
+% \end{tabular}
+% \end{table}
 
-\begin{table}[!h]
-\caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness.
+% \begin{table}[!h]
+% \caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness.
 Each `NA' indicates a term that was not included in the corresponding best-fit model.
@@
 }
-\label{Bestfits}
-\begin{tabular}{l | l l  l l  l l }
-Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
-                & \multicolumn{2}{c}{Vulnerability}\\
-                & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
-\hline
-Intercept               & -0.561 & \textless0.001 & -0.299 & \textless0.001 & -0.561 & \textless0.001 \\
-log(species)            &  0.733 & \textless0.001 &  0.622 & \textless0.001 &  0.733 & \textless0.001 \\
-log(species):Lake       & -0.118 & 0.047          & -0.115 & 0.078          & -0.118 & 0.047 \\
-log(species):Marine     &  0.051 & 0.040          &  0.120 & \textless0.001 &  0.051 & 0.040 \\
-log(species):Stream     & -0.161 & 0.014          & -0.057 & 0.421          & -0.161 & 0.014 \\
-log(species):Latitude   & -0.001 & 0.081          & -0.001 & 0.273          & -0.001 & 0.081 \\
-log(species):Lat:Lake   &  0.006 & \textless0.001 &  0.006 & \textless0.001 &  0.006 & \textless0.001 \\
-log(species):Lat:Stream &  0.004 & 0.018          &  0.003 & 0.059          &  0.004 & 0.018 \\
-\hline
-$R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
-\hline
-\end{tabular}
-\end{table}
+% \label{Bestfits}
+% \begin{tabular}{l | l l  l l  l l }
+% Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
+%                 & \multicolumn{2}{c}{Vulnerability}\\
+%                 & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
+% \hline
+% Intercept               & -0.561 & \textless0.001 & -0.299 & \textless0.001 & -0.561 & \textless0.001 \\
+% log(species)            &  0.733 & \textless0.001 &  0.622 & \textless0.001 &  0.733 & \textless0.001 \\
+% log(species):Lake       & -0.118 & 0.047          & -0.115 & 0.078          & -0.118 & 0.047 \\
+% log(species):Marine     &  0.051 & 0.040          &  0.120 & \textless0.001 &  0.051 & 0.040 \\
+% log(species):Stream     & -0.161 & 0.014          & -0.057 & 0.421          & -0.161 & 0.014 \\
+% log(species):Latitude   & -0.001 & 0.081          & -0.001 & 0.273          & -0.001 & 0.081 \\
+% log(species):Lat:Lake   &  0.006 & \textless0.001 &  0.006 & \textless0.001 &  0.006 & \textless0.001 \\
+% log(species):Lat:Stream &  0.004 & 0.018          &  0.003 & 0.059          &  0.004 & 0.018 \\
+% \hline
+% $R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
+% \hline
+% \end{tabular}
+% \end{table}
 
@@
 
+% \begin{figure}[!h]
+% \label{scalingfig}
+% \includegraphics[width=.9\textwidth]{Figures/nonts_scaling_with_S_grey.eps}
+% \caption{Relationships between species richness and mean links per species, mean generality, and mean 
+% vulnerability (N=259 food webs). Scaling of mean links per species and mean vulnerability with species 
+% richness strengthened with latitude for estuarine, stream, and lake food webs. This strengthening was
+% reversed for marine and terrestrial food webs. Scaling of mean generality with species richness 
+% strengthened with latitude for lake food webs, but did not significantly vary with latitude for other
+% ecosystem types (N=259 food webs). }
+% \end{figure}
+
 \begin{figure}[!h]
-\label{scalingfig}
-\includegraphics[width=.9\textwidth]{Figures/nonts_scaling_with_S_grey.eps}
-\caption{Relationships between species richness and mean links per species, mean generality, and mean 
-vulnerability (N=259 food webs). Scaling of mean links per species and mean vulnerability with species 
-richness strengthened with latitude for estuarine, stream, and lake food webs. This strengthening was
-reversed for marine and terrestrial food webs. Scaling of mean generality with species richness 
-strengthened with latitude for lake food webs, but did not significantly vary with latitude for other
-ecosystem types (N=259 food webs). }
+\label{props_v_lat}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/properties_vs_lat/proportions/nonts_propsvlat.eps}
+\caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability (N=163 food webs). }
+\end{figure}
+
+\begin{figure}[!h]
+\label{TLs_v_lat}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/properties_vs_lat/proportions/nonts_TLvlat.eps}
+\caption{Relationships between latitude and proportions of basal resources, intermediate consumers, and top predators (N=163 food webs). }
+\end{figure}
+
+\begin{figure}[!h]
+\label{LS}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/LS_nonts.eps}
+\caption{Relationships between mean links per species and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs).
+[[More details needed]]}
+\end{figure}
+
+\begin{figure}[!h]
+\label{Gen}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/Gen_nonts.eps}
+\caption{Relationships between mean generality (number of prey) and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs).
+[[More details needed]]}
+\end{figure}
+
+\begin{figure}[!h]
+\label{Vul}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/Vul_nonts.eps}
+\caption{Relationships between mean vulnerability (number of predators) and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs).
+[[More details needed]]}
 \end{figure}

### 2015-04-07 manuscript/latitudepaper.tex
Updated results, still need to apply betas

@@
 
-The effect of latitude on scaling relationships with $S$ varied across
-ecosystem types. The strength of scaling decreased towards the poles for $Z$,
-$G$, and $V$ in lake food webs, while in stream food webs $G$ increased
-towards the poles but $Z$ and $V$ were unaffected (Figs.~\ref{LS,Gen,Vul}).
-In all other ecosystem types, the strength of scaling of $Z$, $G$, and $V$
-with $S$ did not vary over latitude. These trends were all robust to the
-removal of outliers. When scaling relationships were broken down across
-trophic levels, however, the situation was more complex. Scaling relationships
-with $B$, $I$, and $T$ generally did not follow the pattern set by scaling
-relationships with $S$.
+$Z$, $G$, and $V$ all increased with increasing $S$ at all latitudes. The strength of
+this increase varied both over latitude and across ecosystem types. For $Z$,
+scaling was stronger towards the equator in estuarine, marine, stream, and
+terrestrial ecosystems (). In lake ecosystems, however, scaling was stronger
+toward the poles. $G$ and $V$ followed the same trends, except that scaling of $G$
+with $S$ was stronger towards the poles as in lakes ().
 
-[[Need to find a way to express the total effect of all the alphas for a given ecotype...]]
-[[Perhaps with a nice table to refer to?]]
+When considering the proportion of $S$ accounted for by different trophic
+levels, however, the scaling relationships with $Z$, $G$, and $V$ were more
+complex. While $Z$ increased with increasing $I$ as well as with increasing
+$S$, $Z$ tended to decrease with increasing $B$ and $T$. The decrease of $Z$
+with $B$ was stronger towards the poles in estuarine, lake, and stream webs
+(), varied little over latitude in marine webs (), and was stronger towards
+the poles in terrestrial webs (). The best-fitting model for the relationship
+of $Z$ and $I$ did not include any terms for variation in scaling across
+latitude for any ecosystem type. Similar to the scaling of $Z$ with $B$, the
+decrease in $Z$ with increasing $T$ was stronger towards the poles in
+estuarine, lake, and marine webs, although the influence of latitude was
+weaker than with $B$ (). Again like the relationship between $Z$ and $B$,
+scaling of $Z$ with $T$ was stronger towards the equator in terrestrial webs.
+Unlike in the relationship between $Z$ and $B$, however, scaling of $Z$ with
+$T$ was also stronger towards the equator in stream webs.
 
-[[redo the other paragraphs something like this]]
-For example, while $V$ increased with $S$ across all ecosystem types, $V$
-tended to decrease with increasing $B$ and $I$ (Fig.~\ref{LS}). The scaling of
-$V$ with $B$ was stronger towards the poles in estuarine, lake, and stream
-food webs ($\alpha_{Latitude}$=-0.007, $p$=0.006), stronger towards the
-equator in terrestrial webs ($\alpha_{Latitude:Terrestrial}$=0.013,
-$p$=0.002), and weakly related to latitude in marine webs
-($\alpha_{Latitude:Marine}$=0.009, $p$=0.047). Scaling of $V$ with $T$ was
-also stronger towards the equator in terrestrial webs
-($\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067,
-$\alpha_{Terrestrial}$=-0.093, $p$0.526), while scaling of $V$ with $T$ did
-not vary significantly over latitude in estuarine, marine or lake webs
-($\alpha_{Latitude}$=-0.001, $p$=0.52). Contrary to the scaling of $V$ with
-$B$, scaling of $V$ with $T$ in streams was stronger towards the equator
-($\alpha_{Latitude:Stream}$=0.015, $p$\textless0.001,
-$\alpha_{Stream}$=-0.822,$p$\textless0.001).
+As with $Z$, $G$ tended to decrease with increasing $B$ and $T$ and increase
+with increasing $I$. Once again, however, these trends varied with latitude
+and ecosystem type. The decline of G with increasing S was strongest at the
+poles in estaurine, lake, and marine ecosystems; in each ecosystem type $G$
+increased slightly with $B$ in equatorial webs. In marine webs $G$ increased
+slightly with $B$ at all latitudes and in terrestrial webs $G$ increased with
+$B$ in high-latitude webs but decreased slightly with $B$ at the equator. The
+strength of the increase in $G$ with $I$ varied little with latitude except in
+stream webs, where the increase was strongest towards the equator and $G$
+decreased with $I$ in arctic food webs. The best-fitting model for the scaling
+of $G$ with $T$ did not include any terrms for latitude in any ecosystem type.
 
-The scaling of $G$ with $S$ folowed a somewhat similar pattern to the scaling
-of $Z$ with $S$.  Scaling was slightly stronger towards the equator in
-estuarine, marine, and terrestrial food webs ($\alpha_{Latitude}$=-0.001,
-$p$=0.363) but stronger towards the poles in lake and stream food webs
-($\alpha_{Latitude:Lake}$=0.005, $p$=0.002 and
-$\alpha_{Latitude:Stream}$=0.007, $p$=0.002).  The scaling of $G$ with the
-proportion of basal resources was stronger towards the poles in estuarine,
-stream, and lake food webs ($\alpha_{Latitude}$=-0.009, $p$=0.002) but this
-trend was reversed for terrestrial and marine webs
-($\alpha_{Latitude:Marine}$=0.011, $p$=0.028;
-$\alpha_{Latitude:Terrestrial}$=0.015, $p$=0.001). Similarly, the scaling of
-$G$ with the proportion of intermediate consumers was stronger towards the
-equator in [[The picture doesn't match the betas... maybe because of - scaling
-with latitude and with ecosystem type?]] Scaling of $G$ with the proportion of
-top predators did not vary across latitude. Scaling was strongest in stream
-ecosystems ($\alpha_{Stream}$=-0.344, $p$\textless0.001) and weakest in marine
-food webs ($\alpha_{Marine}$=0.170, $p$=0.008).
-
-Scaling of $V$ with $S$ was slightly stronger towards the equator
-($\alpha_{Latitude}$=-0.001, $p$=0.267; Fig.~\ref{}) except in lake food webs
-where scaling was stronger towards the poles ($\alpha_{Latitude:Lake}$=0.005,
-$p$=0.008). When scaling was broken up by trophic level, however, lake food
-webs were not so exceptional. Scaling of $V$ with $B$ was stronger towards the
-poles in estuarine, lake and stream food webs ($\alpha_{Latitude}$=-0.007,
-$p$=0.006). This trend was reversed for marine and terrestrial food webs
-($\alpha_{Latitude:Marine}$=0.009, $p$=0.047;
-$\alpha_{Latitude:Terrestrial}$=0.013, $p$=0.002). Scaling of $V$ with $I$ was
-not affected by latitude in any ecosystem type.  Scaling of $V$ with $T$ was
-slightly stronger towards the equator in estuarine, marine, and lake food webs
-($\alpha_{Latitude}$=-0.001, $p$=0.521) but stronger towards the equator in
-stream and terrestrial food webs ($\alpha_{Latitude:Stream}$=0.015,
-$p$\textless0.001; $\alpha_{Latitude:Terrestrial}$=0.006, $p$=0.067).
+$V$ too generally decreased with increasing $B$ and $T$ while increasing with
+$I$. Similar to $G$, the decline of $V$ with increasing $B$ was strongest
+towards the poles in estuarine, lake, and stream webs, varied little with
+latitude in marine webs, and was strongest towards the equator in terrestrial
+food webs. As with $Z$, the best-fit model for the scaling of $V$ with $I$ did
+not include any terms for latitude in any ecosystem type. Scaling of $V$ with
+$T$ was also simmilar to the pattern for $Z$, with sharper decreases in $V$
+towards the poles in estuarine, lake, and marine webs and stronger towards the
+equator in terrestrial and stream webs.
 

### 2015-04-07 manuscript/latitudepaper.tex
A first stab at the discussion

@@
 overall latitudinal gradients in species richness, links per species, 
-generality, or vulnerability.
+generality, vulnerability, or the proportions of food webs accounted for by 
+basal resources, intermediate consumers, and top predators.
 
@@
 between species richness and other properties is not being driven by underlying variation in
-species richness, allowing us to more clearly assess effects of latitude on scaling.
+species richness, allowing us to more clearly assess effects of latitude on scaling with 
+species richness and proportions of species in different trophic levels.
 
-These effects varied strongly across ecosystem types. In marine and terrestrial food webs,
-scaling of links per species, generality, and vulnerability was not strongly affected by
-latitude. This is consistent with the idea that species' niche breadths do not vary systematically
-with temperature and productivity but that the niche space might be larger in species-rich communities
-~\citep{Davies2007}. In contrast, scaling in of lake, estuarine, and stream was generally stronger
-towards the poles. [[Sentence structure in following?]] This means that species in tropical communities gain fewer additional feeding links
-per additional species in the web, supporting the hypothesis that greater stability in the tropics
-leads to narrower niches~\citep{Brown2004} and a higher proportion of specialists~\citep{}. As food webs
-are generally aggregated in space and time, the greater increase in links in high latitude stream, 
-estuarine, and lake food webs might reflect prey switching as different food sources become
-available~\citep{}.
+Scaling of links per species, generality, and vulnerability with species
+richness varied strongly across ecosystem types. In estuarine, marine, and
+terrestrial food webs scaling of each property varied little with latitude.
+This is consistent with the idea that species' niche breadths do not vary
+systematically with temperature and productivity but that the niche space
+might be larger in species-rich communities~\citep{Davies2007}. In lake food
+webs, in contrast, scaling of each property was much stronger in high-latitude
+food webs. In stream food webs, scaling of links per species and vulnerability
+varied little over latitude while scaling of generality was stronger in high-
+latitude food webs. This means that species in trophical freshwater
+communities gain fewer additional feeding links per additional species in the
+web and is consistent with the hypothesis that greater stability in the
+tropics leads to narrower niches~\citep{Brown2004} and a higher proportion of
+specialists~\citep{}.
+
+In lake food webs, species in tropical food webs also gained fewer predators,
+and therefore fewer links overall. Conversely, for species in high-latitude
+food webs numbers of predators, prey, and links per species all increased
+rapidly with increasing species richness. This may reflect prey switching as
+different food sources become available in different seasons~\citep{}.
+Alternatively, the sharper increases in links per species, generality, and
+vulnerability at higher latitudes may be driven by the relationships between
+each property and the proportion of basal resources in these food webs.
+[[Except each property increases more with S and decreases more with B...]]
+
+Surprisingly species in high-latitude stream food webs, while gaining many
+additional prey species per additional species in the food web, did not
+receive any more predators or links than species in low-latitude streams. The
+limited influence of latitude on the scaling relationships of links per
+species and vulnerability may be because, for these properties, latitude had
+opposite effects on the scaling relationships with proportions of basal
+resources and top predators. When considering generality, however, only the
+proportion of basal resources varied significantly over latitude. [[Same
+problem as in lakes, the trends are opposite.]]
 
@@
 
-Our results were consistent with the latitude-niche breadth hypothesis, but only in certain ecosystem
-types. This suggests that different types of food webs respond differently to differences in climate
-driven by latitudinal gradients. [[A sentence or two explaining why this is important.]]
+% Our results were consistent with the latitude-niche breadth hypothesis, but only in certain ecosystem
+% types. This suggests that different types of food webs respond differently to differences in climate
+% driven by latitudinal gradients. [[A sentence or two explaining why this is important.]]
 

### 2015-04-09 manuscript/latitudepaper.tex
Updated first part of methods

@@
 
-[[Breaking things down by TL:
-
-  Using proportions in main text following Riede et. al.
-
-  With the subset of webs that actually have >0 BIT, there is a relationship between S, Gen, Vul, B, and T and Lat.
-Looks like this might be driven by outliers though...
-so gotta test that but might get to ignore things again.
-
-]]
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+[[Still need to check that new results hold for TS versions of webs.]]
 
@@
 
-We compiled a list of 263 empirical food webs from
+  We compiled a list of 163 empirical food webs from
   multiple sources (see Supplemental Information for web origins and selection
@@
   and intermediate consumers (species with both predators and prey, including cannibalistic
-species). For our future analyses, we considered only those webs with at least one basal
-resource, one intermediate consumer, and one top predator. This reduced our dataset to
-163 food webs.
+  species).
 
@@
   % interactions between them \citep{Dunne2013}. 
+  % As we were considering the log of proportions of basal resources, top predators, and intermediate consumers, each web used in our analysis had to have at least one species in each trophic group.
 
@@
   is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
-Many analyses of food-web structure reduce this variation by aggregating species with identical predator and prey
+  Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
   sets to form ``trophic species'' webs (e.g. ~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
@@
   species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
-of the dataset. As the version of the dataset used did not qualitatively change the results, we present only
+  of the dataset; in each case using the number of species ($S$) and 
+  links ($L$) in each web to calculate the mean number of links per species ($Z$), mean generality 
+  ($G$), and mean vulnerability ($V$) of the web. 
+  The version of the dataset used did not qualitatively change the results, suggesting that
+  the scaling relationships between species richness, other food-web properties, and latitude are very 
+  similar whether or not redundant species are included. For simplicity, we present only
   the results for the original webs in the main text.
-[[so what does this suggest?
-i find that in methods when making these statements it helps to go the step beyond and try and infer why trophic species/SR yielded similar results]] In each case, we counted the number of species ($S$) and
-links in each web and used these to calculate the mean number of links per species ($Z$), mean generality 
-($G$), and mean vulnerability ($V$) of each web.
 
@@
   To determine whether there were latitudinal gradients in food-web structure,
-we first examined simple linear relationships between latitude and $S$, $Z$, $G$, and $V$. 
+  we first examined simple linear relationships between latitude and each of $S$, $Z$, $G$, and $V$. 
   We fit models of the form
@@
   \label{Latfull}
-S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} 
+  S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} .,
   \end{equation}
 
-where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
-latitude (degrees north or south  regardless of direction), $E_{i}$ is the
-ecosystem type of network $i$ (comprising terms for stream, marine, lake, and terrestrial networks with estuarine
-networks being the intercept) and $\epsilon_{i}$ a residual error term. 
-We then simplified these maximal models. To do this, we calculated the AIC
-of the chosen maximal model, as well as the AIC's of a suite of candidate simplified models identified
-using R~\citep{R} function dredge from packages MuMIn~\citep{MuMIn}. Simplified models were obtained by
+  \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
+  latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
+  variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
+  marine, lake, and terrestrial networks with estuarine
+  networks providing the intercept) and $\epsilon_{i}$ a residual error term. 
+  We next calculated the AIC
+  of the maximal model, as well as the AIC's of a suite of candidate simplified models identified
+  using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
+  Simplified models were obtained by
   systematically removing all possible combinations of terms from the full model.
@@
   \label{Power}
-Z_{i}~\alpha S_{i}^{\beta}
+  Z_{i} \~ \alpha S_{i}^{\beta}
   \end{equation}
 
-which is often re-expreseed in logarithmic form
+  \noindent which is often re-expressed in logarithmic form
 
@@
   \label{Loglog}
-\log{Z_{i}} ~ \log{\alpha} + \beta\log{S_{i}}
+  \log{Z_{i}} \~ \log{\alpha} + \beta\log{S_{i}}
   \end{equation}
@@
   Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
-Specifically,~\ref{Power} implies a normally-distributed, additive error and~\ref{Loglog} a lognormal,
+  Specifically, equation~(\ref{Power}) implies a normally-distributed, additive error and equation~(\ref{Loglog}) a lognormal,
   multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
@@
 
-  For relationships of $Z$, $G$, $V$, $B$, $I$, and $T$ to $S$, equation~\ref{Loglog} had a
-  lower AIC than the corresponding equation~\ref{Power}. This indicates that the
+  When considering the relationships between $S$ and $Z$, $G$, $V$, $B$, $I$, and $T$,
+  equation~(\ref{Loglog}) had a
+  lower AIC than the corresponding equation~(\ref{Power}). This indicates that the
   data support an assumption of multiplicative log-normal error better than an
@@
   the logarithmic scale) provide a better description of the data than models
-  where $\epsilon$ is modelled as an additive term on the arithmetic scale
-  [[That's what this means... not sure if explaining it actually adds anything
-  though]] .  We therefore used logarithmic-form models when assessing the
+  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
+  We therefore used logarithmic-form models when assessing the
   effect of latitude on scaling relationships  with $S$.
@@
   Contrary to the expected latitudinal gradient, the best-fit version of
-  equation~\ref{Latfull} for $S$ included a signficant effect of latitude on $S$
+  equation~(\ref{Latfull}) for $S$ included a signficant effect of latitude on $S$
   in stream webs only ($\alpha_{Latitude:Stream}$=-1.69, $p$=0.007).  This
@@
   $\alpha_{Latitude:Stream}$=-1.17, $p$=0.038). The best-fit versions of
-  equation~\ref{Latfull} for $Z$ and $V$ also included relatioships with
+  equation~(\ref{Latfull}) for $Z$ and $V$ also included relationships with
   latitude in stream webs ($\alpha_{Latitude:Stream}$=-0.179, $p$=0.007 and
@@
   $\alpha_{Latitude:Stream}$=-0.046, $p$=0.373, respectively). The best-fit
-  version of equation~\ref{Latfull} for $G$ did not include any effect of
+  version of equation~(\ref{Latfull}) for $G$ did not include any effect of
   latitude in any ecosystem type. Marine food webs
@@
   other ecosystem types (post-removal $\alpha_{Stream}$=3.51,
-  $p$\textless0.001) [[Check streams in $V$, $Z$ for post-removal models]].
+  $p$\textless0.001).
 
@@
 this increase varied both over latitude and across ecosystem types. For $Z$,
-scaling was stronger towards the equator in estuarine, marine, stream, and
-terrestrial ecosystems (). In lake ecosystems, however, scaling was stronger
-toward the poles. $G$ and $V$ followed the same trends, except that scaling of $G$
-with $S$ was stronger towards the poles as in lakes ().
+scaling was stronger towards the equator except in lake ecosystems where scaling was stronger
+towards the poles (Fig.~\ref{LS}). $G$ and $V$ followed the same trends, except that scaling of $G$
+with $S$ was stronger towards the poles as in lakes (Figs.~\ref{Gen, Vul}).
 
@@
 
+   $B$ increased towards the poles ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001)
+   $T$ decreased towards the poles in stream food webs ($\alpha_{Latitude}$=0.001, $p$=0.136;
+  $\alpha_{Latitude:Stream}$=-0.006, $p$=0.030)
+
 In lake food webs, species in tropical food webs also gained fewer predators,
@@
 food webs numbers of predators, prey, and links per species all increased
-rapidly with increasing species richness. This may reflect prey switching as
+rapidly with increasing species richness.
+As there were proportionally fewer top predators in high-latitude lakes yet
+generality, vulnerability, and links per species all increased more rapidly than
+near the equator, it appears that high-latitude predators are more likely to be 
+generalists. This may reflect prey switching as
 different food sources become available in different seasons~\citep{}.
-Alternatively, the sharper increases in links per species, generality, and
-vulnerability at higher latitudes may be driven by the relationships between
-each property and the proportion of basal resources in these food webs.
-[[Except each property increases more with S and decreases more with B...]]
 
@@
 additional prey species per additional species in the food web, did not
-receive any more predators or links than species in low-latitude streams. The
-limited influence of latitude on the scaling relationships of links per
-species and vulnerability may be because, for these properties, latitude had
-opposite effects on the scaling relationships with proportions of basal
-resources and top predators. When considering generality, however, only the
-proportion of basal resources varied significantly over latitude. [[Same
-problem as in lakes, the trends are opposite.]]
+receive any more predators or links than species in low-latitude streams. 
+This may be partly due to the increasing proportion of the food web made up of
+basal resources at higher latitudes. If any additional species is more likely to
+be a basal resource at high latitudes, it will have predators but no prey.
+Combined with the potential for prey-switching between seasonal resources, this 
+could account for the sharper increase in generality with increasing species richness
+in high-latitude streams. Vulnerability and mean links per species, on the other hand,
+increased at the same rate across latitude. [[Still working on why]]
 
@@
 
+\newpage
+
 \begin{figure}[!h]
-\label{LS}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/LS_nonts.eps}
-\caption{Relationships between mean links per species and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs).
-[[More details needed]]}
+\label{S}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
+\caption{}
 \end{figure}
@@
 \begin{figure}[!h]
-\label{Gen}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/Gen_nonts.eps}
-\caption{Relationships between mean generality (number of prey) and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs).
-[[More details needed]]}
+\label{B}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
+\caption{}
 \end{figure}
@@
 \begin{figure}[!h]
-\label{Vul}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/Vul_nonts.eps}
-\caption{Relationships between mean vulnerability (number of predators) and species-richness, proportion of basal resources, proportion of intermediate consumers, or top predators (N=163 food webs).
-[[More details needed]]}
+\label{I}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/I_latlines_nonts.eps}
+\caption{}
+\end{figure}
+
+\begin{figure}[!h]
+\label{T}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/T_latlines_nonts.eps}
+\caption{}
 \end{figure}

### 2015-04-09 manuscript/latitudepaper.tex
First half of results updated

@@
 \vspace{0.4 in}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%%    Look into non-linear regressions for all properties (nls?)
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-[[Still need to check that new results hold for TS versions of webs.]]
 
@@
   % interactions between them \citep{Dunne2013}. 
-  % As we were considering the log of proportions of basal resources, top predators, and intermediate consumers, each web used in our analysis had to have at least one species in each trophic group.
+  % As we were considering the log of proportions of basal resources, top predators, and intermediate consumers, each web used in our analysis 
+  % had to have at least one species in each trophic group.
+
+  % of  the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
+  % \citep{}. Of these, 302 webs had accessible original sources. 
+  % 18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
+  % to have different food web properties than webs attempting to
+  % describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
+  % competition-focused networks
+  % \citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
+  % between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
+  % \citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
+  % we wished to measure
+  % directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
+  % the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
+  % \citep{Vinogradov1978}, such that it is not clear which site the food web represents. 
+  % This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans.
 
@@
   To determine whether there were latitudinal gradients in food-web structure,
-  we first examined simple linear relationships between latitude and each of $S$, $Z$, $G$, and $V$. 
-  We fit models of the form
+  we first examined simple linear relationships between latitude and each of 
+  $S$, $Z$, $G$, $V$, $B$, $I$, and $T$. We fit models of the form
 
@@
   \label{Power}
-  Z_{i} \~ \alpha S_{i}^{\beta}
+  Z_{i} \~ \alpha S_{i}^{\beta} .,
   \end{equation}
@@
   \label{Loglog}
-  \log{Z_{i}} \~ \log{\alpha} + \beta\log{S_{i}}
+  \log{Z_{i}} \~ \log{\alpha} + \beta\log{S_{i}} ..
   \end{equation}
 
-  Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
+  \noindent Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
   Specifically, equation~(\ref{Power}) implies a normally-distributed, additive error and equation~(\ref{Loglog}) a lognormal,
@@
 
-  Although scaling relationships between $S$, $G$, and $V$ have not been explicitly examined (but see scaling 
+  Although scaling relationships between $S$ and $G$ or $S$ and $V$ have not been explicitly examined (but see scaling 
   relationships for the standard devaitions of each property in \citet{Riede2010}), we expect that they will follow
@@
   We then assessed the impact of latitude on the scaling relationships between $Z$, $G$, $V$, and $S$. 
-  Even if there is no direct effect of latitude on specialization, perhaps due to contrasting effects
-  on species richness as described above, there may still be an effect of latitude on the scaling of
-  each property with species richness. In fact, if the species-rich tropics truly have narrower 
+  [[If the species-rich tropics truly have narrower 
   niches~\citep{Brown2004}, then we would expect to see less increase in mean numbers of links, 
-  predators, and prey with increasing species richness in the tropics.
-  In the context of the scaling relationships above, we wish to determine the effect of latitude on
+  predators, and prey with increasing species richness in the tropics. ]]
+  In the context of the scaling relationships above, note that this implies that we aim to determine the effect of latitude on
   the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
-  web property directly, we included a factorial variable for ecosystem type (stream, lake, 
+  web property directly, we included a categorical variable for ecosystem type (stream, lake, 
   terrestrial, marine, or estuary), as well as interactions between food web type and latitude.
 
-  We therefore began by considering models of the form:
+  We therefore began by considering models of the form
 
@@
   \label{PowerLat}
-  Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{2}E_{i}+\beta_{3}LE_{i}} + \epsilon_{i} 
+  Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{2}E_{i}+\beta_{3}LE_{i}} + \epsilon_{i} .,
   \end{equation}
 
-  where $S_{i}$ is the number of species in food web $i$, $L_{i}$ is the absolute latitude of food web $i$ (degrees from the equator, regardless of direction),
-  $E_{i}$ indicates the ecosystem type of food web $i$.
-
-  The logarithmic formulation of this model is:
+  \noindent where $S_{i}$, $L_{i}$, and $E_{i}$ are as defined previously. The logarithmic formulation of this model is
 
@@
   \label{LogLat}
-  \log{Z_{i}} = \log{\alpha}+\beta_{0}\log{S_{i}} + \beta_{1}L\log{S_{i}} +\beta_{2}E\log{S_{i}} +\beta_{3}LE\log{S_{i}} +\epsilon_{i}
+  \log{Z_{i}} = \log{\alpha}+\beta_{0}\log{S_{i}} + \beta_{1}L\log{S_{i}} +\beta_{2}E\log{S_{i}} +\beta_{3}LE\log{S_{i}} +\epsilon_{i} ..
   \end{equation}
@@
   when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
-  We then simplified the model. As with the models describing the relationships between latitude and food-web
-  properties, we calculated the AIC of the maximal and all reduced models, created by systematically removing
-  all possible combinations of terms. Note that if an interaction term was included in a reduced model, all
-  associated main effects were also retained. $S$ was included in all reduced models. Reduced models were
-  identified using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. The best-fitting model
-  was then determined to be the model with the fewest terms where $\Delta$AIC\textless2. Where there were several
-  models with the fewest terms where $\Delta$AIC\textless2, the model with the lowest AIC in this set was chosen as
-  the best-fitting model. The best-fitting model was then fit using R~\citep{R} function lm from package stats~\citep{stats}.
-
-  % of  the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
-  % \citep{}. Of these, 302 webs had accessible original sources. 
-  % 18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
-  % to have different food web properties than webs attempting to
-  % describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
-  % competition-focused networks
-  % \citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
-  % between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
-  % \citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
-  % we wished to measure
-  % directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
-  % the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
-  % \citep{Vinogradov1978}, such that it is not clear which site the food web represents. 
-  % This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans.
+  We then simplified each model following the same procedure as for the relationships between
+  latitude and food-web properties, except that $S$ was retained in all reduced models.
 
@@
   proportion of basal resources $B$, proportion of intermediate consumers $I$,
-  and  proportion of top predators $T$ in turn. All model fitting and model
-  simplification procedures were identical to those described for species-
+  or proportion of top predators $T$. All model fitting and model
+  simplification procedures were identical to those described for species
   richness.
@@
 
-  When considering the relationships between $S$ and $Z$, $G$, $V$, $B$, $I$, and $T$,
-  equation~(\ref{Loglog}) had a
-  lower AIC than the corresponding equation~(\ref{Power}). This indicates that the
-  data support an assumption of multiplicative log-normal error better than an
+  When considering the relationships between species richness and all response variables 
+  (link density, generality, vulnerability, and proportions of basal resources, intermediate consumers, and top predators), equation~(\ref{Loglog}) had a
+  lower AIC than did equation~(\ref{Power}). This indicates that the
+  data support an assumption of multiplicative lognormal error better than an
   assumption of additive normal error. That is, models where $\epsilon$ is
-  modelled as an exponent to a multiplicative term (that is, an additive term on
-  the logarithmic scale) provide a better description of the data than models
+  modelled as an additive term on
+  the logarithmic scale provide a better description of the data than models
   where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
@@
   Contrary to the expected latitudinal gradient, the best-fit version of
-  equation~(\ref{Latfull}) for $S$ included a signficant effect of latitude on $S$
-  in stream webs only ($\alpha_{Latitude:Stream}$=-1.69, $p$=0.007).  This
-  relationship was robust to the removal of three outliers (post-removal
-  $\alpha_{Latitude:Stream}$=-1.17, $p$=0.038). The best-fit versions of
-  equation~(\ref{Latfull}) for $Z$ and $V$ also included relationships with
-  latitude in stream webs ($\alpha_{Latitude:Stream}$=-0.179, $p$=0.007 and
-  $\alpha_{Latitude:Stream}$=-0.179, $p$=0.007, respectively). However, after
-  the removal of three outlying stream webs with very high $Z$ and $V$ (two of
-  which also had unusually high $S$) these relationships were no longer
-  significant ($\alpha_{Latitude:Stream}$=-0-0.046, $p$=0.373 and
-  $\alpha_{Latitude:Stream}$=-0.046, $p$=0.373, respectively). The best-fit
-  version of equation~(\ref{Latfull}) for $G$ did not include any effect of
-  latitude in any ecosystem type. Marine food webs
-  had lower $S$, $Z$, $G$, and $V$ than all other web types (post-removal
-  $\alpha_{Marine}$=-29.5, $p$\textless0.001, $\alpha_{Marine}$=-1.46,
-  $p$=0.035, $\alpha_{Marine}$=-1.74, $p$=0.0612, and $\alpha_{Marine}$=-1.46,
-  $p$=0.035, respectively) while stream food webs had higher $G$ than webs from
-  other ecosystem types (post-removal $\alpha_{Stream}$=3.51,
-  $p$\textless0.001).
+  equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
+  ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
+  relationship was robust to the removal of three outliers (based on Cook's Distance). In the best-fit versions of
+  equation~(\ref{Latfull}) for link density and vulnerability, there were once again
+  significant relationships with latitude in stream food webs but 
+  no other ecosystem type 
+  ($\beta_{Latitude}$=0.022, $p$=0.592 and $\beta_{Latitude:Stream}$=-0.356, $p$=0.007 for link density; 
+  $\beta_{Latitude}$=0.011, $p$=0.589 and $\beta_{Latitude:Stream}$=-0.179, $p$=0.007 for vulnerability). However, after
+  the removal of three outliers these relationships were no longer
+  significant. The best-fit
+  version of equation~(\ref{Latfull}) for generality did not include any effect of
+  latitude in any ecosystem type.
 
-  The relationships between $B$, $I$, and $T$ with latitude were broadly similar
-  to the relationship between $S$ and latitude. $B$ did not vary significantly
-  over latitude except in stream food webs where $B$ increased towards the poles
-  ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001), while $I$ did not vary
-  significantly with latitude in any ecosystem type. Like $S$, $T$ decreased
-  towards the poles in stream food webs ($\alpha_{Latitude}$=0.001, $p$=0.136;
-  $\alpha_{Latitude:Stream}$=-0.006, $p$=0.030) and also decreased towards the
-  poles in lake webs ($\alpha_{Latitude:Lake}$=-0.006, $p$=0.001
+  The relationships between the proportions of species at each trophic level with latitude were broadly similar
+  to the relationship between species richness and latitude. 
+  The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
+  but did not vary with latitude in estuarine, marine, lake, or terrestrial 
+  food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
+  The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
+  The proportion of top predators did not vary with latitude in 
+  estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
+  webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
+  $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
   All of these trends were robust to the removal of outliers.
@@
 
-$Z$, $G$, and $V$ all increased with increasing $S$ at all latitudes. The strength of
+[[Not redone yets]]
+
+Link density, generality, and vulnerability each increased with increasing species richness ($\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675, $p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001).
+For estuarine, marine, and terrestrial food webs this increase did not vary with latitude ($\beta_{Latitude}$=-0.001, $p$=0.334; $\beta_{Latitude}$=-0.001, $p$=0.354; and $\beta_{Latitude}$=-0.001, $p$=0.334)
+
+The strength of
 this increase varied both over latitude and across ecosystem types. For $Z$,

### 2015-04-09 code/recreate_with_subset.R

@@ -117,7 +117,17 @@
     Sp_latdirect=(with(data,lm(Species~Stream*Latitude+Lake+Marine+Terr),na.action=na.fail)) 
     } else {
     Sp_latdirect=(with(data,lm(Species~Stream*Latitude+Lake+Marine),na.action=na.fail)) }
+    cutoff<- 4/((nrow(data)-length(Sp_latdirect$coefficients)-2)) 
+    plot(Sp_latdirect, which=4, cook.levels=cutoff)
+    subset=data[-c(122,126,128),]
 
   LS_latdirect=(with(data,lm(LS~Stream*Latitude+Marine),na.action=na.fail))
+    cutoff<- 4/((nrow(data)-length(LS_latdirect$coefficients)-2)) 
+    plot(LS_latdirect, which=4, cook.levels=cutoff)
+    subset=data[-c(110,122,127),]
+
   Gen_latdirect=(with(data,lm(Gen~Marine+Stream),na.action=na.fail))
   Vul_latdirect=(with(data,lm(Vul~Latitude*Stream+Marine),na.action=na.fail))
+    cutoff<- 4/((nrow(data)-length(Vul_latdirect$coefficients)-2)) 
+    plot(Vul_latdirect, which=4, cook.levels=cutoff)
+    subset=data[-c(110,122,127),]

### 2015-04-09 manuscript/latitudepaper.tex
Updated all results

@@
 
-[[Not redone yets]]
+Link density, generality, and vulnerability each increased with increasing
+species richness (Fig.~\ref{S}; $\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675,
+$p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001).  For estuarine,
+marine, and terrestrial food webs this increase did not vary with latitude
+($\beta_{Latitude}$=-0.001, $p$=0.334; $\beta_{Latitude}$=-0.001, $p$=0.354;
+and $\beta_{Latitude}$=-0.001, $p$=0.334). In lake food webs, link density,
+generality, and vulnerability all increased more quickly towards the poles
+($\beta_{Latitude:Lake}$=0.004, $p$=; $\beta_{Latitude:Lake}$=0.005,
+$p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
+stream food webs, only the strength of scaling of generality increased with
+latitude ($\beta_{Latitude}$=0.007, $p$=0.002).
 
-Link density, generality, and vulnerability each increased with increasing species richness ($\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675, $p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001).
-For estuarine, marine, and terrestrial food webs this increase did not vary with latitude ($\beta_{Latitude}$=-0.001, $p$=0.334; $\beta_{Latitude}$=-0.001, $p$=0.354; and $\beta_{Latitude}$=-0.001, $p$=0.334)
+In general, link density, generality, and vulnerability decreased as the
+proportion of basal resources in a web increased (Fig.~\ref{B}). For
+estuarine, lake, and stream food webs these decreases were steeper towards the
+poles ($\beta_{Latitude}$=-0.007, $p$=0.006 for link density;
+$\beta_{Latitude}$=-0.009, $p$=0.002 for generality; and
+$\beta_{Latitude}$=-0.007, $p$=0.006 for vulnerability).
+In marine food webs there was very little effect of latitude on
+the strength of scaling ($\beta_{Latitude:Marine}$=0.009, $p$=0.047; 
+$\beta_{Latitude:Marine}$=0.011, $p$=0.028; 
+and $\beta_{Latitude:Marine}$=0.009, $p$=0.047 respectively),
+while in terrestrial food webs scaling was stronger towards the 
+equator ($\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002; 
+$\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; 
+and $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002).
 
-The strength of
-this increase varied both over latitude and across ecosystem types. For $Z$,
-scaling was stronger towards the equator except in lake ecosystems where scaling was stronger
-towards the poles (Fig.~\ref{LS}). $G$ and $V$ followed the same trends, except that scaling of $G$
-with $S$ was stronger towards the poles as in lakes (Figs.~\ref{Gen, Vul}).
+In contrast to the proportion of basal resources, link density, generality,
+and vulnerability tended to increase with increasing proportions of
+intermediate consumers (Fig.~\ref{I}). The best-fit models for scaling of link
+density and vulnerability with the proportion of intermediate consumers did
+not include any effect of latitude on scaling in any ecosystem type. Scaling
+of generality was stronger towards the equator in estuarine, lake, marine, and
+stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
+latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
+$p$=0.053). In lake and stream food webs, generality increased more weakly
+with the proporiton of intermediate consumers such that, at low proportions,
+the effect of latitude could negate or reverse the increase.
 
-When considering the proportion of $S$ accounted for by different trophic
-levels, however, the scaling relationships with $Z$, $G$, and $V$ were more
-complex. While $Z$ increased with increasing $I$ as well as with increasing
-$S$, $Z$ tended to decrease with increasing $B$ and $T$. The decrease of $Z$
-with $B$ was stronger towards the poles in estuarine, lake, and stream webs
-(), varied little over latitude in marine webs (), and was stronger towards
-the poles in terrestrial webs (). The best-fitting model for the relationship
-of $Z$ and $I$ did not include any terms for variation in scaling across
-latitude for any ecosystem type. Similar to the scaling of $Z$ with $B$, the
-decrease in $Z$ with increasing $T$ was stronger towards the poles in
-estuarine, lake, and marine webs, although the influence of latitude was
-weaker than with $B$ (). Again like the relationship between $Z$ and $B$,
-scaling of $Z$ with $T$ was stronger towards the equator in terrestrial webs.
-Unlike in the relationship between $Z$ and $B$, however, scaling of $Z$ with
-$T$ was also stronger towards the equator in stream webs.
-
-As with $Z$, $G$ tended to decrease with increasing $B$ and $T$ and increase
-with increasing $I$. Once again, however, these trends varied with latitude
-and ecosystem type. The decline of G with increasing S was strongest at the
-poles in estaurine, lake, and marine ecosystems; in each ecosystem type $G$
-increased slightly with $B$ in equatorial webs. In marine webs $G$ increased
-slightly with $B$ at all latitudes and in terrestrial webs $G$ increased with
-$B$ in high-latitude webs but decreased slightly with $B$ at the equator. The
-strength of the increase in $G$ with $I$ varied little with latitude except in
-stream webs, where the increase was strongest towards the equator and $G$
-decreased with $I$ in arctic food webs. The best-fitting model for the scaling
-of $G$ with $T$ did not include any terrms for latitude in any ecosystem type.
-
-$V$ too generally decreased with increasing $B$ and $T$ while increasing with
-$I$. Similar to $G$, the decline of $V$ with increasing $B$ was strongest
-towards the poles in estuarine, lake, and stream webs, varied little with
-latitude in marine webs, and was strongest towards the equator in terrestrial
-food webs. As with $Z$, the best-fit model for the scaling of $V$ with $I$ did
-not include any terms for latitude in any ecosystem type. Scaling of $V$ with
-$T$ was also simmilar to the pattern for $Z$, with sharper decreases in $V$
-towards the poles in estuarine, lake, and marine webs and stronger towards the
-equator in terrestrial and stream webs.
+As with the proportion of basal resources, link density, generality, and
+vulnerability decreased as the proportion of top predators increased. For
+estuarine, lake, and marine food webs scaling of link density, generality, and
+vulnerability did not vary significantly with latitude
+($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
+$\beta_{Latitude}$=-0.001, $p$=0.526 for vulnerability; the best-fit model for
+generality did not include any terms for latitude in any ecosystem type). In
+stream and terrestrial food webs, the decrease in link density and
+vulnerability was steeper towards the poles, although this trend was
+significant only in streams ($\beta_{Latitude:Stream}$=0.015,
+$p$\textless0.001 and $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link
+density; $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
+$\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability).
 
@@
 \label{S}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_latlines_nonts.eps}
 \caption{}

### 2015-04-09 code/TL_scaling_justlines.py

@@ -116,10 +116,6 @@ def predictionreader(predfile,TL,Bformat):
 def scaleplots(rawdatafile,outfile,Bformat,TL,predfolder):
 
   ecotypes=['Estuary','Lake','Marine','Stream','Terrestrial']
-  # if TL in ['B','T']:
-  #   ecotypes=['Estuary','Stream','Terrestrial','Marine']
-  # elif TL in ['I','S']:
-  #   ecotypes=['Estuary','Lake','Stream','Terrestrial']
 
   xwidth=10
   ywidth=1.5
@@ -131,8 +127,6 @@ def scaleplots(rawdatafile,outfile,Bformat,TL,predfolder):
 
   grace=MultiPanelGrace(colors=ColorBrewerScheme("Greys",n=253))
 
-#  for prop in ['LS','Gen','Vul']:
-  # for TL in ['B','I','T','S']:
   for prop in ['LS','Gen','Vul']:
     if TL!='S':
       preddata=predictionreader(predfolder+'/predictions/'+prop[0]+TL+'.tsv',TL,Bformat)
@@ -149,16 +143,6 @@ def scaleplots(rawdatafile,outfile,Bformat,TL,predfolder):
       graph=grace.add_graph(Panel)
       heatpoints=heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat)
 
-      # datadict=heatpoints[ecotype]
-
-      # for d in datadict:
-      #   color=colorbar.z2color(datadict[d])
-      #   dat=graph.add_dataset([(d[0],d[1])])
-      #   dat.symbol.configure(fill_color=color,color=1,shape=1,linewidth=.5)
-      #     # [(d[0]-0.5*xwidth,d[1]-0.5*ywidth), (d[0]+0.5*xwidth,d[1]+0.5*ywidth)], SolidRectangle, color)
-
-      # for line in [0,10,20,30,40,50,60,70,80,90]:
-      # for line in [0,20,40,60,80]:
       for line in [80,60,40,20,0]:
         preddataset1=graph.add_dataset(preddata[ecotype][line])
 
@@ -168,24 +152,13 @@ def scaleplots(rawdatafile,outfile,Bformat,TL,predfolder):
 
         preddataset1.line.configure(linestyle=linesty,color=colorbar.z2color(line))
 
-        if TL in ['I','S'] and ecotype=='Estuary':
-          preddataset2=graph.add_dataset(preddata['Marine'][line])
[…]

### 2015-04-10 manuscript/latitudepaper.tex
Figure roundup

@@
 \usepackage{amsmath}
+\usepackage{gensymb}
 \usepackage{url}
@@
   \label{Latfull}
-  S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} .,
+  S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
   \end{equation}
@@
   \label{Power}
-  Z_{i} \~ \alpha S_{i}^{\beta} .,
+  Z_{i} \sim \alpha S_{i}^{\beta}  ,
   \end{equation}
@@
   \label{Loglog}
-  \log{Z_{i}} \~ \log{\alpha} + \beta\log{S_{i}} ..
+  \log{Z_{i}} \sim \log{\alpha} + \beta\log{S_{i}}  .
   \end{equation}
@@
   \label{PowerLat}
-  Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{2}E_{i}+\beta_{3}LE_{i}} + \epsilon_{i} .,
+  Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{2}E_{i}+\beta_{3}LE_{i}} + \epsilon_{i} ,
   \end{equation}
@@
   \label{LogLat}
-  \log{Z_{i}} = \log{\alpha}+\beta_{0}\log{S_{i}} + \beta_{1}L\log{S_{i}} +\beta_{2}E\log{S_{i}} +\beta_{3}LE\log{S_{i}} +\epsilon_{i} ..
+  \log{Z_{i}} = \log{\alpha}+\beta_{0}\log{S_{i}} + \beta_{1}L\log{S_{i}} +\beta_{2}E\log{S_{i}} +\beta_{3}LE\log{S_{i}} +\epsilon_{i} .
   \end{equation}
@@
 
-% \begin{figure}[!h]
-% \label{Latfigs}
-% \includegraphics[width=.9\textwidth]{Figures/properties_vs_lat.eps}
-% \caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability.
-No food web property showed a significant latitudinal gradient in this dataset (N=259 food webs).}
-% \end{figure}
-
-% \begin{figure}[!h]
-% \label{scalingfig}
-% \includegraphics[width=.9\textwidth]{Figures/nonts_scaling_with_S_grey.eps}
-% \caption{Relationships between species richness and mean links per species, mean generality, and mean 
-% vulnerability (N=259 food webs). Scaling of mean links per species and mean vulnerability with species 
-% richness strengthened with latitude for estuarine, stream, and lake food webs. This strengthening was
-% reversed for marine and terrestrial food webs. Scaling of mean generality with species richness 
-% strengthened with latitude for lake food webs, but did not significantly vary with latitude for other
-% ecosystem types (N=259 food webs). }
-% \end{figure}
-
-\begin{figure}[!h]
-\label{props_v_lat}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/properties_vs_lat/proportions/nonts_propsvlat.eps}
-\caption{Relationships between latitude and species richness, mean links per species, mean generality, and mean vulnerability (N=163 food webs). }
+\begin{figure}[h]
+\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_latlines_nonts.eps}
+\caption{Scaling of link density, generality, and vulnerability with species richness
+varies across ecosystem types and over latitude. For each property we show 
+prediction curves for food webs at the equator (darkest line) and at 
+20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
+equator. We did not include direction (i.e., North or South) in our analyses. 
+All curves are based on N=163 empirical food webs.}
+\label{S}
 \end{figure}
 
-\begin{figure}[!h]
-\label{TLs_v_lat}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/properties_vs_lat/proportions/nonts_TLvlat.eps}
-\caption{Relationships between latitude and proportions of basal resources, intermediate consumers, and top predators (N=163 food webs). }
+\begin{figure}[!H]
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
+\caption{Scaling of link density, generality, and vulnerability 
+with the proportion of basal resources in a food web
+varies across ecosystem types and over latitude. For each property we show 
+prediction curves for food webs at the equator (darkest line) and at 
+20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
+equator. We did not include direction (i.e., North or South) in our analyses. 
+All curves are based on N=163 empirical food webs.}
+\label{B}
 \end{figure}
@@
 
-\begin{figure}[!h]
-\label{S}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_latlines_nonts.eps}
-\caption{}
+\begin{figure}[h]
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/I_latlines_nonts.eps}
+\caption{Scaling of link density, generality, and vulnerability 
+with the proportion of intermediate consumers in a food web
+varies across ecosystem types and over latitude. For each property we show 
+prediction curves for food webs at the equator (darkest line) and at 
+20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
+equator. We did not include direction (i.e., North or South) in our analyses. 
+All curves are based on N=163 empirical food webs.}
+\label{I}
 \end{figure}
 
-\begin{figure}[!h]
-\label{B}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
-\caption{}
+\begin{figure}[h]
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/T_latlines_nonts.eps}
+\caption{Scaling of link density, generality, and vulnerability 
+with the proportion of top predators in a food web
+varies across ecosystem types and over latitude. For each property we show 
+prediction curves for food webs at the equator (darkest line) and at 
+20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
+equator. We did not include direction (i.e., North or South) in our analyses. 
+All curves are based on N=163 empirical food webs.}
+\label{T}
 \end{figure}
 
-\begin{figure}[!h]
-\label{I}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/I_latlines_nonts.eps}
-\caption{}
-\end{figure}
+\newpage
 
-\begin{figure}[!h]
-\label{T}
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/T_latlines_nonts.eps}
-\caption{}
+\begin{figure}[H]
+\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
+\caption{Scaling relationships for link density, generality (number of prey), 
+and vulnerability (number of predators) 
+against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
+predators (\% Top), and species richness of a food web. 
+For each relationship we show observed values corrected for
+ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). }
+\label{props_v_lat}
 \end{figure}

### 2015-04-10 code/TL_scaleplots.py

@@ -170,8 +170,6 @@ def predictionlines(fixed,prop,ecotype,TL):
 
   delta=fixed['log10('+key+')']
 
-  print alpha, delta
-
   if TL=='S':
     for S in range(1,200):
       predy=alpha*(S**delta)
@@ -191,10 +189,10 @@ def scaleplots(rawdatafile,outfile,Bformat,predfolder):
 
   rawdata=datareader(rawdatafile)
 
-  grace=MultiPanelGrace(colors=ColorBrewerScheme("Paired"))
+  grace=MultiPanelGrace(colors=ColorBrewerScheme("Greys"))
 
   for prop in ['LS','Gen','Vul']:
-    for TL in ['B','I','T','S']:
+    for TL in ['S','B','I','T']:
       if TL!='S':
         fixed=fixed_reader(predfolder+'/coefficients/'+prop[0]+TL+'_co.tsv')
       else:
@@ -204,30 +202,34 @@ def scaleplots(rawdatafile,outfile,Bformat,predfolder):
           fixed=fixed_reader('../mod_data/subset/coefficients/'+prop+'_co.tsv')
 
       graph=grace.add_graph(Panel)
-      print fixed
       for ecotype in ecotypes:
         if ecotype=='Estuary':
+          shap=1
           linecol=1
         elif ecotype=='Lake':
+          shap=2
           linecol=3
         elif ecotype=='Marine':
+          shap=3
           linecol=5
         elif ecotype=='Stream':
+          shap=4
           linecol=7
         else:
+          shap=5
           linecol=11
 
         heatpoints=heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat)
         datadict=heatpoints[ecotype]
         obspoints=graph.add_dataset(datadict)
         obspoints.line.configure(linestyle=0)
-        obspoints.symbol.configure(size=.5,shape=1,fill_color=0,fill_pattern=1,color=linecol)
+        obspoints.symbol.configure(size=.5,shape=1,fill_color=0,fill_pattern=1,color=8)
 
         predictions=predictionlines(fixed,prop,ecotype,TL)
         predline=graph.add_dataset(predictions)
         predline.symbol.shape=0
 
-        # predline.line.configure(linestyle=1,color=linecol)
+        predline.line.configure(linestyle=1,color=1,linewidth=2.5)
         # if TL=='S':
         #   predline.legend=ecotype
 
[…]

### 2015-04-10 code/TL_scaling_justlines.py

@@ -162,7 +162,7 @@ def scaleplots(rawdatafile,outfile,Bformat,TL,predfolder):
 
       if ecotype=='Estuary':
         if prop=='LS':
-          yax="Links/species"
+          yax="Link density"
         elif prop=='Gen':
           yax="Generality"
         elif prop=='Vul':

### 2015-04-10 code/exponent_plots.py
removing old figure code

@@ -1,133 +1,0 @@
-import sys
-import os
-import re
-import random
-from decimal import *
-import math
-
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
-
-from TL_scaleplots import fixed_reader
-
-def scaleplots(rawdatafile,outfile,Bformat,prop,predfolder):
-
-  ecotypes=['Estuary','Lake','Marine','Stream','Terrestrial']
-
-  xwidth=10
-  ywidth=1.5
-
-  dummygrace=MultiPanelGrace(colors=ColorBrewerScheme("RdYlBu",reverse=True,n=253))
-  colorbar = dummygrace.add_graph(ElLinColorBar,domain=(0,90),scale=LINEAR_SCALE,autoscale=False)
-
-  grace=MultiPanelGrace(colors=ColorBrewerScheme("RdYlBu",reverse=True,n=253))
-
-  for TL in ['B','I','T','S']:
-    graph=grace.add_graph(Panel)
-
-    if TL!='S':
-      fixed=fixed_reader(predfolder+'/coefficients/'+prop[0]+TL+'_co.tsv')
-    else:
-      if rawdatafile=='../non_TS/summary-properties.tsv':
-        fixed=fixed_reader('../non_TS/subset/coefficients/'+prop+'_co.tsv')
-      else:
-        fixed=fixed_reader('../mod_data/subset/coefficients/'+prop+'_co.tsv')
-
-
-    for ecotype in ecotypes:
-      ecoline=[]
-
-      if TL=='B':
-        key='Basal'
-        xtex='% Basal'
-      elif TL=='I':
-        key='Intermediate'
-        xtex='% Intermediate'
-      elif TL=='T':
-        key='Toppreds'
-        xtex='% Top'
-      else:
-        key='Species'
-        xtex='Species Richness'
-
-      if 'log10('+key+'):'+ecotype in fixed:
[…]

### 2015-04-10 code/generality_plots.py

@@ -1,195 +1,0 @@
-import sys
-import os
-import re
-import random
-from decimal import *
-import math
-
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText
-
-#Global mins, means, maxes. Doing by ecotype below.
-mean_C=0.1
-min_C=0.025
-max_C=0.25
-
-mean_S=36
-min_S=5
-max_S=109
-
-#Mean dist from centroids
-def linereader(fw_prop):
-  linefile="../mod_data/"+fw_prop+"_coeffs"
-  linetab=open(linefile,'r')
-  lines={}
-  for line in linetab:
-    if len(line.split())==5:
-      effect=line.split()[0][1:-1]
-      beta=float(line.split()[1])
-      lines[effect]=beta
-  return lines
-
-def datareader(fw_prop):
-  datafile="../mod_data/summary-properties.tsv"
-  f=open(datafile,'r')
-  datadict={'estuary':{},'lake':{},'terrestrial':{},'marine':{},'stream':{}}
-  for line in f:
-    if line.split()[0]=='Web':
-      heads=line.split()[1:]
-    else:
-      web=line.split()[0]
-      data=line.split()[1:]
-      Ecotype=line.split()[1]
-      if Ecotype in datadict:
-        datadict[Ecotype][web]={}
-        for term in range(0,len(heads)):
-          if term!='Ecotype':
-            datadict[Ecotype][web][heads[term]]=data[term]
-  return datadict
-
-def plotter(fw_prop,ecotype):
-  datadict=datareader(fw_prop)
-  lines=linereader(fw_prop)
-
-  realdata={}
-  realdata={'Species':[],'Connectance':[],'Latitude':[],fw_prop:[]}
-
-  for web in datadict[ecotype]:
-    for term in realdata:
-      realdata[term].append(float(datadict[ecotype][web][term]))
-
-  mean_C=float(sum(realdata['Connectance']))/len(realdata['Connectance'])
-  min_C=float(sorted(realdata['Connectance'])[1])
-  max_C=float(sorted(realdata['Connectance'])[-1])
-
-  mean_S=float(sum(realdata['Species']))/len(realdata['Species'])
[…]

### 2015-04-10 code/property_plots.py

@@ -1,337 +1,0 @@
-import sys
-import os
-import re
-import random
-from decimal import *
-import math
-
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
-
-# Think I want plots of the raw data (S, LS, G, V vs. lat) with slope lines
-# Plus predictions for LS, G, V vs S (with corrected obs.)
-
-def datareader(rawdatafile):
-  points={'S':{'estuary':[],'lake':[],'marine':[],'stream':[],'terrestrial':[]},
-  'LS':{'estuary':[],'lake':[],'marine':[],'stream':[],'terrestrial':[]},
-  'G':{'estuary':[],'lake':[],'marine':[],'stream':[],'terrestrial':[]},  
-  'V':{'estuary':[],'lake':[],'marine':[],'stream':[],'terrestrial':[]}}
-
-  f=open(rawdatafile,'r')
-  for line in f:
-    if line.split()[0]!='Web':
-      Latitude=float(line.split('\t')[6])
-      Species=int(line.split('\t')[7])
-      LS=float(line.split('\t')[10])
-      G=float(line.split('\t')[12])
-      V=float(line.split('\t')[14])
-      ecotype=line.split('\t')[1]
-
-      points['S'][ecotype].append((Latitude,Species))
-      points['LS'][ecotype].append((Latitude,LS))
-      points['G'][ecotype].append((Latitude,G))
-      points['V'][ecotype].append((Latitude,V))
-  f.close()
-  return points
-
-def fixed_reader(coefffile):
-  fixed_effects={}
-  f=open(coefffile,'r')
-  for line in f:
-    if line.split()[0]!='"Estimate"':
-      name=line.split()[0][1:-1]
-      beta=float(line.split()[1])
-      fixed_effects[name]=beta
-  f.close()
-  return fixed_effects
-
-def heatmappoints(rawdatafile,coefffile,webtype):
[…]

### 2015-04-10 manuscript/latitudepaper.tex
Took a section of results out of the discussion
Figures updated, just need to add final round of changes and we're good to go!

@@
 
-\subsection*{Scaling Relationships with $S$ and Latitude}
-
-  When considering the relationships between species richness and all response variables 
-  (link density, generality, vulnerability, and proportions of basal resources, intermediate consumers, and top predators), equation~(\ref{Loglog}) had a
-  lower AIC than did equation~(\ref{Power}). This indicates that the
-  data support an assumption of multiplicative lognormal error better than an
-  assumption of additive normal error. That is, models where $\epsilon$ is
-  modelled as an additive term on
-  the logarithmic scale provide a better description of the data than models
-  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
-  We therefore used logarithmic-form models when assessing the
-  effect of latitude on scaling relationships  with $S$.
+\subsection*{Relationships with Latitude}
 
@@
   All of these trends were robust to the removal of outliers.
+
+\subsection*{Form of scaling relationships}
+
+  When considering the relationships between species richness and proportions 
+  of basal resources, intermediate consumers, and top predators and all response variables 
+  (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
+  lower AIC than did equation~(\ref{Power}). This indicates that the
+  data support an assumption of multiplicative lognormal error better than an
+  assumption of additive normal error. That is, models where $\epsilon$ is
+  modelled as an additive term on
+  the logarithmic scale provide a better description of the data than models
+  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
+  We therefore used logarithmic-form models when assessing the
+  effect of latitude on scaling relationships  with $S$.
 
@@
 specialists~\citep{}.
-
-   $B$ increased towards the poles ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001)
-   $T$ decreased towards the poles in stream food webs ($\alpha_{Latitude}$=0.001, $p$=0.136;
-  $\alpha_{Latitude:Stream}$=-0.006, $p$=0.030)
 

### 2015-04-10 code/TL_scaleplots.py

@@ -166,7 +166,7 @@ def predictionlines(fixed,prop,ecotype,TL):
   else:
     key='Species'
 
-  alpha=math.exp(fixed['(Intercept)'])
+  alpha=10**fixed['(Intercept)']
 
   delta=fixed['log10('+key+')']
 
@@ -270,19 +270,22 @@ def scaleplots(rawdatafile,outfile,Bformat,predfolder):
         if TL=='T':
           if prop=='LS':
             yax="Link density"
-            ymed=25
+            ymed=math.log10(50)/2
           elif prop=='Gen':
             yax="Generality"
-            ymed=15
+            ymed=math.log10(30)/2
           elif prop=='Vul':
             yax="Vulnerability"
-            ymed=15
+            ymed=math.log10(30)/2
 
-          graph.add_drawing_object(DrawText,text=yax,x=1.1,y=ymed,char_size=.75,loctype='world',rot=270,just=2)
+          graph.add_drawing_object(DrawText,text=yax,x=1.2,y=10**ymed,char_size=.75,loctype='world',rot=270,just=2)
           # graph.yaxis.label.configure(text=yax,place='opposite',char_size=.75)
 
-        graph.world.xmin=0
-        graph.world.ymin=0
+        if TL!='S':
+          graph.world.xmin=0.01
+        else:
+          graph.world.xmin=1
+        graph.world.ymin=1
 
         if prop=='LS':
           graph.world.ymax=50
@@ -290,14 +293,16 @@ def scaleplots(rawdatafile,outfile,Bformat,predfolder):
           graph.world.ymax=30
         else:
           graph.world.ymax=30
-        graph.yaxis.tick.major=10
+        # graph.yaxis.tick.major=10
+        graph.xaxis.set_log()
+        graph.yaxis.set_log()
 
         if TL=='S':
-          graph.world.xmax=200
-          graph.xaxis.tick.major=50
+          graph.world.xmax=350
+          # graph.xaxis.tick.major=50
         else:
           graph.world.xmax=1
-          graph.xaxis.tick.major=.2
+          # graph.xaxis.tick.major=.2
 
         graph.xaxis.tick.configure(minor_ticks=1,major_size=.7,minor_size=.4,major_linewidth=1,minor_linewidth=1)
         graph.xaxis.ticklabel.configure(char_size=.75)

### 2015-04-10 code/TL_scaling_justlines.py

@@ -31,39 +31,6 @@ def fixed_reader(coefffile):
   f.close()
   return fixed_effects
 
-def heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat):
-  # Would probably be more helpful to do a heatmap of observed latitudes.
-  obs={'Lake':{},
-              'Stream':{},
-              'Marine':{},
-              'Terrestrial':{},
-              'Estuary':{}}
-  fixed_effects=fixed
-  f=open(rawdatafile,'r')
-  for line in f:
-    if line.split()[0]!='Web':
-      Latitude=float(line.split('\t')[6])
-      S=int(line.split('\t')[7])
-      LS=float(line.split('\t')[10])
-      L=LS
-      G=float(line.split('\t')[12])
-      Gen=G
-      V=float(line.split('\t')[14])
-      Vul=V
-      ecotype=line.split('\t')[1]
-      ecotype=ecotype.capitalize()
-      B=float(line.split('\t')[-4])
-      I=float(line.split('\t')[-2])
-      T=float(line.split('\t')[-1])
-      if Bformat=='numbers':
-        B=B*S
-        I=I*S
-        T=T*S
-      obs[ecotype][(eval(TL),eval(prop))]=Latitude
-  f.close()
-
-  return obs
-
 def predictionreader(predfile,TL,Bformat):
   predpoints={'Lake':{0:[],10:[],20:[],30:[],40:[],50:[],60:[],70:[],80:[],90:[]},
             'Marine':{0:[],10:[],20:[],30:[],40:[],50:[],60:[],70:[],80:[],90:[]},
@@ -141,7 +108,6 @@ def scaleplots(rawdatafile,outfile,Bformat,TL,predfolder):
 
     for ecotype in ecotypes:
       graph=grace.add_graph(Panel)
-      heatpoints=heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat)
 
       for line in [80,60,40,20,0]:
         preddataset1=graph.add_dataset(preddata[ecotype][line])
@@ -156,9 +122,7 @@ def scaleplots(rawdatafile,outfile,Bformat,TL,predfolder):
         stars=[(.35,25)]
       else:
         stars=[(175,25)]
-      ### Add stars for significant trends
-
-      # if TL=='B' and ecotype in ['Estuary','Lake','Stream']:
+      ### Add stars for significant trends ?
 
       if ecotype=='Estuary':
[…]

### 2015-04-10 manuscript/latitudepaper.tex
Added last round of corrections before sending off to T

@@
 
-  We then assessed the impact of latitude on the scaling relationships between $Z$, $G$, $V$, and $S$. 
+  We then assessed the impact of latitude on the scaling relationships between species richness and 
+  link density, generality, vulnerability.
   [[If the species-rich tropics truly have narrower 
@@
 
-  For each property in $Z$, $G$, and $V$, we used the form of the equation that was best supported
+  For each property in link density, generality, and vulnerability, we used the form of the equation that was best supported
   when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
   We then simplified each model following the same procedure as for the relationships between
-  latitude and food-web properties, except that $S$ was retained in all reduced models.
+  latitude and food-web properties, except that species richness was retained in all reduced models.
 
@@
 
-  We were also interested in the ways that scaling relationships with $S$ might
+  We were also interested in the ways that scaling relationships with species richness might
   be affected by changes to the distribution of species among trophic levels. To
@@
   equation~(\ref{Latfull}) for link density and vulnerability, there were once again
-  significant relationships with latitude in stream food webs but 
-  no other ecosystem type 
-  ($\beta_{Latitude}$=0.022, $p$=0.592 and $\beta_{Latitude:Stream}$=-0.356, $p$=0.007 for link density; 
-  $\beta_{Latitude}$=0.011, $p$=0.589 and $\beta_{Latitude:Stream}$=-0.179, $p$=0.007 for vulnerability). However, after
-  the removal of three outliers these relationships were no longer
-  significant. The best-fit
-  version of equation~(\ref{Latfull}) for generality did not include any effect of
+  significant relationships with latitude in stream food webs, but after the removal of three outliers these trends
+  were no longer significant. Link density and vulnerability did not vary with latitude in any other ecosystem type.
+  Similarly, the best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
   latitude in any ecosystem type.
@@
   We therefore used logarithmic-form models when assessing the
-  effect of latitude on scaling relationships  with $S$.
+  effect of latitude on scaling relationships  with species richness.
 
@@
 species richness (Fig.~\ref{S}; $\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675,
-$p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001).  For estuarine,
+$p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001 respectively).  For estuarine,
 marine, and terrestrial food webs this increase did not vary with latitude
-($\beta_{Latitude}$=-0.001, $p$=0.334; $\beta_{Latitude}$=-0.001, $p$=0.354;
-and $\beta_{Latitude}$=-0.001, $p$=0.334). In lake food webs, link density,
+($\beta_{Latitude}$=-0.001, $p$=0.334 for link density; $\beta_{Latitude}$=-0.001, $p$=0.354 for generality;
+and $\beta_{Latitude}$=-0.001, $p$=0.334 for vulnerability). In lake food webs, link density,
 generality, and vulnerability all increased more quickly towards the poles
-($\beta_{Latitude:Lake}$=0.004, $p$=; $\beta_{Latitude:Lake}$=0.005,
+($\beta_{Latitude:Lake}$=0.004, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
 $p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
-stream food webs, only the strength of scaling of generality increased with
-latitude ($\beta_{Latitude}$=0.007, $p$=0.002).
+stream food webs generality increased more rapidly towards the poles 
+($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability did not vary with latitude.
 
@@
 proportion of basal resources in a web increased (Fig.~\ref{B}). For
-estuarine, lake, and stream food webs these decreases were steeper towards the
+estuarine, lake, and stream food webs these decreases were more gradual towards the
 poles ($\beta_{Latitude}$=-0.007, $p$=0.006 for link density;
@@
 and $\beta_{Latitude:Marine}$=0.009, $p$=0.047 respectively),
-while in terrestrial food webs scaling was stronger towards the 
+while in terrestrial food webs link density, generality, and vulnerability
+decreased more gradually towards the 
 equator ($\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002; 
@@
 density and vulnerability with the proportion of intermediate consumers did
-not include any effect of latitude on scaling in any ecosystem type. Scaling
-of generality was stronger towards the equator in estuarine, lake, marine, and
+not include any effect of latitude on scaling in any ecosystem type. Generality
+increased more rapidly towards the equator in estuarine, lake, marine, and
 stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
 latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
-$p$=0.053). In lake and stream food webs, generality increased more weakly
+$p$=0.053). In lake and stream food webs, generality increased more slowly
 with the proporiton of intermediate consumers such that, at low proportions,
@@
 
-As with the proportion of basal resources, link density, generality, and
+As with the proportion of basal resources; link density, generality, and
 vulnerability decreased as the proportion of top predators increased. For
@@
 stream and terrestrial food webs, the decrease in link density and
-vulnerability was steeper towards the poles, although this trend was
+vulnerability was less sharp towards the poles, although this trend was
 significant only in streams ($\beta_{Latitude:Stream}$=0.015,

### 2015-04-13 code/byTL_Models.R
Updated with natural logs

@@ -10,8 +10,8 @@ library(MuMIn)
 ##############################################################################################
 ##############################################################################################
 
-# infile='../non_TS/summary-properties.tsv'
-infile='../mod_data/summary-properties.tsv'
+infile='../non_TS/summary-properties.tsv'
+# infile='../mod_data/summary-properties.tsv'
 format='proportions'
 # format='numbers'
 

### 2015-04-13 manuscript/latitudepaper.tex
Updated betas

@@
 Link density, generality, and vulnerability each increased with increasing
-species richness (Fig.~\ref{S}; $\beta_0$=0.745, $p$\textless0.001; $\beta_0$=0.675,
-$p$\textless0.001; and $\beta_0$=0.745, $p$\textless0.001 respectively).  For estuarine,
+species richness (Fig.~\ref{S}; $\beta_0$=0.666, $p$\textless0.001; $\beta_0$=0.623,
+$p$\textless0.001; and $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine,
 marine, and terrestrial food webs this increase did not vary with latitude
-($\beta_{Latitude}$=-0.001, $p$=0.334 for link density; $\beta_{Latitude}$=-0.001, $p$=0.354 for generality;
-and $\beta_{Latitude}$=-0.001, $p$=0.334 for vulnerability). In lake food webs, link density,
+($\beta_{Latitude}$=-0.001, $p$=0.267 for link density; $\beta_{Latitude}$=-0.001, $p$=0.363 for generality;
+and $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability). In lake food webs, link density,
 generality, and vulnerability all increased more quickly towards the poles
-($\beta_{Latitude:Lake}$=0.004, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
+($\beta_{Latitude:Lake}$=0.005, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
 $p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
@@
 and vulnerability tended to increase with increasing proportions of
-intermediate consumers (Fig.~\ref{I}). The best-fit models for scaling of link
+intermediate consumers (Fig.~\ref{I}; ). The best-fit models for scaling of link
 density and vulnerability with the proportion of intermediate consumers did
@@
 ($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
-$\beta_{Latitude}$=-0.001, $p$=0.526 for vulnerability; the best-fit model for
+$\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the best-fit model for
 generality did not include any terms for latitude in any ecosystem type). In

### 2015-04-13 code/byTL_Models.R
Same change

@@ -10,8 +10,8 @@ library(MuMIn)
 ##############################################################################################
 ##############################################################################################
 
-# infile='../non_TS/summary-properties.tsv'
-infile='../mod_data/summary-properties.tsv'
+infile='../non_TS/summary-properties.tsv'
+#infile='../mod_data/summary-properties.tsv'
 format='proportions'
 # format='numbers'
 

### 2015-04-13 code/TL_scaleplots.py
Converting to ln figures

@@ -71,18 +71,18 @@ def heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat):
 
       # Correct the observed property based on latitude and ecotype effects
 
-      if 'log10('+key+'):'+ecotype in fixed_effects: 
-        delta=fixed_effects['log10('+key+'):'+ecotype]
+      if 'log('+key+'):'+ecotype in fixed_effects: 
+        delta=fixed_effects['log('+key+'):'+ecotype]
       else:   # If there's no intercept effect of ecosystem
         delta=0
 
-      if 'log10('+key+'):Latitude' in fixed_effects:
-        if 'log10('+key+'):'+ecotype+':Latitude' in fixed_effects:
-         gamma=fixed_effects['log10('+key+'):Latitude']+fixed_effects['log10('+key+'):'+ecotype+':Latitude'] 
-        elif 'log10('+key+'):Latitude:'+ecotype in fixed_effects:
-          gamma=fixed_effects['log10('+key+'):Latitude']+fixed_effects['log10('+key+'):Latitude:'+ecotype]
+      if 'log('+key+'):Latitude' in fixed_effects:
+        if 'log('+key+'):'+ecotype+':Latitude' in fixed_effects:
+         gamma=fixed_effects['log('+key+'):Latitude']+fixed_effects['log('+key+'):'+ecotype+':Latitude'] 
+        elif 'log('+key+'):Latitude:'+ecotype in fixed_effects:
+          gamma=fixed_effects['log('+key+'):Latitude']+fixed_effects['log('+key+'):Latitude:'+ecotype]
         else:  #If there's no lat-by-ecotype interaction
-          gamma=fixed_effects['log10('+key+'):Latitude'] 
+          gamma=fixed_effects['log('+key+'):Latitude'] 
       else: # If there's no latitude effect at all
         gamma=0
 
@@ -133,22 +133,22 @@ def predictionreader(predfile,TL,Bformat):
 
       if Bformat=='proportions':
         if TL=='B':
-          predpoints[ecotype][Lat].append((B,10**pred))
+          predpoints[ecotype][Lat].append((B,math.exp(pred)))
         elif TL=='I':
-          predpoints[ecotype][Lat].append((I,10**pred))
+          predpoints[ecotype][Lat].append((I,math.exp(pred)))
         elif TL=='T':
-          predpoints[ecotype][Lat].append((T,10**pred))
[…]

### 2015-04-13 code/TL_scaling_justlines.py

@@ -59,22 +59,22 @@ def predictionreader(predfile,TL,Bformat):
 
       if Bformat=='proportions':
         if TL=='B':
-          predpoints[ecotype][Lat].append((B,10**pred))
+          predpoints[ecotype][Lat].append((B,math.log(pred)))
         elif TL=='I':
-          predpoints[ecotype][Lat].append((I,10**pred))
+          predpoints[ecotype][Lat].append((I,math.log(pred)))
         elif TL=='T':
-          predpoints[ecotype][Lat].append((T,10**pred))
+          predpoints[ecotype][Lat].append((T,math.log(pred)))
         elif TL=='S':
-          predpoints[ecotype][Lat].append((S,10**pred))
+          predpoints[ecotype][Lat].append((S,math.log(pred)))
       else:
         if TL=='B':
-          predpoints[ecotype][Lat].append((B*S,10**pred))
+          predpoints[ecotype][Lat].append((B*S,math.log(pred)))
         elif TL=='I':
-          predpoints[ecotype][Lat].append((I*S,10**pred))
+          predpoints[ecotype][Lat].append((I*S,math.log(pred)))
         elif TL=='T':
-          predpoints[ecotype][Lat].append((T*S,10**pred))
+          predpoints[ecotype][Lat].append((T*S,math.log(pred)))
         elif TL=='S':
-          predpoints[ecotype][Lat].append((S*S,10**pred))
+          predpoints[ecotype][Lat].append((S*S,math.log(pred)))
 
 
   f.close()

### 2015-05-12 manuscript/coverletter.tex
A shell

\documentclass[12pt]{letter}

\usepackage[britdate,alyssa-signature]{canterbury-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{PhD Candidate}
\department{School of Biological Sciences}
\location{Private Bag 4800}
\telephone{+64 3 364 2729}
\fax{+64 3 364 2590}
\email{alyssa.cirtwill@pg.canterbury.ac.nz}
\url{http://stoufferlab.org}
\name{Alyssa R. Cirtwill}

% \position{PhD student}
% \department{School of Biological Sciences}
% \location{Private Bag 4800}
% \telephone{+64 3 364 2729}
% \fax{+64 3 364 2590}
% \email{alyssa.cirtwill@pg.canterbury.ac.nz}
% \url{http://stoufferlab.org}
% \name{Ms. Alyssa R. Cirtwill}

\newcommand{\mytitle}{\emph{Title title title}}
\newcommand{\myjournal}{\emph{Proceedings of the Royal Society B}}

\begin{document}

\begin{letter}{{\bf RE: \mytitle\\
               ~~~~~~~Cirtwill, Alyssa R; Stouffer, Daniel B; Romanuk, Tamara N\\
               \vspace*{20pt}
               Professor Spencer C.H. Barrett\\
               Editor-in-Chief, Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Prof. Barrett:}

We are happy to invite you to consider our manuscript 
``\mytitle'' for publication in the Theoretical Biology section of the \emph{\myjournal}.

We believe that our study

Thank you again for your consideration of our manuscript.

\closing{Regards,}

\end{letter}

% \newpage

% \setcounter{page}{1}

\end{document}

### 2015-05-12 manuscript/coverletter.tex
First paragraph roughed out

@@
 
-We believe that our study
+We believe that our study will be of general interest to the readership of \emph{\myjournal}} because it deals with the general scaling relationships between the distribution of trophic interactions within a community, species richness, and latitude.
+We assess these relationships both across several ecosystem types and over different trophic levels.
+Our results will therefore be applicable to researchers working with a wide variety of study systems and focal species.
+
+[[A second paragraph going into more detail]]
 

### 2015-05-18 manuscript/latitudepaper.tex
Need to check a few of these references in my thesis

@@
   %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
-  Food webs --networks of feeding links between species-- have been used for over a century to summarize the structure of 
-  ecological communities \citep{Williams2000,earlierwork} and to understand how that structure relates to environmental variables 
-  such as land use [[lets really consider the three env variables used here.
-there really is not a lot of work on land use....i get why prim prod and climate are included....maybe focus on habitat types since you focus on habitats in the analysis]] \citep{Townsend1998,Townsend2004c,Digel2014}, primary productivity \citep{}, and climate\citep{}.
-The latter
+  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
+  ecological communities \citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
+  such as habitat type \citep{Shurin2006,Briand1983}, primary productivity \citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate\citep{Baiser2012,Petchey2010}. The latter
   variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
-  climate is more variable at high latitudes \citep{}.
-[[maybe climatic regimes?
-the issue is that there really are not a lot of studies that look at these things.....]] These variables affect both the resources available and species'
-  metabolisms~\citep{Stegen2012}, and have been proposed as determinants of the strength of 
-  interspecific interactions~\citep{Marquis2005,Schemske2009}. 
+  climate is more variable at high latitudes \citep{mappaper}. These variables affect both the resources available and species' 
+  metabolisms~\citep{,Hechinger2011}, and have been proposed as determinants of the strength of 
+  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
   By modulating interactions between species, latitudinal gradients may also shape food-web structure.
   Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
-  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,,}.
+  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,Macpherson2002,Kaufman1995}.
 
@@
   there should be other effects of latitudinal gradients on food-web structure. Attempts to unravel these effects, however,
-  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}[[Check that I don't say that richness causes structural effects elsewhere]].
-In particular,
+  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. In particular,
   narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,

### 2015-05-18 manuscript/latitudepaper.tex
found a couple more refs

@@
   Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
-  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,Macpherson2002,Kaufman1995}.
+  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}.
 

### 2015-05-18 manuscript/latitudepaper.tex
not sure what I changed

--- 2015-04-13 manuscript/latitudepaper.tex
@@
 \vspace{0.4 in}
+
+\section*{Abstract}
+
+Several properties of food webs---the networks of feeding links between
+species---vary systematically with the species richness of the underlying
+community.  Under the ``latitude-niche breadth hypothesis'', which predicts
+that species in the tropics will tend to evolve narrower niches, one might
+expect that these scaling relationships could also be affected by latitude. To
+test this hypothesis, we analysed the scaling relationships between species
+richness and average generality, vulnerability, and links per species across a
+set of 163 empirical food webs.  We also investigated scaling relationships
+between the three food-web properties and the proportions of the web made up
+by basal resources, intermediate consumers, and top predators. While we
+observed no effect of latitude on scaling relationships in the estuarine,
+marine, and terrestrial food webs, there were strong effects of latitude on
+scaling relationships in the freshwater food webs. [[Need MUCH stronger justification for these... In lakes, this trend is
+driven by increasing generality in high-latitude top predators while in
+streams this trend appears to be driven by greater proportions of basal
+resources in polar communities. Our results therefore provide partial support
+the latitude-niche breadth hypothesis but also suggest that it may have
+limited applicability in many empirical ecosystems. ]]
 

### 2015-05-18 manuscript/latitudepaper.tex
I can has conclusions

@@
 marine, and terrestrial food webs, there were strong effects of latitude on
-scaling relationships in the freshwater food webs. [[Need MUCH stronger justification for these... In lakes, this trend is
-driven by increasing generality in high-latitude top predators while in
-streams this trend appears to be driven by greater proportions of basal
-resources in polar communities. Our results therefore provide partial support
-the latitude-niche breadth hypothesis but also suggest that it may have
-limited applicability in many empirical ecosystems. ]]
+scaling relationships in the freshwater food webs. In these communities,
+the latitude-niche breadth hypothesis appears to hold true while in other habitat
+types niches appear to be broader in the tropics. These contrasting findings
+indicate that it is important to account for habitat type when exploring gradients
+in food-web structure.
 
-\section*{Introduction} [[Add something about ecosystem type since it's in the methods]]
+\section*{Introduction}
 
@@
   Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
-  ecological communities \citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
-  such as habitat type \citep{Shurin2006,Briand1983}, primary productivity \citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate\citep{Baiser2012,Petchey2010}. The latter
+  ecological communities~\citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
+  such as habitat type~\citep{Shurin2006,Briand1983}, primary productivity~\citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate~\citep{Baiser2012,Petchey2010}. The latter
   variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
-  climate is more variable at high latitudes \citep{mappaper}. These variables affect both the resources available and species' 
+  climate is more variable at high latitudes~\citep{mappaper}. These variables affect both the resources available and species' 
   metabolisms~\citep{,Hechinger2011}, and have been proposed as determinants of the strength of 
   interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
-  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
+  By modulating interactions between species, latitudinal gradients may also shape food-web structure~\citep{}.
   Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
-  latitudinal gradient in species richness, one of the most general and robust patterns in ecology \citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}.
+  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}.
 
@@
   turn should evolve smaller niches \citep{Vazquez2004}. These narrow niches should therefore allow more species to 
-  coexist in the tropics than at higher latitudes. Alternatively, higher productivity of the tropics \citep{Brown2004}
-  may result in a broader niche space \citep{Davies2007} which could also allow greater diversification even if niche 
-  sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocably 
+  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics \citep{Brown2004}
+  may result in a broader niche space \citep{Davies2007} which could also sustain greater biodiversity even if niche 
+  sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocally 
   supported \citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
@@
 
-  If decreased seasonality or higher productivity is the cause of higher species-richness in the tropics, then 
-  there should be other effects of latitudinal gradients on food-web structure. Attempts to unravel these effects, however,
-  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. In particular,
+  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
+  degree of specialization (i.e., niche breadth) of species within food webs.
+  Attempts to unravel these effects, however,
+  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
+  For example,
   narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,
@@
   similar whether or not redundant species are included. For simplicity, we present only
-  the results for the original webs in the main text.
+  the results for the original webs.
 
@@
   we first examined simple linear relationships between latitude and each of 
-  $S$, $Z$, $G$, $V$, $B$, $I$, and $T$. We fit models of the form
+  species richness, links per species, generality, vulnerability, and proportions
+  of basal resources, intermediate consumers, and top predators. We fit models of the form
 
@@
   We next calculated the AIC
-  of the maximal model, as well as the AIC's of a suite of candidate simplified models identified
+  of the maximal model as well as the AIC's of a suite of candidate simplified models identified
   using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
@@
   Next, we examined the form of the scaling relationship between each 
-  property ($Z$, $G$, and $V$) and $S$. The scaling relationship between $Z$ and 
-  $S$ has been shown to be a power law \citep{Riede2010} of the form
+  property (links per species, generality, and vulnerability) and 
+  species richness. The scaling relationship between links per species ($Z$) and 
+  species richness ($S$) has been shown to be a power law \citep{Riede2010} of the form
 
@@
 
-  Although scaling relationships between $S$ and $G$ or $S$ and $V$ have not been explicitly examined (but see scaling 
+  Although scaling relationships between species richness and generality or
+  species richness and vulnerability have not been explicitly examined (but see scaling 
   relationships for the standard devaitions of each property in \citet{Riede2010}), we expect that they will follow
-  power laws similar to that of the relationship between $S$ and $Z$. This is because the links taken into account in
-  calculating $G$ and $V$ are subsets of the total links included when calculating $Z$. As with $Z$, we explicitly 
-  compared the error distributions of models for $G$ and $V$ using both the power-law and logarithmic formulations. 
+  power laws similar to that of the relationship between species richness and links per species.
+  This is because the links taken into account in calculating generality and vulnerability are subsets 
+  of the total links included when calculating links per species. As with links per species, we explicitly 
+  compared the error distributions of models for generality and vulnerability using
+  both the power-law and logarithmic formulations. 
   In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
@@
   We then assessed the impact of latitude on the scaling relationships between species richness and 
-  link density, generality, vulnerability.
-  [[If the species-rich tropics truly have narrower 
-  niches~\citep{Brown2004}, then we would expect to see less increase in mean numbers of links, 
-  predators, and prey with increasing species richness in the tropics. ]]
-  In the context of the scaling relationships above, note that this implies that we aim to determine the effect of latitude on
+  link density, generality, vulnerability. In the context of the scaling relationships above, note 
+  that this implies that we aim to determine the effect of latitude on
   the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
@@
   that end, we repeated all of the above analyses replacing species richness by
-  proportion of basal resources $B$, proportion of intermediate consumers $I$,
-  or proportion of top predators $T$. All model fitting and model
+  proportion of basal resources, proportion of intermediate consumers,
+  or proportion of top predators. All model fitting and model
   simplification procedures were identical to those described for species
@@
   ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
-  relationship was robust to the removal of three outliers (based on Cook's Distance). In the best-fit versions of
-  equation~(\ref{Latfull}) for link density and vulnerability, there were once again
-  significant relationships with latitude in stream food webs, but after the removal of three outliers these trends
-  were no longer significant. Link density and vulnerability did not vary with latitude in any other ecosystem type.
-  Similarly, the best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
+  relationship was robust to the removal of three outliers (based on Cook's Distance). 
+  There were also relationships between latitude and link density and latitude and vulnerability
+  in stream food webs, but these trends were non-signficant after the removal of three outliers.
+  Link density and vulnerability did not vary with latitude in any other ecosystem type.
+  The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
   latitude in any ecosystem type.
 
-  The relationships between the proportions of species at each trophic level with latitude were broadly similar
-  to the relationship between species richness and latitude. 
+  The relationships between latitude and the proportions of species at each trophic level were broadly similar
+  to the relationship between latitude and species richness. 
   The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
@@
 
-  When considering the relationships between species richness and proportions 
-  of basal resources, intermediate consumers, and top predators and all response variables 
+  When considering the relationships between species richness or the proportions 
+  of basal resources, intermediate consumers, or top predators and all response variables 
   (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
@@
   ($\beta_{Latitude:Lake}$=0.005, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
-$p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively) In
+  $p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively). In
   stream food webs generality increased more rapidly towards the poles 
@@
   The tendency of food-web structure to exhibit scaling relationships with
-species richness has been well-established \citep{Dunne2004,Riede2010}. As
+  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
   species richness in particular is also known to vary systematically over
-latitude \citep{}, intuitively one might suspect that any relationship
+  latitude~\citep{}, intuitively one might suspect that any relationship
   between food-web properties such as generality might be due to the latitudinal
@@
   The lack of latitudinal gradients in food-web properties in this dataset contrasts
-strongly with other studies which have found consistent variation in species richness,
-[[other properties]] \citep{}. As numbers of species and links included in a food web
+  strongly with other studie~\citep{}. As numbers of species and links included in a food web
   vary strongly with sampling effort as well as with the underlying diversity of the study
@@
   systematically with temperature and productivity but that the niche space
-might be larger in species-rich communities~\citep{Davies2007}. In lake food
-webs, in contrast, scaling of each property was much stronger in high-latitude
-food webs. In stream food webs, scaling of links per species and vulnerability
-varied little over latitude while scaling of generality was stronger in high-
-latitude food webs. This means that species in trophical freshwater
+  might be larger in species-rich communities~\citep{Davies2007}. Rather than
+  niche space depending on temperature and productivity, it may be that species
+  diversity itself affects the niche space available to species (although climate
+  may affect speciation rates and therefore the diversity in a region~\citep()).
+
+  Unlike other ecosystem types, in lake and stream food webs 
+  the scaling of generality was stronger in higher-latitude food webs. 
+  In lake food webs, this trend was echoed in the scaling relationships
+  between species richness and links per species and vulnerability.
+  This means that species in tropical freshwater
   communities gain fewer additional feeding links per additional species in the
-web and is consistent with the hypothesis that greater stability in the
-tropics leads to narrower niches~\citep{Brown2004} and a higher proportion of
-specialists~\citep{}.
-
-In lake food webs, species in tropical food webs also gained fewer predators,
-and therefore fewer links overall. Conversely, for species in high-latitude
-food webs numbers of predators, prey, and links per species all increased
-rapidly with increasing species richness.
-As there were proportionally fewer top predators in high-latitude lakes yet
-generality, vulnerability, and links per species all increased more rapidly than
-near the equator, it appears that high-latitude predators are more likely to be 
-generalists. This may reflect prey switching as
-different food sources become available in different seasons~\citep{}.
-
-Surprisingly species in high-latitude stream food webs, while gaining many
-additional prey species per additional species in the food web, did not
-receive any more predators or links than species in low-latitude streams. 
-This may be partly due to the increasing proportion of the food web made up of
-basal resources at higher latitudes. If any additional species is more likely to
-be a basal resource at high latitudes, it will have predators but no prey.
-Combined with the potential for prey-switching between seasonal resources, this 
-could account for the sharper increase in generality with increasing species richness
-in high-latitude streams. Vulnerability and mean links per species, on the other hand,
-increased at the same rate across latitude. [[Still working on why]]
+  web and that species in tropical lakes also gain fewer predators, and fewer links
+  in general, per additional species. These trends are consistent with the hypothesis
+  that greater stability in the tropics leads to narrower niches~\citep{Brown2004} and a higher proportion of
+  specialists, as has been observed in mutualist networks~\citep{}. Inhabitants of high-latitude
+  freshwater communities may also be more generalist due to prey switching if they rely on a series
+  of ephemeral prey such as maturing insect larvae~\citep{}.
 
@@
 
-% Our results were consistent with the latitude-niche breadth hypothesis, but only in certain ecosystem
-% types. This suggests that different types of food webs respond differently to differences in climate
-% driven by latitudinal gradients. [[A sentence or two explaining why this is important.]]
+  Our results were consistent with the latitude-niche breadth hypothesis in estuarine, marine,
+  and terrestrial communities but instead consistent with the hypothesis of greater specialization
+  in the tropics in stream and lake food webs. This suggests that different mechanisms may structure
+  food webs in different habitat types and that freshwater food webs in particular may be strongly
+  affected by seasonal variation. In addition, different relationships between latitude and niche
+  breadth in different habitat types goes some way towards explaining the equivocal support for
+  the opposing hypotheses of~\citet{Brown2004} and ~\citet{Davies2007}; both have merit but appear
+  to apply to different systems.
 

### 2015-05-19 manuscript/latitudepaper.tex
This should be all the refs

@@
   variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
-  climate is more variable at high latitudes~\citep{mappaper}. These variables affect both the resources available and species' 
-  metabolisms~\citep{,Hechinger2011}, and have been proposed as determinants of the strength of 
+  climate is more variable at high latitudes~\citep{Field1998}. These variables affect both the resources available and species' 
+  metabolisms~\citep{Hechinger2011,OConnor2009,White2009,}, and have been proposed as determinants of the strength of 
   interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
@@
 
-  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\citep{,Vazquez2004}. 
+  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\citep{Vazquez2004}. 
   This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
-  turn should evolve smaller niches \citep{Vazquez2004}. These narrow niches should therefore allow more species to 
-  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics \citep{Brown2004}
-  may result in a broader niche space \citep{Davies2007} which could also sustain greater biodiversity even if niche 
+  turn should evolve smaller niches~\citep{Vazquez2004}. These narrow niches should therefore allow more species to 
+  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics~\citep{Brown2004}
+  may result in a broader niche space~\citep{Davies2007} which could also sustain greater biodiversity even if niche 
   sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocally 
-  supported \citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
-  richness \citep{Lappalainen2006,Krasnov2008,Slove2010}.
+  supported~\citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
+  richness~\citep{Lappalainen2006,Krasnov2008,Slove2010}.
 
@@
   For example,
-  narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{}). However,
+  narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{Dyer2007,Marra1997} but see~\citep{Schleuning2012}). However,
   average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
@@
   possible or, where study sites were described but exact coordinates were not
-  given, obtained estimated coordinates using Google Earth \citep{GoogleEarth}.
+  given, obtained estimated coordinates using Google Earth~\citep{GoogleEarth}.
   We then divided the species in each web into basal resources (those species with
@@
   Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
-  sets to form ``trophic species'' webs (e.g. ~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
+  sets to form ``trophic species'' webs (e.g.~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
   is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
@@
   species richness. The scaling relationship between links per species ($Z$) and 
-  species richness ($S$) has been shown to be a power law \citep{Riede2010} of the form
+  species richness ($S$) has been shown to be a power law~\citep{Riede2010} of the form
 
@@
   multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
-  over another, we follow the recommendations in \citet{Xiao2011} and compared the two
+  over another, we follow the recommendations in~\citet{Xiao2011} and compared the two
   model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
@@
   species richness and vulnerability have not been explicitly examined (but see scaling 
-  relationships for the standard devaitions of each property in \citet{Riede2010}), we expect that they will follow
+  relationships for the standard devaitions of each property in~\citet{Riede2010}), we expect that they will follow
   power laws similar to that of the relationship between species richness and links per species.
@@
   species richness in particular is also known to vary systematically over
-  latitude~\citep{}, intuitively one might suspect that any relationship
+  latitude~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}, intuitively one might suspect that any relationship
   between food-web properties such as generality might be due to the latitudinal
@@
 
-  The lack of latitudinal gradients in food-web properties in this dataset contrasts
-  strongly with other studie~\citep{}. As numbers of species and links included in a food web
+  The lack of a latitudinal gradient in species richness in this dataset contrasts
+  strongly with other studies~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
   vary strongly with sampling effort as well as with the underlying diversity of the study
@@
   than species-poor arctic communities. In addition, it is worth noting that gradients in
-  species richness are generally measured for a single taxonomic group at a time~\citep{}.
+  species richness are generally measured for a single taxonomic group at a time (e.g.~\citep{Kaufman1995}).
   It is possible that these taxa are not well-represented in our food webs and that the
@@
   diversity itself affects the niche space available to species (although climate
-  may affect speciation rates and therefore the diversity in a region~\citep()).
+  may affect speciation rates and therefore the diversity in a region~\citep{Currie2004}).
 
@@
   that greater stability in the tropics leads to narrower niches~\citep{Brown2004} and a higher proportion of
-  specialists, as has been observed in mutualist networks~\citep{}. Inhabitants of high-latitude
-  freshwater communities may also be more generalist due to prey switching if they rely on a series
-  of ephemeral prey such as maturing insect larvae~\citep{}.
+  specialists. This may be partly due to high-latitude species
+  tending to switch between different seasonally-available
+  prey~\citep{Isaac2012,Wilhelm1999} while tropical freshwater ecosystems may have more stable composition.
 

### 2015-05-20 manuscript/latitudepaper.tex
Got citations sorted out, waiting for DBS comments

@@
   Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
-  ecological communities~\citep{Petchey2008,Williams2000,Paine1980} and to understand how that structure relates to environmental variables 
+  ecological communities~\citep{Petchey2008,Williams2000,Paine1966} and to understand how that structure relates to environmental variables 
   such as habitat type~\citep{Shurin2006,Briand1983}, primary productivity~\citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate~\citep{Baiser2012,Petchey2010}. The latter
@@
   climate is more variable at high latitudes~\citep{Field1998}. These variables affect both the resources available and species' 
-  metabolisms~\citep{Hechinger2011,OConnor2009,White2009,}, and have been proposed as determinants of the strength of 
+  metabolisms~\citep{Hechinger2011,White2011,OConnor2009,White2007}, and have been proposed as determinants of the strength of 
   interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
-  By modulating interactions between species, latitudinal gradients may also shape food-web structure~\citep{}.
+  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
   Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
-  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}.
+  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009a,Macpherson2002,Kaufman1995}.
 
@@
   species richness in particular is also known to vary systematically over
-  latitude~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}, intuitively one might suspect that any relationship
+  latitude~\citep{Schemske2009a,Macpherson2002,Kaufman1995}, intuitively one might suspect that any relationship
   between food-web properties such as generality might be due to the latitudinal
@@
   The lack of a latitudinal gradient in species richness in this dataset contrasts
-  strongly with other studies~\citep{Schemske2009a,Stegen2009,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
+  strongly with other studies~\citep{Schemske2009a,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
   vary strongly with sampling effort as well as with the underlying diversity of the study
@@
 \bibliographystyle{jae}%Compile with jae.bst style file
-\bibliography{noISN.bib}% your .bib file(s)
+\bibliography{noISN}% your .bib file(s)
 

### 2015-05-20 manuscript/latitudepaper.tex
Some DBS comments

@@
 
-\title{Generality in food webs scales with species richness, not latitude}
-\author{Alyssa Cirtwill, Daniel Stouffer, Tamara Romanuk}
+\title{Generality in food webs scales with species richness not not with latitude}
+\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
 \date{$^1$School of Biological Sciences\\University of Canterbury\\
 Private Bag 4800\\Christchurch 8140, New Zealand}
+\medskip$^2$Department of Biology\\Life Science Centre\\
+Dalhousie University\\1355 Oxford St.\\P0 BOX 15000\\
+Halifax, NS B3H 4R2\\Canada\\}
 

### 2015-06-10 manuscript/latitudepaper.tex
Updates from travelling
fixed merge remotely
All DBS comments are now incorporated

@@
 
-\title{Generality in food webs scales with species richness not not with latitude}
+\title{Generality in food webs scales with species richness but not with latitude}
 \author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
@@
 marine, and terrestrial food webs, there were strong effects of latitude on
-scaling relationships in the freshwater food webs. In these communities,
-the latitude-niche breadth hypothesis appears to hold true while in other habitat
+scaling relationships in the freshwater food webs. In these communities, the
+latitude-niche breadth hypothesis appears to hold true while in other habitat
 types niches appear to be broader in the tropics. These contrasting findings
-indicate that it is important to account for habitat type when exploring gradients
-in food-web structure.
+indicate that it may be more important to account for habitat than latitude
+when exploring gradients in food-web structure.
 
@@
     species).
-
-  % [[list in supplemental (347 GlobalWeb webs \citep{GlobalWeb}), supplemented 
-  % with 31 food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
-  % and seven food webs used to study the impact of parasites on network structure (ParWebs \citep{Dunne2013}).
-  % Of the GlobalWeb webs, 122 were rejected because their original source could not be found or was unpublished (53), they were source or sink
-  % webs rather than descriptions of an entire community (13), were focused on plant-pollinator, host-parasitoid, or 
-  % competitive interactions (8, 34, and 2, respectively), described inferred interactions in an extinct community (2), were ``generalized 
-  % schemes'' rather than being based on empirical observation (8), or because it was not clear which of a variety of 
-  % described sites the published food web represented (2). (See Table S1 for a list of rejected webs and reasons for their
-  % exclusion.) For three GlobalWeb webs which included parasites as a minor component of the community, as well as the 
-  % seven ParWebs webs, we included a modified version of each web which included only free-living species and the 
-  % interactions between them \citep{Dunne2013}. 
-  % As we were considering the log of proportions of basal resources, top predators, and intermediate consumers, each web used in our analysis 
-  % had to have at least one species in each trophic group.
-
-  % of  the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
-  % \citep{}. Of these, 302 webs had accessible original sources. 
-  % 18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
-  % to have different food web properties than webs attempting to
-  % describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
-  % competition-focused networks
-  % \citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
-  % between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
-  % \citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
-  % we wished to measure
-  % directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
-  % the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
-  % \citep{Vinogradov1978}, such that it is not clear which site the food web represents. 
-  % This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans.
 
@@
     and $\beta_{Latitude:Marine}$=0.009, $p$=0.047 respectively),
-  while in terrestrial food webs link density, generality, and vulnerability
+    while in terrestrial food webs link density, generality, and vulnerability each
     decreased more gradually towards the 
@@
   It is possible that these taxa are not well-represented in our food webs and that the
-  dominant taxa in them do not have an underlying latitudinal gradient in richness. In
-  either case, the lack of association between species richness
-  and latitude in any ecosystem type nevertheless means that any effect of latitude on scaling relationships
-  between species richness and other properties is not being driven by underlying variation in
-  species richness, allowing us to more clearly assess effects of latitude on scaling with 
-  species richness and proportions of species in different trophic levels.
+  dominant taxa in them do not have an underlying latitudinal gradient in richness. 
+  In either case, the lack of a strong association between
+  species richness and latitude in any ecosystem type
+  means that any effect of latitude on other scaling 
+  relationships is not being driven by an underlying 
+  latitudinal gradient in species richness.
+  The lack of confounding effects of latitude allows us to 
+  more clearly assess effects of latitude on scaling with 
+  species richness and proportions of species in different 
+  trophic levels.
 
@@
   may affect speciation rates and therefore the diversity in a region~\citep{Currie2004}). 
+  For example, as plant diversity increases both the 
+  variety of food available to herbivores and the structural variety of the habitat will also increase.
 
-  Unlike other ecosystem types, in lake and stream food webs 
-  the scaling of generality was stronger in higher-latitude food webs. 
+  Unlike other ecosystem types, the scaling of generality
+  in lake and stream food webs was stronger (i.e., 
+  increased more steeply) in higher-latitude food webs. 
   In lake food webs, this trend was echoed in the scaling relationships
@@
   in general, per additional species. These trends are consistent with the hypothesis
-  that greater stability in the tropics leads to narrower niches~\citep{Brown2004} and a higher proportion of
+  that greater stability in the tropics leads to narrower niches~\citep{Vazquez2004} and a higher proportion of
   specialists. This may be partly due to high-latitude species
@@
 
-  Our results were consistent with the latitude-niche breadth hypothesis in estuarine, marine,
-  and terrestrial communities but instead consistent with the hypothesis of greater specialization
+  Our results were inconsistent with the latitude-niche breadth hypothesis in estuarine, marine,
+  and terrestrial communities but consistent with the hypothesis of greater specialization
   in the tropics in stream and lake food webs. This suggests that different mechanisms may structure
@@
   breadth in different habitat types goes some way towards explaining the equivocal support for
-  the opposing hypotheses of~\citet{Brown2004} and ~\citet{Davies2007}; both have merit but appear
+  the opposing hypotheses of narrower niches in the tropics~\citep{Vazquez2004} and broader 
+  niche space in the tropics~\citep{Davies2007}; both have merit but appear
   to apply to different systems.
@@
 \bibliography{noISN}% your .bib file(s)
-
-\newpage
-
-% \section*{Tables}
-
-% \begin{table}[!h]
-% \caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude.
-Note that none
-% of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. Each `NA' indicates a term that was not included in the corresponding best-fit model.}
-% \label{Latlms}
-% \begin{tabular}{l | l l  l l  l l  l l}
-
-% \hline
-% \multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
-% & $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
-% \hline
-% Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
-% Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
-% Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
-% Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
-% \hline
-% \end{tabular}
-% \end{table}
-
-% \begin{table}[!h]
-% \caption{Intercepts and slopes for the best-fitting model describing the relationship between species-richness, mean links per species, mean generality, and mean vulnerability and latitude in trophic-species versions of food webs.
-Note that none
-% of the best-fitting models included a term for latitude or an interaction between latitude and ecosystem type. `NA' a term that was not included in the corresponding best-fit model.}
-% \label{Latlms}
-% \begin{tabular}{l | l l  l l  l l  l l}
-
-% \hline
-% \multirow{2}{*}{Property} & \multicolumn{2}{|c}{Intercept} & \multicolumn{2}{|c}{Stream} & \multicolumn{2}{|c}{Lake} & \multicolumn{2}{|c}{Terrestrial}\\
-% & $\alpha_{0}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ & $p$-value & $\alpha_{2}$ &$p$-value\\
-% \hline
-% Species richness  & 34.6 & \textless0.001 & 22.4 & 0.167 \textless0.001 & NA & NA & NA & NA \\
-% Links per species & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
-% Generality        & 7.32 & \textless0.001 & NA & NA & -1.98 & 0.044 & -3.77 & \textless0.001 \\
-% Vulnerability     & 3.53 & \textless0.001 & NA & NA & NA & NA & NA & NA \\
-% \hline
-% \end{tabular}
-% \end{table}
-
-% \begin{table}[!h]
-% \caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness.
-Each `NA' indicates a term that was not included in the corresponding best-fit model.
-These models refer to the original versions of food webs.
-}
-% \label{Bestfits}
-% \begin{tabular}{l | l l  l l  l l }
-% Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
-%                 & \multicolumn{2}{c}{Vulnerability}\\
-%                 & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
-% \hline
-% Intercept               &-0.453 & \textless0.001 & -0.249 & \textless0.001 & -0.453 & \textless0.001 \\
-% log(species)            & 0.419 & \textless0.001 &  0.663 & \textless0.001 &  0.419 & \textless0.001 \\
-% log(species):Lake       & 0.119 & \textless0.001 & -0.185 & 0.016          &  0.119 & \textless0.001 \\
-% log(species):Marine     & 0.255 & \textless0.001 &  0.090 & 0.002          &  0.255 & \textless0.001 \\
-% log(species):Terrestrial& 0.207 & 0.002          & -0.122 & \textless0.001 &  0.207 & 0.002 \\
-% log(species):Latitude   & 0.004 & \textless0.001 & -0.001 & 0.199          &  0.003 & \textless0.001 \\
-% log(species):Latitude:Marine&-0.004 & 0.007      &  NA    &  NA            & -0.005 & 0.007 \\
-% log(species):Latitude:Terrestrial&-0.005 & 0.002 &  NA    &  NA            & -0.005 & 0.002 \\
-% log(species):Latitude:Lake & NA & NA             &  0.006 & 0.002          &  NA    & NA    \\
-% \hline
-% $R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
-% \hline
-% \end{tabular}
-% \end{table}
-
-% \begin{table}[!h]
-% \caption{Intercepts and slopes for best-fit models describing the effect of latitude on the scaling of mean links per species, mean generality, and mean vulnerability with species richness.
-Each `NA' indicates a term that was not included in the corresponding best-fit model.
-These models refer to the trophic species versions of food webs.
-}
-% \label{Bestfits}
-% \begin{tabular}{l | l l  l l  l l }
-% Effect          & \multicolumn{2}{c|}{Links per species} & \multicolumn{2}{c|}{Generality} 
-%                 & \multicolumn{2}{c}{Vulnerability}\\
-%                 & $\beta$ & $p$-value     &  $\beta$ & $p$-value    &  $\beta$ & $p$-value  \\
-% \hline
-% Intercept               & -0.561 & \textless0.001 & -0.299 & \textless0.001 & -0.561 & \textless0.001 \\
-% log(species)            &  0.733 & \textless0.001 &  0.622 & \textless0.001 &  0.733 & \textless0.001 \\
-% log(species):Lake       & -0.118 & 0.047          & -0.115 & 0.078          & -0.118 & 0.047 \\
-% log(species):Marine     &  0.051 & 0.040          &  0.120 & \textless0.001 &  0.051 & 0.040 \\
-% log(species):Stream     & -0.161 & 0.014          & -0.057 & 0.421          & -0.161 & 0.014 \\
-% log(species):Latitude   & -0.001 & 0.081          & -0.001 & 0.273          & -0.001 & 0.081 \\
-% log(species):Lat:Lake   &  0.006 & \textless0.001 &  0.006 & \textless0.001 &  0.006 & \textless0.001 \\
-% log(species):Lat:Stream &  0.004 & 0.018          &  0.003 & 0.059          &  0.004 & 0.018 \\
-% \hline
-% $R^{2} (adjusted)$   & \multicolumn{2}{c|}{0.706} & \multicolumn{2}{c|}{0.658} & \multicolumn{2}{c}{0.706} \\
-% \hline
-% \end{tabular}
-% \end{table}
 

### 2015-06-14 manuscript/latitudepaper.tex
Abstract is single spaced for prettier fit

--- 2015-05-20 manuscript/latitudepaper.tex
@@
 \footskip 1.0cm
+\begin{document}
 
@@
 \date{$^1$School of Biological Sciences\\University of Canterbury\\
-Private Bag 4800\\Christchurch 8140, New Zealand}
-\medskip$^2$Department of Biology\\Life Science Centre\\
-Dalhousie University\\1355 Oxford St.\\P0 BOX 15000\\
-Halifax, NS B3H 4R2\\Canada\\}
+Private Bag 4800\\Christchurch 8140, New Zealand \\
+\medskip$^2$Department of Biology\\
+Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
+Halifax NS, B3H 4R2\\ Canada\\}
 
-\begin{document}
 \maketitle
@@
 
-\vspace{0.4 in}
+\vspace{0.3 in}
 
+\begin{spacing}{1.0}
 \section*{Abstract}
@@
 in food-web structure.
+\end{spacing}
 
@@
 predators (\% Top), and species richness of a food web. 
-For each relationship we show observed values corrected for
+For each relationship, we show observed values corrected for
 ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). }
@@
 \end{document}
+
+>>>>>>> 7787e1ad724c4c9aa740fb54fce5a4669c120daf

### 2015-06-14 manuscript/supplement.tex

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}
\usepackage[round]{natbib}
\usepackage{float}
\usepackage[running]{lineno}

% some cheats to reduce the need to type complicated bits and pieces
\newcommand{\expect}[1]{\left\langle #1 \right\rangle}
\newcommand{\etal}{\textit{et al.\ }}

\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

% the abstract formatting
\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

\renewcommand\refname{References}
% the abstract formatting

% margin sizes`
\topmargin 0.0cm
\oddsidemargin 0.2cm

% let's get some nature formatted citations
%\usepackage{overcite}
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

\title{Supplementary Information}
\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
\date{$^1$School of Biological Sciences\\University of Canterbury\\
Private Bag 4800\\Christchurch 8140, New Zealand}
\medskip$^2$Department of Biology\\Life Science Centre\\
Dalhousie University\\1355 Oxford St.\\P0 BOX 15000\\
Halifax, NS B3H 4R2\\Canada\\}

\begin{document}
\maketitle
\baselineskip=8.5mm
% \linenumbers

\vspace{0.4 in}
\beginsupplement
\begin{landscape}
\subsection*{Appendix S1: Details of Food Web Sources and Selection}

  [[list in supplemental (347 GlobalWeb webs \citep{GlobalWeb}), supplemented 
  with 31 food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
  and seven food webs used to study the impact of parasites on network structure (ParWebs \citep{Dunne2013}).
  Of the GlobalWeb webs, 122 were rejected because their original source could not be found or was unpublished (53), they were source or sink
  webs rather than descriptions of an entire community (13), were focused on plant-pollinator, host-parasitoid, or 
  competitive interactions (8, 34, and 2, respectively), described inferred interactions in an extinct community (2), were ``generalized 
  schemes'' rather than being based on empirical observation (8), or because it was not clear which of a variety of 
  described sites the published food web represented (2). (See Table S1 for a list of rejected webs and reasons for their
  exclusion.) For three GlobalWeb webs which included parasites as a minor component of the community, as well as the 
  seven ParWebs webs, we included a modified version of each web which included only free-living species and the 
  interactions between them \citep{Dunne2013}. 
  As we were considering the log of proportions of basal resources, top predators, and intermediate consumers, each web used in our analysis 
  had to have at least one species in each trophic group.

  of  the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
  \citep{}. Of these, 302 webs had accessible original sources. 
  18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
  to have different food web properties than webs attempting to
  describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
  competition-focused networks
  \citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
  between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
  \citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
  we wished to measure
  directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
  the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
  \citep{Vinogradov1978}, such that it is not clear which site the food web represents. 
  This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans.

\subsection*{Appendix S2: Supplemental Figures}

\newpage

\begin{figure}[H]
\includegraphics[width=.9\textwidth]{}
\caption{ }
\label{}
\end{figure}

\end{document}

### 2015-06-14 code/TL_latplots.py
Copied over the useful function and will alter it for raw plot.

@@ -1,293 +1,0 @@
-import sys
-import os
-import re
-import random
-from decimal import *
-import math
-
-from PyGrace.grace import Grace
-from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
-from PyGrace.dataset import SYMBOLS
-from PyGrace.Extensions.panel import Panel,MultiPanelGrace
-from PyGrace.drawing_objects import DrawText
-from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
-
-from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
-from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
-
-# Think I want plots of the raw data (S, LS, G, V vs. lat) with slope lines
-# Plus predictions for LS, G, V vs S (with corrected obs.)
-
-def datareader(rawdatafile):
-  points={'S':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
-  'LS':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
-  'Gen':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},  
-  'Vul':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
-  'B':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
-  'I':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]},
-  'T':{'Estuary':[],'Lake':[],'Marine':[],'Stream':[],'Terrestrial':[]}
-  }
-
-  f=open(rawdatafile,'r')
-  for line in f:
-    if line.split()[0]!='Web':
-      Latitude=float(line.split('\t')[6])
-      Species=int(line.split('\t')[7])
-      LS=float(line.split('\t')[10])
-      G=float(line.split('\t')[12])
-      V=float(line.split('\t')[14])
-      ecotype=line.split('\t')[1]
-      ecotype=ecotype.capitalize()
-      B=float(line.split('\t')[-4])
-      I=float(line.split('\t')[-2])
-      T=float(line.split('\t')[-1])
-
-      points['S'][ecotype].append((Latitude,Species))
-      points['LS'][ecotype].append((Latitude,LS))
[…]

### 2015-06-16 manuscript/coverletter.tex
A better draft

--- 2015-05-12 manuscript/coverletter.tex
@@
 
-We believe that our study
+We believe that our study will be of interest not only to theory-focused biologists but also to general readers
+of \emph{\myjournal}} as it deals with global trends in the structure of ecological communities. 
+Specifically, we address the impact of latitude and habitat type on known scaling relationships between empirical
+food-web structure and species richness. Although latitude (as a proxy for temperature, seasonality, and primary 
+productivity) is expected to drive trends in niche size (here measured as the number of feeding links for any 
+given species), we instead show that habitat type has the stronger influence on scaling between niche size and 
+species richness. This suggests that there may indeed be general rules governing the structure of food webs but 
+that these rules differ between different habitat types.
 
-Thank you again for your consideration of our manuscript.
+Our paper thus contributes to the discussions of both the latitude-niche-breadth hypothesis of () and scaling
+laws in food-web structure, as well as being potentially applicable to researchers exploring community 
+structure and specialization in a variety of different systems. We hope you will agree that this broad relevance
+and the novelty of our results justify our manuscript's inclusion in \emph{\myjournal}.
+
+Thank you again for your consideration.
 

### 2015-06-16 manuscript/supplement.tex
described where I got the webs, working on table

@@
 
-  [[list in supplemental (347 GlobalWeb webs \citep{GlobalWeb}), supplemented 
-  with 31 food webs used to study the relationship between consumer and resource body sizes (SizeWebs \citep{Brose2006})
-  and seven food webs used to study the impact of parasites on network structure (ParWebs \citep{Dunne2013}).
-  Of the GlobalWeb webs, 122 were rejected because their original source could not be found or was unpublished (53), they were source or sink
-  webs rather than descriptions of an entire community (13), were focused on plant-pollinator, host-parasitoid, or 
-  competitive interactions (8, 34, and 2, respectively), described inferred interactions in an extinct community (2), were ``generalized 
-  schemes'' rather than being based on empirical observation (8), or because it was not clear which of a variety of 
-  described sites the published food web represented (2). (See Table S1 for a list of rejected webs and reasons for their
-  exclusion.) For three GlobalWeb webs which included parasites as a minor component of the community, as well as the 
-  seven ParWebs webs, we included a modified version of each web which included only free-living species and the 
-  interactions between them \citep{Dunne2013}. 
-  As we were considering the log of proportions of basal resources, top predators, and intermediate consumers, each web used in our analysis 
-  had to have at least one species in each trophic group.
+  We combined published food webs from~\citet{GlobaWeb} (GlobalWeb),~\citet{Brose2006} (Brose), 
+  and~\citet{Dunne2013} (Dunne).
+  Of the 385 food webs available from~\citet{Globalweb}, 122 were rejected because their original
+  source was unpublished or could not be retrieved. We further eliminated 13 source or sink webs
+  (which describe feeding links flowing from or to a particular resource or top predator rather
+  than the interactions of an entire community), 8 plant-pollinator webs, 34 host-parasitoid webs,
+  and 2 networks describing competitive interactions. Finally, we eliminated 2 webs describing 
+  inferred interactions in an extinct community, 8 ``generalized schemes'' that were not based
+  on direct field data, and 2 webs where it was not clear which of several described study sites
+  were used to construct the food web (and therefore the latitude of the food web could not be 
+  included). This left us with 156 webs from~\citet{GlobalWeb}.
 
-  of  the University of Canberra's GlobalWeb database (www.globalwebdb.com) 
-  \citep{}. Of these, 302 webs had accessible original sources. 
-  18 source and sink webs, which describe links to or from a focal taxon, were excluded as they are likely 
-  to have different food web properties than webs attempting to
-  describe the entire community of a site \citep{Williams2002}, as were 8 plant-pollinator, 34 host-parasitoid, and 2 
-  competition-focused networks
-  \citep{Riede2010}. Of the remaining 230 food webs, we excluded two paleowebs (comprised of probable interactions 
-  between extinct or prehistoric species) \citep{Simenstad1978} and five ``generalized schemes'' 
-  \citep{Nybakken1982,Percival1929,Swan1961,Landry1977,Petipa1979,Harrison1963}, as 
-  we wished to measure
-  directly observed rather than inferred interactions. We further excluded a food web aggregated from several sites in 
-  the Pacific Ocean which were widely spread in both latitude and longitude and at markedly different successional stages
-  \citep{Vinogradov1978}, such that it is not clear which site the food web represents. 
-  This left 223 food webs with widely varying levels of taxonomic resolution, 11 of which contained humans.
+  To these, we added 7 webs from~\citet{Dunne2013} that were originally used to assess the roles
+  of parasites within food webs. As all but 3 of the webs from~\citet{GlobalWeb} contained only
+  free-living species, we removed the the parasites (and all interactions involving them) from
+  these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
+  species only. In addition, we included the 96 webs from~\citet{Brose2006}, which were originally
+  collected to XXXYYYY. This gave us a database of 259 webs. However, as we wished to use the
+  logarithmic form of power-law relationships, we then eliminated any food web which did not have
+  at least one each of basal resources, intermediate consumers, and top predators (to obtain non-zero
+  proportions of each category). Our final sample size was thereby reduced to 163 food webs.
+
+ (See Table S1 for a list of rejected webs and reasons for their
+  exclusion.)
 

### 2015-06-17 code/byTL_Models.R
Old changes

@@ -172,10 +172,10 @@ power_analysis=FALSE
       outdir='../non_TS/'     }
 
   LS_marg=S_CIs("LS_min")
-  write.table(LS_marg,file=paste(outdir,'marginals/LS_S_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
-  Gen_marg=S_CIs("Gen_min")
-  write.table(Gen_marg,file=paste(outdir,'marginals/Gen_S_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
+  # Gen_marg=S_CIs("Gen_min")
   Vul_marg=S_CIs("Vul_min")
+  write.table(LS_marg,file=paste(outdir,'marginals/LS_S_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
+  write.table(Gen_marg,file=paste(outdir,'marginals/Gen_S_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
   write.table(Vul_marg,file=paste(outdir,'marginals/Vul_S_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
 
   LS_B_marg=B_CIs("LS_B_min")

### 2015-06-17 code/marginal_CIs.R

@@ -2,7 +2,6 @@ S_CIs <- function(model){
       modname=eval(as.name(model))
       betas=summary(modname)$coefficients[,1]
       covar=vcov(modname)
-      modname
     
       s0=seq(1,200,length.out=500)
       # logged data in the modnames, logged data in the plots. No scaling shenanigans
@@ -13,56 +12,51 @@ S_CIs <- function(model){
       lat_effect <- function(data,ind){
         d <- data[ind,] # Is this the sampling step?
 
-        LS_m <- with(d,lm(log(LS)~log(Species)+log(Species):(Lake+Terr)
-            +log(Species):Latitude+log(Species):Latitude:Lake,na.action=na.fail))
-        latbeta=summary(LS_m)$coefficients[5,1]
-        lakebeta=summary(LS_m)$coefficients[6,1]
+        if(model=='LS_min'){
+          LS_m <- with(d,lm(log(LS)~log(Species)+log(Species):(Lake+Terr)
+              +log(Species):Latitude+log(Species):Latitude:Lake,na.action=na.fail))
+          latbeta=summary(LS_m)$coefficients["log(Species):Latitude",1]
+          lakebeta=summary(LS_m)$coefficients["log(Species):Lake:Latitude",1]
 
-        results=c(latbeta,lakebeta)
-        results
-        # return(results)
-      }
+          results=c(latbeta,lakebeta)
+          results    }
+        if(model=='Gen_min'){
+          Gen_m <- with(d,lm(log(Gen)~log(Species)
+          +log(Species):(Lake+Stream+Terr)+log(Species):Latitude
+          +log(Species):Latitude:(Lake+Stream),na.action=na.fail))
+          latbeta=summary(Gen_m)$coefficients[6,1]
+          lakebeta=summary(Gen_m)$coefficients[7,1]
+          streambeta=summary(Gen_m)$coefficients[8,1]
 
-      bootstraps=boot(data,lat_effect,R=1000)
-      # This is working (i.e., generates variation), now I just need to actually make the CI.
+          results=c(latbeta,lakebeta,streambeta)
+          results    }
+        if(model=='Vul_min'){
+          Vul_m <- with(d,lm(log(Vul)~log(Species)
+          +log(Species):(Lake+Terr)+log(Species):Latitude
+          +log(Species):Latitude:Lake,na.action=na.fail))
[…]

### 2015-06-18 manuscript/coverletter.tex
updated supplement and fixed parentheses in coverletter

@@
 \usepackage{amsmath,amsfonts,amssymb}
-\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
+% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}
 
@@
 
-\newcommand{\mytitle}{\emph{Title title title}}
+\newcommand{\mytitle}{\emph{Generality in food webs scales with species richness but not with latitude}}
 \newcommand{\myjournal}{\emph{Proceedings of the Royal Society B}}
@@
 
-\begin{letter}{{\bf RE: \mytitle\\
+\begin{letter}{\bf RE: \mytitle\\
                ~~~~~~~Cirtwill, Alyssa R; Stouffer, Daniel B; Romanuk, Tamara N\\
@@
 We believe that our study will be of interest not only to theory-focused biologists but also to general readers
-of \emph{\myjournal}} as it deals with global trends in the structure of ecological communities. 
+of \emph{\myjournal} as it deals with global trends in the structure of ecological communities. 
 Specifically, we address the impact of latitude and habitat type on known scaling relationships between empirical
@@
 
-Our paper thus contributes to the discussions of both the latitude-niche-breadth hypothesis of () and scaling
+Our paper thus contributes to the discussions of both the latitude-niche-breadth hypothesis and scaling
 laws in food-web structure, as well as being potentially applicable to researchers exploring community 

### 2015-06-18 manuscript/latitudepaper.tex
updated supplement and fixed parentheses in coverletter

@@
 
-\vspace{0.3 in}
+\vspace{-0.2 in}
 
@@
 by basal resources, intermediate consumers, and top predators. While we
-observed no effect of latitude on scaling relationships in the estuarine,
-marine, and terrestrial food webs, there were strong effects of latitude on
-scaling relationships in the freshwater food webs. In these communities, the
-latitude-niche breadth hypothesis appears to hold true while in other habitat
-types niches appear to be broader in the tropics. These contrasting findings
-indicate that it may be more important to account for habitat than latitude
-when exploring gradients in food-web structure.
+observed no effect of latitude on scaling relationships with species richness
+in the estuarine, marine, and terrestrial food webs, there were strong effects
+of latitude on scaling relationships in the freshwater food webs. In these
+communities, the latitude-niche breadth hypothesis appears to hold true while
+in other habitat types niche breadth appears to vary little. These contrasting
+findings indicate that it may be more important to account for habitat than
+latitude when exploring gradients in food-web structure.
+
+% \end{spacing}
 
@@
   Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
-  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009a,Macpherson2002,Kaufman1995}.
+  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009,Macpherson2002,Kaufman1995}.
 
@@
   If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
-  degree of specialization (i.e., niche breadth) of species within food webs.
+  degree of specialization (i.e., the breadth of the Eltonian niche ~\citep{Elton1927}) of species within food webs.
   Attempts to unravel these effects, however,
@@
   For example,
-  narrower niches imply fewer links per species (i.e., greater specialization in the tropics~\citep{Dyer2007,Marra1997} but see~\citep{Schleuning2012}). However,
+  narrower niches imply fewer links per species (i.e., greater specialization) in the tropics~\citep{Dyer2007,Marra1997}
+  but see~\citep{Schleuning2012}). However,
   average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
@@
     We compiled a list of 163 empirical food webs from
-    multiple sources (see Supplemental Information for web origins and selection
+    multiple sources (see \emph{Appendix S1} for web origins and selection
     criteria). We recorded study site latitude from the original source where
@@
     species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
-    of the dataset; in each case using the number of species ($S$) and 
-    links ($L$) in each web to calculate the mean number of links per species ($Z$), mean generality 
-    ($G$), and mean vulnerability ($V$) of the web. 
+    of the dataset; in each case using the number of species and 
+    links in each web to calculate the mean link density (number of links per species), mean generality 
+    (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
     The version of the dataset used did not qualitatively change the results, suggesting that
@@
 
-  \subsection*{Relationships with Latitude}
-
-    To determine whether there were latitudinal gradients in food-web structure,
-    we first examined simple linear relationships between latitude and each of 
-    species richness, links per species, generality, vulnerability, and proportions
-    of basal resources, intermediate consumers, and top predators. We fit models of the form
-
-    \begin{equation}
-    \label{Latfull}
-    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
-    \end{equation}
-
-    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
-    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
-    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
-    marine, lake, and terrestrial networks with estuarine
-    networks providing the intercept) and $\epsilon_{i}$ a residual error term. 
-    We next calculated the AIC
-    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
-    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
-    Simplified models were obtained by
-    systematically removing all possible combinations of terms from the full model.
-    The best-fitting model was then determined to be the model with the fewest terms 
-    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
-    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
-    model.
-
   \subsection*{Scaling Relationships with S}
 
-    Next, we examined the form of the scaling relationship between each 
-    property (links per species, generality, and vulnerability) and 
-    species richness. The scaling relationship between links per species ($Z$) and 
-    species richness ($S$) has been shown to be a power law~\citep{Riede2010} of the form
+    The scaling relationships between link density ($Z$) and species richness ($S$)
+    has been shown to be a power law~\citep{Riede2010} of the form
 
@@
 
-    \noindent Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
-    Specifically, equation~(\ref{Power}) implies a normally-distributed, additive error and equation~(\ref{Loglog}) a lognormal,
-    multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
-    over another, we follow the recommendations in~\citet{Xiao2011} and compared the two
-    model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
-    data was then used to test for potential effects of latitude.
-
-    Although scaling relationships between species richness and generality or
-    species richness and vulnerability have not been explicitly examined (but see scaling 
-    relationships for the standard devaitions of each property in~\citet{Riede2010}), we expect that they will follow
-    power laws similar to that of the relationship between species richness and links per species.
-    This is because the links taken into account in calculating generality and vulnerability are subsets 
-    of the total links included when calculating links per species. As with links per species, we explicitly 
-    compared the error distributions of models for generality and vulnerability using
-    both the power-law and logarithmic formulations. 
-    In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
-    species richness.
+    \noindent As the two forms imply different error distributions, neither of which has strong
+    \emph{a priori} justification in our dataset, we followed the recommendations in~\citet{Xiao2011}
+    to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
+    The logarithmic form (equation~\ref{Loglog}) provided the better fit to the data,
+    as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
+    We therefor used logarithmic models throughout the rest of the study.
 
@@
 
-    We then assessed the impact of latitude on the scaling relationships between species richness and 
-    link density, generality, vulnerability. In the context of the scaling relationships above, note 
-    that this implies that we aim to determine the effect of latitude on
-    the scaling exponent $\beta$. As when examining the relationships between latitude and each food 
-    web property directly, we included a categorical variable for ecosystem type (stream, lake, 
-    terrestrial, marine, or estuary), as well as interactions between food web type and latitude.
+    After determining the appropriate form of the scaling relationship, we
+    then assessed the impact of latitude on the scaling relationships between
+    species richness and  link density, generality, vulnerability. In the
+    context of the scaling relationships above, note  that this implies that
+    we aim to determine the effect of latitude on the scaling exponent
+    $\beta$. As when examining the relationships between latitude and each
+    food  web property directly, we included a categorical variable for
+    ecosystem type (stream, lake,  terrestrial, marine, or estuary), as well
+    as interactions between food web type and latitude.
 
@@
 
-  \subsection*{Relationships with Latitude}
+  Link density, generality, and vulnerability each increased with increasing
+  species richness (Fig~\ref{props_v_lat}; $\beta_0$=0.666,
+  $p$\textless0.001; $\beta_0$=0.623, $p$\textless0.001; and
+  $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine, marine,
+  and terrestrial food webs the strength of this scaling did not vary with
+  latitude ($\beta_{Latitude}$=-0.001, $p$=0.267 for link density;
+  $\beta_{Latitude}$=-0.001, $p$=0.363 for generality; and
+  $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability; Fig.~\ref{S}). In
+  lake food webs, however, the scaling of each property was stronger towards
+  the poles ($\beta_{Latitude:Lake}$=0.005, $p$=0.008;
+  $\beta_{Latitude:Lake}$=0.005, $p$=0.002; and
+  $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively). In stream food
+  webs generality increased more rapidly towards the poles
+  ($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability
+  did not vary with latitude.
 
-    Contrary to the expected latitudinal gradient, the best-fit version of
-    equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
-    ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
-    relationship was robust to the removal of three outliers (based on Cook's Distance). 
-    There were also relationships between latitude and link density and latitude and vulnerability
-    in stream food webs, but these trends were non-signficant after the removal of three outliers.
-    Link density and vulnerability did not vary with latitude in any other ecosystem type.
-    The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
-    latitude in any ecosystem type.
+  Unlike species richness, only generality increased with increasing
+  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
+  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
+  density, generality, and vulnerability respectively,
+  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
+  effects of latitude on the scaling relationships. Thus, the scaling
+  exponents for link density and vulnerability were negative for estaurine,
+  lake, and stream communities and became more negative towards the poles
+  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
+  $p$=0.006, respectively; Fig.~\ref{B}). For the scaling of link density and
+  vulnerability in marine and terrestrial communities, the overall effect of
+  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
+  $p$=0.047; $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002 and
+  $\beta_{Latitude:Marine}$=0.009, $p$=0.047;
+  $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002, respectively) such that
+  there was little overall scaling relationship. In contrast, the scaling
+  exponent of generality with the proportion of basal resources was positive
+  near the equator and negative near the poles in estuarine, lake, and stream
+  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
+  exponents for marine and terrestrial communities were not significantly
+  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
+  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; Fig.~\ref{B}).
 
-    The relationships between latitude and the proportions of species at each trophic level were broadly similar
-    to the relationship between latitude and species richness. 
-    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
-    but did not vary with latitude in estuarine, marine, lake, or terrestrial 
-    food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
-    The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
-    The proportion of top predators did not vary with latitude in 
-    estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
-    webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
-    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
-    All of these trends were robust to the removal of outliers.
+  As with species richness, link density, generality, and vulnerability
+  generally increased with the proportion of intermediate consumers in a web
+  ($\beta_0$=1.74, $p$\textless0.001; $\beta_0$=1.92, $p$\textless0.001; and
+  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}).
+  The strength of this scaling decreased towards the poles in estuarine,
+  lake, marine, and stream communities in each case
+  ($\beta_{Latitude}$=-0.012, $p$=0.007; $\beta_{Latitude}$=-0.018,
+  $p$\textless0.001; and $\beta_{Latitude}$=-0.012, $p$=0.007, respectively;
+  Fig~\ref{I}). In terrestrial communities, however, scaling was stronger
+  towards the  poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for
+  link density; $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for
+  generality; and $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.022 for
+  vulnerability, respectively).
 
-  \subsection*{Form of scaling relationships}
-
-    When considering the relationships between species richness or the proportions 
-    of basal resources, intermediate consumers, or top predators and all response variables 
-    (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
-    lower AIC than did equation~(\ref{Power}). This indicates that the
-    data support an assumption of multiplicative lognormal error better than an
-    assumption of additive normal error. That is, models where $\epsilon$ is
-    modelled as an additive term on
-    the logarithmic scale provide a better description of the data than models
-    where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
-    We therefore used logarithmic-form models when assessing the
-    effect of latitude on scaling relationships  with species richness.
-
-  \subsection*{Effect of Latitude on Scaling with S, B, I, and T}
-
-    Link density, generality, and vulnerability each increased with increasing
-    species richness (Fig.~\ref{S}; $\beta_0$=0.666, $p$\textless0.001; $\beta_0$=0.623,
-    $p$\textless0.001; and $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine,
-    marine, and terrestrial food webs this increase did not vary with latitude
-    ($\beta_{Latitude}$=-0.001, $p$=0.267 for link density; $\beta_{Latitude}$=-0.001, $p$=0.363 for generality;
-    and $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability). In lake food webs, link density,
-    generality, and vulnerability all increased more quickly towards the poles
-    ($\beta_{Latitude:Lake}$=0.005, $p$=0.008; $\beta_{Latitude:Lake}$=0.005,
-    $p$=0.002; and $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively). In
-    stream food webs generality increased more rapidly towards the poles 
-    ($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability did not vary with latitude.
-
-    In general, link density, generality, and vulnerability decreased as the
-    proportion of basal resources in a web increased (Fig.~\ref{B}). For
-    estuarine, lake, and stream food webs these decreases were more gradual towards the
-    poles ($\beta_{Latitude}$=-0.007, $p$=0.006 for link density;
-    $\beta_{Latitude}$=-0.009, $p$=0.002 for generality; and
-    $\beta_{Latitude}$=-0.007, $p$=0.006 for vulnerability).
-    In marine food webs there was very little effect of latitude on
-    the strength of scaling ($\beta_{Latitude:Marine}$=0.009, $p$=0.047; 
-    $\beta_{Latitude:Marine}$=0.011, $p$=0.028; 
-    and $\beta_{Latitude:Marine}$=0.009, $p$=0.047 respectively),
-    while in terrestrial food webs link density, generality, and vulnerability each
-    decreased more gradually towards the 
-    equator ($\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002; 
-    $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; 
-    and $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002).
-
-    In contrast to the proportion of basal resources, link density, generality,
-    and vulnerability tended to increase with increasing proportions of
-    intermediate consumers (Fig.~\ref{I}; ). The best-fit models for scaling of link
-    density and vulnerability with the proportion of intermediate consumers did
-    not include any effect of latitude on scaling in any ecosystem type. Generality
-    increased more rapidly towards the equator in estuarine, lake, marine, and
-    stream food webs ($\beta_{Latitude}$=-0.006, $p$=0.009) and varied little with
-    latitude in terrestrial food webs ($\beta_{Latitude:Terrestrial}$=0.008,
-    $p$=0.053). In lake and stream food webs, generality increased more slowly
-    with the proporiton of intermediate consumers such that, at low proportions,
-    the effect of latitude could negate or reverse the increase.
-
-    As with the proportion of basal resources; link density, generality, and
-    vulnerability decreased as the proportion of top predators increased. For
-    estuarine, lake, and marine food webs scaling of link density, generality, and
-    vulnerability did not vary significantly with latitude
-    ($\beta_{Latitude}$=-0.001, $p$=0.527 for link density;
-    $\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the best-fit model for
-    generality did not include any terms for latitude in any ecosystem type). In
-    stream and terrestrial food webs, the decrease in link density and
-    vulnerability was less sharp towards the poles, although this trend was
-    significant only in streams ($\beta_{Latitude:Stream}$=0.015,
-    $p$\textless0.001 and $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link
-    density; $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
-    $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability).
+  In contrast, link density, generality, and vulnerability decreased as the
+  proportion of top predators increased ($\beta_0$=-0.511, $p$\textless0.001;
+  $\beta_0$=-0.418, $p$\textless0.001; and $\beta_0$=-0.511, $p$\textless0.001
+  respectively; Fig~\ref{props_v_lat}). For estuarine, lake, and marine
+  food webs the strength of this scaling did not
+  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.527 for
+  link density; $\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the
+  best-fit model for generality did not include any terms for latitude in
+  any ecosystem type). In stream and terrestrial food webs, scaling was more
+  strongly negative in the tropics and did not differ from zero near the poles,
+  although this trend was only significant in streams
+  ($\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
+  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link density;
+  $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
+  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability; Fig~\ref{T}).
 
@@
   species richness in particular is also known to vary systematically over
-  latitude~\citep{Schemske2009a,Macpherson2002,Kaufman1995}, intuitively one might suspect that any relationship
-  between food-web properties such as generality might be due to the latitudinal
-  gradient in species richness. In this dataset, however, we did not find
-  overall latitudinal gradients in species richness, links per species, 
-  generality, vulnerability, or the proportions of food webs accounted for by 
-  basal resources, intermediate consumers, and top predators.
+  latitude~\citep{Schemske2009,Macpherson2002,Kaufman1995}, intuitively one
+  might suspect that any relationship between food-web properties such as
+  generality might be due to the latitudinal gradient in species richness. In
+  this dataset, however, we did not find overall latitudinal gradients in
+  species richness, links per species,  generality, vulnerability, or the
+  proportions of food webs accounted for by  basal resources, intermediate
+  consumers, and top predators (see \emph{Appendix S3} for details).
 
   The lack of a latitudinal gradient in species richness in this dataset contrasts
-  strongly with other studies~\citep{Schemske2009a,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
+  strongly with other studies~\citep{Schemske2009,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
   vary strongly with sampling effort as well as with the underlying diversity of the study
@@
   may affect speciation rates and therefore the diversity in a region~\citep{Currie2004}). 
-  For example, as plant diversity increases both the 
+  For example, as the plant diversity of a community increases both the 
   variety of food available to herbivores and the structural variety of the habitat will also increase.
 
-  Unlike other ecosystem types, the scaling of generality
-  in lake and stream food webs was stronger (i.e., 
-  increased more steeply) in higher-latitude food webs. 
-  In lake food webs, this trend was echoed in the scaling relationships
-  between species richness and links per species and vulnerability.
-  This means that species in tropical freshwater
-  communities gain fewer additional feeding links per additional species in the
-  web and that species in tropical lakes also gain fewer predators, and fewer links
-  in general, per additional species. These trends are consistent with the hypothesis
-  that greater stability in the tropics leads to narrower niches~\citep{Vazquez2004} and a higher proportion of
-  specialists. This may be partly due to high-latitude species
-  tending to switch between different seasonally-available
-  prey~\citep{Isaac2012,Wilhelm1999} while tropical freshwater ecosystems may have more stable composition.
+  Unlike other ecosystem types, the scaling of generality in lake and stream
+  food webs was stronger (i.e.,generality increased more steeply with
+  increasing species richness) in higher-latitude food webs.In lake food webs,
+  this trend was echoed in the scaling relationships between species richness
+  and links per species and vulnerability. This means that species in tropical
+  freshwater communities gain fewer additional feeding links per additional
+  species in the web and that species in tropical lakes also gain fewer
+  predators, and fewer links in general, per additional species than species
+  in high-latitude lakes. These trends are consistent with the hypothesis that
+  greater stability in the tropics leads to narrower
+  niches~\citep{Vazquez2004} and a higher proportion of specialists. This may
+  be partly due to high-latitude species tending to switch between different
+  seasonally-available prey~\citep{Isaac2012,Wilhelm1999} while tropical
+  freshwater ecosystems may have more stable composition.
 
@@
 
-%\end{spacing}
 \newpage
@@
 
+\end{spacing}
 \newpage
@@
 \section*{Figures}
+\begin{figure}[h]
+\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
+\caption{Scaling relationships for link density, generality (number of prey), 
+and vulnerability (number of predators) 
+against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
+predators (\% Top), and species richness of a food web. 
+For each relationship, we show observed values corrected for
+ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). For
+the uncorrected values, see Fig.~\emph{S1}, \emph{Appendix S4}.}
+\label{props_v_lat}
+\end{figure}
+
+% \begin{figure}[H]
+% \includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
+% \caption{Scaling relationships for link density, generality (number of prey), 
+% and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
+% intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
+% For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
+% any effects of habitat type or latitude (N=163 food webs). }
+% \label{props_v_lat_obs}
+% \end{figure}
+
+% \newpage
 
 \begin{figure}[h]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_latlines_nonts.eps}
-\caption{Scaling of link density, generality, and vulnerability with species richness
-varies across ecosystem types and over latitude. For each property we show 
-prediction curves for food webs at the equator (darkest line) and at 
-20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
-equator. We did not include direction (i.e., North or South) in our analyses. 
-All curves are based on N=163 empirical food webs.}
+\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for species richness (black
+line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
+regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
 \label{S}
@@
 \begin{figure}[!H]
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/B_latlines_nonts.eps}
-\caption{Scaling of link density, generality, and vulnerability 
-with the proportion of basal resources in a food web
-varies across ecosystem types and over latitude. For each property we show 
-prediction curves for food webs at the equator (darkest line) and at 
-20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
-equator. We did not include direction (i.e., North or South) in our analyses. 
-All curves are based on N=163 empirical food webs.}
+\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
+from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
 \label{B}
@@
 \begin{figure}[h]
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/I_latlines_nonts.eps}
-\caption{Scaling of link density, generality, and vulnerability 
-with the proportion of intermediate consumers in a food web
-varies across ecosystem types and over latitude. For each property we show 
-prediction curves for food webs at the equator (darkest line) and at 
-20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
-equator. We did not include direction (i.e., North or South) in our analyses. 
-All curves are based on N=163 empirical food webs.}
+\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
+from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
 \label{I}
@@
 \begin{figure}[h]
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/T_latlines_nonts.eps}
-\caption{Scaling of link density, generality, and vulnerability 
-with the proportion of top predators in a food web
-varies across ecosystem types and over latitude. For each property we show 
-prediction curves for food webs at the equator (darkest line) and at 
-20\degree, 40\degree, 60\degree, and 80\degree (lightest line) from the 
-equator. We did not include direction (i.e., North or South) in our analyses. 
-All curves are based on N=163 empirical food webs.}
+\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
+from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
 \label{T}
@@
 
-\newpage
-
-\begin{figure}[H]
-\includegraphics[width=.9\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
-\caption{Scaling relationships for link density, generality (number of prey), 
-and vulnerability (number of predators) 
-against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
-predators (\% Top), and species richness of a food web. 
-For each relationship, we show observed values corrected for
-ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). }
-\label{props_v_lat}
-\end{figure}
-
 \end{document}

### 2015-06-18 manuscript/supplement.tex
updated supplement and fixed parentheses in coverletter

@@
 
-\subsection*{Appendix S2: Supplemental Figures}
+\subsection*{Appendix S2: Supplemental Methods and Results - scaling Relationships with S}
+
+  \subsubsection*{Methods}
+
+    The scaling relationships between link density ($Z$) and species richness ($S$)
+    has been shown to be a power law~\citep{Riede2010} of the form
+
+    \begin{equation}
+    \label{Power}
+    Z_{i} \sim \alpha S_{i}^{\beta}  ,
+    \end{equation}
+
+    \noindent which is often re-expressed in logarithmic form
+
+    \begin{equation}
+    \label{Loglog}
+    \log{Z_{i}} \sim \log{\alpha} + \beta\log{S_{i}}  .
+    \end{equation}
+
+    \noindent Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
+    Specifically, equation~(\ref{Power}) implies a normally-distributed, additive error and equation~(\ref{Loglog}) a lognormal,
+    multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
+    over another, we follow the recommendations in~\citet{Xiao2011} and compared the two
+    model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
+    data was then used to test for potential effects of latitude.
+
+    Although scaling relationships between species richness and generality or
+    species richness and vulnerability have not been explicitly examined (but see scaling 
+    relationships for the standard devaitions of each property in~\citet{Riede2010}), we expect that they will follow
+    power laws similar to that of the relationship between species richness and links per species.
+    This is because the links taken into account in calculating generality and vulnerability are subsets 
+    of the total links included when calculating links per species. As with links per species, we explicitly 
+    compared the error distributions of models for generality and vulnerability using
+    both the power-law and logarithmic formulations. 
+    In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
+    species richness.
+
+  \subsubsection*{Results}
+
+    When considering the relationships between species richness or the proportions 
+    of basal resources, intermediate consumers, or top predators and all response variables 
+    (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
+    lower AIC than did equation~(\ref{Power}). This indicates that the
+    data support an assumption of multiplicative lognormal error better than an
+    assumption of additive normal error. That is, models where $\epsilon$ is
+    modelled as an additive term on
+    the logarithmic scale provide a better description of the data than models
+    where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
+    We therefore used logarithmic-form models when assessing the
+    effect of latitude on scaling relationships  with species richness.
+
+\subsection*{Appendix S3: Supplemental Methods and Results - relationships with latitude}
+
+  \subsubsection*{Methods}
+
+    To determine whether there were latitudinal gradients in food-web structure,
+    we first examined simple linear relationships between latitude and each of 
+    species richness, links per species, generality, vulnerability, and proportions
+    of basal resources, intermediate consumers, and top predators. We fit models of the form
+
+    \begin{equation}
+    \label{Latfull}
+    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
+    \end{equation}
+
+    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
+    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
+    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
+    marine, lake, and terrestrial networks with estuarine
+    networks providing the intercept) and $\epsilon_{i}$ a residual error term. 
+    We next calculated the AIC
+    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
+    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
+    Simplified models were obtained by
+    systematically removing all possible combinations of terms from the full model.
+    The best-fitting model was then determined to be the model with the fewest terms 
+    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
+    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
+    model.
+
+  \subsubsection*{Results}
+    Contrary to the expected latitudinal gradient, the best-fit version of
+    equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
+    ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
+    relationship was robust to the removal of three outliers (based on Cook's Distance). 
+    There were also relationships between latitude and link density and latitude and vulnerability
+    in stream food webs, but these trends were non-signficant after the removal of three outliers.
+    Link density and vulnerability did not vary with latitude in any other ecosystem type.
+    The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
+    latitude in any ecosystem type.
+
+    The relationships between latitude and the proportions of species at each trophic level were broadly similar
+    to the relationship between latitude and species richness. 
+    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
+    but did not vary with latitude in estuarine, marine, lake, or terrestrial 
+    food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
+    The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
+    The proportion of top predators did not vary with latitude in 
+    estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
+    webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
+    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
+    All of these trends were robust to the removal of outliers.
+
+\subsection*{Appendix S4: Supplemental Figures}
+
+\begin{figure}[H]
+\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
+\caption{Scaling relationships for link density, generality (number of prey), 
+and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
+intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
+For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
+any effects of habitat type or latitude (N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
+observed values correcting for the effects of habitat type and latitude. }
+\label{props_v_lat_obs}
+\end{figure}
 

### 2015-06-18 code/byTL_Models.R

@@ -8,8 +8,8 @@ library(MuMIn)
 infile='../non_TS/summary-properties.tsv'
 #infile='../mod_data/summary-properties.tsv'
 
-# format='proportions'
-format='numbers'
+format='proportions'
+# format='numbers'
 
 # for(format in c('proportions','numbers')){
 power_analysis=FALSE

### 2015-06-18 manuscript/latitudepaper.tex
Tentative last paragraph of discussion

@@
 
-  Unlike species richness, only generality increased with increasing
+  Unlike species richness, only generality showed an overall increase with increasing
   proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
@@
 
+  The scaling of link density, generality and vulnerability with proportions
+  of species at different trophic levels, however, did not differ between lakes
+  and most other food webs. Indeed, there was comparatively little variation in
+  scaling with the trophic-level breakdown of a web across ecosystem types.
+  Terrestrial food webs tended to exhibit less change in scaling over latitude
+  than other ecosystem types, as did marine webs when considering scaling with
+  the proportion of basal resources. More excitingly, the negative relationships
+  between the proportion of top predators in a web and link density and
+  vulnerability were weaker (i.e., the scaling exponent was more strongly
+  negative) in low-latitude stream ecosystems. This may imply that high-latitude
+  top predators tend to be more generalist than their low-latitude equivalents.
+  More generally, the lack of correspondence between the scaling of food-web
+  properties with species richness and with proportions of species at each
+  trophic level suggests that the size and trophic breakdowns of a community can
+  provide different information about the breadth of niches in that community.
+
 \section*{Conclusion}

### 2015-06-19 manuscript/latitudepaper.tex
trying out the new figs
Updated figures in many ways

@@
   ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
-  $p$=0.006, respectively; Fig.~\ref{B}). For the scaling of link density and
+  $p$=0.006, respectively; Fig.~\ref{BIT}). For the scaling of link density and
   vulnerability in marine and terrestrial communities, the overall effect of
@@
   different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
-  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001; Fig.~\ref{B}).
+  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001).
 
@@
   $p$\textless0.001; and $\beta_{Latitude}$=-0.012, $p$=0.007, respectively;
-  Fig~\ref{I}). In terrestrial communities, however, scaling was stronger
+  Fig~\ref{BIT}). In terrestrial communities, however, scaling was stronger
   towards the  poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for
@@
   $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
-  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability; Fig~\ref{T}).
+  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability; Fig~\ref{BIT}).
 
@@
 \begin{figure}[h]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for species richness (black
+\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
+\caption{Changes to the scaling of link density with species richness across ecosystem
+types and over latitude. We show the scaling exponent for species richness (black
 line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
-regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
+regardless of direction. The scaling relationships are based on N=163 empiricl food webs. 
+Exponents for the scaling of generality and vulnerability with species richness were very 
+similar to those for link density, except for the scaling of generality in streams where 
+the size of the exponent increased towards the poles. See \emph{Fig. S2, Appendix 5} for 
+all scaling relationships.}
 \label{S}
@@
 \begin{figure}[!H]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
+\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
@@
 basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
-from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
-\label{B}
-\end{figure}
-
-\newpage
-
-\begin{figure}[h]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
-from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
-\label{I}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
-from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
-\label{T}
+from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.
+Exponents for the scaling relationships of generality and vulnerability with each proportion were very
+similar to those of the scaling relationships with link density, except for the scaling of generality
+with the proportion of top predators where there was no effect of latitude on the size of the exponent
+in any ecosystem type. See \emph{Figs. S3-S5, Appendix 5} for all scaling relationships.}
+\label{BIT}
 \end{figure}

### 2015-06-19 manuscript/supplement.tex
Updated figures in many ways

@@
 
-\begin{figure}[H]
-\includegraphics[width=.9\textwidth]{}
-\caption{ }
-\label{}
+\begin{figure}[h]
+\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for species richness (black
+line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
+regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
+\label{S}
+\end{figure}
+
+\begin{figure}[!H]
+\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
+from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
+\label{B}
+\end{figure}
+
+\newpage
+
+\begin{figure}[h]
+\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
+from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
+\label{I}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
+from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
+\label{T}
 \end{figure}

### 2015-06-19 code/TL_marginal_latitude.py

@@ -328,11 +328,11 @@ def plotter(prop,TL,ecotype,graph,form):
     major=.5
     prec=1
   elif TL=='B':
-    prec=1
+    prec=0
     if form=='proportions':
       graph.world.ymin=-1.25
       graph.world.ymax=1
-      major=.5
+      major=1
     else:
       graph.world.ymin=0
       graph.world.ymax=.60000001
@@ -445,8 +445,10 @@ def main():
 
   Sgrace=MultiPanelGrace(colors=ColorBrewerScheme('Greys'))
 
-  # Sgrace.add_label_scheme('dummy',names)
-  # Sgrace.set_label_scheme('dummy')
+  Snames=['Estuarine','Lake','Marine','Stream','Terrestrial']
+
+  Sgrace.add_label_scheme('dummy',Snames)
+  Sgrace.set_label_scheme('dummy')
   
   for ecotype in ecotypes:   
     if ecotype=='Estuary':
@@ -464,7 +466,7 @@ def main():
 
     plotter(prop,TL,ecotype,graph,form)
       # graph.remove_extraworld_drawing_objects()
-    graph.xaxis.label.configure(text='Absolute latitude',place='normal',just=2,char_size=.85)
+    graph.xaxis.label.configure(text='Absolute latitude',place='opposite',just=2,char_size=.65)
     # graph.add_drawing_object(DrawText,text=typ, x=100, y=.75,loctype='world', rot=270,char_size=.85,just=2)
     graph.panel_label.configure(char_size=.75,placement='iul',dy=.02,dx=.03)
 
@@ -476,7 +478,8 @@ def main():
   Sgrace.hide_redundant_yticklabels()
   Sgrace.hide_redundant_labels()
 
-  Sgrace.set_col_yaxislabel(col=0,rowspan=(0,4),label='Scaling exponent of link density with species richness',place='normal',just=2,char_size=1,perpendicular_offset=0.08)
+  Sgrace.set_col_yaxislabel(col=0,rowspan=(0,4),label='Scaling exponent of link density with species richness',place='normal',just=2,char_size=1,perpendicular_offset=0.07)
+  Sgrace.set_row_xaxislabel(row=4,colspan=(0,0),label='Absolute latitude',place='normal',just=2,char_size=1,perpendicular_offset=0.05)
 
   Sgrace.write_file('../manuscript/Figures/by_TL/marginal/justS_marginal_latitude.eps')
  
@@ -495,7 +498,14 @@ def main():
[…]

### 2015-06-19 manuscript/latitudepaper.tex
spellcheck

@@
 
-% \end{spacing}
+\end{spacing}
 
@@
   %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
-  Food webs --networks of feeding links between species-- have been used for several decades to summarize the structure of 
+  Food webs --networks of feeding links between species-- have been used for several decades to summarise the structure of 
   ecological communities~\citep{Petchey2008,Williams2000,Paine1966} and to understand how that structure relates to environmental variables 
@@
   If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
-  degree of specialization (i.e., the breadth of the Eltonian niche ~\citep{Elton1927}) of species within food webs.
+  degree of specialisation (i.e., the breadth of the Eltonian niche ~\citep{Elton1927}) of species within food webs.
   Attempts to unravel these effects, however,
@@
   For example,
-  narrower niches imply fewer links per species (i.e., greater specialization) in the tropics~\citep{Dyer2007,Marra1997}
+  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics~\citep{Dyer2007,Marra1997}
   but see~\citep{Schleuning2012}). However,
   average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
-  that a latitudinal effect on specialization may be obscured by a latitudinal gradient in species richness. If this is
-  the case, it may still be possible to uncover effects of latitude on specialization by examining the shape of the scaling 
-  relationship between specialization and species richness over changing latitude. Here, we use three measures of specialization:
+  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness. If this is
+  the case, it may still be possible to uncover effects of latitude on specialisation by examining the shape of the scaling 
+  relationship between specialisation and species richness over changing latitude. Here, we use three measures of specialisation:
   mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
-  latitude affects the scaling of each property with species richness, we test effects of latitude on specialization implied by
+  latitude affects the scaling of each property with species richness, we test effects of latitude on specialisation implied by
   the ``latitude-niche breadth hypothesis''.
@@
   effects of latitude on the scaling relationships. Thus, the scaling
-  exponents for link density and vulnerability were negative for estaurine,
+  exponents for link density and vulnerability were negative for estuarine,
   lake, and stream communities and became more negative towards the poles
@@
   food webs was stronger (i.e.,generality increased more steeply with
-  increasing species richness) in higher-latitude food webs.In lake food webs,
+  increasing species richness) in higher-latitude food webs. In lake food webs,
   this trend was echoed in the scaling relationships between species richness
@@
   vulnerability were weaker (i.e., the scaling exponent was more strongly
-  negative) in low-latitude stream ecosystems. This may imply that high-latitude
-  top predators tend to be more generalist than their low-latitude equivalents.
+  negative) in low-latitude stream ecosystems. This may imply that top predators
+  in high-latitude streams tend to be more generalist than their low-latitude equivalents.
   More generally, the lack of correspondence between the scaling of food-web
@@
   Our results were inconsistent with the latitude-niche breadth hypothesis in estuarine, marine,
-  and terrestrial communities but consistent with the hypothesis of greater specialization
+  and terrestrial communities but consistent with the hypothesis of greater specialisation
   in the tropics in stream and lake food webs. This suggests that different mechanisms may structure
@@
 
-\end{spacing}
+% \end{spacing}
 \newpage
@@
 line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
-regardless of direction. The scaling relationships are based on N=163 empiricl food webs. 
+regardless of direction. The scaling relationships are based on N=163 empirical food webs. 
 Exponents for the scaling of generality and vulnerability with species richness were very 
@@
 basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
-from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.
+from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.
 Exponents for the scaling relationships of generality and vulnerability with each proportion were very

### 2015-06-22 manuscript/latitudepaper.tex
Added DBS comments except for finding more refs

@@
 \title{Generality in food webs scales with species richness but not with latitude}
-\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
-\date{$^1$School of Biological Sciences\\University of Canterbury\\
+\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
+\date{\small$^1$School of Biological Sciences\\University of Canterbury\\
 Private Bag 4800\\Christchurch 8140, New Zealand \\
@@
 Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
-Halifax NS, B3H 4R2\\ Canada\\}
+Halifax NS, B3H 4R2, Canada\\
+\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
+Private Bag 4800\\Christchurch 8140, New Zealand \\}
 
@@
 
-\vspace{-0.2 in}
+\vspace{-0.3 in}
 
@@
 Several properties of food webs---the networks of feeding links between
-species---vary systematically with the species richness of the underlying
+species---are known to vary systematically with the species richness of the underlying
 community.  Under the ``latitude-niche breadth hypothesis'', which predicts
@@
   For example,
-  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics~\citep{Dyer2007,Marra1997}
-  but see~\citep{Schleuning2012}). However,
+  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics(~\citealp{Dyer2007,Marra1997};
+  but see~\citealp{Schleuning2012}). However,
   average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
@@
     Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
-    sets to form ``trophic species'' webs (e.g.~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}). As this study
+    sets to form ``trophic species'' webs ~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}. As our study
     is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
-    species with redundant sets of interactions. We therefore analysed both original and trophic-species versions
+    species with identical sets of interactions. We therefore analysed both original and trophic-species versions
     of the dataset; in each case using the number of species and 
@@
     the scaling relationships between species richness, other food-web properties, and latitude are very 
-    similar whether or not redundant species are included. For simplicity, we present only
+    similar whether or not redundant species are included. For simplicity, here we present only
     the results for the original webs.
@@
 
-    The scaling relationships between link density ($Z$) and species richness ($S$)
+    The scaling relationship between link density ($Z$) and species richness ($S$)
     has been shown to be a power law~\citep{Riede2010} of the form
@@
 
-    \noindent As the two forms imply different error distributions, neither of which has strong
+    \noindent As the two forms imply a statistical fit to the data to different error 
+    distributions, neither of which has strong
     \emph{a priori} justification in our dataset, we followed the recommendations in~\citet{Xiao2011}
@@
     as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
-    We therefor used logarithmic models throughout the rest of the study.
+    We therefore used and present logarithmic models throughout the rest of the study.
 
@@
     context of the scaling relationships above, note  that this implies that
-    we aim to determine the effect of latitude on the scaling exponent
-    $\beta$. As when examining the relationships between latitude and each
-    food  web property directly, we included a categorical variable for
+    we wished to determine the effect of latitude on the scaling exponent
+    $\beta$. We included a categorical variable for
     ecosystem type (stream, lake,  terrestrial, marine, or estuary), as well
@@
 
-    \noindent where $S_{i}$, $L_{i}$, and $E_{i}$ are as defined previously. The logarithmic formulation of this model is
+    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
+    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
+    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
+    marine, lake, and terrestrial networks with estuarine
+    networks providing the intercept) and $\epsilon_{i}$ a residual error term.
+    The logarithmic formulation of this model is
 
@@
 
-    For each property in link density, generality, and vulnerability, we used the form of the equation that was best supported
-    when describing the scaling of the property with species richness alone~\citep{Xiao2011}.
-    We then simplified each model following the same procedure as for the relationships between
-    latitude and food-web properties, except that species richness was retained in all reduced models.
+    We then simplified each model. To do this, we calculated the AIC of the
+    maximal model as well as the AIC's of a suite of candidate simplified
+    models identified using the R~\citep{R} function dredge from package
+    MuMIn~\citep{MuMIn}.  Simplified models were obtained by systematically
+    removing all possible combinations  of terms from the full model with the
+    restriction that species richness was retained in all reduced models. The
+    best-fitting model was then determined to be the model with the fewest
+    terms  where $\Delta$AIC\textless2. If several models shared the fewest
+    number of terms  and had $\Delta$AIC\textless2, the model with the lowest
+    AIC in that set was chosen as the best-fit model.
 
@@
   Link density, generality, and vulnerability each increased with increasing
-  species richness (Fig~\ref{props_v_lat}; $\beta_0$=0.666,
-  $p$\textless0.001; $\beta_0$=0.623, $p$\textless0.001; and
-  $\beta_0$=0.666, $p$\textless0.001 respectively).  For estuarine, marine,
-  and terrestrial food webs the strength of this scaling did not vary with
-  latitude ($\beta_{Latitude}$=-0.001, $p$=0.267 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=0.363 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=0.267 for vulnerability; Fig.~\ref{S}). In
+  species richness ($\beta_0$=0.643, $p$\textless0.001; $\beta_0$=0.599,
+  $p$\textless0.001; and $\beta_0$=0.643, $p$\textless0.001, respectively;
+  Fig~\ref{props_v_lat}).For estuarine, marine, and terrestrial food webs the
+  strength of this scaling did not vary with latitude
+  ($\beta_{Latitude}$=-0.001, $p$=0.232 for link density;
+  $\beta_{Latitude}$=-0.001, $p$=0.257 for generality; and
+  $\beta_{Latitude}$=-0.001, $p$=0.233 for vulnerability; Fig.~\ref{S}). In
   lake food webs, however, the scaling of each property was stronger towards
-  the poles ($\beta_{Latitude:Lake}$=0.005, $p$=0.008;
-  $\beta_{Latitude:Lake}$=0.005, $p$=0.002; and
-  $\beta_{Latitude:Lake}$=0.005, $p$=0.008, respectively). In stream food
-  webs generality increased more rapidly towards the poles
-  ($\beta_{Latitude}$=0.007, $p$=0.002) while link density and vulnerability
-  did not vary with latitude.
+  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.006;
+  $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001; and
+  $\beta_{Latitude:Lake}$=0.005, $p$=0.005, respectively). In stream food
+  webs, generality increased more rapidly towards the poles
+  ($\beta_{Latitude:Stream}$=0.007, $p$\textless0.001) while link density and
+  vulnerability did not vary with latitude.
 
@@
   $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
-  density, generality, and vulnerability respectively,
+  density, generality, and vulnerability, respectively;
   Fig.~\ref{props_v_lat}). In each case, however, there were substantial
@@
   lake, and stream communities and became more negative towards the poles
-  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
-  $p$=0.006, respectively; Fig.~\ref{BIT}). For the scaling of link density and
+  ($\beta_{Latitude}$=-0.007, $p$=0.005 and $\beta_{Latitude}$=-0.007,
+  $p$=0.005, respectively; Fig.~\ref{BIT}). For the scaling of link density and
   vulnerability in marine and terrestrial communities, the overall effect of
   latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
-  $p$=0.047; $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002 and
-  $\beta_{Latitude:Marine}$=0.009, $p$=0.047;
-  $\beta_{Latitude:Terrestrial}$=0.013, $p$=0.002, respectively) such that
+  $p$=0.037; $\beta_{Latitude:Terrestrial}$=0.011, $p$=0.005 and
+  $\beta_{Latitude:Marine}$=0.009, $p$=0.036;
+  $\beta_{Latitude:Terrestrial}$=0.011, $p$=0.005, respectively) such that
   there was little overall scaling relationship. In contrast, the scaling
@@
   exponents for marine and terrestrial communities were not significantly
-  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.028;
-  $\beta_{Latitude:Terrestrial}$=0.015, $p$=0.001).
+  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.021;
+  $\beta_{Latitude:Terrestrial}$=0.014, $p$=0.003).
 
@@
   ($\beta_0$=1.74, $p$\textless0.001; $\beta_0$=1.92, $p$\textless0.001; and
-  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}).
-  The strength of this scaling decreased towards the poles in estuarine,
-  lake, marine, and stream communities in each case
-  ($\beta_{Latitude}$=-0.012, $p$=0.007; $\beta_{Latitude}$=-0.018,
-  $p$\textless0.001; and $\beta_{Latitude}$=-0.012, $p$=0.007, respectively;
-  Fig~\ref{BIT}). In terrestrial communities, however, scaling was stronger
-  towards the  poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for
-  link density; $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for
-  generality; and $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.022 for
-  vulnerability, respectively).
+  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). The
+  strength of this scaling decreased towards the poles in estuarine, lake,
+  marine, and stream communities in each case ($\beta_{Latitude}$=-0.012,
+  $p$=0.007; $\beta_{Latitude}$=-0.018, $p$\textless0.001; and
+  $\beta_{Latitude}$=-0.012, $p$=0.007, respectively; Fig~\ref{BIT}). In
+  terrestrial communities, however, scaling was always stronger towards
+  the poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for link density;
+  $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for generality; and
+  $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for vulnerability,
+  respectively).
 
@@
   food webs the strength of this scaling did not
-  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.527 for
-  link density; $\beta_{Latitude}$=-0.001, $p$=0.521 for vulnerability; the
+  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.572 for
+  link density; $\beta_{Latitude}$=-0.001, $p$=0.566 for vulnerability; the
   best-fit model for generality did not include any terms for latitude in
@@
   although this trend was only significant in streams
-  ($\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
-  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.069 for link density;
-  $\beta_{Latitude:Stream}$=0.015, $p$\textless0.001 and
-  $\beta_{Latitude:Terrestrial}$=0.006, $p$=0.067 for vulnerability; Fig~\ref{BIT}).
+  ($\beta_{Latitude:Stream}$=0.011, $p$=0.002 and
+  $\beta_{Latitude:Terrestrial}$=0.005, $p$=0.136 for link density;
+  $\beta_{Latitude:Stream}$=0.012, $p$=0.002 and
+  $\beta_{Latitude:Terrestrial}$=0.005, $p$=0.133 for vulnerability; Fig~\ref{BIT}).
 
@@
 
-  Our results were inconsistent with the latitude-niche breadth hypothesis in estuarine, marine,
-  and terrestrial communities but consistent with the hypothesis of greater specialisation
-  in the tropics in stream and lake food webs. This suggests that different mechanisms may structure
-  food webs in different habitat types and that freshwater food webs in particular may be strongly
-  affected by seasonal variation. In addition, different relationships between latitude and niche
-  breadth in different habitat types goes some way towards explaining the equivocal support for
-  the opposing hypotheses of narrower niches in the tropics~\citep{Vazquez2004} and broader 
-  niche space in the tropics~\citep{Davies2007}; both have merit but appear
-  to apply to different systems.
+  Overall, our results were inconsistent with the latitude-niche breadth
+  hypothesis in estuarine, marine, and terrestrial communities but consistent
+  with the hypothesis of greater specialisation in the tropics in stream and
+  lake food webs. This suggests that different mechanisms may structure food
+  webs in different habitat types and that freshwater food webs in particular
+  may be strongly affected by seasonal variation. In addition, different
+  relationships between latitude and niche breadth in different habitat types
+  goes some way towards explaining the equivocal support for the opposing
+  hypotheses of narrower niches in the tropics~\citep{Vazquez2004} and broader
+  niche space in the tropics~\citep{Davies2007}; both have merit but appear to
+  apply to different systems.
 
@@
 \includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
-\caption{Scaling relationships for link density, generality (number of prey), 
-and vulnerability (number of predators) 
-against the proportions of basal resources (\% Basal), intermediate consumers (\% Intermediate), top 
-predators (\% Top), and species richness of a food web. 
-For each relationship, we show observed values corrected for
-ecosystem type and latitude (grey circles), as well as the overall scaling relationship (N=163 food webs). For
-the uncorrected values, see Fig.~\emph{S1}, \emph{Appendix S4}.}
+\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
+relative to species richness and the proportions of basal resources (\% Basal), intermediate 
+consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
+and vulnerability were re-scaled to remove the effects of latitude and, where applicable, ecosystem
+type by dividing the observed value of link density, generality, or vulnerability by species richness
+or the proportion of species at a given trophic level raised to an exponent including the effects of
+latitude, ecosystem type, and their interaction. Note that estuarine food webs were used as the intercept
+ecosystem type in all models, but that at most two ecosystem types had interactions between ecosystem type and
+latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
+we show these rescaled values (white circles), as well as the overall scaling relationship using estuarine
+ecosystems as a baseline (N=163 food webs). For a figure with the uncorrected values,
+see Fig.~\emph{S1}, \emph{Appendix S4}.}
 \label{props_v_lat}
 \end{figure}
-
-% \begin{figure}[H]
-% \includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
-% \caption{Scaling relationships for link density, generality (number of prey), 
-% and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
-% intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
-% For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
-% any effects of habitat type or latitude (N=163 food webs). }
-% \label{props_v_lat_obs}
-% \end{figure}
-
-% \newpage
 
@@
 \caption{Changes to the scaling of link density with species richness across ecosystem
-types and over latitude. We show the scaling exponent for species richness (black
-line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
-regardless of direction. The scaling relationships are based on N=163 empirical food webs. 
-Exponents for the scaling of generality and vulnerability with species richness were very 
-similar to those for link density, except for the scaling of generality in streams where 
-the size of the exponent increased towards the poles. See \emph{Fig. S2, Appendix 5} for 
-all scaling relationships.}
-\label{S}
-\end{figure}
+types and over latitude. We show the estimated scaling exponent for species richness (black
+line) with its 95\% confidence interval (in grey), based on N=163 empirical food webs.
+Latitude is given in degrees from the equator regardless of direction. The
+behaviour of exponents for the scaling of generality and vulnerability with
+species richness was very  similar to those for link density, except for the
+scaling of generality in streams where  the size of the exponent increased
+towards the poles. See \emph{Fig. S2, Appendix 5} for  all scaling
+relationships.} \label{S} \end{figure}
 
@@
 \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
-from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.
-Exponents for the scaling relationships of generality and vulnerability with each proportion were very
-similar to those of the scaling relationships with link density, except for the scaling of generality
-with the proportion of top predators where there was no effect of latitude on the size of the exponent
-in any ecosystem type. See \emph{Figs. S3-S5, Appendix 5} for all scaling relationships.}
+\caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
+consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
+we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
+on N=163 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
+The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
+proportion was very similar to those of the scaling relationships with link density, except for the 
+scaling of generalitywith the proportion of top predators where there was no effect of latitude on the 
+size of the exponent in any ecosystem type. See \emph{Figs. S3-S5, Appendix 5} for all scaling relationships.}
 \label{BIT}

### 2015-06-22 manuscript/supplement.tex
updated figures and compiled

@@
 
+\begin{document}
+
 \title{Supplementary Information}
-\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
-\date{$^1$School of Biological Sciences\\University of Canterbury\\
-Private Bag 4800\\Christchurch 8140, New Zealand}
-\medskip$^2$Department of Biology\\Life Science Centre\\
-Dalhousie University\\1355 Oxford St.\\P0 BOX 15000\\
-Halifax, NS B3H 4R2\\Canada\\}
+\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
+\date{\small$^1$School of Biological Sciences\\University of Canterbury\\
+Private Bag 4800\\Christchurch 8140, New Zealand \\
+\medskip$^2$Department of Biology\\
+Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
+Halifax NS, B3H 4R2, Canada\\
+\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
+Private Bag 4800\\Christchurch 8140, New Zealand \\}
 
-\begin{document}
 \maketitle
@@
 \beginsupplement
-\begin{landscape}
+% \begin{landscape}
 \subsection*{Appendix S1: Details of Food Web Sources and Selection}
@@
 
+\newpage
+
 \subsection*{Appendix S4: Supplemental Figures}
 
-\begin{figure}[H]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
+\begin{figure}[h]
+\centerline{\includegraphics*[width=.75\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}}
 \caption{Scaling relationships for link density, generality (number of prey), 
@@
 \begin{figure}[h]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
@@
 
-\begin{figure}[!H]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
+\begin{figure}[!h]
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
@@
 \begin{figure}[h]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
@@
 
-\begin{figure}[h]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
+\begin{figure}[!h]
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
@@
 
+\newpage
+
+\bibliographystyle{jae}%Compile with jae.bst style file
+\bibliography{noISN}% your .bib file(s)
+
 \end{document}

### 2015-06-22 code/TL_observedfits.py

@@ -284,7 +284,7 @@ def scaleplots(rawdatafile,outfile,Bformat,predfolder):
 
   grace.multi(rows=3,cols=4,vgap=.04,hgap=.04)
 
-  grace.set_col_yaxislabel(col=0,rowspan=(0,2),label='Corrected observed value',place='normal',just=2,char_size=1,perpendicular_offset=0.06)
+  grace.set_col_yaxislabel(col=0,rowspan=(0,2),label='Re-scaled value',place='normal',just=2,char_size=1,perpendicular_offset=0.06)
 
   grace.hide_redundant_xticklabels()
   grace.hide_redundant_yticklabels()

### 2015-06-22 manuscript/latitudepaper.tex
updated figures and compiled
took care of the easy fixes

@@
 \begin{figure}[h]
-\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}
+\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
-and vulnerability were re-scaled to remove the effects of latitude and, where applicable, ecosystem
-type by dividing the observed value of link density, generality, or vulnerability by species richness
-or the proportion of species at a given trophic level raised to an exponent including the effects of
-latitude, ecosystem type, and their interaction. Note that estuarine food webs were used as the intercept
-ecosystem type in all models, but that at most two ecosystem types had interactions between ecosystem type and
+and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
+type. As the these relationships take the form of power laws, we did this by dividing the food-web
+property (e.g. link density) by the predictor (e.g. \% Basal) raised to an exponent including the 
+effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
+type and latitude. Note that in all cases estuarine food webs were used as the baseline 
+ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
 latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
-we show these rescaled values (white circles), as well as the overall scaling relationship using estuarine
-ecosystems as a baseline (N=163 food webs). For a figure with the uncorrected values,
+we show the rescaled values (white circles) as well as the overall scaling relationship using estuarine
+ecosystems as a baseline (black line, N=163 food webs). For a figure with the uncorrected values,
 see Fig.~\emph{S1}, \emph{Appendix S4}.}
@@
 scaling of generality in streams where  the size of the exponent increased
-towards the poles. See \emph{Fig. S2, Appendix 5} for  all scaling
+towards the poles. See Fig.~\emph{S2, Appendix 5} for  all scaling
 relationships.} \label{S} \end{figure}
@@
 proportion was very similar to those of the scaling relationships with link density, except for the 
-scaling of generalitywith the proportion of top predators where there was no effect of latitude on the 
-size of the exponent in any ecosystem type. See \emph{Figs. S3-S5, Appendix 5} for all scaling relationships.}
+scaling of generality with the proportion of top predators where there was no effect of latitude on the 
+size of the exponent in any ecosystem type. See Figs.~\emph{S3-S5, Appendix 5} for all scaling relationships.}
 \label{BIT}

### 2015-06-22 manuscript/supplement.tex
took care of the easy fixes

@@
 
-  We combined published food webs from~\citet{GlobaWeb} (GlobalWeb),~\citet{Brose2006} (Brose), 
-  and~\citet{Dunne2013} (Dunne).
+  We combined published food webs from~\citet{GlobaWeb},~\citet{Brose2006}, 
+  and~\citet{Dunne2013}.
   Of the 385 food webs available from~\citet{Globalweb}, 122 were rejected because their original
@@
   species only. In addition, we included the 96 webs from~\citet{Brose2006}, which were originally
-  collected to XXXYYYY. This gave us a database of 259 webs. However, as we wished to use the
+  collected to XXXYYYY. This gave us a database of 259 webs. As we wished to use the
   logarithmic form of power-law relationships, we then eliminated any food web which did not have
@@
 
- (See Table S1 for a list of rejected webs and reasons for their
-  exclusion.)
+ See Table S1 for a list of rejected webs and reasons for their
+  exclusion.
 
@@
     In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
-    species richness.
+    species richness. We then repeated this analysis 
+    to model the scaling of link density, generality, 
+    and vulnerability with the proportions of basal 
+    resources, intermediate consumers, and top predators
+    in a food web.
 
@@
     When considering the relationships between species richness or the proportions 
-    of basal resources, intermediate consumers, or top predators and all response variables 
+    of basal resources, intermediate consumers, or top predators, and all response variables 
     (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
@@
     relationship was robust to the removal of three outliers (based on Cook's Distance). 
-    There were also relationships between latitude and link density and latitude and vulnerability
+    There were also relationships between latitude and link density and between latitude and vulnerability
     in stream food webs, but these trends were non-signficant after the removal of three outliers.
@@
 \centerline{\includegraphics*[width=.75\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}}
-\caption{Scaling relationships for link density, generality (number of prey), 
-and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
+\caption{Scaling relationships for link density, generality, 
+and vulnerability relative to species richness and the proportions of basal resources (\% Basal),
 intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
-For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
-any effects of habitat type or latitude (N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
+For each relationship, we show observed values (white circles) and 
+a simplified form of the scaling relationship described in equation XX (\emph{Main Text}), neglecting 
+any effects of habitat type or latitude (black line, N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
 observed values correcting for the effects of habitat type and latitude. }
@@
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for species richness (black
-line) with a 95\% confidence interval (in grey). Latitude is given in degrees from the equator
-regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
+types and over latitude. For each property we show the estimated scaling exponent for species richness (black
+line) with its 95\% confidence interval (in grey),
+based on N=163 empirical food webs. Latitude is 
+given in degrees from the equator
+regardless of direction.}
 \label{S}
@@
 types and over latitude. For each property we show the scaling exponent for the proportion of
-basal resources (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
-from the equator regardless of direction. The scaling relationships are based on N=163 empirical food webs.}
+basal resources (black line) with its 95\% confidence interval (in grey), based on N=163 
+empirical food webs. Latitude is given in degrees
+from the equator regardless of direction.}
 \label{B}
@@
 types and over latitude. For each property we show the scaling exponent for the proportion of
-intermediate consumers (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
-from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
+intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
+N=163 empirical food webs. Latitude is given in degrees
+from the equator regardless of direction.}
 \label{I}
@@
 types and over latitude. For each property we show the scaling exponent for the proportion of
-top predators (black line) with a 95\% confidence interval (in grey). Latitude is given in degrees
-from the equator regardless of direction. The scaling relationships are based on N=163 empiricl food webs.}
+top predators (black line) with its 95\% confidence interval (in grey), based on N=163 
+empirical food webs. Latitude is given in degrees
+from the equator regardless of direction.}
 \label{T}

### 2015-06-22 manuscript/supplement.tex
Got the correct reference for Brose

@@
   these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
-  species only. In addition, we included the 96 webs from~\citet{Brose2006}, which were originally
-  collected to XXXYYYY. This gave us a database of 259 webs. As we wished to use the
-  logarithmic form of power-law relationships, we then eliminated any food web which did not have
-  at least one each of basal resources, intermediate consumers, and top predators (to obtain non-zero
-  proportions of each category). Our final sample size was thereby reduced to 163 food webs.
+  species only. In addition, we included 12 of the 96 webs from~\citet{Brose2005}, which were originally
+  collected to test the relationship between consumer and
+  resources body sizes. The remaining webs the~\citet{Brose2005}
+  dataset were also included in the~\citet{GlobalWeb} 
+  dataset. This gave us a database of 259 webs. As we
+  wished to use the logarithmic form of power-law
+  relationships, we then eliminated any food web which
+  did not have at least one each of basal resources,
+  intermediate consumers, and top predators (to obtain 
+  non-zero proportions of each category). Our final sample
+  size was thereby reduced to 163 food webs.
 

### 2015-06-22 manuscript/coverletter.tex
Second try on coverletter

@@
 We are happy to invite you to consider our manuscript 
-``\mytitle'' for publication in the Theoretical Biology section of the \emph{\myjournal}.
+``\mytitle'' for publication in the Population and Community Ecology section of the \emph{\myjournal}.
+
+Our study aims to combine two well-established but disparate ecological themes, namely the analysis of macroecological gradients and the search for general laws governing the structure of communities, as measured through food webs (networks of who eats whom).
+In particular, we were interested in the possibility of a link between the well-known latitudinal gradients in species richness of some taxa (e.g., birds, land plants) and the scaling relationships between species richness and food-web structure.
+With regard to the former, one  hypothesized mechanism for greater species richness in the tropics is the latitude-niche-breadth hypothesis, which predicts that the greater stability of temperature and productivity in the tropics will permit species to evolve narrower niches and therefore more finely partition habitats.
+If this hypothesis holds true, then tropical species should be more specialized than their high-latitude counterparts.
+
+In terms of a food web, this means that we would naively expect that tropical species will have relatively fewer feeding links than polar species.
+However, the number of feeding links in which a species is involved is known to scale with the number of species in the community food web following a power law.
+Therefore we also expect that species in tropical food webs will participate in many feeding links by virtue of their speciose communities.
+This apparent paradox can be resolved by adding an effect of latitude to the exponent of the power law.
+We tested for the impact of such an exponent, as well as potential interactions between the effects of latitude and ecosystem type on scaling laws.
+
+We found that, in general, there was little effect of latitude on scaling relationships between diet breadth and species richness.
+If diet breadth may be taken as a measure of a species' Eltonian (biotic) niche, this means that our results are inconsistent with the latitude-niche-breadth hypothesis.
+Ecosystem type, on the other hand, had a greater impact on scaling exponents, suggesting that different processes may structure food webs in different habitats.
+
+Our results are the pinnacle of interestingness and you should publish them before we decide to give them to Nature instead.
+Everyone will love us and then the world will shower me with options for my future.
+That's how this works, right?
 

### 2015-06-24 manuscript/coverletter.tex
Updated coverletter, results in main text

@@
 
-\begin{letter}{\bf RE: \mytitle\\
-               ~~~~~~~Cirtwill, Alyssa R; Stouffer, Daniel B; Romanuk, Tamara N\\
-               \vspace*{20pt}
-               Professor Spencer C.H. Barrett\\
-               Editor-in-Chief, Proceedings of the Royal Society B\\
+\begin{letter}{\bf Professor Spencer C.H. Barrett\\
+               Editor-in-Chief\\
+               Proceedings of the Royal Society B\\
                6-9 Carlton House Terrace\\
@@
 
-Our study aims to combine two well-established but disparate ecological themes, namely the analysis of macroecological gradients and the search for general laws governing the structure of communities, as measured through food webs (networks of who eats whom).
-In particular, we were interested in the possibility of a link between the well-known latitudinal gradients in species richness of some taxa (e.g., birds, land plants) and the scaling relationships between species richness and food-web structure.
-With regard to the former, one  hypothesized mechanism for greater species richness in the tropics is the latitude-niche-breadth hypothesis, which predicts that the greater stability of temperature and productivity in the tropics will permit species to evolve narrower niches and therefore more finely partition habitats.
-If this hypothesis holds true, then tropical species should be more specialized than their high-latitude counterparts.
+Our study aims to combine two well-established but disparate ecological
+themes, namely the analysis of macroecological gradients and the search for
+general laws governing the structure of food webs (networks of who eats whom
+within a community). In particular, we were interested in the possibility of a
+link between the well-known latitudinal gradients in species richness of some
+taxa (e.g., birds, land plants) and the scaling relationships between species
+richness and food-web structure. With regard to the former, one  hypothesized
+mechanism for greater species richness in the tropics is the latitude-niche-
+breadth hypothesis, which predicts that the greater stability of temperature
+and productivity in the tropics will permit species to evolve narrower niches
+and therefore more finely partition habitats. If this hypothesis holds true,
+then tropical species should be more specialized than their high-latitude
+counterparts. In terms of a food web, this means that we would naively expect
+that tropical species will have relatively fewer feeding links than polar
+species. However, the number of feeding links in which a species is involved
+is known to scale with the number of species in the community food web
+following a power law. Therefore we also naively expect that species in
+tropical food webs will participate in many feeding links by virtue of their
+speciose communities. This apparent paradox can be resolved by adding an
+effect of latitude to the exponent of the power law. We tested for the impact
+of such an exponent, as well as potential interactions between the effects of
+latitude and ecosystem type on scaling laws.
 
-In terms of a food web, this means that we would naively expect that tropical species will have relatively fewer feeding links than polar species.
-However, the number of feeding links in which a species is involved is known to scale with the number of species in the community food web following a power law.
-Therefore we also expect that species in tropical food webs will participate in many feeding links by virtue of their speciose communities.
-This apparent paradox can be resolved by adding an effect of latitude to the exponent of the power law.
-We tested for the impact of such an exponent, as well as potential interactions between the effects of latitude and ecosystem type on scaling laws.
+In general we found little evidence of an effect of latitude on scaling
+relationships between diet breadth and species richness, implying that
+latitudinal variation in food-web structure may be driven purely by
+latitudinal gradients in species richness. If diet breadth may be taken as a
+measure of a species' Eltonian (biotic) niche, this means that our results are
+inconsistent with the latitude-niche-breadth hypothesis. Ecosystem type, on
+the other hand, had a greater impact on scaling exponents, suggesting that
+different processes may structure food webs in different habitats. Indeed,
+freshwater food webs departed from the overall trend and showed strong effects
+of latitude on scaling relationships. In these food webs alone was the
+latitude-niche-breadth hypothesis supported by our results.
 
-We found that, in general, there was little effect of latitude on scaling relationships between diet breadth and species richness.
-If diet breadth may be taken as a measure of a species' Eltonian (biotic) niche, this means that our results are inconsistent with the latitude-niche-breadth hypothesis.
-Ecosystem type, on the other hand, had a greater impact on scaling exponents, suggesting that different processes may structure food webs in different habitats.
-
-Our results are the pinnacle of interestingness and you should publish them before we decide to give them to Nature instead.
-Everyone will love us and then the world will shower me with options for my future.
-That's how this works, right?
-
-We believe that our study will be of interest not only to theory-focused biologists but also to general readers
-of \emph{\myjournal} as it deals with global trends in the structure of ecological communities. 
-Specifically, we address the impact of latitude and habitat type on known scaling relationships between empirical
-food-web structure and species richness. Although latitude (as a proxy for temperature, seasonality, and primary 
-productivity) is expected to drive trends in niche size (here measured as the number of feeding links for any 
-given species), we instead show that habitat type has the stronger influence on scaling between niche size and 
-species richness. This suggests that there may indeed be general rules governing the structure of food webs but 
-that these rules differ between different habitat types.
-
-Our paper thus contributes to the discussions of both the latitude-niche-breadth hypothesis and scaling
-laws in food-web structure, as well as being potentially applicable to researchers exploring community 
-structure and specialization in a variety of different systems. We hope you will agree that this broad relevance
-and the novelty of our results justify our manuscript's inclusion in \emph{\myjournal}.
+By linking macroecology and food-web ecology, we believe that our study will
+be of interest to ecologists, theory-focused biologists, and to general
+readers of \emph{\myjournal}. Our results are potentially applicable to
+researchers exploring community structure and specialization in a variety of
+different systems and also provide a new perspective on the debate over the
+latitude-niche-breadth hypothesis. We hope you will agree that this broad
+relevance and the novelty of our results justify consideration of our
+manuscript's inclusion in \emph{\myjournal}.
 

### 2015-06-24 manuscript/latitudepaper.tex
Updated coverletter, results in main text

@@
   Link density, generality, and vulnerability each increased with increasing
-  species richness ($\beta_0$=0.643, $p$\textless0.001; $\beta_0$=0.599,
-  $p$\textless0.001; and $\beta_0$=0.643, $p$\textless0.001, respectively;
+  species richness ($\beta_0$=0.644, $p$\textless0.001; $\beta_0$=0.557,
+  $p$\textless0.001; and $\beta_0$=0.644, $p$\textless0.001, respectively;
   Fig~\ref{props_v_lat}).For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
-  ($\beta_{Latitude}$=-0.001, $p$=0.232 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=0.257 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=0.233 for vulnerability; Fig.~\ref{S}). In
+  ($\beta_{Latitude}$=-0.001, $p$=0.206 for link density;
+  $\beta_{Latitude}$=-0.001, $p$=0.373 for generality; and
+  $\beta_{Latitude}$=-0.001, $p$=0.207 for vulnerability; Fig.~\ref{S}). In
   lake food webs, however, the scaling of each property was stronger towards
-  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.006;
+  the poles ($\beta_{Latitude:Lake}$=0.005, $p$=0.005;
   $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001; and
@@
   Unlike species richness, only generality showed an overall increase with increasing
-  proportions of basal resources in a web ($\beta_0$=-0.024, $p$=0.838;
-  $\beta_0$=0.333, $p$=0.012; and $\beta_0$=-0.024, $p$=0.839 for link
+  proportions of basal resources in a web ($\beta_0$=-0.030, $p$=0.801;
+  $\beta_0$=0.328, $p$=0.013; and $\beta_0$=-0.030, $p$=0.802 for link
   density, generality, and vulnerability, respectively;
@@
   lake, and stream communities and became more negative towards the poles
-  ($\beta_{Latitude}$=-0.007, $p$=0.005 and $\beta_{Latitude}$=-0.007,
+  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
   $p$=0.005, respectively; Fig.~\ref{BIT}). For the scaling of link density and
@@
   latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
-  $p$=0.037; $\beta_{Latitude:Terrestrial}$=0.011, $p$=0.005 and
-  $\beta_{Latitude:Marine}$=0.009, $p$=0.036;
-  $\beta_{Latitude:Terrestrial}$=0.011, $p$=0.005, respectively) such that
+  $p$=0.038; $\beta_{Latitude:Terrestrial}$=0.012, $p$=0.003 and
+  $\beta_{Latitude:Marine}$=0.009, $p$=0.037;
+  $\beta_{Latitude:Terrestrial}$=0.012, $p$=0.003, respectively) such that
   there was little overall scaling relationship. In contrast, the scaling
@@
   different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.021;
-  $\beta_{Latitude:Terrestrial}$=0.014, $p$=0.003).
+  $\beta_{Latitude:Terrestrial}$=0.014, $p$=0.002.
 
@@
   generally increased with the proportion of intermediate consumers in a web
-  ($\beta_0$=1.74, $p$\textless0.001; $\beta_0$=1.92, $p$\textless0.001; and
-  $\beta_0$=1.75, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). The
-  strength of this scaling decreased towards the poles in estuarine, lake,
-  marine, and stream communities in each case ($\beta_{Latitude}$=-0.012,
-  $p$=0.007; $\beta_{Latitude}$=-0.018, $p$\textless0.001; and
-  $\beta_{Latitude}$=-0.012, $p$=0.007, respectively; Fig~\ref{BIT}). In
-  terrestrial communities, however, scaling was always stronger towards
-  the poles ($\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for link density;
-  $\beta_{Latitude:Terrestrial}$=0.022, $p$=0.004 for generality; and
-  $\beta_{Latitude:Terrestrial}$=0.016, $p$=0.023 for vulnerability,
-  respectively).
+  ($\beta_0$=2.10, $p$\textless0.001; $\beta_0$=0.592, $p$=0.006; and
+  $\beta_0$=0.843, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
+  The best-fit models for link density and vulnerability did not include
+  any effect of latitude. In contrast, the strength of the scaling relationship
+  for generality increased weakly towards the poles in estuarine, marine, and
+  terrestrial food webs ($\beta_{Latitude}$=0.003, $p$=0.486) but decreased 
+  towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.019, $p$=0.027
+  and $\beta_{Latitude:Stream}$=-0.031, $p$=0.002; Fig~\ref{BIT}).
 
-  In contrast, link density, generality, and vulnerability decreased as the
-  proportion of top predators increased ($\beta_0$=-0.511, $p$\textless0.001;
-  $\beta_0$=-0.418, $p$\textless0.001; and $\beta_0$=-0.511, $p$\textless0.001
-  respectively; Fig~\ref{props_v_lat}). For estuarine, lake, and marine
-  food webs the strength of this scaling did not
-  vary significantly with latitude ($\beta_{Latitude}$=-0.001, $p$=0.572 for
-  link density; $\beta_{Latitude}$=-0.001, $p$=0.566 for vulnerability; the
-  best-fit model for generality did not include any terms for latitude in
-  any ecosystem type). In stream and terrestrial food webs, scaling was more
-  strongly negative in the tropics and did not differ from zero near the poles,
-  although this trend was only significant in streams
-  ($\beta_{Latitude:Stream}$=0.011, $p$=0.002 and
-  $\beta_{Latitude:Terrestrial}$=0.005, $p$=0.136 for link density;
-  $\beta_{Latitude:Stream}$=0.012, $p$=0.002 and
-  $\beta_{Latitude:Terrestrial}$=0.005, $p$=0.133 for vulnerability; Fig~\ref{BIT}).
+  In contrast to the generally positive scaling relationships above, link
+  density, generality, and vulnerability decreased as the proportion of top
+  predators increased ($\beta_0$=-0.584, $p$\textless0.001; $\beta_0$=-0.418,
+  $p$\textless0.001; and $\beta_0$=-0.585, $p$\textless0.001 respectively;
+  Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
+  strength of this scaling did not vary significantly with latitude
+  ($\beta_{Latitude}$=0.001, $p$=0.652 for link density;
+  $\beta_{Latitude}$=0.001, $p$=0.654 for vulnerability) except in stream food
+  webs, where scaling was more strongly negative in the tropics and near zero
+  near the poles ($\beta_{Latitude:Stream}$=0.010, $p$=0.006 for link density;
+  $\beta_{Latitude:Stream}$=0.010, $p$=0.007 for vulnerability;
+  Fig~\ref{BIT}). The best-fit model for generality did not include any terms
+  for latitude in any ecosystem type). In stream food webs, scaling was more
+  strongly negative in the tropics and did not differ from zero near the poles
 
@@
 
-  The lack of a latitudinal gradient in species richness in this dataset contrasts
-  strongly with other studies~\citep{Schemske2009,Macpherson2002,Kaufman1995}. As numbers of species and links included in a food web
-  vary strongly with sampling effort as well as with the underlying diversity of the study
-  area, it is possible that the lack of latitudinal trends here is a result of researchers
-  tending to expend similar amounts of sampling effort across studies. This could result in
-  food webs describing species-rich tropical communities omitting more species and links
-  than species-poor arctic communities. In addition, it is worth noting that gradients in
-  species richness are generally measured for a single taxonomic group at a time (e.g.~\citep{Kaufman1995}).
-  It is possible that these taxa are not well-represented in our food webs and that the
-  dominant taxa in them do not have an underlying latitudinal gradient in richness. 
-  In either case, the lack of a strong association between
-  species richness and latitude in any ecosystem type
-  means that any effect of latitude on other scaling 
-  relationships is not being driven by an underlying 
-  latitudinal gradient in species richness.
-  The lack of confounding effects of latitude allows us to 
-  more clearly assess effects of latitude on scaling with 
-  species richness and proportions of species in different 
-  trophic levels.
+  The lack of a latitudinal gradient in species richness in this dataset
+  contrasts strongly with other
+  studies~\citep{Schemske2009,Macpherson2002,Kaufman1995}. As numbers of
+  species and links included in a food web vary strongly with sampling effort
+  as well as with the underlying diversity of the study area, it is possible
+  that the lack of latitudinal trends here is a result of researchers tending
+  to expend similar amounts of sampling effort across studies. This could
+  result in food webs describing species-rich tropical communities omitting
+  more species and links than species-poor arctic communities. In addition, it
+  is worth noting that gradients in species richness are generally measured
+  for a single taxonomic group at a time
+  (e.g.~\citep{Schemske2009,Macpherson2002,Kaufman1995}). It is possible that
+  these taxa are not well-represented in our food webs and that the dominant
+  taxa in them do not have an underlying latitudinal gradient in richness.  In
+  either case, the lack of a strong association between species richness and
+  latitude in any ecosystem type means that any effect of latitude on other
+  scaling  relationships is not being driven by an underlying  latitudinal
+  gradient in species richness. The lack of confounding effects of latitude
+  allows us to  more clearly assess effects of latitude on scaling with
+  species richness and proportions of species in different  trophic levels.
 

### 2015-06-24 manuscript/latitudepaper.tex
found one ref

@@
   is worth noting that gradients in species richness are generally measured
-  for a single taxonomic group at a time
-  (e.g.~\citep{Schemske2009,Macpherson2002,Kaufman1995}). It is possible that
-  these taxa are not well-represented in our food webs and that the dominant
-  taxa in them do not have an underlying latitudinal gradient in richness.  In
-  either case, the lack of a strong association between species richness and
-  latitude in any ecosystem type means that any effect of latitude on other
-  scaling  relationships is not being driven by an underlying  latitudinal
-  gradient in species richness. The lack of confounding effects of latitude
-  allows us to  more clearly assess effects of latitude on scaling with
-  species richness and proportions of species in different  trophic levels.
+  for a single taxonomic group at a
+  time~\citep[e.g.]{Schemske2009,Macpherson2002,Kaufman1995}. It is possible
+  that these taxa are not well-represented in our food webs and that the
+  dominant taxa in them do not have an underlying latitudinal gradient in
+  richness.In either case, the lack of a strong association between species
+  richness and latitude in any ecosystem type means that any effect of
+  latitude on other scalingrelationships is not being driven by an
+  underlyinglatitudinal gradient in species richness. The lack of confounding
+  effects of latitude allows us tomore clearly assess effects of latitude on
+  scaling with species richness and proportions of species in differenttrophic
+  levels.
 
@@
   negative) in low-latitude stream ecosystems. This may imply that top predators
-  in high-latitude streams tend to be more generalist than their low-latitude equivalents.
+  in high-latitude streams tend to be more generalist than their low-latitude
+  equivalents~\citep{Winemiller2008}.
   More generally, the lack of correspondence between the scaling of food-web

### 2015-06-24 manuscript/latitudepaper.tex
The Brose webs aren't Brose webs

@@
   %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
-  Food webs --networks of feeding links between species-- have been used for several decades to summarise the structure of 
-  ecological communities~\citep{Petchey2008,Williams2000,Paine1966} and to understand how that structure relates to environmental variables 
-  such as habitat type~\citep{Shurin2006,Briand1983}, primary productivity~\citep{Vermaat2009,Thompson2005a,Townsend1998}, and climate~\citep{Baiser2012,Petchey2010}. The latter
-  variables in turn have strong gradients over latitude, with productivity and temperature both being higher in the tropics while 
-  climate is more variable at high latitudes~\citep{Field1998}. These variables affect both the resources available and species' 
-  metabolisms~\citep{Hechinger2011,White2011,OConnor2009,White2007}, and have been proposed as determinants of the strength of 
-  interspecific interactions~\citep{Lang2012,Schleuning2012,Schemske2009}. 
-  By modulating interactions between species, latitudinal gradients may also shape food-web structure.
-  Indeed, these latitudinal environmental gradients have been put forward as potential drivers for the 
-  latitudinal gradient in species richness, one of the most general and robust patterns in ecology~\citep{Schemske2009,Macpherson2002,Kaufman1995}.
+
+  Food webs --networks of feeding links between species-- have been used for
+  several decades to summarise the structure of  ecological
+  communities~\citep{Paine1966,Williams2000,Petchey2008} and to understand how
+  that structure relates to environmental variables  such as habitat
+  type~\citep{Briand1983,Shurin2006}, primary
+  productivity~\citep{Townsend1998,Thompson2005a,Vermaat2009}, and
+  climate~\citep{Petchey2010,Baiser2012}. The latter variables in turn have
+  strong gradients over latitude, with productivity and temperature both being
+  higher in the tropics while  climate is more variable at high
+  latitudes~\citep{Field1998}. These variables affect both the resources
+  available and species'
+  metabolisms~\citep{White2007,OConnor2009,Hechinger2011,White2011}, and have
+  been proposed as determinants of the strength of  interspecific
+  interactions~\citep{Schemske2009,Lang2012,Schleuning2012}.  By modulating
+  interactions between species, latitudinal gradients may also shape food-web
+  structure. Indeed, these latitudinal environmental gradients have been put
+  forward as potential drivers for the  latitudinal gradient in species
+  richness, one of the most general and robust patterns in
+  ecology~\citep{Kaufman1995,Macpherson2002,Schemske2009}.
 
@@
   For example,
-  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics(~\citealp{Dyer2007,Marra1997};
+  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics(~\citealp{Marra1997,Dyer2007};
   but see~\citealp{Schleuning2012}). However,
@@
     Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
-    sets to form ``trophic species'' webs ~\citep{Martinez1991,Vermaat2009,Dunne2004,Dunne2013}. As our study
+    sets to form ``trophic species'' webs ~\citep{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
     is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
@@
   species richness in particular is also known to vary systematically over
-  latitude~\citep{Schemske2009,Macpherson2002,Kaufman1995}, intuitively one
+  latitude~\citep{Kaufman1995,Schemske2009,Macpherson2002}, intuitively one
   might suspect that any relationship between food-web properties such as
@@
   contrasts strongly with other
-  studies~\citep{Schemske2009,Macpherson2002,Kaufman1995}. As numbers of
+  studies~\citep{Kaufman1995,Schemske2009,Macpherson2002}. As numbers of
   species and links included in a food web vary strongly with sampling effort
@@
   for a single taxonomic group at a
-  time~\citep[e.g.]{Schemske2009,Macpherson2002,Kaufman1995}. It is possible
+  time~\citep[e.g.]{Kaufman1995,Schemske2009,Macpherson2002}. It is possible
   that these taxa are not well-represented in our food webs and that the
@@
   be partly due to high-latitude species tending to switch between different
-  seasonally-available prey~\citep{Isaac2012,Wilhelm1999} while tropical
+  seasonally-available prey~\citep{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
   freshwater ecosystems may have more stable composition.
@@
   in high-latitude streams tend to be more generalist than their low-latitude
-  equivalents~\citep{Winemiller2008}.
+  equivalents~\citep{Winemiller2008}, perhaps due to prey-switching during seasonal
+  food shortages~\citep{Magalhaes1993}.
   More generally, the lack of correspondence between the scaling of food-web
@@
   trophic level suggests that the size and trophic breakdowns of a community can
-  provide different information about the breadth of niches in that community.
+  each provide different information~\citep{Downing2002}.
 

### 2015-06-24 manuscript/supplement.tex
The Brose webs aren't Brose webs

@@
 
-  We combined published food webs from~\citet{GlobaWeb},~\citet{Brose2006}, 
+  We combined published food webs from~\citet{GlobaWeb},~\citet{Riede2011}, 
   and~\citet{Dunne2013}.
@@
   these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
-  species only. In addition, we included 12 of the 96 webs from~\citet{Brose2005}, which were originally
+  species only. In addition, we included 30 of the 35 webs from~\citet{Riede2011}, which were originally
   collected to test the relationship between consumer and
@@
   dataset were also included in the~\citet{GlobalWeb} 
-  dataset. This gave us a database of 259 webs. As we
+  dataset. This gave us a database of 264 webs. As we
   wished to use the logarithmic form of power-law
@@
   non-zero proportions of each category). Our final sample
-  size was thereby reduced to 163 food webs.
+  size was thereby reduced to 197 food webs.
+
+% Tree hole and pitcher plant webs counted as "lakes", wetlands could be either lakesor streams depending on the study
 

### 2015-06-25 manuscript/coverletter.tex
Incorporated DBS changes

--- 2015-06-18 manuscript/coverletter.tex
@@
 
-\usepackage[britdate,alyssa-signature]{canterbury-letter}
+\usepackage[britdate]{canterbury-letter}
+% \usepackage[britdate,alyssa-signature]{canterbury-letter}
 \usepackage{times}
@@
 
-\newcommand{\mytitle}{\emph{Generality in food webs scales with species richness but not with latitude}}
+\newcommand{\mytitle}{\emph{Specialisation in food webs scales with species richness but not with latitude}}
 \newcommand{\myjournal}{\emph{Proceedings of the Royal Society B}}
@@
 We are happy to invite you to consider our manuscript 
-``\mytitle'' for publication in the Theoretical Biology section of the \emph{\myjournal}.
+``\mytitle'' for publication in the Population and Community Ecology section of the \myjournal.
 
-We believe that our study will be of interest not only to theory-focused biologists but also to general readers
-of \emph{\myjournal} as it deals with global trends in the structure of ecological communities. 
-Specifically, we address the impact of latitude and habitat type on known scaling relationships between empirical
-food-web structure and species richness. Although latitude (as a proxy for temperature, seasonality, and primary 
-productivity) is expected to drive trends in niche size (here measured as the number of feeding links for any 
-given species), we instead show that habitat type has the stronger influence on scaling between niche size and 
-species richness. This suggests that there may indeed be general rules governing the structure of food webs but 
-that these rules differ between different habitat types.
+Our study aims to combine two well-established but disparate ecological
+themes, namely the analysis of macroecological gradients and the search for
+general laws governing the structure of food webs (networks of who eats whom
+within a community). In particular, we explored the possibility of a link
+between the well-known latitudinal gradients in species richness of some taxa
+(e.g., birds, terrestrial plants) and the scaling relationships between
+species richness and food-web structure. With regard to the former, one
+hypothesized mechanism for greater species richness in the tropics is the
+latitude-niche-breadth hypothesis, which predicts that the greater stability
+of temperature and productivity in the tropics will permit species to evolve
+narrower niches and therefore more finely partition habitats. If this
+hypothesis holds true, then tropical species should be more specialized---have
+fewer feeding links---than their high-latitude counterparts. However, the
+number of feeding links in which a species is involved is also known to
+increase with the number of species in the community food web following a
+power law. Therefore we also naively expect that species in tropical food webs
+will participate in relatively many feeding links by virtue of their speciose
+communities. To address this apparent paradox, we tested for an effect of
+latitude on the strength of the relationship between specialisation and species 
+richness.
 
-Our paper thus contributes to the discussions of both the latitude-niche-breadth hypothesis and scaling
-laws in food-web structure, as well as being potentially applicable to researchers exploring community 
-structure and specialization in a variety of different systems. We hope you will agree that this broad relevance
-and the novelty of our results justify our manuscript's inclusion in \emph{\myjournal}.
+In general, we found little evidence of an effect of latitude on the
+relationship between specialisation and species richness, implying that
+latitudinal variation in food-web structure may be driven purely by
+latitudinal gradients in species richness. If diet breadth may be taken as a
+measure of a species' Eltonian (biotic) niche, this means that our results are
+food webs do not conform to the latitude-niche-breadth hypothesis. Ecosystem
+type, on the other hand, had a greater impact on scaling exponents, suggesting
+that different processes may structure food webs in different habitats.
+Indeed, freshwater food webs departed from the overall trend and showed strong
+effects of latitude on scaling relationships. Only in these food webs was the
+latitude-niche-breadth hypothesis.
+
+By linking macroecology and food-web ecology, we believe that our study will
+be of interest to ecologists, theory-focused biologists, and to general
+readers of \myjournal. Our results are potentially applicable to researchers
+exploring community structure and specialization in a variety of different
+systems and also provide a new community-wide perspective on the validity of
+the latitude-niche-breadth hypothesis. We hope you will agree that this broad
+relevance and the novelty of our results justify consideration of our
+manuscript for \myjournal.
 
@@
 
-\closing{Regards,}
+% \closing{Regards,}
 

### 2015-06-25 manuscript/coverletter.tex
one more tiny change

@@
 latitudinal gradients in species richness. If diet breadth may be taken as a
-measure of a species' Eltonian (biotic) niche, this means that our results are
-food webs do not conform to the latitude-niche-breadth hypothesis. Ecosystem
+measure of a species' Eltonian (biotic) niche, this means that food webs
+in general do not conform to the latitude-niche-breadth hypothesis. Ecosystem
 type, on the other hand, had a greater impact on scaling exponents, suggesting

### 2015-06-28 manuscript/supplement.tex
Updated pred-prey lists and code for new updated web

@@
   We combined published food webs from~\citet{GlobaWeb},~\citet{Riede2011},
-  and~\citet{Dunne2013}.
-  Of the 385 food webs available from~\citet{Globalweb}, 122 were rejected because their original
-  source was unpublished or could not be retrieved. We further eliminated 13 source or sink webs
-  (which describe feeding links flowing from or to a particular resource or top predator rather
-  than the interactions of an entire community), 8 plant-pollinator webs, 34 host-parasitoid webs,
-  and 2 networks describing competitive interactions. Finally, we eliminated 2 webs describing 
-  inferred interactions in an extinct community, 8 ``generalized schemes'' that were not based
-  on direct field data, and 2 webs where it was not clear which of several described study sites
-  were used to construct the food web (and therefore the latitude of the food web could not be 
-  included). This left us with 156 webs from~\citet{GlobalWeb}.
+  and~\citet{Dunne2013}. Of the 358 food webs available
+  from~\citet{Globalweb}, 59 were rejected because their original source was
+  unpublished or could not be retrieved. We further eliminated 13 source or
+  sink webs (which describe feeding links flowing from or to a particular
+  resource or top predator rather than the interactions of an entire
+  community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
+  describing competitive interactions. Finally, we eliminated 2 webs
+  describing  inferred interactions in an extinct community, 10 ``generalized
+  schemes'' that were not based on direct field data, and 4 webs where it was
+  not clear which of several described study sites were used to construct the
+  food web (and therefore the latitude of the food web could not be
+  included). This left us with 226 webs from~\citet{GlobalWeb}.
 
-  To these, we added 7 webs from~\citet{Dunne2013} that were originally used to assess the roles
-  of parasites within food webs. As all but 3 of the webs from~\citet{GlobalWeb} contained only
-  free-living species, we removed the the parasites (and all interactions involving them) from
-  these webs (and the 3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living 
-  species only. In addition, we included 30 of the 35 webs from~\citet{Riede2011}, which were originally
-  collected to test the relationship between consumer and
-  resources body sizes. The remaining webs the~\citet{Brose2005}
-  dataset were also included in the~\citet{GlobalWeb} 
-  dataset. This gave us a database of 264 webs. As we
-  wished to use the logarithmic form of power-law
-  relationships, we then eliminated any food web which
-  did not have at least one each of basal resources,
-  intermediate consumers, and top predators (to obtain 
-  non-zero proportions of each category). Our final sample
-  size was thereby reduced to 197 food webs.
+  To these, we added 7 webs from~\citet{Dunne2013} that were originally used
+  to assess the roles of parasites within food webs. As all but 3 of the webs
+  from~\citet{GlobalWeb} contained only free-living species, we removed the
+  the parasites (and all interactions involving them) from these webs (and the
+  3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living
+  species only. In addition, we included 30 of the 40 webs
+  from~\citet{Riede2011}, which were originally collected to test the
+  relationship between consumer and resources body sizes. Nine of the
+  remaining webs in the~\citet{Riede2011} dataset were also included in
+  the~\citet{GlobalWeb}  dataset, and the last web was derived from an
+  unpublished source. This gave us a database of 263 webs. As we wished to use
+  the logarithmic form of power-law relationships, we then eliminated any food
+  web which did not have at least one each of basal resources, intermediate
+  consumers, and top predators (to obtain  non-zero proportions of each
+  category). Our final sample size was thereby reduced to XXX food webs.
 

### 2015-06-28 code/food_web_properties.py

@@ -97,6 +97,7 @@ def clustering(directory,item):
   return Clus
 
 def food_web_properties(directory,item,G):
+
   Clus=clustering(directory,item)
 
   N=len(G.nodes())
@@ -195,31 +196,22 @@ def websorter(metafile,directory):
   for line in f:
     newline=line.split('\n')[0]
     items=newline.split('*')
-    if items[17][:3] in ['Use','use']:
+    if items[9][:3] in ['Use','use']:
       webno=items[0]
       try:
         webfile='WEB'+str(int(webno))+'.web'
       except:
         webfile=webno+'.web'
       uselist.append(webfile)
-      ecotype=items[3]
-      Humans=items[19]
-      Site=items[21]
-      if ecotype in ['lake','stream']:
-        ecotype2='freshwater'
-      else:
-        ecotype2=ecotype
-      year=items[6]
-      latitude=items[10]
-      info=[ecotype,ecotype2,year,Humans,Site,latitude]
+      ecotype=items[2]
+      Site=items[10]
+      latitude=items[5]
+      info=[ecotype,Site,latitude]
       infodict[webfile]=info
   f.close()
 
   header=['Web',
           'Ecotype',
-          'Ecotype2',
-          'Year_pub',
-          'Humans',
           'Site',
           'Latitude',
           'Species',
@@ -271,10 +263,9 @@ def websorter(metafile,directory):
   outfile.close()
 
 
-
 def main():
   
-  metafile = '../mod_data/sup_data/food_web_notes.csv'
+  metafile = '../mod_data/sup_data/food_web_notes_updated.csv'
   directory = '../mod_data/lists/pred-prey-lists-to-use/'
   motifdir = '../mod_data/Roles/'
 

### 2015-06-28 code/listcreator.py

@@ -26,7 +26,7 @@ def create_predprey_list(webfile):
   predpreydict={}
   specieslist=set()
 
-  print webfile
+  # print webfile
 
   for item in rowdict[predators]:
     specieslist.add(item)
@@ -51,7 +51,8 @@ def create_predprey_list(webfile):
   try:
     webname=re.findall(r'(WEB\w+)',webfile)[0]+'.web'
   except:
-    webname='Carpinteria2006.web' 
+    webname=webfile.split('/')[-1].split('.')[0] 
+    print webname
 
   decodefile=open('../mod_data/species-keys/all-webs/'+webname,'w')
   for species in specieslist:

### 2015-06-28 code/power_analyses.R
Now checking power law vs logarithmic for all properties vs. TL's not TLs vs S

@@ -141,6 +141,7 @@ power_analysis = function (x, y, CI_boot = TRUE, diagno = TRUE, output_plot = FA
 ##############################################################################################
 ##############################################################################################
 
+  print('species')
 
   power_analysis(data$Species,data$LS)   #To determine whether scaling of LS~S is more lognormal or nonlinear.
                         #It is lognormal, AIC=766.8 vs 1150.3 with nonlinear.
@@ -149,14 +150,29 @@ power_analysis = function (x, y, CI_boot = TRUE, diagno = TRUE, output_plot = FA
   power_analysis(data$Species,data$Vul)   #To determine whether scaling of Vul~S is more lognormal or nonlinear.
                         #It is lognormal, AIC=766.9 vs 1150.6
 
+  print('Basal')
+
+  power_analysis(data$Basal,data$LS)   #To determine whether scaling of LS~S is more lognormal or nonlinear.
+                        #It is lognormal, AIC=766.8 vs 1150.3 with nonlinear.
+  power_analysis(data$Basal,data$Gen)   #To determine whether scaling of Gen~S is more lognormal or nonlinear.
+                        #It is lognormal, AIC=1037.4 vs 1265.9 with nonlinear.
+  power_analysis(data$Basal,data$Vul)   #To determine whether scaling of Vul~S is more lognormal or nonlinear.
 
 
+  print('Intermediate')
 
-  power_analysis(data$Species,data$Basal)   #To determine whether scaling of LS~S is more lognormal or nonlinear.
-                        #It is lognormal, AIC=-141 vs -112 with nonlinear.
-  # power_analysis(data$Species,data$Herbivores)   #To determine whether scaling of Gen~S is more lognormal or nonlinear.
-  # Too many zeros.
-  power_analysis(data$Species,data$Intermediate)   #To determine whether scaling of Vul~S is more lognormal or nonlinear.
-                        #It is lognormal, AIC=-121.4 vs -72.6
-  power_analysis(data$Species,data$Toppreds)   #To determine whether scaling of Vul~S is more lognormal or nonlinear.
-                        #It is lognormal, AIC=-163.5 vs -138.7
+  power_analysis(data$Intermediate,data$LS)   #To determine whether scaling of LS~S is more lognormal or nonlinear.
+                        #It is lognormal, AIC=766.8 vs 1150.3 with nonlinear.
[…]

### 2015-06-28 code/recreate_with_subset.R
updated all the models with the new dataset. Not much change.

@@ -7,11 +7,13 @@
     ,na.action=na.fail))
   ls_dredge=dredge(LS_full,rank=AIC)
   if(infile=='../mod_data/summary-properties.tsv'){
+    # TS - updated 29/06/2015
     LS_min =with(data,lm(log(LS)~log(Species)
-    +log(Species):(Lake+Terr)
+    +log(Species):Lake
     +log(Species):Latitude
     +log(Species):Latitude:Lake
     ,na.action=na.fail))    } else {
+      # non-TS - updated 29/06/2015
     LS_min=with(data,lm(log(LS)~log(Species)
     +log(Species):(Lake+Terr)
     +log(Species):Latitude
@@ -20,17 +22,16 @@
 
     # cutoff<- 4/((nrow(data)-length(LS_min$coefficients)-2)) 
     # plot(LS_min, which=4, cook.levels=cutoff)
-    # #  57, 66, 138 are outliers.
-    # if(infile=='../mod_data/summary-properties.tsv'){
-    #   subset=data[-c(57,127,138),]
-    # } else {
-    #   subset=data[-c(57,66,138),]
-    # }
+    if(infile!='../mod_data/summary-properties.tsv'){
+      # The only change is that the different intercept for terrestrial is not sig.
+      subset=data[-c(60,136,163),]
+      subLS_min=(with(subset,lm(log(LS)~log(Species)
+      +log(Species):(Lake+Terr)
+      +log(Species):Latitude
+      +log(Species):Latitude:Lake,na.action=na.fail)))
+    }
 
-    # subLS_min=(with(subset,lm(log(LS)~log(Species)
-    # +log(Species):(Lake+Terr)
-    # +log(Species):Latitude
-    # +log(Species):Latitude:Lake,na.action=na.fail)))
+
   obs_LS=(with(data,lm(log(LS)~log(Species),na.action=na.fail)))
 
   Gen_full=with(data,lm(log(Gen)~log(Species)
@@ -40,13 +41,26 @@
     ,na.action=na.fail))
   g_dredge=dredge(Gen_full,rank=AIC)
   if(infile=='../mod_data/summary-properties.tsv'){
+    # TS - updated 29/06/2015
     Gen_min=with(data,lm(log(Gen)~log(Species)
       +log(Species):(Lake+Stream)
       +log(Species):Latitude
-      +log(Species):Latitude:Lake
[…]

### 2015-06-29 manuscript/latitudepaper.tex
Updated text

@@
 
-\title{Generality in food webs scales with species richness but not with latitude}
-\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
+\title{Specialisation in food webs scales with species richness but not with latitude}
+\author{Alyssa R. Cirtwill$^{1,2,3}$, Daniel B. Stouffer$^{1,2}$, Tamara N. Romanuk$^{3}$}
 \date{\small$^1$School of Biological Sciences\\University of Canterbury\\
 Private Bag 4800\\Christchurch 8140, New Zealand \\
-\medskip$^2$Department of Biology\\
+\medskip$^2$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
+Private Bag 4800\\Christchurch 8140, New Zealand \\
+\medskip$^3$Department of Biology\\
 Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
-Halifax NS, B3H 4R2, Canada\\
-\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
-Private Bag 4800\\Christchurch 8140, New Zealand \\}
+Halifax NS, B3H 4R2, Canada\\}
 
@@
   Link density, generality, and vulnerability each increased with increasing
-  species richness ($\beta_0$=0.644, $p$\textless0.001; $\beta_0$=0.557,
-  $p$\textless0.001; and $\beta_0$=0.644, $p$\textless0.001, respectively;
+  species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
+  $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
   Fig~\ref{props_v_lat}).For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
-  ($\beta_{Latitude}$=-0.001, $p$=0.206 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=0.373 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=0.207 for vulnerability; Fig.~\ref{S}). In
+  ($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
+  $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
+  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). In
   lake food webs, however, the scaling of each property was stronger towards
-  the poles ($\beta_{Latitude:Lake}$=0.005, $p$=0.005;
-  $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001; and
-  $\beta_{Latitude:Lake}$=0.005, $p$=0.005, respectively). In stream food
+  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
+  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
+  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
   webs, generality increased more rapidly towards the poles
-  ($\beta_{Latitude:Stream}$=0.007, $p$\textless0.001) while link density and
+  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
   vulnerability did not vary with latitude.
 
-  Unlike species richness, only generality showed an overall increase with increasing
-  proportions of basal resources in a web ($\beta_0$=-0.030, $p$=0.801;
-  $\beta_0$=0.328, $p$=0.013; and $\beta_0$=-0.030, $p$=0.802 for link
-  density, generality, and vulnerability, respectively;
+  Unlike species richness, only generality showed an overall increase with
+  increasing proportions of basal resources in a web ($\beta_0$=0.019,
+  $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
+  link density, generality, and vulnerability, respectively;
   Fig.~\ref{props_v_lat}). In each case, however, there were substantial
@@
   lake, and stream communities and became more negative towards the poles
-  ($\beta_{Latitude}$=-0.007, $p$=0.006 and $\beta_{Latitude}$=-0.007,
-  $p$=0.005, respectively; Fig.~\ref{BIT}). For the scaling of link density and
-  vulnerability in marine and terrestrial communities, the overall effect of
-  latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.009,
-  $p$=0.038; $\beta_{Latitude:Terrestrial}$=0.012, $p$=0.003 and
-  $\beta_{Latitude:Marine}$=0.009, $p$=0.037;
-  $\beta_{Latitude:Terrestrial}$=0.012, $p$=0.003, respectively) such that
-  there was little overall scaling relationship. In contrast, the scaling
+  ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
+  $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
+  density and vulnerability in marine and terrestrial communities, the overall
+  effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
+  $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
+  $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
+  $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
+  that there was little overall scaling relationship. In contrast, the scaling
   exponent of generality with the proportion of basal resources was positive
   near the equator and negative near the poles in estuarine, lake, and stream
-  communities ($\beta_{Latitude}$=-0.009, $p$=0.002) while the scaling
-  exponents for marine and terrestrial communities were not significantly
-  different from zero ($\beta_{Latitude:Marine}$=0.011, $p$=0.021;
-  $\beta_{Latitude:Terrestrial}$=0.014, $p$=0.002.
+  communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
+  very little change in the scaling exponents for marine and terrestrial
+  communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
+  $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
 
@@
   generally increased with the proportion of intermediate consumers in a web
-  ($\beta_0$=2.10, $p$\textless0.001; $\beta_0$=0.592, $p$=0.006; and
-  $\beta_0$=0.843, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
+  ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
+  $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
   The best-fit models for link density and vulnerability did not include
@@
   for generality increased weakly towards the poles in estuarine, marine, and
-  terrestrial food webs ($\beta_{Latitude}$=0.003, $p$=0.486) but decreased 
-  towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.019, $p$=0.027
-  and $\beta_{Latitude:Stream}$=-0.031, $p$=0.002; Fig~\ref{BIT}).
+  terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
+  towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
+  and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).
 
@@
   density, generality, and vulnerability decreased as the proportion of top
-  predators increased ($\beta_0$=-0.584, $p$\textless0.001; $\beta_0$=-0.418,
-  $p$\textless0.001; and $\beta_0$=-0.585, $p$\textless0.001 respectively;
+  predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
+  $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
   Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
   strength of this scaling did not vary significantly with latitude
-  ($\beta_{Latitude}$=0.001, $p$=0.652 for link density;
-  $\beta_{Latitude}$=0.001, $p$=0.654 for vulnerability) except in stream food
+  ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
+  $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability) except in stream and terrestrial food
   webs, where scaling was more strongly negative in the tropics and near zero
-  near the poles ($\beta_{Latitude:Stream}$=0.010, $p$=0.006 for link density;
-  $\beta_{Latitude:Stream}$=0.010, $p$=0.007 for vulnerability;
+  near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
+  $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and
+  $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
+  for vulnerability;
   Fig~\ref{BIT}). The best-fit model for generality did not include any terms
-  for latitude in any ecosystem type). In stream food webs, scaling was more
-  strongly negative in the tropics and did not differ from zero near the poles
+  for latitude in any ecosystem type.
 

### 2015-06-29 manuscript/supplement.tex
Double-checked description of rejects in supplement, table is ready except for references
Updated supplemental text.

@@
   consumers, and top predators (to obtain  non-zero proportions of each
-  category). Our final sample size was thereby reduced to XXX food webs.
+  category). Our final sample size was thereby reduced to 196 food webs.
 
@@
     Contrary to the expected latitudinal gradient, the best-fit version of
-    equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
-    ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
-    relationship was robust to the removal of three outliers (based on Cook's Distance). 
-    There were also relationships between latitude and link density and between latitude and vulnerability
-    in stream food webs, but these trends were non-signficant after the removal of three outliers.
-    Link density and vulnerability did not vary with latitude in any other ecosystem type.
-    The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
-    latitude in any ecosystem type.
+    equation~(\ref{Latfull}) for species richness did not 
+    include a signficant effect of latitude for any 
+    ecosystem type. Further, there were no relationships
+    between link density, generality, or vulnerability
+    with latitude for any ecosystem type.
 
-    The relationships between latitude and the proportions of species at each trophic level were broadly similar
-    to the relationship between latitude and species richness. 
-    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
+    The relationships between latitude and the proportions of species at each trophic level were more complex. 
+    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.011, $p$\textless0.001) 
     but did not vary with latitude in estuarine, marine, lake, or terrestrial 
-    food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
-    The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
-    The proportion of top predators did not vary with latitude in 
-    estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
-    webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
-    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
-    All of these trends were robust to the removal of outliers.
+    food webs ($\beta_{Latitude}$=0.001, $p$=0.080),
+    while the proportion of intermediate consumers decreased towards the poles in all ecosystem types
+    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
+    $\beta_{Latitude:Lake}$=0.005, $p$=0.016).
+    The proportion of top predators in a food web, 
+    meanwhile, decreased towards the poles in lake and 
+    stream food webs but did not vary in other ecosystem
+    types ($\beta_{Latitude}$=0.002, $p$=0.151; 
+    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001; and
+    $\beta_{Latitude:Stream}$=-0.007, $p$=0.006).
+
+    % Does this need to be taken into account? Do I mention
+    % it later?
+    % All of these trends were robust to the removal of outliers.
+    % Was it? Do I even care?
 

### 2015-06-29 manuscript/coverletter.tex

@@
 
-\usepackage[britdate]{canterbury-letter}
-% \usepackage[britdate,alyssa-signature]{canterbury-letter}
+%\usepackage[britdate]{canterbury-letter}
+\usepackage[britdate,alyssa-signature]{canterbury-letter}
 \usepackage{times}
@@
 species richness and food-web structure. With regard to the former, one
-hypothesized mechanism for greater species richness in the tropics is the
+hypothesised mechanism for greater species richness in the tropics is the
 latitude-niche-breadth hypothesis, which predicts that the greater stability
@@
 narrower niches and therefore more finely partition habitats. If this
-hypothesis holds true, then tropical species should be more specialized---have
+hypothesis holds true, then tropical species should be more specialised---have
 fewer feeding links---than their high-latitude counterparts. However, the
@@
 readers of \myjournal. Our results are potentially applicable to researchers
-exploring community structure and specialization in a variety of different
+exploring community structure and specialisation in a variety of different
 systems and also provide a new community-wide perspective on the validity of
@@
 
-% \closing{Regards,}
+\closing{Regards,}
 

### 2015-06-29 code/byTL_Models.R
lets not worry about marginals for TS versions

@@ -4,8 +4,8 @@ library(nlrwr)
 library(lmerTest)
 library(MuMIn)
 
-infile='../non_TS/summary-properties.tsv'
-# infile='../mod_data/summary-properties.tsv'
+# infile='../non_TS/summary-properties.tsv'
+infile='../mod_data/summary-properties.tsv'
 
 format='proportions'
 # format='numbers' # Don't care about numbers actually
@@ -252,33 +252,38 @@ power_analysis=FALSE
     source('number_marginal_CIs.R')
   }
 
-  LS_marg=S_CIs("LS_min")
-  write.table(LS_marg,file=paste(outdir,'marginals/LS_S_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
-  Gen_marg=S_CIs("Gen_min")
-  write.table(Gen_marg,file=paste(outdir,'marginals/Gen_S_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
-  Vul_marg=S_CIs("Vul_min")
-  write.table(Vul_marg,file=paste(outdir,'marginals/Vul_S_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
+  # Not going to bother working out the marginals for TS models.
 
-  LS_B_marg=B_CIs("LS_B_min")
-  write.table(LS_B_marg,file=paste(outdir,'marginals/LS_B_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
-  Gen_B_marg=B_CIs("Gen_B_min")
-  write.table(Gen_B_marg,file=paste(outdir,'marginals/Gen_B_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
-  Vul_B_marg=B_CIs("Vul_B_min")
-  write.table(Vul_B_marg,file=paste(outdir,'marginals/Vul_B_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
+  if(infile=='../non_TS/summary-properties.tsv'){
 
-  LS_I_marg=I_CIs("LS_I_min")
-  write.table(LS_I_marg,file=paste(outdir,'marginals/LS_I_marginal.tsv',sep=''),sep='\t',col.names=TRUE)
-  Gen_I_marg=I_CIs("Gen_I_min")
[…]

### 2015-06-29 code/byTL_Models.R
nonTS

@@ -4,8 +4,8 @@ library(nlrwr)
 library(lmerTest)
 library(MuMIn)
 
-infile='../non_TS/summary-properties.tsv'
-# infile='../mod_data/summary-properties.tsv'
+# infile='../non_TS/summary-properties.tsv'
+infile='../mod_data/summary-properties.tsv'
 
 format='proportions'
 # format='numbers' # Don't care about numbers actually

### 2015-07-01 manuscript/bigtable.tex
Big big table

% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \caption{Add caption}
    \begin{tabular}{rrrrrrrrr}
    \toprule
    Web ID & Collection & Original Source & Location & Ecosystem & Latitude(degrees) & Used  & Reason for rejection & Notes \\
    \midrule
    Alamitos & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,12,25 N & Yes   &       &  \\
    Alford & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,15,41.59 N & Yes   &       &  \\
    Beaver & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,18,58.13 N & Yes   &       &  \\
    Bere  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Woodward2008} & England & stream & 50,45,7 N & Yes   &       &  \\
    Bridge & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,09,42.66 N & Yes   &       &  \\
    Broad & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.896938 S & Yes   &       &  \\
    Broadstone & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Woodward2005} & stream & stream & 51,01,05 N & Yes   &       &  \\
    Calero & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,11,09 - 20 N & Yes   &       &  \\
    Canton & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) &  \\
    Carpinteria2006 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Lafferty2006} & USA   & estuary & 34.41 - 34.40 N & Yes   &       &  \\
    Chub  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 43,31,39.36 N & Yes   &       &  \\
    Coachella & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Polis1991a} & desert & terrestrial & 33,54 N & Yes   &       &  \\
    Connery & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,18,42.10 N & Yes   &       &  \\
    Corte & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,56,28 - 37,57,39 N & Yes   &       &  \\
    Coyote & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       &  \\
    German & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) &  \\
    GrandeCl & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
    GrandeSc & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
    Guadalupe & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,27,54 - 37,21,17 N & Yes   &       &  \\
    Hainich   & ~\textbackslash{}citet{Riede2011} & Unpublished & Germany & terrestrial &       & No    & Could not locate original source &  \\
    LittleKyeBurn & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) &  \\
    LittleRock & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Martinez1991} & USA   & lake  & 45,44,07.94 N & Yes   &       &  \\
    Mondego & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Patricio2006} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    Montane Forest, Arizona & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) &  \\
    Reef  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Opitz1996} & Caribbean & marine & 18,29 - 17,53 N & Yes   &       &  \\
    Sierra & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Brose2005} & USA   & lake  & 36,50 - 37,02 N & Yes   &       &  \\
    SimberloffE1 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,37.29 N & Yes   &       &  \\
    SimberloffE2 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,33 N & Yes   &       &  \\
    SimberloffE3 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,41,23.82 N & Yes   &       &  \\
    SimberloffE7 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 25,15 N & Yes   &       &  \\
    SimberloffE9 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       &  \\
    SimberloffST2 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,36,16 N & Yes   &       &  \\
    Skipwith & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Warren1989} & England & lake  & 53,40 N & Yes   &       &  \\
    Stink & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 43,37,55.88 N & Yes   &       &  \\
    StMarks & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Christian1999} & USA   & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) &  \\
    Stony  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) &  \\
    TreleaseWoods & ~\textbackslash{}citet{Riede2011} & \multicolumn{1}{l}{~\textbackslash{}citet{Twomey1945}} & USA   & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) &  \\
    Tuesday & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Jonsson2005} & USA   & lake  & 46,13 N & Yes   &       &  \\
    Weddell Sea & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Brose2005} & Antarctica & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) &  \\
    Ythan & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Huxham1996} & UK    & marine &       & No    & Duplicated in Dunne (YthanDunne) &  \\
    BahiaDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & Mexico & estuary & 30.43 - 30.46 N & Yes   &       & Parasites removed \\
    CarpinteriaDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & USA   & estuary & 34.41 - 34.40 N & Yes   &       & Parasites removed \\
    EsteroDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & Mexico & estuary & 31.78 - 31.69 N & Yes   &       & Parasites removed \\
    FjordDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Zander2011} & Germany & estuary & 54.92 - 54.75 N & Yes   &       & Parasites removed \\
    OtagoDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Mouritsen2011} & New Zealand & estuary & 45.78 - 45.88 S & Yes   &       & Parasites removed \\
    SyltDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Thieltges2011} & Denmark & estuary & 54.83 - 55.12 N & Yes   &       & Parasites removed \\
    YthanDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Huxham1996} & Scotland & estuary & 57,18,32 N & Yes   &       & Parasites removed \\
    1     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Qazim1970}} & India & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    2     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Day1967}} & South Africa & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    3     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Woodwell1967}} & USA   & \multicolumn{1}{l}{estuary} & 41,03,11 N & Yes   &       &  \\
    4     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Johnston1956}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Sink web &  \\
    5     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Teal1962}} & USA   & \multicolumn{1}{l}{estuary} & 31,28,38 N & Yes   &       &  \\
    6     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{MacGinitie1935}} & USA   & \multicolumn{1}{l}{estuary} & 36,48,18 N & Yes   &       &  \\
    7     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kremer1978}} & USA   & \multicolumn{1}{l}{marine} & 41,45 - 41,30 N & Yes   &       &  \\
    8     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Nixon1973}} & USA   & \multicolumn{1}{l}{estuary} & 41,33,00 N & Yes   &       &  \\
    9     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1967}} & Ireland & \multicolumn{1}{l}{stream} &       & No    & Could not locate original source &  \\
    10    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
    11    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
    12    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
    13    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
    14    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
    15    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
    16    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Copeland1974}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    17    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hiatt1960}} & Marshall Islands - Pacific Ocean & \multicolumn{1}{l}{marine} & 4,30 - 15 N & No    & Generalized scheme &  \\
    18    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Niering1963a}} & Polynesia & \multicolumn{1}{l}{terrestrial} & 1,01,29 - 1,06,23 N & Yes   &       &  \\
    19    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brooks1963}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    20    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Knox1970}} & Antarctica & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
    21    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Patten1979}} & Antarctica & \multicolumn{1}{l}{marine} & 70-85 S & Yes   &       &  \\
    22    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Summerhayes1923}} & Norway & \multicolumn{1}{l}{terrestrial} & 74,27,54 N & Yes   &       &  \\
    23    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    24    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    25    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    26    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
    27    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Varley1970}} & England & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
    28    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Paviour-Smith1956}} & New Zealand & \multicolumn{1}{l}{estuary} & 45,51,30 S & Yes   &       &  \\
    29    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dunbar1953}} & Arctic seas & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
    30    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mackintosh1964}} & Antarctica & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
    31    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    32    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    33    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
    34    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jones1949}} & UK    & \multicolumn{1}{l}{stream} & 51,41 - 51,55 N & Yes   &       &  \\
    35    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Minshall1967}} & USA   & \multicolumn{1}{l}{stream} & 37,18,26 N & Yes   &       &  \\
    36    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
    37    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Clarke1967}} & USA   & \multicolumn{1}{l}{marine} & 41,02,49 N & Yes   &       &  \\
    38    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
    39    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
    40    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Harrison1962}} & Malaysia & \multicolumn{1}{l}{terrestrial} &       & No    & Generalized scheme &  \\
    41    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parin1970}} & Israel & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    42    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Vinogradov1978}} & Pacific Ocean & \multicolumn{1}{l}{marine} &       & No    & Study site unclear &  \\
    43    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rosenthal1974}} & USA   & \multicolumn{1}{l}{marine} & 32,57 N & Yes   &       &  \\
    44    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Yanez1978}} & Mexico & \multicolumn{1}{l}{marine} & 17,26,21 N & Yes   &       &  \\
    45    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Tilly1968}} & USA   & \multicolumn{1}{l}{stream} & 41,22,55 N & Yes   &       &  \\
    46    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Patten1975}} & USA   & \multicolumn{1}{l}{lake} & 33,54 N & Yes   &       &  \\
    47    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Harris1980}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Study site unclear &  \\
    48    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Simenstad1978}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Extinct species &  \\
    49    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Simenstad1978}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Extinct species &  \\
    50    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Nybakken1982}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
    51    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & USA   & \multicolumn{1}{l}{marine} & 42,38,56 N & Yes   &       &  \\
    52    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Paine1980a}} & USA   & \multicolumn{1}{l}{marine} & 58,27 N & Yes   &       &  \\
    53    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Paine1980a}} & USA   & \multicolumn{1}{l}{marine} & 48,19 - 48,37 N & Yes   &       &  \\
    54    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{Unpublished} & Barbados & \multicolumn{1}{l}{marine} &       & No    & Unpublished &  \\
    55    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Milne1972}} & Scotland & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    56    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Milne1972}} & Scotland & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    57    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Yanez1978}} & Mexico & \multicolumn{1}{l}{marine} & 17,26,21 N & Yes   &       &  \\
    58    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Russia & \multicolumn{1}{l}{lake} & 51,46 N & Yes   &       &  \\
    59    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Twomey1945}} & USA   & \multicolumn{1}{l}{terrestrial} & 40,09,47 N & Yes   &       &  \\
    60    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rasmussen1941}} & USA   & \multicolumn{1}{l}{terrestrial} & 36,5-37 N & Yes   &       &  \\
    61    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Summerhayes1928}} & Norway & \multicolumn{1}{l}{terrestrial} & 77,52,30 N & Yes   &       &  \\
    62    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Summerhayes1928}} & Norway & \multicolumn{1}{l}{terrestrial} & 77,52,30 N & Yes   &       &  \\
    63    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jones1950}} & UK    & \multicolumn{1}{l}{stream} & 52,25,08 N & Yes   &       &  \\
    64    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cummins1966}} & USA   & \multicolumn{1}{l}{stream} & 41,39,33 N & Yes   &       &  \\
    65    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Tsuda1972}} & Japan & \multicolumn{1}{l}{stream} & 34,21,20 - 34,23,21 N & Yes   &       &  \\
    66    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mann1972a}} & England & \multicolumn{1}{l}{stream} & 51,30 N & Yes   &       &  \\
    67    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Carlson1968}} & USA   & \multicolumn{1}{l}{river} & 40,24,16 N & Yes   &       &  \\
    68    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Morgan1972}} & Scotland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    69    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Portugal & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
    70    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kemp1977}} & USA   & \multicolumn{1}{l}{estuary} & 28,54,08 N & Yes   &       &  \\
    71    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Sorokin1972}} & Russia & \multicolumn{1}{l}{lake} & 48,00 N & Yes   &       &  \\
    72    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baril1983}} & Canada & \multicolumn{1}{l}{lake} & 46,02 N & Yes   &       &  \\
    73    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schiemer1979}} & Austria & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    74    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & South Africa & \multicolumn{1}{l}{marine} & 34,15,00 S & Yes   &       &  \\
    75    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Pechlaner1972}} & Austria & \multicolumn{1}{l}{lake} & 47,11 N & Yes   &       &  \\
    76    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schiemer1979}} & Austria & \multicolumn{1}{l}{lake} & 47,42 - 47,54 N & Yes   &       &  \\
    77    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Ethiopia & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    78    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Burgis1972}} & Uganda & \multicolumn{1}{l}{lake} & 0     & Yes   &       &  \\
    79    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Sarvala1974}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    80    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Sarvala1974}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    81    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hatanaka1977}} & Japan & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    82    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & France & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
    83    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    84    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Wilbur1972}} & USA   & \multicolumn{1}{l}{lake} & 42,28,42 N & Yes   &       &  \\
    85    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mizuno1982}} & Malaysia & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
    86    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hogetsu1979}} & Japan & \multicolumn{1}{l}{marine} & 34,36 - 35,38 N & Yes   &       &  \\
    87    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bradstreet1982}} & Canada & \multicolumn{1}{l}{terrestrial} & 72,46,34.95 N & Yes   &       &  \\
    88    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kuusela1980}} & Finland & \multicolumn{1}{l}{stream} &       & No    & Could not locate original source &  \\
    89    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hartley1948}} & England & \multicolumn{1}{l}{stream} & 52,13 N & Yes   &       &  \\
    91    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Japan & terrestrial &       & No    & Could not locate original source &  \\
    92    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Swan1961}} & Tibet & terrestrial &       & No    & Generalized scheme &  \\
    93    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Pattie1966}} & USA   & terrestrial & 45 N  & Yes   &       &  \\
    94    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brown1971}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    95    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brown1975}} & USA   & terrestrial & 70,11,14.18 N & Yes   &       &  \\
    96    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Russia & terrestrial &       & No    & Could not locate original source &  \\
    97    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Russia & terrestrial &       & No    & Could not locate original source &  \\
    98    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Holm1980}} & Namibia & terrestrial &       & No    & Could not locate original source &  \\
    99    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Howes1954}} & USA   & terrestrial & 32,36 N & Yes   &       &  \\
    100   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & India & terrestrial &       & No    & Could not locate original source &  \\
    101   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & \multicolumn{1}{l}{France} & lake  &       & No    & Could not locate original source &  \\
    102   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Shushkina1973}} & \multicolumn{1}{l}{Pacific Ocean} & marine & 10 S - 15 N & Yes   &       &  \\
    103   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Petipa1979}} & \multicolumn{1}{l}{Pacific Ocean} & marine &       & No    & Generalized scheme &  \\
    104   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & \multicolumn{1}{l}{Panama} & marine & 4,48,04 N & Yes   &       &  \\
    105   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Edwards1982}} & \multicolumn{1}{l}{USA} & marine & 42,40 N & Yes   &       &  \\
    106   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Glynn1965}} & \multicolumn{1}{l}{USA} & marine &       & No    & Could not locate original source &  \\
    107   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Peterson1979}} & \multicolumn{1}{l}{USA} & marine & 39,52,02 N & Yes   &       &  \\
    108   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hewatt1937}} & \multicolumn{1}{l}{USA} & marine & 36,37 N & Yes   &       &  \\
    109   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Castilla1981}} & \multicolumn{1}{l}{Chile} & marine &       & No    & Could not locate original source &  \\
    110   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
    111   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
    112   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
    113   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
    114   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Marshall1982}} & \multicolumn{1}{l}{Zimbabwe} & lake  & 17,54,11.90 S & Yes   &       &  \\
    115   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Koepcke1952}} & \multicolumn{1}{l}{Peru} & marine &       & No    & Could not locate original source &  \\
    116   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hurlbert1972}} & \multicolumn{1}{l}{U.S.A.} & lake  & 35,09,19 S & Yes   &       &  \\
    117   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Zaret1973}} & \multicolumn{1}{l}{Panama} & lake  & 9,11,31.50 N & Yes   &       &  \\
    118   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bindloss1972}} & \multicolumn{1}{l}{UK} & lake  & 56,41,18.71 N & Yes   &       &  \\
    119   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mann1972}} & \multicolumn{1}{l}{UK} & stream & 51,27 N & Yes   &       &  \\
    120   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Moriarty1973}} & \multicolumn{1}{l}{Uganda} & lake  & 0,00,58 N & Yes   &       &  \\
    121   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{VanEs1977}} & \multicolumn{1}{l}{Germany} & estuary & 53,20 - 53,15 N & Yes   &       &  \\
    122   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Nixon1973}} & \multicolumn{1}{l}{USA} & estuary & 41,33,04 N & Yes   &       &  \\
    123   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Harris1972}} & \multicolumn{1}{l}{USA} & terrestrial & 40,45,28 N & Yes   &       &  \\
    124   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Collins1976}} & \multicolumn{1}{l}{USA} & stream & 44,34 N & Yes   &       &  \\
    125   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Landry1977}} & \multicolumn{1}{l}{Unspecified} & marine &       & No    & Generalized scheme &  \\
    126   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Larsson1978}} & \multicolumn{1}{l}{Norway} & lake  & 61,26,00 N & Yes   &       &  \\
    127   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1979}} & \multicolumn{1}{l}{Malaysia} & lake  &       & No    & Could not locate original source &  \\
    128   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1979}} & \multicolumn{1}{l}{Malaysia} & lake  &       & No    & Could not locate original source &  \\
    129   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{Unpublished} & \multicolumn{1}{l}{Unspecified} & terrestrial &       & No    & Unpublished &  \\
    130   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Odum1975}} & \multicolumn{1}{l}{USA} & estuary & 27,12 N & Yes   &       &  \\
    131   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & \multicolumn{1}{l}{Malaysia} & lake  & 4,12,37 N & Yes   &       &  \\
    132   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & \multicolumn{1}{l}{Malaysia} & lake  & 4,12,37 N & Yes   &       &  \\
    133   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & \multicolumn{1}{l}{Sri Lanka} & lake  & 7,52,22 N & Yes   &       &  \\
    134   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & \multicolumn{1}{l}{Madagascar} & lake  & 19 S  & Yes   &       &  \\
    135   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & Seychelles & lake  & 4,40,46 S & Yes   &       &  \\
    136   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bradshaw1983}} & USA   & lake  &       & No    & Could not locate original source &  \\
    137   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Corker1984}} & Hong Kong & lake  & 22,14-22,17 N & Yes   &       &  \\
    138   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1983}} & UK    & lake  &       & No    & Could not locate original source &  \\
    139   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1983}} & Australia & lake  &       & No    & Could not locate original source &  \\
    140   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Siefert1979}} & Venezuela & terrestrial & 10,21 N & Yes   &       &  \\
    141   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Seifert1976}} & Costa Rica & terrestrial &       & No    & Competition network &  \\
    142   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Seifert1976}} & Costa Rica & terrestrial &       & No    & Competition network &  \\
    143   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Snow1958}} & USA   & lake  & 34,41,45 N & Yes   &       &  \\
    144   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Snow1958}} & Germany & lake  &       & No    & Could not locate original source &  \\
    145   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
    146   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
    147   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
    148   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
    149   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Force1974}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    150   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hopkins1984}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    151   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Richards1926}} & UK    & terrestrial & 51,20,04 N & Yes   &       &  \\
    152   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Whittaker1984}} & USA   & terrestrial &       & No    & Source web &  \\
    153   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mayse1978}} & USA   & terrestrial & 40,06,38 N & Yes   &       &  \\
    154   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mayse1978}} & USA   & terrestrial & 39,56,41 N & Yes   &       &  \\
    155   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1975}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    156   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    157   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    158   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    159   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    160   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    161   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    162   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    163   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    164   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    165   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    166   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    167   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
    168   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    169   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    170   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    171   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    172   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    173   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    174   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    175   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    176   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    177   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    178   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
    179   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Robinson1953}} & England & terrestrial &       & No    & Source web &  \\
    180   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
    181   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
    182   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
    183   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
    184   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1972}} & UK    & terrestrial &       & No    & Could not locate original source &  \\
    185   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Chapman1955}} & UK    & terrestrial &       & No    & Source web &  \\
    186   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cornaby1974}} & Costa Rica & terrestrial &       & No    & Source web &  \\
    187   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cornaby1974}} & Costa Rica & terrestrial &       & No    & Source web &  \\
    188   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jiron1981}} & Costa Rica & terrestrial &       & No    & Source web &  \\
    189   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    190   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    191   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    192   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    193   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    194   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    195   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schoenly1983a}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    196   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schoenly1983a}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
    197   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mohr1943}} & USA   & terrestrial &       & No    & Source web &  \\
    198   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schoenly1983}} & Mexico & terrestrial &       & No    & Source web &  \\
    199   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Valiela1969}} & USA   & terrestrial &       & No    & Source web &  \\
    200   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Valiela1974}} & USA   & terrestrial &       & No    & Source web &  \\
    201   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Valiela1974}} & USA   & terrestrial &       & No    & Source web &  \\
    202   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Allan1982}} & USA   & stream & 38,50,21 N & Yes   &       &  \\
    203   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Collins1976}} & USA   & stream & 44,24 N & Yes   &       &  \\
    204   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & lake  & 11,36,39 S & Yes   &       & Used whole-lake web only \\
    205   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hildrew1985}} & UK    & stream & 51,01,05 N & Yes   &       &  \\
    206   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jones1949}} & UK    & stream & 51,41 - 51,55 N & Yes   &       &  \\
    207   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Koslucher1973}} & USA   & stream & 41,57 - 42,14 N & Yes   &       &  \\
    208   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Minckley1963}} & USA   & stream & 37,56 N & Yes   &       &  \\
    209   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Minshall1967}} & USA   & stream & 37,18,26 N & Yes   &       &  \\
    210   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Percival1929}} & UK    & stream &       & No    & Generalized scheme &  \\
    211   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ricker1935}} & Canada & stream &       & No    & Could not locate original source &  \\
    212   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ricker1935}} & Canada & stream &       & No    & Could not locate original source &  \\
    213   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Badcock1949}} & UK    & stream & 53 N  & Yes   &       &  \\
    214   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2003}} & USA   & stream & 44,40,44 N & Yes   &       &  \\
    215   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2003}} & USA   & stream & 40,40,52 N & Yes   &       &  \\
    216   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2003}} & USA   & stream & 35,02,50 N & Yes   &       &  \\
    217   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2003}} & USA   & stream & 35,03,50 N & Yes   &       &  \\
    218   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.79 S & Yes   &       &  \\
    219   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 44.64 S & Yes   &       &  \\
    220   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
    221   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
    222   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
    223   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
    224   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
    225   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
    226   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.61 S & Yes   &       &  \\
    227   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 44.97 S & Yes   &       &  \\
    228   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 44.95 S & Yes   &       &  \\
    229   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 44.96 S & Yes   &       &  \\
    230   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45 S  & Yes   &       &  \\
    231   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.58 S & Yes   &       &  \\
    232   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.61 S & Yes   &       &  \\
    233   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.782 S & Yes   &       &  \\
    234   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.803 S & Yes   &       &  \\
    235   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.752 S & Yes   &       &  \\
    236   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
    237   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
    238   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
    239   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
    240   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
    241   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
    242   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
    243   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
    244   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
    245   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
    246   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
    247   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
    248   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004}} & New Zealand & estuary & 45,51,28 S & Yes   &       & Parasites removed \\
    249   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2005}} & Brazil & stream & 24,30 S & Yes   &       &  \\
    250   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2006}} & Brazil & lake  & 22,57,38 S & Yes   &       &  \\
    251   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2006}} & Brazil & lake  & 22,57,38 S & Yes   &       &  \\
    252   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2010}} & Brazil & stream & 18,40 S & Yes   &       &  \\
    253   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2011}} & Angola & marine & 5 - 17,15 S & Yes   &       &  \\
    254   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2013}} & Brazil & stream & 21 S  & Yes   &       &  \\
    255   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2013}} & Brazil & stream & 21 S  & Yes   &       &  \\
    256   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2013}} & Brazil & stream &       & No    & Could not locate original source &  \\
    257   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    258   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    259   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    260   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    261   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    262   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
    263   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schnieder1997}} & USA   & lake  & 45,58,50 N & Yes   &       &  \\
    264   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Stagliano2002}} & USA   & terrestrial & 39,06,27 N & Yes   &       &  \\
    265   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Lin2006}} & Taiwan & marine & 22,27 N & Yes   &       &  \\
    266   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cornejo-Donoso2008}} & Antarctica & marine & 60 - 69 S & Yes   &       &  \\
    267   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Zetina-Rejon2003}} & Mexico & marine & 23.15 - 22.9N & Yes   &       &  \\
    268   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cruz-Escalona2007}} & Mexico & marine & 18,45 - 18,50 N & Yes   &       &  \\
    269   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Liu2007}} & China & lake  & 29,32,35 N & Yes   &       &  \\
    270   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Filguera2011}} & Spain & marine & 42,17,37 - 42,19,29 N & Yes   &       &  \\
    271   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Amundsen2013}} & Norway & lake  & 69,07 N & Yes   &       & Parasites removed \\
    272   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hampton2011}} & USA   & lake  & 48,03,29 N & Yes   &       &  \\
    273   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
    274   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
    275   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
    276   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
    277   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Massana1996}} & Spain & lake  & 42,08,6 - 42,07 N & Yes   &       &  \\
    278   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Stewart2011}} & USA   & lake  & 43.7 N & Yes   &       &  \\
    279   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Stewart2011}} & USA   & lake  & 43.7 N & Yes   &       &  \\
    280   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 43,58 N & Yes   &       &  \\
    281   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 44,58 N & Yes   &       &  \\
    282   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 45,58 N & Yes   &       &  \\
    283   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 46,58 N & Yes   &       &  \\
    284   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 47,58 N & Yes   &       &  \\
    285   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 48,58 N & Yes   &       &  \\
    286   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 49,58 N & Yes   &       &  \\
    287   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 50,58 N & Yes   &       &  \\
    288   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Christian1999}} & USA   & estuary & 30,05,39 N & Yes   &       &  \\
    289   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fetahi2011}} & Ethiopia & lake  & 11,15 N & Yes   &       &  \\
    290   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brodeur1992}} & USA   & marine & 43 - 48 N & Yes   &       &  \\
    291   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brodeur1992}} & USA   & marine & 44 - 48 N & Yes   &       &  \\
    292   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brodeur1992}} & USA   & marine & 45 - 48 N & Yes   &       &  \\
    293   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brodeur1992}} & USA   & marine & 46 - 48 N & Yes   &       &  \\
    294   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Gaedke1994} & Europe & lake  & 47,37,30 N & Yes   &       &  \\
    295   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Preston2012}} & USA   & lake  & 37.66 N & Yes   &       & Parasites removed \\
    296   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ratsirarson1996}} & Madagascar & lake  & 24,55 S & Yes   &       &  \\
    297   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    298   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    299   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    300   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    301   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    302   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    303   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    304   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    305   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    306   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    307   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    308   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
    309   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Gontikaki2011}} & Atlantic Ocean & marine & 61,13,88 N & Yes   &       &  \\
    310   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Khan2009}} & India & lake  & 12,45,25 N & Yes   &       &  \\
    311   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Memmott2000}} & UK    & terrestrial &       & No    & Source web &  \\
    312   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2009}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
    313   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2009}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
    314   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
    315   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
    316   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
    317   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
    318   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
    319   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
    320   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 42 - 49 N & Yes   &       &  \\
    321   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 43 - 49 N & Yes   &       &  \\
    322   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 44 - 49 N & Yes   &       &  \\
    323   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 45 - 49 N & Yes   &       &  \\
    324   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 46 - 49 N & Yes   &       &  \\
    325   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Lewis2002}} & Belize & terrestrial &       & No    & Host-parasitoid web &  \\
    326   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Lewis2002}} & Belize & terrestrial &       & No    & Host-parasitoid web &  \\
    327   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,13 S & Yes   &       &  \\
    328   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,20,0 S & Yes   &       &  \\
    329   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,35 S & Yes   &       &  \\
    330   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,13 S & Yes   &       &  \\
    331   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,20,0 S & Yes   &       &  \\
    332   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Huang2008}} & China & stream & 31.70 N & Yes   &       &  \\
    333   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Link2002}} & USA   & marine & 33,51 - 44,49 N & Yes   &       &  \\
    334   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Alcorlo2001}} & Spain & lake  & 41,26,36 N & Yes   &       &  \\
    335   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Alcorlo2001}} & Spain & lake  & 41,26,05 N & Yes   &       &  \\
    336   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Alcorlo2001}} & Spain & lake  & 41,26,36 N & Yes   &       &  \\
    337   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Alcorlo2001}} & Spain & lake  & 41,26,05 N & Yes   &       &  \\
    338   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Torres2013}} & South Atlantic & marine &       & No    & Could not locate original source &  \\
    339   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bulman2001}} & Australia & marine & 37-39 S & Yes   &       &  \\
    340   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Smith2007}} & Antarctica & marine & 74-78 S & Yes   &       &  \\
    341   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Lancraft1991}} & Antarctica & marine & 58,20.8 - 60,10.4 S & Yes   &       &  \\
    342   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hopkins1993}} & Antarctica & marine & 57,00 - 60,45 S & Yes   &       &  \\
    343   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1987}} & Australia & lake  & 28,12 S & Yes   &       &  \\
    344   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hodkinson2004}} & Norway & terrestrial &       & No    & Host-parasitoid web &  \\
    345   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Boit2012}} & Europe & lake  & 47,38,10 N & Yes   &       &  \\
    346   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rayner2010}} & Australia & stream & 17,7 S & Yes   &       &  \\
    347   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Motta2005}} & Brazil & stream & 23,03 S & Yes   &       &  \\
    348   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
    349   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
    350   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
    351   & ~\textbackslash{}citet{GlobalWeb} & ~\textbackslash{}citet{Warren1989} & UK    & lake  &       & No    & Could not locate original source &  \\
    352   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Poepperl2003}} & Germany & stream & 54,06 N & No    & describes compartments, not species &  \\
    353   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Poepperl2003}} & Germany & stream & 54,06 N & No    & describes compartments, not species &  \\
    354   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Goldwasser1993}} & St. Martin & terrestrial & 18,03 N & Yes   &       &  \\
    355   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen2003}} & USA   & lake  & 46,13 N & Yes   &       &  \\
    356   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen2003}} & USA   & lake  & 46,13 N & Yes   &       &  \\
    357   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Yodzis1998}} & South Africa & marine & 34,21 - 16 S & No    & Study site unclear &  \\
    358   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schroter2003}} & Europe & terrestrial &       & No    & Generalized scheme &  \\
    359   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baiser2012}} & North America & lake  &       & No    & Study site unclear &  \\
    \bottomrule
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%

### 2015-07-01 manuscript/supplement.tex
working on adding in big table

@@
 \newcommand{\expect}[1]{\left\langle #1 \right\rangle}
-\newcommand{\etal}{\textit{et al.\ }}
+\newcommand{\etal}{\textit{et al.\ }
 
@@
         \setcounter{table}{0}
-        \renewcommand{\thetable}{S\arabic{table}}%
+        \renewcommand{\thetable}{S\arabic{table}%
         \setcounter{figure}{0}
-        \renewcommand{\thefigure}{S\arabic{figure}}%
+        \renewcommand{\thefigure}{S\arabic{figure}%
      }
@@
 \begin{quote} \bf}
-{\end{quote}}
+{\end{quote}
 
@@
 
-  We combined published food webs from~\citet{GlobaWeb},~\citet{Riede2011},
+  We combined published food webs from~\citet{GlobalWeb},~\citet{Riede2011},
   and~\citet{Dunne2013}. Of the 358 food webs available
-  from~\citet{Globalweb}, 59 were rejected because their original source was
+  from~\citet{GlobalWeb}, 59 were rejected because their original source was
   unpublished or could not be retrieved. We further eliminated 13 source or
@@
 
- See Table S1 for a list of rejected webs and reasons for their
+ See Table~\ref{S1} for a list of rejected webs and reasons for their
   exclusion.
+
+\newpage
+\begin{landscape}
+
+  \begin{table}[h!]
+  \centering
+  \caption{Sources of food webs considered for use in this study. ``Collection" indicates the direct source of the
+  food web (i.e., where the interaction matrix was obtained) while ``Original source" indicates the original publication
+  of the food web. We also show the ecosystem type, country of origin, and latitude for each food web, as well as whether
+  it was ultimately included in the study.  }
+  \label{S1}
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+    \begin{tabular}{rrrrrrrrr}
+      \hline
+      Web ID & Collection & Original Source & Location & Ecosystem & Latitude(degrees) & Used  & Reason for rejection & Notes \\
+      \hline
+      Alamitos & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,12,25 N & Yes   &       &  \\
+      Alford & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,15,41.59 N & Yes   &       &  \\
+      Beaver & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,18,58.13 N & Yes   &       &  \\
+      Bere  & ~\citet{Riede2011} & ~\citet{Woodward2008} & England & stream & 50,45,7 N & Yes   &       &  \\
+      Bridge & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,09,42.66 N & Yes   &       &  \\
+      Broad & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.896938 S & Yes   &       &  \\
+      Broadstone & ~\citet{Riede2011} & ~\citet{Woodward2005} & stream & stream & 51,01,05 N & Yes   &       &  \\
+      Calero & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,11,09 - 20 N & Yes   &       &  \\
+      Canton & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) &  \\
+      Carpinteria2006 & ~\citet{Riede2011} & ~\citet{Lafferty2006} & USA   & estuary & 34.41 - 34.40 N & Yes   &       &  \\
+      Chub  & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 43,31,39.36 N & Yes   &       &  \\
+      Coachella & ~\citet{Riede2011} & ~\citet{Polis1991a} & desert & terrestrial & 33,54 N & Yes   &       &  \\
+      Connery & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,18,42.10 N & Yes   &       &  \\
+      Corte & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,56,28 - 37,57,39 N & Yes   &       &  \\
+      Coyote & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       &  \\
+      German & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) &  \\
+      GrandeCl & ~\citet{Riede2011} & ~\citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
+      GrandeSc & ~\citet{Riede2011} & ~\citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
+      Guadalupe & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,27,54 - 37,21,17 N & Yes   &       &  \\
+      Hainich   & ~\citet{Riede2011} & Unpublished & Germany & terrestrial &       & No    & Could not locate original source &  \\
+      LittleKyeBurn & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) &  \\
+      LittleRock & ~\citet{Riede2011} & ~\citet{Martinez1991} & USA   & lake  & 45,44,07.94 N & Yes   &       &  \\
+      Mondego & ~\citet{Riede2011} & ~\citet{Patricio2006} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+      Montane Forest, Arizona & ~\citet{Riede2011} & ~\citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) &  \\
+      Reef  & ~\citet{Riede2011} & ~\citet{Opitz1996} & Caribbean & marine & 18,29 - 17,53 N & Yes   &       &  \\
+      Sierra & ~\citet{Riede2011} & ~\citet{Brose2005} & USA   & lake  & 36,50 - 37,02 N & Yes   &       &  \\
+      SimberloffE1 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,37.29 N & Yes   &       &  \\
+      SimberloffE2 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,33 N & Yes   &       &  \\
+      SimberloffE3 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,41,23.82 N & Yes   &       &  \\
+      SimberloffE7 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 25,15 N & Yes   &       &  \\
+      SimberloffE9 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       &  \\
+      SimberloffST2 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,36,16 N & Yes   &       &  \\
+      Skipwith & ~\citet{Riede2011} & ~\citet{Warren1989} & England & lake  & 53,40 N & Yes   &       &  \\
+      Stink & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 43,37,55.88 N & Yes   &       &  \\
+      StMarks & ~\citet{Riede2011} & ~\citet{Christian1999} & USA   & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) &  \\
+      Stony  & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) &  \\
+      TreleaseWoods & ~\citet{Riede2011} & \multicolumn{1}{l}{~\citet{Twomey1945} & USA   & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) &  \\
+      Tuesday & ~\citet{Riede2011} & ~\citet{Jonsson2005} & USA   & lake  & 46,13 N & Yes   &       &  \\
+      Weddell Sea & ~\citet{Riede2011} & ~\citet{Brose2005} & Antarctica & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) &  \\
+      Ythan & ~\citet{Riede2011} & ~\citet{Huxham1996} & UK    & marine &       & No    & Duplicated in Dunne (YthanDunne) &  \\
+      BahiaDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & Mexico & estuary & 30.43 - 30.46 N & Yes   &       & Parasites removed \\
+      CarpinteriaDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & USA   & estuary & 34.41 - 34.40 N & Yes   &       & Parasites removed \\
+      EsteroDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & Mexico & estuary & 31.78 - 31.69 N & Yes   &       & Parasites removed \\
+      FjordDunne & ~\citet{Dunne2013} & ~\citet{Zander2011} & Germany & estuary & 54.92 - 54.75 N & Yes   &       & Parasites removed \\
+      OtagoDunne & ~\citet{Dunne2013} & ~\citet{Mouritsen2011} & New Zealand & estuary & 45.78 - 45.88 S & Yes   &       & Parasites removed \\
+      SyltDunne & ~\citet{Dunne2013} & ~\citet{Thieltges2011} & Denmark & estuary & 54.83 - 55.12 N & Yes   &       & Parasites removed \\
+      YthanDunne & ~\citet{Dunne2013} & ~\citet{Huxham1996} & Scotland & estuary & 57,18,32 N & Yes   &       & Parasites removed \\
+      1     & ~\citet{GlobalWeb} & ~\citet{Qazim1970} & India & estuary &       & No    & Could not locate original source &  \\
+      2     & ~\citet{GlobalWeb} & ~\citet{Day1967} & South Africa & estuary &       & No    & Could not locate original source &  \\
+      3     & ~\citet{GlobalWeb} & ~\citet{Woodwell1967} & USA   & estuary & 41,03,11 N & Yes   &       &  \\
+      4     & ~\citet{GlobalWeb} & ~\citet{Johnston1956} & USA   & estuary &       & No    & Sink web &  \\
+      5     & ~\citet{GlobalWeb} & ~\citet{Teal1962} & USA   & estuary & 31,28,38 N & Yes   &       &  \\
+      6     & ~\citet{GlobalWeb} & ~\citet{MacGinitie1935} & USA   & estuary & 36,48,18 N & Yes   &       &  \\
+      7     & ~\citet{GlobalWeb} & ~\citet{Kremer1978} & USA   & marine & 41,45 - 41,30 N & Yes   &       &  \\
+      8     & ~\citet{GlobalWeb} & ~\citet{Nixon1973} & USA   & estuary & 41,33,00 N & Yes   &       &  \\
+      9     & ~\citet{GlobalWeb} & ~\citet{Kitching1967} & Ireland & stream &       & No    & Could not locate original source &  \\
+      10    & ~\citet{GlobalWeb} & ~\citet{Menge1976} & USA   & marine & 41 - 47 N & Yes   &       &  \\
+      11    & ~\citet{GlobalWeb} & ~\citet{Menge1976} & USA   & marine & 41 - 47 N & Yes   &       &  \\
+      12    & ~\citet{GlobalWeb} & ~\citet{Menge1976} & USA   & marine & 45,45 - 49 N & Yes   &       &  \\
+      13    & ~\citet{GlobalWeb} & ~\citet{Menge1976} & USA   & marine & 45,45 - 49 N & Yes   &       &  \\
+      14    & ~\citet{GlobalWeb} & ~\citet{Walsh1967} & Hawaii & estuary & 21,26,09 N & No    & Could not locate original source &  \\
+      15    & ~\citet{GlobalWeb} & ~\citet{Walsh1967} & Hawaii & estuary & 21,26,09 N & No    & Could not locate original source &  \\
+      16    & ~\citet{GlobalWeb} & ~\citet{Copeland1974} & USA   & estuary &       & No    & Could not locate original source &  \\
+      17    & ~\citet{GlobalWeb} & ~\citet{Hiatt1960} & Marshall Islands - Pacific Ocean & marine & 4,30 - 15 N & No    & Generalized scheme &  \\
+      18    & ~\citet{GlobalWeb} & ~\citet{Niering1963a} & Polynesia & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       &  \\
+      19    & ~\citet{GlobalWeb} & ~\citet{Brooks1963} & USA   & lake &       & No    & Could not locate original source &  \\
+      20    & ~\citet{GlobalWeb} & ~\citet{Knox1970} & Antarctica & terrestrial &       & No    & Could not locate original source &  \\
+      21    & ~\citet{GlobalWeb} & ~\citet{Patten1979} & Antarctica & marine & 70-85 S & Yes   &       &  \\
+      22    & ~\citet{GlobalWeb} & ~\citet{Summerhayes1923} & Norway & terrestrial & 74,27,54 N & Yes   &       &  \\
+      23    & ~\citet{GlobalWeb} & ~\citet{Bird1930} & Canada & terrestrial & 50,25,17 N & Yes   &       &  \\
+      24    & ~\citet{GlobalWeb} & ~\citet{Bird1930} & Canada & terrestrial & 50,25,17 N & Yes   &       &  \\
+      25    & ~\citet{GlobalWeb} & ~\citet{Bird1930} & Canada & terrestrial & 50,25,17 N & Yes   &       &  \\
+      26    & ~\citet{GlobalWeb} & ~\citet{Bird1930} & Canada & terrestrial & 50,25,17 N & Yes   &       &  \\
+      27    & ~\citet{GlobalWeb} & ~\citet{Varley1970} & England & terrestrial &       & No    & Could not locate original source &  \\
+      28    & ~\citet{GlobalWeb} & ~\citet{Paviour-Smith1956} & New Zealand & estuary & 45,51,30 S & Yes   &       &  \\
+      29    & ~\citet{GlobalWeb} & ~\citet{Dunbar1953} & Arctic seas & marine &       & No    & Generalized scheme &  \\
+      30    & ~\citet{GlobalWeb} & ~\citet{Mackintosh1964} & Antarctica & marine &       & No    & Generalized scheme &  \\
+      31    & ~\citet{GlobalWeb} & ~\citet{Petipa1970} & Black Sea & marine &       & No    & Could not locate original source &  \\
+      32    & ~\citet{GlobalWeb} & ~\citet{Petipa1970} & Black Sea & marine &       & No    & Could not locate original source &  \\
+      33    & ~\citet{GlobalWeb} & ~\citet{Fryer1959} & Malawi & lake & 11,36,39 S & Yes   &       &  \\
+      34    & ~\citet{GlobalWeb} & ~\citet{Jones1949} & UK    & stream & 51,41 - 51,55 N & Yes   &       &  \\
+      35    & ~\citet{GlobalWeb} & ~\citet{Minshall1967} & USA   & stream & 37,18,26 N & Yes   &       &  \\
+      36    & ~\citet{GlobalWeb} & ~\citet{Walsh1967} & Hawaii & estuary & 21,26,09 N & No    & Could not locate original source &  \\
+      37    & ~\citet{GlobalWeb} & ~\citet{Clarke1967} & USA   & marine & 41,02,49 N & Yes   &       &  \\
+      38    & ~\citet{GlobalWeb} & ~\citet{Fryer1959} & Malawi & lake & 11,36,39 S & Yes   &       &  \\
+      39    & ~\citet{GlobalWeb} & ~\citet{Fryer1959} & Malawi & lake & 11,36,39 S & Yes   &       &  \\
+      40    & ~\citet{GlobalWeb} & ~\citet{Harrison1962} & Malaysia & terrestrial &       & No    & Generalized scheme &  \\
+      41    & ~\citet{GlobalWeb} & ~\citet{Parin1970} & Israel & marine &       & No    & Could not locate original source &  \\
+      42    & ~\citet{GlobalWeb} & ~\citet{Vinogradov1978} & Pacific Ocean & marine &       & No    & Study site unclear &  \\
+      43    & ~\citet{GlobalWeb} & ~\citet{Rosenthal1974} & USA   & marine & 32,57 N & Yes   &       &  \\
+      44    & ~\citet{GlobalWeb} & ~\citet{Yanez1978} & Mexico & marine & 17,26,21 N & Yes   &       &  \\
+      45    & ~\citet{GlobalWeb} & ~\citet{Tilly1968} & USA   & stream & 41,22,55 N & Yes   &       &  \\
+      46    & ~\citet{GlobalWeb} & ~\citet{Patten1975} & USA   & lake & 33,54 N & Yes   &       &  \\
+      47    & ~\citet{GlobalWeb} & ~\citet{Harris1980} & USA   & lake &       & No    & Study site unclear &  \\
+      48    & ~\citet{GlobalWeb} & ~\citet{Simenstad1978} & USA   & marine &       & No    & Extinct species &  \\
+      49    & ~\citet{GlobalWeb} & ~\citet{Simenstad1978} & USA   & marine &       & No    & Extinct species &  \\
+      50    & ~\citet{GlobalWeb} & ~\citet{Nybakken1982} & USA   & marine &       & No    & Generalized scheme &  \\
+      51    & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA   & marine & 42,38,56 N & Yes   &       &  \\
+      52    & ~\citet{GlobalWeb} & ~\citet{Paine1980a} & USA   & marine & 58,27 N & Yes   &       &  \\
+      53    & ~\citet{GlobalWeb} & ~\citet{Paine1980a} & USA   & marine & 48,19 - 48,37 N & Yes   &       &  \\
+      54    & ~\citet{GlobalWeb} & Unpublished & Barbados & marine &       & No    & Unpublished &  \\
+      55    & ~\citet{GlobalWeb} & ~\citet{Milne1972} & Scotland & estuary &       & No    & Could not locate original source &  \\
+      56    & ~\citet{GlobalWeb} & ~\citet{Milne1972} & Scotland & estuary &       & No    & Could not locate original source &  \\
+      57    & ~\citet{GlobalWeb} & ~\citet{Yanez1978} & Mexico & marine & 17,26,21 N & Yes   &       &  \\
+      58    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Russia & lake & 51,46 N & Yes   &       &  \\
+      59    & ~\citet{GlobalWeb} & ~\citet{Twomey1945} & USA   & terrestrial & 40,09,47 N & Yes   &       &  \\
+      60    & ~\citet{GlobalWeb} & ~\citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & Yes   &       &  \\
+      61    & ~\citet{GlobalWeb} & ~\citet{Summerhayes1928} & Norway & terrestrial & 77,52,30 N & Yes   &       &  \\
+      62    & ~\citet{GlobalWeb} & ~\citet{Summerhayes1928} & Norway & terrestrial & 77,52,30 N & Yes   &       &  \\
+      63    & ~\citet{GlobalWeb} & ~\citet{Jones1950} & UK    & stream & 52,25,08 N & Yes   &       &  \\
+      64    & ~\citet{GlobalWeb} & ~\citet{Cummins1966} & USA   & stream & 41,39,33 N & Yes   &       &  \\
+      65    & ~\citet{GlobalWeb} & ~\citet{Tsuda1972} & Japan & stream & 34,21,20 - 34,23,21 N & Yes   &       &  \\
+      66    & ~\citet{GlobalWeb} & ~\citet{Mann1972a} & England & stream & 51,30 N & Yes   &       &  \\
+      67    & ~\citet{GlobalWeb} & ~\citet{Carlson1968} & USA   & river} & 40,24,16 N & Yes   &       &  \\
+      68    & ~\citet{GlobalWeb} & ~\citet{Morgan1972} & Scotland & lake &       & No    & Could not locate original source &  \\
+      69    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Portugal & estuary &       & No    & Could not locate original source &  \\
+      70    & ~\citet{GlobalWeb} & ~\citet{Kemp1977} & USA   & estuary & 28,54,08 N & Yes   &       &  \\
+      71    & ~\citet{GlobalWeb} & ~\citet{Sorokin1972} & Russia & lake & 48,00 N & Yes   &       &  \\
+      72    & ~\citet{GlobalWeb} & ~\citet{Baril1983} & Canada & lake & 46,02 N & Yes   &       &  \\
+      73    & ~\citet{GlobalWeb} & ~\citet{Schiemer1979} & Austria & lake &       & No    & Could not locate original source &  \\
+      74    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & South Africa & marine & 34,15,00 S & Yes   &       &  \\
+      75    & ~\citet{GlobalWeb} & ~\citet{Pechlaner1972} & Austria & lake & 47,11 N & Yes   &       &  \\
+      76    & ~\citet{GlobalWeb} & ~\citet{Schiemer1979} & Austria & lake & 47,42 - 47,54 N & Yes   &       &  \\
+      77    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Ethiopia & lake &       & No    & Could not locate original source &  \\
+      78    & ~\citet{GlobalWeb} & ~\citet{Burgis1972} & Uganda & lake & 0     & Yes   &       &  \\
+      79    & ~\citet{GlobalWeb} & ~\citet{Sarvala1974} & Finland & lake &       & No    & Could not locate original source &  \\
+      80    & ~\citet{GlobalWeb} & ~\citet{Sarvala1974} & Finland & lake &       & No    & Could not locate original source &  \\
+      81    & ~\citet{GlobalWeb} & ~\citet{Hatanaka1977} & Japan & marine &       & No    & Could not locate original source &  \\
+      82    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & France & marine &       & No    & Could not locate original source &  \\
+      83    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Finland & lake &       & No    & Could not locate original source &  \\
+      84    & ~\citet{GlobalWeb} & ~\citet{Wilbur1972} & USA   & lake & 42,28,42 N & Yes   &       &  \\
+      85    & ~\citet{GlobalWeb} & ~\citet{Mizuno1982} & Malaysia & lake &       & No    & Could not locate original source &  \\
+      86    & ~\citet{GlobalWeb} & ~\citet{Hogetsu1979} & Japan & marine & 34,36 - 35,38 N & Yes   &       &  \\
+      87    & ~\citet{GlobalWeb} & ~\citet{Bradstreet1982} & Canada & terrestrial & 72,46,34.95 N & Yes   &       &  \\
+      88    & ~\citet{GlobalWeb} & ~\citet{Kuusela1980} & Finland & stream &       & No    & Could not locate original source &  \\
+      89    & ~\citet{GlobalWeb} & ~\citet{Hartley1948} & England & stream & 52,13 N & Yes   &       &  \\
+      91    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Japan & terrestrial &       & No    & Could not locate original source &  \\
+      92    & ~\citet{GlobalWeb} & ~\citet{Swan1961} & Tibet & terrestrial &       & No    & Generalized scheme &  \\
+      93    & ~\citet{GlobalWeb} & ~\citet{Pattie1966} & USA   & terrestrial & 45 N  & Yes   &       &  \\
+      94    & ~\citet{GlobalWeb} & ~\citet{Brown1971} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      95    & ~\citet{GlobalWeb} & ~\citet{Brown1975} & USA   & terrestrial & 70,11,14.18 N & Yes   &       &  \\
+      96    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Russia & terrestrial &       & No    & Could not locate original source &  \\
+      97    & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & Russia & terrestrial &       & No    & Could not locate original source &  \\
+      98    & ~\citet{GlobalWeb} & ~\citet{Holm1980} & Namibia & terrestrial &       & No    & Could not locate original source &  \\
+      99    & ~\citet{GlobalWeb} & ~\citet{Howes1954} & USA   & terrestrial & 32,36 N & Yes   &       &  \\
+      100   & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & India & terrestrial &       & No    & Could not locate original source &  \\
+      101   & ~\citet{GlobalWeb} & ~\citet{Cohen1990} & France & lake  &       & No    & Could not locate original source &  \\
+      102   & ~\citet{GlobalWeb} & ~\citet{Shushkina1973} & Pacific Ocean & marine & 10 S - 15 N & Yes   &       &  \\
+      103   & ~\citet{GlobalWeb} & ~\citet{Petipa1979} & Pacific Ocean & marine &       & No    & Generalized scheme &  \\
+      104   & ~\citet{GlobalWeb} & ~\citet{Menge1976} & Panama & marine & 4,48,04 N & Yes   &       &  \\
+      105   & ~\citet{GlobalWeb} & ~\citet{Edwards1982} & USA & marine & 42,40 N & Yes   &       &  \\
+      106   & ~\citet{GlobalWeb} & ~\citet{Glynn1965} & USA & marine &       & No    & Could not locate original source &  \\
+      107   & ~\citet{GlobalWeb} & ~\citet{Peterson1979} & USA & marine & 39,52,02 N & Yes   &       &  \\
+      108   & ~\citet{GlobalWeb} & ~\citet{Hewatt1937} & USA & marine & 36,37 N & Yes   &       &  \\
+      109   & ~\citet{GlobalWeb} & ~\citet{Castilla1981} & Chile} & marine &       & No    & Could not locate original source &  \\
+      110   & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA & marine & 42,38,56 N & Yes   &       &  \\
+      111   & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA & marine & 42,38,56 N & Yes   &       &  \\
+      112   & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA & marine & 42,38,56 N & Yes   &       &  \\
+      113   & ~\citet{GlobalWeb} & ~\citet{Dexter1947} & USA & marine & 42,38,56 N & Yes   &       &  \\
+      114   & ~\citet{GlobalWeb} & ~\citet{Marshall1982} & Zimbabwe & lake  & 17,54,11.90 S & Yes   &       &  \\
+      115   & ~\citet{GlobalWeb} & ~\citet{Koepcke1952} & Peru} & marine &       & No    & Could not locate original source &  \\
+      116   & ~\citet{GlobalWeb} & ~\citet{Hurlbert1972} & USA & lake  & 35,09,19 S & Yes   &       &  \\
+      117   & ~\citet{GlobalWeb} & ~\citet{Zaret1973} & Panama & lake  & 9,11,31.50 N & Yes   &       &  \\
+      118   & ~\citet{GlobalWeb} & ~\citet{Bindloss1972} & UK & lake  & 56,41,18.71 N & Yes   &       &  \\
+      119   & ~\citet{GlobalWeb} & ~\citet{Mann1972} & UK & stream & 51,27 N & Yes   &       &  \\
+      120   & ~\citet{GlobalWeb} & ~\citet{Moriarty1973} & Uganda & lake  & 0,00,58 N & Yes   &       &  \\
+      121   & ~\citet{GlobalWeb} & ~\citet{VanEs1977} & Germany & estuary & 53,20 - 53,15 N & Yes   &       &  \\
+      122   & ~\citet{GlobalWeb} & ~\citet{Nixon1973} & USA & estuary & 41,33,04 N & Yes   &       &  \\
+      123   & ~\citet{GlobalWeb} & ~\citet{Harris1972} & USA & terrestrial & 40,45,28 N & Yes   &       &  \\
+      124   & ~\citet{GlobalWeb} & ~\citet{Collins1976} & USA & stream & 44,34 N & Yes   &       &  \\
+      125   & ~\citet{GlobalWeb} & ~\citet{Landry1977} & Unspecified & marine &       & No    & Generalized scheme &  \\
+      126   & ~\citet{GlobalWeb} & ~\citet{Larsson1978} & Norway & lake  & 61,26,00 N & Yes   &       &  \\
+      127   & ~\citet{GlobalWeb} & ~\citet{Beaver1979} & Malaysia & lake  &       & No    & Could not locate original source &  \\
+      128   & ~\citet{GlobalWeb} & ~\citet{Beaver1979} & Malaysia & lake  &       & No    & Could not locate original source &  \\
+      129   & ~\citet{GlobalWeb} & Unpublished & Unspecified & terrestrial &       & No    & Unpublished &  \\
+      130   & ~\citet{GlobalWeb} & ~\citet{Odum1975} & USA & estuary & 27,12 N & Yes   &       &  \\
+      131   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Malaysia & lake  & 4,12,37 N & Yes   &       &  \\
+      132   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Malaysia & lake  & 4,12,37 N & Yes   &       &  \\
+      133   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Sri Lanka & lake  & 7,52,22 N & Yes   &       &  \\
+      134   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Madagascar & lake  & 19 S  & Yes   &       &  \\
+      135   & ~\citet{GlobalWeb} & ~\citet{Beaver1985} & Seychelles & lake  & 4,40,46 S & Yes   &       &  \\
+      136   & ~\citet{GlobalWeb} & ~\citet{Bradshaw1983} & USA   & lake  &       & No    & Could not locate original source &  \\
+      137   & ~\citet{GlobalWeb} & ~\citet{Corker1984} & Hong Kong & lake  & 22,14-22,17 N & Yes   &       &  \\
+      138   & ~\citet{GlobalWeb} & ~\citet{Kitching1983} & UK    & lake  &       & No    & Could not locate original source &  \\
+      139   & ~\citet{GlobalWeb} & ~\citet{Kitching1983} & Australia & lake  &       & No    & Could not locate original source &  \\
+      140   & ~\citet{GlobalWeb} & ~\citet{Siefert1979} & Venezuela & terrestrial & 10,21 N & Yes   &       &  \\
+      141   & ~\citet{GlobalWeb} & ~\citet{Seifert1976} & Costa Rica & terrestrial &       & No    & Competition network &  \\
+      142   & ~\citet{GlobalWeb} & ~\citet{Seifert1976} & Costa Rica & terrestrial &       & No    & Competition network &  \\
+      143   & ~\citet{GlobalWeb} & ~\citet{Snow1958} & USA   & lake  & 34,41,45 N & Yes   &       &  \\
+      144   & ~\citet{GlobalWeb} & ~\citet{Snow1958} & Germany & lake  &       & No    & Could not locate original source &  \\
+      145   & ~\citet{GlobalWeb} & ~\citet{Rejmanek1979} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
+      146   & ~\citet{GlobalWeb} & ~\citet{Rejmanek1979} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
+      147   & ~\citet{GlobalWeb} & ~\citet{Rejmanek1979} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
+      148   & ~\citet{GlobalWeb} & ~\citet{Rejmanek1979} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
+      149   & ~\citet{GlobalWeb} & ~\citet{Force1974} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      150   & ~\citet{GlobalWeb} & ~\citet{Hopkins1984} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      151   & ~\citet{GlobalWeb} & ~\citet{Richards1926} & UK    & terrestrial & 51,20,04 N & Yes   &       &  \\
+      152   & ~\citet{GlobalWeb} & ~\citet{Whittaker1984} & USA   & terrestrial &       & No    & Source web &  \\
+      153   & ~\citet{GlobalWeb} & ~\citet{Mayse1978} & USA   & terrestrial & 40,06,38 N & Yes   &       &  \\
+      154   & ~\citet{GlobalWeb} & ~\citet{Mayse1978} & USA   & terrestrial & 39,56,41 N & Yes   &       &  \\
+      155   & ~\citet{GlobalWeb} & ~\citet{Askew1975} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      156   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      157   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      158   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      159   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      160   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      161   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      162   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      163   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      164   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      165   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      166   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      167   & ~\citet{GlobalWeb} & ~\citet{Askew1961} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+      168   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      169   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      170   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      171   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      172   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      173   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      174   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      175   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      176   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      177   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      178   & ~\citet{GlobalWeb} & ~\citet{Hawkins1984} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+      179   & ~\citet{GlobalWeb} & ~\citet{Robinson1953} & England & terrestrial &       & No    & Source web &  \\
+      180   & ~\citet{GlobalWeb} & ~\citet{Savely1939} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
+      181   & ~\citet{GlobalWeb} & ~\citet{Savely1939} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
+      182   & ~\citet{GlobalWeb} & ~\citet{Savely1939} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
+      183   & ~\citet{GlobalWeb} & ~\citet{Savely1939} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
+      184   & ~\citet{GlobalWeb} & ~\citet{Beaver1972} & UK    & terrestrial &       & No    & Could not locate original source &  \\
+      185   & ~\citet{GlobalWeb} & ~\citet{Chapman1955} & UK    & terrestrial &       & No    & Source web &  \\
+      186   & ~\citet{GlobalWeb} & ~\citet{Cornaby1974} & Costa Rica & terrestrial &       & No    & Source web &  \\
+      187   & ~\citet{GlobalWeb} & ~\citet{Cornaby1974} & Costa Rica & terrestrial &       & No    & Source web &  \\
+      188   & ~\citet{GlobalWeb} & ~\citet{Jiron1981} & Costa Rica & terrestrial &       & No    & Source web &  \\
+      189   & ~\citet{GlobalWeb} & ~\citet{McKinnerney1978} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      190   & ~\citet{GlobalWeb} & ~\citet{McKinnerney1978} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      191   & ~\citet{GlobalWeb} & ~\citet{McKinnerney1978} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      192   & ~\citet{GlobalWeb} & ~\citet{McKinnerney1978} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      193   & ~\citet{GlobalWeb} & ~\citet{McKinnerney1978} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      194   & ~\citet{GlobalWeb} & ~\citet{McKinnerney1978} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      195   & ~\citet{GlobalWeb} & ~\citet{Schoenly1983a} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      196   & ~\citet{GlobalWeb} & ~\citet{Schoenly1983a} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+      197   & ~\citet{GlobalWeb} & ~\citet{Mohr1943} & USA   & terrestrial &       & No    & Source web &  \\
+      198   & ~\citet{GlobalWeb} & ~\citet{Schoenly1983} & Mexico & terrestrial &       & No    & Source web &  \\
+      199   & ~\citet{GlobalWeb} & ~\citet{Valiela1969} & USA   & terrestrial &       & No    & Source web &  \\
+      200   & ~\citet{GlobalWeb} & ~\citet{Valiela1974} & USA   & terrestrial &       & No    & Source web &  \\
+      201   & ~\citet{GlobalWeb} & ~\citet{Valiela1974} & USA   & terrestrial &       & No    & Source web &  \\
+      202   & ~\citet{GlobalWeb} & ~\citet{Allan1982} & USA   & stream & 38,50,21 N & Yes   &       &  \\
+      203   & ~\citet{GlobalWeb} & ~\citet{Collins1976} & USA   & stream & 44,24 N & Yes   &       &  \\
+      204   & ~\citet{GlobalWeb} & ~\citet{Fryer1959} & Malawi & lake  & 11,36,39 S & Yes   &       & Used whole-lake web only \\
+      205   & ~\citet{GlobalWeb} & ~\citet{Hildrew1985} & UK    & stream & 51,01,05 N & Yes   &       &  \\
+      206   & ~\citet{GlobalWeb} & ~\citet{Jones1949} & UK    & stream & 51,41 - 51,55 N & Yes   &       &  \\
+      207   & ~\citet{GlobalWeb} & ~\citet{Koslucher1973} & USA   & stream & 41,57 - 42,14 N & Yes   &       &  \\
+      208   & ~\citet{GlobalWeb} & ~\citet{Minckley1963} & USA   & stream & 37,56 N & Yes   &       &  \\
+      209   & ~\citet{GlobalWeb} & ~\citet{Minshall1967} & USA   & stream & 37,18,26 N & Yes   &       &  \\
+      210   & ~\citet{GlobalWeb} & ~\citet{Percival1929} & UK    & stream &       & No    & Generalized scheme &  \\
+      211   & ~\citet{GlobalWeb} & ~\citet{Ricker1935} & Canada & stream &       & No    & Could not locate original source &  \\
+      212   & ~\citet{GlobalWeb} & ~\citet{Ricker1935} & Canada & stream &       & No    & Could not locate original source &  \\
+      213   & ~\citet{GlobalWeb} & ~\citet{Badcock1949} & UK    & stream & 53 N  & Yes   &       &  \\
+      214   & ~\citet{GlobalWeb} & ~\citet{Thompson2003} & USA   & stream & 44,40,44 N & Yes   &       &  \\
+      215   & ~\citet{GlobalWeb} & ~\citet{Thompson2003} & USA   & stream & 40,40,52 N & Yes   &       &  \\
+      216   & ~\citet{GlobalWeb} & ~\citet{Thompson2003} & USA   & stream & 35,02,50 N & Yes   &       &  \\
+      217   & ~\citet{GlobalWeb} & ~\citet{Thompson2003} & USA   & stream & 35,03,50 N & Yes   &       &  \\
+      218   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45.79 S & Yes   &       &  \\
+      219   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 44.64 S & Yes   &       &  \\
+      220   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.29 S & Yes   &       &  \\
+      221   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.41 S & Yes   &       &  \\
+      222   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
+      223   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+      224   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+      225   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.115 S & Yes   &       &  \\
+      226   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45.61 S & Yes   &       &  \\
+      227   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 44.97 S & Yes   &       &  \\
+      228   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 44.95 S & Yes   &       &  \\
+      229   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 44.96 S & Yes   &       &  \\
+      230   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45 S  & Yes   &       &  \\
+      231   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45.58 S & Yes   &       &  \\
+      232   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45.61 S & Yes   &       &  \\
+      233   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45.782 S & Yes   &       &  \\
+      234   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45.803 S & Yes   &       &  \\
+      235   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45.752 S & Yes   &       &  \\
+      236   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.29 S & Yes   &       &  \\
+      237   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.41 S & Yes   &       &  \\
+      238   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
+      239   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+      240   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+      241   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.115 S & Yes   &       &  \\
+      242   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.29 S & Yes   &       &  \\
+      243   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.41 S & Yes   &       &  \\
+      244   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
+      245   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+      246   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+      247   & ~\citet{GlobalWeb} & ~\citet{Thompson2004c} & New Zealand & stream & 46.115 S & Yes   &       &  \\
+      248   & ~\citet{GlobalWeb} & ~\citet{Thompson2004} & New Zealand & estuary & 45,51,28 S & Yes   &       & Parasites removed \\
+      249   & ~\citet{GlobalWeb} & ~\citet{Angelini2005} & Brazil & stream & 24,30 S & Yes   &       &  \\
+      250   & ~\citet{GlobalWeb} & ~\citet{Angelini2006} & Brazil & lake  & 22,57,38 S & Yes   &       &  \\
+      251   & ~\citet{GlobalWeb} & ~\citet{Angelini2006} & Brazil & lake  & 22,57,38 S & Yes   &       &  \\
+      252   & ~\citet{GlobalWeb} & ~\citet{Angelini2010} & Brazil & stream & 18,40 S & Yes   &       &  \\
+      253   & ~\citet{GlobalWeb} & ~\citet{Angelini2011} & Angola & marine & 5 - 17,15 S & Yes   &       &  \\
+      254   & ~\citet{GlobalWeb} & ~\citet{Angelini2013} & Brazil & stream & 21 S  & Yes   &       &  \\
+      255   & ~\citet{GlobalWeb} & ~\citet{Angelini2013} & Brazil & stream & 21 S  & Yes   &       &  \\
+      256   & ~\citet{GlobalWeb} & ~\citet{Angelini2013} & Brazil & stream &       & No    & Could not locate original source &  \\
+      257   & ~\citet{GlobalWeb} & ~\citet{Baeta2011} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+      258   & ~\citet{GlobalWeb} & ~\citet{Baeta2011} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+      259   & ~\citet{GlobalWeb} & ~\citet{Baeta2011} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+      260   & ~\citet{GlobalWeb} & ~\citet{Baeta2011} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+      261   & ~\citet{GlobalWeb} & ~\citet{Baeta2011} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+      262   & ~\citet{GlobalWeb} & ~\citet{Baeta2011} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+      263   & ~\citet{GlobalWeb} & ~\citet{Schnieder1997} & USA   & lake  & 45,58,50 N & Yes   &       &  \\
+      264   & ~\citet{GlobalWeb} & ~\citet{Stagliano2002} & USA   & terrestrial & 39,06,27 N & Yes   &       &  \\
+      265   & ~\citet{GlobalWeb} & ~\citet{Lin2006} & Taiwan & marine & 22,27 N & Yes   &       &  \\
+      266   & ~\citet{GlobalWeb} & ~\citet{Cornejo-Donoso2008} & Antarctica & marine & 60 - 69 S & Yes   &       &  \\
+      267   & ~\citet{GlobalWeb} & ~\citet{Zetina-Rejon2003} & Mexico & marine & 23.15 - 22.9N & Yes   &       &  \\
+      268   & ~\citet{GlobalWeb} & ~\citet{Cruz-Escalona2007} & Mexico & marine & 18,45 - 18,50 N & Yes   &       &  \\
+      269   & ~\citet{GlobalWeb} & ~\citet{Liu2007} & China & lake  & 29,32,35 N & Yes   &       &  \\
+      270   & ~\citet{GlobalWeb} & ~\citet{Filguera2011} & Spain & marine & 42,17,37 - 42,19,29 N & Yes   &       &  \\
+      271   & ~\citet{GlobalWeb} & ~\citet{Amundsen2013} & Norway & lake  & 69,07 N & Yes   &       & Parasites removed \\
+      272   & ~\citet{GlobalWeb} & ~\citet{Hampton2011} & USA   & lake  & 48,03,29 N & Yes   &       &  \\
+      273   & ~\citet{GlobalWeb} & ~\citet{Parker2006} & Alaska & stream & 69,1 N & Yes   &       &  \\
+      274   & ~\citet{GlobalWeb} & ~\citet{Parker2006} & Alaska & stream & 69,1 N & Yes   &       &  \\
+      275   & ~\citet{GlobalWeb} & ~\citet{Parker2006} & Alaska & stream & 69,1 N & Yes   &       &  \\
+      276   & ~\citet{GlobalWeb} & ~\citet{Parker2006} & Alaska & stream & 69,1 N & Yes   &       &  \\
+      277   & ~\citet{GlobalWeb} & ~\citet{Massana1996} & Spain & lake  & 42,08,6 - 42,07 N & Yes   &       &  \\
+      278   & ~\citet{GlobalWeb} & ~\citet{Stewart2011} & USA   & lake  & 43.7 N & Yes   &       &  \\
+      279   & ~\citet{GlobalWeb} & ~\citet{Stewart2011} & USA   & lake  & 43.7 N & Yes   &       &  \\
+      280   & ~\citet{GlobalWeb} & ~\citet{Cromar1996} & Canada & stream & 43,58 N & Yes   &       &  \\
+      281   & ~\citet{GlobalWeb} & ~\citet{Cromar1996} & Canada & stream & 44,58 N & Yes   &       &  \\
+      282   & ~\citet{GlobalWeb} & ~\citet{Cromar1996} & Canada & stream & 45,58 N & Yes   &       &  \\
+      283   & ~\citet{GlobalWeb} & ~\citet{Cromar1996} & Canada & stream & 46,58 N & Yes   &       &  \\
+      284   & ~\citet{GlobalWeb} & ~\citet{Cromar1996} & Canada & stream & 47,58 N & Yes   &       &  \\
+      285   & ~\citet{GlobalWeb} & ~\citet{Cromar1996} & Canada & stream & 48,58 N & Yes   &       &  \\
+      286   & ~\citet{GlobalWeb} & ~\citet{Cromar1996} & Canada & stream & 49,58 N & Yes   &       &  \\
+      287   & ~\citet{GlobalWeb} & ~\citet{Cromar1996} & Canada & stream & 50,58 N & Yes   &       &  \\
+      288   & ~\citet{GlobalWeb} & ~\citet{Christian1999} & USA   & estuary & 30,05,39 N & Yes   &       &  \\
+      289   & ~\citet{GlobalWeb} & ~\citet{Fetahi2011} & Ethiopia & lake  & 11,15 N & Yes   &       &  \\
+      290   & ~\citet{GlobalWeb} & ~\citet{Brodeur1992} & USA   & marine & 43 - 48 N & Yes   &       &  \\
+      291   & ~\citet{GlobalWeb} & ~\citet{Brodeur1992} & USA   & marine & 44 - 48 N & Yes   &       &  \\
+      292   & ~\citet{GlobalWeb} & ~\citet{Brodeur1992} & USA   & marine & 45 - 48 N & Yes   &       &  \\
+      293   & ~\citet{GlobalWeb} & ~\citet{Brodeur1992} & USA   & marine & 46 - 48 N & Yes   &       &  \\
+      294   & ~\citet{GlobalWeb} & ~\citet{Gaedke1994} & Europe & lake  & 47,37,30 N & Yes   &       &  \\
+      295   & ~\citet{GlobalWeb} & ~\citet{Preston2012} & USA   & lake  & 37.66 N & Yes   &       & Parasites removed \\
+      296   & ~\citet{GlobalWeb} & ~\citet{Ratsirarson1996} & Madagascar & lake  & 24,55 S & Yes   &       &  \\
+      297   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      298   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      299   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      300   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      301   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      302   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      303   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      304   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      305   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      306   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      307   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      308   & ~\citet{GlobalWeb} & ~\citet{Closs1994} & Australia & stream & 37,40 S & Yes   &       &  \\
+      309   & ~\citet{GlobalWeb} & ~\citet{Gontikaki2011} & Atlantic Ocean & marine & 61,13,88 N & Yes   &       &  \\
+      310   & ~\citet{GlobalWeb} & ~\citet{Khan2009} & India & lake  & 12,45,25 N & Yes   &       &  \\
+      311   & ~\citet{GlobalWeb} & ~\citet{Memmott2000} & UK    & terrestrial &       & No    & Source web &  \\
+      312   & ~\citet{GlobalWeb} & ~\citet{Kaiser-Bunbury2009} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+      313   & ~\citet{GlobalWeb} & ~\citet{Kaiser-Bunbury2009} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+      314   & ~\citet{GlobalWeb} & ~\citet{Kaiser-Bunbury2011} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+      315   & ~\citet{GlobalWeb} & ~\citet{Kaiser-Bunbury2011} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+      316   & ~\citet{GlobalWeb} & ~\citet{Kaiser-Bunbury2011} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+      317   & ~\citet{GlobalWeb} & ~\citet{Kaiser-Bunbury2011} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+      318   & ~\citet{GlobalWeb} & ~\citet{Kaiser-Bunbury2011} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+      319   & ~\citet{GlobalWeb} & ~\citet{Kaiser-Bunbury2011} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+      320   & ~\citet{GlobalWeb} & ~\citet{Ruzicka2012} & USA   & marine & 42 - 49 N & Yes   &       &  \\
+      321   & ~\citet{GlobalWeb} & ~\citet{Ruzicka2012} & USA   & marine & 43 - 49 N & Yes   &       &  \\
+      322   & ~\citet{GlobalWeb} & ~\citet{Ruzicka2012} & USA   & marine & 44 - 49 N & Yes   &       &  \\
+      323   & ~\citet{GlobalWeb} & ~\citet{Ruzicka2012} & USA   & marine & 45 - 49 N & Yes   &       &  \\
+      324   & ~\citet{GlobalWeb} & ~\citet{Ruzicka2012} & USA   & marine & 46 - 49 N & Yes   &       &  \\
+      325   & ~\citet{GlobalWeb} & ~\citet{Lewis2002} & Belize & terrestrial &       & No    & Host-parasitoid web &  \\
+      326   & ~\citet{GlobalWeb} & ~\citet{Lewis2002} & Belize & terrestrial &       & No    & Host-parasitoid web &  \\
+      327   & ~\citet{GlobalWeb} & ~\citet{Kelleway2010} & Australia & stream & 29,13 S & Yes   &       &  \\
+      328   & ~\citet{GlobalWeb} & ~\citet{Kelleway2010} & Australia & stream & 29,20,0 S & Yes   &       &  \\
+      329   & ~\citet{GlobalWeb} & ~\citet{Kelleway2010} & Australia & stream & 29,35 S & Yes   &       &  \\
+      330   & ~\citet{GlobalWeb} & ~\citet{Kelleway2010} & Australia & stream & 29,13 S & Yes   &       &  \\
+      331   & ~\citet{GlobalWeb} & ~\citet{Kelleway2010} & Australia & stream & 29,20,0 S & Yes   &       &  \\
+      332   & ~\citet{GlobalWeb} & ~\citet{Huang2008} & China & stream & 31.70 N & Yes   &       &  \\
+      333   & ~\citet{GlobalWeb} & ~\citet{Link2002} & USA   & marine & 33,51 - 44,49 N & Yes   &       &  \\
+      334   & ~\citet{GlobalWeb} & ~\citet{Alcorlo2001} & Spain & lake  & 41,26,36 N & Yes   &       &  \\
+      335   & ~\citet{GlobalWeb} & ~\citet{Alcorlo2001} & Spain & lake  & 41,26,05 N & Yes   &       &  \\
+      336   & ~\citet{GlobalWeb} & ~\citet{Alcorlo2001} & Spain & lake  & 41,26,36 N & Yes   &       &  \\
+      337   & ~\citet{GlobalWeb} & ~\citet{Alcorlo2001} & Spain & lake  & 41,26,05 N & Yes   &       &  \\
+      338   & ~\citet{GlobalWeb} & ~\citet{Torres2013} & South Atlantic & marine &       & No    & Could not locate original source &  \\
+      339   & ~\citet{GlobalWeb} & ~\citet{Bulman2001} & Australia & marine & 37-39 S & Yes   &       &  \\
+      340   & ~\citet{GlobalWeb} & ~\citet{Smith2007} & Antarctica & marine & 74-78 S & Yes   &       &  \\
+      341   & ~\citet{GlobalWeb} & ~\citet{Lancraft1991} & Antarctica & marine & 58,20.8 - 60,10.4 S & Yes   &       &  \\
+      342   & ~\citet{GlobalWeb} & ~\citet{Hopkins1993} & Antarctica & marine & 57,00 - 60,45 S & Yes   &       &  \\
+      343   & ~\citet{GlobalWeb} & ~\citet{Kitching1987} & Australia & lake  & 28,12 S & Yes   &       &  \\
+      344   & ~\citet{GlobalWeb} & ~\citet{Hodkinson2004} & Norway & terrestrial &       & No    & Host-parasitoid web &  \\
+      345   & ~\citet{GlobalWeb} & ~\citet{Boit2012} & Europe & lake  & 47,38,10 N & Yes   &       &  \\
+      346   & ~\citet{GlobalWeb} & ~\citet{Rayner2010} & Australia & stream & 17,7 S & Yes   &       &  \\
+      347   & ~\citet{GlobalWeb} & ~\citet{Motta2005} & Brazil & stream & 23,03 S & Yes   &       &  \\
+      348   & ~\citet{GlobalWeb} & ~\citet{Douglass2011} & USA   & marine & 37,13 N & Yes   &       &  \\
+      349   & ~\citet{GlobalWeb} & ~\citet{Douglass2011} & USA   & marine & 37,13 N & Yes   &       &  \\
+      350   & ~\citet{GlobalWeb} & ~\citet{Douglass2011} & USA   & marine & 37,13 N & Yes   &       &  \\
+      351   & ~\citet{GlobalWeb} & ~\citet{Warren1989} & UK    & lake  &       & No    & Could not locate original source &  \\
+      352   & ~\citet{GlobalWeb} & ~\citet{Poepperl2003} & Germany & stream & 54,06 N & No    & describes compartments, not species &  \\
+      353   & ~\citet{GlobalWeb} & ~\citet{Poepperl2003} & Germany & stream & 54,06 N & No    & describes compartments, not species &  \\
+      354   & ~\citet{GlobalWeb} & ~\citet{Goldwasser1993} & St. Martin & terrestrial & 18,03 N & Yes   &       &  \\
+      355   & ~\citet{GlobalWeb} & ~\citet{Cohen2003} & USA   & lake  & 46,13 N & Yes   &       &  \\
+      356   & ~\citet{GlobalWeb} & ~\citet{Cohen2003} & USA   & lake  & 46,13 N & Yes   &       &  \\
+      357   & ~\citet{GlobalWeb} & ~\citet{Yodzis1998} & South Africa & marine & 34,21 - 16 S & No    & Study site unclear &  \\
+      358   & ~\citet{GlobalWeb} & ~\citet{Schroter2003} & Europe & terrestrial &       & No    & Generalized scheme &  \\
+      359   & ~\citet{GlobalWeb} & ~\citet{Baiser2012} & North America & lake  &       & No    & Study site unclear &  \\
+      \hline
+    \end{tabular}%
+  \end{table}%
+
+\end{landscape}
+\newpage
 
@@
     The relationships between latitude and the proportions of species at each trophic level were more complex. 
-    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.011, $p$\textless0.001) 
+    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001) 
     but did not vary with latitude in estuarine, marine, lake, or terrestrial 
@@
     $\beta_{Latitude:Lake}$=-0.006, $p$=0.001; and
-    $\beta_{Latitude:Stream}$=-0.007, $p$=0.006).
+    $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
 
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[width=.75\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}}
+\centerline{\includegraphics*[width=.75\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
 \caption{Scaling relationships for link density, generality, 
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
@@
 \begin{figure}[!h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
@@
 \begin{figure}[!h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}
 \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem

### 2015-07-01 code/TL_marginal_latitude.py
Was missing the latitude-ecotype interaction for LS vs T in terrestrials

@@ -398,7 +398,7 @@ def main():
 
   names=['','','','','','','','','','','','','','','','','','','','','','','','','','','','','','','','']
 
-  for form in ['proportions','numbers']:
+  for form in ['proportions']:#,'numbers']:
     for TL in TLs:
       # Make a separate graph for each TL
       grace=MultiPanelGrace(colors=ColorBrewerScheme('Greys'))

### 2015-07-01 code/marginal_CIs.R

@@ -225,7 +225,7 @@ T_CIs <- function(model){
         stream_upper <- stream_m + 1.64*stream_se
         stream_lower <- stream_m - 1.64*stream_se
 
-        terr_m <- marginal + betas["log(Toppreds):Terr"] + betas["log(Toppreds):Terr:Latitude"]
+        terr_m <- marginal + betas["log(Toppreds):Terr"] + lat*betas["log(Toppreds):Terr:Latitude"]
         terr_se <- sqrt(se^2 +
           lat^2*covar["log(Toppreds):Terr:Latitude","log(Toppreds):Terr:Latitude"] 
           +2*lat*covar["log(Toppreds):Terr:Latitude","log(Toppreds)"]

### 2015-07-01 manuscript/latitudepaper.tex
Version uploaded to Proc R Soc

@@
   If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
-  degree of specialisation (i.e., the breadth of the Eltonian niche ~\citep{Elton1927}) of species within food webs.
+  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927}) of species within food webs.
   Attempts to unravel these effects, however,
@@
   For example,
-  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics(~\citealp{Marra1997,Dyer2007};
+  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\citealp{Marra1997,Dyer2007};
   but see~\citealp{Schleuning2012}). However,
@@
 
-    We compiled a list of 163 empirical food webs from
+    We compiled a list of 166 empirical food webs from
     multiple sources (see \emph{Appendix S1} for web origins and selection
@@
     marine, lake, and terrestrial networks with estuarine
-    networks providing the intercept) and $\epsilon_{i}$ a residual error term.
+    networks providing the intercept) and $\epsilon_{i}$ is a residual error term.
     The logarithmic formulation of this model is
@@
   $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
-  that there was little overall scaling relationship. In contrast, the scaling
+  that there was weak scaling at most latitudes. In contrast, the scaling
   exponent of generality with the proportion of basal resources was positive
@@
   ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability) except in stream and terrestrial food
-  webs, where scaling was more strongly negative in the tropics and near zero
-  near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
-  $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and
-  $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
-  for vulnerability;
-  Fig~\ref{BIT}). The best-fit model for generality did not include any terms
+  $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
+  In stream and terrestrial food webs, however, scaling was more strongly negative in the 
+  tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
+  and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
+  $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
+  for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
   for latitude in any ecosystem type.
@@
   species richness in particular is also known to vary systematically over
-  latitude~\citep{Kaufman1995,Schemske2009,Macpherson2002}, intuitively one
-  might suspect that any relationship between food-web properties such as
-  generality might be due to the latitudinal gradient in species richness. In
-  this dataset, however, we did not find overall latitudinal gradients in
-  species richness, links per species,  generality, vulnerability, or the
-  proportions of food webs accounted for by  basal resources, intermediate
-  consumers, and top predators (see \emph{Appendix S3} for details).
+  latitude~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009},
+  intuitively one might suspect that any relationship between food-web
+  properties such as generality might be due to the latitudinal gradient in
+  species richness. In this dataset, however, we did not find overall
+  latitudinal gradients in species richness, links per species,generality,
+  vulnerability, or the proportions of food webs accounted for by basal
+  resources, intermediate consumers, and top predators, except in lake and
+  stream food webs where the proportions of top predators tended to decrease
+  towards the poles  (see \emph{Appendix S3} for details).
 
@@
   contrasts strongly with other
-  studies~\citep{Kaufman1995,Schemske2009,Macpherson2002}. As numbers of
-  species and links included in a food web vary strongly with sampling effort
-  as well as with the underlying diversity of the study area, it is possible
-  that the lack of latitudinal trends here is a result of researchers tending
-  to expend similar amounts of sampling effort across studies. This could
-  result in food webs describing species-rich tropical communities omitting
-  more species and links than species-poor arctic communities. In addition, it
-  is worth noting that gradients in species richness are generally measured
-  for a single taxonomic group at a
-  time~\citep[e.g.]{Kaufman1995,Schemske2009,Macpherson2002}. It is possible
+  studies~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. As
+  numbers of species and links included in a food web vary strongly with
+  sampling effort as well as with the underlying diversity of the study area,
+  it is possible that the lack of latitudinal trends here is a result of
+  researchers tending to expend similar amounts of sampling effort across
+  studies. This could result in food webs describing species-rich tropical
+  communities omitting more species and links than species-poor arctic
+  communities. In addition, it is worth noting that gradients in species
+  richness are generally measured for a single taxonomic group at a
+  time~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is possible
   that these taxa are not well-represented in our food webs and that the
@@
   richness and latitude in any ecosystem type means that any effect of
-  latitude on other scalingrelationships is not being driven by an
-  underlyinglatitudinal gradient in species richness. The lack of confounding
-  effects of latitude allows us tomore clearly assess effects of latitude on
-  scaling with species richness and proportions of species in differenttrophic
+  latitude on other scaling relationships is not being driven by an underlying
+  latitudinal gradient in species richness. The lack of confounding effects of
+  latitude allows us to more clearly assess effects of latitude on scaling
+  with species richness and proportions of species in different trophic
   levels.
@@
   in high-latitude lakes. These trends are consistent with the hypothesis that
-  greater stability in the tropics leads to narrower
-  niches~\citep{Vazquez2004} and a higher proportion of specialists. This may
-  be partly due to high-latitude species tending to switch between different
-  seasonally-available prey~\citep{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
+  greater stability in the tropics leads to narrower niches~\citep{Vazquez2004}
+  and a higher proportion of specialists. This may be partly due to high-latitude 
+  species tending to switch between different seasonally-available 
+  prey~\citep{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
   freshwater ecosystems may have more stable composition.
@@
   The scaling of link density, generality and vulnerability with proportions
-  of species at different trophic levels, however, did not differ between lakes
-  and most other food webs. Indeed, there was comparatively little variation in
-  scaling with the trophic-level breakdown of a web across ecosystem types.
-  Terrestrial food webs tended to exhibit less change in scaling over latitude
-  than other ecosystem types, as did marine webs when considering scaling with
-  the proportion of basal resources. More excitingly, the negative relationships
-  between the proportion of top predators in a web and link density and
-  vulnerability were weaker (i.e., the scaling exponent was more strongly
-  negative) in low-latitude stream ecosystems. This may imply that top predators
-  in high-latitude streams tend to be more generalist than their low-latitude
-  equivalents~\citep{Winemiller2008}, perhaps due to prey-switching during seasonal
-  food shortages~\citep{Magalhaes1993}.
-  More generally, the lack of correspondence between the scaling of food-web
-  properties with species richness and with proportions of species at each
-  trophic level suggests that the size and trophic breakdowns of a community can
-  each provide different information~\citep{Downing2002}.
+  of species at different trophic levels, however, did not differ between
+  lakes and most other food webs. Indeed, there was comparatively little
+  variation in scaling with the trophic-level breakdown of a web across
+  ecosystem types. Nevertheless, the negative relationships between the
+  proportion of top predators in a web and link density and vulnerability were
+  weaker (i.e., the scaling exponent was more strongly negative) in low-latitude 
+  stream ecosystems. This may imply that top predators in high-latitude 
+  streams tend to be more generalist than their low-latitude
+  equivalents~\citep{Winemiller2008}, perhaps due to prey-switching during
+  seasonal food shortages~\citep{Magalhaes1993}. More generally, the lack of
+  correspondence between the scaling of food-web properties with species
+  richness and with proportions of species at each trophic level suggests that
+  the size and trophic breakdowns of a community can each provide different
+  information~\citep{Downing2002}.
 
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
+% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
-type. As the these relationships take the form of power laws, we did this by dividing the food-web
+type. As these relationships take the form of power laws, we did this by dividing the food-web
 property (e.g. link density) by the predictor (e.g. \% Basal) raised to an exponent including the 
@@
 latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
-we show the rescaled values (white circles) as well as the overall scaling relationship using estuarine
-ecosystems as a baseline (black line, N=163 food webs). For a figure with the uncorrected values,
+we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
+ecosystems as a baseline (black line, N=166 food webs). For a figure with the uncorrected values,
 see Fig.~\emph{S1}, \emph{Appendix S4}.}
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
+% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
 \caption{Changes to the scaling of link density with species richness across ecosystem
 types and over latitude. We show the estimated scaling exponent for species richness (black
-line) with its 95\% confidence interval (in grey), based on N=163 empirical food webs.
+line) with its 95\% confidence interval (in grey), based on N=166 empirical food webs.
 Latitude is given in degrees from the equator regardless of direction. The
@@
 \begin{figure}[!H]
-\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
+% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
 \caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
@@
 we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
-on N=163 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
+on N=166 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
 The behaviour of exponents for the scaling relationships of generality and vulnerability with each 

### 2015-07-01 manuscript/latitudepaper.tex
on second thought, maybe I'm not CIE

@@
 \title{Specialisation in food webs scales with species richness but not with latitude}
-\author{Alyssa R. Cirtwill$^{1,2,3}$, Daniel B. Stouffer$^{1,2}$, Tamara N. Romanuk$^{3}$}
+\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
 \date{\small$^1$School of Biological Sciences\\University of Canterbury\\
 Private Bag 4800\\Christchurch 8140, New Zealand \\
-\medskip$^2$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
-Private Bag 4800\\Christchurch 8140, New Zealand \\
-\medskip$^3$Department of Biology\\
+\medskip$^2$Department of Biology\\
 Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
-Halifax NS, B3H 4R2, Canada\\}
+Halifax NS, B3H 4R2, Canada\\
+\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
+Private Bag 4800\\Christchurch 8140, New Zealand \\}
 

### 2015-07-01 manuscript/supplement.tex
lets have some line numbers here too

--- 2015-06-29 manuscript/supplement.tex
@@
 \author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
-\date{\small$^1$School of Biological Sciences\\University of Canterbury\\
+\date{\footnotesize$^1$School of Biological Sciences\\University of Canterbury\\
 Private Bag 4800\\Christchurch 8140, New Zealand \\
@@
 \beginsupplement
+\linenumbers
 % \begin{landscape}
@@
   species only. In addition, we included 30 of the 40 webs
-  from~\citet{Riede2011}, which were originally collected to test the
-  relationship between consumer and resources body sizes. Nine of the
+  from~\citet{Riede2011}. Nine of the
   remaining webs in the~\citet{Riede2011} dataset were also included in
@@
 
- See Table S1 for a list of rejected webs and reasons for their
+ See Table~\ref{S1} for a list of rejected webs and reasons for their
   exclusion.
 
-\subsection*{Appendix S2: Supplemental Methods and Results - scaling Relationships with S}
+  \newpage
+  \begin{landscape}
+
+    \begin{table}[h!]
+    \centering
+    \caption{Sources of food webs considered for use in this study. ``Collection" indicates the direct source of the
+    food web (i.e., where the interaction matrix was obtained) while ``Original source" indicates the original publication
+    of the food web. We also show the ecosystem type, country of origin, and latitude for each food web, as well as whether
+    it was ultimately included in the study. Collection 1 is~\citet{Riede2011}, collection 2 is~\citet{Dunne2013}, and collection 3 is~\citet{GlobalWeb}.}
+    \label{S1}
+
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection \\
+        \hline
+        Alamitos & 1 & \citet{Harrison1995}    & stream & 37,12,25 N & Yes   &       \\
+        Alford & 1 & \citet{Havens1992}    & lake  & 44,15,41.59 N & Yes   &       \\
+        Beaver & 1 & \citet{Havens1992}    & lake  & 44,18,58.13 N & Yes   &       \\
+        Bere  & 1 & \citet{Woodward2008}  & stream & 50,45,7 N & Yes   &       \\
+        Bridge & 1 & \citet{Havens1992}    & lake  & 44,09,42.66 N & Yes   &       \\
+        Broad & 1 & \citet{Townsend1998}  & stream & 45.896938 S & Yes   &       \\
+        Broadstone & 1 & \citet{Woodward2005} & stream  & 51,01,05 N & Yes   &       \\
+        Calero & 1 & \citet{Harrison1995}    & stream & 37,11,09 - 20 N & Yes   &       \\
+        Canton & 1 & \citet{Townsend1998}  & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) \\
+        Carpinteria2006 & 1 & \citet{Lafferty2006}    & estuary & 34.41 - 34.40 N & Yes   &       \\
+        Chub  & 1 & \citet{Havens1992}    & lake  & 43,31,39.36 N & Yes   &       \\
+        Coachella & 1 & \citet{Polis1991a} & terrestrial & 33,54 N & Yes   &       \\
+        Connery & 1 & \citet{Havens1992}    & lake  & 44,18,42.10 N & Yes   &       \\
+        Corte & 1 & \citet{Harrison1995}    & stream & 37,56,28 - 37,57,39 N & Yes   &       \\
+        Coyote & 1 & \citet{Harrison1995}    & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       \\
+        German & 1 & \citet{Townsend1998}  & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) \\
+        GrandeCl & 1 & \citet{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
+        GrandeSc & 1 & \citet{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
+        Guadalupe & 1 & \citet{Harrison1995}    & stream & 37,27,54 - 37,21,17 N & Yes   &       \\
+        Hainich   & 1 & Unpublished  & terrestrial &       & No    & Could not locate original source \\
+        LittleKyeBurn & 1 & \citet{Townsend1998}  & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) \\
+        LittleRock & 1 & \citet{Martinez1991}    & lake  & 45,44,07.94 N & Yes   &       \\
+        Mondego & 1 & \citet{Patricio2006}  & estuary & 40,08 N & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        Montane Forest & 1 & \citet{Rasmussen1941}    & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) \\
+        Reef  & 1 & \citet{Opitz1996}  & marine & 18,29 - 17,53 N & Yes   &       \\
+        Sierra & 1 & \citet{Brose2005}    & lake  & 36,50 - 37,02 N & Yes   &       \\
+        SimberloffE1 & 1 & \citet{Simberloff1976}  & terrestrial & 24,40,37.29 N & Yes   &       \\
+        SimberloffE2 & 1 & \citet{Simberloff1976}  & terrestrial & 24,40,33 N & Yes   &       \\
+        SimberloffE3 & 1 & \citet{Simberloff1976}  & terrestrial & 24,41,23.82 N & Yes   &       \\
+        SimberloffE7 & 1 & \citet{Simberloff1976}  & terrestrial & 25,15 N & Yes   &       \\
+        SimberloffE9 & 1 & \citet{Simberloff1976}  & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       \\
+        SimberloffST2 & 1 & \citet{Simberloff1976}  & terrestrial & 24,36,16 N & Yes   &       \\
+        Skipwith & 1 & \citet{Warren1989}  & lake  & 53,40 N & Yes   &       \\
+        Stink & 1 & \citet{Havens1992}    & lake  & 43,37,55.88 N & Yes   &       \\
+        StMarks & 1 & \citet{Christian1999}    & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) \\
+        Stony  & 1 & \citet{Townsend1998}  & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) \\
+        TreleaseWoods & 1 & \citet{Twomey1945}    & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) \\
+        Tuesday & 1 & \citet{Jonsson2005}    & lake  & 46,13 N & Yes   &       \\
+        Weddell Sea & 1 & \citet{Brose2005}  & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) \\
+        Ythan & 1 & \citet{Huxham1996}     & marine &       & No    & Duplicated in Dunne (YthanDunne) \\
+        BahiaDunne & 2 & \citet{Hechinger2011}  & estuary & 30.43 - 30.46 N & Yes   &        \\
+        CarpinteriaDunne & 2 & \citet{Hechinger2011}    & estuary & 34.41 - 34.40 N & Yes   &        \\
+        EsteroDunne & 2 & \citet{Hechinger2011}  & estuary & 31.78 - 31.69 N & Yes   &        \\
+        FjordDunne & 2 & \citet{Zander2011}  & estuary & 54.92 - 54.75 N & Yes   &        \\
+        OtagoDunne & 2 & \citet{Mouritsen2011}  & estuary & 45.78 - 45.88 S & Yes   &        \\
+        SyltDunne & 2 & \citet{Thieltges2011}  & estuary & 54.83 - 55.12 N & Yes   &        \\
+        YthanDunne & 2 & \citet{Huxham1996}  & estuary & 57,18,32 N & Yes   &        \\
+        1     & 3 & \citet{Qazim1970}  & estuary &       & No    & Could not locate original source \\
+        2     & 3 & \citet{Day1967} & estuary &       & No    & Could not locate original source \\
+        3     & 3 & \citet{Woodwell1967}    & estuary & 41,03,11 N & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        4     & 3 & \citet{Johnston1956}    & estuary &       & No    & Sink web \\
+        5     & 3 & \citet{Teal1962}    & estuary & 31,28,38 N & Yes   &       \\
+        6     & 3 & \citet{MacGinitie1935}    & estuary & 36,48,18 N & Yes   &       \\
+        7     & 3 & \citet{Kremer1978}    & marine & 41,45 - 41,30 N & Yes   &       \\
+        8     & 3 & \citet{Nixon1973}    & estuary & 41,33,00 N & Yes   &       \\
+        9     & 3 & \citet{Kitching1967}  & stream &       & No    & Could not locate original source \\
+        10    & 3 & \citet{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
+        11    & 3 & \citet{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
+        12    & 3 & \citet{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
+        13    & 3 & \citet{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
+        14    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
+        15    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
+        16    & 3 & \citet{Copeland1974}    & estuary &       & No    & Could not locate original source \\
+        17    & 3 & \citet{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalized scheme \\
+        18    & 3 & \citet{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
+        19    & 3 & \citet{Brooks1963}    & lake &       & No    & Could not locate original source \\
+        20    & 3 & \citet{Knox1970}  & terrestrial &       & No    & Could not locate original source \\
+        21    & 3 & \citet{Patten1979}  & marine & 70-85 S & Yes   &       \\
+        22    & 3 & \citet{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
+        23    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        24    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        25    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        26    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        27    & 3 & \citet{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
+        28    & 3 & \citet{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
+        29    & 3 & \citet{Dunbar1953}  & marine &       & No    & Generalized scheme \\
+        30    & 3 & \citet{Mackintosh1964}  & marine &       & No    & Generalized scheme \\
+        31    & 3 & \citet{Petipa1970}  & marine &       & No    & Could not locate original source \\
+      \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        32    & 3 & \citet{Petipa1970}  & marine &       & No    & Could not locate original source \\
+        33    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
+        34    & 3 & \citet{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
+        35    & 3 & \citet{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
+        36    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
+        37    & 3 & \citet{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
+        38    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
+        39    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
+        40    & 3 & \citet{Harrison1962}  & terrestrial &       & No    & Generalized scheme \\
+        41    & 3 & \citet{Parin1970}  & marine &       & No    & Could not locate original source \\
+        42    & 3 & \citet{Vinogradov1978}  & marine &       & No    & Study site unclear \\
+        43    & 3 & \citet{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
+        44    & 3 & \citet{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
+        45    & 3 & \citet{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
+        46    & 3 & \citet{Patten1975}    & lake & 33,54 N & Yes   &       \\
+        47    & 3 & \citet{Harris1980}    & lake &       & No    & Study site unclear \\
+        48    & 3 & \citet{Simenstad1978}    & marine &       & No    & Extinct species \\
+        49    & 3 & \citet{Simenstad1978}    & marine &       & No    & Extinct species \\
+        50    & 3 & \citet{Nybakken1982}    & marine &       & No    & Generalized scheme \\
+        51    & 3 & \citet{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
+        52    & 3 & \citet{Paine1980a}    & marine & 58,27 N & Yes   &       \\
+        53    & 3 & \citet{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
+        54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
+        55    & 3 & \citet{Milne1972}  & estuary &       & No    & Could not locate original source \\
+        56    & 3 & \citet{Milne1972}  & estuary &       & No    & Could not locate original source \\
+        57    & 3 & \citet{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
+        58    & 3 & \citet{Cohen1990}  & lake & 51,46 N & Yes   &       \\
+        59    & 3 & \citet{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
+        60    & 3 & \citet{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
+        61    & 3 & \citet{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
+        62    & 3 & \citet{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        63    & 3 & \citet{Jones1950}     & stream & 52,25,08 N & Yes   &       \\
+        64    & 3 & \citet{Cummins1966}    & stream & 41,39,33 N & Yes   &       \\
+        65    & 3 & \citet{Tsuda1972}  & stream & 34,21,20 - 34,23,21 N & Yes   &       \\
+        66    & 3 & \citet{Mann1972a}  & stream & 51,30 N & Yes   &       \\
+        67    & 3 & \citet{Carlson1968}    & stream & 40,24,16 N & Yes   &       \\
+        68    & 3 & \citet{Morgan1972}  & lake &       & No    & Could not locate original source \\
+        69    & 3 & \citet{Cohen1990}  & estuary &       & No    & Could not locate original source \\
+        70    & 3 & \citet{Kemp1977}    & estuary & 28,54,08 N & Yes   &       \\
+        71    & 3 & \citet{Sorokin1972}  & lake & 48,00 N & Yes   &       \\
+        72    & 3 & \citet{Baril1983}  & lake & 46,02 N & Yes   &       \\
+        73    & 3 & \citet{Schiemer1979}  & lake &       & No    & Could not locate original source \\
+        74    & 3 & \citet{Cohen1990} & marine & 34,15,00 S & Yes   &       \\
+        75    & 3 & \citet{Pechlaner1972}  & lake & 47,11 N & Yes   &       \\
+        76    & 3 & \citet{Schiemer1979}  & lake & 47,42 - 47,54 N & Yes   &       \\
+        77    & 3 & \citet{Cohen1990}  & lake &       & No    & Could not locate original source \\
+        78    & 3 & \citet{Burgis1972}  & lake & 0     & Yes   &       \\
+        79    & 3 & \citet{Sarvala1974}  & lake &       & No    & Could not locate original source \\
+        80    & 3 & \citet{Sarvala1974}  & lake &       & No    & Could not locate original source \\
+        81    & 3 & \citet{Hatanaka1977}  & marine &       & No    & Could not locate original source \\
+        82    & 3 & \citet{Cohen1990} & marine &       & No    & Could not locate original source \\
+        83    & 3 & \citet{Cohen1990}  & lake &       & No    & Could not locate original source \\
+        84    & 3 & \citet{Wilbur1972}    & lake & 42,28,42 N & Yes   &       \\
+        85    & 3 & \citet{Mizuno1982}  & lake &       & No    & Could not locate original source \\
+        86    & 3 & \citet{Hogetsu1979}  & marine & 34,36 - 35,38 N & Yes   &       \\
+        87    & 3 & \citet{Bradstreet1982}  & terrestrial & 72,46,34.95 N & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        88    & 3 & \citet{Kuusela1980}  & stream &       & No    & Could not locate original source \\
+        89    & 3 & \citet{Hartley1948}  & stream & 52,13 N & Yes   &       \\
+        91    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
+        92    & 3 & \citet{Swan1961}  & terrestrial &       & No    & Generalized scheme \\
+        93    & 3 & \citet{Pattie1966}    & terrestrial & 45 N  & Yes   &       \\
+        94    & 3 & \citet{Brown1971}    & terrestrial &       & No    & Could not locate original source \\
+        95    & 3 & \citet{Brown1975}    & terrestrial & 70,11,14.18 N & Yes   &       \\
+        96    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
+        97    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
+        98    & 3 & \citet{Holm1980}  & terrestrial &       & No    & Could not locate original source \\
+        99    & 3 & \citet{Howes1954}    & terrestrial & 32,36 N & Yes   &       \\
+        100   & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
+        101   & 3 & \citet{Cohen1990} & lake  &       & No    & Could not locate original source \\
+        102   & 3 & \citet{Shushkina1979}  & marine & 10 S - 15 N & Yes   &       \\
+        103   & 3 & \citet{Petipa1979}  & marine &       & No    & Generalized scheme \\
+        104   & 3 & \citet{Menge1976}  & marine & 4,48,04 N & Yes   &       \\
+        105   & 3 & \citet{Edwards1982}  & marine & 42,40 N & Yes   &       \\
+        106   & 3 & \citet{Glynn1965}  & marine &       & No    & Could not locate original source \\
+        107   & 3 & \citet{Peterson1979}  & marine & 39,52,02 N & Yes   &       \\
+        108   & 3 & \citet{Hewatt1937}  & marine & 36,37 N & Yes   &       \\
+        109   & 3 & \citet{Castilla1981} & marine &       & No    & Could not locate original source \\
+        110   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
+        111   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
+        112   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
+        113   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
+        114   & 3 & \citet{Marshall1982}  & lake  & 17,54,11.90 S & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        115   & 3 & \citet{Koepcke1952}  & marine &       & No    & Could not locate original source \\
+        116   & 3 & \citet{Hurlbert1972}  & lake  & 35,09,19 S & Yes   &       \\
+        117   & 3 & \citet{Zaret1973}  & lake  & 9,11,31.50 N & Yes   &       \\
+        118   & 3 & \citet{Bindloss1972}  & lake  & 56,41,18.71 N & Yes   &       \\
+        119   & 3 & \citet{Mann1972}  & stream & 51,27 N & Yes   &       \\
+        120   & 3 & \citet{Moriarty1973}  & lake  & 0,00,58 N & Yes   &       \\
+        121   & 3 & \citet{VanEs1977}  & estuary & 53,20 - 53,15 N & Yes   &       \\
+        122   & 3 & \citet{Nixon1973}  & estuary & 41,33,04 N & Yes   &       \\
+        123   & 3 & \citet{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
+        124   & 3 & \citet{Collins1976}  & stream & 44,34 N & Yes   &       \\
+        125   & 3 & \citet{Landry1977}  & marine &       & No    & Generalized scheme \\
+        126   & 3 & \citet{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
+        127   & 3 & \citet{Beaver1979}  & lake  &       & No    & Could not locate original source \\
+        128   & 3 & \citet{Beaver1979}  & lake  &       & No    & Could not locate original source \\
+        129   & 3 & Unpublished & terrestrial &       & No    & Unpublished \\
+        130   & 3 & \citet{Odum1975}  & estuary & 27,12 N & Yes   &       \\
+        131   & 3 & \citet{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
+        132   & 3 & \citet{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
+        133   & 3 & \citet{Beaver1985}  & lake  & 7,52,22 N & Yes   &       \\
+        134   & 3 & \citet{Beaver1985}  & lake  & 19 S  & Yes   &       \\
+        135   & 3 & \citet{Beaver1985}  & lake  & 4,40,46 S & Yes   &       \\
+        136   & 3 & \citet{Bradshaw1983}    & lake  &       & No    & Could not locate original source \\
+        137   & 3 & \citet{Corker1984}  & lake  & 22,14-22,17 N & Yes   &       \\
+        138   & 3 & \citet{Kitching1983}     & lake  &       & No    & Could not locate original source \\
+        139   & 3 & \citet{Kitching1983}  & lake  &       & No    & Could not locate original source \\
+        140   & 3 & \citet{Seifert1979}  & terrestrial & 10,21 N & Yes   &       \\
+        141   & 3 & \citet{Seifert1976}  & terrestrial &       & No    & Competition network \\
+        142   & 3 & \citet{Seifert1976}  & terrestrial &       & No    & Competition network \\
+        143   & 3 & \citet{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
+         \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        144   & 3 & \citet{Snow1958}  & lake  &       & No    & Could not locate original source \\
+        145   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
+        146   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
+        147   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
+        148   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
+        149   & 3 & \citet{Force1974}    & terrestrial &       & No    & Host-parasitoid web \\
+        150   & 3 & \citet{Hopkins1984}     & terrestrial &       & No    & Host-parasitoid web \\
+        151   & 3 & \citet{Richards1926}     & terrestrial & 51,20,04 N & Yes   &       \\
+        152   & 3 & \citet{Whittaker1984}    & terrestrial &       & No    & Source web \\
+        153   & 3 & \citet{Mayse1978}    & terrestrial & 40,06,38 N & Yes   &       \\
+        154   & 3 & \citet{Mayse1978}    & terrestrial & 39,56,41 N & Yes   &       \\
+        155   & 3 & \citet{Askew1975}     & terrestrial &       & No    & Host-parasitoid web \\
+        156   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        157   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        158   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        159   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        160   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        161   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        162   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        163   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        164   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        165   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        166   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        167   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        168   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        169   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\        
+        170   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        171   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\      
+        172   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        173   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        174   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        175   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        176   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        177   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        178   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        \hline
+        \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        179   & 3 & \citet{Robinson1953}  & terrestrial &       & No    & Source web \\
+        180   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        181   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        182   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        183   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        184   & 3 & \citet{Beaver1972}     & terrestrial &       & No    & Could not locate original source \\
+        185   & 3 & \citet{Chapman1955}     & terrestrial &       & No    & Source web \\
+        186   & 3 & \citet{Cornaby1974}  & terrestrial &       & No    & Source web \\
+        187   & 3 & \citet{Cornaby1974}  & terrestrial &       & No    & Source web \\
+        188   & 3 & \citet{Jiron1981}  & terrestrial &       & No    & Source web \\
+        189   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        190   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        191   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        192   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        193   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        194   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        195   & 3 & \citet{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
+        196   & 3 & \citet{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
+        197   & 3 & \citet{Mohr1943}    & terrestrial &       & No    & Source web \\
+        198   & 3 & \citet{Schoenly1983}  & terrestrial &       & No    & Source web \\
+        199   & 3 & \citet{Valiela1969}    & terrestrial &       & No    & Source web \\
+        200   & 3 & \citet{Valiela1974}    & terrestrial &       & No    & Source web \\
+        201   & 3 & \citet{Valiela1974}    & terrestrial &       & No    & Source web \\
+        202   & 3 & \citet{Allan1982}    & stream & 38,50,21 N & Yes   &       \\
+        203   & 3 & \citet{Collins1976}    & stream & 44,24 N & Yes   &       \\
+        204   & 3 & \citet{Fryer1959} & lake  & 11,36,39 S & Yes   &       \\
+        205   & 3 & \citet{Hildrew1985}     & stream & 51,01,05 N & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        206   & 3 & \citet{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
+        207   & 3 & \citet{Koslucher1973}    & stream & 41,57 - 42,14 N & Yes   &       \\
+        208   & 3 & \citet{Minckley1963}    & stream & 37,56 N & Yes   &       \\
+        209   & 3 & \citet{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
+        210   & 3 & \citet{Percival1929}     & stream &       & No    & Generalized scheme \\
+        211   & 3 & \citet{Ricker1935}  & stream &       & No    & Could not locate original source \\
+        212   & 3 & \citet{Ricker1935}  & stream &       & No    & Could not locate original source \\
+        213   & 3 & \citet{Badcock1949}     & stream & 53 N  & Yes   &       \\
+        214   & 3 & \citet{Thompson2003}    & stream & 44,40,44 N & Yes   &       \\
+        215   & 3 & \citet{Thompson2003}    & stream & 40,40,52 N & Yes   &       \\
+        216   & 3 & \citet{Thompson2003}    & stream & 35,02,50 N & Yes   &       \\
+        217   & 3 & \citet{Thompson2003}    & stream & 35,03,50 N & Yes   &       \\
+        218   & 3 & \citet{Thompson2004c}  & stream & 45.79 S & Yes   &       \\
+        219   & 3 & \citet{Thompson2004c}  & stream & 44.64 S & Yes   &       \\
+        220   & 3 & \citet{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
+        221   & 3 & \citet{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
+        222   & 3 & \citet{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
+        223   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        224   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        225   & 3 & \citet{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
+        226   & 3 & \citet{Thompson2004c}  & stream & 45.61 S & Yes   &       \\
+        227   & 3 & \citet{Thompson2004c}  & stream & 44.97 S & Yes   &       \\
+        228   & 3 & \citet{Thompson2004c}  & stream & 44.95 S & Yes   &       \\
+        229   & 3 & \citet{Thompson2004c}  & stream & 44.96 S & Yes   &       \\
+        230   & 3 & \citet{Thompson2004c}  & stream & 45 S  & Yes   &       \\
+        231   & 3 & \citet{Thompson2004c}  & stream & 45.58 S & Yes   &       \\
+        232   & 3 & \citet{Thompson2004c}  & stream & 45.61 S & Yes   &       \\
+        233   & 3 & \citet{Thompson2004c}  & stream & 45.782 S & Yes   &       \\
+        234   & 3 & \citet{Thompson2004c}  & stream & 45.803 S & Yes   &       \\
+        235   & 3 & \citet{Thompson2004c}  & stream & 45.752 S & Yes   &       \\
+        236   & 3 & \citet{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
+        237   & 3 & \citet{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
+        238   & 3 & \citet{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
+        239   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+         \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        240   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        241   & 3 & \citet{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
+        242   & 3 & \citet{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
+        243   & 3 & \citet{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
+        244   & 3 & \citet{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
+        245   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        246   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        247   & 3 & \citet{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
+        248   & 3 & \citet{Thompson2004}  & estuary & 45,51,28 S & Yes   &        \\
+        249   & 3 & \citet{Angelini2005}  & stream & 24,30 S & Yes   &       \\
+        250   & 3 & \citet{Angelini2006}  & lake  & 22,57,38 S & Yes   &       \\
+        251   & 3 & \citet{Angelini2006}  & lake  & 22,57,38 S & Yes   &       \\
+        252   & 3 & \citet{Angelini2010}  & stream & 18,40 S & Yes   &       \\
+        253   & 3 & \citet{Angelini2011}  & marine & 5 - 17,15 S & Yes   &       \\
+        254   & 3 & \citet{Angelini2013}  & stream & 21 S  & Yes   &       \\
+        255   & 3 & \citet{Angelini2013}  & stream & 21 S  & Yes   &       \\
+        256   & 3 & \citet{Angelini2013}  & stream &       & No    & Could not locate original source \\
+        257   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        258   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        259   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        260   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        261   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        262   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        263   & 3 & \citet{Schneider1997}    & lake  & 45,58,50 N & Yes   &       \\
+        264   & 3 & \citet{Stagliano2002}    & terrestrial & 39,06,27 N & Yes   &       \\
+        265   & 3 & \citet{Lin2006}  & marine & 22,27 N & Yes   &       \\
+        266   & 3 & \citet{Cornejo-Donoso2008}  & marine & 60 - 69 S & Yes   &       \\
+        267   & 3 & \citet{Zetina-Rejon2003}  & marine & 23.15 - 22.9N & Yes   &       \\
+        268   & 3 & \citet{Cruz-Escalona2007}  & marine & 18,45 - 18,50 N & Yes   &       \\
+        269   & 3 & \citet{Liu2007}  & lake  & 29,32,35 N & Yes   &       \\
+         \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        270   & 3 & \citet{Filgueira2011}  & marine & 42,17,37 - 42,19,29 N & Yes   &       \\
+        271   & 3 & \citet{Amundsen2013}  & lake  & 69,07 N & Yes   &        \\
+        272   & 3 & \citet{Hampton2011}    & lake  & 48,03,29 N & Yes   &       \\
+        273   & 3 & \citet{Parker2006}  & stream & 69,1 N & Yes   &       \\
+        274   & 3 & \citet{Parker2006}  & stream & 69,1 N & Yes   &       \\
+        275   & 3 & \citet{Parker2006}  & stream & 69,1 N & Yes   &       \\
+        276   & 3 & \citet{Parker2006}  & stream & 69,1 N & Yes   &       \\
+        277   & 3 & \citet{Massana1996}  & lake  & 42,08,6 - 42,07 N & Yes   &       \\
+        278   & 3 & \citet{Stewart2011}    & lake  & 43.7 N & Yes   &       \\
+        279   & 3 & \citet{Stewart2011}    & lake  & 43.7 N & Yes   &       \\
+        280   & 3 & \citet{Cromar1996}  & stream & 43,58 N & Yes   &       \\
+        281   & 3 & \citet{Cromar1996}  & stream & 44,58 N & Yes   &       \\
+        282   & 3 & \citet{Cromar1996}  & stream & 45,58 N & Yes   &       \\
+        283   & 3 & \citet{Cromar1996}  & stream & 46,58 N & Yes   &       \\
+        284   & 3 & \citet{Cromar1996}  & stream & 47,58 N & Yes   &       \\
+        285   & 3 & \citet{Cromar1996}  & stream & 48,58 N & Yes   &       \\
+        286   & 3 & \citet{Cromar1996}  & stream & 49,58 N & Yes   &       \\
+        287   & 3 & \citet{Cromar1996}  & stream & 50,58 N & Yes   &       \\
+        288   & 3 & \citet{Christian1999}    & estuary & 30,05,39 N & Yes   &       \\
+        289   & 3 & \citet{Fetahi2011}  & lake  & 11,15 N & Yes   &       \\
+        290   & 3 & \citet{Brodeur1992}    & marine & 43 - 48 N & Yes   &       \\
+        291   & 3 & \citet{Brodeur1992}    & marine & 44 - 48 N & Yes   &       \\
+        292   & 3 & \citet{Brodeur1992}    & marine & 45 - 48 N & Yes   &       \\
+        293   & 3 & \citet{Brodeur1992}    & marine & 46 - 48 N & Yes   &       \\
+        294   & 3 & \citet{Gaedke1994}  & lake  & 47,37,30 N & Yes   &       \\
+        295   & 3 & \citet{Preston2012}    & lake  & 37.66 N & Yes   &        \\
+        296   & 3 & \citet{Ratsirarson1996}  & lake  & 24,55 S & Yes   &       \\
+        297   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        298   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        299   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        300   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        301   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        302   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        303   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+         \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        304   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        305   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        306   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        307   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        308   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        309   & 3 & \citet{Gontikaki2011}  & marine & 61,13,88 N & Yes   &       \\
+        310   & 3 & \citet{Khan2009}  & lake  & 12,45,25 N & Yes   &       \\
+        311   & 3 & \citet{Memmott2000}     & terrestrial &       & No    & Source web \\
+        312   & 3 & \citet{Kaiser-Bunbury2009}  & terrestrial &       & No    & Plant-pollinator web \\
+        313   & 3 & \citet{Kaiser-Bunbury2009}  & terrestrial &       & No    & Plant-pollinator web \\
+        314   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        315   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        316   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        317   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        318   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        319   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        320   & 3 & \citet{Ruzicka2012}    & marine & 42 - 49 N & Yes   &       \\
+        321   & 3 & \citet{Ruzicka2012}    & marine & 43 - 49 N & Yes   &       \\
+        322   & 3 & \citet{Ruzicka2012}    & marine & 44 - 49 N & Yes   &       \\
+        323   & 3 & \citet{Ruzicka2012}    & marine & 45 - 49 N & Yes   &       \\
+        324   & 3 & \citet{Ruzicka2012}    & marine & 46 - 49 N & Yes   &       \\
+        325   & 3 & \citet{Lewis2002}  & terrestrial &       & No    & Host-parasitoid web \\
+        326   & 3 & \citet{Lewis2002}  & terrestrial &       & No    & Host-parasitoid web \\
+        327   & 3 & \citet{Kelleway2010}  & stream & 29,13 S & Yes   &       \\
+        328   & 3 & \citet{Kelleway2010}  & stream & 29,20,0 S & Yes   &       \\
+        329   & 3 & \citet{Kelleway2010}  & stream & 29,35 S & Yes   &       \\
+        330   & 3 & \citet{Kelleway2010}  & stream & 29,13 S & Yes   &       \\
+        331   & 3 & \citet{Kelleway2010}  & stream & 29,20,0 S & Yes   &       \\
+        332   & 3 & \citet{Huang2008}  & stream & 31.70 N & Yes   &       \\
+        333   & 3 & \citet{Link2002}    & marine & 33,51 - 44,49 N & Yes   &       \\
+        334   & 3 & \citet{Alcorlo2001}  & lake  & 41,26,36 N & Yes   &       \\
+        335   & 3 & \citet{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
+        336   & 3 & \citet{Alcorlo2001}  & lake  & 41,26,36 N & Yes   &       \\
+        337   & 3 & \citet{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
+         \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        338   & 3 & \citet{Torres2013}  & marine &       & No    & Could not locate original source \\
+        339   & 3 & \citet{Bulman2001}  & marine & 37-39 S & Yes   &       \\
+        340   & 3 & \citet{Smith2007}  & marine & 74-78 S & Yes   &       \\
+        341   & 3 & \citet{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
+        342   & 3 & \citet{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes   &       \\
+        343   & 3 & \citet{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
+        344   & 3 & \citet{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
+        345   & 3 & \citet{Boit2012}  & lake  & 47,38,10 N & Yes   &       \\
+        346   & 3 & \citet{Rayner2010}  & stream & 17,7 S & Yes   &       \\
+        347   & 3 & \citet{Motta2005}  & stream & 23,03 S & Yes   &       \\
+        348   & 3 & \citet{Douglass2011}    & marine & 37,13 N & Yes   &       \\
+        349   & 3 & \citet{Douglass2011}    & marine & 37,13 N & Yes   &       \\
+        350   & 3 & \citet{Douglass2011}    & marine & 37,13 N & Yes   &       \\
+        351   & 3 & \citet{Warren1989}     & lake  &       & No    & Could not locate original source \\
+        352   & 3 & \citet{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
+        353   & 3 & \citet{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
+        354   & 3 & \citet{Goldwasser1993}  & terrestrial & 18,03 N & Yes   &       \\
+        355   & 3 & \citet{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
+        356   & 3 & \citet{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
+        357   & 3 & \citet{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
+        358   & 3 & \citet{Schroter2003}  & terrestrial &       & No    & Generalized scheme \\
+        359   & 3 & \citet{Baiser2012}  & lake  &       & No    & Study site unclear \\
+        \hline
+      \end{tabular}%
+        }
+    \end{table}%
+
+  \end{landscape}
+\newpage
+
+\subsection*{Appendix S2: Scaling Relationships with S}
 
@@
     multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
-    over another, we follow the recommendations in~\citet{Xiao2011} and compared the two
+    over another, we follow the recommendations in\citet{Xiao2011} and compared the two
     model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
@@
     species richness and vulnerability have not been explicitly examined (but see scaling 
-    relationships for the standard devaitions of each property in~\citet{Riede2010}), we expect that they will follow
+    relationships for the standard devaitions of each property in\citet{Riede2010}), we expect that they will follow
     power laws similar to that of the relationship between species richness and links per species.
@@
 
-\subsection*{Appendix S3: Supplemental Methods and Results - relationships with latitude}
+\subsection*{Appendix S3: Relationships with latitude}
 
@@
     marine, lake, and terrestrial networks with estuarine
-    networks providing the intercept) and $\epsilon_{i}$ a residual error term. 
+    networks providing the intercept) and $\epsilon_{i}$ is a residual error term. 
     We next calculated the AIC
@@
 For each relationship, we show observed values (white circles) and 
-a simplified form of the scaling relationship described in equation XX (\emph{Main Text}), neglecting 
-any effects of habitat type or latitude (black line, N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
+a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
+any effects of habitat type or latitude (black line, N=166 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
 observed values correcting for the effects of habitat type and latitude. }
@@
 line) with its 95\% confidence interval (in grey),
-based on N=163 empirical food webs. Latitude is 
+based on N=166 empirical food webs. Latitude is 
 given in degrees from the equator
@@
 types and over latitude. For each property we show the scaling exponent for the proportion of
-basal resources (black line) with its 95\% confidence interval (in grey), based on N=163 
+basal resources (black line) with its 95\% confidence interval (in grey), based on N=166 
 empirical food webs. Latitude is given in degrees
@@
 intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
-N=163 empirical food webs. Latitude is given in degrees
+N=166 empirical food webs. Latitude is given in degrees
 from the equator regardless of direction.}
@@
 types and over latitude. For each property we show the scaling exponent for the proportion of
-top predators (black line) with its 95\% confidence interval (in grey), based on N=163 
+top predators (black line) with its 95\% confidence interval (in grey), based on N=166 
 empirical food webs. Latitude is given in degrees

### 2015-07-01 manuscript/bigtable.tex
Bib files and the rough conversion of my giant table, as submitted July 1 to Proc R Soc

@@
     \midrule
-    Alamitos & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,12,25 N & Yes   &       &  \\
-    Alford & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,15,41.59 N & Yes   &       &  \\
-    Beaver & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,18,58.13 N & Yes   &       &  \\
-    Bere  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Woodward2008} & England & stream & 50,45,7 N & Yes   &       &  \\
-    Bridge & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,09,42.66 N & Yes   &       &  \\
-    Broad & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.896938 S & Yes   &       &  \\
-    Broadstone & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Woodward2005} & stream & stream & 51,01,05 N & Yes   &       &  \\
-    Calero & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,11,09 - 20 N & Yes   &       &  \\
-    Canton & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) &  \\
-    Carpinteria2006 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Lafferty2006} & USA   & estuary & 34.41 - 34.40 N & Yes   &       &  \\
-    Chub  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 43,31,39.36 N & Yes   &       &  \\
-    Coachella & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Polis1991a} & desert & terrestrial & 33,54 N & Yes   &       &  \\
-    Connery & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 44,18,42.10 N & Yes   &       &  \\
-    Corte & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,56,28 - 37,57,39 N & Yes   &       &  \\
-    Coyote & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       &  \\
-    German & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) &  \\
-    GrandeCl & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
-    GrandeSc & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
-    Guadalupe & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Harrison1995} & USA   & stream & 37,27,54 - 37,21,17 N & Yes   &       &  \\
-    Hainich   & ~\textbackslash{}citet{Riede2011} & Unpublished & Germany & terrestrial &       & No    & Could not locate original source &  \\
-    LittleKyeBurn & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) &  \\
-    LittleRock & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Martinez1991} & USA   & lake  & 45,44,07.94 N & Yes   &       &  \\
-    Mondego & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Patricio2006} & Portugal & estuary & 40,08 N & Yes   &       &  \\
-    Montane Forest, Arizona & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) &  \\
-    Reef  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Opitz1996} & Caribbean & marine & 18,29 - 17,53 N & Yes   &       &  \\
-    Sierra & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Brose2005} & USA   & lake  & 36,50 - 37,02 N & Yes   &       &  \\
-    SimberloffE1 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,37.29 N & Yes   &       &  \\
-    SimberloffE2 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,33 N & Yes   &       &  \\
-    SimberloffE3 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,41,23.82 N & Yes   &       &  \\
-    SimberloffE7 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 25,15 N & Yes   &       &  \\
-    SimberloffE9 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       &  \\
-    SimberloffST2 & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Simberloff1976} & Mangrove islands & terrestrial & 24,36,16 N & Yes   &       &  \\
-    Skipwith & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Warren1989} & England & lake  & 53,40 N & Yes   &       &  \\
-    Stink & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Havens1992} & USA   & lake  & 43,37,55.88 N & Yes   &       &  \\
-    StMarks & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Christian1999} & USA   & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) &  \\
-    Stony  & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Townsend1998} & New Zealand & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) &  \\
-    TreleaseWoods & ~\textbackslash{}citet{Riede2011} & \multicolumn{1}{l}{~\textbackslash{}citet{Twomey1945}} & USA   & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) &  \\
-    Tuesday & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Jonsson2005} & USA   & lake  & 46,13 N & Yes   &       &  \\
-    Weddell Sea & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Brose2005} & Antarctica & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) &  \\
-    Ythan & ~\textbackslash{}citet{Riede2011} & ~\textbackslash{}citet{Huxham1996} & UK    & marine &       & No    & Duplicated in Dunne (YthanDunne) &  \\
-    BahiaDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & Mexico & estuary & 30.43 - 30.46 N & Yes   &       & Parasites removed \\
-    CarpinteriaDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & USA   & estuary & 34.41 - 34.40 N & Yes   &       & Parasites removed \\
-    EsteroDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Hechinger2011} & Mexico & estuary & 31.78 - 31.69 N & Yes   &       & Parasites removed \\
-    FjordDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Zander2011} & Germany & estuary & 54.92 - 54.75 N & Yes   &       & Parasites removed \\
-    OtagoDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Mouritsen2011} & New Zealand & estuary & 45.78 - 45.88 S & Yes   &       & Parasites removed \\
-    SyltDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Thieltges2011} & Denmark & estuary & 54.83 - 55.12 N & Yes   &       & Parasites removed \\
-    YthanDunne & ~\textbackslash{}citet{Dunne2013} & ~\textbackslash{}citet{Huxham1996} & Scotland & estuary & 57,18,32 N & Yes   &       & Parasites removed \\
-    1     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Qazim1970}} & India & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
-    2     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Day1967}} & South Africa & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
-    3     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Woodwell1967}} & USA   & \multicolumn{1}{l}{estuary} & 41,03,11 N & Yes   &       &  \\
-    4     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Johnston1956}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Sink web &  \\
-    5     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Teal1962}} & USA   & \multicolumn{1}{l}{estuary} & 31,28,38 N & Yes   &       &  \\
-    6     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{MacGinitie1935}} & USA   & \multicolumn{1}{l}{estuary} & 36,48,18 N & Yes   &       &  \\
-    7     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kremer1978}} & USA   & \multicolumn{1}{l}{marine} & 41,45 - 41,30 N & Yes   &       &  \\
-    8     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Nixon1973}} & USA   & \multicolumn{1}{l}{estuary} & 41,33,00 N & Yes   &       &  \\
-    9     & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1967}} & Ireland & \multicolumn{1}{l}{stream} &       & No    & Could not locate original source &  \\
-    10    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
-    11    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
-    12    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
-    13    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
-    14    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
-    15    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
-    16    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Copeland1974}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
-    17    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hiatt1960}} & Marshall Islands - Pacific Ocean & \multicolumn{1}{l}{marine} & 4,30 - 15 N & No    & Generalized scheme &  \\
-    18    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Niering1963a}} & Polynesia & \multicolumn{1}{l}{terrestrial} & 1,01,29 - 1,06,23 N & Yes   &       &  \\
-    19    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brooks1963}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
-    20    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Knox1970}} & Antarctica & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
-    21    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Patten1979}} & Antarctica & \multicolumn{1}{l}{marine} & 70-85 S & Yes   &       &  \\
-    22    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Summerhayes1923}} & Norway & \multicolumn{1}{l}{terrestrial} & 74,27,54 N & Yes   &       &  \\
-    23    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
-    24    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
-    25    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
-    26    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
-    27    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Varley1970}} & England & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
-    28    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Paviour-Smith1956}} & New Zealand & \multicolumn{1}{l}{estuary} & 45,51,30 S & Yes   &       &  \\
-    29    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dunbar1953}} & Arctic seas & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
-    30    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mackintosh1964}} & Antarctica & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
-    31    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
-    32    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
-    33    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
-    34    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jones1949}} & UK    & \multicolumn{1}{l}{stream} & 51,41 - 51,55 N & Yes   &       &  \\
-    35    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Minshall1967}} & USA   & \multicolumn{1}{l}{stream} & 37,18,26 N & Yes   &       &  \\
-    36    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
-    37    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Clarke1967}} & USA   & \multicolumn{1}{l}{marine} & 41,02,49 N & Yes   &       &  \\
-    38    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
-    39    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
-    40    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Harrison1962}} & Malaysia & \multicolumn{1}{l}{terrestrial} &       & No    & Generalized scheme &  \\
-    41    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parin1970}} & Israel & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
-    42    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Vinogradov1978}} & Pacific Ocean & \multicolumn{1}{l}{marine} &       & No    & Study site unclear &  \\
-    43    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rosenthal1974}} & USA   & \multicolumn{1}{l}{marine} & 32,57 N & Yes   &       &  \\
-    44    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Yanez1978}} & Mexico & \multicolumn{1}{l}{marine} & 17,26,21 N & Yes   &       &  \\
-    45    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Tilly1968}} & USA   & \multicolumn{1}{l}{stream} & 41,22,55 N & Yes   &       &  \\
-    46    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Patten1975}} & USA   & \multicolumn{1}{l}{lake} & 33,54 N & Yes   &       &  \\
-    47    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Harris1980}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Study site unclear &  \\
-    48    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Simenstad1978}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Extinct species &  \\
-    49    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Simenstad1978}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Extinct species &  \\
-    50    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Nybakken1982}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
-    51    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & USA   & \multicolumn{1}{l}{marine} & 42,38,56 N & Yes   &       &  \\
-    52    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Paine1980a}} & USA   & \multicolumn{1}{l}{marine} & 58,27 N & Yes   &       &  \\
-    53    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Paine1980a}} & USA   & \multicolumn{1}{l}{marine} & 48,19 - 48,37 N & Yes   &       &  \\
-    54    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{Unpublished} & Barbados & \multicolumn{1}{l}{marine} &       & No    & Unpublished &  \\
-    55    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Milne1972}} & Scotland & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
-    56    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Milne1972}} & Scotland & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
-    57    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Yanez1978}} & Mexico & \multicolumn{1}{l}{marine} & 17,26,21 N & Yes   &       &  \\
-    58    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Russia & \multicolumn{1}{l}{lake} & 51,46 N & Yes   &       &  \\
-    59    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Twomey1945}} & USA   & \multicolumn{1}{l}{terrestrial} & 40,09,47 N & Yes   &       &  \\
-    60    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rasmussen1941}} & USA   & \multicolumn{1}{l}{terrestrial} & 36,5-37 N & Yes   &       &  \\
-    61    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Summerhayes1928}} & Norway & \multicolumn{1}{l}{terrestrial} & 77,52,30 N & Yes   &       &  \\
-    62    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Summerhayes1928}} & Norway & \multicolumn{1}{l}{terrestrial} & 77,52,30 N & Yes   &       &  \\
-    63    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jones1950}} & UK    & \multicolumn{1}{l}{stream} & 52,25,08 N & Yes   &       &  \\
-    64    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cummins1966}} & USA   & \multicolumn{1}{l}{stream} & 41,39,33 N & Yes   &       &  \\
-    65    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Tsuda1972}} & Japan & \multicolumn{1}{l}{stream} & 34,21,20 - 34,23,21 N & Yes   &       &  \\
-    66    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mann1972a}} & England & \multicolumn{1}{l}{stream} & 51,30 N & Yes   &       &  \\
-    67    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Carlson1968}} & USA   & \multicolumn{1}{l}{river} & 40,24,16 N & Yes   &       &  \\
-    68    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Morgan1972}} & Scotland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
-    69    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Portugal & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
-    70    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kemp1977}} & USA   & \multicolumn{1}{l}{estuary} & 28,54,08 N & Yes   &       &  \\
-    71    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Sorokin1972}} & Russia & \multicolumn{1}{l}{lake} & 48,00 N & Yes   &       &  \\
-    72    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baril1983}} & Canada & \multicolumn{1}{l}{lake} & 46,02 N & Yes   &       &  \\
-    73    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schiemer1979}} & Austria & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
-    74    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & South Africa & \multicolumn{1}{l}{marine} & 34,15,00 S & Yes   &       &  \\
-    75    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Pechlaner1972}} & Austria & \multicolumn{1}{l}{lake} & 47,11 N & Yes   &       &  \\
-    76    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schiemer1979}} & Austria & \multicolumn{1}{l}{lake} & 47,42 - 47,54 N & Yes   &       &  \\
-    77    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Ethiopia & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
-    78    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Burgis1972}} & Uganda & \multicolumn{1}{l}{lake} & 0     & Yes   &       &  \\
-    79    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Sarvala1974}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
-    80    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Sarvala1974}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
-    81    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hatanaka1977}} & Japan & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
-    82    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & France & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
-    83    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
-    84    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Wilbur1972}} & USA   & \multicolumn{1}{l}{lake} & 42,28,42 N & Yes   &       &  \\
-    85    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mizuno1982}} & Malaysia & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
-    86    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hogetsu1979}} & Japan & \multicolumn{1}{l}{marine} & 34,36 - 35,38 N & Yes   &       &  \\
-    87    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bradstreet1982}} & Canada & \multicolumn{1}{l}{terrestrial} & 72,46,34.95 N & Yes   &       &  \\
-    88    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kuusela1980}} & Finland & \multicolumn{1}{l}{stream} &       & No    & Could not locate original source &  \\
-    89    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hartley1948}} & England & \multicolumn{1}{l}{stream} & 52,13 N & Yes   &       &  \\
-    91    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Japan & terrestrial &       & No    & Could not locate original source &  \\
-    92    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Swan1961}} & Tibet & terrestrial &       & No    & Generalized scheme &  \\
-    93    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Pattie1966}} & USA   & terrestrial & 45 N  & Yes   &       &  \\
-    94    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brown1971}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    95    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brown1975}} & USA   & terrestrial & 70,11,14.18 N & Yes   &       &  \\
-    96    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Russia & terrestrial &       & No    & Could not locate original source &  \\
-    97    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & Russia & terrestrial &       & No    & Could not locate original source &  \\
-    98    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Holm1980}} & Namibia & terrestrial &       & No    & Could not locate original source &  \\
-    99    & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Howes1954}} & USA   & terrestrial & 32,36 N & Yes   &       &  \\
-    100   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & India & terrestrial &       & No    & Could not locate original source &  \\
-    101   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen1990}} & \multicolumn{1}{l}{France} & lake  &       & No    & Could not locate original source &  \\
-    102   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Shushkina1973}} & \multicolumn{1}{l}{Pacific Ocean} & marine & 10 S - 15 N & Yes   &       &  \\
-    103   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Petipa1979}} & \multicolumn{1}{l}{Pacific Ocean} & marine &       & No    & Generalized scheme &  \\
-    104   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Menge1976}} & \multicolumn{1}{l}{Panama} & marine & 4,48,04 N & Yes   &       &  \\
-    105   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Edwards1982}} & \multicolumn{1}{l}{USA} & marine & 42,40 N & Yes   &       &  \\
-    106   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Glynn1965}} & \multicolumn{1}{l}{USA} & marine &       & No    & Could not locate original source &  \\
-    107   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Peterson1979}} & \multicolumn{1}{l}{USA} & marine & 39,52,02 N & Yes   &       &  \\
-    108   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hewatt1937}} & \multicolumn{1}{l}{USA} & marine & 36,37 N & Yes   &       &  \\
-    109   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Castilla1981}} & \multicolumn{1}{l}{Chile} & marine &       & No    & Could not locate original source &  \\
-    110   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
-    111   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
-    112   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
-    113   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
-    114   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Marshall1982}} & \multicolumn{1}{l}{Zimbabwe} & lake  & 17,54,11.90 S & Yes   &       &  \\
-    115   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Koepcke1952}} & \multicolumn{1}{l}{Peru} & marine &       & No    & Could not locate original source &  \\
-    116   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hurlbert1972}} & \multicolumn{1}{l}{U.S.A.} & lake  & 35,09,19 S & Yes   &       &  \\
-    117   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Zaret1973}} & \multicolumn{1}{l}{Panama} & lake  & 9,11,31.50 N & Yes   &       &  \\
-    118   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bindloss1972}} & \multicolumn{1}{l}{UK} & lake  & 56,41,18.71 N & Yes   &       &  \\
-    119   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mann1972}} & \multicolumn{1}{l}{UK} & stream & 51,27 N & Yes   &       &  \\
-    120   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Moriarty1973}} & \multicolumn{1}{l}{Uganda} & lake  & 0,00,58 N & Yes   &       &  \\
-    121   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{VanEs1977}} & \multicolumn{1}{l}{Germany} & estuary & 53,20 - 53,15 N & Yes   &       &  \\
-    122   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Nixon1973}} & \multicolumn{1}{l}{USA} & estuary & 41,33,04 N & Yes   &       &  \\
-    123   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Harris1972}} & \multicolumn{1}{l}{USA} & terrestrial & 40,45,28 N & Yes   &       &  \\
-    124   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Collins1976}} & \multicolumn{1}{l}{USA} & stream & 44,34 N & Yes   &       &  \\
-    125   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Landry1977}} & \multicolumn{1}{l}{Unspecified} & marine &       & No    & Generalized scheme &  \\
-    126   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Larsson1978}} & \multicolumn{1}{l}{Norway} & lake  & 61,26,00 N & Yes   &       &  \\
-    127   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1979}} & \multicolumn{1}{l}{Malaysia} & lake  &       & No    & Could not locate original source &  \\
-    128   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1979}} & \multicolumn{1}{l}{Malaysia} & lake  &       & No    & Could not locate original source &  \\
-    129   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{Unpublished} & \multicolumn{1}{l}{Unspecified} & terrestrial &       & No    & Unpublished &  \\
-    130   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Odum1975}} & \multicolumn{1}{l}{USA} & estuary & 27,12 N & Yes   &       &  \\
-    131   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & \multicolumn{1}{l}{Malaysia} & lake  & 4,12,37 N & Yes   &       &  \\
-    132   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & \multicolumn{1}{l}{Malaysia} & lake  & 4,12,37 N & Yes   &       &  \\
-    133   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & \multicolumn{1}{l}{Sri Lanka} & lake  & 7,52,22 N & Yes   &       &  \\
-    134   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & \multicolumn{1}{l}{Madagascar} & lake  & 19 S  & Yes   &       &  \\
-    135   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1985}} & Seychelles & lake  & 4,40,46 S & Yes   &       &  \\
-    136   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bradshaw1983}} & USA   & lake  &       & No    & Could not locate original source &  \\
-    137   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Corker1984}} & Hong Kong & lake  & 22,14-22,17 N & Yes   &       &  \\
-    138   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1983}} & UK    & lake  &       & No    & Could not locate original source &  \\
-    139   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1983}} & Australia & lake  &       & No    & Could not locate original source &  \\
-    140   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Siefert1979}} & Venezuela & terrestrial & 10,21 N & Yes   &       &  \\
-    141   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Seifert1976}} & Costa Rica & terrestrial &       & No    & Competition network &  \\
-    142   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Seifert1976}} & Costa Rica & terrestrial &       & No    & Competition network &  \\
-    143   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Snow1958}} & USA   & lake  & 34,41,45 N & Yes   &       &  \\
-    144   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Snow1958}} & Germany & lake  &       & No    & Could not locate original source &  \\
-    145   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
-    146   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
-    147   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
-    148   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
-    149   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Force1974}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    150   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hopkins1984}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    151   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Richards1926}} & UK    & terrestrial & 51,20,04 N & Yes   &       &  \\
-    152   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Whittaker1984}} & USA   & terrestrial &       & No    & Source web &  \\
-    153   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mayse1978}} & USA   & terrestrial & 40,06,38 N & Yes   &       &  \\
-    154   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mayse1978}} & USA   & terrestrial & 39,56,41 N & Yes   &       &  \\
-    155   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1975}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    156   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    157   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    158   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    159   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    160   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    161   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    162   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    163   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    164   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    165   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    166   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    167   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
-    168   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    169   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    170   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    171   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    172   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    173   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    174   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    175   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    176   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    177   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    178   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
-    179   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Robinson1953}} & England & terrestrial &       & No    & Source web &  \\
-    180   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
-    181   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
-    182   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
-    183   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
-    184   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Beaver1972}} & UK    & terrestrial &       & No    & Could not locate original source &  \\
-    185   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Chapman1955}} & UK    & terrestrial &       & No    & Source web &  \\
-    186   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cornaby1974}} & Costa Rica & terrestrial &       & No    & Source web &  \\
-    187   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cornaby1974}} & Costa Rica & terrestrial &       & No    & Source web &  \\
-    188   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jiron1981}} & Costa Rica & terrestrial &       & No    & Source web &  \\
-    189   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    190   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    191   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    192   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    193   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    194   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    195   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schoenly1983a}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    196   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schoenly1983a}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
-    197   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Mohr1943}} & USA   & terrestrial &       & No    & Source web &  \\
-    198   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schoenly1983}} & Mexico & terrestrial &       & No    & Source web &  \\
-    199   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Valiela1969}} & USA   & terrestrial &       & No    & Source web &  \\
-    200   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Valiela1974}} & USA   & terrestrial &       & No    & Source web &  \\
-    201   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Valiela1974}} & USA   & terrestrial &       & No    & Source web &  \\
-    202   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Allan1982}} & USA   & stream & 38,50,21 N & Yes   &       &  \\
-    203   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Collins1976}} & USA   & stream & 44,24 N & Yes   &       &  \\
-    204   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fryer1959}} & Malawi & lake  & 11,36,39 S & Yes   &       & Used whole-lake web only \\
-    205   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hildrew1985}} & UK    & stream & 51,01,05 N & Yes   &       &  \\
-    206   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Jones1949}} & UK    & stream & 51,41 - 51,55 N & Yes   &       &  \\
-    207   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Koslucher1973}} & USA   & stream & 41,57 - 42,14 N & Yes   &       &  \\
-    208   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Minckley1963}} & USA   & stream & 37,56 N & Yes   &       &  \\
-    209   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Minshall1967}} & USA   & stream & 37,18,26 N & Yes   &       &  \\
-    210   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Percival1929}} & UK    & stream &       & No    & Generalized scheme &  \\
-    211   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ricker1935}} & Canada & stream &       & No    & Could not locate original source &  \\
-    212   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ricker1935}} & Canada & stream &       & No    & Could not locate original source &  \\
-    213   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Badcock1949}} & UK    & stream & 53 N  & Yes   &       &  \\
-    214   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2003}} & USA   & stream & 44,40,44 N & Yes   &       &  \\
-    215   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2003}} & USA   & stream & 40,40,52 N & Yes   &       &  \\
-    216   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2003}} & USA   & stream & 35,02,50 N & Yes   &       &  \\
-    217   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2003}} & USA   & stream & 35,03,50 N & Yes   &       &  \\
-    218   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.79 S & Yes   &       &  \\
-    219   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 44.64 S & Yes   &       &  \\
-    220   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
-    221   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
-    222   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
-    223   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
-    224   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
-    225   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
-    226   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.61 S & Yes   &       &  \\
-    227   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 44.97 S & Yes   &       &  \\
-    228   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 44.95 S & Yes   &       &  \\
-    229   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 44.96 S & Yes   &       &  \\
-    230   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45 S  & Yes   &       &  \\
-    231   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.58 S & Yes   &       &  \\
-    232   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.61 S & Yes   &       &  \\
-    233   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.782 S & Yes   &       &  \\
-    234   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.803 S & Yes   &       &  \\
-    235   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45.752 S & Yes   &       &  \\
-    236   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
-    237   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
-    238   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
-    239   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
-    240   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
-    241   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
-    242   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
-    243   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
-    244   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
-    245   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
-    246   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
-    247   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
-    248   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Thompson2004}} & New Zealand & estuary & 45,51,28 S & Yes   &       & Parasites removed \\
-    249   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2005}} & Brazil & stream & 24,30 S & Yes   &       &  \\
-    250   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2006}} & Brazil & lake  & 22,57,38 S & Yes   &       &  \\
-    251   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2006}} & Brazil & lake  & 22,57,38 S & Yes   &       &  \\
-    252   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2010}} & Brazil & stream & 18,40 S & Yes   &       &  \\
-    253   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2011}} & Angola & marine & 5 - 17,15 S & Yes   &       &  \\
-    254   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2013}} & Brazil & stream & 21 S  & Yes   &       &  \\
-    255   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2013}} & Brazil & stream & 21 S  & Yes   &       &  \\
-    256   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Angelini2013}} & Brazil & stream &       & No    & Could not locate original source &  \\
-    257   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
-    258   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
-    259   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
-    260   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
-    261   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
-    262   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
-    263   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schnieder1997}} & USA   & lake  & 45,58,50 N & Yes   &       &  \\
-    264   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Stagliano2002}} & USA   & terrestrial & 39,06,27 N & Yes   &       &  \\
-    265   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Lin2006}} & Taiwan & marine & 22,27 N & Yes   &       &  \\
-    266   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cornejo-Donoso2008}} & Antarctica & marine & 60 - 69 S & Yes   &       &  \\
-    267   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Zetina-Rejon2003}} & Mexico & marine & 23.15 - 22.9N & Yes   &       &  \\
-    268   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cruz-Escalona2007}} & Mexico & marine & 18,45 - 18,50 N & Yes   &       &  \\
-    269   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Liu2007}} & China & lake  & 29,32,35 N & Yes   &       &  \\
-    270   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Filguera2011}} & Spain & marine & 42,17,37 - 42,19,29 N & Yes   &       &  \\
-    271   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Amundsen2013}} & Norway & lake  & 69,07 N & Yes   &       & Parasites removed \\
-    272   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hampton2011}} & USA   & lake  & 48,03,29 N & Yes   &       &  \\
-    273   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
-    274   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
-    275   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
-    276   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
-    277   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Massana1996}} & Spain & lake  & 42,08,6 - 42,07 N & Yes   &       &  \\
-    278   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Stewart2011}} & USA   & lake  & 43.7 N & Yes   &       &  \\
-    279   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Stewart2011}} & USA   & lake  & 43.7 N & Yes   &       &  \\
-    280   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 43,58 N & Yes   &       &  \\
-    281   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 44,58 N & Yes   &       &  \\
-    282   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 45,58 N & Yes   &       &  \\
-    283   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 46,58 N & Yes   &       &  \\
-    284   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 47,58 N & Yes   &       &  \\
-    285   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 48,58 N & Yes   &       &  \\
-    286   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 49,58 N & Yes   &       &  \\
-    287   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cromar1996}} & Canada & stream & 50,58 N & Yes   &       &  \\
-    288   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Christian1999}} & USA   & estuary & 30,05,39 N & Yes   &       &  \\
-    289   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Fetahi2011}} & Ethiopia & lake  & 11,15 N & Yes   &       &  \\
-    290   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brodeur1992}} & USA   & marine & 43 - 48 N & Yes   &       &  \\
-    291   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brodeur1992}} & USA   & marine & 44 - 48 N & Yes   &       &  \\
-    292   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brodeur1992}} & USA   & marine & 45 - 48 N & Yes   &       &  \\
-    293   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Brodeur1992}} & USA   & marine & 46 - 48 N & Yes   &       &  \\
-    294   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Gaedke1994} & Europe & lake  & 47,37,30 N & Yes   &       &  \\
-    295   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Preston2012}} & USA   & lake  & 37.66 N & Yes   &       & Parasites removed \\
-    296   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ratsirarson1996}} & Madagascar & lake  & 24,55 S & Yes   &       &  \\
-    297   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    298   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    299   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    300   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    301   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    302   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    303   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    304   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    305   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    306   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    307   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    308   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
-    309   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Gontikaki2011}} & Atlantic Ocean & marine & 61,13,88 N & Yes   &       &  \\
-    310   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Khan2009}} & India & lake  & 12,45,25 N & Yes   &       &  \\
-    311   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Memmott2000}} & UK    & terrestrial &       & No    & Source web &  \\
-    312   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2009}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
-    313   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2009}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
-    314   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
-    315   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
-    316   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
-    317   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
-    318   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
-    319   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
-    320   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 42 - 49 N & Yes   &       &  \\
-    321   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 43 - 49 N & Yes   &       &  \\
-    322   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 44 - 49 N & Yes   &       &  \\
-    323   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 45 - 49 N & Yes   &       &  \\
-    324   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Ruzicka2012}} & USA   & marine & 46 - 49 N & Yes   &       &  \\
-    325   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Lewis2002}} & Belize & terrestrial &       & No    & Host-parasitoid web &  \\
-    326   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Lewis2002}} & Belize & terrestrial &       & No    & Host-parasitoid web &  \\
-    327   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,13 S & Yes   &       &  \\
-    328   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,20,0 S & Yes   &       &  \\
-    329   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,35 S & Yes   &       &  \\
-    330   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,13 S & Yes   &       &  \\
-    331   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kelleway2010}} & Australia & stream & 29,20,0 S & Yes   &       &  \\
-    332   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Huang2008}} & China & stream & 31.70 N & Yes   &       &  \\
-    333   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Link2002}} & USA   & marine & 33,51 - 44,49 N & Yes   &       &  \\
-    334   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Alcorlo2001}} & Spain & lake  & 41,26,36 N & Yes   &       &  \\
-    335   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Alcorlo2001}} & Spain & lake  & 41,26,05 N & Yes   &       &  \\
-    336   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Alcorlo2001}} & Spain & lake  & 41,26,36 N & Yes   &       &  \\
-    337   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Alcorlo2001}} & Spain & lake  & 41,26,05 N & Yes   &       &  \\
-    338   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Torres2013}} & South Atlantic & marine &       & No    & Could not locate original source &  \\
-    339   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Bulman2001}} & Australia & marine & 37-39 S & Yes   &       &  \\
-    340   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Smith2007}} & Antarctica & marine & 74-78 S & Yes   &       &  \\
-    341   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Lancraft1991}} & Antarctica & marine & 58,20.8 - 60,10.4 S & Yes   &       &  \\
-    342   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hopkins1993}} & Antarctica & marine & 57,00 - 60,45 S & Yes   &       &  \\
-    343   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Kitching1987}} & Australia & lake  & 28,12 S & Yes   &       &  \\
-    344   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Hodkinson2004}} & Norway & terrestrial &       & No    & Host-parasitoid web &  \\
-    345   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Boit2012}} & Europe & lake  & 47,38,10 N & Yes   &       &  \\
-    346   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Rayner2010}} & Australia & stream & 17,7 S & Yes   &       &  \\
-    347   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Motta2005}} & Brazil & stream & 23,03 S & Yes   &       &  \\
-    348   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
-    349   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
-    350   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
-    351   & ~\textbackslash{}citet{GlobalWeb} & ~\textbackslash{}citet{Warren1989} & UK    & lake  &       & No    & Could not locate original source &  \\
-    352   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Poepperl2003}} & Germany & stream & 54,06 N & No    & describes compartments, not species &  \\
-    353   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Poepperl2003}} & Germany & stream & 54,06 N & No    & describes compartments, not species &  \\
-    354   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Goldwasser1993}} & St. Martin & terrestrial & 18,03 N & Yes   &       &  \\
-    355   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen2003}} & USA   & lake  & 46,13 N & Yes   &       &  \\
-    356   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Cohen2003}} & USA   & lake  & 46,13 N & Yes   &       &  \\
-    357   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Yodzis1998}} & South Africa & marine & 34,21 - 16 S & No    & Study site unclear &  \\
-    358   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Schroter2003}} & Europe & terrestrial &       & No    & Generalized scheme &  \\
-    359   & ~\textbackslash{}citet{GlobalWeb} & \multicolumn{1}{l}{~\textbackslash{}citet{Baiser2012}} & North America & lake  &       & No    & Study site unclear &  \\
+    Alamitos & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,12,25 N & Yes   &       &  \\
+    Alford & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,15,41.59 N & Yes   &       &  \\
+    Beaver & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,18,58.13 N & Yes   &       &  \\
+    Bere  & ~\citet{Riede2011} & ~\citet{Woodward2008} & England & stream & 50,45,7 N & Yes   &       &  \\
+    Bridge & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,09,42.66 N & Yes   &       &  \\
+    Broad & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.896938 S & Yes   &       &  \\
+    Broadstone & ~\citet{Riede2011} & ~\citet{Woodward2005} & stream & stream & 51,01,05 N & Yes   &       &  \\
+    Calero & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,11,09 - 20 N & Yes   &       &  \\
+    Canton & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) &  \\
+    Carpinteria2006 & ~\citet{Riede2011} & ~\citet{Lafferty2006} & USA   & estuary & 34.41 - 34.40 N & Yes   &       &  \\
+    Chub  & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 43,31,39.36 N & Yes   &       &  \\
+    Coachella & ~\citet{Riede2011} & ~\citet{Polis1991a} & desert & terrestrial & 33,54 N & Yes   &       &  \\
+    Connery & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 44,18,42.10 N & Yes   &       &  \\
+    Corte & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,56,28 - 37,57,39 N & Yes   &       &  \\
+    Coyote & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       &  \\
+    German & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) &  \\
+    GrandeCl & ~\citet{Riede2011} & ~\citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
+    GrandeSc & ~\citet{Riede2011} & ~\citet{CattinBlandenier2004} & wetland & terrestrial & 46,47,09 N & Yes   &       &  \\
+    Guadalupe & ~\citet{Riede2011} & ~\citet{Harrison1995} & USA   & stream & 37,27,54 - 37,21,17 N & Yes   &       &  \\
+    Hainich   & ~\citet{Riede2011} & Unpublished & Germany & terrestrial &       & No    & Could not locate original source &  \\
+    LittleKyeBurn & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) &  \\
+    LittleRock & ~\citet{Riede2011} & ~\citet{Martinez1991} & USA   & lake  & 45,44,07.94 N & Yes   &       &  \\
+    Mondego & ~\citet{Riede2011} & ~\citet{Patricio2006} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+    Montane Forest, Arizona & ~\citet{Riede2011} & ~\citet{Rasmussen1941} & USA   & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) &  \\
+    Reef  & ~\citet{Riede2011} & ~\citet{Opitz1996} & Caribbean & marine & 18,29 - 17,53 N & Yes   &       &  \\
+    Sierra & ~\citet{Riede2011} & ~\citet{Brose2005} & USA   & lake  & 36,50 - 37,02 N & Yes   &       &  \\
+    SimberloffE1 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,37.29 N & Yes   &       &  \\
+    SimberloffE2 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,40,33 N & Yes   &       &  \\
+    SimberloffE3 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,41,23.82 N & Yes   &       &  \\
+    SimberloffE7 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 25,15 N & Yes   &       &  \\
+    SimberloffE9 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       &  \\
+    SimberloffST2 & ~\citet{Riede2011} & ~\citet{Simberloff1976} & Mangrove islands & terrestrial & 24,36,16 N & Yes   &       &  \\
+    Skipwith & ~\citet{Riede2011} & ~\citet{Warren1989} & England & lake  & 53,40 N & Yes   &       &  \\
+    Stink & ~\citet{Riede2011} & ~\citet{Havens1992} & USA   & lake  & 43,37,55.88 N & Yes   &       &  \\
+    StMarks & ~\citet{Riede2011} & ~\citet{Christian1999} & USA   & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) &  \\
+    Stony  & ~\citet{Riede2011} & ~\citet{Townsend1998} & New Zealand & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) &  \\
+    TreleaseWoods & ~\citet{Riede2011} & \multicolumn{1}{l}{~\citet{Twomey1945}} & USA   & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) &  \\
+    Tuesday & ~\citet{Riede2011} & ~\citet{Jonsson2005} & USA   & lake  & 46,13 N & Yes   &       &  \\
+    Weddell Sea & ~\citet{Riede2011} & ~\citet{Brose2005} & Antarctica & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) &  \\
+    Ythan & ~\citet{Riede2011} & ~\citet{Huxham1996} & UK    & marine &       & No    & Duplicated in Dunne (YthanDunne) &  \\
+    BahiaDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & Mexico & estuary & 30.43 - 30.46 N & Yes   &       & Parasites removed \\
+    CarpinteriaDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & USA   & estuary & 34.41 - 34.40 N & Yes   &       & Parasites removed \\
+    EsteroDunne & ~\citet{Dunne2013} & ~\citet{Hechinger2011} & Mexico & estuary & 31.78 - 31.69 N & Yes   &       & Parasites removed \\
+    FjordDunne & ~\citet{Dunne2013} & ~\citet{Zander2011} & Germany & estuary & 54.92 - 54.75 N & Yes   &       & Parasites removed \\
+    OtagoDunne & ~\citet{Dunne2013} & ~\citet{Mouritsen2011} & New Zealand & estuary & 45.78 - 45.88 S & Yes   &       & Parasites removed \\
+    SyltDunne & ~\citet{Dunne2013} & ~\citet{Thieltges2011} & Denmark & estuary & 54.83 - 55.12 N & Yes   &       & Parasites removed \\
+    YthanDunne & ~\citet{Dunne2013} & ~\citet{Huxham1996} & Scotland & estuary & 57,18,32 N & Yes   &       & Parasites removed \\
+    1     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Qazim1970}} & India & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
+    2     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Day1967}} & South Africa & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
+    3     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Woodwell1967}} & USA   & \multicolumn{1}{l}{estuary} & 41,03,11 N & Yes   &       &  \\
+    4     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Johnston1956}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Sink web &  \\
+    5     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Teal1962}} & USA   & \multicolumn{1}{l}{estuary} & 31,28,38 N & Yes   &       &  \\
+    6     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{MacGinitie1935}} & USA   & \multicolumn{1}{l}{estuary} & 36,48,18 N & Yes   &       &  \\
+    7     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kremer1978}} & USA   & \multicolumn{1}{l}{marine} & 41,45 - 41,30 N & Yes   &       &  \\
+    8     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Nixon1973}} & USA   & \multicolumn{1}{l}{estuary} & 41,33,00 N & Yes   &       &  \\
+    9     & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kitching1967}} & Ireland & \multicolumn{1}{l}{stream} &       & No    & Could not locate original source &  \\
+    10    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
+    11    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 41 - 47 N & Yes   &       &  \\
+    12    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
+    13    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & USA   & \multicolumn{1}{l}{marine} & 45,45 - 49 N & Yes   &       &  \\
+    14    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
+    15    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
+    16    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Copeland1974}} & USA   & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
+    17    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hiatt1960}} & Marshall Islands - Pacific Ocean & \multicolumn{1}{l}{marine} & 4,30 - 15 N & No    & Generalized scheme &  \\
+    18    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Niering1963a}} & Polynesia & \multicolumn{1}{l}{terrestrial} & 1,01,29 - 1,06,23 N & Yes   &       &  \\
+    19    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Brooks1963}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
+    20    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Knox1970}} & Antarctica & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
+    21    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Patten1979}} & Antarctica & \multicolumn{1}{l}{marine} & 70-85 S & Yes   &       &  \\
+    22    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Summerhayes1923}} & Norway & \multicolumn{1}{l}{terrestrial} & 74,27,54 N & Yes   &       &  \\
+    23    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
+    24    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
+    25    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
+    26    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bird1930}} & Canada & \multicolumn{1}{l}{terrestrial} & 50,25,17 N & Yes   &       &  \\
+    27    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Varley1970}} & England & \multicolumn{1}{l}{terrestrial} &       & No    & Could not locate original source &  \\
+    28    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Paviour-Smith1956}} & New Zealand & \multicolumn{1}{l}{estuary} & 45,51,30 S & Yes   &       &  \\
+    29    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Dunbar1953}} & Arctic seas & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
+    30    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Mackintosh1964}} & Antarctica & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
+    31    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
+    32    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Petipa1970}} & Black Sea & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
+    33    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
+    34    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Jones1949}} & UK    & \multicolumn{1}{l}{stream} & 51,41 - 51,55 N & Yes   &       &  \\
+    35    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Minshall1967}} & USA   & \multicolumn{1}{l}{stream} & 37,18,26 N & Yes   &       &  \\
+    36    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Walsh1967}} & Hawaii & \multicolumn{1}{l}{estuary} & 21,26,09 N & No    & Could not locate original source &  \\
+    37    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Clarke1967}} & USA   & \multicolumn{1}{l}{marine} & 41,02,49 N & Yes   &       &  \\
+    38    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
+    39    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Fryer1959}} & Malawi & \multicolumn{1}{l}{lake} & 11,36,39 S & Yes   &       &  \\
+    40    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Harrison1962}} & Malaysia & \multicolumn{1}{l}{terrestrial} &       & No    & Generalized scheme &  \\
+    41    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Parin1970}} & Israel & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
+    42    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Vinogradov1978}} & Pacific Ocean & \multicolumn{1}{l}{marine} &       & No    & Study site unclear &  \\
+    43    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Rosenthal1974}} & USA   & \multicolumn{1}{l}{marine} & 32,57 N & Yes   &       &  \\
+    44    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Yanez1978}} & Mexico & \multicolumn{1}{l}{marine} & 17,26,21 N & Yes   &       &  \\
+    45    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Tilly1968}} & USA   & \multicolumn{1}{l}{stream} & 41,22,55 N & Yes   &       &  \\
+    46    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Patten1975}} & USA   & \multicolumn{1}{l}{lake} & 33,54 N & Yes   &       &  \\
+    47    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Harris1980}} & USA   & \multicolumn{1}{l}{lake} &       & No    & Study site unclear &  \\
+    48    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Simenstad1978}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Extinct species &  \\
+    49    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Simenstad1978}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Extinct species &  \\
+    50    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Nybakken1982}} & USA   & \multicolumn{1}{l}{marine} &       & No    & Generalized scheme &  \\
+    51    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Dexter1947}} & USA   & \multicolumn{1}{l}{marine} & 42,38,56 N & Yes   &       &  \\
+    52    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Paine1980a}} & USA   & \multicolumn{1}{l}{marine} & 58,27 N & Yes   &       &  \\
+    53    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Paine1980a}} & USA   & \multicolumn{1}{l}{marine} & 48,19 - 48,37 N & Yes   &       &  \\
+    54    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{Unpublished} & Barbados & \multicolumn{1}{l}{marine} &       & No    & Unpublished &  \\
+    55    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Milne1972}} & Scotland & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
+    56    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Milne1972}} & Scotland & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
+    57    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Yanez1978}} & Mexico & \multicolumn{1}{l}{marine} & 17,26,21 N & Yes   &       &  \\
+    58    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & Russia & \multicolumn{1}{l}{lake} & 51,46 N & Yes   &       &  \\
+    59    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Twomey1945}} & USA   & \multicolumn{1}{l}{terrestrial} & 40,09,47 N & Yes   &       &  \\
+    60    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Rasmussen1941}} & USA   & \multicolumn{1}{l}{terrestrial} & 36,5-37 N & Yes   &       &  \\
+    61    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Summerhayes1928}} & Norway & \multicolumn{1}{l}{terrestrial} & 77,52,30 N & Yes   &       &  \\
+    62    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Summerhayes1928}} & Norway & \multicolumn{1}{l}{terrestrial} & 77,52,30 N & Yes   &       &  \\
+    63    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Jones1950}} & UK    & \multicolumn{1}{l}{stream} & 52,25,08 N & Yes   &       &  \\
+    64    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cummins1966}} & USA   & \multicolumn{1}{l}{stream} & 41,39,33 N & Yes   &       &  \\
+    65    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Tsuda1972}} & Japan & \multicolumn{1}{l}{stream} & 34,21,20 - 34,23,21 N & Yes   &       &  \\
+    66    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Mann1972a}} & England & \multicolumn{1}{l}{stream} & 51,30 N & Yes   &       &  \\
+    67    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Carlson1968}} & USA   & \multicolumn{1}{l}{river} & 40,24,16 N & Yes   &       &  \\
+    68    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Morgan1972}} & Scotland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
+    69    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & Portugal & \multicolumn{1}{l}{estuary} &       & No    & Could not locate original source &  \\
+    70    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kemp1977}} & USA   & \multicolumn{1}{l}{estuary} & 28,54,08 N & Yes   &       &  \\
+    71    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Sorokin1972}} & Russia & \multicolumn{1}{l}{lake} & 48,00 N & Yes   &       &  \\
+    72    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Baril1983}} & Canada & \multicolumn{1}{l}{lake} & 46,02 N & Yes   &       &  \\
+    73    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Schiemer1979}} & Austria & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
+    74    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & South Africa & \multicolumn{1}{l}{marine} & 34,15,00 S & Yes   &       &  \\
+    75    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Pechlaner1972}} & Austria & \multicolumn{1}{l}{lake} & 47,11 N & Yes   &       &  \\
+    76    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Schiemer1979}} & Austria & \multicolumn{1}{l}{lake} & 47,42 - 47,54 N & Yes   &       &  \\
+    77    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & Ethiopia & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
+    78    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Burgis1972}} & Uganda & \multicolumn{1}{l}{lake} & 0     & Yes   &       &  \\
+    79    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Sarvala1974}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
+    80    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Sarvala1974}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
+    81    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hatanaka1977}} & Japan & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
+    82    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & France & \multicolumn{1}{l}{marine} &       & No    & Could not locate original source &  \\
+    83    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & Finland & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
+    84    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Wilbur1972}} & USA   & \multicolumn{1}{l}{lake} & 42,28,42 N & Yes   &       &  \\
+    85    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Mizuno1982}} & Malaysia & \multicolumn{1}{l}{lake} &       & No    & Could not locate original source &  \\
+    86    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hogetsu1979}} & Japan & \multicolumn{1}{l}{marine} & 34,36 - 35,38 N & Yes   &       &  \\
+    87    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bradstreet1982}} & Canada & \multicolumn{1}{l}{terrestrial} & 72,46,34.95 N & Yes   &       &  \\
+    88    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kuusela1980}} & Finland & \multicolumn{1}{l}{stream} &       & No    & Could not locate original source &  \\
+    89    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hartley1948}} & England & \multicolumn{1}{l}{stream} & 52,13 N & Yes   &       &  \\
+    91    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & Japan & terrestrial &       & No    & Could not locate original source &  \\
+    92    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Swan1961}} & Tibet & terrestrial &       & No    & Generalized scheme &  \\
+    93    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Pattie1966}} & USA   & terrestrial & 45 N  & Yes   &       &  \\
+    94    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Brown1971}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    95    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Brown1975}} & USA   & terrestrial & 70,11,14.18 N & Yes   &       &  \\
+    96    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & Russia & terrestrial &       & No    & Could not locate original source &  \\
+    97    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & Russia & terrestrial &       & No    & Could not locate original source &  \\
+    98    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Holm1980}} & Namibia & terrestrial &       & No    & Could not locate original source &  \\
+    99    & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Howes1954}} & USA   & terrestrial & 32,36 N & Yes   &       &  \\
+    100   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & India & terrestrial &       & No    & Could not locate original source &  \\
+    101   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen1990}} & \multicolumn{1}{l}{France} & lake  &       & No    & Could not locate original source &  \\
+    102   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Shushkina1973}} & \multicolumn{1}{l}{Pacific Ocean} & marine & 10 S - 15 N & Yes   &       &  \\
+    103   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Petipa1979}} & \multicolumn{1}{l}{Pacific Ocean} & marine &       & No    & Generalized scheme &  \\
+    104   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Menge1976}} & \multicolumn{1}{l}{Panama} & marine & 4,48,04 N & Yes   &       &  \\
+    105   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Edwards1982}} & \multicolumn{1}{l}{USA} & marine & 42,40 N & Yes   &       &  \\
+    106   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Glynn1965}} & \multicolumn{1}{l}{USA} & marine &       & No    & Could not locate original source &  \\
+    107   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Peterson1979}} & \multicolumn{1}{l}{USA} & marine & 39,52,02 N & Yes   &       &  \\
+    108   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hewatt1937}} & \multicolumn{1}{l}{USA} & marine & 36,37 N & Yes   &       &  \\
+    109   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Castilla1981}} & \multicolumn{1}{l}{Chile} & marine &       & No    & Could not locate original source &  \\
+    110   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
+    111   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
+    112   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
+    113   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Dexter1947}} & \multicolumn{1}{l}{USA} & marine & 42,38,56 N & Yes   &       &  \\
+    114   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Marshall1982}} & \multicolumn{1}{l}{Zimbabwe} & lake  & 17,54,11.90 S & Yes   &       &  \\
+    115   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Koepcke1952}} & \multicolumn{1}{l}{Peru} & marine &       & No    & Could not locate original source &  \\
+    116   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hurlbert1972}} & \multicolumn{1}{l}{U.S.A.} & lake  & 35,09,19 S & Yes   &       &  \\
+    117   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Zaret1973}} & \multicolumn{1}{l}{Panama} & lake  & 9,11,31.50 N & Yes   &       &  \\
+    118   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bindloss1972}} & \multicolumn{1}{l}{UK} & lake  & 56,41,18.71 N & Yes   &       &  \\
+    119   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Mann1972}} & \multicolumn{1}{l}{UK} & stream & 51,27 N & Yes   &       &  \\
+    120   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Moriarty1973}} & \multicolumn{1}{l}{Uganda} & lake  & 0,00,58 N & Yes   &       &  \\
+    121   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{VanEs1977}} & \multicolumn{1}{l}{Germany} & estuary & 53,20 - 53,15 N & Yes   &       &  \\
+    122   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Nixon1973}} & \multicolumn{1}{l}{USA} & estuary & 41,33,04 N & Yes   &       &  \\
+    123   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Harris1972}} & \multicolumn{1}{l}{USA} & terrestrial & 40,45,28 N & Yes   &       &  \\
+    124   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Collins1976}} & \multicolumn{1}{l}{USA} & stream & 44,34 N & Yes   &       &  \\
+    125   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Landry1977}} & \multicolumn{1}{l}{Unspecified} & marine &       & No    & Generalized scheme &  \\
+    126   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Larsson1978}} & \multicolumn{1}{l}{Norway} & lake  & 61,26,00 N & Yes   &       &  \\
+    127   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Beaver1979}} & \multicolumn{1}{l}{Malaysia} & lake  &       & No    & Could not locate original source &  \\
+    128   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Beaver1979}} & \multicolumn{1}{l}{Malaysia} & lake  &       & No    & Could not locate original source &  \\
+    129   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{Unpublished} & \multicolumn{1}{l}{Unspecified} & terrestrial &       & No    & Unpublished &  \\
+    130   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Odum1975}} & \multicolumn{1}{l}{USA} & estuary & 27,12 N & Yes   &       &  \\
+    131   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Beaver1985}} & \multicolumn{1}{l}{Malaysia} & lake  & 4,12,37 N & Yes   &       &  \\
+    132   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Beaver1985}} & \multicolumn{1}{l}{Malaysia} & lake  & 4,12,37 N & Yes   &       &  \\
+    133   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Beaver1985}} & \multicolumn{1}{l}{Sri Lanka} & lake  & 7,52,22 N & Yes   &       &  \\
+    134   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Beaver1985}} & \multicolumn{1}{l}{Madagascar} & lake  & 19 S  & Yes   &       &  \\
+    135   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Beaver1985}} & Seychelles & lake  & 4,40,46 S & Yes   &       &  \\
+    136   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bradshaw1983}} & USA   & lake  &       & No    & Could not locate original source &  \\
+    137   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Corker1984}} & Hong Kong & lake  & 22,14-22,17 N & Yes   &       &  \\
+    138   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kitching1983}} & UK    & lake  &       & No    & Could not locate original source &  \\
+    139   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kitching1983}} & Australia & lake  &       & No    & Could not locate original source &  \\
+    140   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Siefert1979}} & Venezuela & terrestrial & 10,21 N & Yes   &       &  \\
+    141   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Seifert1976}} & Costa Rica & terrestrial &       & No    & Competition network &  \\
+    142   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Seifert1976}} & Costa Rica & terrestrial &       & No    & Competition network &  \\
+    143   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Snow1958}} & USA   & lake  & 34,41,45 N & Yes   &       &  \\
+    144   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Snow1958}} & Germany & lake  &       & No    & Could not locate original source &  \\
+    145   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
+    146   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
+    147   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
+    148   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Rejmanek1979}} & Europe & terrestrial &       & No    & Host-parasitoid web &  \\
+    149   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Force1974}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    150   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hopkins1984}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    151   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Richards1926}} & UK    & terrestrial & 51,20,04 N & Yes   &       &  \\
+    152   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Whittaker1984}} & USA   & terrestrial &       & No    & Source web &  \\
+    153   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Mayse1978}} & USA   & terrestrial & 40,06,38 N & Yes   &       &  \\
+    154   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Mayse1978}} & USA   & terrestrial & 39,56,41 N & Yes   &       &  \\
+    155   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1975}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    156   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    157   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    158   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    159   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    160   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    161   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    162   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    163   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    164   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    165   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    166   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    167   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Askew1961}} & UK    & terrestrial &       & No    & Host-parasitoid web &  \\
+    168   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    169   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    170   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    171   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    172   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    173   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    174   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    175   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    176   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    177   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    178   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hawkins1984}} & USA   & terrestrial &       & No    & Host-parasitoid web &  \\
+    179   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Robinson1953}} & England & terrestrial &       & No    & Source web &  \\
+    180   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
+    181   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
+    182   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
+    183   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Savely1939}} & USA   & terrestrial & 36,01,02 N & Yes   &       &  \\
+    184   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Beaver1972}} & UK    & terrestrial &       & No    & Could not locate original source &  \\
+    185   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Chapman1955}} & UK    & terrestrial &       & No    & Source web &  \\
+    186   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cornaby1974}} & Costa Rica & terrestrial &       & No    & Source web &  \\
+    187   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cornaby1974}} & Costa Rica & terrestrial &       & No    & Source web &  \\
+    188   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Jiron1981}} & Costa Rica & terrestrial &       & No    & Source web &  \\
+    189   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    190   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    191   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    192   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    193   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    194   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{McKinnerney1978}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    195   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Schoenly1983a}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    196   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Schoenly1983a}} & USA   & terrestrial &       & No    & Could not locate original source &  \\
+    197   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Mohr1943}} & USA   & terrestrial &       & No    & Source web &  \\
+    198   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Schoenly1983}} & Mexico & terrestrial &       & No    & Source web &  \\
+    199   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Valiela1969}} & USA   & terrestrial &       & No    & Source web &  \\
+    200   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Valiela1974}} & USA   & terrestrial &       & No    & Source web &  \\
+    201   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Valiela1974}} & USA   & terrestrial &       & No    & Source web &  \\
+    202   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Allan1982}} & USA   & stream & 38,50,21 N & Yes   &       &  \\
+    203   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Collins1976}} & USA   & stream & 44,24 N & Yes   &       &  \\
+    204   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Fryer1959}} & Malawi & lake  & 11,36,39 S & Yes   &       & Used whole-lake web only \\
+    205   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hildrew1985}} & UK    & stream & 51,01,05 N & Yes   &       &  \\
+    206   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Jones1949}} & UK    & stream & 51,41 - 51,55 N & Yes   &       &  \\
+    207   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Koslucher1973}} & USA   & stream & 41,57 - 42,14 N & Yes   &       &  \\
+    208   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Minckley1963}} & USA   & stream & 37,56 N & Yes   &       &  \\
+    209   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Minshall1967}} & USA   & stream & 37,18,26 N & Yes   &       &  \\
+    210   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Percival1929}} & UK    & stream &       & No    & Generalized scheme &  \\
+    211   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Ricker1935}} & Canada & stream &       & No    & Could not locate original source &  \\
+    212   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Ricker1935}} & Canada & stream &       & No    & Could not locate original source &  \\
+    213   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Badcock1949}} & UK    & stream & 53 N  & Yes   &       &  \\
+    214   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2003}} & USA   & stream & 44,40,44 N & Yes   &       &  \\
+    215   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2003}} & USA   & stream & 40,40,52 N & Yes   &       &  \\
+    216   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2003}} & USA   & stream & 35,02,50 N & Yes   &       &  \\
+    217   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2003}} & USA   & stream & 35,03,50 N & Yes   &       &  \\
+    218   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45.79 S & Yes   &       &  \\
+    219   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 44.64 S & Yes   &       &  \\
+    220   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
+    221   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
+    222   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
+    223   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+    224   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+    225   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
+    226   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45.61 S & Yes   &       &  \\
+    227   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 44.97 S & Yes   &       &  \\
+    228   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 44.95 S & Yes   &       &  \\
+    229   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 44.96 S & Yes   &       &  \\
+    230   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45 S  & Yes   &       &  \\
+    231   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45.58 S & Yes   &       &  \\
+    232   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45.61 S & Yes   &       &  \\
+    233   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45.782 S & Yes   &       &  \\
+    234   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45.803 S & Yes   &       &  \\
+    235   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45.752 S & Yes   &       &  \\
+    236   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
+    237   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
+    238   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
+    239   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+    240   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+    241   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
+    242   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.29 S & Yes   &       &  \\
+    243   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.41 S & Yes   &       &  \\
+    244   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 45,57,0 S & Yes   &       &  \\
+    245   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+    246   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.08 S & Yes   &       &  \\
+    247   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004c}} & New Zealand & stream & 46.115 S & Yes   &       &  \\
+    248   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Thompson2004}} & New Zealand & estuary & 45,51,28 S & Yes   &       & Parasites removed \\
+    249   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Angelini2005}} & Brazil & stream & 24,30 S & Yes   &       &  \\
+    250   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Angelini2006}} & Brazil & lake  & 22,57,38 S & Yes   &       &  \\
+    251   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Angelini2006}} & Brazil & lake  & 22,57,38 S & Yes   &       &  \\
+    252   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Angelini2010}} & Brazil & stream & 18,40 S & Yes   &       &  \\
+    253   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Angelini2011}} & Angola & marine & 5 - 17,15 S & Yes   &       &  \\
+    254   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Angelini2013}} & Brazil & stream & 21 S  & Yes   &       &  \\
+    255   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Angelini2013}} & Brazil & stream & 21 S  & Yes   &       &  \\
+    256   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Angelini2013}} & Brazil & stream &       & No    & Could not locate original source &  \\
+    257   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+    258   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+    259   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+    260   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+    261   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+    262   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Baeta2011}} & Portugal & estuary & 40,08 N & Yes   &       &  \\
+    263   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Schnieder1997}} & USA   & lake  & 45,58,50 N & Yes   &       &  \\
+    264   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Stagliano2002}} & USA   & terrestrial & 39,06,27 N & Yes   &       &  \\
+    265   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Lin2006}} & Taiwan & marine & 22,27 N & Yes   &       &  \\
+    266   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cornejo-Donoso2008}} & Antarctica & marine & 60 - 69 S & Yes   &       &  \\
+    267   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Zetina-Rejon2003}} & Mexico & marine & 23.15 - 22.9N & Yes   &       &  \\
+    268   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cruz-Escalona2007}} & Mexico & marine & 18,45 - 18,50 N & Yes   &       &  \\
+    269   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Liu2007}} & China & lake  & 29,32,35 N & Yes   &       &  \\
+    270   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Filguera2011}} & Spain & marine & 42,17,37 - 42,19,29 N & Yes   &       &  \\
+    271   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Amundsen2013}} & Norway & lake  & 69,07 N & Yes   &       & Parasites removed \\
+    272   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hampton2011}} & USA   & lake  & 48,03,29 N & Yes   &       &  \\
+    273   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
+    274   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
+    275   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
+    276   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Parker2006}} & Alaska & stream & 69,1 N & Yes   &       &  \\
+    277   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Massana1996}} & Spain & lake  & 42,08,6 - 42,07 N & Yes   &       &  \\
+    278   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Stewart2011}} & USA   & lake  & 43.7 N & Yes   &       &  \\
+    279   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Stewart2011}} & USA   & lake  & 43.7 N & Yes   &       &  \\
+    280   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cromar1996}} & Canada & stream & 43,58 N & Yes   &       &  \\
+    281   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cromar1996}} & Canada & stream & 44,58 N & Yes   &       &  \\
+    282   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cromar1996}} & Canada & stream & 45,58 N & Yes   &       &  \\
+    283   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cromar1996}} & Canada & stream & 46,58 N & Yes   &       &  \\
+    284   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cromar1996}} & Canada & stream & 47,58 N & Yes   &       &  \\
+    285   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cromar1996}} & Canada & stream & 48,58 N & Yes   &       &  \\
+    286   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cromar1996}} & Canada & stream & 49,58 N & Yes   &       &  \\
+    287   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cromar1996}} & Canada & stream & 50,58 N & Yes   &       &  \\
+    288   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Christian1999}} & USA   & estuary & 30,05,39 N & Yes   &       &  \\
+    289   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Fetahi2011}} & Ethiopia & lake  & 11,15 N & Yes   &       &  \\
+    290   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Brodeur1992}} & USA   & marine & 43 - 48 N & Yes   &       &  \\
+    291   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Brodeur1992}} & USA   & marine & 44 - 48 N & Yes   &       &  \\
+    292   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Brodeur1992}} & USA   & marine & 45 - 48 N & Yes   &       &  \\
+    293   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Brodeur1992}} & USA   & marine & 46 - 48 N & Yes   &       &  \\
+    294   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Gaedke1994} & Europe & lake  & 47,37,30 N & Yes   &       &  \\
+    295   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Preston2012}} & USA   & lake  & 37.66 N & Yes   &       & Parasites removed \\
+    296   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Ratsirarson1996}} & Madagascar & lake  & 24,55 S & Yes   &       &  \\
+    297   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    298   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    299   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    300   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    301   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    302   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    303   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    304   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    305   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    306   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    307   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    308   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Closs1994}} & Australia & stream & 37,40 S & Yes   &       &  \\
+    309   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Gontikaki2011}} & Atlantic Ocean & marine & 61,13,88 N & Yes   &       &  \\
+    310   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Khan2009}} & India & lake  & 12,45,25 N & Yes   &       &  \\
+    311   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Memmott2000}} & UK    & terrestrial &       & No    & Source web &  \\
+    312   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kaiser-Bunbury2009}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+    313   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kaiser-Bunbury2009}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+    314   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+    315   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+    316   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+    317   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+    318   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+    319   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kaiser-Bunbury2011}} & Mauritius & terrestrial &       & No    & Plant-pollinator web &  \\
+    320   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Ruzicka2012}} & USA   & marine & 42 - 49 N & Yes   &       &  \\
+    321   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Ruzicka2012}} & USA   & marine & 43 - 49 N & Yes   &       &  \\
+    322   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Ruzicka2012}} & USA   & marine & 44 - 49 N & Yes   &       &  \\
+    323   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Ruzicka2012}} & USA   & marine & 45 - 49 N & Yes   &       &  \\
+    324   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Ruzicka2012}} & USA   & marine & 46 - 49 N & Yes   &       &  \\
+    325   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Lewis2002}} & Belize & terrestrial &       & No    & Host-parasitoid web &  \\
+    326   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Lewis2002}} & Belize & terrestrial &       & No    & Host-parasitoid web &  \\
+    327   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kelleway2010}} & Australia & stream & 29,13 S & Yes   &       &  \\
+    328   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kelleway2010}} & Australia & stream & 29,20,0 S & Yes   &       &  \\
+    329   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kelleway2010}} & Australia & stream & 29,35 S & Yes   &       &  \\
+    330   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kelleway2010}} & Australia & stream & 29,13 S & Yes   &       &  \\
+    331   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kelleway2010}} & Australia & stream & 29,20,0 S & Yes   &       &  \\
+    332   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Huang2008}} & China & stream & 31.70 N & Yes   &       &  \\
+    333   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Link2002}} & USA   & marine & 33,51 - 44,49 N & Yes   &       &  \\
+    334   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Alcorlo2001}} & Spain & lake  & 41,26,36 N & Yes   &       &  \\
+    335   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Alcorlo2001}} & Spain & lake  & 41,26,05 N & Yes   &       &  \\
+    336   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Alcorlo2001}} & Spain & lake  & 41,26,36 N & Yes   &       &  \\
+    337   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Alcorlo2001}} & Spain & lake  & 41,26,05 N & Yes   &       &  \\
+    338   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Torres2013}} & South Atlantic & marine &       & No    & Could not locate original source &  \\
+    339   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Bulman2001}} & Australia & marine & 37-39 S & Yes   &       &  \\
+    340   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Smith2007}} & Antarctica & marine & 74-78 S & Yes   &       &  \\
+    341   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Lancraft1991}} & Antarctica & marine & 58,20.8 - 60,10.4 S & Yes   &       &  \\
+    342   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hopkins1993}} & Antarctica & marine & 57,00 - 60,45 S & Yes   &       &  \\
+    343   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Kitching1987}} & Australia & lake  & 28,12 S & Yes   &       &  \\
+    344   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Hodkinson2004}} & Norway & terrestrial &       & No    & Host-parasitoid web &  \\
+    345   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Boit2012}} & Europe & lake  & 47,38,10 N & Yes   &       &  \\
+    346   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Rayner2010}} & Australia & stream & 17,7 S & Yes   &       &  \\
+    347   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Motta2005}} & Brazil & stream & 23,03 S & Yes   &       &  \\
+    348   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
+    349   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
+    350   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Douglass2011}} & USA   & marine & 37,13 N & Yes   &       &  \\
+    351   & ~\citet{GlobalWeb} & ~\citet{Warren1989} & UK    & lake  &       & No    & Could not locate original source &  \\
+    352   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Poepperl2003}} & Germany & stream & 54,06 N & No    & describes compartments, not species &  \\
+    353   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Poepperl2003}} & Germany & stream & 54,06 N & No    & describes compartments, not species &  \\
+    354   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Goldwasser1993}} & St. Martin & terrestrial & 18,03 N & Yes   &       &  \\
+    355   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen2003}} & USA   & lake  & 46,13 N & Yes   &       &  \\
+    356   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Cohen2003}} & USA   & lake  & 46,13 N & Yes   &       &  \\
+    357   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Yodzis1998}} & South Africa & marine & 34,21 - 16 S & No    & Study site unclear &  \\
+    358   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Schroter2003}} & Europe & terrestrial &       & No    & Generalized scheme &  \\
+    359   & ~\citet{GlobalWeb} & \multicolumn{1}{l}{~\citet{Baiser2012}} & North America & lake  &       & No    & Study site unclear &  \\
     \bottomrule
     \end{tabular}%
-  \label{tab:addlabel}%
 \end{table}%

### 2015-07-01 manuscript/latitudepaper.tex
and maybe a short acknowledgements section would be nice
just to be safe, add the current NSERC
mislabelled sections. urgh.
Reviewers like line numbers
Added data accessibility section after getting bounced

@@
 \end{spacing}
+
+\linenumbers
 
@@
 
+\section*{Data Accessibility}
+
+  Food webs used in this study were retrieved from the University of Canberra's 
+  GlobalWeb database (\citealp{GlobalWeb}; \emph{www.globalwebdb.com}) and from
+  two papers (\citealp{Riede2011}; \emph{http://dx.doi.org/10.1111/j.1461-0248.2010.01568.x}
+  and \citealp{Dunne2013}; \emph{http://dx.doi.org/10.1371/journal.pbio.1001579}). Original sources for the
+  food webs are given in \emph{Appendix S1}.
+
+\section*{Acknowledgements}
+
+  We thank members of the Romanuk, Stouffer, and Tylianakis labs for their comments on
+  the manuscript.
+  This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
+  graduate scholarship (to ARC).
+
 \newpage
@@
 
-\section*{Figures}
+\section*{Figure Captions}
+
 \begin{figure}[h]
@@
 
-\begin{figure}[!H]
+\begin{figure}[h]
 % \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}

### 2015-08-15 manuscript/AC-reply-to-referees.tex
Broke apart replies. AE is a grump about exploratory analyses

\documentclass[12pt]{letter}

\usepackage[britdate]{canterbury-letter}
% \usepackage[britdate,alyssa-signature]{canterbury-letter}
\usepackage{times}
\usepackage{letterbib}
\usepackage{geometry}
\usepackage[round]{natbib}
\usepackage{graphicx}
\geometry{a4paper}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage[running]{lineno}
\usepackage{amsmath,amsfonts,amssymb}
% \usepackage[margin=10pt,font=small,labelfont=bf]{caption}

%\usepackage{natbib}
% \bibpunct[; ]{(}{)}{;}{a}{,}{;}

\newenvironment{refquote}{\bigskip \begin{it}}{\end{it}\smallskip}

\newenvironment{figure}{}

\position{PhD Candidate}
\department{School of Biological Sciences}
\location{Private Bag 4800}
\telephone{+64 3 364 2729}
\fax{+64 3 364 2590}
\email{alyssa.cirtwill@pg.canterbury.ac.nz}
\url{http://stoufferlab.org}
\name{Alyssa R. Cirtwill}

% \position{PhD student}
% \department{School of Biological Sciences}
% \location{Private Bag 4800}
% \telephone{+64 3 364 2729}
% \fax{+64 3 364 2590}
% \email{alyssa.cirtwill@pg.canterbury.ac.nz}
% \url{http://stoufferlab.org}
% \name{Ms. Alyssa R. Cirtwill}

\newcommand{\mytitle}{\emph{Specialisation in food webs scales with species richness but not with latitude}}
\newcommand{\myjournal}{\emph{Proceedings of the Royal Society B}}

\begin{document}

\begin{letter}{\bf Dr. Daniel Costa\\
               Editor\\
               Proceedings of the Royal Society B\\
               6-9 Carlton House Terrace\\
               London, UK\\
               SW1Y 5AG\\
                }

\opening{Dear Dr. Costa:}

We have now finished the revisions for the resubmission of our manuscript
``\mytitle'' for consideration in the Population and Community Ecology section
of the \myjournal.

In your original decision, you encouraged us to resubmit a revised version of
the manuscript noting that, while the Reviewers were quite positive, they and
the Associate Editor had a few substantial concerns. We appreciate the
comments by the Associate Editor and the Referees, and have taken care to
address each one while keeping within the size limits set by \myjournal. We
feel that the revised manuscript is both stronger and more accessible, and
hope that it will please the Editors.

Thank you again for your consideration of our revised manuscript.

% \closing{Regards,}

\end{letter}

\newpage

\setcounter{page}{1}

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Associate Editor}
% ---------------------------------------

  The Associate Editor stated that both Referees found our study ``very
  interesting'', but echoed and added to their concerns. In particular, the
  Associate Editor requested a demonstration that our results are not
  ``artefacts of differences in sampling effort between studies''. To address
  this, we have taken the Associate Editor's advice and performed the extra
  analyses suggested by Referee 1 (described in detail below). We have also
  taken the Associate Editor's specific comments to heart and address each one
  in turn. We hope that our replies (preceded by \textbf{R:} [[do something
  good]].

  1) Title doesn't reflect our trends in freshwater communities.

  \begin{refquote}

    Title: the current title seems to suggest that this scaling with latitude
    did never happen, while it was present in freshwater food webs.

  \end{refquote}

  \textbf{R:} We had originally intended to emphasize that, contrary to our expectations,
  scaling relationships did not vary over latitude in most ecosystems. We have amended our
  title to ``[[newtitle]]'' in order to better capture the scaling that did occur in streams.

  2) L29, L42: suggest the likely directions of effects.

  \begin{refquote}

    L29. To help the reader, please be explicit about the direction of these ‘direct relationships’.

    \smallskip

    L42. Can you make a directional prediction on how latitude is expected to
    affect the scaling? Otherwise, the study becomes rather exploratory
    presenting some phenomenological patterns not grounded in theory that need
    ad hoc explanations in the discussion. Similarly, can you provide a priori
    motivations why the relationship may differ among ecosystem types?

  \end{refquote}

  \textbf{R:} Well, this was an exploratory study. I think that's fine. We explored, we discovered, Science! And I looked at differences between ecosystem types because they're usually different ... so there. I should probably lie about it though.

  I guess scaling of species richness with latitude might be different in different food webs, maybe I can cite that?
  Clearly we didn't develop the crossover between the latitude-specialization and latitude-species trends :(

  Line 29:

  \begin{quotation}

  If the latitude-niche breadth hypothesis is correct, there should also be
  direct relationships between latitude and the degree of specialisation
  (i.e., the breadth of the Eltonian niche; Elton, 1927) of species within
  food webs. Specifically, narrower niches in the tropics would equate to
  greater specialisation (narrower niches) while constant niche sizes but
  greater productivity would translate to constant specialisation and niche
  width across latitude.

  \end{quotation}

  \begin{quotation}

  \end{quotation}

  3) L98-99: explain our model-selection procedure in more detail.

  \begin{refquote}

    L98-99. According to some experts (e.g. the landmark 2002 book by Burnham
    and Anderson) when models differ less than 2 units in AIC, they have the
    same support and fit. On what theoretical grounds do you motivate the
    choice to select the model with the lowest AIC as the best-fit model when
    models have $\delta$AIC\textless2? To what extent does this choice affect your
    conclusions?

  \end{refquote}

  \textbf{R:} We are also aware of this research. This is why we in fact
  considered all models with $\delta$AIC\textless2   as described in lines
  97-98. Where possible, we chose the model from that array with the fewest
  degrees of freedom. We only differentiated between models with very similar
  AICs when there were several models with the same degrees of freedom. In general
  these models differed only in which ecosystem types were included for intercept
  effects (including the different slopes in lake and stream ecosystems had larger
  effects) [[Maybe give him a list of the top models?]]. As we were only interested
  in changes in the slope of the scaling relationship with latitude, the slight changes
  in the intercepts would not change our conclusions at all.

  4) Move by-trophic-level analyses to appendix and/or better-explain our motivations.

  \begin{refquote}

    L100-106. After reading the introduction, it is not clear why you ‘were
    also interested’ in this topic. I suggest following the advice of reviewer
    2 and moving this part and the associated results to the appendix. Please
    also then explain why this is a priori interesting and relevant to
    investigate in the context of your study.

  \end{refquote}

  \textbf{R:} We thought that breaking down the food webs into trophic levels would
  provide an extra dimension of detail for this analysis. If scaling relationships
  had varied strongly with latitude for one trophic level and not another, that also
  would have guided our thoughts about potential mechanisms. We are happy to remove this
  analysis to the appendix, but I don't feel like justifying why everything has to be
  have a priori expectations and mechanisms. It's all post-hoc bullshitting anyway.

  5) L113: is there any covariance in the network properties?

  \begin{refquote}

    L113. To what extent do the property estimates covary with each other?
    This may be presented in an appendix.

  \end{refquote}

  6) L116: missing supporting statistics

  \begin{refquote}

    L116. It seems the stats to support this statement are missing.

  \end{refquote}

  7) L187-198: provide citations for an absence of prey-switching in communities other than streams.

  \begin{refquote}

    L187-198. For your explanation why the scaling relationship changes with
    latitude in lake and stream food webs and not in the other ecosystem types
    to be convincing it is not enough to cite studies that high-latitude
    aquatic species tend to switch between different seasonally available
    prey, you also need to provide evidence from the literature that this is
    not the case in the other ecosystem types.

  \end{refquote}

  8) Ensure layout (especially citations) matches journal specifications.

  \begin{refquote}

    Please strictly follow the author guidelines with regard to layout (for
    example how to cite studies in the text).

  \end{refquote}

  \newpage

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Reviewer 1}
% ---------------------------------------

  Polite pre-amble.

  ``This is an interesting paper that takes advantage of recent compilations
  of food webs to test basic theory with respect to latitudinal gradients in
  niche breadth. The paper is exceptionally well written and presented, and this
  is a credit to the    authors. The analysis is of a hitherto unattempted size,
  and is sophisticated and well thought out.''

  ``The paper is remarkable for a lack of grammatical and other errors."

% ---------------------------------------
  \emph{
  1) Some trends may be due to differences in sampling effort, especially
  due to differences between Thompson \& Townsend stream food webs and other
  stream webs.}

  \begin{refquote}

    My concern here is how much of the pattern can be attributed to true
    ecological effects – as opposed to the consequences of differences in the
    effort used to describe different food webs... It could be explored to some extent by
    analysing for an effect of particular authors (e.g. the Thompson and
    Townsend food webs which dominate the stream dataset) but ultimately there
    is every chance that the results here are artefacts of differences in
    sampling effort between studies. Might it be possible to randomise the
    datasets, excluding particular food webs (or authors) to determine
    robustness to this effect??

  \end{refquote}

  \textbf{R:} We share the reviewer's concern that variation in sampling
  effort could be driving the trends we observe. To ensure that this is not
  the case, we have performed several tests. We have included a brief
  allusion to these tests in the main text and a fuller explanation in the
  supplemental information.

  [[Details of the tests]]

  \begin{quotation}

  \end{quotation}

   2) Emphasize our results for streams, include the possibility that they
   may be due to greater seasonality in stream food webs.

  \begin{refquote}

    It is particularly interesting in that stream systems (as opposed to
    estuarine, marine or terrestrial food webs) are more likely to be affected
    by seasonal variability – and this is the mechanism evoked as underpinning
    the latitudinal gradient. I am surprised that the authors didn’t make more
    of this point – to some degree the difference in habitats supports their
    proposed mechanism, and this could be discussed.

  \end{refquote}

  \textbf{R:} [[We'll need to look for citations re: seasonal effects in streams.]]

  \begin{quotation}

  \end{quotation}

  \newpage

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
{\Large \bf Reply to Reviewer 2}
% ---------------------------------------

  Polite pre-amble.
  ``This is an interesting study on a timely and important topic. The core analysis of the paper (scaling relationships of food web metrics with species richness) are convincingly presented and comprehensively discussed.''

% ---------------------------------------

  1) Network terminology and methods might be inaccessible to researchers
  withoout network background.

  \begin{refquote}

    the accessibility to readers outside the food-web community could be
    improved by a more detailed explanation of the methods, especially the
    applied network metrics and underlying scaling relationships; a conceptual
    figure visualizing the expected relationships for different communities
    according to the latitude-niche breadth hypothesis could be very helpful
    here

    \smallskip

     For readers outside the field, please explain in more detail the
     difference between `original species' and `trophic species' in food webs.

  \end{refquote}

  \textbf{R:} We thank the reviewer for their concern that our manuscript
  should be accessible to as wide a variety of    researchers as possible, and
  have followed the reviewer's suggestions in several places in the manuscript.

  2) Move by-trophic-level analysis to supplemental information, consider
  numbers of species rather than proportions.

  \begin{refquote}

    the additional analyses of scaling relationships by trophic levels and
    latitude-species richness relationships are not well introduced. If the
    analysis on scaling relationships by trophic levels was maintained, then
    it should already be mentioned in the Introduction (including specific
    expectations for this analysis) and would require a more comprehensive
    discussion.

    \smallskip

    The abstract is incomplete. Results of the analysis on the scaling
    relationships by trophic levels are missing.

    \smallskip

    Please justify why you use the proportion of species within a trophic
    level and not the absolute number of species per trophic level; at a first
    glance, this would be more intuitive for me given the focus of the study
    on scaling relationships with species richness.

  \end{refquote}

  \textbf{R:}

  3) Move description of the species-richness gradient to methods and results.

  \begin{refquote}

     Analyses of species richness along latitude should already be mentioned
     and described in the Methods and should be referred to in the Results
     section instead of the Discussion.

     \smallskip

      The start of the Discussion confused me since it presents another
      additional analysis. This analysis on the latitudinal gradient in
      species richness is interesting and important for the interpretation of
      the patterns, but should already be presented in Methods and Results
      section.

  \end{refquote}

  \textbf{R:} [[Going to be hard to fit this in gracefully.]]

  4) Explain habitat categories.

  \begin{refquote}

    Please describe in more detail why you used the chosen habitat categories
    and provide the number of webs per habitat type also in the main
    manuscript.

  \end{refquote}

  \textbf{R:} We followed the habitat categories listed in [[foodwebdb.org]].
  Although more detailed descriptions were also    provided, we opted to use the
  set of five more general habitat types in order to have a greater number of
  food webs in each category.

  5) The y-xais of Fig. 1 is unclear, top predators are unlabelled.

  \begin{refquote}

    Please re-label the y-axis on Fig. 1 to improve clarity. The top predators
    are missing in this figure although they are mentioned in the legend.

  \end{refquote}

  \textbf{R:} [[Sure fine whatever]]

  6) Add generality, vulnerability to Fig. 2 in main text.

  \begin{refquote}

    I would suggest adding generality and vulnerability to Fig. 2 in the main
    manuscript (instead of showing them in Fig. S2 only).

  \end{refquote}

  \textbf{R:} [[That's going to be ugly]]

  \newpage

\bibliographystyle{geb}%Compile with jae.bst style file
\bibliography{noISBN.bib}

\end{document}

### 2015-08-23 manuscript/AC-reply-to-referees.tex
Toronto airport edits

@@
 
-  \textbf{R:} Well, this was an exploratory study.
-I think that's fine.
-We explored, we discovered, Science!
-And I looked at differences between ecosystem types because they're usually different ...
-so there.
-I should probably lie about it though.
-
-  I guess scaling of species richness with latitude might be different in different food webs, maybe I can cite that?
-  Clearly we didn't develop the crossover between the latitude-specialization and latitude-species trends :(
+  \textbf{R:} Providing \emph{a priori} expectations for the directions of relationships between latitude and niche width/specialisation is difficult due to the 
+  contrasting hypotheses of narrower niches in the tropics~\citep{Vazquez2004} versus broader niche space in the tropics~\citep{Davies2007}.
+Given the limited support available for either hypothesis, it was equally likely that scaling of specialization with species richness might be stronger or weaker towards the poles.
+  We do not share the Associate Editor's concern that this makes our study too exploratory but rather had intended to use the results of our analyses to support one or the other of these hypotheses.
+We have added to the manuscript at lines XX and YY to more explicitly frame our study as a test of these two versions of the latitude-niche breadth hypothesis.
 
@@
   direct relationships between latitude and the degree of specialisation
-  (i.e., the breadth of the Eltonian niche; Elton, 1927) of species within
+  (i.e., the breadth of the Eltonian niche;~\citealp{Elton1927}) of species within
   food webs. Specifically, narrower niches in the tropics would equate to
@@
 
+  \smallskip
+
+  Line 43:
+
   \begin{quotation}
+
+  By testing whether latitude affects the scaling of each property with
+  species richness, we test for the effects of latitude on specialisation
+  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
+  specialisation with species richness is weaker at the tropics (i.e., if
+  species gain fewer links, predators, or prey as the size of the network
+  increases), this will indicate narrower niches at the tropics. If, however,
+  the scaling of specialisation with species richness does not vary over
+  latitude, this will support the hypothesis that niches are similarly-sized
+  worldwide but that there is a broader niche space in the tropics.
 
@@
 
-  \textbf{R:} We are also aware of this research. This is why we in fact
-  considered all models with $\delta$AIC\textless2   as described in lines
-  97-98. Where possible, we chose the model from that array with the fewest
-  degrees of freedom. We only differentiated between models with very similar
-  AICs when there were several models with the same degrees of freedom. In general
-  these models differed only in which ecosystem types were included for intercept
-  effects (including the different slopes in lake and stream ecosystems had larger
-  effects) [[Maybe give him a list of the top models?]]. As we were only interested
-  in changes in the slope of the scaling relationship with latitude, the slight changes
-  in the intercepts would not change our conclusions at all.
+  \textbf{R:} We are also aware of the general consensus    that models where
+  $\delta$AIC\textess2 are roughly equally well-supported. This is why our
+  procedure (as stated in lines XX-XX) was to first consider the set of models
+  where $\delta$AIC\textess2 and select the model with the fewest degrees of
+  freedom. We chose the smallest model where $\delta$AIC\textess2 in order to
+  avoid over-fitting the models. We only used AIC as a deciding factor where
+  there were several models that shared the minimal degrees of freedom and all
+  had $\delta$AIC\textess2.  In fact, this scenario did not occur for the
+  models presented in the previous draft   (it does occur when the by-trophic-
+  level models use counts of species rather than proportions), so we have simply
+  removed the description of this step of our analysis from the main text. [[If we go with species counts, will need to describe what the differences are between the similar models]]
 
@@
 
-  \textbf{R:} We thought that breaking down the food webs into trophic levels would
-  provide an extra dimension of detail for this analysis. If scaling relationships
-  had varied strongly with latitude for one trophic level and not another, that also
-  would have guided our thoughts about potential mechanisms. We are happy to remove this
-  analysis to the appendix, but I don't feel like justifying why everything has to be
-  have a priori expectations and mechanisms. It's all post-hoc bullshitting anyway.
+  \textbf{R:} We have followed Reviewer 2's suggestion and 
+  moved these additional analyses to the supplemental 
+  iformation. This analysis was purely exploratory. The 
+  scaling of specialisation with proportions (or numbers) 
+  of species at different trophic levels has not been 
+  previously investigated (to our knowledge), and it 
+  seemed to us to be a logical extension of the main 
+  analysis. If the Associate Editor disagrees in principle 
+  with exploratory science, we are willing to remove these 
+  analyses altogether.
 
@@
 
+  \textbf{R:} As the Associate Editor likely suspected, the property estimates
+  are all strongly    positively correlated. As generality and vulnerability
+  describe the two components (number of prey and number    of predators,
+  respectively) of links per species, this is   to be expected. We have added a
+  brief description of this correlation to the main text as we believe it   will
+  provide some context for the very similar results for link density and
+  vulnerability.
+
+  \begin{quotation}
+
+    Link density, generality, and vulnerability were strongly and positively
+    correlated ($R^2$=0.891 for link density and generality,
+    $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.890
+    for generality and vulnerability).
+
+  \end{quotation}
+
   6) L116: missing supporting statistics
@@
   \end{refquote}
+
+  \textbf{R:} We have ammended the text (lines XX-XX) to support our statement.
+
+  \begin{quotation}
+    In stream food
+    webs, generality increased more rapidly towards the poles
+    ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
+    vulnerability did not vary with latitude (i.e., the interaction term $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
+  \end{quotation}
 
@@
 
+  \textbf{R:} [[Try to find evidence that this doesn't happen, otherwise I guess we're just going to have to hedge like summbitches??]]
+
   8) Ensure layout (especially citations) matches journal specifications.
@@
   \end{refquote}
+
+  \textbf{R:} Can do, boss.
 

### 2015-08-23 manuscript/latitudepaper.tex
Toronto airport edits

@@
   degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927}) of species within food webs.
+  Specifically, narrower niches in the tropics would equate to
+  greater specialisation (narrower niches) while constant niche sizes but
+  greater productivity would translate to constant specialisation and niche
+  width across latitude.
   Attempts to unravel these effects, however,
@@
   relationship between specialisation and species richness over changing latitude. Here, we use three measures of specialisation:
-  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators). By testing whether
-  latitude affects the scaling of each property with species richness, we test effects of latitude on specialisation implied by
-  the ``latitude-niche breadth hypothesis''.
+  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators).   By testing whether latitude affects the scaling of each property with
+  species richness, we test for the effects of latitude on specialisation
+  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
+  specialisation with species richness is weaker at the tropics (i.e., if
+  species gain fewer links, predators, or prey as the size of the network
+  increases), this will indicate narrower niches at the tropics. If, however,
+  the scaling of specialisation with species richness does not vary over
+  latitude, this will support the hypothesis that niches are similarly-sized
+  worldwide but that there is a broader niche space in the tropics.
 
@@
 
-    % Logarithm of a sum is awful:   log(a+c) = log(a) + log(1+b^[log(c)-log(a)]) But can probably feed that into R...
-
     After determining the appropriate form of the scaling relationship, we
@@
     best-fitting model was then determined to be the model with the fewest
-    terms  where $\Delta$AIC\textless2. If several models shared the fewest
-    number of terms  and had $\Delta$AIC\textless2, the model with the lowest
-    AIC in that set was chosen as the best-fit model.
-
-  \section*{Scaling by Trophic Levels}
-
-    We were also interested in the ways that scaling relationships with species richness might
-    be affected by changes to the distribution of species among trophic levels. To
-    that end, we repeated all of the above analyses replacing species richness by
-    proportion of basal resources, proportion of intermediate consumers,
-    or proportion of top predators. All model fitting and model
-    simplification procedures were identical to those described for species
-    richness.
+    terms  where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
+    % If several models shared the fewest
+    % number of terms  and had $\Delta$AIC\textless2, the model with the lowest
+    % AIC in that set was chosen as the best-fit model.
 
@@
 
-  Link density, generality, and vulnerability each increased with increasing
+  Link density, generality, and vulnerability were strongly and positively
+  correlated ($R^2$=0.891 for link density and generality,
+  $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.890
+  for generality and vulnerability). Each property 
+  increased with increasing
   species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
@@
   ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
-  vulnerability did not vary with latitude.
-
-  Unlike species richness, only generality showed an overall increase with
-  increasing proportions of basal resources in a web ($\beta_0$=0.019,
-  $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
-  link density, generality, and vulnerability, respectively;
-  Fig.~\ref{props_v_lat}). In each case, however, there were substantial
-  effects of latitude on the scaling relationships. Thus, the scaling
-  exponents for link density and vulnerability were negative for estuarine,
-  lake, and stream communities and became more negative towards the poles
-  ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
-  $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
-  density and vulnerability in marine and terrestrial communities, the overall
-  effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
-  $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
-  $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
-  $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
-  that there was weak scaling at most latitudes. In contrast, the scaling
-  exponent of generality with the proportion of basal resources was positive
-  near the equator and negative near the poles in estuarine, lake, and stream
-  communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
-  very little change in the scaling exponents for marine and terrestrial
-  communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
-  $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
-
-  As with species richness, link density, generality, and vulnerability
-  generally increased with the proportion of intermediate consumers in a web
-  ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
-  $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
-  The best-fit models for link density and vulnerability did not include
-  any effect of latitude. In contrast, the strength of the scaling relationship
-  for generality increased weakly towards the poles in estuarine, marine, and
-  terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
-  towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
-  and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).
-
-  In contrast to the generally positive scaling relationships above, link
-  density, generality, and vulnerability decreased as the proportion of top
-  predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
-  $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
-  Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
-  strength of this scaling did not vary significantly with latitude
-  ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
-  In stream and terrestrial food webs, however, scaling was more strongly negative in the 
-  tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
-  and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
-  $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
-  for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
-  for latitude in any ecosystem type.
+  vulnerability did not vary with latitude (i.e., the interaction term $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
 

### 2015-08-23 manuscript/supplement.tex
Toronto airport edits

@@
 
-\subsection*{Appendix S2: Scaling Relationships with S}
+\subsection*{Appendix S2: Forms of scaling Relationships with S}
 
@@
 
+\subsection*{Appendix S4: Scaling relationships by trophic level}
+
+  \subsubsection*{Methods}
+
+    We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
+    in the ways that scaling relationships with species richness might
+    be affected by changes to the distribution of species among trophic levels. To
+    that end, we repeated our analyses replacing species richness with the
+    proportion of basal resources, proportion of intermediate consumers,
+    or proportion of top predators. All model fitting procedures were identical to those
+    described for species richness. The model simplicication procedure was similar to
+    the procedure described for species richness, except that in some cases there were
+    multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
+    In these cases, we defined the best-fitting model as the model with the lowest AIC in the
+    set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.
+
+  \subsubsection*{Results}
+
+    Unlike species richness, only generality showed an overall increase with
+    increasing proportions of basal resources in a web ($\beta_0$=0.019,
+    $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
+    link density, generality, and vulnerability, respectively;
+    Fig.~\ref{props_v_lat}). In each case, however, there were substantial
+    effects of latitude on the scaling relationships. Thus, the scaling
+    exponents for link density and vulnerability were negative for estuarine,
+    lake, and stream communities and became more negative towards the poles
+    ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
+    $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
+    density and vulnerability in marine and terrestrial communities, the overall
+    effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
+    $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
+    $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
+    $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
+    that there was weak scaling at most latitudes. In contrast, the scaling
+    exponent of generality with the proportion of basal resources was positive
+    near the equator and negative near the poles in estuarine, lake, and stream
+    communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
+    very little change in the scaling exponents for marine and terrestrial
+    communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
+    $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
+
+    As with species richness, link density, generality, and vulnerability
+    generally increased with the proportion of intermediate consumers in a web
+    ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
+    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
+    The best-fit models for link density and vulnerability did not include
+    any effect of latitude. In contrast, the strength of the scaling relationship
+    for generality increased weakly towards the poles in estuarine, marine, and
+    terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
+    towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
+    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).
+
+    In contrast to the generally positive scaling relationships above, link
+    density, generality, and vulnerability decreased as the proportion of top
+    predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
+    $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
+    Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
+    strength of this scaling did not vary significantly with latitude
+    ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
+    $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
+    In stream and terrestrial food webs, however, scaling was more strongly negative in the 
+    tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
+    and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
+    $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
+    for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
+    for latitude in any ecosystem type.
+
 \newpage
 
-\subsection*{Appendix S4: Supplemental Figures}
+\subsection*{Appendix S5: Supplemental Figures}
 

### 2015-08-24 manuscript/AC-reply-to-referees.tex
All but one of the AE's points has been addressed

@@
 
-  \textbf{R:} Can do, boss.
+  \textbf{R:} We have changed all refences to the Vancouver style and have added sections for author contributions, conflicts of interest, and funding.
+  [[Check the in-text citations match published papers]]
 
@@
 
-  \textbf{R:}
+  \textbf{R:} Following the Referee's suggestion, we have moved our analysis of scaling relationships by trophic levels to the supplemental information. [[Need to address the rest of this.]]
 

### 2015-08-24 manuscript/latitudepaper.tex
All but one of the AE's points has been addressed

@@
 
+\section*{Competing interestes}
+
+  We have no competing interests.
+
+\section*{Authors' contributions}
+
+  ARC, DBS, and TNR designed the study, ARC collected
+  published data, performed the analyses, and drafted the 
+  article. DBS and TNR substantially revised the article;
+  all authors approved the final version.
+
 \section*{Acknowledgements}
@@
   the manuscript.
+
+\section*{Funding}
   This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
@@
 \newpage
-\bibliographystyle{jae}%Compile with jae.bst style file
+\bibliographystyle{vancouver}%Compile with vancouver.bst style file
 \bibliography{noISN}% your .bib file(s)

### 2015-08-25 manuscript/AC-reply-to-referees.tex
Expanded the R file to include a column per author

@@
   \textbf{R:} We are also aware of the general consensus    that models where
-  $\delta$AIC\textess2 are roughly equally well-supported. This is why our
+  $\delta$AIC\textless2 are roughly equally well-supported. This is why our
   procedure (as stated in lines XX-XX) was to first consider the set of models
-  where $\delta$AIC\textess2 and select the model with the fewest degrees of
-  freedom. We chose the smallest model where $\delta$AIC\textess2 in order to
+  where $\delta$AIC\textless2 and select the model with the fewest degrees of
+  freedom. We chose the smallest model where $\delta$AIC\textless2 in order to
   avoid over-fitting the models. We only used AIC as a deciding factor where
   there were several models that shared the minimal degrees of freedom and all
-  had $\delta$AIC\textess2.  In fact, this scenario did not occur for the
+  had $\delta$AIC\textless2.  In fact, this scenario did not occur for the
   models presented in the previous draft   (it does occur when the by-trophic-
@@
   have followed the reviewer's suggestions in several places in the manuscript.
+  [[sent DBS a draft of the conceptual figure]]
+
+  At lines XX-XX we have added parenthetical explanations of the original and 
+  trophic-species versions of food webs.
+
+  \begin{quotation}
+
+    We therefore analysed both original (i.e., without aggregating any species) and
+    trophic-species (i.e., after aggregating species with identical predators and
+    prey) versions of the dataset;
+
+  \end{quotation}
 
@@
 
-  \textbf{R:} Following the Referee's suggestion, we have moved our analysis of scaling relationships by trophic levels to the supplemental information. [[Need to address the rest of this.]]
+  \textbf{R:} Following the Referee's suggestion, we have moved our analysis
+  of scaling relationships by trophic levels to the supplemental information.
+  We hope that this will address the Referee's first two concerns above. We thank the
+  Referee for this suggestion as it has allowed us more space to describe our network
+  measures in more accessible terms.
+
+  In fact we did analyse absolute numbers of species within a trophic level as well 
+  as proportions. Both ways of defining the distribution of species across trophic levels
+  have benefits (absolute numbers are more intuitive, as the Referee points out, while
+  proportions feature in more of the food-web literature) and so we ultimately decided
+  on proportions because the trends were clearer than in absolute numbers. [[Should we just
+  give both now that this is in the supplemental?]]
 

### 2015-08-25 code/byauthor_jacknife_setup.py

@@ -5,8 +5,7 @@ import random
 import pybtex
 from pybtex.database.input import bibtex
 
-used_webs=set(["Alcorlo2001","Allan1982","Amundsen2013","Angelini2005","Angelini2006","Angelini2010","Angelini2011","Angelini2013","Badcock1949","Baeta2011","Baril1983","Beaver1985","Bindloss1972","Bird1930","Boit2012","Bradstreet1982","Brodeur1992","Brose2005","Brown1975","Bulman2001","Burgis1972","Carlson1968","CattinBlandenier2004","Christian1999","Clarke1967","Closs1994","Cohen1990","Cohen2003","Collins1976","Corker1984","Cornejo-Donoso2008","Cromar1996","Cruz-Escalona2007","Cummins1966","Dexter1947","Douglass2011","Edwards1982","Fetahi2011","Filgueira2011","Fryer1959","Gaedke1994","Goldwasser1993","Gontikaki2011","Hampton2011","Harris1972","Harrison1995","Hartley1948","Havens1992","Hechinger2011","Hewatt1937","Hildrew1985","Hogetsu1979","Hopkins1993","Howes1954","Huang2008","Hurlbert1972","Huxham1996","Jones1949","Jones1950","Jonsson2005","Kelleway2010","Kemp1977","Khan2009","Kitching1987","Koslucher1973","Kremer1978","Lafferty2006","Lancraft1991","Larsson1978","Lin2006","Link2002","Liu2007","MacGinitie1935","Mann1972","Mann1972a","Marshall1982","Martinez1991","Massana1996","Mayse1978","Menge1976","Minckley1963","Minshall1967","Moriarty1973","Motta2005","Mouritsen2011","Niering1963a","Nixon1973","Odum1975","Opitz1996","Paine1980a","Parker2006","Patricio2006","Patten1975","Patten1979","Pattie1966","Paviour-Smith1956","Pechlaner1972","Peterson1979","Polis1991a","Preston2012","Rasmussen1941","Ratsirarson1996","Rayner2010","Richards1926","Rosenthal1974","Ruzicka2012","Savely1939","Schiemer1979","Schneider1997","Seifert1979","Shushkina1979","Simberloff1976","Smith2007","Snow1958","Sorokin1972","Stagliano2002","Stewart2011","Summerhayes1923","Summerhayes1928","Teal1962","Thieltges2011","Thompson2003","Thompson2004","Thompson2004c","Tilly1968","Towns
[…]

### 2015-08-25 code/food_web_properties.py

@@ -5,6 +5,8 @@ import random
 import networkx as nx
 from decimal import *
 from math import *
+
+from byauthor_jacknife_setup import *
 # import role_dictionary_maker as RD
 
 #For new lists, calculate properties.
@@ -188,7 +190,18 @@ def food_web_properties(directory,item,G):
     stroutput.append(str(thing))
   return stroutput 
 
-def websorter(metafile,directory):
+def authors_by_web(bibfile,used_webs,webkeys):
+  authorset,authors_by_key,authors_with_initials=bibreader(bibfile,used_webs)
+  web_to_key=web_key_dict(webkeys)
+
+  # The idea here will be to add columns for each author to the datafile so I can jacknife by authors.
+  web_to_authors={}
+  for web in web_to_key:
+    authors=authors_by_key[web_to_key[web]]
+    web_to_authors[web]=authors
+  return web_to_authors
+
+def websorter(metafile,directory,bibfile,webkeys):
   infodict={}
   uselist=[]
   f=open(metafile)
@@ -229,10 +242,15 @@ def websorter(metafile,directory):
           'Herbivores',
           'Intermediate',
           'Toppreds']
-  header=header
+
+  authorset,authors_by_key,authors_with_initials=bibreader(bibfile,used_webs)
+  web_to_authors=authors_by_web(bibfile,used_webs,webkeys)
+
+  bigheader=header+list(sorted(authorset))
+  # Header is expanded with a list of authors... now I need to fill those columns.
 
   outfile=open('../mod_data/summary-properties.tsv','w')
-  outfile.write('\t'.join(header))
+  outfile.write(u'\t'.join(header).encode('utf-8').strip())
   outfile.write('\n')
 
   for item in uselist:
@@ -248,7 +266,7 @@ def websorter(metafile,directory):
            # extfile.write('\t'.join(map(str,[eval(item) for item in extheader])))
 
   out2=open('../non_TS/summary-properties.tsv','w')
-  out2.write('\t'.join(header))
+  out2.write(u'\t'.join(bigheader).encode('utf-8').strip())
   out2.write('\n')
 
   for item in uselist:
@@ -258,6 +276,19 @@ def websorter(metafile,directory):
     out2.write('\t'.join(info))
     out2.write('\t')
     out2.write('\t'.join(snoutputs))
+
+    try:
+      shortitem=item.split('.web')[0].split('WEB')[1]
+    except IndexError:
[…]

### 2015-08-25 code/recreate_with_subset.R

@@ -19,6 +19,7 @@
     +log(Species):Latitude
     +log(Species):Latitude:Lake,
     na.action=na.fail))    }
+    # Decided on DF
 
     # cutoff<- 4/((nrow(data)-length(LS_min$coefficients)-2)) 
     # plot(LS_min, which=4, cook.levels=cutoff)
@@ -54,6 +55,7 @@
       +log(Species):Latitude:(Lake+Stream)
       ,na.action=na.fail))
     }
+    # Decided on DF
 
     # cutoff<- 4/((nrow(data)-length(Gen_min$coefficients)-2)) 
     # plot(Gen_min, which=4, cook.levels=cutoff)
@@ -88,6 +90,7 @@
       +log(Species):Latitude
       +log(Species):Latitude:Lake
       ,na.action=na.fail))  }
+    # Decided based on Df
 
     # cutoff<- 4/((nrow(data)-length(Vul_min$coefficients)-2)) 
     # plot(Vul_min, which=4, cook.levels=cutoff)

### 2015-08-27 code/byTL_Models.R
Jackknife figures are a big ol' go

@@ -91,6 +91,7 @@ by_TL=FALSE
   for(i in 1:nrow(olddata)){
     newdata=olddata[-i,]
     name=olddata$Web[i]
+    print(name)
 
     data=newdata
     source('recreate_with_subset.R')

### 2015-08-27 manuscript/AC-reply-to-referees.tex

@@
 
-  \textbf{R:} [[Try to find evidence that this doesn't happen, otherwise I guess we're just going to have to hedge like summbitches??]]
+  \textbf{R:} We do not think it likely that we will be able to find evidence that prey-
+    switching does not occur in certain ecosystem types because, by definition,
+    it is impossible to document an event that does not occur. In fact, there are almost
+    certainly examples of species which switch between different prey in any ecosystem type
+    at any latitude. As we do not feel qualified to conduct a review of the frequencies of
+    prey-switching, we have instead revised our discussion following an excellent suggestion
+    by Referee 1 to focus on the greater seasonality experienced by stream communities.
+    [[not done, will need to tone this down.]]
+
+  \begin{quotation}
+  \end{quotation}
 
@@
 
-  \textbf{R:} We have changed all refences to the Vancouver style and have added sections for author contributions, conflicts of interest, and funding.
+  \textbf{R:} We have changed all refences to the Vancouver style and have 
+    added sections for author contributions, conflicts of interest, and funding.
     [[Check the in-text citations match published papers]]
@@
 
-  Polite pre-amble.
-
-  ``This is an interesting paper that takes advantage of recent compilations
+  The Reviewer was very positive about our manuscript, calling it
+  ``an interesting paper that takes advantage of recent compilations
   of food webs to test basic theory with respect to latitudinal gradients in
-  niche breadth. The paper is exceptionally well written and presented, and this
-  is a credit to the    authors. The analysis is of a hitherto unattempted size,
-  and is sophisticated and well thought out.''
-
-  ``The paper is remarkable for a lack of grammatical and other errors."
+  niche breadth'', ``exceptionally well written and presented'', ``sophisticated
+  and well thought out''. We thank the Reviewer for their kind words,
+  and also for their suggestions for further improving our manuscript. We
+  have addressed each comment below (in italics), and are confident that our
+  responses (preceded by a \textbf{R}) have further improved the manuscript.
 
@@
   \textbf{R:} We share the reviewer's concern that variation in sampling
-  effort could be driving the trends we observe. To ensure that this is not
-  the case, we have performed several tests. We have included a brief
-  allusion to these tests in the main text and a fuller explanation in the
-  supplemental information.
-
-  [[Details of the tests]]
+  effort could be driving the trends we observe, as it is highly likely that
+  the authors of all 196 webs in our dataset did not follow the same procedures.
+  Following the reviewer's suggestion, we have jackknifed our models by systematically
+  removing each web in turn and then re-running our analysis. We then repeated this
+  process, removing each author (or set of authors where authors worked on identical sets
+  of food webs) in turn and re-fitting the models. We are happy to report that removing
+  any single web had no significant effect on any model, nor did removing any author
+  (we removed Thompson and Townsend separately as each worked on one web that the other
+  did not). We have added a description of these methods and summary figures of their results
+  to the supporting information, and we thank the reviewer for suggesting this validation
+  of our overall results. [[done]] We have also added a brief note in the main text to direct other
+  readers with similar concerns to the supporting information. [[not done]]
 
@@
   ``This is an interesting study on a timely and important topic.
-The core analysis of the paper (scaling relationships of food web metrics with species richness) are convincingly presented and comprehensively discussed.''
+The core analysis of the paper (scaling relationships of food web metrics with species richness) are convincingly presented and comprehensively discussed.''1
 

### 2015-08-27 manuscript/supplement.tex

@@
 % \begin{landscape}
-\subsection*{Appendix S1: Details of Food Web Sources and Selection}
+\subsection*{Appendix S1: Details of food web sources and selection}
 
@@
 
-\subsection*{Appendix S2: Forms of scaling Relationships with S}
+\subsection*{Appendix S2: Forms of scaling relationships with species richness}
 
@@
     % Was it? Do I even care?
+
+\subsection*{Appendix SX: Testing for effects of sampling effort}
+
+  \subsubsection*{Methods}
+    As our dataset consists of food webs published over several decades, from 
+    many countries, and by many research groups, it is highly likely that not
+    all webs were compiled using the same procedure or with the same degree of
+    sampling effort. In order to insure that our results were not driven by
+    particularly unusual food webs, or by unusually well- or poorly-sampled webs 
+    derived from any particular group, we performed two jackknife tests of our 
+    results. In the first test, we removed one web from our dataset and re-fit 
+    our models, then repeated this process for all webs in the dataset. We then 
+    plotted the estimates for each coefficient in each of our models in order to 
+    determine whether the omission of any web dramatically changed the resulting 
+    model. In the second test, we removed groups of webs assembled by a given 
+    author (or authors, where two or more authors assembled identical sets of 
+    food webs) and again plotted the resulting collection of estimates for each
+    coefficient. We did not plot the coefficients resulting from the removal of
+    authors who compiled a single food web, as these were included in the first
+    test. This allowed us to determine whether the inclusion or exclusion
+    of the webs assembled by a particular researcher or group of researchers
+    affected our results.
+
+  \subsubsection*{Results}
+
+    None of our models were affected by the removal of any single food web.
+    Estimates of co-efficients from all jackknifed datasets were extremely
+    similar (Figs.~\ref{LS_web,Gen_web,Vul_web}). Moreover, our models were also robust to the removal
+    of any given author (Figs.~\ref{LS_auth,Gen_auth,Vul_auth}). We are therefore very confident that,
+    while there are undoubtedly differences in the methods used to compile food webs,
+    these differences are not driving the trends we report in this study.
+
+    \begin{figure}[h]
+    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_web.eps}}
+    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
+    in the equation after the removal of each web in the dataset. All estimates are colour
+    coded according the ecosystem type of the removed web.}
+    \label{LS_web}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_web.eps}}
+    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
+    in the equation after the removal of each web in the dataset. All estimates are colour
+    coded according the ecosystem type of the removed web.}
+    \label{Gen_web}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_web.eps}}
+    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
+    in the equation after the removal of each web in the dataset. All estimates are colour
+    coded according the ecosystem type of the removed web.}
+    \label{Vul_web}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_author.eps}}
+    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    when jackknifing across authors of the published food webs used in this study. 
+    We show the estimates (+/- 1SE) of each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset.}
+    \label{LS_web}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_author.eps}}
+    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    when jackknifing across authors of the published food webs used in this study. 
+    We show the estimates (+/- 1SE) of each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset.}
+    \label{Gen_web}
+    \end{figure}
+
+    \begin{figure}[h]
+    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_author.eps}}
+    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    when jackknifing across authors of the published food webs used in this study. 
+    We show the estimates (+/- 1SE) of each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset.}
+    \label{Vul_web}
+    \end{figure}
 

### 2015-08-27 manuscript/AC-reply-to-referees.tex
Significant additions to the reply

@@
   to the supporting information, and we thank the reviewer for suggesting this validation
-  of our overall results. [[done]] We have also added a brief note in the main text to direct other
-  readers with similar concerns to the supporting information. [[not done]]
+  of our overall results. We have also added a brief note in the main text to direct other
+  readers with similar concerns to the supporting information (lines XX-XX). [[At the end of the 
+  section describing our analyses - didn't seeem to fit after the first mention of sampling effort]]
+  [[done]]
 
   \begin{quotation}
+
+    As a supplemental check to ensure that variation in sampling effor across
+    food webs was not responsible for the trends we observed, we then repeated
+    our analyses using jackknifed data sets in which we 1) sequentially removed
+    each food web in the dataset and 2) sequentially removed sets of food webs 
+    associated with each author of the food webs in the dataset. Parameter 
+    estimates varied very little across either series of jackknifes (\emph{Appendix SXX}).
 
@@
 
-  Polite pre-amble.
-  ``This is an interesting study on a timely and important topic.
-The core analysis of the paper (scaling relationships of food web metrics with species richness) are convincingly presented and comprehensively discussed.''1
+  The Reviewer stated that our study is interesting and covers ``a timely and
+  important topic. The core analysis of the paper (scaling relationships of
+  food web metrics with species richness) are convincingly presented and
+  comprehensively discussed.'' Nevertheless, the Reviewer has suggested several
+  ways in which our manuscript could be improved. We have responded to each suggestion
+  in turn, and believe that our replies (preceded by \textbf{R}) have further improved
+  the manuscript.
 
@@
   have followed the reviewer's suggestions in several places in the manuscript.
-  [[sent DBS a draft of the conceptual figure]]
+  We now include a conceptual figure to clearly and succinctly link the changes
+  to scaling relationships we expected to the two versions of the latitude-niche
+  breadth hypothesis (Fig. 1).
 
   At lines XX-XX we have added parenthetical explanations of the original and 
-  trophic-species versions of food webs.
+  trophic-species versions of food webs. We have also added parenthetical definitions
+  of link density, generality, and vulnerability at the begining of the results section
+  to remind readers of the biological meaning of these measures.
 
@@
     trophic-species (i.e., after aggregating species with identical predators and
-    prey) versions of the dataset;
+    prey) versions of the dataset ...
+
+    \smallskip
+
+      Link density (mean number of feeding links per species), generality
+      (mean number of prey per species), and vulnerability (mean number of predators
+      per species) were strongly and positively correlated ...
 
@@
 
-  \textbf{R:} [[Going to be hard to fit this in gracefully.]]
+  \textbf{R:} We had originally viewed this analysis as a very minor part of our paper,
+  but are happy to follow the Reviewer's suggestion and integrate it in the methods and
+  results along with our main analyses. We have described the methods for this analysis
+  in lines XX-XX and summarize our results in lines XX-XX.
+
+  \begin{quotation}
+
+    \subsection*{Gradients over latitude}
+
+    To put our dataset in the context of other research on latitudinal gradients in species richness,
+    we first examined simple linear relationships between latitude and each of 
+    species richness, links per species, generality, vulnerability, and proportions
+    of basal resources, intermediate consumers, and top predators. We fit models of the form
+
+    \begin{equation}
+    \label{Latfull}
+    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
+    \end{equation}
+
+    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
+    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
+    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
+    marine, lake, and terrestrial networks with estuarine
+    networks providing the intercept) and $\epsilon_{i}$ is a residual error term. 
+    We next calculated the AIC
+    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
+    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
+    Simplified models were obtained by
+    systematically removing all possible combinations of terms from the full model.
+    The best-fitting model was then determined to be the model with the fewest terms 
+    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
+    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
+    model.
+
+    \smallskip
+
+    Contrary to the expected latitudinal gradient, the best-fit version of
+    equation~(\ref{Latfull}) for species richness did not  include a signficant
+    effect of latitude for any  ecosystem type. Further, there were no
+    relationships between link density, generality, or vulnerability with
+    latitude for any ecosystem type.
+
+  \end{quotation}
 
@@
 
-  \textbf{R:} We followed the habitat categories listed in [[foodwebdb.org]].
-  Although more detailed descriptions were also    provided, we opted to use the
-  set of five more general habitat types in order to have a greater number of
-  food webs in each category.
+  \textbf{R:} We followed the habitat categories given by the publications which
+  aggregated the food webs. Although more detailed descriptions were also provided, 
+  we opted to use the set of five more general habitat types in order to have a 
+  greater number of food webs in each category.
+
+  We have added a brief explanation, and the number of webs in each ecosystem type, at lines XX-XX:
+
+  \begin{quotation}
+    We grouped food web by ecosystem type (stream, N=71; lake, N=47; marine, N=28; estuarine, N=18;
+    and terrestrial, N=31) according to their designation in previous aggregations of food webs 
+    (i.e.,~\citet{GlobalWeb,Riede2011,Dunne2013}).
+
+  \end{quotation}
 

### 2015-08-27 manuscript/latitudepaper.tex
Significant additions to the reply

@@
     and intermediate consumers (species with both predators and prey, including cannibalistic
-    species).
+    species). We grouped food web by ecosystem type (stream, N=71; lake, N=47; marine, 
+    N=28; estuarine, N=18; and terrestrial, N=31) according to their designation in 
+    previous aggregations of food webs (i.e.,~\citet{GlobalWeb,Riede2011,Dunne2013}).
 
@@
     is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
-    species with identical sets of interactions. We therefore analysed both original and trophic-species versions
+    species with identical sets of interactions. We therefore analysed both original (i.e., without aggregating 
+    any species) and trophic-species (i.e., after aggregating species with identical predators and prey) versions
     of the dataset; in each case using the number of species and 
-    links in each web to calculate the mean link density (number of links per species), mean generality 
+    feeding links in each web to calculate the mean link density (number of links per species), mean generality 
     (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
@@
     similar whether or not redundant species are included. For simplicity, here we present only
-    the results for the original webs.
+    the results for the original (un-aggregated) webs.
+
+  \subsection*{Gradients over latitude}
+
+    To put our dataset in the context of other research on latitudinal gradients in species richness,
+    we first examined simple linear relationships between latitude and each of 
+    species richness, links per species, generality, vulnerability, and proportions
+    of basal resources, intermediate consumers, and top predators. We fit models of the form
+
+    \begin{equation}
+    \label{Latfull}
+    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
+    \end{equation}
+
+    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
+    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
+    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
+    marine, lake, and terrestrial networks with estuarine
+    networks providing the intercept) and $\epsilon_{i}$ is a residual error term. 
+    We next calculated the AIC
+    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
+    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
+    Simplified models were obtained by
+    systematically removing all possible combinations of terms from the full model.
+    The best-fitting model was then determined to be the model with the fewest terms 
+    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
+    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
+    model.
 
@@
     terms  where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
+    As a supplemental check to ensure that variation in sampling effor across
+    food webs was not responsible for the trends we observed, we then repeated
+    our analyses using jackknifed data sets in which we 1) sequentially removed
+    each food web in the dataset and 2) sequentially removed sets of food webs 
+    associated with each author of the food webs in the dataset. Parameter 
+    estimates varied very little across either series of jackknifes (\emph{Appendix SXX}).
     % If several models shared the fewest
@@
 
-  Link density, generality, and vulnerability were strongly and positively
-  correlated ($R^2$=0.891 for link density and generality,
+  Contrary to the expected latitudinal gradient, the best-fit version of
+  equation~(\ref{Latfull}) for species richness did not  include a signficant
+  effect of latitude for any  ecosystem type. Further, there were no
+  relationships between link density, generality, or vulnerability with
+  latitude for any ecosystem type. Link density (mean number of feeding links
+  per species), generality (mean number of prey per species), and
+  vulnerability (mean number of predators per species) were strongly and
+  positively correlated ($R^2$=0.891 for link density and generality,
   $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.890
-  for generality and vulnerability). Each property 
-  increased with increasing
+  for generality and vulnerability).
+
+  Each property increased with increasing
   species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,

### 2015-08-27 manuscript/supplement.tex
Significant additions to the reply

@@
 
-\subsection*{Appendix S3: Relationships with latitude}
-
-  \subsubsection*{Methods}
-
-    To determine whether there were latitudinal gradients in food-web structure,
-    we first examined simple linear relationships between latitude and each of 
-    species richness, links per species, generality, vulnerability, and proportions
-    of basal resources, intermediate consumers, and top predators. We fit models of the form
-
-    \begin{equation}
-    \label{Latfull}
-    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
-    \end{equation}
-
-    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
-    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
-    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
-    marine, lake, and terrestrial networks with estuarine
-    networks providing the intercept) and $\epsilon_{i}$ is a residual error term. 
-    We next calculated the AIC
-    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
-    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
-    Simplified models were obtained by
-    systematically removing all possible combinations of terms from the full model.
-    The best-fitting model was then determined to be the model with the fewest terms 
-    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
-    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
-    model.
-
-  \subsubsection*{Results}
-    Contrary to the expected latitudinal gradient, the best-fit version of
-    equation~(\ref{Latfull}) for species richness did not 
-    include a signficant effect of latitude for any 
-    ecosystem type. Further, there were no relationships
-    between link density, generality, or vulnerability
-    with latitude for any ecosystem type.
-
-    The relationships between latitude and the proportions of species at each trophic level were more complex. 
-    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001) 
-    but did not vary with latitude in estuarine, marine, lake, or terrestrial 
-    food webs ($\beta_{Latitude}$=0.001, $p$=0.080),
-    while the proportion of intermediate consumers decreased towards the poles in all ecosystem types
-    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
-    $\beta_{Latitude:Lake}$=0.005, $p$=0.016).
-    The proportion of top predators in a food web, 
-    meanwhile, decreased towards the poles in lake and 
-    stream food webs but did not vary in other ecosystem
-    types ($\beta_{Latitude}$=0.002, $p$=0.151; 
-    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001; and
-    $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
-
-    % Does this need to be taken into account? Do I mention
-    % it later?
-    % All of these trends were robust to the removal of outliers.
-    % Was it? Do I even care?
-
 \subsection*{Appendix SX: Testing for effects of sampling effort}
@@
   \subsubsection*{Results}
+
+    The relationships between latitude and the proportions of species at each
+    trophic level were more complex than the flat relationship between latitude
+    and species richness in this dataset.  The proportion of basal resources
+    increased towards the poles in stream webs
+    ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
+    with latitude in estuarine, marine, lake, or terrestrial  food webs
+    ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
+    intermediate consumers decreased towards the poles in all ecosystem types
+    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
+    $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
+    in a food web,  meanwhile, decreased towards the poles in lake and  stream
+    food webs but did not vary in other ecosystem types
+    ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
+    $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
 

### 2015-08-27 code/byTL_Models.R

@@ -3,7 +3,6 @@
 library(nlrwr)
 library(lmerTest)
 library(MuMIn)
-library(bootstrap)
 
 infile='../non_TS/summary-properties.tsv'
 # infile='../mod_data/summary-properties.tsv'

### 2015-08-28 code/jackknife_display_figure.py
Prior to replacing authors with AU

@@ -1,0 +1,463 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+# import nose
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+#from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+
+def websbytype(datafile):
+  webtypedict={'terrestrial':[],'stream':[],'estuary':[],'lake':[],'marine':[]}
+
+  f=open(datafile)
+  for line in f:
+    if line.split()[1] in webtypedict:
+      web=line.split()[0]
+      # Because I didn't want webs missing a TL
+      if float(line.split()[15])>0 and float(line.split()[16])+float(line.split()[17])>0 and float(line.split()[18])>0:
+        webtypedict[line.split()[1]].append(line.split()[0])
+
+  return webtypedict
+
+
+def baselines(directory,prop):  # Get non-jackknifed parameters to make red dashed lines.
+  f=open('../non_TS/coefficients/'+prop+'_co.tsv','r')
+
+  basis={}
+
+  for line in f:
+    if line.split()[0]!='"Estimate"':
+      basis[line.split()[0]]=float(line.split()[1])
+
+  return basis
+
+# Jackknifing by webs
+def web_coefficient_zoo(directory,webfiles,prop):
+  weblist=[]
+
+  if prop in ['LS','Vul']:
+    betadict={'"(Intercept)"':{},'"log(Species)"':{},'"log(Species):Lakeweb"':{},
+              '"log(Species):Terr"':{},'"log(Species):Latitude"':{},'"log(Species):Lakeweb:Latitude"':{}}
+  elif prop=='Gen':
+    betadict={'"(Intercept)"':{},'"log(Species)"':{},'"log(Species):Lakeweb"':{},'"log(Species):Stream"':{},
[…]

### 2015-08-28 manuscript/supplement.tex
Fixed figures

@@
     \caption{Estimates of the coefficients in equation XX do not vary significantly
-    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
-    in the equation after the removal of each web in the dataset. All estimates are colour
+    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
+    in the equation after the removal of each web in the dataset. 
+    The estimate for the full, non-jackknifed
+    dataset is indicated by the red, dashed line. All estimates are colour
     coded according the ecosystem type of the removed web.}
@@
     \caption{Estimates of the coefficients in equation XX do not vary significantly
-    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
-    in the equation after the removal of each web in the dataset. All estimates are colour
+    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
+    in the equation after the removal of each web in the dataset. The estimate for the full, non-jackknifed
+    dataset is indicated by the red, dashed line. All estimates are colour
     coded according the ecosystem type of the removed web.}
@@
     \caption{Estimates of the coefficients in equation XX do not vary significantly
-    when jackknifing across food webs. We show the estimates (+/- 1SE) of each coefficient
-    in the equation after the removal of each web in the dataset. All estimates are colour
+    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
+    in the equation after the removal of each web in the dataset.  The estimate for the full, non-jackknifed 
+    dataset is indicated by the red, dashed line. All estimates are colour
     coded according the ecosystem type of the removed web.}
@@
     when jackknifing across authors of the published food webs used in this study. 
-    We show the estimates (+/- 1SE) of each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset.}
+    We show the estimates (with 95\% confidence intervals) of each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset.
+    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
     \label{LS_web}
@@
     when jackknifing across authors of the published food webs used in this study. 
-    We show the estimates (+/- 1SE) of each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset.}
+    We show the estimates (with 95\% confidence intervals) of each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset.
+    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
     \label{Gen_web}
@@
     when jackknifing across authors of the published food webs used in this study. 
-    We show the estimates (+/- 1SE) of each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset.}
+    We show the estimates (with 95\% confidence intervals) of each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset.
+    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
     \label{Vul_web}

### 2015-08-28 code/byTL_Models.R

@@ -82,7 +82,6 @@ by_TL=FALSE
   source('redundant_authors.R')
 
   # Calculate the base models.
-  source('recreate_with_subset.R')
 
   olddata=data
 
@@ -117,8 +116,9 @@ by_TL=FALSE
     }
   }
 
-
   data=olddata
+
+  source('recreate_with_subset.R')
 
   if(infile=='../mod_data/summary-properties.tsv'){
     outdir='../mod_data/'  } else {

### 2015-08-28 code/jackknife_display_figure.py

@@ -163,72 +163,72 @@ def web_jackknife_plotter(directory,webfiles,prop,datafile):
 
     if prop in ['LS','Vul']:
       if key=='"(Intercept)"' and prop=='LS':
-        graph.world.xmin=-.600001
-        graph.world.xmax=0
+        graph.world.xmin=-.700001
+        graph.world.xmax=.1
         major=.3
         labtext=labels[0]
       elif key=='"(Intercept)"' and prop=='Vul':
-        graph.world.xmin=-1.25
-        graph.world.xmax=-.75
-        major=.25
+        graph.world.xmin=-1.5
+        graph.world.xmax=-.5
+        major=.5
         labtext=labels[0]
       elif key=='"log(Species)"':
         graph.world.xmin=.49999999
-        graph.world.xmax=.75
+        graph.world.xmax=.8
         major=.1
         labtext=labels[1]
       elif key=='"log(Species):Latitude"':
-        graph.world.xmin=-.0025
-        graph.world.xmax=.0005
-        major=.001
+        graph.world.xmin=-.004
+        graph.world.xmax=.002
+        major=.002
         labtext=labels[2]
       elif key=='"log(Species):Lakeweb"':
-        graph.world.xmin=-.2
-        graph.world.xmax=0.05
-        major=.1
+        graph.world.xmin=-.3
+        graph.world.xmax=0.1
+        major=.15
         labtext=labels[3]
       elif key=='"log(Species):Terr"':
-        graph.world.xmin=-.1
-        graph.world.xmax=0
+        graph.world.xmin=-.1500001
+        graph.world.xmax=.02
         major=.05
         labtext=labels[4]
       else:
-        graph.world.xmin=0
+        graph.world.xmin=-.005
         graph.world.xmax=.01
         major=.005
         labtext=labels[5]
     elif prop=='Gen':
       if key in ['"log(Species):Lakeweb:Latitude"','"log(Species):Stream:Latitude"']:
         graph.world.xmin=0
-        graph.world.xmax=.01
+        graph.world.xmax=.015
         major=.005
         if key=='"log(Species):Lakeweb:Latitude"':
           labtext=labels[5]
         else:
           labtext=labels[6]
       elif key=='"(Intercept)"':
-        graph.world.xmax=-.3999999
-        graph.world.xmin=-.9
-        major=.2
+        graph.world.xmax=-.25
+        graph.world.xmin=-1.05
+        major=.3
         labtext=labels[0]
[…]

### 2015-08-28 manuscript/latitudepaper.tex
change roundup

@@
 \title{Specialisation in food webs scales with species richness but not with latitude}
-\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
-\date{\small$^1$School of Biological Sciences\\University of Canterbury\\
+\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
+\date{\small$^1$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
 Private Bag 4800\\Christchurch 8140, New Zealand \\
@@
 Life Science Centre, Dalhousie University\\1355 Oxford St., P0 BOX 15000\\
-Halifax NS, B3H 4R2, Canada\\
-\medskip$^3$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
-Private Bag 4800\\Christchurch 8140, New Zealand \\}
+Halifax NS, B3H 4R2, Canada\\}
 
@@
   If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
-  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927}) of species within food webs.
+  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927,Leibold2010}) of species within food webs.
   Specifically, narrower niches in the tropics would equate to
@@
   average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
-  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness. If this is
-  the case, it may still be possible to uncover effects of latitude on specialisation by examining the shape of the scaling 
-  relationship between specialisation and species richness over changing latitude. Here, we use three measures of specialisation:
-  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators).   By testing whether latitude affects the scaling of each property with
+  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness.
+
+  If this is the case, it may still be possible to uncover effects of latitude
+  on specialisation by examining the shape of the scaling  relationship
+  between specialisation and species richness over changing latitude. Here, we
+  use three measures of specialisation: mean links per species, mean
+  generality (number of prey), and mean vulnerability (number of predators).
+  By testing whether latitude affects the scaling of each property with
   species richness, we test for the effects of latitude on specialisation
@@
   the scaling of specialisation with species richness does not vary over
-  latitude, this will support the hypothesis that niches are similarly-sized
+  latitude, this will indicate that niches are similarly-sized
   worldwide but that there is a broader niche space in the tropics.
@@
   $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
-  Fig~\ref{props_v_lat}).For estuarine, marine, and terrestrial food webs the
+  Fig~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
@@
   ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
-  vulnerability did not vary with latitude (i.e., the interaction term $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
+  vulnerability did not vary with latitude (i.e., the interaction term 
+  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
 
@@
   This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
-  graduate scholarship (to ARC).
+  graduate scholarship (to ARC), as well as by a Rutherford XXXYYY (to DBS).
 
@@
 
+[[Need to find a spot to refer to the conceptual figure]]
 \begin{figure}[h]
-% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
+\centerline{\includegraphics*[width=.85\textwidth]{Figures/Other/conceptual_figure.eps}}
+\caption{In A) we show the known scaling relationship between link density (links per species, L/S) and 
+species richness. This scaling relationship is a power law and therefore linear in a log-log plot.
+In B) we show two versions of the latitudinal-niche breadth hypothesis that have been proposed to
+explain this gradient. Hypothesis 1 posits that greater environmental stability in the tropics will 
+allow species to evolve narrower niches (indicated by the grey trapezoid). Hypothesis 2 suggests that species
+will have constant niche sizes over latitude (indicated by the grey rectangle) but that
+greater primary productivity in the tropics creates a larger niche space (indicated by the 
+white trapezoid) such that each species still occupies a smaller proportion of the total niche
+space. These two hypotheses have different implications for the scaling of food-web properties
+such as the number of feeding links per species (L/S) with species richness. C) If hypothesis 1 is 
+true, then the exponent of the scaling relationship between link density and species richness should 
+be larger towards the poles, where each additional species in the food-web will have a larger niche 
+(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this
+distribution should not vary significantly over latitude.}
+\label{concept}
+\end{figure}
+
+\begin{figure}[h]
+\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
-relative to species richness and the proportions of basal resources (\% Basal), intermediate 
-consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
+relative to the species richness of a food web. Link density, generality,
 and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
 type. As these relationships take the form of power laws, we did this by dividing the food-web
-property (e.g. link density) by the predictor (e.g. \% Basal) raised to an exponent including the 
+property (e.g. link density) by species richness raised to an exponent including the 
 effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
+\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
 \caption{Changes to the scaling of link density with species richness across ecosystem
@@
 
-\begin{figure}[h]
-% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
-\caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
-consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
-we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
-on N=166 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
-The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
-proportion was very similar to those of the scaling relationships with link density, except for the 
-scaling of generality with the proportion of top predators where there was no effect of latitude on the 
-size of the exponent in any ecosystem type. See Figs.~\emph{S3-S5, Appendix 5} for all scaling relationships.}
-\label{BIT}
-\end{figure}
+% \begin{figure}[h]
+% % \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
+% \caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
+% consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
+% we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
+% on N=166 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
+% The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
+% proportion was very similar to those of the scaling relationships with link density, except for the 
+% scaling of generality with the proportion of top predators where there was no effect of latitude on the 
+% size of the exponent in any ecosystem type. See Figs.~\emph{S3-S5, Appendix 5} for all scaling relationships.}
+% \label{BIT}
+% \end{figure}
 

### 2015-08-28 code/TL_observedfits.py

@@ -38,11 +38,11 @@ def datareader(rawdatafile,TL,Bformat):
       GenSD=float(line.split('\t')[10])
       Vul=float(line.split('\t')[11])
       VulSD=float(line.split('\t')[12])
-      B=float(line.split('\t')[-4])
-      H=float(line.split('\t')[-3])
-      I=float(line.split('\t')[-2])
+      B=float(line.split('\t')[15])
+      H=float(line.split('\t')[16])
+      I=float(line.split('\t')[17])
       I=I+H # Include the herbivores as intermediates
-      T=float(line.split('\t')[-1])
+      T=float(line.split('\t')[18])
 
       for response in ['LS','Gen','Vul']:
         points[response].append((eval(TL),eval(response)))
@@ -79,7 +79,6 @@ def heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat):
     key='Toppreds'
   else:
     key='Species'
-
   f=open(rawdatafile,'r')
   for line in f:
     # print line.split()
@@ -92,11 +91,11 @@ def heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat):
       LS=float(line.split('\t')[7])
       Gen=float(line.split('\t')[9])
       Vul=float(line.split('\t')[11])
-      B=float(line.split('\t')[-4])
-      H=float(line.split('\t')[-3])
-      I=float(line.split('\t')[-2])
+      B=float(line.split('\t')[15])
+      H=float(line.split('\t')[16])
+      I=float(line.split('\t')[17])
       I=H+I
-      T=float(line.split('\t')[-1])
+      T=float(line.split('\t')[18])
 
       # Correct the observed property based on latitude and ecotype effects
 
@@ -120,7 +119,6 @@ def heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat):
       if B>0 and I>0 and T>0:
         correction=eval(TL)**exponent
         y=float(Decimal(eval(prop))/Decimal(correction))
-
         obs[ecotype].append((eval(TL),y))
   f.close()
 
@@ -204,22 +202,173 @@ def predictionlines(fixed,prop,TL):
 
   return ecoline
 
-def scaleplots(rawdatafile,outfile,Bformat,predfolder):
+def S_scaleplots(rawdatafile,outfile1,Bformat,predfolder):
+
[…]

### 2015-08-28 manuscript/latitudepaper.tex
Removed fancy citations for Vancouver style

@@
 %\usepackage{overcite}
-\usepackage[round]{natbib}
+% \usepackage[round]{natbib}
 
@@
   several decades to summarise the structure of  ecological
-  communities~\citep{Paine1966,Williams2000,Petchey2008} and to understand how
+  communities~\cite{Paine1966,Williams2000,Petchey2008} and to understand how
   that structure relates to environmental variables  such as habitat
-  type~\citep{Briand1983,Shurin2006}, primary
-  productivity~\citep{Townsend1998,Thompson2005a,Vermaat2009}, and
-  climate~\citep{Petchey2010,Baiser2012}. The latter variables in turn have
+  type~\cite{Briand1983,Shurin2006}, primary
+  productivity~\cite{Townsend1998,Thompson2005a,Vermaat2009}, and
+  climate~\cite{Petchey2010,Baiser2012}. The latter variables in turn have
   strong gradients over latitude, with productivity and temperature both being
   higher in the tropics while  climate is more variable at high
-  latitudes~\citep{Field1998}. These variables affect both the resources
+  latitudes~\cite{Field1998}. These variables affect both the resources
   available and species'
-  metabolisms~\citep{White2007,OConnor2009,Hechinger2011,White2011}, and have
+  metabolisms~\cite{White2007,OConnor2009,Hechinger2011,White2011}, and have
   been proposed as determinants of the strength of  interspecific
-  interactions~\citep{Schemske2009,Lang2012,Schleuning2012}.  By modulating
+  interactions~\cite{Schemske2009,Lang2012,Schleuning2012}.  By modulating
   interactions between species, latitudinal gradients may also shape food-web
@@
   richness, one of the most general and robust patterns in
-  ecology~\citep{Kaufman1995,Macpherson2002,Schemske2009}.
+  ecology~\cite{Kaufman1995,Macpherson2002,Schemske2009}.
 
   % These gradients, together with the strength and generality of associations between biological processes and environmental variables, suggest that variation in network structure 
-  % may also be explained by ecological gradients \citep{Baiser2012}.
+  % may also be explained by ecological gradients \cite{Baiser2012}.
 
-  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\citep{Vazquez2004}. 
+  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\cite{Vazquez2004}. 
   This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
-  turn should evolve smaller niches~\citep{Vazquez2004}. These narrow niches should therefore allow more species to 
-  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics~\citep{Brown2004}
-  may result in a broader niche space~\citep{Davies2007} which could also sustain greater biodiversity even if niche 
+  turn should evolve smaller niches~\cite{Vazquez2004}. These narrow niches should therefore allow more species to 
+  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics~\cite{Brown2004}
+  may result in a broader niche space~\cite{Davies2007} which could also sustain greater biodiversity even if niche 
   sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocally 
-  supported~\citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
-  richness~\citep{Lappalainen2006,Krasnov2008,Slove2010}.
+  supported~\cite{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
+  richness~\cite{Lappalainen2006,Krasnov2008,Slove2010}.
 
   If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
-  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927,Leibold2010}) of species within food webs.
+  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\cite{Elton1927,Leibold2010}) of species within food webs.
   Specifically, narrower niches in the tropics would equate to
@@
   Attempts to unravel these effects, however,
-  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
+  are complicated by known relationships between species richness and many other network properties~\cite{Riede2010}. 
   For example,
-  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\citealp{Marra1997,Dyer2007};
-  but see~\citealp{Schleuning2012}). However,
-  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
+  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\cite{Marra1997,Dyer2007};
+  but see~\cite{Schleuning2012}). However,
+  average numbers of links per species tend to increase in larger food webs~\cite{Dunne2006,Riede2010}. This means
   that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness.
@@
     possible or, where study sites were described but exact coordinates were not
-    given, obtained estimated coordinates using Google Earth~\citep{GoogleEarth}.
+    given, obtained estimated coordinates using Google Earth~\cite{GoogleEarth}.
     We then divided the species in each web into basal resources (those species with
@@
     N=28; estuarine, N=18; and terrestrial, N=31) according to their designation in 
-    previous aggregations of food webs (i.e.,~\citet{GlobalWeb,Riede2011,Dunne2013}).
+    previous aggregations of food webs (i.e.,~\cite{GlobalWeb,Riede2011,Dunne2013}).
 
@@
     Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
-    sets to form ``trophic species'' webs ~\citep{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
+    sets to form ``trophic species'' webs ~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
     is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
@@
     of the maximal model as well as the AIC's of a suite of candidate simplified models identified
-    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
+    using the R~\cite{R} function dredge from package MuMIn~\cite{MuMIn}. 
     Simplified models were obtained by
@@
     The scaling relationship between link density ($Z$) and species richness ($S$)
-    has been shown to be a power law~\citep{Riede2010} of the form
+    has been shown to be a power law~\cite{Riede2010} of the form
 
@@
     distributions, neither of which has strong
-    \emph{a priori} justification in our dataset, we followed the recommendations in~\citet{Xiao2011}
+    \emph{a priori} justification in our dataset, we followed the recommendations in~\cite{Xiao2011}
     to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
@@
     maximal model as well as the AIC's of a suite of candidate simplified
-    models identified using the R~\citep{R} function dredge from package
-    MuMIn~\citep{MuMIn}.  Simplified models were obtained by systematically
+    models identified using the R~\cite{R} function dredge from package
+    MuMIn~\cite{MuMIn}.  Simplified models were obtained by systematically
     removing all possible combinations  of terms from the full model with the
@@
   The tendency of food-web structure to exhibit scaling relationships with
-  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
+  species richness has been well-established~\cite{Dunne2004,Riede2010}. As
   species richness in particular is also known to vary systematically over
-  latitude~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009},
+  latitude~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009},
   intuitively one might suspect that any relationship between food-web
@@
   contrasts strongly with other
-  studies~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. As
+  studies~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. As
   numbers of species and links included in a food web vary strongly with
@@
   richness are generally measured for a single taxonomic group at a
-  time~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is possible
+  time~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is possible
   that these taxa are not well-represented in our food webs and that the
@@
   systematically with temperature and productivity but that the niche space
-  might be larger in species-rich communities~\citep{Davies2007}. Rather than
+  might be larger in species-rich communities~\cite{Davies2007}. Rather than
   niche space depending on temperature and productivity, it may be that species
   diversity itself affects the niche space available to species (although climate
-  may affect speciation rates and therefore the diversity in a region~\citep{Currie2004}). 
+  may affect speciation rates and therefore the diversity in a region~\cite{Currie2004}). 
   For example, as the plant diversity of a community increases both the 
@@
   in high-latitude lakes. These trends are consistent with the hypothesis that
-  greater stability in the tropics leads to narrower niches~\citep{Vazquez2004}
+  greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
   and a higher proportion of specialists. This may be partly due to high-latitude 
   species tending to switch between different seasonally-available 
-  prey~\citep{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
+  prey~\cite{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
   freshwater ecosystems may have more stable composition.
@@
   streams tend to be more generalist than their low-latitude
-  equivalents~\citep{Winemiller2008}, perhaps due to prey-switching during
-  seasonal food shortages~\citep{Magalhaes1993}. More generally, the lack of
+  equivalents~\cite{Winemiller2008}, perhaps due to prey-switching during
+  seasonal food shortages~\cite{Magalhaes1993}. More generally, the lack of
   correspondence between the scaling of food-web properties with species
@@
   the size and trophic breakdowns of a community can each provide different
-  information~\citep{Downing2002}.
+  information~\cite{Downing2002}.
 
@@
   goes some way towards explaining the equivocal support for the opposing
-  hypotheses of narrower niches in the tropics~\citep{Vazquez2004} and broader
-  niche space in the tropics~\citep{Davies2007}; both have merit but appear to
+  hypotheses of narrower niches in the tropics~\cite{Vazquez2004} and broader
+  niche space in the tropics~\cite{Davies2007}; both have merit but appear to
   apply to different systems.
@@
   Food webs used in this study were retrieved from the University of Canberra's 
-  GlobalWeb database (\citealp{GlobalWeb}; \emph{www.globalwebdb.com}) and from
-  two papers (\citealp{Riede2011}; \emph{http://dx.doi.org/10.1111/j.1461-0248.2010.01568.x}
-  and \citealp{Dunne2013}; \emph{http://dx.doi.org/10.1371/journal.pbio.1001579}). Original sources for the
+  GlobalWeb database (\cite{GlobalWeb}; \emph{www.globalwebdb.com}) and from
+  two papers (\cite{Riede2011}; \emph{http://dx.doi.org/10.1111/j.1461-0248.2010.01568.x}
+  and \cite{Dunne2013}; \emph{http://dx.doi.org/10.1371/journal.pbio.1001579}). Original sources for the
   food webs are given in \emph{Appendix S1}.
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[width=.85\textwidth]{Figures/Other/conceptual_figure.eps}}
+\centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
 \caption{In A) we show the known scaling relationship between link density (links per species, L/S) and 
@@
 be larger towards the poles, where each additional species in the food-web will have a larger niche 
-(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this
-distribution should not vary significantly over latitude.}
+(i.e., more feeding links). If hypothesis 2 is true, then the exponent of thisdistribution should not vary significantly over latitude.}
 \label{concept}
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
+\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
 \caption{Changes to the scaling of link density with species richness across ecosystem

### 2015-08-28 code/TL_marginal_latitude.py
One last thing

@@ -441,6 +441,7 @@ def main():
 
   form="proportions"
   TL='S'
+  prop="LS"
 
   Sgrace=MultiPanelGrace(colors=ColorBrewerScheme('Greys'))
 
@@ -448,34 +449,33 @@ def main():
 
   Sgrace.add_label_scheme('dummy',Snames)
   Sgrace.set_label_scheme('dummy')
+  
+  for ecotype in ecotypes:   
+    if ecotype=='Estuary':
+      typ='Estuarine'
+    elif ecotype=='Marine':
+      typ='Marine'
+    elif ecotype=='Lake':
+      typ='Lake'
+    elif ecotype=='Stream':
+      typ='Stream'
+    else:
+      typ='Terrestrial'
 
-  for ecotype in ecotypes[:3]:   
-    for prop in ['LS','Gen','Vul']:  
-      if ecotype=='Estuary':
-        typ='Estuarine'
-      elif ecotype=='Marine':
-        typ='Marine'
-      elif ecotype=='Lake':
-        typ='Lake'
-      elif ecotype=='Stream':
-        typ='Stream'
-      else:
-        typ='Terrestrial'
+    graph=Sgrace.add_graph(Panel)
 
-      graph=Sgrace.add_graph(Panel)
+    plotter(prop,TL,ecotype,graph,form)
+    graph.xaxis.label.configure(text='Absolute latitude',place='opposite',just=2,char_size=.65)
+    graph.panel_label.configure(char_size=.75,placement='iul',dy=.02,dx=.03)
 
-      plotter(prop,TL,ecotype,graph,form)
-      # graph.xaxis.label.configure(text='Absolute latitude',place='opposite',just=2,char_size=.65)
-      # graph.panel_label.configure(char_size=.75,placement='iul',dy=.02,dx=.03)
-
-  Sgrace.multi(rows=3,cols=3,vgap=.04,hgap=.04)
+  Sgrace.multi(rows=5,cols=1,vgap=.04,hgap=.04)
 
   Sgrace.hide_redundant_xticklabels()
   Sgrace.hide_redundant_yticklabels()
   Sgrace.hide_redundant_labels()
 
-  # Sgrace.set_col_yaxislabel(col=0,rowspan=(0,4),label='Scaling exponent of link density with species richness',place='normal',just=2,char_size=1,perpendicular_offset=0.07)
[…]

### 2015-09-01 manuscript/AC-reply-to-referees.tex

@@
   1) Network terminology and methods might be inaccessible to researchers
-  withoout network background.
+  without network background.
 
@@
 
-    \subsection*{Gradients over latitude}
+    \textbf{Gradients over latitude}
 
@@
 
-  \textbf{R:} [[Sure fine whatever]]
+  \textbf{R:} The top predators were indeed included in this figure (we suspect that the reviewer
+  may have experienced a printing error), but as we have followed the reviewer's earlier
+  suggestion and moved the by-trophic-level analysis to the supplemental information this becomes
+  a moot point. We have slightly modified the y-axis on the new version of this figure and feel that
+  it is now much clearer.
 
@@
 
-  \textbf{R:} [[That's going to be ugly]]
+  \textbf{R:} We have followed the reviewer's suggestion.
 

### 2015-09-02 manuscript/latitudepaper.tex
Tried to throw something together about freshwaters

@@
 
-\title{Specialisation in food webs scales with species richness but not with latitude}
+\title{Latitudinal gradients in niche breadth vary across ecosystem types.}
 \author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
@@
   species richness. In this dataset, however, we did not find overall
-  latitudinal gradients in species richness, links per species,generality,
-  vulnerability, or the proportions of food webs accounted for by basal
-  resources, intermediate consumers, and top predators, except in lake and
-  stream food webs where the proportions of top predators tended to decrease
-  towards the poles  (see \emph{Appendix S3} for details).
+  latitudinal gradients in species richness, links per species, generality, or
+  vulnerability.
+  % , or the proportions of food webs accounted for by basal
+  % resources, intermediate consumers, and top predators, except in lake and
+  % stream food webs where the proportions of top predators tended to decrease
+  % towards the poles  (see \emph{Appendix S3} for details).
 
@@
   studies. This could result in food webs describing species-rich tropical
-  communities omitting more species and links than species-poor arctic
+  communities omitting more species and links than studies of species-poor arctic
   communities. In addition, it is worth noting that gradients in species
@@
   dominant taxa in them do not have an underlying latitudinal gradient in
-  richness.In either case, the lack of a strong association between species
+  richness. In either case, the lack of a strong association between species
   richness and latitude in any ecosystem type means that any effect of
@@
   greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
-  and a higher proportion of specialists. This may be partly due to high-latitude 
-  species tending to switch between different seasonally-available 
-  prey~\cite{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
-  freshwater ecosystems may have more stable composition.
+  and a higher proportion of specialists. That freshwater food webs supported
+  the hypothesis of narrower niches in the tropics, while other ecosystem types
+  did not, is particularly exciting given that these ecosystems (especially streams)
+  are known for being highly variable and that seasonal variability is one of the
+  proposed drivers of the latitude-niche breadth hypothesis~\cite{Vazquez2004}.
 
-  The scaling of link density, generality and vulnerability with proportions
-  of species at different trophic levels, however, did not differ between
-  lakes and most other food webs. Indeed, there was comparatively little
-  variation in scaling with the trophic-level breakdown of a web across
-  ecosystem types. Nevertheless, the negative relationships between the
-  proportion of top predators in a web and link density and vulnerability were
-  weaker (i.e., the scaling exponent was more strongly negative) in low-latitude 
-  stream ecosystems. This may imply that top predators in high-latitude 
-  streams tend to be more generalist than their low-latitude
-  equivalents~\cite{Winemiller2008}, perhaps due to prey-switching during
-  seasonal food shortages~\cite{Magalhaes1993}. More generally, the lack of
-  correspondence between the scaling of food-web properties with species
-  richness and with proportions of species at each trophic level suggests that
-  the size and trophic breakdowns of a community can each provide different
-  information~\cite{Downing2002}.
+  Both streams and lakes can experience severe changes in water temperature and volume
+  (e.g., floods, drying, freezing) that remove food or other resources (notably oxygen
+  during freezing events~\cite{})~\cite{Winterbourn1997, one for lakes}. These events
+  are often linked to seasonal events such as snowmelts (although not always-- New Zealand
+  streams are a notable exception~\cite{Winterbourn1997}). Further, both temperate streams 
+  and lakes tend to experience seasonal strong pulses of allochthonous inputs (e.g., fallen leaves, 
+  terrestrial invertebrates~\cite{Nakano2001,Zeng2008,}; again New Zealand streams are an
+  exception to this trend~\cite{Winterbourn1997}). These trends combined mean that,
+  relative to larger, more abiotically stable estuarine and marine communities, freshwater
+  food webs may experience high turnover in both community composition and productivity.
+  Even in New Zealand streams, which experience unpredictable flooding and do not typically
+  receive seasonal allochthonous subsidies, more frequent disturbance is associated with lower
+  diversity and density of insect larvae, and lower species richness~\cite{Winterbourn1997}.
+
+  High variation in the abundances of different resources could select for more generalist consumers
+  in temperature freshwater communities, as seen in our dataset. In this case the non-seasonality of
+  New Zealand streams, which account for 31/71 of the stream webs in our dataset, supports this
+  hypothesis as the New Zealand stream fauna are known to be ecological generalists,
+  probably as a result of variability of their habitat~\cite{Winterbourn1997}. In other freshwater
+  communities the sequence of available resources might be more predictable, but the ability to 
+  switch between different prey is not likely to be less important. Importantly, while terrestrial
+  communities are also strongly seasonal at high latitudes, and can also obtain significant allochthonous
+  inputs~\cite{Nakano2001}, terrestrial consumers tend to be more morphologically specialized for
+  feeding on particular prey~\cite{Liem1990}. This means that primarily gape-limited aquatic consumers
+  tend to be more general across all types of aquatic habitats~\cite{Liem1990,Shurin2006}.
+  The key to this this explanation of the differences between freshwater and marine and estuarine 
+  ecosystems is whether the former experience more severe seasonal variation. Although we are not
+  aware of any study explicitly comparing seasonal variation in freshwater and saltwater or brackish
+  food webs in a similar location, we believe that freshwater ecosystems are indeed likely to 
+  experience more severe changes because of their small size. While oceans and estuaries certainly
+  do vary in terms of water temperature and nutrients over the course of a year~\cite{}, because they
+  are not isolated in the midst of a terrestrial matrix these changes are buffered. Further, estuaries
+  and especially marine environments do not typically freeze over or dry up completely-- these dramatic
+  changes are unique to freshwater communities.
+
+  % This may be partly due to high-latitude 
+  % species tending to switch between different seasonally-available 
+  % prey~\cite{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
+  % freshwater ecosystems may have more stable composition.
+
+  % The scaling of link density, generality and vulnerability with proportions
+  % of species at different trophic levels, however, did not differ between
+  % lakes and most other food webs. Indeed, there was comparatively little
+  % variation in scaling with the trophic-level breakdown of a web across
+  % ecosystem types. Nevertheless, the negative relationships between the
+  % proportion of top predators in a web and link density and vulnerability were
+  % weaker (i.e., the scaling exponent was more strongly negative) in low-latitude 
+  % stream ecosystems. This may imply that top predators in high-latitude 
+  % streams tend to be more generalist than their low-latitude
+  % equivalents~\cite{Winemiller2008}, perhaps due to prey-switching during
+  % seasonal food shortages~\cite{Magalhaes1993}. More generally, the lack of
+  % correspondence between the scaling of food-web properties with species
+  % richness and with proportions of species at each trophic level suggests that
+  % the size and trophic breakdowns of a community can each provide different
+  % information~\cite{Downing2002}.
 
@@
   We thank members of the Romanuk, Stouffer, and Tylianakis labs for their comments on
-  the manuscript.
+  the manuscript. We also thank Angus McIntosh for valuable discussion on stream food webs.
 
@@
   This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
-  graduate scholarship (to ARC), as well as by a Rutherford XXXYYY (to DBS).
+  graduate scholarship (to ARC), a Rutherford XXXYYY (to DBS), and an NSERC Discovery Grant to TNR.
 
+1
 \newpage

### 2015-09-02 code/byTL_Models.R
Still need to figure out how to align axes, redo once jackknife has finished

@@ -63,20 +63,21 @@ by_TL=FALSE
 
 
   # # Check for redundant authors
-  # auths=as.data.frame(data[,20:188])
+  # auths=as.data.frame(data[,20:185])
   # for(col1 in colnames(auths)){
   #   duplicates=c(col1)
   #   for(col2 in colnames(auths)){
   #     v1=as.vector(auths[,col1])
   #     v2=as.vector(auths[,col2])
-  #     if(cor(v1,v2)==1){
-  #       duplicates=union(duplicates,c(col2))
-  #     }
+  #     if(sum(v1)>0 && sum(v2)>0){
+  #       if(cor(v1,v2)==1){
+  #         duplicates=union(duplicates,c(col2))
+  #       }
   #   }
   #   if(length(duplicates)>1){
   #   print(duplicates)
   #   }
-  # }
+  # }}
 
   # Eliminate the redundant authors for jacknifing.
   source('redundant_authors.R')
@@ -101,11 +102,21 @@ by_TL=FALSE
 
   # Jackknifing by authors (slightly harder)
 
+  removals=matrix(nrow=50,ncol=2,data=NA)
+
   # If an author is only on one web, then I've already checked that in the webwise version :)
-  for(i in 20:189){
+  j=1
+  for(i in 20:185){
     if(sum(olddata[,i])>1){
       newdata=olddata[which(olddata[,i]==0),]
       name=colnames(olddata)[i]
+
+      removed=dim(olddata)[1]-dim(newdata)[1]
+      removals[j,1]=name
+      removals[j,2]=removed
+
+      print(c(name,removed,j))
+      j=j+1
 
       data=newdata
       source('recreate_with_subset.R')
@@ -116,6 +127,7 @@ by_TL=FALSE
     }
   }
 
+  write.table(removals,file='../Jackknifed/webs_per_author.tsv',sep='\t')
   data=olddata
 
   source('recreate_with_subset.R')

### 2015-09-02 code/byauthor_jacknife_setup.py

@@ -75,7 +75,7 @@ def duplicate_surnames(sur,auth):
 		surname='de_Morais'
 	elif sur==u'van Oevelen':
 		surname='van_Oevelen'
-	elif sur==u'{38 coauthors}':
+	elif sur in [u'{38 coauthors}','Coauthors']:
 		surname='38_coauthors'
 	elif sur==u'{Ali Dawah}':
 		surname='Ali_Dawah'
@@ -97,7 +97,10 @@ def duplicate_surnames(sur,auth):
 		surname='Chavez'
 	elif 'Patr' in sur and 'cio' in sur:
 		surname='Patricio'
-
+	elif sur in ['McLaughlin','Mclaughlin']:
+		surname='McLaughlin'
+	elif 'Silander' in sur:
+		surname='Silander'
 
 
 	# Surprisingly, Joseph J. Torres and Jose J. Torres seem to be the same person.

### 2015-09-02 code/jackknife_display_figure.py

@@ -82,25 +82,38 @@ def author_coefficient_zoo(directory,authorfiles,prop):
         betadict[line.split()[0]][web]=(float(line.split()[1]),float(line.split()[2]))
   return betadict, weblist
 
+
+def removalcounter(removalfile):
+  removals={}
+  f=open(removalfile,'r')
+  for line in f:
+    if len(line.split())==3:
+      author=line.split()[1][1:-1]
+      removed=int(line.split()[2][1:-1])
+      removals[author]=removed
+  f.close()
+  return removals
+
+
 def utilities(prop):
   if prop in ['LS','Vul']:
     labels=[\
-    LatexString(r"Intercept\n  "), \
-    LatexString(r"Species\n  "), \
-    LatexString(r"Species:\nLatitude"), \
-    LatexString(r"Species:\nLake"), \
-    LatexString(r"Species:\nTerrestrial"), \
-    LatexString(r"Species:\nLake:Latitude")]
+    LatexString(r"\f{Symbol}a\f{}"), \
+    LatexString(r"\f{Symbol}b\f{}\s0\s"), \
+    LatexString(r"\f{Symbol}b\f{}\s1\s"), \
+    LatexString(r"\f{Symbol}b\f{}\s2, E = Lake\s"), \
+    LatexString(r"\f{Symbol}b\f{}\s2, E = Terrestrial\s"), \
+    LatexString(r"\f{Symbol}b\f{}\s3, E = Lake\s")]
     keylist=['"(Intercept)"','"log(Species)"','"log(Species):Latitude"','"log(Species):Lakeweb"','"log(Species):Terr"','"log(Species):Lakeweb:Latitude"']
   elif prop=='Gen':
     labels=[\
-      LatexString(r"Intercept\n  "), \
-      LatexString(r"Species\n  "), \
-      LatexString(r"Species:\nLatitude"), \
-      LatexString(r"Species:\nLake"), \
-      LatexString(r"Species:\nStream"), \
-      LatexString(r"Species:\nLake:Latitude"), \
-      LatexString(r"Species:\nStream:Latitude")]
+    LatexString(r"\f{Symbol}a\f{}"), \
+    LatexString(r"\f{Symbol}b\f{}\s0\s"), \
+    LatexString(r"\f{Symbol}b\f{}\s1\s"), \
+    LatexString(r"\f{Symbol}b\f{}\s2, E = Lake\s"), \
[…]

### 2015-09-02 code/redundant_authors.R

@@ -31,12 +31,14 @@
 
 # Redundant with Aloisio
   data$Carvalho <- NULL
+  data$Aloisio <- NULL # Only helped with one web, it had no intermediates or herbs.
 
 # Redundant with Althaus
   data$Bax <- NULL
   data$Bulman <- NULL
   data$He <- NULL
   data$Williams_A <- NULL
+  data$Althaus <- NULL # No intermediates here either.
 
 # Redundant with Amundsen
   data$Klemetsen <- NULL

### 2015-09-02 manuscript/latitudepaper.tex
Small changes

@@
   on specialisation by examining the shape of the scaling  relationship
-  between specialisation and species richness over changing latitude. Here, we
+  between specialisation and species richness over changing latitude. As
+  food webs describing different ecosystem types may differ both in their
+  food-web structure~\cite{Dunne2004,Shurin2006} and in the extent to [[seasonal
+  variation? Latitudinal gradients in S? Productivity? whatnow?]], we also included
+  ecosystem type as a covariate.   Here, we
   use three measures of specialisation: mean links per species, mean
@@
   implied by the ``latitude-niche breadth hypothesis''. If the scaling of
-  specialisation with species richness is weaker at the tropics (i.e., if
+  specialisation with species richness is weaker in the tropics (i.e., if
   species gain fewer links, predators, or prey as the size of the network

### 2015-09-02 manuscript/latitudepaper.tex
DBS comments

@@
 
-\title{Latitudinal gradients in niche breadth vary across ecosystem types.}
+\title{Latitudinal gradients in biotic niche breadth vary across ecosystem types.}
 \author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
@@
   greater productivity would translate to constant specialisation and niche
-  width across latitude.
+  width across latitude (Fig.~\ref{concept}).
   Attempts to unravel these effects, however,
@@
   on specialisation by examining the shape of the scaling  relationship
-  between specialisation and species richness over changing latitude. As
-  food webs describing different ecosystem types may differ both in their
-  food-web structure~\cite{Dunne2004,Shurin2006} and in the extent to [[seasonal
-  variation? Latitudinal gradients in S? Productivity? whatnow?]], we also included
-  ecosystem type as a covariate.   Here, we
-  use three measures of specialisation: mean links per species, mean
-  generality (number of prey), and mean vulnerability (number of predators).
+  between specialisation and species richness over changing latitude. 
   By testing whether latitude affects the scaling of each property with
   species richness, we test for the effects of latitude on specialisation
-  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
-  specialisation with species richness is weaker in the tropics (i.e., if
-  species gain fewer links, predators, or prey as the size of the network
-  increases), this will indicate narrower niches at the tropics. If, however,
-  the scaling of specialisation with species richness does not vary over
-  latitude, this will indicate that niches are similarly-sized
+  implied by the ``latitude-niche breadth hypothesis'' (Fig.~\ref{concept}). 
+  If the scaling of specialisation with species richness is weaker in the 
+  tropics (i.e., if species gain fewer links, predators, or prey as the size 
+  of the network increases), this will indicate narrower niches at the tropics. 
+  If, however, the scaling of specialisation with species richness does not 
+  vary over latitude, this will indicate that niches are similarly-sized
   worldwide but that there is a broader niche space in the tropics.
+  Additionally, as food webs describing different ecosystem types may differ
+  in their topology~\cite{Dunne2004,Shurin2006} and may be subject to different
+  latitudinal gradients in species richness~\cite{} or productivity~\cite{},
+  we also explored the differences in scaling relationships across ecosystem types.
+  Here, we use three measures of specialisation; mean links per species, mean
+  generality (number of prey), and mean vulnerability (number of predators).
 
@@
 
-  \subsection*{Gradients over latitude}
+  \subsection*{Gradients over Latitude}
 
@@
     marine, lake, and terrestrial networks with estuarine
-    networks providing the intercept) and $\epsilon_{i}$ is a residual error term. 
+    networks corresponding to $E_{i}=0$) and $\epsilon_{i}$ is a residual error term. 
     We next calculated the AIC
@@
     The best-fitting model was then determined to be the model with the fewest terms 
-    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
-    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
-    model.
+    where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
 
-  \subsection*{Scaling Relationships with S}
+  \subsection*{Scaling Relationships with Species Richness}
 
@@
     models identified using the R~\cite{R} function dredge from package
-    MuMIn~\cite{MuMIn}.  Simplified models were obtained by systematically
-    removing all possible combinations  of terms from the full model with the
-    restriction that species richness was retained in all reduced models. The
-    best-fitting model was then determined to be the model with the fewest
-    terms  where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
-    As a supplemental check to ensure that variation in sampling effor across
-    food webs was not responsible for the trends we observed, we then repeated
-    our analyses using jackknifed data sets in which we 1) sequentially removed
-    each food web in the dataset and 2) sequentially removed sets of food webs 
-    associated with each author of the food webs in the dataset. Parameter 
-    estimates varied very little across either series of jackknifes (\emph{Appendix SXX}).
+    MuMIn~\cite{MuMIn}.  Simplified models were obtained by using the same
+    procedure as described above. Parameter estimates for the simplified models
+    varied very little across either series of jackknifes (\emph{Appendix S3}).
     % If several models shared the fewest

### 2015-09-02 manuscript/supplement.tex
change roundup
DBS comments

@@
 % \begin{landscape}
+
 \subsection*{Appendix S1: Details of food web sources and selection}
@@
 
-\subsection*{Appendix SX: Testing for effects of sampling effort}
+\subsection*{Appendix S3: Testing for effects of sampling effort}
 
@@
     \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_web.eps}}
-    \caption{Estimates of the coefficients in equation XX do not vary significantly
-    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
-    in the equation after the removal of each web in the dataset. 
-    The estimate for the full, non-jackknifed
-    dataset is indicated by the red, dashed line. All estimates are colour
-    coded according the ecosystem type of the removed web.}
+    \caption{Estimates of the coefficients for scaling of link density with species richness
+    in equation 5 (main text) do not vary significantly when jackknifing across food webs. 
+    We show the pseudovalues for each coefficient in the equation after the removal of each 
+    web in the dataset. The estimate for the full, non-jackknifed dataset is indicated by 
+    the red, dashed line.}
     \label{LS_web}
@@
     \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_web.eps}}
-    \caption{Estimates of the coefficients in equation XX do not vary significantly
-    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
+    \caption{Estimates of the coefficients for scaling of generality with species richness
+    (see equation 5, main text) do not vary significantly
+    when jackknifing across food webs. We show the pseudovalues for each coefficient
     in the equation after the removal of each web in the dataset. The estimate for the full, non-jackknifed
-    dataset is indicated by the red, dashed line. All estimates are colour
-    coded according the ecosystem type of the removed web.}
+    dataset is indicated by the red, dashed line. }
     \label{Gen_web}
@@
     \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_web.eps}}
-    \caption{Estimates of the coefficients in equation XX do not vary significantly
-    when jackknifing across food webs. We show the estimates (with 95\% confidence intervals) of each coefficient
+    \caption{Estimates of the coefficients for scaling of vulnerability with species richness
+    (see equation 5, main text) do not vary significantly
+    when jackknifing across food webs. We show the pseudovalues for each coefficient
     in the equation after the removal of each web in the dataset.  The estimate for the full, non-jackknifed 
-    dataset is indicated by the red, dashed line. All estimates are colour
-    coded according the ecosystem type of the removed web.}
+    dataset is indicated by the red, dashed line.}
     \label{Vul_web}
@@
     \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_author.eps}}
-    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    \caption{Estimates of the coefficients for scaling of link density with species richness
+    in equation 5 (main text) do not vary significantly
     when jackknifing across authors of the published food webs used in this study. 
-    We show the estimates (with 95\% confidence intervals) of each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset.
+    We show the pseudovalues for each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset. Authors
+    who compiled only a single web were jackknifed as part of the by-web jackknife.
     The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
@@
     \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_author.eps}}
-    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    \caption{Estimates of the coefficients for scaling of generality with species richness
+    (see equation 5, main text) do not vary significantly
     when jackknifing across authors of the published food webs used in this study. 
-    We show the estimates (with 95\% confidence intervals) of each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset.
+    We show the pseudovalues for each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset. Authors
+    who compiled only a single web were jackknifed as part of the by-web jackknife.
     The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
@@
     \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_author.eps}}
-    \caption{Estimates of the coefficients in equation XX do not vary significantly
+    \caption{Estimates of the coefficients for the scaling of vulnerability with species richness
+    (see equation 5, main text) do not vary significantly
     when jackknifing across authors of the published food webs used in this study. 
-    We show the estimates (with 95\% confidence intervals) of each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset.
+    We show the pseudovalues for each coefficient
+    in the equation after the removal of all webs compiled by each author in the dataset. Authors
+    who compiled only a single web were jackknifed as part of the by-web jackknife.
     The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}

### 2015-09-03 manuscript/supplement.tex
Last chance before expunging by-TL analysis

@@
 
-  We combined published food webs from~\citet{GlobalWeb},~\citet{Riede2011},
-  and~\citet{Dunne2013}. Of the 358 food webs available
-  from~\citet{GlobalWeb}, 59 were rejected because their original source was
+  We combined published food webs from~\cite{GlobalWeb},~\cite{Riede2011},
+  and~\cite{Dunne2013}. Of the 358 food webs available
+  from~\cite{GlobalWeb}, 59 were rejected because their original source was
   unpublished or could not be retrieved. We further eliminated 13 source or
@@
   food web (and therefore the latitude of the food web could not be
-  included). This left us with 226 webs from~\citet{GlobalWeb}.
+  included). This left us with 226 webs from~\cite{GlobalWeb}.
 
-  To these, we added 7 webs from~\citet{Dunne2013} that were originally used
+  To these, we added 7 webs from~\cite{Dunne2013} that were originally used
   to assess the roles of parasites within food webs. As all but 3 of the webs
-  from~\citet{GlobalWeb} contained only free-living species, we removed the
+  from~\cite{GlobalWeb} contained only free-living species, we removed the
   the parasites (and all interactions involving them) from these webs (and the
-  3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living
+  3 webs containing parasites from~\cite{GlobalWeb}) leaving free-living
   species only. In addition, we included 30 of the 40 webs
-  from~\citet{Riede2011}. Nine of the
-  remaining webs in the~\citet{Riede2011} dataset were also included in
-  the~\citet{GlobalWeb}  dataset, and the last web was derived from an
-  unpublished source. This gave us a database of 263 webs. As we wished to use
-  the logarithmic form of power-law relationships, we then eliminated any food
-  web which did not have at least one each of basal resources, intermediate
-  consumers, and top predators (to obtain  non-zero proportions of each
-  category). Our final sample size was thereby reduced to 196 food webs.
+  from~\cite{Riede2011}. Nine of the
+  remaining webs in the~\cite{Riede2011} dataset were also included in
+  the~\cite{GlobalWeb}  dataset, and the last web was derived from an
+  unpublished source. This gave us a database of 263 webs. As a measure of
+  quality-control, we then eliminated any food web which did not have at least
+  one each of basal resources, intermediate consumers, and top predators. Webs
+  which did not meet this requirement tended to be very small and poorly-resolved.
+  Our final sample size was thereby reduced to 196 food webs.
 
@@
     of the food web. We also show the ecosystem type, country of origin, and latitude for each food web, as well as whether
-    it was ultimately included in the study. Collection 1 is~\citet{Riede2011}, collection 2 is~\citet{Dunne2013}, and collection 3 is~\citet{GlobalWeb}.}
+    it was ultimately included in the study. Collection 1 is~\cite{Riede2011}, collection 2 is~\cite{Dunne2013}, and collection 3 is~\cite{GlobalWeb}.}
     \label{S1}
@@
         \hline
-        Alamitos & 1 & \citet{Harrison1995}    & stream & 37,12,25 N & Yes   &       \\
-        Alford & 1 & \citet{Havens1992}    & lake  & 44,15,41.59 N & Yes   &       \\
-        Beaver & 1 & \citet{Havens1992}    & lake  & 44,18,58.13 N & Yes   &       \\
-        Bere  & 1 & \citet{Woodward2008}  & stream & 50,45,7 N & Yes   &       \\
-        Bridge & 1 & \citet{Havens1992}    & lake  & 44,09,42.66 N & Yes   &       \\
-        Broad & 1 & \citet{Townsend1998}  & stream & 45.896938 S & Yes   &       \\
-        Broadstone & 1 & \citet{Woodward2005} & stream  & 51,01,05 N & Yes   &       \\
-        Calero & 1 & \citet{Harrison1995}    & stream & 37,11,09 - 20 N & Yes   &       \\
-        Canton & 1 & \citet{Townsend1998}  & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) \\
-        Carpinteria2006 & 1 & \citet{Lafferty2006}    & estuary & 34.41 - 34.40 N & Yes   &       \\
-        Chub  & 1 & \citet{Havens1992}    & lake  & 43,31,39.36 N & Yes   &       \\
-        Coachella & 1 & \citet{Polis1991a} & terrestrial & 33,54 N & Yes   &       \\
-        Connery & 1 & \citet{Havens1992}    & lake  & 44,18,42.10 N & Yes   &       \\
-        Corte & 1 & \citet{Harrison1995}    & stream & 37,56,28 - 37,57,39 N & Yes   &       \\
-        Coyote & 1 & \citet{Harrison1995}    & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       \\
-        German & 1 & \citet{Townsend1998}  & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) \\
-        GrandeCl & 1 & \citet{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
-        GrandeSc & 1 & \citet{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
-        Guadalupe & 1 & \citet{Harrison1995}    & stream & 37,27,54 - 37,21,17 N & Yes   &       \\
+        Alamitos & 1 & \cite{Harrison1995}    & stream & 37,12,25 N & Yes   &       \\
+        Alford & 1 & \cite{Havens1992}    & lake  & 44,15,41.59 N & Yes   &       \\
+        Beaver & 1 & \cite{Havens1992}    & lake  & 44,18,58.13 N & Yes   &       \\
+        Bere  & 1 & \cite{Woodward2008}  & stream & 50,45,7 N & Yes   &       \\
+        Bridge & 1 & \cite{Havens1992}    & lake  & 44,09,42.66 N & Yes   &       \\
+        Broad & 1 & \cite{Townsend1998}  & stream & 45.896938 S & Yes   &       \\
+        Broadstone & 1 & \cite{Woodward2005} & stream  & 51,01,05 N & Yes   &       \\
+        Calero & 1 & \cite{Harrison1995}    & stream & 37,11,09 - 20 N & Yes   &       \\
+        Canton & 1 & \cite{Townsend1998}  & stream & 45.752 S & No    & Duplicated in GlobalWeb (web 235) \\
+        Carpinteria2006 & 1 & \cite{Lafferty2006}    & estuary & 34.41 - 34.40 N & Yes   &       \\
+        Chub  & 1 & \cite{Havens1992}    & lake  & 43,31,39.36 N & Yes   &       \\
+        Coachella & 1 & \cite{Polis1991a} & terrestrial & 33,54 N & Yes   &       \\
+        Connery & 1 & \cite{Havens1992}    & lake  & 44,18,42.10 N & Yes   &       \\
+        Corte & 1 & \cite{Harrison1995}    & stream & 37,56,28 - 37,57,39 N & Yes   &       \\
+        Coyote & 1 & \cite{Harrison1995}    & stream & 37,53,11.66 - 37,53,17.06 N & Yes   &       \\
+        German & 1 & \cite{Townsend1998}  & stream & 44.97 S & No    & Duplicated in GlobalWeb (web 227) \\
+        GrandeCl & 1 & \cite{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
+        GrandeSc & 1 & \cite{CattinBlandenier2004} & terrestrial & 46,47,09 N & Yes   &       \\
+        Guadalupe & 1 & \cite{Harrison1995}    & stream & 37,27,54 - 37,21,17 N & Yes   &       \\
         Hainich   & 1 & Unpublished  & terrestrial &       & No    & Could not locate original source \\
-        LittleKyeBurn & 1 & \citet{Townsend1998}  & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) \\
-        LittleRock & 1 & \citet{Martinez1991}    & lake  & 45,44,07.94 N & Yes   &       \\
-        Mondego & 1 & \citet{Patricio2006}  & estuary & 40,08 N & Yes   &       \\
+        LittleKyeBurn & 1 & \cite{Townsend1998}  & stream & 45 S  & No    & Duplicated in GlobalWeb (web 230) \\
+        LittleRock & 1 & \cite{Martinez1991}    & lake  & 45,44,07.94 N & Yes   &       \\
+        Mondego & 1 & \cite{Patricio2006}  & estuary & 40,08 N & Yes   &       \\
         \hline
@@
         \hline
-        Montane Forest & 1 & \citet{Rasmussen1941}    & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) \\
-        Reef  & 1 & \citet{Opitz1996}  & marine & 18,29 - 17,53 N & Yes   &       \\
-        Sierra & 1 & \citet{Brose2005}    & lake  & 36,50 - 37,02 N & Yes   &       \\
-        SimberloffE1 & 1 & \citet{Simberloff1976}  & terrestrial & 24,40,37.29 N & Yes   &       \\
-        SimberloffE2 & 1 & \citet{Simberloff1976}  & terrestrial & 24,40,33 N & Yes   &       \\
-        SimberloffE3 & 1 & \citet{Simberloff1976}  & terrestrial & 24,41,23.82 N & Yes   &       \\
-        SimberloffE7 & 1 & \citet{Simberloff1976}  & terrestrial & 25,15 N & Yes   &       \\
-        SimberloffE9 & 1 & \citet{Simberloff1976}  & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       \\
-        SimberloffST2 & 1 & \citet{Simberloff1976}  & terrestrial & 24,36,16 N & Yes   &       \\
-        Skipwith & 1 & \citet{Warren1989}  & lake  & 53,40 N & Yes   &       \\
-        Stink & 1 & \citet{Havens1992}    & lake  & 43,37,55.88 N & Yes   &       \\
-        StMarks & 1 & \citet{Christian1999}    & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) \\
-        Stony  & 1 & \citet{Townsend1998}  & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) \\
-        TreleaseWoods & 1 & \citet{Twomey1945}    & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) \\
-        Tuesday & 1 & \citet{Jonsson2005}    & lake  & 46,13 N & Yes   &       \\
-        Weddell Sea & 1 & \citet{Brose2005}  & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) \\
-        Ythan & 1 & \citet{Huxham1996}     & marine &       & No    & Duplicated in Dunne (YthanDunne) \\
-        BahiaDunne & 2 & \citet{Hechinger2011}  & estuary & 30.43 - 30.46 N & Yes   &        \\
-        CarpinteriaDunne & 2 & \citet{Hechinger2011}    & estuary & 34.41 - 34.40 N & Yes   &        \\
-        EsteroDunne & 2 & \citet{Hechinger2011}  & estuary & 31.78 - 31.69 N & Yes   &        \\
-        FjordDunne & 2 & \citet{Zander2011}  & estuary & 54.92 - 54.75 N & Yes   &        \\
-        OtagoDunne & 2 & \citet{Mouritsen2011}  & estuary & 45.78 - 45.88 S & Yes   &        \\
-        SyltDunne & 2 & \citet{Thieltges2011}  & estuary & 54.83 - 55.12 N & Yes   &        \\
-        YthanDunne & 2 & \citet{Huxham1996}  & estuary & 57,18,32 N & Yes   &        \\
-        1     & 3 & \citet{Qazim1970}  & estuary &       & No    & Could not locate original source \\
-        2     & 3 & \citet{Day1967} & estuary &       & No    & Could not locate original source \\
-        3     & 3 & \citet{Woodwell1967}    & estuary & 41,03,11 N & Yes   &       \\
+        Montane Forest & 1 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) \\
+        Reef  & 1 & \cite{Opitz1996}  & marine & 18,29 - 17,53 N & Yes   &       \\
+        Sierra & 1 & \cite{Brose2005}    & lake  & 36,50 - 37,02 N & Yes   &       \\
+        SimberloffE1 & 1 & \cite{Simberloff1976}  & terrestrial & 24,40,37.29 N & Yes   &       \\
+        SimberloffE2 & 1 & \cite{Simberloff1976}  & terrestrial & 24,40,33 N & Yes   &       \\
+        SimberloffE3 & 1 & \cite{Simberloff1976}  & terrestrial & 24,41,23.82 N & Yes   &       \\
+        SimberloffE7 & 1 & \cite{Simberloff1976}  & terrestrial & 25,15 N & Yes   &       \\
+        SimberloffE9 & 1 & \cite{Simberloff1976}  & terrestrial & 25,01,59.64 - 25,02,55.44 N & Yes   &       \\
+        SimberloffST2 & 1 & \cite{Simberloff1976}  & terrestrial & 24,36,16 N & Yes   &       \\
+        Skipwith & 1 & \cite{Warren1989}  & lake  & 53,40 N & Yes   &       \\
+        Stink & 1 & \cite{Havens1992}    & lake  & 43,37,55.88 N & Yes   &       \\
+        StMarks & 1 & \cite{Christian1999}    & estuary & 30,05 N & No    & Duplicated in GlobalWeb (web 288) \\
+        Stony  & 1 & \cite{Townsend1998}  & stream & 45.58 S & No    & Duplicated in GlobalWeb (web 231) \\
+        TreleaseWoods & 1 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & No    & Duplicated in GlobalWeb (web 59) \\
+        Tuesday & 1 & \cite{Jonsson2005}    & lake  & 46,13 N & Yes   &       \\
+        Weddell Sea & 1 & \cite{Brose2005}  & marine & 58,20.8 - 60,10.4 S & No    & Duplicated in GlobalWeb (web 341) \\
+        Ythan & 1 & \cite{Huxham1996}     & marine &       & No    & Duplicated in Dunne (YthanDunne) \\
+        BahiaDunne & 2 & \cite{Hechinger2011}  & estuary & 30.43 - 30.46 N & Yes   &        \\
+        CarpinteriaDunne & 2 & \cite{Hechinger2011}    & estuary & 34.41 - 34.40 N & Yes   &        \\
+        EsteroDunne & 2 & \cite{Hechinger2011}  & estuary & 31.78 - 31.69 N & Yes   &        \\
+        FjordDunne & 2 & \cite{Zander2011}  & estuary & 54.92 - 54.75 N & Yes   &        \\
+        OtagoDunne & 2 & \cite{Mouritsen2011}  & estuary & 45.78 - 45.88 S & Yes   &        \\
+        SyltDunne & 2 & \cite{Thieltges2011}  & estuary & 54.83 - 55.12 N & Yes   &        \\
+        YthanDunne & 2 & \cite{Huxham1996}  & estuary & 57,18,32 N & Yes   &        \\
+        1     & 3 & \cite{Qazim1970}  & estuary &       & No    & Could not locate original source \\
+        2     & 3 & \cite{Day1967} & estuary &       & No    & Could not locate original source \\
+        3     & 3 & \cite{Woodwell1967}    & estuary & 41,03,11 N & Yes   &       \\
         \hline
@@
         \hline
-        4     & 3 & \citet{Johnston1956}    & estuary &       & No    & Sink web \\
-        5     & 3 & \citet{Teal1962}    & estuary & 31,28,38 N & Yes   &       \\
-        6     & 3 & \citet{MacGinitie1935}    & estuary & 36,48,18 N & Yes   &       \\
-        7     & 3 & \citet{Kremer1978}    & marine & 41,45 - 41,30 N & Yes   &       \\
-        8     & 3 & \citet{Nixon1973}    & estuary & 41,33,00 N & Yes   &       \\
-        9     & 3 & \citet{Kitching1967}  & stream &       & No    & Could not locate original source \\
-        10    & 3 & \citet{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
-        11    & 3 & \citet{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
-        12    & 3 & \citet{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
-        13    & 3 & \citet{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
-        14    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
-        15    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
-        16    & 3 & \citet{Copeland1974}    & estuary &       & No    & Could not locate original source \\
-        17    & 3 & \citet{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalized scheme \\
-        18    & 3 & \citet{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
-        19    & 3 & \citet{Brooks1963}    & lake &       & No    & Could not locate original source \\
-        20    & 3 & \citet{Knox1970}  & terrestrial &       & No    & Could not locate original source \\
-        21    & 3 & \citet{Patten1979}  & marine & 70-85 S & Yes   &       \\
-        22    & 3 & \citet{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
-        23    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
-        24    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
-        25    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
-        26    & 3 & \citet{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
-        27    & 3 & \citet{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
-        28    & 3 & \citet{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
-        29    & 3 & \citet{Dunbar1953}  & marine &       & No    & Generalized scheme \\
-        30    & 3 & \citet{Mackintosh1964}  & marine &       & No    & Generalized scheme \\
-        31    & 3 & \citet{Petipa1970}  & marine &       & No    & Could not locate original source \\
+        4     & 3 & \cite{Johnston1956}    & estuary &       & No    & Sink web \\
+        5     & 3 & \cite{Teal1962}    & estuary & 31,28,38 N & Yes   &       \\
+        6     & 3 & \cite{MacGinitie1935}    & estuary & 36,48,18 N & Yes   &       \\
+        7     & 3 & \cite{Kremer1978}    & marine & 41,45 - 41,30 N & Yes   &       \\
+        8     & 3 & \cite{Nixon1973}    & estuary & 41,33,00 N & Yes   &       \\
+        9     & 3 & \cite{Kitching1967}  & stream &       & No    & Could not locate original source \\
+        10    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
+        11    & 3 & \cite{Menge1976}    & marine & 41 - 47 N & Yes   &       \\
+        12    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
+        13    & 3 & \cite{Menge1976}    & marine & 45,45 - 49 N & Yes   &       \\
+        14    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
+        15    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
+        16    & 3 & \cite{Copeland1974}    & estuary &       & No    & Could not locate original source \\
+        17    & 3 & \cite{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalized scheme \\
+        18    & 3 & \cite{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
+        19    & 3 & \cite{Brooks1963}    & lake &       & No    & Could not locate original source \\
+        20    & 3 & \cite{Knox1970}  & terrestrial &       & No    & Could not locate original source \\
+        21    & 3 & \cite{Patten1979}  & marine & 70-85 S & Yes   &       \\
+        22    & 3 & \cite{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
+        23    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        24    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        25    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        26    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        27    & 3 & \cite{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
+        28    & 3 & \cite{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
+        29    & 3 & \cite{Dunbar1953}  & marine &       & No    & Generalized scheme \\
+        30    & 3 & \cite{Mackintosh1964}  & marine &       & No    & Generalized scheme \\
+        31    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
       \hline
@@
         \hline
-        32    & 3 & \citet{Petipa1970}  & marine &       & No    & Could not locate original source \\
-        33    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
-        34    & 3 & \citet{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
-        35    & 3 & \citet{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
-        36    & 3 & \citet{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
-        37    & 3 & \citet{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
-        38    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
-        39    & 3 & \citet{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
-        40    & 3 & \citet{Harrison1962}  & terrestrial &       & No    & Generalized scheme \\
-        41    & 3 & \citet{Parin1970}  & marine &       & No    & Could not locate original source \\
-        42    & 3 & \citet{Vinogradov1978}  & marine &       & No    & Study site unclear \\
-        43    & 3 & \citet{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
-        44    & 3 & \citet{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
-        45    & 3 & \citet{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
-        46    & 3 & \citet{Patten1975}    & lake & 33,54 N & Yes   &       \\
-        47    & 3 & \citet{Harris1980}    & lake &       & No    & Study site unclear \\
-        48    & 3 & \citet{Simenstad1978}    & marine &       & No    & Extinct species \\
-        49    & 3 & \citet{Simenstad1978}    & marine &       & No    & Extinct species \\
-        50    & 3 & \citet{Nybakken1982}    & marine &       & No    & Generalized scheme \\
-        51    & 3 & \citet{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
-        52    & 3 & \citet{Paine1980a}    & marine & 58,27 N & Yes   &       \\
-        53    & 3 & \citet{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
+        32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
+        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
+        34    & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
+        35    & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
+        36    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
+        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
+        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
+        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
+        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalized scheme \\
+        41    & 3 & \cite{Parin1970}  & marine &       & No    & Could not locate original source \\
+        42    & 3 & \cite{Vinogradov1978}  & marine &       & No    & Study site unclear \\
+        43    & 3 & \cite{Rosenthal1974}    & marine & 32,57 N & Yes   &       \\
+        44    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
+        45    & 3 & \cite{Tilly1968}    & stream & 41,22,55 N & Yes   &       \\
+        46    & 3 & \cite{Patten1975}    & lake & 33,54 N & Yes   &       \\
+        47    & 3 & \cite{Harris1980}    & lake &       & No    & Study site unclear \\
+        48    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
+        49    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
+        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalized scheme \\
+        51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
+        52    & 3 & \cite{Paine1980a}    & marine & 58,27 N & Yes   &       \\
+        53    & 3 & \cite{Paine1980a}    & marine & 48,19 - 48,37 N & Yes   &       \\
         54    & 3 & Unpublished  & marine &       & No    & Unpublished \\
-        55    & 3 & \citet{Milne1972}  & estuary &       & No    & Could not locate original source \\
-        56    & 3 & \citet{Milne1972}  & estuary &       & No    & Could not locate original source \\
-        57    & 3 & \citet{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
-        58    & 3 & \citet{Cohen1990}  & lake & 51,46 N & Yes   &       \\
-        59    & 3 & \citet{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
-        60    & 3 & \citet{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
-        61    & 3 & \citet{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
-        62    & 3 & \citet{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
+        55    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
+        56    & 3 & \cite{Milne1972}  & estuary &       & No    & Could not locate original source \\
+        57    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
+        58    & 3 & \cite{Cohen1990}  & lake & 51,46 N & Yes   &       \\
+        59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
+        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
+        61    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
+        62    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
         \hline
@@
         \hline
-        63    & 3 & \citet{Jones1950}     & stream & 52,25,08 N & Yes   &       \\
-        64    & 3 & \citet{Cummins1966}    & stream & 41,39,33 N & Yes   &       \\
-        65    & 3 & \citet{Tsuda1972}  & stream & 34,21,20 - 34,23,21 N & Yes   &       \\
-        66    & 3 & \citet{Mann1972a}  & stream & 51,30 N & Yes   &       \\
-        67    & 3 & \citet{Carlson1968}    & stream & 40,24,16 N & Yes   &       \\
-        68    & 3 & \citet{Morgan1972}  & lake &       & No    & Could not locate original source \\
-        69    & 3 & \citet{Cohen1990}  & estuary &       & No    & Could not locate original source \\
-        70    & 3 & \citet{Kemp1977}    & estuary & 28,54,08 N & Yes   &       \\
-        71    & 3 & \citet{Sorokin1972}  & lake & 48,00 N & Yes   &       \\
-        72    & 3 & \citet{Baril1983}  & lake & 46,02 N & Yes   &       \\
-        73    & 3 & \citet{Schiemer1979}  & lake &       & No    & Could not locate original source \\
-        74    & 3 & \citet{Cohen1990} & marine & 34,15,00 S & Yes   &       \\
-        75    & 3 & \citet{Pechlaner1972}  & lake & 47,11 N & Yes   &       \\
-        76    & 3 & \citet{Schiemer1979}  & lake & 47,42 - 47,54 N & Yes   &       \\
-        77    & 3 & \citet{Cohen1990}  & lake &       & No    & Could not locate original source \\
-        78    & 3 & \citet{Burgis1972}  & lake & 0     & Yes   &       \\
-        79    & 3 & \citet{Sarvala1974}  & lake &       & No    & Could not locate original source \\
-        80    & 3 & \citet{Sarvala1974}  & lake &       & No    & Could not locate original source \\
-        81    & 3 & \citet{Hatanaka1977}  & marine &       & No    & Could not locate original source \\
-        82    & 3 & \citet{Cohen1990} & marine &       & No    & Could not locate original source \\
-        83    & 3 & \citet{Cohen1990}  & lake &       & No    & Could not locate original source \\
-        84    & 3 & \citet{Wilbur1972}    & lake & 42,28,42 N & Yes   &       \\
-        85    & 3 & \citet{Mizuno1982}  & lake &       & No    & Could not locate original source \\
-        86    & 3 & \citet{Hogetsu1979}  & marine & 34,36 - 35,38 N & Yes   &       \\
-        87    & 3 & \citet{Bradstreet1982}  & terrestrial & 72,46,34.95 N & Yes   &       \\
+        63    & 3 & \cite{Jones1950}     & stream & 52,25,08 N & Yes   &       \\
+        64    & 3 & \cite{Cummins1966}    & stream & 41,39,33 N & Yes   &       \\
+        65    & 3 & \cite{Tsuda1972}  & stream & 34,21,20 - 34,23,21 N & Yes   &       \\
+        66    & 3 & \cite{Mann1972a}  & stream & 51,30 N & Yes   &       \\
+        67    & 3 & \cite{Carlson1968}    & stream & 40,24,16 N & Yes   &       \\
+        68    & 3 & \cite{Morgan1972}  & lake &       & No    & Could not locate original source \\
+        69    & 3 & \cite{Cohen1990}  & estuary &       & No    & Could not locate original source \\
+        70    & 3 & \cite{Kemp1977}    & estuary & 28,54,08 N & Yes   &       \\
+        71    & 3 & \cite{Sorokin1972}  & lake & 48,00 N & Yes   &       \\
+        72    & 3 & \cite{Baril1983}  & lake & 46,02 N & Yes   &       \\
+        73    & 3 & \cite{Schiemer1979}  & lake &       & No    & Could not locate original source \\
+        74    & 3 & \cite{Cohen1990} & marine & 34,15,00 S & Yes   &       \\
+        75    & 3 & \cite{Pechlaner1972}  & lake & 47,11 N & Yes   &       \\
+        76    & 3 & \cite{Schiemer1979}  & lake & 47,42 - 47,54 N & Yes   &       \\
+        77    & 3 & \cite{Cohen1990}  & lake &       & No    & Could not locate original source \\
+        78    & 3 & \cite{Burgis1972}  & lake & 0     & Yes   &       \\
+        79    & 3 & \cite{Sarvala1974}  & lake &       & No    & Could not locate original source \\
+        80    & 3 & \cite{Sarvala1974}  & lake &       & No    & Could not locate original source \\
+        81    & 3 & \cite{Hatanaka1977}  & marine &       & No    & Could not locate original source \\
+        82    & 3 & \cite{Cohen1990} & marine &       & No    & Could not locate original source \\
+        83    & 3 & \cite{Cohen1990}  & lake &       & No    & Could not locate original source \\
+        84    & 3 & \cite{Wilbur1972}    & lake & 42,28,42 N & Yes   &       \\
+        85    & 3 & \cite{Mizuno1982}  & lake &       & No    & Could not locate original source \\
+        86    & 3 & \cite{Hogetsu1979}  & marine & 34,36 - 35,38 N & Yes   &       \\
+        87    & 3 & \cite{Bradstreet1982}  & terrestrial & 72,46,34.95 N & Yes   &       \\
         \hline
@@
         \hline
-        88    & 3 & \citet{Kuusela1980}  & stream &       & No    & Could not locate original source \\
-        89    & 3 & \citet{Hartley1948}  & stream & 52,13 N & Yes   &       \\
-        91    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
-        92    & 3 & \citet{Swan1961}  & terrestrial &       & No    & Generalized scheme \\
-        93    & 3 & \citet{Pattie1966}    & terrestrial & 45 N  & Yes   &       \\
-        94    & 3 & \citet{Brown1971}    & terrestrial &       & No    & Could not locate original source \\
-        95    & 3 & \citet{Brown1975}    & terrestrial & 70,11,14.18 N & Yes   &       \\
-        96    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
-        97    & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
-        98    & 3 & \citet{Holm1980}  & terrestrial &       & No    & Could not locate original source \\
-        99    & 3 & \citet{Howes1954}    & terrestrial & 32,36 N & Yes   &       \\
-        100   & 3 & \citet{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
-        101   & 3 & \citet{Cohen1990} & lake  &       & No    & Could not locate original source \\
-        102   & 3 & \citet{Shushkina1979}  & marine & 10 S - 15 N & Yes   &       \\
-        103   & 3 & \citet{Petipa1979}  & marine &       & No    & Generalized scheme \\
-        104   & 3 & \citet{Menge1976}  & marine & 4,48,04 N & Yes   &       \\
-        105   & 3 & \citet{Edwards1982}  & marine & 42,40 N & Yes   &       \\
-        106   & 3 & \citet{Glynn1965}  & marine &       & No    & Could not locate original source \\
-        107   & 3 & \citet{Peterson1979}  & marine & 39,52,02 N & Yes   &       \\
-        108   & 3 & \citet{Hewatt1937}  & marine & 36,37 N & Yes   &       \\
-        109   & 3 & \citet{Castilla1981} & marine &       & No    & Could not locate original source \\
-        110   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
-        111   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
-        112   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
-        113   & 3 & \citet{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
-        114   & 3 & \citet{Marshall1982}  & lake  & 17,54,11.90 S & Yes   &       \\
+        88    & 3 & \cite{Kuusela1980}  & stream &       & No    & Could not locate original source \\
+        89    & 3 & \cite{Hartley1948}  & stream & 52,13 N & Yes   &       \\
+        91    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
+        92    & 3 & \cite{Swan1961}  & terrestrial &       & No    & Generalized scheme \\
+        93    & 3 & \cite{Pattie1966}    & terrestrial & 45 N  & Yes   &       \\
+        94    & 3 & \cite{Brown1971}    & terrestrial &       & No    & Could not locate original source \\
+        95    & 3 & \cite{Brown1975}    & terrestrial & 70,11,14.18 N & Yes   &       \\
+        96    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
+        97    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
+        98    & 3 & \cite{Holm1980}  & terrestrial &       & No    & Could not locate original source \\
+        99    & 3 & \cite{Howes1954}    & terrestrial & 32,36 N & Yes   &       \\
+        100   & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
+        101   & 3 & \cite{Cohen1990} & lake  &       & No    & Could not locate original source \\
+        102   & 3 & \cite{Shushkina1979}  & marine & 10 S - 15 N & Yes   &       \\
+        103   & 3 & \cite{Petipa1979}  & marine &       & No    & Generalized scheme \\
+        104   & 3 & \cite{Menge1976}  & marine & 4,48,04 N & Yes   &       \\
+        105   & 3 & \cite{Edwards1982}  & marine & 42,40 N & Yes   &       \\
+        106   & 3 & \cite{Glynn1965}  & marine &       & No    & Could not locate original source \\
+        107   & 3 & \cite{Peterson1979}  & marine & 39,52,02 N & Yes   &       \\
+        108   & 3 & \cite{Hewatt1937}  & marine & 36,37 N & Yes   &       \\
+        109   & 3 & \cite{Castilla1981} & marine &       & No    & Could not locate original source \\
+        110   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
+        111   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
+        112   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
+        113   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
+        114   & 3 & \cite{Marshall1982}  & lake  & 17,54,11.90 S & Yes   &       \\
         \hline
@@
         \hline
-        115   & 3 & \citet{Koepcke1952}  & marine &       & No    & Could not locate original source \\
-        116   & 3 & \citet{Hurlbert1972}  & lake  & 35,09,19 S & Yes   &       \\
-        117   & 3 & \citet{Zaret1973}  & lake  & 9,11,31.50 N & Yes   &       \\
-        118   & 3 & \citet{Bindloss1972}  & lake  & 56,41,18.71 N & Yes   &       \\
-        119   & 3 & \citet{Mann1972}  & stream & 51,27 N & Yes   &       \\
-        120   & 3 & \citet{Moriarty1973}  & lake  & 0,00,58 N & Yes   &       \\
-        121   & 3 & \citet{VanEs1977}  & estuary & 53,20 - 53,15 N & Yes   &       \\
-        122   & 3 & \citet{Nixon1973}  & estuary & 41,33,04 N & Yes   &       \\
-        123   & 3 & \citet{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
-        124   & 3 & \citet{Collins1976}  & stream & 44,34 N & Yes   &       \\
-        125   & 3 & \citet{Landry1977}  & marine &       & No    & Generalized scheme \\
-        126   & 3 & \citet{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
-        127   & 3 & \citet{Beaver1979}  & lake  &       & No    & Could not locate original source \\
-        128   & 3 & \citet{Beaver1979}  & lake  &       & No    & Could not locate original source \\
+        115   & 3 & \cite{Koepcke1952}  & marine &       & No    & Could not locate original source \\
+        116   & 3 & \cite{Hurlbert1972}  & lake  & 35,09,19 S & Yes   &       \\
+        117   & 3 & \cite{Zaret1973}  & lake  & 9,11,31.50 N & Yes   &       \\
+        118   & 3 & \cite{Bindloss1972}  & lake  & 56,41,18.71 N & Yes   &       \\
+        119   & 3 & \cite{Mann1972}  & stream & 51,27 N & Yes   &       \\
+        120   & 3 & \cite{Moriarty1973}  & lake  & 0,00,58 N & Yes   &       \\
+        121   & 3 & \cite{VanEs1977}  & estuary & 53,20 - 53,15 N & Yes   &       \\
+        122   & 3 & \cite{Nixon1973}  & estuary & 41,33,04 N & Yes   &       \\
+        123   & 3 & \cite{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
+        124   & 3 & \cite{Collins1976}  & stream & 44,34 N & Yes   &       \\
+        125   & 3 & \cite{Landry1977}  & marine &       & No    & Generalized scheme \\
+        126   & 3 & \cite{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
+        127   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
+        128   & 3 & \cite{Beaver1979}  & lake  &       & No    & Could not locate original source \\
         129   & 3 & Unpublished & terrestrial &       & No    & Unpublished \\
-        130   & 3 & \citet{Odum1975}  & estuary & 27,12 N & Yes   &       \\
-        131   & 3 & \citet{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
-        132   & 3 & \citet{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
-        133   & 3 & \citet{Beaver1985}  & lake  & 7,52,22 N & Yes   &       \\
-        134   & 3 & \citet{Beaver1985}  & lake  & 19 S  & Yes   &       \\
-        135   & 3 & \citet{Beaver1985}  & lake  & 4,40,46 S & Yes   &       \\
-        136   & 3 & \citet{Bradshaw1983}    & lake  &       & No    & Could not locate original source \\
-        137   & 3 & \citet{Corker1984}  & lake  & 22,14-22,17 N & Yes   &       \\
-        138   & 3 & \citet{Kitching1983}     & lake  &       & No    & Could not locate original source \\
-        139   & 3 & \citet{Kitching1983}  & lake  &       & No    & Could not locate original source \\
-        140   & 3 & \citet{Seifert1979}  & terrestrial & 10,21 N & Yes   &       \\
-        141   & 3 & \citet{Seifert1976}  & terrestrial &       & No    & Competition network \\
-        142   & 3 & \citet{Seifert1976}  & terrestrial &       & No    & Competition network \\
-        143   & 3 & \citet{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
+        130   & 3 & \cite{Odum1975}  & estuary & 27,12 N & Yes   &       \\
+        131   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
+        132   & 3 & \cite{Beaver1985}  & lake  & 4,12,37 N & Yes   &       \\
+        133   & 3 & \cite{Beaver1985}  & lake  & 7,52,22 N & Yes   &       \\
+        134   & 3 & \cite{Beaver1985}  & lake  & 19 S  & Yes   &       \\
+        135   & 3 & \cite{Beaver1985}  & lake  & 4,40,46 S & Yes   &       \\
+        136   & 3 & \cite{Bradshaw1983}    & lake  &       & No    & Could not locate original source \\
+        137   & 3 & \cite{Corker1984}  & lake  & 22,14-22,17 N & Yes   &       \\
+        138   & 3 & \cite{Kitching1983}     & lake  &       & No    & Could not locate original source \\
+        139   & 3 & \cite{Kitching1983}  & lake  &       & No    & Could not locate original source \\
+        140   & 3 & \cite{Seifert1979}  & terrestrial & 10,21 N & Yes   &       \\
+        141   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
+        142   & 3 & \cite{Seifert1976}  & terrestrial &       & No    & Competition network \\
+        143   & 3 & \cite{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
          \hline
@@
         \hline
-        144   & 3 & \citet{Snow1958}  & lake  &       & No    & Could not locate original source \\
-        145   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
-        146   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
-        147   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
-        148   & 3 & \citet{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
-        149   & 3 & \citet{Force1974}    & terrestrial &       & No    & Host-parasitoid web \\
-        150   & 3 & \citet{Hopkins1984}     & terrestrial &       & No    & Host-parasitoid web \\
-        151   & 3 & \citet{Richards1926}     & terrestrial & 51,20,04 N & Yes   &       \\
-        152   & 3 & \citet{Whittaker1984}    & terrestrial &       & No    & Source web \\
-        153   & 3 & \citet{Mayse1978}    & terrestrial & 40,06,38 N & Yes   &       \\
-        154   & 3 & \citet{Mayse1978}    & terrestrial & 39,56,41 N & Yes   &       \\
-        155   & 3 & \citet{Askew1975}     & terrestrial &       & No    & Host-parasitoid web \\
-        156   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        157   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        158   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        159   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        160   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        161   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        162   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        163   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        164   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        165   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        166   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        167   & 3 & \citet{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
-        168   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        169   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\        
-        170   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        171   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\      
-        172   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        173   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        174   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        175   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        176   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        177   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        178   & 3 & \citet{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        144   & 3 & \cite{Snow1958}  & lake  &       & No    & Could not locate original source \\
+        145   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
+        146   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
+        147   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
+        148   & 3 & \cite{Rejmanek1979}  & terrestrial &       & No    & Host-parasitoid web \\
+        149   & 3 & \cite{Force1974}    & terrestrial &       & No    & Host-parasitoid web \\
+        150   & 3 & \cite{Hopkins1984}     & terrestrial &       & No    & Host-parasitoid web \\
+        151   & 3 & \cite{Richards1926}     & terrestrial & 51,20,04 N & Yes   &       \\
+        152   & 3 & \cite{Whittaker1984}    & terrestrial &       & No    & Source web \\
+        153   & 3 & \cite{Mayse1978}    & terrestrial & 40,06,38 N & Yes   &       \\
+        154   & 3 & \cite{Mayse1978}    & terrestrial & 39,56,41 N & Yes   &       \\
+        155   & 3 & \cite{Askew1975}     & terrestrial &       & No    & Host-parasitoid web \\
+        156   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        157   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        158   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        159   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        160   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        161   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        162   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        163   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        164   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        165   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        166   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        167   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+        168   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        169   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\        
+        170   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        171   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\      
+        172   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        173   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        174   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        175   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        176   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        177   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
+        178   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
         \hline
@@
         \hline
-        179   & 3 & \citet{Robinson1953}  & terrestrial &       & No    & Source web \\
-        180   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
-        181   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
-        182   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
-        183   & 3 & \citet{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
-        184   & 3 & \citet{Beaver1972}     & terrestrial &       & No    & Could not locate original source \\
-        185   & 3 & \citet{Chapman1955}     & terrestrial &       & No    & Source web \\
-        186   & 3 & \citet{Cornaby1974}  & terrestrial &       & No    & Source web \\
-        187   & 3 & \citet{Cornaby1974}  & terrestrial &       & No    & Source web \\
-        188   & 3 & \citet{Jiron1981}  & terrestrial &       & No    & Source web \\
-        189   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
-        190   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
-        191   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
-        192   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
-        193   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
-        194   & 3 & \citet{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
-        195   & 3 & \citet{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
-        196   & 3 & \citet{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
-        197   & 3 & \citet{Mohr1943}    & terrestrial &       & No    & Source web \\
-        198   & 3 & \citet{Schoenly1983}  & terrestrial &       & No    & Source web \\
-        199   & 3 & \citet{Valiela1969}    & terrestrial &       & No    & Source web \\
-        200   & 3 & \citet{Valiela1974}    & terrestrial &       & No    & Source web \\
-        201   & 3 & \citet{Valiela1974}    & terrestrial &       & No    & Source web \\
-        202   & 3 & \citet{Allan1982}    & stream & 38,50,21 N & Yes   &       \\
-        203   & 3 & \citet{Collins1976}    & stream & 44,24 N & Yes   &       \\
-        204   & 3 & \citet{Fryer1959} & lake  & 11,36,39 S & Yes   &       \\
-        205   & 3 & \citet{Hildrew1985}     & stream & 51,01,05 N & Yes   &       \\
+        179   & 3 & \cite{Robinson1953}  & terrestrial &       & No    & Source web \\
+        180   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        181   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        182   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        183   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        184   & 3 & \cite{Beaver1972}     & terrestrial &       & No    & Could not locate original source \\
+        185   & 3 & \cite{Chapman1955}     & terrestrial &       & No    & Source web \\
+        186   & 3 & \cite{Cornaby1974}  & terrestrial &       & No    & Source web \\
+        187   & 3 & \cite{Cornaby1974}  & terrestrial &       & No    & Source web \\
+        188   & 3 & \cite{Jiron1981}  & terrestrial &       & No    & Source web \\
+        189   & 3 & \cite{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        190   & 3 & \cite{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        191   & 3 & \cite{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        192   & 3 & \cite{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        193   & 3 & \cite{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        194   & 3 & \cite{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        195   & 3 & \cite{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
+        196   & 3 & \cite{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
+        197   & 3 & \cite{Mohr1943}    & terrestrial &       & No    & Source web \\
+        198   & 3 & \cite{Schoenly1983}  & terrestrial &       & No    & Source web \\
+        199   & 3 & \cite{Valiela1969}    & terrestrial &       & No    & Source web \\
+        200   & 3 & \cite{Valiela1974}    & terrestrial &       & No    & Source web \\
+        201   & 3 & \cite{Valiela1974}    & terrestrial &       & No    & Source web \\
+        202   & 3 & \cite{Allan1982}    & stream & 38,50,21 N & Yes   &       \\
+        203   & 3 & \cite{Collins1976}    & stream & 44,24 N & Yes   &       \\
+        204   & 3 & \cite{Fryer1959} & lake  & 11,36,39 S & Yes   &       \\
+        205   & 3 & \cite{Hildrew1985}     & stream & 51,01,05 N & Yes   &       \\
         \hline
@@
         \hline
-        206   & 3 & \citet{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
-        207   & 3 & \citet{Koslucher1973}    & stream & 41,57 - 42,14 N & Yes   &       \\
-        208   & 3 & \citet{Minckley1963}    & stream & 37,56 N & Yes   &       \\
-        209   & 3 & \citet{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
-        210   & 3 & \citet{Percival1929}     & stream &       & No    & Generalized scheme \\
-        211   & 3 & \citet{Ricker1935}  & stream &       & No    & Could not locate original source \\
-        212   & 3 & \citet{Ricker1935}  & stream &       & No    & Could not locate original source \\
-        213   & 3 & \citet{Badcock1949}     & stream & 53 N  & Yes   &       \\
-        214   & 3 & \citet{Thompson2003}    & stream & 44,40,44 N & Yes   &       \\
-        215   & 3 & \citet{Thompson2003}    & stream & 40,40,52 N & Yes   &       \\
-        216   & 3 & \citet{Thompson2003}    & stream & 35,02,50 N & Yes   &       \\
-        217   & 3 & \citet{Thompson2003}    & stream & 35,03,50 N & Yes   &       \\
-        218   & 3 & \citet{Thompson2004c}  & stream & 45.79 S & Yes   &       \\
-        219   & 3 & \citet{Thompson2004c}  & stream & 44.64 S & Yes   &       \\
-        220   & 3 & \citet{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
-        221   & 3 & \citet{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
-        222   & 3 & \citet{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
-        223   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        224   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        225   & 3 & \citet{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
-        226   & 3 & \citet{Thompson2004c}  & stream & 45.61 S & Yes   &       \\
-        227   & 3 & \citet{Thompson2004c}  & stream & 44.97 S & Yes   &       \\
-        228   & 3 & \citet{Thompson2004c}  & stream & 44.95 S & Yes   &       \\
-        229   & 3 & \citet{Thompson2004c}  & stream & 44.96 S & Yes   &       \\
-        230   & 3 & \citet{Thompson2004c}  & stream & 45 S  & Yes   &       \\
-        231   & 3 & \citet{Thompson2004c}  & stream & 45.58 S & Yes   &       \\
-        232   & 3 & \citet{Thompson2004c}  & stream & 45.61 S & Yes   &       \\
-        233   & 3 & \citet{Thompson2004c}  & stream & 45.782 S & Yes   &       \\
-        234   & 3 & \citet{Thompson2004c}  & stream & 45.803 S & Yes   &       \\
-        235   & 3 & \citet{Thompson2004c}  & stream & 45.752 S & Yes   &       \\
-        236   & 3 & \citet{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
-        237   & 3 & \citet{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
-        238   & 3 & \citet{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
-        239   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        206   & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
+        207   & 3 & \cite{Koslucher1973}    & stream & 41,57 - 42,14 N & Yes   &       \\
+        208   & 3 & \cite{Minckley1963}    & stream & 37,56 N & Yes   &       \\
+        209   & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
+        210   & 3 & \cite{Percival1929}     & stream &       & No    & Generalized scheme \\
+        211   & 3 & \cite{Ricker1935}  & stream &       & No    & Could not locate original source \\
+        212   & 3 & \cite{Ricker1935}  & stream &       & No    & Could not locate original source \\
+        213   & 3 & \cite{Badcock1949}     & stream & 53 N  & Yes   &       \\
+        214   & 3 & \cite{Thompson2003}    & stream & 44,40,44 N & Yes   &       \\
+        215   & 3 & \cite{Thompson2003}    & stream & 40,40,52 N & Yes   &       \\
+        216   & 3 & \cite{Thompson2003}    & stream & 35,02,50 N & Yes   &       \\
+        217   & 3 & \cite{Thompson2003}    & stream & 35,03,50 N & Yes   &       \\
+        218   & 3 & \cite{Thompson2004c}  & stream & 45.79 S & Yes   &       \\
+        219   & 3 & \cite{Thompson2004c}  & stream & 44.64 S & Yes   &       \\
+        220   & 3 & \cite{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
+        221   & 3 & \cite{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
+        222   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
+        223   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        224   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        225   & 3 & \cite{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
+        226   & 3 & \cite{Thompson2004c}  & stream & 45.61 S & Yes   &       \\
+        227   & 3 & \cite{Thompson2004c}  & stream & 44.97 S & Yes   &       \\
+        228   & 3 & \cite{Thompson2004c}  & stream & 44.95 S & Yes   &       \\
+        229   & 3 & \cite{Thompson2004c}  & stream & 44.96 S & Yes   &       \\
+        230   & 3 & \cite{Thompson2004c}  & stream & 45 S  & Yes   &       \\
+        231   & 3 & \cite{Thompson2004c}  & stream & 45.58 S & Yes   &       \\
+        232   & 3 & \cite{Thompson2004c}  & stream & 45.61 S & Yes   &       \\
+        233   & 3 & \cite{Thompson2004c}  & stream & 45.782 S & Yes   &       \\
+        234   & 3 & \cite{Thompson2004c}  & stream & 45.803 S & Yes   &       \\
+        235   & 3 & \cite{Thompson2004c}  & stream & 45.752 S & Yes   &       \\
+        236   & 3 & \cite{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
+        237   & 3 & \cite{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
+        238   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
+        239   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
          \hline
@@
         \hline
-        240   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        241   & 3 & \citet{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
-        242   & 3 & \citet{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
-        243   & 3 & \citet{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
-        244   & 3 & \citet{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
-        245   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        246   & 3 & \citet{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        247   & 3 & \citet{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
-        248   & 3 & \citet{Thompson2004}  & estuary & 45,51,28 S & Yes   &        \\
-        249   & 3 & \citet{Angelini2005}  & stream & 24,30 S & Yes   &       \\
-        250   & 3 & \citet{Angelini2006}  & lake  & 22,57,38 S & Yes   &       \\
-        251   & 3 & \citet{Angelini2006}  & lake  & 22,57,38 S & Yes   &       \\
-        252   & 3 & \citet{Angelini2010}  & stream & 18,40 S & Yes   &       \\
-        253   & 3 & \citet{Angelini2011}  & marine & 5 - 17,15 S & Yes   &       \\
-        254   & 3 & \citet{Angelini2013}  & stream & 21 S  & Yes   &       \\
-        255   & 3 & \citet{Angelini2013}  & stream & 21 S  & Yes   &       \\
-        256   & 3 & \citet{Angelini2013}  & stream &       & No    & Could not locate original source \\
-        257   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        258   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        259   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        260   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        261   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        262   & 3 & \citet{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        263   & 3 & \citet{Schneider1997}    & lake  & 45,58,50 N & Yes   &       \\
-        264   & 3 & \citet{Stagliano2002}    & terrestrial & 39,06,27 N & Yes   &       \\
-        265   & 3 & \citet{Lin2006}  & marine & 22,27 N & Yes   &       \\
-        266   & 3 & \citet{Cornejo-Donoso2008}  & marine & 60 - 69 S & Yes   &       \\
-        267   & 3 & \citet{Zetina-Rejon2003}  & marine & 23.15 - 22.9N & Yes   &       \\
-        268   & 3 & \citet{Cruz-Escalona2007}  & marine & 18,45 - 18,50 N & Yes   &       \\
-        269   & 3 & \citet{Liu2007}  & lake  & 29,32,35 N & Yes   &       \\
+        240   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        241   & 3 & \cite{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
+        242   & 3 & \cite{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
+        243   & 3 & \cite{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
+        244   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
+        245   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        246   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        247   & 3 & \cite{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
+        248   & 3 & \cite{Thompson2004}  & estuary & 45,51,28 S & Yes   &        \\
+        249   & 3 & \cite{Angelini2005}  & stream & 24,30 S & Yes   &       \\
+        250   & 3 & \cite{Angelini2006}  & lake  & 22,57,38 S & Yes   &       \\
+        251   & 3 & \cite{Angelini2006}  & lake  & 22,57,38 S & Yes   &       \\
+        252   & 3 & \cite{Angelini2010}  & stream & 18,40 S & Yes   &       \\
+        253   & 3 & \cite{Angelini2011}  & marine & 5 - 17,15 S & Yes   &       \\
+        254   & 3 & \cite{Angelini2013}  & stream & 21 S  & Yes   &       \\
+        255   & 3 & \cite{Angelini2013}  & stream & 21 S  & Yes   &       \\
+        256   & 3 & \cite{Angelini2013}  & stream &       & No    & Could not locate original source \\
+        257   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        258   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        259   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        260   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        261   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        262   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        263   & 3 & \cite{Schneider1997}    & lake  & 45,58,50 N & Yes   &       \\
+        264   & 3 & \cite{Stagliano2002}    & terrestrial & 39,06,27 N & Yes   &       \\
+        265   & 3 & \cite{Lin2006}  & marine & 22,27 N & Yes   &       \\
+        266   & 3 & \cite{Cornejo-Donoso2008}  & marine & 60 - 69 S & Yes   &       \\
+        267   & 3 & \cite{Zetina-Rejon2003}  & marine & 23.15 - 22.9N & Yes   &       \\
+        268   & 3 & \cite{Cruz-Escalona2007}  & marine & 18,45 - 18,50 N & Yes   &       \\
+        269   & 3 & \cite{Liu2007}  & lake  & 29,32,35 N & Yes   &       \\
          \hline
@@
         \hline
-        270   & 3 & \citet{Filgueira2011}  & marine & 42,17,37 - 42,19,29 N & Yes   &       \\
-        271   & 3 & \citet{Amundsen2013}  & lake  & 69,07 N & Yes   &        \\
-        272   & 3 & \citet{Hampton2011}    & lake  & 48,03,29 N & Yes   &       \\
-        273   & 3 & \citet{Parker2006}  & stream & 69,1 N & Yes   &       \\
-        274   & 3 & \citet{Parker2006}  & stream & 69,1 N & Yes   &       \\
-        275   & 3 & \citet{Parker2006}  & stream & 69,1 N & Yes   &       \\
-        276   & 3 & \citet{Parker2006}  & stream & 69,1 N & Yes   &       \\
-        277   & 3 & \citet{Massana1996}  & lake  & 42,08,6 - 42,07 N & Yes   &       \\
-        278   & 3 & \citet{Stewart2011}    & lake  & 43.7 N & Yes   &       \\
-        279   & 3 & \citet{Stewart2011}    & lake  & 43.7 N & Yes   &       \\
-        280   & 3 & \citet{Cromar1996}  & stream & 43,58 N & Yes   &       \\
-        281   & 3 & \citet{Cromar1996}  & stream & 44,58 N & Yes   &       \\
-        282   & 3 & \citet{Cromar1996}  & stream & 45,58 N & Yes   &       \\
-        283   & 3 & \citet{Cromar1996}  & stream & 46,58 N & Yes   &       \\
-        284   & 3 & \citet{Cromar1996}  & stream & 47,58 N & Yes   &       \\
-        285   & 3 & \citet{Cromar1996}  & stream & 48,58 N & Yes   &       \\
-        286   & 3 & \citet{Cromar1996}  & stream & 49,58 N & Yes   &       \\
-        287   & 3 & \citet{Cromar1996}  & stream & 50,58 N & Yes   &       \\
-        288   & 3 & \citet{Christian1999}    & estuary & 30,05,39 N & Yes   &       \\
-        289   & 3 & \citet{Fetahi2011}  & lake  & 11,15 N & Yes   &       \\
-        290   & 3 & \citet{Brodeur1992}    & marine & 43 - 48 N & Yes   &       \\
-        291   & 3 & \citet{Brodeur1992}    & marine & 44 - 48 N & Yes   &       \\
-        292   & 3 & \citet{Brodeur1992}    & marine & 45 - 48 N & Yes   &       \\
-        293   & 3 & \citet{Brodeur1992}    & marine & 46 - 48 N & Yes   &       \\
-        294   & 3 & \citet{Gaedke1994}  & lake  & 47,37,30 N & Yes   &       \\
-        295   & 3 & \citet{Preston2012}    & lake  & 37.66 N & Yes   &        \\
-        296   & 3 & \citet{Ratsirarson1996}  & lake  & 24,55 S & Yes   &       \\
-        297   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        298   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        299   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        300   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        301   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        302   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        303   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        270   & 3 & \cite{Filgueira2011}  & marine & 42,17,37 - 42,19,29 N & Yes   &       \\
+        271   & 3 & \cite{Amundsen2013}  & lake  & 69,07 N & Yes   &        \\
+        272   & 3 & \cite{Hampton2011}    & lake  & 48,03,29 N & Yes   &       \\
+        273   & 3 & \cite{Parker2006}  & stream & 69,1 N & Yes   &       \\
+        274   & 3 & \cite{Parker2006}  & stream & 69,1 N & Yes   &       \\
+        275   & 3 & \cite{Parker2006}  & stream & 69,1 N & Yes   &       \\
+        276   & 3 & \cite{Parker2006}  & stream & 69,1 N & Yes   &       \\
+        277   & 3 & \cite{Massana1996}  & lake  & 42,08,6 - 42,07 N & Yes   &       \\
+        278   & 3 & \cite{Stewart2011}    & lake  & 43.7 N & Yes   &       \\
+        279   & 3 & \cite{Stewart2011}    & lake  & 43.7 N & Yes   &       \\
+        280   & 3 & \cite{Cromar1996}  & stream & 43,58 N & Yes   &       \\
+        281   & 3 & \cite{Cromar1996}  & stream & 44,58 N & Yes   &       \\
+        282   & 3 & \cite{Cromar1996}  & stream & 45,58 N & Yes   &       \\
+        283   & 3 & \cite{Cromar1996}  & stream & 46,58 N & Yes   &       \\
+        284   & 3 & \cite{Cromar1996}  & stream & 47,58 N & Yes   &       \\
+        285   & 3 & \cite{Cromar1996}  & stream & 48,58 N & Yes   &       \\
+        286   & 3 & \cite{Cromar1996}  & stream & 49,58 N & Yes   &       \\
+        287   & 3 & \cite{Cromar1996}  & stream & 50,58 N & Yes   &       \\
+        288   & 3 & \cite{Christian1999}    & estuary & 30,05,39 N & Yes   &       \\
+        289   & 3 & \cite{Fetahi2011}  & lake  & 11,15 N & Yes   &       \\
+        290   & 3 & \cite{Brodeur1992}    & marine & 43 - 48 N & Yes   &       \\
+        291   & 3 & \cite{Brodeur1992}    & marine & 44 - 48 N & Yes   &       \\
+        292   & 3 & \cite{Brodeur1992}    & marine & 45 - 48 N & Yes   &       \\
+        293   & 3 & \cite{Brodeur1992}    & marine & 46 - 48 N & Yes   &       \\
+        294   & 3 & \cite{Gaedke1994}  & lake  & 47,37,30 N & Yes   &       \\
+        295   & 3 & \cite{Preston2012}    & lake  & 37.66 N & Yes   &        \\
+        296   & 3 & \cite{Ratsirarson1996}  & lake  & 24,55 S & Yes   &       \\
+        297   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        298   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        299   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        300   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        301   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        302   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        303   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
          \hline
@@
         \hline
-        304   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        305   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        306   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        307   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        308   & 3 & \citet{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        309   & 3 & \citet{Gontikaki2011}  & marine & 61,13,88 N & Yes   &       \\
-        310   & 3 & \citet{Khan2009}  & lake  & 12,45,25 N & Yes   &       \\
-        311   & 3 & \citet{Memmott2000}     & terrestrial &       & No    & Source web \\
-        312   & 3 & \citet{Kaiser-Bunbury2009}  & terrestrial &       & No    & Plant-pollinator web \\
-        313   & 3 & \citet{Kaiser-Bunbury2009}  & terrestrial &       & No    & Plant-pollinator web \\
-        314   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
-        315   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
-        316   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
-        317   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
-        318   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
-        319   & 3 & \citet{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
-        320   & 3 & \citet{Ruzicka2012}    & marine & 42 - 49 N & Yes   &       \\
-        321   & 3 & \citet{Ruzicka2012}    & marine & 43 - 49 N & Yes   &       \\
-        322   & 3 & \citet{Ruzicka2012}    & marine & 44 - 49 N & Yes   &       \\
-        323   & 3 & \citet{Ruzicka2012}    & marine & 45 - 49 N & Yes   &       \\
-        324   & 3 & \citet{Ruzicka2012}    & marine & 46 - 49 N & Yes   &       \\
-        325   & 3 & \citet{Lewis2002}  & terrestrial &       & No    & Host-parasitoid web \\
-        326   & 3 & \citet{Lewis2002}  & terrestrial &       & No    & Host-parasitoid web \\
-        327   & 3 & \citet{Kelleway2010}  & stream & 29,13 S & Yes   &       \\
-        328   & 3 & \citet{Kelleway2010}  & stream & 29,20,0 S & Yes   &       \\
-        329   & 3 & \citet{Kelleway2010}  & stream & 29,35 S & Yes   &       \\
-        330   & 3 & \citet{Kelleway2010}  & stream & 29,13 S & Yes   &       \\
-        331   & 3 & \citet{Kelleway2010}  & stream & 29,20,0 S & Yes   &       \\
-        332   & 3 & \citet{Huang2008}  & stream & 31.70 N & Yes   &       \\
-        333   & 3 & \citet{Link2002}    & marine & 33,51 - 44,49 N & Yes   &       \\
-        334   & 3 & \citet{Alcorlo2001}  & lake  & 41,26,36 N & Yes   &       \\
-        335   & 3 & \citet{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
-        336   & 3 & \citet{Alcorlo2001}  & lake  & 41,26,36 N & Yes   &       \\
-        337   & 3 & \citet{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
+        304   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        305   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        306   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        307   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        308   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        309   & 3 & \cite{Gontikaki2011}  & marine & 61,13,88 N & Yes   &       \\
+        310   & 3 & \cite{Khan2009}  & lake  & 12,45,25 N & Yes   &       \\
+        311   & 3 & \cite{Memmott2000}     & terrestrial &       & No    & Source web \\
+        312   & 3 & \cite{Kaiser-Bunbury2009}  & terrestrial &       & No    & Plant-pollinator web \\
+        313   & 3 & \cite{Kaiser-Bunbury2009}  & terrestrial &       & No    & Plant-pollinator web \\
+        314   & 3 & \cite{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        315   & 3 & \cite{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        316   & 3 & \cite{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        317   & 3 & \cite{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        318   & 3 & \cite{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        319   & 3 & \cite{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
+        320   & 3 & \cite{Ruzicka2012}    & marine & 42 - 49 N & Yes   &       \\
+        321   & 3 & \cite{Ruzicka2012}    & marine & 43 - 49 N & Yes   &       \\
+        322   & 3 & \cite{Ruzicka2012}    & marine & 44 - 49 N & Yes   &       \\
+        323   & 3 & \cite{Ruzicka2012}    & marine & 45 - 49 N & Yes   &       \\
+        324   & 3 & \cite{Ruzicka2012}    & marine & 46 - 49 N & Yes   &       \\
+        325   & 3 & \cite{Lewis2002}  & terrestrial &       & No    & Host-parasitoid web \\
+        326   & 3 & \cite{Lewis2002}  & terrestrial &       & No    & Host-parasitoid web \\
+        327   & 3 & \cite{Kelleway2010}  & stream & 29,13 S & Yes   &       \\
+        328   & 3 & \cite{Kelleway2010}  & stream & 29,20,0 S & Yes   &       \\
+        329   & 3 & \cite{Kelleway2010}  & stream & 29,35 S & Yes   &       \\
+        330   & 3 & \cite{Kelleway2010}  & stream & 29,13 S & Yes   &       \\
+        331   & 3 & \cite{Kelleway2010}  & stream & 29,20,0 S & Yes   &       \\
+        332   & 3 & \cite{Huang2008}  & stream & 31.70 N & Yes   &       \\
+        333   & 3 & \cite{Link2002}    & marine & 33,51 - 44,49 N & Yes   &       \\
+        334   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,36 N & Yes   &       \\
+        335   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
+        336   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,36 N & Yes   &       \\
+        337   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
          \hline
@@
         \hline
-        338   & 3 & \citet{Torres2013}  & marine &       & No    & Could not locate original source \\
-        339   & 3 & \citet{Bulman2001}  & marine & 37-39 S & Yes   &       \\
-        340   & 3 & \citet{Smith2007}  & marine & 74-78 S & Yes   &       \\
-        341   & 3 & \citet{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
-        342   & 3 & \citet{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes   &       \\
-        343   & 3 & \citet{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
-        344   & 3 & \citet{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
-        345   & 3 & \citet{Boit2012}  & lake  & 47,38,10 N & Yes   &       \\
-        346   & 3 & \citet{Rayner2010}  & stream & 17,7 S & Yes   &       \\
-        347   & 3 & \citet{Motta2005}  & stream & 23,03 S & Yes   &       \\
-        348   & 3 & \citet{Douglass2011}    & marine & 37,13 N & Yes   &       \\
-        349   & 3 & \citet{Douglass2011}    & marine & 37,13 N & Yes   &       \\
-        350   & 3 & \citet{Douglass2011}    & marine & 37,13 N & Yes   &       \\
-        351   & 3 & \citet{Warren1989}     & lake  &       & No    & Could not locate original source \\
-        352   & 3 & \citet{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
-        353   & 3 & \citet{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
-        354   & 3 & \citet{Goldwasser1993}  & terrestrial & 18,03 N & Yes   &       \\
-        355   & 3 & \citet{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
-        356   & 3 & \citet{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
-        357   & 3 & \citet{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
-        358   & 3 & \citet{Schroter2003}  & terrestrial &       & No    & Generalized scheme \\
-        359   & 3 & \citet{Baiser2012}  & lake  &       & No    & Study site unclear \\
+        338   & 3 & \cite{Torres2013}  & marine &       & No    & Could not locate original source \\
+        339   & 3 & \cite{Bulman2001}  & marine & 37-39 S & Yes   &       \\
+        340   & 3 & \cite{Smith2007}  & marine & 74-78 S & Yes   &       \\
+        341   & 3 & \cite{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
+        342   & 3 & \cite{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes   &       \\
+        343   & 3 & \cite{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
+        344   & 3 & \cite{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
+        345   & 3 & \cite{Boit2012}  & lake  & 47,38,10 N & Yes   &       \\
+        346   & 3 & \cite{Rayner2010}  & stream & 17,7 S & Yes   &       \\
+        347   & 3 & \cite{Motta2005}  & stream & 23,03 S & Yes   &       \\
+        348   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
+        349   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
+        350   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
+        351   & 3 & \cite{Warren1989}     & lake  &       & No    & Could not locate original source \\
+        352   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
+        353   & 3 & \cite{Poepperl2003}  & stream & 54,06 N & No    & describes compartments, not species \\
+        354   & 3 & \cite{Goldwasser1993}  & terrestrial & 18,03 N & Yes   &       \\
+        355   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
+        356   & 3 & \cite{Cohen2003}    & lake  & 46,13 N & Yes   &       \\
+        357   & 3 & \cite{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
+        358   & 3 & \cite{Schroter2003}  & terrestrial &       & No    & Generalized scheme \\
+        359   & 3 & \cite{Baiser2012}  & lake  &       & No    & Study site unclear \\
         \hline
@@
     The scaling relationships between link density ($Z$) and species richness ($S$)
-    has been shown to be a power law~\citep{Riede2010} of the form
+    has been shown to be a power law~\cite{Riede2010} of the form
 
@@
 
-    \noindent Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
-    Specifically, equation~(\ref{Power}) implies a normally-distributed, additive error and equation~(\ref{Loglog}) a lognormal,
-    multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
-    over another, we follow the recommendations in\citet{Xiao2011} and compared the two
-    model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
+    \noindent Although these relationships are very similar, they imply different error distributions~\cite{Xiao2011}.
+    Specifically, equation~(\ref{Power}) implies a normally-distributed, additive 
+    error and equation~(\ref{Loglog}) a lognormal,
+    multiplicative error. As we have no \emph{a priori} reason to believe that our dataset 
+    has one error distribution over another, we follow the recommendations in~\cite{Xiao2011} and compared the two
+    model formulations explicitly. The model with the error distribution that best approximates the one
+    observed in the empirical
     data was then used to test for potential effects of latitude.
@@
     species richness and vulnerability have not been explicitly examined (but see scaling 
-    relationships for the standard devaitions of each property in\citet{Riede2010}), we expect that they will follow
+    relationships for the standard devaitions of each property in~\cite{Riede2010}), we expect that they will follow
     power laws similar to that of the relationship between species richness and links per species.
@@
 a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
-any effects of habitat type or latitude (black line, N=166 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
+any effects of habitat type or latitude (black line, N=196 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
 observed values correcting for the effects of habitat type and latitude. }
@@
 line) with its 95\% confidence interval (in grey),
-based on N=166 empirical food webs. Latitude is 
+based on N=196 empirical food webs. Latitude is 
 given in degrees from the equator
@@
 types and over latitude. For each property we show the scaling exponent for the proportion of
-basal resources (black line) with its 95\% confidence interval (in grey), based on N=166 
+basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
 empirical food webs. Latitude is given in degrees
@@
 intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
-N=166 empirical food webs. Latitude is given in degrees
+N=196 empirical food webs. Latitude is given in degrees
 from the equator regardless of direction.}
@@
 types and over latitude. For each property we show the scaling exponent for the proportion of
-top predators (black line) with its 95\% confidence interval (in grey), based on N=166 
+top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
 empirical food webs. Latitude is given in degrees

### 2015-09-03 manuscript/latitudepaper.tex
Finished and spellchecked.

@@
 % \usepackage[round]{natbib}
+\usepackage[numbers,sort&compress]{natbib}
 
@@
 richness and average generality, vulnerability, and links per species across a
-set of 163 empirical food webs.  We also investigated scaling relationships
+set of 196 empirical food webs.  We also investigated scaling relationships
 between the three food-web properties and the proportions of the web made up
@@
 
-  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\cite{Vazquez2004}. 
-  This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
-  turn should evolve smaller niches~\cite{Vazquez2004}. These narrow niches should therefore allow more species to 
-  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics~\cite{Brown2004}
-  may result in a broader niche space~\cite{Davies2007} which could also sustain greater biodiversity even if niche 
-  sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocally 
-  supported~\cite{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
+  One proposed link between species richness and latitude is the 
+  ``latitude-niche breadth hypothesis''~\cite{Vazquez2004}.  This hypothesis 
+  predicts that decreased seasonality in the tropics should lead to more stable
+  populations, which in turn should evolve smaller niches~\cite{Vazquez2004}.
+  These narrow niches should therefore allow more species to  coexist in the
+  tropics than at higher latitudes. Alternatively, the higher productivity of
+  the tropics~\cite{Brown2004} may result in a broader niche
+  space~\cite{Davies2007} which could also sustain greater biodiversity even
+  if niche  sizes are globally similar. Although the assumptions of the
+  latitude-niche breadth hypothesis are only equivocally
+  supported~\cite{Vazquez2004}, it remains a compelling potential mechanism
+  for the latitudinal gradient in species
   richness~\cite{Lappalainen2006,Krasnov2008,Slove2010}.
 
-  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
-  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\cite{Elton1927,Leibold2010}) of species within food webs.
-  Specifically, narrower niches in the tropics would equate to
-  greater specialisation (narrower niches) while constant niche sizes but
-  greater productivity would translate to constant specialisation and niche
-  width across latitude (Fig.~\ref{concept}).
-  Attempts to unravel these effects, however,
-  are complicated by known relationships between species richness and many other network properties~\cite{Riede2010}. 
-  For example,
-  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\cite{Marra1997,Dyer2007};
-  but see~\cite{Schleuning2012}). However,
-  average numbers of links per species tend to increase in larger food webs~\cite{Dunne2006,Riede2010}. This means
-  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness.
+  If the latitude-niche breadth hypothesis is correct, there should also be
+  direct relationships between latitude and the degree of specialisation
+  (i.e., the breadth of the Eltonian niche; ~\cite{Elton1927,Leibold2010}) of
+  species within food webs. Specifically, narrower niches in the tropics would
+  equate to greater specialisation (narrower niches) while constant niche
+  sizes but greater productivity would translate to constant specialisation
+  and niche width across latitude (Fig.~\ref{concept}). Attempts to unravel
+  these effects, however, are complicated by known relationships between
+  species richness and many other network properties~\cite{Riede2010}.  For
+  example, narrower niches imply fewer links per species (i.e., greater
+  specialisation) in the tropics (\cite{Marra1997,Dyer2007}; but
+  see~\cite{Schleuning2012}). However, average numbers of links per species
+  tend to increase in larger food webs~\cite{Dunne2006,Riede2010}. This means
+  that a latitudinal effect on specialisation may be obscured by a latitudinal
+  gradient in species richness.
 
   If this is the case, it may still be possible to uncover effects of latitude
-  on specialisation by examining the shape of the scaling  relationship
-  between specialisation and species richness over changing latitude. 
-  By testing whether latitude affects the scaling of each property with
-  species richness, we test for the effects of latitude on specialisation
-  implied by the ``latitude-niche breadth hypothesis'' (Fig.~\ref{concept}). 
-  If the scaling of specialisation with species richness is weaker in the 
-  tropics (i.e., if species gain fewer links, predators, or prey as the size 
-  of the network increases), this will indicate narrower niches at the tropics. 
-  If, however, the scaling of specialisation with species richness does not 
-  vary over latitude, this will indicate that niches are similarly-sized
-  worldwide but that there is a broader niche space in the tropics.
-  Additionally, as food webs describing different ecosystem types may differ
-  in their topology~\cite{Dunne2004,Shurin2006} and may be subject to different
-  latitudinal gradients in species richness~\cite{} or productivity~\cite{},
-  we also explored the differences in scaling relationships across ecosystem types.
-  Here, we use three measures of specialisation; mean links per species, mean
-  generality (number of prey), and mean vulnerability (number of predators).
+  on specialisation by examining the shape of the scaling relationship between
+  specialisation and species richness over changing latitude.  By testing
+  whether latitude affects the scaling of each property with species richness,
+  we test for the effects of latitude on specialisation implied by the
+  ``latitude-niche breadth hypothesis'' (Fig.~\ref{concept}).  If the scaling
+  of specialisation with species richness is weaker in the  tropics (i.e., if
+  species gain fewer links, predators, or prey as the size  of the network
+  increases), this will indicate narrower niches at the tropics.  If, however,
+  the scaling of specialisation with species richness does not  vary over
+  latitude, this will indicate that niches are similarly-sized worldwide but
+  that there is a broader niche space in the tropics. Additionally, as food
+  webs describing different ecosystem types may differ in their
+  topology~\cite{Dunne2004,Shurin2006}, we also explored the differences in
+  scaling relationships across ecosystem types. Here, we use three measures of
+  specialisation; mean links per species, mean generality (number of prey),
+  and mean vulnerability (number of predators).
 
@@
 
-    We compiled a list of 166 empirical food webs from
+    We compiled a list of 196 empirical food webs from
     multiple sources (see \emph{Appendix S1} for web origins and selection
@@
     given, obtained estimated coordinates using Google Earth~\cite{GoogleEarth}.
-    We then divided the species in each web into basal resources (those species with
-    consumers but no prey), top predators (those species with prey but no predators),
-    and intermediate consumers (species with both predators and prey, including cannibalistic
-    species). We grouped food web by ecosystem type (stream, N=71; lake, N=47; marine, 
+    If a range of latitudes (e.g. $42-49^{\circ}N$) was provided, we used the midpoint
+    of this range. We grouped food web by ecosystem type (stream, N=71; lake, N=47; marine, 
     N=28; estuarine, N=18; and terrestrial, N=31) according to their designation in 
@@
     marine, lake, and terrestrial networks with estuarine
-    networks providing the intercept) and $\epsilon_{i}$ is a residual error term.
+    networks corresponding to $E_{i}=0$) and $\epsilon_{i}$ is a residual error term.
     The logarithmic formulation of this model is
@@
 
-    We then simplified each model. To do this, we calculated the AIC of the
-    maximal model as well as the AIC's of a suite of candidate simplified
-    models identified using the R~\cite{R} function dredge from package
-    MuMIn~\cite{MuMIn}.  Simplified models were obtained by using the same
-    procedure as described above. Parameter estimates for the simplified models
-    varied very little across either series of jackknifes (\emph{Appendix S3}).
+    We then simplified each model following the procedure described above.
+    As a supplemental check to ensure that variation in sampling effort
+    across food webs was not responsible for the trends we observed, we then
+    repeated our analyses using jackknifed data sets in which we 1) sequentially
+    removed each food web in the dataset and 2) sequentially removed sets of food webs
+    that shared a common author. The first jackknife essentially controls for the
+    influence of any single outlier, while the second controls for the influence
+    of particular research groups, some of which contributed large numbers of food
+    webs (up to 27) to the dataset. Parameter estimates for the simplified models 
+    varied very little across either jackknife test (see \emph{Appendix S3} for details),
+    indicating that the trends we observed were not due to either strong outliers or
+    to substantial differences in sampling effort across research groups.
     % If several models shared the fewest
@@
 
-  Contrary to the expected latitudinal gradient, the best-fit version of
-  equation~(\ref{Latfull}) for species richness did not  include a signficant
-  effect of latitude for any  ecosystem type. Further, there were no
+  Link density (mean number of feeding links per species), generality (mean
+  number of prey per species), and vulnerability (mean number of predators per
+  species) were strongly and positively correlated ($R^2$=0.891 for link
+  density and generality, $R^2$\textgreater0.999 for link density and
+  vulnerability, and $R^2$=0.890 for generality and vulnerability). Contrary
+  to the expected latitudinal gradient, the best-fit version of
+  equation~(\ref{Latfull}) for species richness did not include a significant
+  effect of latitude for any ecosystem type. Further, there were no significant
   relationships between link density, generality, or vulnerability with
-  latitude for any ecosystem type. Link density (mean number of feeding links
-  per species), generality (mean number of prey per species), and
-  vulnerability (mean number of predators per species) were strongly and
-  positively correlated ($R^2$=0.891 for link density and generality,
-  $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.890
-  for generality and vulnerability).
+  latitude for any ecosystem type.
 
-  Each property increased with increasing
+  Each measure of specialisation increased with increasing
   species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
   $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
-  Fig~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
+  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
@@
   properties such as generality might be due to the latitudinal gradient in
-  species richness. In this dataset, however, we did not find overall
+  species richness. In this dataset, however, we found no evidence to support
   latitudinal gradients in species richness, links per species, generality, or
@@
   studies. This could result in food webs describing species-rich tropical
-  communities omitting more species and links than studies of species-poor arctic
-  communities. In addition, it is worth noting that gradients in species
-  richness are generally measured for a single taxonomic group at a
-  time~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is possible
-  that these taxa are not well-represented in our food webs and that the
-  dominant taxa in them do not have an underlying latitudinal gradient in
-  richness. In either case, the lack of a strong association between species
-  richness and latitude in any ecosystem type means that any effect of
-  latitude on other scaling relationships is not being driven by an underlying
-  latitudinal gradient in species richness. The lack of confounding effects of
-  latitude allows us to more clearly assess effects of latitude on scaling
-  with species richness and proportions of species in different trophic
-  levels.
+  communities omitting more species and links than studies of species-poor
+  arctic communities if research groups spend similar person-hours assembling
+  webs and can observe similar numbers of species and links per person-hour.
+  In addition, it is worth noting that gradients in species richness are
+  generally measured for a single taxonomic group at a
+  time~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is
+  possible that these taxa are not well-represented in our food webs and that
+  the dominant taxa that are represented do not have an underlying latitudinal
+  gradient in richness. In either case, the lack of a strong association
+  between species richness and latitude in any ecosystem type means that any
+  effect of latitude on other scaling relationships is not being driven by an
+  underlying latitudinal gradient in species richness. This is fortunate since
+  the lack of confounding effects of latitude allows us to more clearly assess
+  effects of latitude on scaling with species richness.
 
@@
   niche space depending on temperature and productivity, it may be that species
-  diversity itself affects the niche space available to species (although climate
+  diversity itself affects the biotic niche space available to species (although climate
   may affect speciation rates and therefore the diversity in a region~\cite{Currie2004}). 
@@
   Unlike other ecosystem types, the scaling of generality in lake and stream
-  food webs was stronger (i.e.,generality increased more steeply with
+  food webs was stronger (i.e., generality increased more steeply with
   increasing species richness) in higher-latitude food webs. In lake food webs,
   this trend was echoed in the scaling relationships between species richness
-  and links per species and vulnerability. This means that species in tropical
+  and vulnerability and links per species. This means that species in tropical
   freshwater communities gain fewer additional feeding links per additional
@@
   greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
-  and a higher proportion of specialists. That freshwater food webs supported
-  the hypothesis of narrower niches in the tropics, while other ecosystem types
-  did not, is particularly exciting given that these ecosystems (especially streams)
-  are known for being highly variable and that seasonal variability is one of the
-  proposed drivers of the latitude-niche breadth hypothesis~\cite{Vazquez2004}.
+  and a higher proportion of specialists.
 
-  Both streams and lakes can experience severe changes in water temperature and volume
-  (e.g., floods, drying, freezing) that remove food or other resources (notably oxygen
-  during freezing events~\cite{})~\cite{Winterbourn1997, one for lakes}. These events
-  are often linked to seasonal events such as snowmelts (although not always-- New Zealand
-  streams are a notable exception~\cite{Winterbourn1997}). Further, both temperate streams 
-  and lakes tend to experience seasonal strong pulses of allochthonous inputs (e.g., fallen leaves, 
-  terrestrial invertebrates~\cite{Nakano2001,Zeng2008,}; again New Zealand streams are an
-  exception to this trend~\cite{Winterbourn1997}). These trends combined mean that,
-  relative to larger, more abiotically stable estuarine and marine communities, freshwater
-  food webs may experience high turnover in both community composition and productivity.
-  Even in New Zealand streams, which experience unpredictable flooding and do not typically
-  receive seasonal allochthonous subsidies, more frequent disturbance is associated with lower
-  diversity and density of insect larvae, and lower species richness~\cite{Winterbourn1997}.
+  That freshwater food webs supported the hypothesis of narrower niches in the
+  tropics --while other ecosystem types did not-- is noteworthy given that
+  these ecosystems (especially streams) are known for being highly variable
+  and that seasonal variability is one of the proposed drivers of the
+  latitude-niche breadth hypothesis~\cite{Vazquez2004}. Both streams and lakes
+  can experience severe changes in water temperature and volume (e.g., floods,
+  drying, freezing) that remove food or other resources (notably oxygen during
+  freezing events)~\cite{Winterbourn1997,Meding2001}. These events are often
+  linked to seasonal events such as snowmelts or summer
+  drought~\cite{Winterbourn1997}).Further, both temperate streams and lakes
+  tend to experience seasonal strong pulses of allochthonous inputs (e.g.,
+  fallen leaves,terrestrial
+  invertebrates~\cite{Nakano2001,Lennon2004,Zeng2008}. These trends combined
+  mean that, relative to larger, more abiotically stable estuarine and marine
+  communities, freshwater food webs may experience high turnover in both
+  community composition and productivity. Notable exceptions from the above
+  trends are New Zealand stream communities (representing 31 of the 71 stream
+  food webs in our dataset), which experience unpredictable flooding and
+  drying throughout the year and do not receive seasonally pulsed
+  subsidies~\cite{Winterbourn1997,Winterbourn1981}. However, as this subset of
+  webs is very tightly grouped in latitude ($44.64-46.41^{\circ}$S, within an
+  overall range of $23-69.02^{\circ}$), it is unlikely that they have greatly
+  influenced our results (see also \emph{Appendix S3}). Moreover, just as in
+  highly-variable communities where said variation is more seasonal, New
+  Zealand communities are typified by ecological
+  generalists~\cite{Winterbourn1997,Winterbourn1981} implying that they appear
+  to fit the general pattern of streams worldwide.
 
-  High variation in the abundances of different resources could select for more generalist consumers
-  in temperature freshwater communities, as seen in our dataset. In this case the non-seasonality of
-  New Zealand streams, which account for 31/71 of the stream webs in our dataset, supports this
-  hypothesis as the New Zealand stream fauna are known to be ecological generalists,
-  probably as a result of variability of their habitat~\cite{Winterbourn1997}. In other freshwater
-  communities the sequence of available resources might be more predictable, but the ability to 
-  switch between different prey is not likely to be less important. Importantly, while terrestrial
-  communities are also strongly seasonal at high latitudes, and can also obtain significant allochthonous
-  inputs~\cite{Nakano2001}, terrestrial consumers tend to be more morphologically specialized for
-  feeding on particular prey~\cite{Liem1990}. This means that primarily gape-limited aquatic consumers
-  tend to be more general across all types of aquatic habitats~\cite{Liem1990,Shurin2006}.
-  The key to this this explanation of the differences between freshwater and marine and estuarine 
-  ecosystems is whether the former experience more severe seasonal variation. Although we are not
-  aware of any study explicitly comparing seasonal variation in freshwater and saltwater or brackish
-  food webs in a similar location, we believe that freshwater ecosystems are indeed likely to 
-  experience more severe changes because of their small size. While oceans and estuaries certainly
-  do vary in terms of water temperature and nutrients over the course of a year~\cite{}, because they
-  are not isolated in the midst of a terrestrial matrix these changes are buffered. Further, estuaries
-  and especially marine environments do not typically freeze over or dry up completely-- these dramatic
-  changes are unique to freshwater communities.
+  Importantly, while terrestrial communities are also strongly seasonal at
+  high latitudes, and can also obtain significant allochthonous
+  inputs~\cite{Nakano2001}, terrestrial consumers tend to be more
+  morphologically specialised for feeding on particular prey~\cite{Liem1990}.
+  This means that primarily gape-limited aquatic consumers tend to be more
+  general across all types of aquatic habitats~\cite{Liem1990,Shurin2006}. The
+  key to this this explanation of the differences between freshwater and
+  marine and estuarine  ecosystems is whether the former experience more
+  severe seasonal variation. Although we are not aware of any study explicitly
+  comparing seasonal variation in freshwater and saltwater or brackish food
+  webs in a similar location, we believe that freshwater ecosystems are indeed
+  likely to  experience more severe changes because of their small size. While
+  oceans and estuaries certainly do vary in terms of water temperature and
+  nutrients over the course of a year~\cite{Baird1989}, because they are not isolated
+  in the midst of a terrestrial matrix these changes are likely to be slower
+  and milder than in freshwaters. Net primary productivity in particular is
+  much more variable over the course of a year in non-marine communities~\cite{Field1998},
+  suggesting that niche breadths may also be more variable over the course of the year.
 
@@
   hypotheses of narrower niches in the tropics~\cite{Vazquez2004} and broader
-  niche space in the tropics~\cite{Davies2007}; both have merit but appear to
-  apply to different systems.
+  niche space in the tropics~\cite{Davies2007}. Our study indicates that both 
+  have merit but would appear to apply to different systems.
 
@@
 
-\section*{Competing interestes}
+\section*{Competing interests}
 
@@
   ARC, DBS, and TNR designed the study, ARC collected
-  published data, performed the analyses, and drafted the 
-  article. DBS and TNR substantially revised the article;
+  published data, performed the analyses, and wrote the
+  first draft. DBS and TNR substantially revised the article;
   all authors approved the final version.
@@
   This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
-  graduate scholarship (to ARC), a Rutherford XXXYYY (to DBS), and an NSERC Discovery Grant to TNR.
+  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
+  Rutherford Discovery Fellowship, both administered by the Royal Society of New Zealand 
+  (to DBS), and an NSERC Discovery Grant (to TNR).
 
-1
 \newpage
-\bibliographystyle{vancouver}%Compile with vancouver.bst style file
+\bibliographystyle{prsb}%Compile with vancouver.bst style file
 \bibliography{noISN}% your .bib file(s)
@@
 
-[[Need to find a spot to refer to the conceptual figure]]
 \begin{figure}[h]
@@
 be larger towards the poles, where each additional species in the food-web will have a larger niche 
-(i.e., more feeding links). If hypothesis 2 is true, then the exponent of thisdistribution should not vary significantly over latitude.}
+(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this distribution should not vary significantly over latitude.}
 \label{concept}
@@
 effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
-type and latitude. Note that in all cases estuarine food webs were used as the baseline 
+type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
 ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
-latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
+latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
 we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
-ecosystems as a baseline (black line, N=166 food webs). For a figure with the uncorrected values,
-see Fig.~\emph{S1}, \emph{Appendix S4}.}
+ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
+see Fig.~\emph{S7}, \emph{Appendix S4}.}
 \label{props_v_lat}
@@
 \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density with species richness across ecosystem
+\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
 types and over latitude. We show the estimated scaling exponent for species richness (black
-line) with its 95\% confidence interval (in grey), based on N=166 empirical food webs.
-Latitude is given in degrees from the equator regardless of direction. The
-behaviour of exponents for the scaling of generality and vulnerability with
-species richness was very  similar to those for link density, except for the
-scaling of generality in streams where  the size of the exponent increased
-towards the poles. See Fig.~\emph{S2, Appendix 5} for  all scaling
-relationships.} \label{S} \end{figure}
+line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
+Latitude is given in degrees from the equator regardless of direction.} \label{S} \end{figure}
 

### 2015-09-03 manuscript/supplement.tex
Finished and spellchecked.

@@
 \usepackage{setspace}
-\usepackage[round]{natbib}
+\usepackage[numbers,sort&compress]{natbib}
 \usepackage{float}
@@
 \title{Supplementary Information}
-\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
-\date{\footnotesize$^1$School of Biological Sciences\\University of Canterbury\\
+\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
+\date{\footnotesize$^1$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
 Private Bag 4800\\Christchurch 8140, New Zealand \\
@@
   describing competitive interactions. Finally, we eliminated 2 webs
-  describing  inferred interactions in an extinct community, 10 ``generalized
+  describing  inferred interactions in an extinct community, 10 ``generalised
   schemes'' that were not based on direct field data, and 4 webs where it was
@@
         16    & 3 & \cite{Copeland1974}    & estuary &       & No    & Could not locate original source \\
-        17    & 3 & \cite{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalized scheme \\
+        17    & 3 & \cite{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalised scheme \\
         18    & 3 & \cite{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
@@
         28    & 3 & \cite{Paviour-Smith1956}  & estuary & 45,51,30 S & Yes   &       \\
-        29    & 3 & \cite{Dunbar1953}  & marine &       & No    & Generalized scheme \\
-        30    & 3 & \cite{Mackintosh1964}  & marine &       & No    & Generalized scheme \\
+        29    & 3 & \cite{Dunbar1953}  & marine &       & No    & Generalised scheme \\
+        30    & 3 & \cite{Mackintosh1964}  & marine &       & No    & Generalised scheme \\
         31    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
@@
         39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
-        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalized scheme \\
+        40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalised scheme \\
         41    & 3 & \cite{Parin1970}  & marine &       & No    & Could not locate original source \\
@@
         49    & 3 & \cite{Simenstad1978}    & marine &       & No    & Extinct species \\
-        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalized scheme \\
+        50    & 3 & \cite{Nybakken1982}    & marine &       & No    & Generalised scheme \\
         51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
@@
         91    & 3 & \cite{Cohen1990}  & terrestrial &       & No    & Could not locate original source \\
-        92    & 3 & \cite{Swan1961}  & terrestrial &       & No    & Generalized scheme \\
+        92    & 3 & \cite{Swan1961}  & terrestrial &       & No    & Generalised scheme \\
         93    & 3 & \cite{Pattie1966}    & terrestrial & 45 N  & Yes   &       \\
@@
         102   & 3 & \cite{Shushkina1979}  & marine & 10 S - 15 N & Yes   &       \\
-        103   & 3 & \cite{Petipa1979}  & marine &       & No    & Generalized scheme \\
+        103   & 3 & \cite{Petipa1979}  & marine &       & No    & Generalised scheme \\
         104   & 3 & \cite{Menge1976}  & marine & 4,48,04 N & Yes   &       \\
@@
         124   & 3 & \cite{Collins1976}  & stream & 44,34 N & Yes   &       \\
-        125   & 3 & \cite{Landry1977}  & marine &       & No    & Generalized scheme \\
+        125   & 3 & \cite{Landry1977}  & marine &       & No    & Generalised scheme \\
         126   & 3 & \cite{Larsson1978}  & lake  & 61,26,00 N & Yes   &       \\
@@
         209   & 3 & \cite{Minshall1967}    & stream & 37,18,26 N & Yes   &       \\
-        210   & 3 & \cite{Percival1929}     & stream &       & No    & Generalized scheme \\
+        210   & 3 & \cite{Percival1929}     & stream &       & No    & Generalised scheme \\
         211   & 3 & \cite{Ricker1935}  & stream &       & No    & Could not locate original source \\
@@
         357   & 3 & \cite{Yodzis1998} & marine & 34,21 - 16 S & No    & Study site unclear \\
-        358   & 3 & \cite{Schroter2003}  & terrestrial &       & No    & Generalized scheme \\
+        358   & 3 & \cite{Schroter2003}  & terrestrial &       & No    & Generalised scheme \\
         359   & 3 & \cite{Baiser2012}  & lake  &       & No    & Study site unclear \\
@@
     species richness and vulnerability have not been explicitly examined (but see scaling 
-    relationships for the standard devaitions of each property in~\cite{Riede2010}), we expect that they will follow
+    relationships for the standard deviations of each property in~\cite{Riede2010}), we expect that they will follow
     power laws similar to that of the relationship between species richness and links per species.
@@
     In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
-    species richness. We then repeated this analysis 
-    to model the scaling of link density, generality, 
-    and vulnerability with the proportions of basal 
-    resources, intermediate consumers, and top predators
-    in a food web.
+    species richness.
 
@@
 
-    When considering the relationships between species richness or the proportions 
-    of basal resources, intermediate consumers, or top predators, and all response variables 
+    When considering the relationships between species richness and all response variables 
     (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
@@
 
+\newpage
+
 \subsection*{Appendix S3: Testing for effects of sampling effort}
@@
     particularly unusual food webs, or by unusually well- or poorly-sampled webs 
-    derived from any particular group, we performed two jackknife tests of our 
+    derived from any particular research group, we performed two jackknife tests of our 
     results. In the first test, we removed one web from our dataset and re-fit 
     our models, then repeated this process for all webs in the dataset. We then 
-    plotted the estimates for each coefficient in each of our models in order to 
+    compared the estimates for each coefficient in each of our models in order to 
     determine whether the omission of any web dramatically changed the resulting 
-    model. In the second test, we removed groups of webs assembled by a given 
+    model and conclusions. In the second test, we removed groups of webs assembled by a given 
     author (or authors, where two or more authors assembled identical sets of 
@@
 
-    None of our models were affected by the removal of any single food web.
-    Estimates of co-efficients from all jackknifed datasets were extremely
-    similar (Figs.~\ref{LS_web,Gen_web,Vul_web}). Moreover, our models were also robust to the removal
-    of any given author (Figs.~\ref{LS_auth,Gen_auth,Vul_auth}). We are therefore very confident that,
-    while there are undoubtedly differences in the methods used to compile food webs,
-    these differences are not driving the trends we report in this study.
-
-    \begin{figure}[h]
-    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_web.eps}}
+    None of our models were affected by the removal of any single food web
+    or by the removal of a set of webs compiled by a common researcher (or group of
+    researchers).
+    Estimates of coefficients from all jackknifed datasets were extremely
+    similar (Figs.~\ref{LS_web},\ref{Gen_web},\ref{Vul_web},\ref{LS_auth},\ref{Gen_auth},\ref{Vul_auth}). 
+    We are therefore very confident that, while there are undoubtedly differences 
+    in the methods used to compile food webs, these differences provide an
+    insufficient explanation for the trends we report in this study.
+
+\newpage
+
+    \begin{figure}[!h]
+    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/LS_web.eps}}
     \caption{Estimates of the coefficients for scaling of link density with species richness
@@
 
-    \begin{figure}[h]
-    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_web.eps}}
+\newpage
+
+    \begin{figure}[!h]
+    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Gen_web.eps}}
     \caption{Estimates of the coefficients for scaling of generality with species richness
@@
 
-    \begin{figure}[h]
-    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_web.eps}}
+\newpage
+
+    \begin{figure}[!h]
+    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Vul_web.eps}}
     \caption{Estimates of the coefficients for scaling of vulnerability with species richness
@@
 
-    \begin{figure}[h]
-    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/LS_author.eps}}
+\newpage
+
+    \begin{figure}[!h]
+    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/LS_author.eps}}
     \caption{Estimates of the coefficients for scaling of link density with species richness
@@
 
-    \begin{figure}[h]
-    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Gen_author.eps}}
+\newpage
+
+    \begin{figure}[!h]
+    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Gen_author.eps}}
     \caption{Estimates of the coefficients for scaling of generality with species richness
@@
 
-    \begin{figure}[h]
-    \centerline{\includegraphics*[width=.8\textwidth]{Figures/Jackknife/Vul_author.eps}}
+\newpage
+
+    \begin{figure}[!h]
+    \centerline{\includegraphics*[height=.75\textheight]{Figures/Jackknife/Vul_author.eps}}
     \caption{Estimates of the coefficients for the scaling of vulnerability with species richness
@@
 
-\subsection*{Appendix S4: Scaling relationships by trophic level}
-
-  \subsubsection*{Methods}
-
-    We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
-    in the ways that scaling relationships with species richness might
-    be affected by changes to the distribution of species among trophic levels. To
-    that end, we repeated our analyses replacing species richness with the
-    proportion of basal resources, proportion of intermediate consumers,
-    or proportion of top predators. All model fitting procedures were identical to those
-    described for species richness. The model simplicication procedure was similar to
-    the procedure described for species richness, except that in some cases there were
-    multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
-    In these cases, we defined the best-fitting model as the model with the lowest AIC in the
-    set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.
-
-  \subsubsection*{Results}
-
-    The relationships between latitude and the proportions of species at each
-    trophic level were more complex than the flat relationship between latitude
-    and species richness in this dataset.  The proportion of basal resources
-    increased towards the poles in stream webs
-    ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
-    with latitude in estuarine, marine, lake, or terrestrial  food webs
-    ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
-    intermediate consumers decreased towards the poles in all ecosystem types
-    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
-    $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
-    in a food web,  meanwhile, decreased towards the poles in lake and  stream
-    food webs but did not vary in other ecosystem types
-    ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
-    $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
-
-    Unlike species richness, only generality showed an overall increase with
-    increasing proportions of basal resources in a web ($\beta_0$=0.019,
-    $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
-    link density, generality, and vulnerability, respectively;
-    Fig.~\ref{props_v_lat}). In each case, however, there were substantial
-    effects of latitude on the scaling relationships. Thus, the scaling
-    exponents for link density and vulnerability were negative for estuarine,
-    lake, and stream communities and became more negative towards the poles
-    ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
-    $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
-    density and vulnerability in marine and terrestrial communities, the overall
-    effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
-    $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
-    $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
-    $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
-    that there was weak scaling at most latitudes. In contrast, the scaling
-    exponent of generality with the proportion of basal resources was positive
-    near the equator and negative near the poles in estuarine, lake, and stream
-    communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
-    very little change in the scaling exponents for marine and terrestrial
-    communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
-    $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
-
-    As with species richness, link density, generality, and vulnerability
-    generally increased with the proportion of intermediate consumers in a web
-    ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
-    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
-    The best-fit models for link density and vulnerability did not include
-    any effect of latitude. In contrast, the strength of the scaling relationship
-    for generality increased weakly towards the poles in estuarine, marine, and
-    terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
-    towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
-    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).
-
-    In contrast to the generally positive scaling relationships above, link
-    density, generality, and vulnerability decreased as the proportion of top
-    predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
-    $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
-    Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
-    strength of this scaling did not vary significantly with latitude
-    ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
-    $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
-    In stream and terrestrial food webs, however, scaling was more strongly negative in the 
-    tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
-    and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
-    $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
-    for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
-    for latitude in any ecosystem type.
-
-\newpage
-
-\subsection*{Appendix S5: Supplemental Figures}
-
-\begin{figure}[h]
-\centerline{\includegraphics*[width=.75\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}}
+% \subsection*{Appendix S4: Scaling relationships by trophic level}
+
+%   \subsubsection*{Methods}
+
+%     We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
+%     in the ways that scaling relationships with species richness might
+%     be affected by changes to the distribution of species among trophic levels. To
+%     that end, we repeated our analyses replacing species richness with the
+%     proportion of basal resources, proportion of intermediate consumers,
+%     or proportion of top predators. All model fitting procedures were identical to those
+%     described for species richness. The model simplicication procedure was similar to
+%     the procedure described for species richness, except that in some cases there were
+%     multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
+%     In these cases, we defined the best-fitting model as the model with the lowest AIC in the
+%     set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.
+
+%   \subsubsection*{Results}
+
+%     The relationships between latitude and the proportions of species at each
+%     trophic level were more complex than the flat relationship between latitude
+%     and species richness in this dataset.  The proportion of basal resources
+%     increased towards the poles in stream webs
+%     ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
+%     with latitude in estuarine, marine, lake, or terrestrial  food webs
+%     ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
+%     intermediate consumers decreased towards the poles in all ecosystem types
+%     except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
+%     $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
+%     in a food web,  meanwhile, decreased towards the poles in lake and  stream
+%     food webs but did not vary in other ecosystem types
+%     ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
+%     $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
+
+%     Unlike species richness, only generality showed an overall increase with
+%     increasing proportions of basal resources in a web ($\beta_0$=0.019,
+%     $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
+%     link density, generality, and vulnerability, respectively;
+%     Fig.~\ref{props_v_lat}). In each case, however, there were substantial
+%     effects of latitude on the scaling relationships. Thus, the scaling
+%     exponents for link density and vulnerability were negative for estuarine,
+%     lake, and stream communities and became more negative towards the poles
+%     ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
+%     $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
+%     density and vulnerability in marine and terrestrial communities, the overall
+%     effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
+%     $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
+%     $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
+%     $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
+%     that there was weak scaling at most latitudes. In contrast, the scaling
+%     exponent of generality with the proportion of basal resources was positive
+%     near the equator and negative near the poles in estuarine, lake, and stream
+%     communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
+%     very little change in the scaling exponents for marine and terrestrial
+%     communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
+%     $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
+
+%     As with species richness, link density, generality, and vulnerability
+%     generally increased with the proportion of intermediate consumers in a web
+%     ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
+%     $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
+%     The best-fit models for link density and vulnerability did not include
+%     any effect of latitude. In contrast, the strength of the scaling relationship
+%     for generality increased weakly towards the poles in estuarine, marine, and
+%     terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
+%     towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
+%     and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).
+
+%     In contrast to the generally positive scaling relationships above, link
+%     density, generality, and vulnerability decreased as the proportion of top
+%     predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
+%     $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
+%     Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
+%     strength of this scaling did not vary significantly with latitude
+%     ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
+%     $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
+%     In stream and terrestrial food webs, however, scaling was more strongly negative in the 
+%     tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
+%     and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
+%     $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
+%     for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
+%     for latitude in any ecosystem type.
+
+\newpage
+
+\subsection*{Appendix S4: Supplemental Figure}
+
+\begin{figure}[!h]
+\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_observed.eps}}
 \caption{Scaling relationships for link density, generality, 
@@
 
-\newpage
-
-\begin{figure}[h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the estimated scaling exponent for species richness (black
-line) with its 95\% confidence interval (in grey),
-based on N=196 empirical food webs. Latitude is 
-given in degrees from the equator
-regardless of direction.}
-\label{S}
-\end{figure}
-
-\begin{figure}[!h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
-empirical food webs. Latitude is given in degrees
-from the equator regardless of direction.}
-\label{B}
-\end{figure}
-
-\newpage
-
-\begin{figure}[h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
-N=196 empirical food webs. Latitude is given in degrees
-from the equator regardless of direction.}
-\label{I}
-\end{figure}
-
-\begin{figure}[!h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
-empirical food webs. Latitude is given in degrees
-from the equator regardless of direction.}
-\label{T}
-\end{figure}
-
-\newpage
-
-\bibliographystyle{jae}%Compile with jae.bst style file
+% \begin{figure}[h]
+% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+% types and over latitude. For each property we show the estimated scaling exponent for species richness (black
+% line) with its 95\% confidence interval (in grey),
+% based on N=196 empirical food webs. Latitude is 
+% given in degrees from the equator
+% regardless of direction.}
+% \label{S}
+% \end{figure}
+
+% \begin{figure}[!h]
+% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
+% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+% types and over latitude. For each property we show the scaling exponent for the proportion of
+% basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
+% empirical food webs. Latitude is given in degrees
+% from the equator regardless of direction.}
+% \label{B}
+% \end{figure}
+
+% \newpage
+
+% \begin{figure}[h]
+% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
+% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+% types and over latitude. For each property we show the scaling exponent for the proportion of
+% intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
+% N=196 empirical food webs. Latitude is given in degrees
+% from the equator regardless of direction.}
+% \label{I}
+% \end{figure}
+
+% \begin{figure}[!h]
+% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
+% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+% types and over latitude. For each property we show the scaling exponent for the proportion of
+% top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
+% empirical food webs. Latitude is given in degrees
+% from the equator regardless of direction.}
+% \label{T}
+% \end{figure}
+
+\newpage
+
+\bibliographystyle{prsb}%Compile with jae.bst style file
 \bibliography{noISN}% your .bib file(s)

### 2015-09-04 manuscript/supplement.tex
Main text files almost done - need to add by-TL back to SI, reference in main text

@@
 
-\subsection*{Appendix S1: Details of food web sources and selection}
+\subsection*{Appendix S1: details of food web sources and selection}
 
@@
         57    & 3 & \cite{Yanez1978}  & marine & 17,26,21 N & Yes   &       \\
-        58    & 3 & \cite{Cohen1990}  & lake & 51,46 N & Yes   &       \\
+        58    & 3 & \cite{Smirnov1961}  & lake & 51,46 N & Yes   &       \\
         59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
@@
         73    & 3 & \cite{Schiemer1979}  & lake &       & No    & Could not locate original source \\
-        74    & 3 & \cite{Cohen1990} & marine & 34,15,00 S & Yes   &       \\
+        74    & 3 & \cite{Brown1964} & marine & 34,15,00 S & Yes   &       \\
         75    & 3 & \cite{Pechlaner1972}  & lake & 47,11 N & Yes   &       \\
@@
 
-\subsection*{Appendix S2: Forms of scaling relationships with species richness}
+\subsection*{Appendix S2: forms of scaling relationships with species richness}
 
@@
 
-\subsection*{Appendix S3: Testing for effects of sampling effort}
+\subsection*{Appendix S3: testing for effects of sampling effort}
 
@@
     We show the pseudovalues for each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset. Authors
+    in the equation after the removal of all webs compiled by each author (or set of authors where
+    multiple authors compiled identical sets of webs) in the dataset. Authors
     who compiled only a single web were jackknifed as part of the by-web jackknife.
-    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
+    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
+    the number of webs removed in each jackknife is given in parentheses.}
     \label{LS_web}
@@
     We show the pseudovalues for each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset. Authors
+    in the equation after the removal of all webs compiled by each author (or set of authors where
+    multiple authors compiled identical sets of webs) in the dataset. Authors
     who compiled only a single web were jackknifed as part of the by-web jackknife.
-    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
+    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
+    the number of webs removed in each jackknife is given in parentheses.}
     \label{Gen_web}
@@
     We show the pseudovalues for each coefficient
-    in the equation after the removal of all webs compiled by each author in the dataset. Authors
+    in the equation after the removal of all webs compiled by each author (or set of authors where
+    multiple authors compiled identical sets of webs) in the dataset. Authors
     who compiled only a single web were jackknifed as part of the by-web jackknife.
-    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line.}
+    The estimate for the full, non-jackknifed dataset is indicated by the red, dashed line, and
+    the number of webs removed in each jackknife is given in parentheses.}
     \label{Vul_web}
@@
 
-\subsection*{Appendix S4: Supplemental Figure}
+\subsection*{Appendix S5: supplemental figure}
 
@@
 \caption{Scaling relationships for link density, generality, 
-and vulnerability relative to species richness and the proportions of basal resources (\% Basal),
-intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
+and vulnerability relative to species richness of a food web. 
 For each relationship, we show observed values (white circles) and 

### 2015-09-04 manuscript/supplement.tex
local changes

--- 2015-09-03 manuscript/supplement.tex
@@
     As our dataset consists of food webs published over several decades, from 
-    many countries, and by many research groups, it is highly likely that not
-    all webs were compiled using the same procedure or with the same degree of
-    sampling effort. In order to insure that our results were not driven by
+    many countries, and by many research groups, there are
+    differences in the procedures used to assemble the food
+    webs and likely also differences in the amount of
+    sampling effort allocated to each web. In order to 
+    ensure that our results were not driven by
     particularly unusual food webs, or by unusually well- or poorly-sampled webs 
@@
 
-    None of our models were affected by the removal of any single food web
+    None of our models were greatly affected by the removal of any single food web
     or by the removal of a set of webs compiled by a common researcher (or group of
@@
     We are therefore very confident that, while there are undoubtedly differences 
-    in the methods used to compile food webs, these differences provide an
-    insufficient explanation for the trends we report in this study.
+    in the methods used to compile food webs, these differences do not explain the trends we report in this study.
 

### 2015-09-04 manuscript/latitudepaper.tex
abbreviated journals

@@
 Several properties of food webs---the networks of feeding links between
-species---are known to vary systematically with the species richness of the underlying
-community.  Under the ``latitude-niche breadth hypothesis'', which predicts
-that species in the tropics will tend to evolve narrower niches, one might
-expect that these scaling relationships could also be affected by latitude. To
-test this hypothesis, we analysed the scaling relationships between species
-richness and average generality, vulnerability, and links per species across a
-set of 196 empirical food webs.  We also investigated scaling relationships
-between the three food-web properties and the proportions of the web made up
-by basal resources, intermediate consumers, and top predators. While we
-observed no effect of latitude on scaling relationships with species richness
-in the estuarine, marine, and terrestrial food webs, there were strong effects
-of latitude on scaling relationships in the freshwater food webs. In these
-communities, the latitude-niche breadth hypothesis appears to hold true while
-in other habitat types niche breadth appears to vary little. These contrasting
-findings indicate that it may be more important to account for habitat than
-latitude when exploring gradients in food-web structure.
+species---are known to vary systematically with the species richness of the
+underlying community.  Under the ``latitude-niche breadth hypothesis'', which
+predicts that species in the tropics will tend to evolve narrower niches, one
+might expect that these scaling relationships could also be affected by
+latitude. To test this hypothesis, we analysed the scaling relationships
+between species richness and average generality, vulnerability, and links per
+species across a set of 196 empirical food webs. In estuarine, marine, and 
+terrestrial food webs there was no effect of latitude on any scaling relationship,
+suggesting constant niche breadth in these habitats. In freshwater communities,
+on the other hand, there were strong effects of latitude on scaling relationships,
+supporting the latitude-niche breadth hypothesis. These contrasting findings
+indicate that it may be more important to account for habitat than latitude
+when exploring gradients in food-web structure.
 
@@
   whether latitude affects the scaling of each property with species richness,
-  we test for the effects of latitude on specialisation implied by the
+  we test for the effects of latitude on specialisation predicted by the
   ``latitude-niche breadth hypothesis'' (Fig.~\ref{concept}).  If the scaling
@@
     If a range of latitudes (e.g. $42-49^{\circ}N$) was provided, we used the midpoint
-    of this range. We grouped food web by ecosystem type (stream, N=71; lake, N=47; marine, 
+    of this range. We grouped food webs by ecosystem type (stream, N=71; lake, N=47; marine, 
     N=28; estuarine, N=18; and terrestrial, N=31) according to their designation in 
@@
     is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
-    Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
-    sets to form ``trophic species'' webs ~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
+    Many analyses of food-web structure attempt to reduce this variation by using food webs comprised of ``trophic
+    species'' --aggregations of species with idendical sets of predators and prey-- rather than taxonomic 
+    species~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
     is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
@@
     the scaling relationships between species richness, other food-web properties, and latitude are very 
-    similar whether or not redundant species are included. For simplicity, here we present only
-    the results for the original (un-aggregated) webs.
+    similar whether or not species with identical sets of predators and prey are included. For simplicity, 
+    here we present only the results for the original (un-aggregated, taxonomic species) webs.
 
@@
     as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
-    We therefore used and present logarithmic models throughout the rest of the study.
+    We therefore used and present logarithmic models throughout the rest of the analyses.
 
@@
   linked to seasonal events such as snowmelts or summer
-  drought~\cite{Winterbourn1997}).Further, both temperate streams and lakes
+  drought~\cite{Winterbourn1997}). Further, both temperate streams and lakes
   tend to experience seasonal strong pulses of allochthonous inputs (e.g.,
@@
   invertebrates~\cite{Nakano2001,Lennon2004,Zeng2008}. These trends combined
-  mean that, relative to larger, more abiotically stable estuarine and marine
-  communities, freshwater food webs may experience high turnover in both
-  community composition and productivity. Notable exceptions from the above
+  mean that, relative to estuarine and marine communities, freshwater food 
+  webs may experience high turnover in both community composition and 
+  productivity~\cite{Tilzer1988,Magalhaes1993,Baird1989}. Notable exceptions from the above
   trends are New Zealand stream communities (representing 31 of the 71 stream
@@
   highly-variable communities where said variation is more seasonal, New
-  Zealand communities are typified by ecological
+  Zealand communities are dominated by ecological
   generalists~\cite{Winterbourn1997,Winterbourn1981} implying that they appear
@@
   Importantly, while terrestrial communities are also strongly seasonal at
-  high latitudes, and can also obtain significant allochthonous
-  inputs~\cite{Nakano2001}, terrestrial consumers tend to be more
+  high latitudes and can recieve significant allochthonous
+  inputs~\cite{Nakano2001}, terrestrial consumers tend to be
   morphologically specialised for feeding on particular prey~\cite{Liem1990}.
@@
   general across all types of aquatic habitats~\cite{Liem1990,Shurin2006}. The
-  key to this this explanation of the differences between freshwater and
+  key to this explanation of the differences between freshwater and
   marine and estuarine  ecosystems is whether the former experience more
@@
   likely to  experience more severe changes because of their small size. While
-  oceans and estuaries certainly do vary in terms of water temperature and
-  nutrients over the course of a year~\cite{Baird1989}, because they are not isolated
-  in the midst of a terrestrial matrix these changes are likely to be slower
-  and milder than in freshwaters. Net primary productivity in particular is
+  oceans and estuaries certainly vary in terms of water temperature and
+  nutrients over the course of a year~\cite{Baird1989}, these changes are likely to be slower
+  and milder than in freshwaters because marine and estuarine communities are buffered 
+  by being open to the ocean rather than isolated
+  in the midst of a terrestrial matrix . Net primary productivity in particular is
   much more variable over the course of a year in non-marine communities~\cite{Field1998},
@@
 \bibliographystyle{prsb}%Compile with vancouver.bst style file
-\bibliography{noISN}% your .bib file(s)
+\bibliography{abbreviated}% your .bib file(s)
 
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
-\caption{In A) we show the known scaling relationship between link density (links per species, L/S) and 
+% \centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
+\caption{In A) we show the known scaling relationship between link density (links per species) and 
 species richness. This scaling relationship is a power law and therefore linear in a log-log plot.
@@
 explain this gradient. Hypothesis 1 posits that greater environmental stability in the tropics will 
-allow species to evolve narrower niches (indicated by the grey trapezoid). Hypothesis 2 suggests that species
-will have constant niche sizes over latitude (indicated by the grey rectangle) but that
-greater primary productivity in the tropics creates a larger niche space (indicated by the 
-white trapezoid) such that each species still occupies a smaller proportion of the total niche
-space. These two hypotheses have different implications for the scaling of food-web properties
-such as the number of feeding links per species (L/S) with species richness. C) If hypothesis 1 is 
+allow species to evolve narrower niches (indicated by parabolas) than those at the poles. Hypothesis 2 
+suggests that species will have constant niche sizes over latitude but that greater primary productivity 
+in the tropics creates a larger niche space such that each species still occupies a smaller proportion 
+of the total niche space. These two hypotheses have different implications for the scaling of food-web 
+properties such as the number of feeding links per species with species richness. C) If hypothesis 1 is 
 true, then the exponent of the scaling relationship between link density and species richness should 
 be larger towards the poles, where each additional species in the food-web will have a larger niche 
-(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this distribution should not vary significantly over latitude.}
+(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this distribution should 
+not vary significantly over latitude.}
 \label{concept}
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
+% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
-see Fig.~\emph{S7}, \emph{Appendix S4}.}
+see Fig.~\emph{S7}, \emph{Appendix S5}.}
 \label{props_v_lat}
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem

### 2015-09-04 manuscript/latitudepaper.tex
Fine I won't say taxonomic species

@@
     Many analyses of food-web structure attempt to reduce this variation by using food webs comprised of ``trophic
-    species'' --aggregations of species with idendical sets of predators and prey-- rather than taxonomic 
-    species~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
+    species'' --aggregations of species with idendical sets of predators and prey-- rather than  
+    species \emph{per se}~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
     is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
@@
     similar whether or not species with identical sets of predators and prey are included. For simplicity, 
-    here we present only the results for the original (un-aggregated, taxonomic species) webs.
+    here we present only the results for the original (un-aggregated, original species) webs.
 

### 2015-09-04 manuscript/latitudepaper.tex
spellcheckered

@@
     Many analyses of food-web structure attempt to reduce this variation by using food webs comprised of ``trophic
-    species'' --aggregations of species with idendical sets of predators and prey-- rather than  
+    species'' --aggregations of species with identical sets of predators and prey-- rather than  
     species \emph{per se}~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
@@
   Importantly, while terrestrial communities are also strongly seasonal at
-  high latitudes and can recieve significant allochthonous
+  high latitudes and can receive significant allochthonous
   inputs~\cite{Nakano2001}, terrestrial consumers tend to be

### 2015-09-04 manuscript/supplement.tex
Un-commented the by-TL analyses

@@
 
-% \subsection*{Appendix S4: Scaling relationships by trophic level}
-
-%   \subsubsection*{Methods}
-
-%     We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
-%     in the ways that scaling relationships with species richness might
-%     be affected by changes to the distribution of species among trophic levels. To
-%     that end, we repeated our analyses replacing species richness with the
-%     proportion of basal resources, proportion of intermediate consumers,
-%     or proportion of top predators. All model fitting procedures were identical to those
-%     described for species richness. The model simplicication procedure was similar to
-%     the procedure described for species richness, except that in some cases there were
-%     multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
-%     In these cases, we defined the best-fitting model as the model with the lowest AIC in the
-%     set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.
-
-%   \subsubsection*{Results}
-
-%     The relationships between latitude and the proportions of species at each
-%     trophic level were more complex than the flat relationship between latitude
-%     and species richness in this dataset.  The proportion of basal resources
-%     increased towards the poles in stream webs
-%     ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
-%     with latitude in estuarine, marine, lake, or terrestrial  food webs
-%     ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
-%     intermediate consumers decreased towards the poles in all ecosystem types
-%     except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
-%     $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
-%     in a food web,  meanwhile, decreased towards the poles in lake and  stream
-%     food webs but did not vary in other ecosystem types
-%     ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
-%     $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
-
-%     Unlike species richness, only generality showed an overall increase with
-%     increasing proportions of basal resources in a web ($\beta_0$=0.019,
-%     $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
-%     link density, generality, and vulnerability, respectively;
-%     Fig.~\ref{props_v_lat}). In each case, however, there were substantial
-%     effects of latitude on the scaling relationships. Thus, the scaling
-%     exponents for link density and vulnerability were negative for estuarine,
-%     lake, and stream communities and became more negative towards the poles
-%     ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
-%     $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
-%     density and vulnerability in marine and terrestrial communities, the overall
-%     effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
-%     $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
-%     $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
-%     $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
-%     that there was weak scaling at most latitudes. In contrast, the scaling
-%     exponent of generality with the proportion of basal resources was positive
-%     near the equator and negative near the poles in estuarine, lake, and stream
-%     communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
-%     very little change in the scaling exponents for marine and terrestrial
-%     communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
-%     $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
-
-%     As with species richness, link density, generality, and vulnerability
-%     generally increased with the proportion of intermediate consumers in a web
-%     ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
-%     $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
-%     The best-fit models for link density and vulnerability did not include
-%     any effect of latitude. In contrast, the strength of the scaling relationship
-%     for generality increased weakly towards the poles in estuarine, marine, and
-%     terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
-%     towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
-%     and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).
-
-%     In contrast to the generally positive scaling relationships above, link
-%     density, generality, and vulnerability decreased as the proportion of top
-%     predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
-%     $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
-%     Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
-%     strength of this scaling did not vary significantly with latitude
-%     ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
-%     $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
-%     In stream and terrestrial food webs, however, scaling was more strongly negative in the 
-%     tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
-%     and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
-%     $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
-%     for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
-%     for latitude in any ecosystem type.
-
-\newpage
-
-\subsection*{Appendix S5: supplemental figure}
+\subsection*{Appendix S4: Scaling relationships by trophic level}
+
+  \subsubsection*{Methods}
+
+    [[Explain why we were interested]]
+    We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
+    in the ways that scaling relationships with species richness might
+    be affected by changes to the distribution of species among trophic levels. To
+    that end, we repeated our analyses replacing species richness with the
+    proportion of basal resources, proportion of intermediate consumers,
+    or proportion of top predators. All model fitting procedures were identical to those
+    described for species richness. The model simplicication procedure was similar to
+    the procedure described for species richness, except that in some cases there were
+    multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
+    In these cases, we defined the best-fitting model as the model with the lowest AIC in the
+    set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.
+
+  \subsubsection*{Results}
+
+    The relationships between latitude and the proportions of species at each
+    trophic level were more complex than the flat relationship between latitude
+    and species richness in this dataset.  The proportion of basal resources
+    increased towards the poles in stream webs
+    ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
+    with latitude in estuarine, marine, lake, or terrestrial  food webs
+    ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
+    intermediate consumers decreased towards the poles in all ecosystem types
+    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
+    $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
+    in a food web,  meanwhile, decreased towards the poles in lake and  stream
+    food webs but did not vary in other ecosystem types
+    ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
+    $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
+
+    Unlike species richness, only generality showed an overall increase with
+    increasing proportions of basal resources in a web ($\beta_0$=0.019,
+    $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
+    link density, generality, and vulnerability, respectively;
+    Fig.~\ref{props_v_lat}). In each case, however, there were substantial
+    effects of latitude on the scaling relationships. Thus, the scaling
+    exponents for link density and vulnerability were negative for estuarine,
+    lake, and stream communities and became more negative towards the poles
+    ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
+    $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
+    density and vulnerability in marine and terrestrial communities, the overall
+    effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
+    $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
+    $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
+    $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
+    that there was weak scaling at most latitudes. In contrast, the scaling
+    exponent of generality with the proportion of basal resources was positive
+    near the equator and negative near the poles in estuarine, lake, and stream
+    communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
+    very little change in the scaling exponents for marine and terrestrial
+    communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
+    $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
+
+    As with species richness, link density, generality, and vulnerability
+    generally increased with the proportion of intermediate consumers in a web
+    ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
+    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
+    The best-fit models for link density and vulnerability did not include
+    any effect of latitude. In contrast, the strength of the scaling relationship
+    for generality increased weakly towards the poles in estuarine, marine, and
+    terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
+    towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
+    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).
+
+    In contrast to the generally positive scaling relationships above, link
+    density, generality, and vulnerability decreased as the proportion of top
+    predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
+    $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
+    Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
+    strength of this scaling did not vary significantly with latitude
+    ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
+    $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
+    In stream and terrestrial food webs, however, scaling was more strongly negative in the 
+    tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
+    and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
+    $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
+    for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
+    for latitude in any ecosystem type.
+
+\newpage
+
+\subsection*{Appendix S5: supplemental figures}
 
@@
 
-% \begin{figure}[h]
-% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
-% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-% types and over latitude. For each property we show the estimated scaling exponent for species richness (black
-% line) with its 95\% confidence interval (in grey),
-% based on N=196 empirical food webs. Latitude is 
-% given in degrees from the equator
-% regardless of direction.}
-% \label{S}
-% \end{figure}
-
-% \begin{figure}[!h]
-% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
-% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-% types and over latitude. For each property we show the scaling exponent for the proportion of
-% basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
-% empirical food webs. Latitude is given in degrees
-% from the equator regardless of direction.}
-% \label{B}
-% \end{figure}
-
-% \newpage
-
-% \begin{figure}[h]
-% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
-% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-% types and over latitude. For each property we show the scaling exponent for the proportion of
-% intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
-% N=196 empirical food webs. Latitude is given in degrees
-% from the equator regardless of direction.}
-% \label{I}
-% \end{figure}
-
-% \begin{figure}[!h]
-% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
-% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-% types and over latitude. For each property we show the scaling exponent for the proportion of
-% top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
-% empirical food webs. Latitude is given in degrees
-% from the equator regardless of direction.}
-% \label{T}
-% \end{figure}
+\begin{figure}[!h]
+\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts.eps}}
+\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
+relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
+Link density, generality,
+and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
+type. As these relationships take the form of power laws, we did this by dividing the food-web
+property (e.g. link density) by species richness raised to an exponent including the 
+effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
+type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
+ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
+latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
+we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
+ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
+see Fig.~\ref{TL_observed}.}
+\label{TL_rescaled}
+\end{figure}
+
+\begin{figure}[!h]
+\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
+\caption{Scaling relationships for link density, generality, 
+and vulnerability relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
+For each relationship, we show observed values (white circles) and 
+a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
+any effects of habitat type or latitude (black line, N=196 food webs). See Fig.~\ref{TL_rescaled} to compare with 
+observed values correcting for the effects of habitat type and latitude. }
+\label{TL_observed}
+\end{figure}
+
+\begin{figure}[h]
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the estimated scaling exponent for species richness (black
+line) with its 95\% confidence interval (in grey),
+based on N=196 empirical food webs. Latitude is 
+given in degrees from the equator
+regardless of direction.}
+\label{S}
+\end{figure}
+
+\begin{figure}[!h]
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
+empirical food webs. Latitude is given in degrees
+from the equator regardless of direction.}
+\label{B}
+\end{figure}
+
+\newpage
+
+\begin{figure}[h]
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
+N=196 empirical food webs. Latitude is given in degrees
+from the equator regardless of direction.}
+\label{I}
+\end{figure}
+
+\begin{figure}[!h]
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
+\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+types and over latitude. For each property we show the scaling exponent for the proportion of
+top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
+empirical food webs. Latitude is given in degrees
+from the equator regardless of direction.}
+\label{T}
+\end{figure}
 

### 2015-09-04 manuscript/latitudepaper.tex
Added a ref to the by-TL results

@@
 
+    We then repeated the above analyses to measure the 
+    effect of latitude on the scaling of specialisation 
+    with numbers and proportions of species at different 
+    trophic levels (i.e., basal resources, intermediate 
+    consumers, and top predators). As different trophic 
+    levels represent different sections of the biotic niche 
+    space, we expected that latitude might affect the 
+    scaling of specialisation with the proportion of 
+    species in each trophic level differently. The results
+    of these supplemental analyses largely echo the the
+    results of the species-richness analyses, and are 
+    presented in~\emph{Appendix S4}.
+
 \section*{Results}

### 2015-09-04 manuscript/supplement.tex
A very small addition to the supplement.

@@
 
-    [[Explain why we were interested]]
-    We were also interested [[AE wants us to say why, because curiosity isn't a good reason to do science]] 
-    in the ways that scaling relationships with species richness might
-    be affected by changes to the distribution of species among trophic levels. To
-    that end, we repeated our analyses replacing species richness with the
-    proportion of basal resources, proportion of intermediate consumers,
-    or proportion of top predators. All model fitting procedures were identical to those
-    described for species richness. The model simplicication procedure was similar to
-    the procedure described for species richness, except that in some cases there were
-    multiple models with $\delta$AIC\textless2 that shared the minimal degrees of freedom.
-    In these cases, we defined the best-fitting model as the model with the lowest AIC in the
-    set of models with $\delta$AIC\textless2 and the minimal degrees of freedom.
+    We were also interested in the ways that scaling
+    relationships with species richness might
+    be affected by changes to the distribution of species 
+    among trophic levels. [[more justification of why]]
+    To that end, we repeated our 
+    analyses replacing species richness with the
+    proportion of basal resources, proportion of 
+    intermediate consumers, or proportion of top 
+    predators. All model fitting procedures were identical 
+    to those described for species richness. The model 
+    simplicication procedure was similar to
+    the procedure described for species richness, except 
+    that in some cases there were multiple models with 
+    $\delta$AIC\textless2 that shared the minimal degrees 
+    of freedom. In these cases, we defined the 
+    best-fitting model as the model with the lowest AIC in 
+    the set of models with $\delta$AIC\textless2 and the 
+    minimal degrees of freedom.
 
@@
 
+    As with species richness, specialisation scaled with
+    the numbers and proportions of species at each trophic
+    level following a lognormal distribution.
     The relationships between latitude and the proportions of species at each

### 2015-09-04 manuscript/supplement.tex
updated refs to supplemental figures

@@
     link density, generality, and vulnerability, respectively;
-    Fig.~\ref{props_v_lat}). In each case, however, there were substantial
+    Fig.~\ref{TL_rescaled}). In each case, however, there were substantial
     effects of latitude on the scaling relationships. Thus, the scaling
@@
     ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
-    $p$\textless0.001, respectively; Fig.~\ref{BIT}). For the scaling of link
+    $p$\textless0.001, respectively; Fig.~\ref{B}). For the scaling of link
     density and vulnerability in marine and terrestrial communities, the overall
@@
     ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
-    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{props_v_lat}). 
+    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{TL_rescaled}). 
     The best-fit models for link density and vulnerability did not include
@@
     towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
-    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{BIT}).
+    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{I}).
 
@@
     $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
-    Fig~\ref{props_v_lat}). For estuarine, lake, and marine food webs the
+    Fig~\ref{TL_rescaled}). For estuarine, lake, and marine food webs the
     strength of this scaling did not vary significantly with latitude
@@
     $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
-    for vulnerability; Fig.~\ref{BIT}. The best-fit model for generality did not include any terms
+    for vulnerability; Fig.~\ref{T}. The best-fit model for generality did not include any terms
     for latitude in any ecosystem type.
@@
 
-\begin{figure}[h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the estimated scaling exponent for species richness (black
-line) with its 95\% confidence interval (in grey),
-based on N=196 empirical food webs. Latitude is 
-given in degrees from the equator
-regardless of direction.}
-\label{S}
-\end{figure}
-
 \begin{figure}[!h]

### 2015-09-04 manuscript/supplement.tex
cosmetic changes

@@
     None of our models were greatly affected by the removal of any single food web
-    or by the removal of a set of webs compiled by a common researcher (or group of
-    researchers).
+    or by the removal of a set of webs compiled by a common author (or group of
+    authors).
     Estimates of coefficients from all jackknifed datasets were extremely
@@
     We are therefore very confident that, while there are undoubtedly differences 
-    in the methods used to compile food webs, these differences do not explain the trends we report in this study.
+    in the methods used to compile food webs, these differences do not explain the trends we report.
 
@@
     the number of webs removed in each jackknife is given in parentheses.}
-    \label{LS_web}
+    \label{LS_auth}
     \end{figure}
@@
     the number of webs removed in each jackknife is given in parentheses.}
-    \label{Gen_web}
+    \label{Gen_auth}
     \end{figure}
@@
     the number of webs removed in each jackknife is given in parentheses.}
-    \label{Vul_web}
+    \label{Vul_auth}
     \end{figure}
@@
 
+\newpage
+
 \begin{figure}[!h]
@@
 
-\begin{figure}[!h]
-\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
+\newpage
+
+\begin{figure}[!h]
+\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
 \caption{Scaling relationships for link density, generality, 
@@
 
-\newpage
-
-\begin{figure}[h]
+\begin{figure}[!h]
 \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}

### 2015-09-06 manuscript/AC-reply-to-referees.tex
DBS comments
Added DBS changes to sup, should be g2g

@@
 
-\newcommand{\mytitle}{\emph{Specialisation in food webs scales with species richness but not with latitude}}
+\newcommand{\mytitle}{\emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types.}}
 \newcommand{\myjournal}{\emph{Proceedings of the Royal Society B}}
@@
 feel that the revised manuscript is both stronger and more accessible, and
-hope that it will please the Editors.
+hope that it will please the Editors and Reviewers alike.
 
@@
   taken the Associate Editor's specific comments to heart and address each one
-  in turn. We hope that our replies (preceded by \textbf{R:} [[do something
-  good]].
+  in turn. We hope that our replies (preceded by \textbf{R:} 
+  will assuage the Associate Editor's concerns and are 
+  confident that our manuscript is strengthened as a result.
 
@@
   \textbf{R:} We had originally intended to emphasize that, contrary to our expectations,
-  scaling relationships did not vary over latitude in most ecosystems. We have amended our
-  title to ``[[newtitle]]'' in order to better capture the scaling that did occur in streams.
+  scaling relationships did not vary over latitude in~\emph{most} ecosystems. We have now amended our
+  title to ``\mytitle'' in order to better capture the scaling that did occur in streams.
 
@@
 
-  \textbf{R:} Providing \emph{a priori} expectations for the directions of relationships between latitude and niche width/specialisation is difficult due to the 
-  contrasting hypotheses of narrower niches in the tropics~\citep{Vazquez2004} versus broader niche space in the tropics~\citep{Davies2007}.
-Given the limited support available for either hypothesis, it was equally likely that scaling of specialization with species richness might be stronger or weaker towards the poles.
-  We do not share the Associate Editor's concern that this makes our study too exploratory but rather had intended to use the results of our analyses to support one or the other of these hypotheses.
-We have added to the manuscript at lines XX and YY to more explicitly frame our study as a test of these two versions of the latitude-niche breadth hypothesis.
+  \textbf{R:} The goal of our study was to give support to
+  one of two contrasting hypotheses (narrower niches in the
+  tropics~\cite{Vazquez2004} versus broader niche space in 
+  the tropics~\cite{Davies2007}). Given the limited support
+  available for either hypothesis, we had no~\emph{a priori}
+  expectation that one was more likely than the other-- that
+  is, it was plausible that scaling of specialisation with
+  species richness might be stronger towards the poles or 
+  that scaling would be unaffected by latitude. We have 
+  added to the introduction at lines 22-27 to make these two
+  potential relationships clearer and at lines 37-42 to more
+  explicitly frame our study as a test of these two versions 
+  of the latitude-niche breadth hypothesis. We have also 
+  followed Reviewer 2's suggestion and now provide a 
+  conceptual figure (Fig. 1) that clearly places our study
+  within this context. We also now provide an explanation 
+  for why we included ecosystem type as a covariate at lines
+  42-44.
 
-  Line 29:
+  Lines 22-27:
 
@@
 
-  If the latitude-niche breadth hypothesis is correct, there should also be
-  direct relationships between latitude and the degree of specialisation
-  (i.e., the breadth of the Eltonian niche;~\citealp{Elton1927}) of species within
-  food webs. Specifically, narrower niches in the tropics would equate to
-  greater specialisation (narrower niches) while constant niche sizes but
-  greater productivity would translate to constant specialisation and niche
-  width across latitude.
+    If the latitude-niche breadth hypothesis is correct, 
+    there should also be direct relationships between 
+    latitude and the degree of specialisation (i.e., the 
+    breadth of the Eltonian 
+    niche;~\cite{Elton1927,Leibold2010}) of species within
+    food webs. Specifically, narrower niches in the tropics 
+    would equate to greater specialisation (narrower niches) 
+    while constant niche sizes but greater productivity 
+    would translate to constant specialisation and niche 
+    width across latitude (Fig. 1).
 
@@
 
-  \smallskip
-
-  Line 43:
+  Lines 37-44:
 
@@
 
-  By testing whether latitude affects the scaling of each property with
-  species richness, we test for the effects of latitude on specialisation
-  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
-  specialisation with species richness is weaker at the tropics (i.e., if
-  species gain fewer links, predators, or prey as the size of the network
-  increases), this will indicate narrower niches at the tropics. If, however,
-  the scaling of specialisation with species richness does not vary over
-  latitude, this will support the hypothesis that niches are similarly-sized
-  worldwide but that there is a broader niche space in the tropics.
+    If the scaling of specialisation with species richness 
+    is weaker in the  tropics (i.e., if species gain fewer
+    links, predators, or prey as the size  of the network
+    increases), this will indicate narrower niches at the 
+    tropics.  If, however, the scaling of specialisation 
+    with species richness does not vary over latitude, this 
+    will indicate that niches are similarly-sized worldwide 
+    but that there is a broader niche space in the tropics. 
+    Additionally, as food webs describing different 
+    ecosystem types may differ in their 
+    topology~\cite{Dunne2004,Shurin2006}, we also explored 
+    the differences in scaling relationships across 
+    ecosystem types.
 
@@
   $\delta$AIC\textless2 are roughly equally well-supported. This is why our
-  procedure (as stated in lines XX-XX) was to first consider the set of models
+  procedure (as stated in lines 83-86) was to first consider the set of models
   where $\delta$AIC\textless2 and select the model with the fewest degrees of
   freedom. We chose the smallest model where $\delta$AIC\textless2 in order to
-  avoid over-fitting the models. We only used AIC as a deciding factor where
-  there were several models that shared the minimal degrees of freedom and all
-  had $\delta$AIC\textless2.  In fact, this scenario did not occur for the
-  models presented in the previous draft   (it does occur when the by-trophic-
-  level models use counts of species rather than proportions), so we have simply
-  removed the description of this step of our analysis from the main text. [[If we go with species counts, will need to describe what the differences are between the similar models]]
+  avoid over-fitting the models.
+
+  We only used AIC as a deciding factor where
+  there were several models that shared the minimal degrees 
+  of freedom and all had $\delta$AIC\textless2. In fact, 
+  this scenario did not occur for the models presented in 
+  the previous draft (it does occur when the 
+  by-trophic-level models use counts of species rather than
+  proportions, an analysis which we had explored in an 
+  earlier draft). To avoid confusion we have therefore 
+  removed the description of this step of our analysis from 
+  the main text.
+
+  Lines 83-86:
+
+  \begin{quotation}
+
+    Simplified models were obtained by systematically 
+    removing all possible combinations of terms from the 
+    full model. The best-fitting model was then determined 
+    to be the model with the fewest terms where 
+    $\Delta$AIC\textless2, as this model is the least likely 
+    to suffer from over-fitting.
+
+  \end{quotation}
 
@@
   moved these additional analyses to the supplemental 
-  iformation. This analysis was purely exploratory. The 
-  scaling of specialisation with proportions (or numbers) 
-  of species at different trophic levels has not been 
-  previously investigated (to our knowledge), and it 
-  seemed to us to be a logical extension of the main 
-  analysis. If the Associate Editor disagrees in principle 
-  with exploratory science, we are willing to remove these 
-  analyses altogether.
+  information. We were interested in exploring scaling 
+  relationships with different trophic level because each
+  represents a different component of the niche space and 
+  therefore interact differently with latitude, and have now
+  added a brief explanation of our motivation in lines 
+  121-127.
+
+  \begin{quotation}
+
+    We then repeated the above analyses to measure the 
+    effect of latitude on the scaling of specialisation 
+    with numbers and proportions of species at different 
+    trophic levels (i.e., basal resources, intermediate 
+    consumers, and top predators). As different trophic 
+    levels represent different sections of the biotic niche 
+    space, we expected that latitude might affect the 
+    scaling of specialisation with the proportion of 
+    species in each trophic level differently. The results
+    of these supplemental analyses largely echo the the
+    results of the species-richness analyses, and are 
+    presented in~\emph{Appendix S4}.
+
+  \end{quotation}
 
@@
 
-  \textbf{R:} As the Associate Editor likely suspected, the property estimates
-  are all strongly    positively correlated. As generality and vulnerability
-  describe the two components (number of prey and number    of predators,
-  respectively) of links per species, this is   to be expected. We have added a
-  brief description of this correlation to the main text as we believe it   will
-  provide some context for the very similar results for link density and
-  vulnerability.
+  \textbf{R:} As the Associate Editor likely suspected, the 
+  property estimates are all strongly positively correlated. 
+  As generality and vulnerability describe the two 
+  components (number of prey and number of predators,
+  respectively) of links per species, this is to be 
+  expected. We have added a brief description of these 
+  correlations to the main text (lines 129-132) as we 
+  believe it will provide some context for the very similar 
+  results for link density and vulnerability.
 
@@
 
-  \textbf{R:} We have ammended the text (lines XX-XX) to support our statement.
+  \textbf{R:} We have ammended the text (lines 143-146) to support our statement.
 
@@
 
-  \textbf{R:} We do not think it likely that we will be able to find evidence that prey-
-    switching does not occur in certain ecosystem types because, by definition,
-    it is impossible to document an event that does not occur. In fact, there are almost
-    certainly examples of species which switch between different prey in any ecosystem type
-    at any latitude. As we do not feel qualified to conduct a review of the frequencies of
-    prey-switching, we have instead revised our discussion following an excellent suggestion
-    by Referee 1 to focus on the greater seasonality experienced by stream communities.
-    [[not done, will need to tone this down.]]
-
-  \begin{quotation}
-  \end{quotation}
+  \textbf{R:} Following Reviewer 1's suggestion, we have restructured our discussion
+    to focus more on seasonality in different ecosystem types than on prey-switching.
+    As we are not aware of any studies explicitly comparing the frequencies of 
+    prey-switching in different ecosystem types, and do not feel qualified to conduct
+    such a review ourselves, we hope that this revised discussion will be satisfactory.
 
@@
     added sections for author contributions, conflicts of interest, and funding.
-    [[Check the in-text citations match published papers]]
 
@@
   the authors of all 196 webs in our dataset did not follow the same procedures.
-  Following the reviewer's suggestion, we have jackknifed our models by systematically
-  removing each web in turn and then re-running our analysis. We then repeated this
-  process, removing each author (or set of authors where authors worked on identical sets
-  of food webs) in turn and re-fitting the models. We are happy to report that removing
-  any single web had no significant effect on any model, nor did removing any author
-  (we removed Thompson and Townsend separately as each worked on one web that the other
-  did not). We have added a description of these methods and summary figures of their results
-  to the supporting information, and we thank the reviewer for suggesting this validation
-  of our overall results. We have also added a brief note in the main text to direct other
-  readers with similar concerns to the supporting information (lines XX-XX). [[At the end of the 
-  section describing our analyses - didn't seeem to fit after the first mention of sampling effort]]
-  [[done]]
+  Following the reviewer's suggestion, we have performed a jackknife analysis by
+  systematically removing each web in turn and then repeating our analysis. We
+  also performed a similar process removing each set of 
+  food webs compiled by a common author (or set of authors
+  where all authors worked on identical sets of food webs).
+  We are happy to report that removing
+  any single web had no significant effect on any model, 
+  nor did removing any set of webs compiled by a common 
+  author. 
+  We have added a description of these methods and summary
+  of their results to the supporting information 
+  (~\emph{Appendix S3}), and we thank the reviewer for 
+  suggesting this validation of our overall results. We 
+  have also added a brief note in the main text to direct 
+  other readers with similar concerns to the supporting 
+  information (lines 111-120).
+
+  We removed webs compiled by Thompson and by 
+  Townsend separately as each author compiled one food
+  web that the other did not. However, as 26/28 of the
+  food webs compiled by Thompson~\emph{or} Townsend were
+  compiled by both together, the results of both jackknife
+  iterations were very similar (as seen in authors 7 and 6, 
+  respectively, in~\emph{Figs. S4-S6, Appendix S3}). 
+  We are particularly reassured by~\emph{Fig. S5}, where
+  the removal of large subsets of the stream food webs
+  had very little impact on the coefficient representing
+  the effect of latitude on the scaling of generality with
+  species richness in streams.
 
@@
     associated with each author of the food webs in the dataset. Parameter 
-    estimates varied very little across either series of jackknifes (\emph{Appendix SXX}).
+    estimates varied very little across either series of jackknifes (\emph{Appendix S3}).
 
@@
 
-  \textbf{R:} [[We'll need to look for citations re: seasonal effects in streams.]]
+  \textbf{R:} We thank the Reviewer for this suggestion, 
+  and have substantially revised our discussion (lines 
+  190-225) to follow it. The Reviewer will note that our 
+  arguments include lakes as well as streams since both 
+  systems showed effects of latitude on scaling, and both 
+  experience severe seasonal variability as the Reviewer
+  points out for streams. We have also added a brief note 
+  to address the potential that the New Zealand stream food 
+  webs mentioned by the Reviewer above might be affecting 
+  our results. As described below, they are grouped in a 
+  narrow band of latitude; this likely explains their 
+  minimal impact on the trends we observe. We think that 
+  our discussion is much stronger after these changes.
 
   \begin{quotation}
+
+    That freshwater food webs supported the hypothesis of 
+    narrower niches in the tropics --while other ecosystem 
+    types did not-- is noteworthy given that these
+    ecosystems (especially streams) are known for being 
+    highly variable and that seasonal variability is one of 
+    the proposed drivers of the latitude-niche breadth 
+    hypothesis~\cite{Vazquez2004}. Both streams and lakes
+    can experience severe changes in water temperature and 
+    volume (e.g., floods, drying, freezing) that remove 
+    food or other resources (notably oxygen during
+    freezing events)~\cite{Winterbourn1997,Meding2001}. 
+    These events are often linked to seasonal events such 
+    as snowmelts or summer drought~\cite{Winterbourn1997}). 
+    Further, both temperate streams and lakes tend to 
+    experience seasonal strong pulses of allochthonous 
+    inputs (e.g., fallen leaves, terrestrial
+    invertebrates~\cite{Nakano2001,Lennon2004,Zeng2008}. 
+    These trends combined mean that, relative to estuarine 
+    and marine communities, freshwater food webs may 
+    experience high turnover in both community composition 
+    and productivity~\cite{Tilzer1988,Magalhaes1993,Baird1989}. Notable exceptions from the above
+    trends are New Zealand stream communities (representing 
+    31 of the 71 stream food webs in our dataset), which 
+    experience unpredictable flooding and drying throughout 
+    the year and do not receive seasonally pulsed
+    subsidies~\cite{Winterbourn1997,Winterbourn1981}. 
+    However, as this subset of webs is very tightly grouped 
+    in latitude ($44.64-46.41^{\circ}$S, within an
+    overall range of $23-69.02^{\circ}$ for stream 
+    communities), it is unlikely that they have greatly
+    influenced our results (see also \emph{Appendix S3}). 
+    Moreover, just as in highly-variable communities where 
+    said variation is more seasonal, New Zealand 
+    communities are dominated by ecological
+    generalists~\cite{Winterbourn1997,Winterbourn1981} 
+    implying that they appear to fit the general pattern of 
+    streams worldwide.
+
+    Importantly, while terrestrial communities are also 
+    strongly seasonal at high latitudes and can receive 
+    significant allochthonous inputs~\cite{Nakano2001}, 
+    terrestrial consumers tend to be morphologically 
+    specialised for feeding on particular 
+    prey~\cite{Liem1990}. This means that primarily 
+    gape-limited aquatic consumers tend to be more
+    generalist across all types of aquatic habitats than 
+    terrestrial consumers~\cite{Liem1990,Shurin2006}. The
+    key to this explanation of the differences between 
+    freshwater and marine and estuarine  ecosystems is 
+    whether the former experience more severe seasonal 
+    variation. Although we are not aware of any study 
+    explicitly comparing seasonal variation in freshwater 
+    and saltwater or brackish food webs in a similar 
+    location, we believe that freshwater ecosystems are 
+    indeed likely to  experience more severe changes 
+    because of their small size. While oceans and estuaries 
+    certainly vary in terms of water temperature and
+    nutrients over the course of a year~\cite{Baird1989}, 
+    these changes are likely to be slower and milder than 
+    in freshwaters because marine and estuarine communities 
+    are buffered by being open to the ocean rather than 
+    isolated in the midst of a terrestrial matrix. Net 
+    primary productivity in particular is much more 
+    variable over the course of a year in non-marine 
+    communities~\cite{Field1998}, suggesting that niche 
+    breadths may also be more variable over the course of 
+    the year.
 
@@
   We now include a conceptual figure to clearly and succinctly link the changes
-  to scaling relationships we expected to the two versions of the latitude-niche
+  to scaling relationships we expected to these two versions of the latitude-niche
   breadth hypothesis (Fig. 1).
 
-  At lines XX-XX we have added parenthetical explanations of the original and 
-  trophic-species versions of food webs. We have also added parenthetical definitions
+  We have explained ``trophic species webs" more thoroughly
+  in lines 58-60 and added parenthetical definitions of
+  trophic-species and orignal webs in lines 62-64. We have also added parenthetical definitions
   of link density, generality, and vulnerability at the begining of the results section
@@
 
-    We therefore analysed both original (i.e., without aggregating any species) and
-    trophic-species (i.e., after aggregating species with identical predators and
+    Many analyses of food-web structure attempt to reduce 
+    this variation by using food webs comprised of ``trophic
+    species'' --aggregations of species with identical sets 
+    of predators and prey-- rather than species 
+    \emph{per se}~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}.
+
+    \smallskip
+
+    We therefore analysed both original (i.e., without 
+    aggregating any species) and trophic-species (i.e., 
+    after aggregating species with identical predators and 
     prey) versions of the dataset ...
@@
 
-      Link density (mean number of feeding links per species), generality
-      (mean number of prey per species), and vulnerability (mean number of predators
-      per species) were strongly and positively correlated ...
+    Link density (mean number of feeding links per 
+    species), generality (mean number of prey per species), 
+    and vulnerability (mean number of predators per 
+    species) were strongly and positively correlated ...
 
@@
 
-  In fact we did analyse absolute numbers of species within a trophic level as well 
+  In fact, we originally did analyse absolute numbers of species within a trophic level as well 
   as proportions. Both ways of defining the distribution of species across trophic levels
   have benefits (absolute numbers are more intuitive, as the Referee points out, while
-  proportions feature in more of the food-web literature) and so we ultimately decided
-  on proportions because the trends were clearer than in absolute numbers. [[Should we just
-  give both now that this is in the supplemental?]]
+  proportions feature in more of the food-web literature).
+  Further, as the two measures are closely related, the
+  trends captured using proportions were almost identical
+  to those captured using absolute numbers. We ultimately
+  decided on proportions because the trends were clearer 
+  than in absolute numbers.
 
@@
 
-  \textbf{R:} We had originally viewed this analysis as a very minor part of our paper,
-  but are happy to follow the Reviewer's suggestion and integrate it in the methods and
-  results along with our main analyses. We have described the methods for this analysis
-  in lines XX-XX and summarize our results in lines XX-XX.
+  \textbf{R:} Given the lack of significant relationships,
+  we had originally viewed this analysis as a very minor 
+  part of our paper, but are happy to follow the Reviewer's 
+  suggestion and integrate it in the methods and
+  results along with our main analyses. We now describe 
+  the methods for this analysis in lines 74-86 and 
+  summarize our results in lines 132-136.
 
@@
 
-    \textbf{Gradients over latitude}
+    \textbf{Gradients over Latitude}
 
@@
     marine, lake, and terrestrial networks with estuarine
-    networks providing the intercept) and $\epsilon_{i}$ is a residual error term. 
+    networks corresponding to $E_{i}=0$) and $\epsilon_{i}$ is a residual error term. 
     We next calculated the AIC
     of the maximal model as well as the AIC's of a suite of candidate simplified models identified
-    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
+    using the R~\cite{R} function dredge from package MuMIn~\cite{MuMIn}. 
     Simplified models were obtained by
@@
     The best-fitting model was then determined to be the model with the fewest terms 
-    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
-    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
-    model.
+    where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
 
@@
 
-    Contrary to the expected latitudinal gradient, the best-fit version of
-    equation~(\ref{Latfull}) for species richness did not  include a signficant
-    effect of latitude for any  ecosystem type. Further, there were no
-    relationships between link density, generality, or vulnerability with
+    Contrary to the expected latitudinal gradient, the 
+    best-fit version of equation (1) did not include a 
+    significant effect of latitude for any ecosystem type. 
+    Further, there were no significant relationships 
+    between link density, generality, or vulnerability with
     latitude for any ecosystem type.

### 2015-09-06 manuscript/latitudepaper.tex
Added DBS changes to sup, should be g2g

@@
 
-    \noindent As the two forms imply a statistical fit to the data to different error 
+    \noindent As the two forms imply a statistical fit of the data to different error 
     distributions, neither of which has strong
@@
 
-    We then simplified each model following the procedure described above.
+    We then simplified versions of model~\ref{LogLat} for link density, generality, and vulnerability following the procedure described above.
     As a supplemental check to ensure that variation in sampling effort
@@
   to the expected latitudinal gradient, the best-fit version of
-  equation~(\ref{Latfull}) for species richness did not include a significant
+  equation~(\ref{Latfull}) did not include a significant
   effect of latitude for any ecosystem type. Further, there were no significant
@@
   tend to experience seasonal strong pulses of allochthonous inputs (e.g.,
-  fallen leaves,terrestrial
+  fallen leaves, terrestrial
   invertebrates~\cite{Nakano2001,Lennon2004,Zeng2008}. These trends combined
@@
   webs is very tightly grouped in latitude ($44.64-46.41^{\circ}$S, within an
-  overall range of $23-69.02^{\circ}$), it is unlikely that they have greatly
+  overall range of $23-69.02^{\circ}$ for stream communities), it is unlikely that they have greatly
   influenced our results (see also \emph{Appendix S3}). Moreover, just as in
@@
   This means that primarily gape-limited aquatic consumers tend to be more
-  general across all types of aquatic habitats~\cite{Liem1990,Shurin2006}. The
+  generalist across all types of aquatic habitats than terrestrial consumers~\cite{Liem1990,Shurin2006}. The
   key to this explanation of the differences between freshwater and
@@
   by being open to the ocean rather than isolated
-  in the midst of a terrestrial matrix . Net primary productivity in particular is
+  in the midst of a terrestrial matrix. Net primary productivity in particular is
   much more variable over the course of a year in non-marine communities~\cite{Field1998},

### 2015-09-07 manuscript/AC-reply-to-referees.tex
Changed main text, reply

@@
 
-  Lines 22-27:
-
   \begin{quotation}
@@
 
-  \end{quotation}
-
-  Lines 37-44:
-
-  \begin{quotation}
+    \smallskip
 
@@
 
-  Lines 83-86:
-
   \begin{quotation}
@@
 
-  \textbf{R:} We have followed Reviewer 2's suggestion and 
-  moved these additional analyses to the supplemental 
-  information. We were interested in exploring scaling 
-  relationships with different trophic level because each
-  represents a different component of the niche space and 
-  therefore interact differently with latitude, and have now
-  added a brief explanation of our motivation in lines 
-  121-127.
-
-  \begin{quotation}
-
-    We then repeated the above analyses to measure the 
-    effect of latitude on the scaling of specialisation 
-    with numbers and proportions of species at different 
-    trophic levels (i.e., basal resources, intermediate 
-    consumers, and top predators). As different trophic 
-    levels represent different sections of the biotic niche 
-    space, we expected that latitude might affect the 
-    scaling of specialisation with the proportion of 
-    species in each trophic level differently. The results
-    of these supplemental analyses largely echo the the
-    results of the species-richness analyses, and are 
-    presented in~\emph{Appendix S4}.
-
-  \end{quotation}
+  \textbf{R:} After carefully considering the Associate 
+  Editor and Reviewer's comments, we have opted to remove
+  the by-trophic-level analyses entirely. Due to length
+  restrictions, we were not able to both expand our 
+  description of the motivations for and implications of
+  these analyses and accommodate the other changes suggested
+  by the Associate Editor and Reviewers. We chose to focus
+  on ensuring that the discussion of the species-richness
+  results is as clear and complete as possible, and believe
+  that our manuscript is stronger and more to-the-point
+  after these changes.
 
@@
   expected. We have added a brief description of these 
-  correlations to the main text (lines 129-132) as we 
+  correlations to the main text (lines 122-125) as we 
   believe it will provide some context for the very similar 
@@
 
-  \textbf{R:} We have ammended the text (lines 143-146) to support our statement.
+  \textbf{R:} We have ammended the text (lines 135-138) to support our statement.
 
@@
 
-  \textbf{R:} Following Reviewer 1's suggestion, we have restructured our discussion
+  \textbf{R:} Following Reviewer 1's suggestion, we have 
+    restructured our discussion
     to focus more on seasonality in different ecosystem types than on prey-switching.
@@
   and have substantially revised our discussion (lines 
-  190-225) to follow it. The Reviewer will note that our 
+  182-217) to follow it. The Reviewer will note that our 
   arguments include lakes as well as streams since both 
@@
 
-  2) Move by-trophic-level analysis to supplemental information, consider
-  numbers of species rather than proportions.
+  2) Reconsider by-trophic-level analysis.
 
@@
 
-  \textbf{R:} Following the Referee's suggestion, we have moved our analysis
-  of scaling relationships by trophic levels to the supplemental information.
-  We hope that this will address the Referee's first two concerns above. We thank the
-  Referee for this suggestion as it has allowed us more space to describe our network
-  measures in more accessible terms.
-
-  In fact, we originally did analyse absolute numbers of species within a trophic level as well 
-  as proportions. Both ways of defining the distribution of species across trophic levels
-  have benefits (absolute numbers are more intuitive, as the Referee points out, while
-  proportions feature in more of the food-web literature).
-  Further, as the two measures are closely related, the
-  trends captured using proportions were almost identical
-  to those captured using absolute numbers. We ultimately
-  decided on proportions because the trends were clearer 
-  than in absolute numbers.
+  \textbf{R:} We appreciate the Reviewer's concerns about 
+  the integration of these results into the main text. Due 
+  to length restrictions, we were unable to explain our 
+  motivations and discuss our results more fully in the main
+  text. Moreover,
+  referring briefly to by-trophic-level results in the supplemental
+  information repeated the problems with lack of justification and
+  poor integration of the by-trophic-level results with the 
+  species-richness results. To that end we have opted to remove
+  these results entirely. Instead, we have prioritised enriching
+  our discussion of the species-richness results, clarifying our
+  methods, and including the latitudinal gradient in species-richness
+  as requested below. We hope that, on balance, this restructuring has
+  resulted in a clearer and more well-integrated manuscript.
 
@@
   the methods for this analysis in lines 74-86 and 
-  summarize our results in lines 132-136.
+  summarize our results in lines 125-128.
 
@@
 
-  We have added a brief explanation, and the number of webs in each ecosystem type, at lines XX-XX:
+  We have added a brief explanation, and the number of webs in each ecosystem type, at lines 52-55:
 
@@
 
-  \textbf{R:} The top predators were indeed included in this figure (we suspect that the reviewer
-  may have experienced a printing error), but as we have followed the reviewer's earlier
-  suggestion and moved the by-trophic-level analysis to the supplemental information this becomes
-  a moot point. We have slightly modified the y-axis on the new version of this figure and feel that
-  it is now much clearer.
+  \textbf{R:} We thank the reviewer for pointing this out 
+  and, while the inclusion of top predators specifically
+  is moot since these results have been moved to the 
+  supplemental information, have taken care that all labels
+  are included in all figures. We have also re-labelled the
+  y-axes on Fig. 2 (the old Fig. 1) to improve clarity.
 

### 2015-09-07 manuscript/latitudepaper.tex
Changed main text, reply

@@
 
-    We then repeated the above analyses to measure the 
-    effect of latitude on the scaling of specialisation 
-    with numbers and proportions of species at different 
-    trophic levels (i.e., basal resources, intermediate 
-    consumers, and top predators). As different trophic 
-    levels represent different sections of the biotic niche 
-    space, we expected that latitude might affect the 
-    scaling of specialisation with the proportion of 
-    species in each trophic level differently. The results
-    of these supplemental analyses largely echo the the
-    results of the species-richness analyses, and are 
-    presented in~\emph{Appendix S4}.
+    % We then repeated the above analyses to measure the 
+    % effect of latitude on the scaling of specialisation 
+    % with numbers and proportions of species at different 
+    % trophic levels (i.e., basal resources, intermediate 
+    % consumers, and top predators). As different trophic 
+    % levels represent different sections of the biotic niche 
+    % space, we expected that latitude might affect the 
+    % scaling of specialisation with the proportion of 
+    % species in each trophic level differently. The results
+    % of these supplemental analyses largely echo the the
+    % results of the species-richness analyses, and are 
+    % presented in~\emph{Appendix S4}.
 
@@
 ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
-see Fig.~\emph{S7}, \emph{Appendix S5}.}
+see Fig.~\emph{S7}, \emph{Appendix S4}.}
 \label{props_v_lat}

### 2015-09-07 manuscript/supplement.tex
Maybe done?

@@
 
-\subsection*{Appendix S4: Scaling relationships by trophic level}
-
-  \subsubsection*{Methods}
-
-    We were also interested in the ways that scaling
-    relationships with species richness might
-    be affected by changes to the distribution of species 
-    among trophic levels. [[more justification of why]]
-    To that end, we repeated our 
-    analyses replacing species richness with the
-    proportion of basal resources, proportion of 
-    intermediate consumers, or proportion of top 
-    predators. All model fitting procedures were identical 
-    to those described for species richness. The model 
-    simplicication procedure was similar to
-    the procedure described for species richness, except 
-    that in some cases there were multiple models with 
-    $\delta$AIC\textless2 that shared the minimal degrees 
-    of freedom. In these cases, we defined the 
-    best-fitting model as the model with the lowest AIC in 
-    the set of models with $\delta$AIC\textless2 and the 
-    minimal degrees of freedom.
-
-  \subsubsection*{Results}
-
-    As with species richness, specialisation scaled with
-    the numbers and proportions of species at each trophic
-    level following a lognormal distribution.
-    The relationships between latitude and the proportions of species at each
-    trophic level were more complex than the flat relationship between latitude
-    and species richness in this dataset.  The proportion of basal resources
-    increased towards the poles in stream webs
-    ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
-    with latitude in estuarine, marine, lake, or terrestrial  food webs
-    ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
-    intermediate consumers decreased towards the poles in all ecosystem types
-    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
-    $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
-    in a food web,  meanwhile, decreased towards the poles in lake and  stream
-    food webs but did not vary in other ecosystem types
-    ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
-    $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
-
-    Unlike species richness, only generality showed an overall increase with
-    increasing proportions of basal resources in a web ($\beta_0$=0.019,
-    $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
-    link density, generality, and vulnerability, respectively;
-    Fig.~\ref{TL_rescaled}). In each case, however, there were substantial
-    effects of latitude on the scaling relationships. Thus, the scaling
-    exponents for link density and vulnerability were negative for estuarine,
-    lake, and stream communities and became more negative towards the poles
-    ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
-    $p$\textless0.001, respectively; Fig.~\ref{B}). For the scaling of link
-    density and vulnerability in marine and terrestrial communities, the overall
-    effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
-    $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
-    $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
-    $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
-    that there was weak scaling at most latitudes. In contrast, the scaling
-    exponent of generality with the proportion of basal resources was positive
-    near the equator and negative near the poles in estuarine, lake, and stream
-    communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
-    very little change in the scaling exponents for marine and terrestrial
-    communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
-    $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
-
-    As with species richness, link density, generality, and vulnerability
-    generally increased with the proportion of intermediate consumers in a web
-    ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
-    $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{TL_rescaled}). 
-    The best-fit models for link density and vulnerability did not include
-    any effect of latitude. In contrast, the strength of the scaling relationship
-    for generality increased weakly towards the poles in estuarine, marine, and
-    terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
-    towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
-    and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{I}).
-
-    In contrast to the generally positive scaling relationships above, link
-    density, generality, and vulnerability decreased as the proportion of top
-    predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
-    $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
-    Fig~\ref{TL_rescaled}). For estuarine, lake, and marine food webs the
-    strength of this scaling did not vary significantly with latitude
-    ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
-    $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
-    In stream and terrestrial food webs, however, scaling was more strongly negative in the 
-    tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
-    and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
-    $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
-    for vulnerability; Fig.~\ref{T}. The best-fit model for generality did not include any terms
-    for latitude in any ecosystem type.
-
-\newpage
-
-\subsection*{Appendix S5: supplemental figures}
+% \subsection*{Appendix S4: Scaling relationships by trophic level}
+
+%   \subsubsection*{Methods}
+
+%     We were also interested in the ways that scaling
+%     relationships with species richness might
+%     be affected by changes to the distribution of species 
+%     among trophic levels. [[more justification of why]]
+%     To that end, we repeated our 
+%     analyses replacing species richness with the
+%     proportion of basal resources, proportion of 
+%     intermediate consumers, or proportion of top 
+%     predators. All model fitting procedures were identical 
+%     to those described for species richness. The model 
+%     simplicication procedure was similar to
+%     the procedure described for species richness, except 
+%     that in some cases there were multiple models with 
+%     $\delta$AIC\textless2 that shared the minimal degrees 
+%     of freedom. In these cases, we defined the 
+%     best-fitting model as the model with the lowest AIC in 
+%     the set of models with $\delta$AIC\textless2 and the 
+%     minimal degrees of freedom.
+
+%   \subsubsection*{Results}
+
+%     As with species richness, specialisation scaled with
+%     the numbers and proportions of species at each trophic
+%     level following a lognormal distribution.
+%     The relationships between latitude and the proportions of species at each
+%     trophic level were more complex than the flat relationship between latitude
+%     and species richness in this dataset.  The proportion of basal resources
+%     increased towards the poles in stream webs
+%     ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
+%     with latitude in estuarine, marine, lake, or terrestrial  food webs
+%     ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
+%     intermediate consumers decreased towards the poles in all ecosystem types
+%     except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
+%     $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
+%     in a food web,  meanwhile, decreased towards the poles in lake and  stream
+%     food webs but did not vary in other ecosystem types
+%     ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
+%     $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
+
+%     Unlike species richness, only generality showed an overall increase with
+%     increasing proportions of basal resources in a web ($\beta_0$=0.019,
+%     $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
+%     link density, generality, and vulnerability, respectively;
+%     Fig.~\ref{TL_rescaled}). In each case, however, there were substantial
+%     effects of latitude on the scaling relationships. Thus, the scaling
+%     exponents for link density and vulnerability were negative for estuarine,
+%     lake, and stream communities and became more negative towards the poles
+%     ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
+%     $p$\textless0.001, respectively; Fig.~\ref{B}). For the scaling of link
+%     density and vulnerability in marine and terrestrial communities, the overall
+%     effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
+%     $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
+%     $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
+%     $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
+%     that there was weak scaling at most latitudes. In contrast, the scaling
+%     exponent of generality with the proportion of basal resources was positive
+%     near the equator and negative near the poles in estuarine, lake, and stream
+%     communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
+%     very little change in the scaling exponents for marine and terrestrial
+%     communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
+%     $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
+
+%     As with species richness, link density, generality, and vulnerability
+%     generally increased with the proportion of intermediate consumers in a web
+%     ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
+%     $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{TL_rescaled}). 
+%     The best-fit models for link density and vulnerability did not include
+%     any effect of latitude. In contrast, the strength of the scaling relationship
+%     for generality increased weakly towards the poles in estuarine, marine, and
+%     terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
+%     towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
+%     and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{I}).
+
+%     In contrast to the generally positive scaling relationships above, link
+%     density, generality, and vulnerability decreased as the proportion of top
+%     predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
+%     $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
+%     Fig~\ref{TL_rescaled}). For estuarine, lake, and marine food webs the
+%     strength of this scaling did not vary significantly with latitude
+%     ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
+%     $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
+%     In stream and terrestrial food webs, however, scaling was more strongly negative in the 
+%     tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
+%     and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
+%     $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
+%     for vulnerability; Fig.~\ref{T}. The best-fit model for generality did not include any terms
+%     for latitude in any ecosystem type.
+
+\newpage
+
+\subsection*{Appendix S5: supplemental figure}
 
@@
 
-\newpage
-
-\begin{figure}[!h]
-\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts.eps}}
-\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
-relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
-Link density, generality,
-and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
-type. As these relationships take the form of power laws, we did this by dividing the food-web
-property (e.g. link density) by species richness raised to an exponent including the 
-effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
-type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
-ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
-latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
-we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
-ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
-see Fig.~\ref{TL_observed}.}
-\label{TL_rescaled}
-\end{figure}
-
-\newpage
-
-\begin{figure}[!h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
-\caption{Scaling relationships for link density, generality, 
-and vulnerability relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
-For each relationship, we show observed values (white circles) and 
-a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
-any effects of habitat type or latitude (black line, N=196 food webs). See Fig.~\ref{TL_rescaled} to compare with 
-observed values correcting for the effects of habitat type and latitude. }
-\label{TL_observed}
-\end{figure}
-
-\newpage
-
-\begin{figure}[!h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
-empirical food webs. Latitude is given in degrees
-from the equator regardless of direction.}
-\label{B}
-\end{figure}
-
-\begin{figure}[!h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
-N=196 empirical food webs. Latitude is given in degrees
-from the equator regardless of direction.}
-\label{I}
-\end{figure}
-
-\newpage
-
-\begin{figure}[!h]
-\centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-types and over latitude. For each property we show the scaling exponent for the proportion of
-top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
-empirical food webs. Latitude is given in degrees
-from the equator regardless of direction.}
-\label{T}
-\end{figure}
+% \newpage
+
+% \begin{figure}[!h]
+% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts.eps}}
+% \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
+% relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
+% Link density, generality,
+% and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
+% type. As these relationships take the form of power laws, we did this by dividing the food-web
+% property (e.g. link density) by species richness raised to an exponent including the 
+% effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
+% type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
+% ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
+% latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
+% we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
+% ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
+% see Fig.~\ref{TL_observed}.}
+% \label{TL_rescaled}
+% \end{figure}
+
+% \newpage
+
+% \begin{figure}[!h]
+% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
+% \caption{Scaling relationships for link density, generality, 
+% and vulnerability relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
+% For each relationship, we show observed values (white circles) and 
+% a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
+% any effects of habitat type or latitude (black line, N=196 food webs). See Fig.~\ref{TL_rescaled} to compare with 
+% observed values correcting for the effects of habitat type and latitude. }
+% \label{TL_observed}
+% \end{figure}
+
+% \newpage
+
+% \begin{figure}[!h]
+% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
+% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+% types and over latitude. For each property we show the scaling exponent for the proportion of
+% basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
+% empirical food webs. Latitude is given in degrees
+% from the equator regardless of direction.}
+% \label{B}
+% \end{figure}
+
+% \begin{figure}[!h]
+% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
+% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+% types and over latitude. For each property we show the scaling exponent for the proportion of
+% intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
+% N=196 empirical food webs. Latitude is given in degrees
+% from the equator regardless of direction.}
+% \label{I}
+% \end{figure}
+
+% \newpage
+
+% \begin{figure}[!h]
+% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
+% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
+% types and over latitude. For each property we show the scaling exponent for the proportion of
+% top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
+% empirical food webs. Latitude is given in degrees
+% from the equator regardless of direction.}
+% \label{T}
+% \end{figure}
 

### 2015-09-08 manuscript/supplement.tex
Bibliographies are done

@@
     {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
         \hline
@@
         Mondego & 1 & \cite{Patricio2006}  & estuary & 40,08 N & Yes   &       \\
-        \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         Montane Forest & 1 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & No    & Duplicated in GlobalWeb (web60) \\
@@
         SimberloffE2 & 1 & \cite{Simberloff1976}  & terrestrial & 24,40,33 N & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         SimberloffE3 & 1 & \cite{Simberloff1976}  & terrestrial & 24,41,23.82 N & Yes   &       \\
@@
         3     & 3 & \cite{Woodwell1967}    & estuary & 41,03,11 N & Yes   &       \\
-        \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         4     & 3 & \cite{Johnston1956}    & estuary &       & No    & Sink web \\
@@
         15    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         16    & 3 & \cite{Copeland1974}    & estuary &       & No    & Could not locate original source \\
@@
         31    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
-      \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
@@
         51    & 3 & \cite{Dexter1947}    & marine & 42,38,56 N & Yes   &       \\
+      \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         52    & 3 & \cite{Paine1980a}    & marine & 58,27 N & Yes   &       \\
@@
         62    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
-        \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         63    & 3 & \cite{Jones1950}     & stream & 52,25,08 N & Yes   &       \\
@@
         85    & 3 & \cite{Mizuno1982}  & lake &       & No    & Could not locate original source \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         86    & 3 & \cite{Hogetsu1979}  & marine & 34,36 - 35,38 N & Yes   &       \\
         87    & 3 & \cite{Bradstreet1982}  & terrestrial & 72,46,34.95 N & Yes   &       \\
-        \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         88    & 3 & \cite{Kuusela1980}  & stream &       & No    & Could not locate original source \\
@@
         114   & 3 & \cite{Marshall1982}  & lake  & 17,54,11.90 S & Yes   &       \\
-        \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         115   & 3 & \cite{Koepcke1952}  & marine &       & No    & Could not locate original source \\
@@
         122   & 3 & \cite{Nixon1973}  & estuary & 41,33,04 N & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         123   & 3 & \cite{Harris1972}  & terrestrial & 40,45,28 N & Yes   &       \\
@@
         143   & 3 & \cite{Snow1958}    & lake  & 34,41,45 N & Yes   &       \\
-         \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         144   & 3 & \cite{Snow1958}  & lake  &       & No    & Could not locate original source \\
@@
         158   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
+         \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         159   & 3 & \cite{Askew1961}     & terrestrial &       & No    & Host-parasitoid web \\
@@
         178   & 3 & \cite{Hawkins1984}    & terrestrial &       & No    & Host-parasitoid web \\
-        \hline
-        \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         179   & 3 & \cite{Robinson1953}  & terrestrial &       & No    & Source web \\
@@
         194   & 3 & \cite{McKinnerney1978}    & terrestrial &       & No    & Could not locate original source \\
+        \hline
+        \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         195   & 3 & \cite{Schoenly1983a}    & terrestrial &       & No    & Could not locate original source \\
@@
         205   & 3 & \cite{Hildrew1985}     & stream & 51,01,05 N & Yes   &       \\
-        \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         206   & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
@@
         230   & 3 & \cite{Thompson2004c}  & stream & 45 S  & Yes   &       \\
+        \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         231   & 3 & \cite{Thompson2004c}  & stream & 45.58 S & Yes   &       \\
@@
         239   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-         \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         240   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
@@
         266   & 3 & \cite{Cornejo-Donoso2008}  & marine & 60 - 69 S & Yes   &       \\
+         \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         267   & 3 & \cite{Zetina-Rejon2003}  & marine & 23.15 - 22.9N & Yes   &       \\
@@
         269   & 3 & \cite{Liu2007}  & lake  & 29,32,35 N & Yes   &       \\
-         \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         270   & 3 & \cite{Filgueira2011}  & marine & 42,17,37 - 42,19,29 N & Yes   &       \\
@@
         300   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+         \hline
+      \end{tabular}}%
+      \end{table}
+
+        \newpage
+
+    \begin{table}[h!]
+    \centering
+    {\footnotesize
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
         301   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
@@
         303   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
-         \hline
-      \end{tabular}}%
-      \end{table}
-
-        \newpage
-
-    \begin{table}[h!]
-    \centering
-    {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
         304   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
@@
         336   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,36 N & Yes   &       \\
-        337   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
          \hline
@@
     {\footnotesize
-      \begin{tabular}{p{2.8cm}p{1.3cm}p{5.5cm}p{2.2cm}p{2.5cm}lp{3.5cm}}
-        \hline
-        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
-        \hline
+      \begin{tabular}{p{2.8cm}p{1.3cm}p{3cm}p{2.2cm}p{2.5cm}lp{8.2cm}}
+        \hline
+        Web ID & Collection & Original Source & Ecosystem & Latitude(degrees) & Used  & Reason for rejection  \\
+        \hline
+        337   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,05 N & Yes   &       \\
         338   & 3 & \cite{Torres2013}  & marine &       & No    & Could not locate original source \\
@@
 \bibliographystyle{prsb}%Compile with jae.bst style file
-\bibliography{noISN}% your .bib file(s)
+\bibliography{abbreviated}% your .bib file(s)
 

### 2015-09-08 manuscript/AC-reply-to-referees.tex
no more changes, spellchecked

@@
 
-\usepackage[britdate]{canterbury-letter}
-% \usepackage[britdate,alyssa-signature]{canterbury-letter}
+%\usepackage[britdate]{canterbury-letter}
+ \usepackage[britdate,alyssa-signature]{canterbury-letter}
 \usepackage{times}
@@
 
-  \textbf{R:} We had originally intended to emphasize that, contrary to our expectations,
+  \textbf{R:} We had originally intended to emphasise that, contrary to our expectations,
   scaling relationships did not vary over latitude in~\emph{most} ecosystems. We have now amended our
@@
 
-  \textbf{R:} We have ammended the text (lines 135-138) to support our statement.
+  \textbf{R:} We have amended the text (lines 135-138) to support our statement.
 
@@
 
-  \textbf{R:} We have changed all refences to the Vancouver style and have 
+  \textbf{R:} We have changed all references to the Vancouver style and have 
     added sections for author contributions, conflicts of interest, and funding.
@@
 
-    As a supplemental check to ensure that variation in sampling effor across
+    As a supplemental check to ensure that variation in sampling effort across
     food webs was not responsible for the trends we observed, we then repeated
@@
 
-   2) Emphasize our results for streams, include the possibility that they
+   2) Emphasise our results for streams, include the possibility that they
    may be due to greater seasonality in stream food webs.
@@
     applied network metrics and underlying scaling relationships; a conceptual
-    figure visualizing the expected relationships for different communities
+    figure visualising the expected relationships for different communities
     according to the latitude-niche breadth hypothesis could be very helpful
@@
   in lines 58-60 and added parenthetical definitions of
-  trophic-species and orignal webs in lines 62-64. We have also added parenthetical definitions
-  of link density, generality, and vulnerability at the begining of the results section
+  trophic-species and original webs in lines 62-64. We have also added parenthetical definitions
+  of link density, generality, and vulnerability at the beginning of the results section
   to remind readers of the biological meaning of these measures.
@@
   the methods for this analysis in lines 74-86 and 
-  summarize our results in lines 125-128.
+  summarise our results in lines 125-128.
 
@@
 
-  5) The y-xais of Fig. 1 is unclear, top predators are unlabelled.
+  5) The y-axis of Fig. 1 is unclear, top predators are unlabelled.
 

### 2015-09-08 manuscript/AC-reply-to-referees.tex
forgot to add siggy
Added regs
big bad deltas

@@
 \usepackage{geometry}
-\usepackage[round]{natbib}
+\usepackage[numbers,sort&compress]{natbib}
 \usepackage{graphicx}
@@
     choice to select the model with the lowest AIC as the best-fit model when
-    models have $\delta$AIC\textless2? To what extent does this choice affect your
+    models have $\Delta$AIC\textless2? To what extent does this choice affect your
     conclusions?
@@
   \textbf{R:} We are also aware of the general consensus    that models where
-  $\delta$AIC\textless2 are roughly equally well-supported. This is why our
+  $\Delta$AIC\textless2 are roughly equally well-supported. This is why our
   procedure (as stated in lines 83-86) was to first consider the set of models
-  where $\delta$AIC\textless2 and select the model with the fewest degrees of
-  freedom. We chose the smallest model where $\delta$AIC\textless2 in order to
+  where $\Delta$AIC\textless2 and select the model with the fewest degrees of
+  freedom. We chose the smallest model where $\Delta$AIC\textless2 in order to
   avoid over-fitting the models.
@@
   there were several models that shared the minimal degrees 
-  of freedom and all had $\delta$AIC\textless2. In fact, 
+  of freedom and all had $\Delta$AIC\textless2. In fact, 
   this scenario did not occur for the models presented in 
@@
 
-\bibliographystyle{geb}%Compile with jae.bst style file
-\bibliography{noISBN.bib}
+\bibliographystyle{prsb} 
+\bibliography{abbreviated}
 

### 2015-09-08 manuscript/AC-reply-to-referees.tex
switching reviewer to referee

@@
 In your original decision, you encouraged us to resubmit a revised version of
-the manuscript noting that, while the Reviewers were quite positive, they and
+the manuscript noting that, while the Referees were quite positive, they and
 the Associate Editor had a few substantial concerns. We appreciate the
@@
 feel that the revised manuscript is both stronger and more accessible, and
-hope that it will please the Editors and Reviewers alike.
+hope that it will please the Editors and Referees alike.
 
@@
   of the latitude-niche breadth hypothesis. We have also 
-  followed Reviewer 2's suggestion and now provide a 
+  followed Referee 2's suggestion and now provide a 
   conceptual figure (Fig. 1) that clearly places our study
@@
     L100-106. After reading the introduction, it is not clear why you ‘were
-    also interested’ in this topic. I suggest following the advice of reviewer
+    also interested’ in this topic. I suggest following the advice of Referee
     2 and moving this part and the associated results to the appendix. Please
@@
   \textbf{R:} After carefully considering the Associate 
-  Editor and Reviewer's comments, we have opted to remove
+  Editor and Referee's comments, we have opted to remove
   the by-trophic-level analyses entirely. Due to length
@@
   these analyses and accommodate the other changes suggested
-  by the Associate Editor and Reviewers. We chose to focus
+  by the Associate Editor and Referees. We chose to focus
   on ensuring that the discussion of the species-richness
@@
 
-  \textbf{R:} Following Reviewer 1's suggestion, we have 
+  \textbf{R:} Following Referee 1's suggestion, we have 
     restructured our discussion
@@
 % -----------------------------------------------------------------------------
-{\Large \bf Reply to Reviewer 1}
+{\Large \bf Reply to Referee 1}
 % ---------------------------------------
 
-  The Reviewer was very positive about our manuscript, calling it
+  The Referee was very positive about our manuscript, calling it
   ``an interesting paper that takes advantage of recent compilations
@@
   niche breadth'', ``exceptionally well written and presented'', ``sophisticated
-  and well thought out''. We thank the Reviewer for their kind words,
+  and well thought out''. We thank the Referee for their kind words,
   and also for their suggestions for further improving our manuscript. We
@@
 
-  \textbf{R:} We share the reviewer's concern that variation in sampling
+  \textbf{R:} We share the Referee's concern that variation in sampling
   effort could be driving the trends we observe, as it is highly likely that
   the authors of all 196 webs in our dataset did not follow the same procedures.
-  Following the reviewer's suggestion, we have performed a jackknife analysis by
+  Following the Referee's suggestion, we have performed a jackknife analysis by
   systematically removing each web in turn and then repeating our analysis. We
@@
   of their results to the supporting information 
-  (~\emph{Appendix S3}), and we thank the reviewer for 
+  (~\emph{Appendix S3}), and we thank the Referee for 
   suggesting this validation of our overall results. We 
@@
 
-  \textbf{R:} We thank the Reviewer for this suggestion, 
+  \textbf{R:} We thank the Referee for this suggestion, 
   and have substantially revised our discussion (lines 
-  182-217) to follow it. The Reviewer will note that our 
+  182-217) to follow it. The Referee will note that our 
   arguments include lakes as well as streams since both 
   systems showed effects of latitude on scaling, and both 
-  experience severe seasonal variability as the Reviewer
+  experience severe seasonal variability as the Referee
   points out for streams. We have also added a brief note 
   to address the potential that the New Zealand stream food 
-  webs mentioned by the Reviewer above might be affecting 
+  webs mentioned by the Referee above might be affecting 
   our results. As described below, they are grouped in a 
@@
 % -----------------------------------------------------------------------------
-{\Large \bf Reply to Reviewer 2}
+{\Large \bf Reply to Referee 2}
 % ---------------------------------------
 
-  The Reviewer stated that our study is interesting and covers ``a timely and
+  The Referee stated that our study is interesting and covers ``a timely and
   important topic. The core analysis of the paper (scaling relationships of
   food web metrics with species richness) are convincingly presented and
-  comprehensively discussed.'' Nevertheless, the Reviewer has suggested several
+  comprehensively discussed.'' Nevertheless, the Referee has suggested several
   ways in which our manuscript could be improved. We have responded to each suggestion
@@
 
-  \textbf{R:} We thank the reviewer for their concern that our manuscript
+  \textbf{R:} We thank the Referee for their concern that our manuscript
   should be accessible to as wide a variety of researchers as possible, and
-  have followed the reviewer's suggestions in several places in the manuscript.
+  have followed the Referee's suggestions in several places in the manuscript.
   We now include a conceptual figure to clearly and succinctly link the changes
@@
 
-  \textbf{R:} We appreciate the Reviewer's concerns about 
+  \textbf{R:} We appreciate the Referee's concerns about 
   the integration of these results into the main text. Due 
@@
   we had originally viewed this analysis as a very minor 
-  part of our paper, but are happy to follow the Reviewer's 
+  part of our paper, but are happy to follow the Referee's 
   suggestion and integrate it in the methods and
@@
 
-  \textbf{R:} We thank the reviewer for pointing this out 
+  \textbf{R:} We thank the Referee for pointing this out 
   and, while the inclusion of top predators specifically
@@
 
-  \textbf{R:} We have followed the reviewer's suggestion.
+  \textbf{R:} We have followed the Referee's suggestion.
 

### 2015-09-08 manuscript/AC-reply-to-referees.tex
A few minor changes to reply

@@
   scaling relationships did not vary over latitude in~\emph{most} ecosystems. We have now amended our
-  title to ``\mytitle'' in order to better capture the scaling that did occur in streams.
+  title to ``\mytitle'' in order to better capture the scaling that did occur in lakes and streams.
 
@@
   motivations and discuss our results more fully in the main
-  text. Moreover,
-  referring briefly to by-trophic-level results in the supplemental
-  information repeated the problems with lack of justification and
-  poor integration of the by-trophic-level results with the 
-  species-richness results. To that end we have opted to remove
-  these results entirely. Instead, we have prioritised enriching
+  text. Moreover, including brief references in the
+  main text to by-trophic-level results contained in
+  the supplemental information seemed to exacerbate
+  the problems of poor integration of the by-trophic-level results with the 
+  species-richness results. Ultimately, we have opted to remove
+  these results entirely. Rather than maintaining 
+  these results, we have prioritised enriching
   our discussion of the species-richness results, clarifying our

### 2015-09-08 manuscript/latitudepaper.tex
Bibliographies are done
Consistent significant digits in range of latitude

@@
 \usepackage{pdflscape}
-%\usepackage{rotating}
-% make Figure 1 etc bold
 \usepackage[labelfont=bf]{caption}
@@
 
-% let's get some nature formatted citations
-%\usepackage{overcite}
-% \usepackage[round]{natbib}
 \usepackage[numbers,sort&compress]{natbib}
 
-% some cheats to reduce the need to type complicated bits and pieces
 \newcommand{\expect}[1]{\left\langle #1 \right\rangle}
@@
 
-% the abstract formatting
 \newenvironment{sciabstract}{%
@@
 
-% margin sizes`
 \topmargin 0.0cm
@@
 
-\linenumbers
+% \linenumbers
 
 \section*{Introduction}
-
-  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
 
@@
   ecology~\cite{Kaufman1995,Macpherson2002,Schemske2009}.
-
-  % These gradients, together with the strength and generality of associations between biological processes and environmental variables, suggest that variation in network structure 
-  % may also be explained by ecological gradients \cite{Baiser2012}.
 
@@
     to substantial differences in sampling effort across research groups.
-    % If several models shared the fewest
-    % number of terms  and had $\Delta$AIC\textless2, the model with the lowest
-    % AIC in that set was chosen as the best-fit model.
-
-    % We then repeated the above analyses to measure the 
-    % effect of latitude on the scaling of specialisation 
-    % with numbers and proportions of species at different 
-    % trophic levels (i.e., basal resources, intermediate 
-    % consumers, and top predators). As different trophic 
-    % levels represent different sections of the biotic niche 
-    % space, we expected that latitude might affect the 
-    % scaling of specialisation with the proportion of 
-    % species in each trophic level differently. The results
-    % of these supplemental analyses largely echo the the
-    % results of the species-richness analyses, and are 
-    % presented in~\emph{Appendix S4}.
 
@@
   vulnerability.
-  % , or the proportions of food webs accounted for by basal
-  % resources, intermediate consumers, and top predators, except in lake and
-  % stream food webs where the proportions of top predators tended to decrease
-  % towards the poles  (see \emph{Appendix S3} for details).
 
@@
   webs is very tightly grouped in latitude ($44.64-46.41^{\circ}$S, within an
-  overall range of $23-69.02^{\circ}$ for stream communities), it is unlikely that they have greatly
+  overall range of $23.00-69.02^{\circ}$ for stream communities), it is unlikely that they have greatly
   influenced our results (see also \emph{Appendix S3}). Moreover, just as in
@@
   suggesting that niche breadths may also be more variable over the course of the year.
-
-  % This may be partly due to high-latitude 
-  % species tending to switch between different seasonally-available 
-  % prey~\cite{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
-  % freshwater ecosystems may have more stable composition.
-
-  % The scaling of link density, generality and vulnerability with proportions
-  % of species at different trophic levels, however, did not differ between
-  % lakes and most other food webs. Indeed, there was comparatively little
-  % variation in scaling with the trophic-level breakdown of a web across
-  % ecosystem types. Nevertheless, the negative relationships between the
-  % proportion of top predators in a web and link density and vulnerability were
-  % weaker (i.e., the scaling exponent was more strongly negative) in low-latitude 
-  % stream ecosystems. This may imply that top predators in high-latitude 
-  % streams tend to be more generalist than their low-latitude
-  % equivalents~\cite{Winemiller2008}, perhaps due to prey-switching during
-  % seasonal food shortages~\cite{Magalhaes1993}. More generally, the lack of
-  % correspondence between the scaling of food-web properties with species
-  % richness and with proportions of species at each trophic level suggests that
-  % the size and trophic breakdowns of a community can each provide different
-  % information~\cite{Downing2002}.
 
@@
 \newpage
-\bibliographystyle{prsb}%Compile with vancouver.bst style file
-\bibliography{abbreviated}% your .bib file(s)
+\bibliographystyle{prsb}
+\bibliography{abbreviated}
 
-% \end{spacing}
 \newpage
@@
 
-% \begin{figure}[h]
-% % \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
-% \caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
-% consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
-% we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
-% on N=166 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
-% The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
-% proportion was very similar to those of the scaling relationships with link density, except for the 
-% scaling of generality with the proportion of top predators where there was no effect of latitude on the 
-% size of the exponent in any ecosystem type. See Figs.~\emph{S3-S5, Appendix 5} for all scaling relationships.}
-% \label{BIT}
-% \end{figure}
-
 \end{document}

### 2015-09-08 manuscript/supplement.tex
removed double the, couple of touchups to references

@@
   to assess the roles of parasites within food webs. As all but 3 of the webs
-  from~\cite{GlobalWeb} contained only free-living species, we removed the
+  from~\cite{GlobalWeb} contained only free-living species, we removed
   the parasites (and all interactions involving them) from these webs (and the

### 2015-10-05 talk/ABC_2015.tex
did first part of intro

\documentclass{beamer}

\mode<presentation>
{
  \usetheme{Singapore}
  \renewcommand{\insertnavigation}[1]{}
  \setbeamercovered{transparent}
}

\usepackage[english]{babel}
\usepackage[absolute,overlay]{textpos}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage[T1]{fontenc}
\usepackage{soul}
\usepackage{pdflscape}
\usepackage{multirow}

\beamertemplatenavigationsymbolsempty

\newcommand{\citations}[1]
   {
     \begin{textblock}{16}[1,1](15.75,15.25)
       \flushright{\scriptsize #1}
     \end{textblock}
   }

\definecolor{MedPurple}{RGB}{194,165,207}
\definecolor{DeepPurple}{RGB}{118,42,131}
\definecolor{LightGreen}{RGB}{166,219,160}
\definecolor{DarkGreen}{RGB}{0,68,27}
\definecolor{MedGreen}{RGB}{90,174,97}

\setbeamercolor{title}{fg=DeepPurple}
\setbeamercolor{frametitle}{fg=DeepPurple}
\setbeamercolor{structure}{fg=DarkGreen}

\setbeamercolor{*}{bg=LightGreen}

\title[Specialisation \& the Latitude-niche-breadth Hypothesis]
{Specialisation \& the Latitude-niche-breadth Hypothesis}

\author[A.R. Cirtwill, D.B. Stouffer, \& T.N. Romanuk]{\textbf{Alyssa R. Cirtwill}, Daniel B. Stouffer, \& Tamara N. Romanuk} 
\institute[]
{
 %
  Stouffer Lab\\
  School of Biological Sciences\\
  University of Canterbury\\
  Christchurch, New Zealand\\
  ~\\
  www.stoufferlab.org\\
  %
}
\date[Short Occasion] 
{23 October 2015 | ABC 2015}

\subject{Talks}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

% %%Start Introduction Slides%%
\section*{Background}

  \begin{frame}{Why are there more species in the tropics?}

    \begin{center}
      Large species-richness map

    \textbf{Alyssa R. Cirtwill, Daniel B. Stouffer, Tamara N. Romanuk}

    \end{center}
  \end{frame}

  \begin{frame}{Why are there more species in the tropics?}

    \begin{center}
      Large species-richness map

    Productivity? Envionmental stability? Speciation rates?

    \end{center}
  \end{frame}

  \begin{frame}{Why are there more species in the tropics?}

    \begin{center}
      Large species-richness map

    \textbf{Productivity? Envionmental stability?} Speciation rates?

    \end{center}
  \end{frame}

  \begin{frame}{Latitude-Niche Breadth Hypothesis}

    \begin{center}
      \includegraphics[width=.8\textwidth]{Figures/latitude_niche_breadth_1.eps}
    \end{center}

    \footnotesize{Vazquez, D.P. \& Stevens, R.D. 2004. The latitudinal gradient in niche breadth: concepts and evidence. \emph{The American Naturalist} \textbf{164}, E1-19.}
  \end{frame}

  \begin{frame}{Latitude-Niche Breadth Hypothesis}

    \begin{center}
      \includegraphics[width=.8\textwidth]{Figures/latitude_niche_breadth_2.eps}
    \end{center}

    \footnotesize{Vazquez, D.P. \& Stevens, R.D. 2004. The latitudinal gradient in niche breadth: concepts and evidence. \emph{The American Naturalist} \textbf{164}, E1-19.}
  \end{frame}

  \begin{frame}{Latitude-Niche Breadth Hypothesis}

    \begin{center}
      \includegraphics[width=.8\textwidth]{Figures/latitude_niche_breadth_3.eps}
    \end{center}

    \footnotesize{Vazquez, D.P. \& Stevens, R.D. 2004. The latitudinal gradient in niche breadth: concepts and evidence. \emph{The American Naturalist} \textbf{164}, E1-19.}
  \end{frame}

  \begin{frame}{Alternatively ...}

    \begin{center}
      \includegraphics[width=.8\textwidth]{Figures/latitude_niche_breadth_4.eps}
    \end{center}

    \footnotesize{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology} \textbf{88}, 1940-1947.}
  \end{frame}

  \begin{frame}{Alternatively ...}

    \begin{center}
      \includegraphics[width=.8\textwidth]{Figures/latitude_niche_breadth_5.eps}
    \end{center}

    \footnotesize{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology} \textbf{88}, 1940-1947.}
  \end{frame}

\section*{Food Webs}
  \begin{frame}{Testing The Hypotheses}

    \begin{center}
      \includegraphics[width=.8\textwidth]{Figures/hypothesis_comparison.eps}

    \end{center}

    \begin{columns}
    \column{1in}
    \column{1in}
      - Greater specialisation in the tropics
    \column{1in}
    \column{1in}
      - Similar specialisation at all latitudes
    \column{1in}
    \end{columns}

  \end{frame}

  \begin{frame}{Testing The Hypotheses}

    \begin{center}
      \includegraphics[width=.8\textwidth]{Figures/hypothesis_comparison.eps}

    \end{center}

    \begin{columns}
    \column{1in}
    \column{1in}
      - More feeding links per species in tropics
    \column{1in}
    \column{1in}
      - Similar feeding links per species at all latitudes
    \column{1in}
    \end{columns}

  \end{frame}

\end{document}

### 2015-10-07 talk/ABC_2015.tex
introduction completed

@@
 
-\begin{frame}
-  \titlepage
-\end{frame}
+% \begin{frame}
+%   \titlepage
+% \end{frame}
 
@@
     \begin{center}
-      Large species-richness map
+      \includegraphics*[width=.8\textwidth]{Figures/plant_richness.eps}
 
-    \textbf{Alyssa R. Cirtwill, Daniel B. Stouffer, Tamara N. Romanuk}
+      \vspace{1cm}
+
+    \textbf{Alyssa R. Cirtwill}, Daniel B. Stouffer, Tamara N. Romanuk
+
+    \vspace{1cm}
+
+    23 October 2015 | ABC 2015
 
@@
     \begin{center}
-      Large species-richness map
+      \includegraphics*[width=.8\textwidth]{Figures/plant_richness.eps}
 
-    Productivity? Envionmental stability? Speciation rates?
+      \vspace{1cm}
 
+      Envionmental stability? 
+      Productivity? 
+      Speciation rates?
+
+      \vspace{1cm}
+      {\color{white} 23 October 2015 | ABC 2015}
     \end{center}
@@
     \begin{center}
-      Large species-richness map
+      \includegraphics*[width=.8\textwidth]{Figures/plant_richness.eps}
 
-    \textbf{Productivity? Envionmental stability?} Speciation rates?
+      \vspace{1cm}
+
+      \textbf{Envionmental stability?} 
+      \textbf{Productivity?} 
+      Speciation rates?
+
+      \vspace{1cm}
+      {\color{white} 23 October 2015 | ABC 2015}
 
@@
 
-    \footnotesize{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology} \textbf{88}, 1940-1947.}
+    \tiny{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology} \textbf{88}, 1940-1947.}
   \end{frame}
@@
     \begin{columns}
-    \column{1in}
-    \column{1in}
+    \column{.5in}
+    \column{1.75in}
       - Greater specialisation in the tropics
-    \column{1in}
-    \column{1in}
+    \column{.5in}
+    \column{1.75in}
       - Similar specialisation at all latitudes
-    \column{1in}
+    \column{.5in}
     \end{columns}
@@
     \begin{columns}
-    \column{1in}
-    \column{1in}
+    \column{.5in}
+    \column{1.75in}
       - More feeding links per species in tropics
-    \column{1in}
-    \column{1in}
+    \column{.5in}
+    \column{1.75in}
       - Similar feeding links per species at all latitudes
-    \column{1in}
+    \column{.5in}
     \end{columns}
@@
 
+  \begin{frame}{Testing The Hypotheses}
+
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/LittleRockLake.eps}
+
+    195 food webs \\
+    0-78 degrees (absolute latitude) \\
+    Mean L/S, Generality, Vulnerability
+
+    \end{center}
+
+  \end{frame}
+
+  \begin{frame}{Testing The Hypotheses}
+
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/LittleRockLake.eps}
+
+    195 food webs \\
+    0-78 degrees (absolute latitude) \\
+    Mean \textbf{L/S}, Generality, Vulnerability
+
+    \end{center}
+
+  \end{frame}
+
 \end{document}

### 2015-10-08 manuscript/AC-reply-to-referees_2.tex
MS and reply done

--- 2015-09-08 manuscript/AC-reply-to-referees.tex
@@
 
-We have now finished the revisions for the resubmission of our manuscript
-``\mytitle'' for consideration in the Population and Community Ecology section
-of the \myjournal.
-
-In your original decision, you encouraged us to resubmit a revised version of
-the manuscript noting that, while the Reviewers were quite positive, they and
-the Associate Editor had a few substantial concerns. We appreciate the
-comments by the Associate Editor and the Referees, and have taken care to
-address each one while keeping within the size limits set by \myjournal. We
-feel that the revised manuscript is both stronger and more accessible, and
-hope that it will please the Editors and Reviewers alike.
-
-Thank you again for your consideration of our revised manuscript.
+Thank you for accepting our manuscript ``\mytitle'', as well as for giving us
+the opportunity to address a final round of comments from the reviewers. We
+have followed their suggestions and are proud to submit our revision.
+Thank you for contributing your time and effort as editor.
 
@@
 
-  The Associate Editor stated that both Referees found our study ``very
-  interesting'', but echoed and added to their concerns. In particular, the
-  Associate Editor requested a demonstration that our results are not
-  ``artefacts of differences in sampling effort between studies''. To address
-  this, we have taken the Associate Editor's advice and performed the extra
-  analyses suggested by Referee 1 (described in detail below). We have also
-  taken the Associate Editor's specific comments to heart and address each one
-  in turn. We hope that our replies (preceded by \textbf{R:} 
-  will assuage the Associate Editor's concerns and are 
-  confident that our manuscript is strengthened as a result.
+  We thank the Associate Editor for his kind words and congratulations, as
+  well as for the care and attention shown to our manuscript during the review
+  process. We have followed the latest suggestions by the reviewers and are
+  happy to acknowledge the Associate Editor and Reviewers' 
+  contributions in the manuscript.
 
-  1) Title doesn't reflect our trends in freshwater communities.
+{\Large \bf Reply to Reviewer 1}
 
-  \begin{refquote}
+  We thank the Reviewer for their positive comments and have formally
+  acknowledged their contributions in the manuscript. We are pleased that our
+  jack-knife analysis has satisfied their concerns about variability between
+  studies and appreciate the suggestion that we look into Riede et. al.'s 2011
+  results. Although their results for lakes and streams are very interesting
+  in the context of our study, our manuscript is already rather lengthy for
+  \myjournal. As such, we have included only a very brief reference to Riede
+  et. al.'s work. We hope that this will be enough to encourage future
+  research exploring the links between specialisation, predator-prey biomass
+  ratios, and latitude.
 
-    Title: the current title seems to suggest that this scaling with latitude
-    did never happen, while it was present in freshwater food webs.
+{\Large \bf Reply to Reviewer 2}
 
-  \end{refquote}
-
-  \textbf{R:} We had originally intended to emphasise that, contrary to our expectations,
-  scaling relationships did not vary over latitude in~\emph{most} ecosystems. We have now amended our
-  title to ``\mytitle'' in order to better capture the scaling that did occur in streams.
-
-  2) L29, L42: suggest the likely directions of effects.
-
-  \begin{refquote}
-
-    L29. To help the reader, please be explicit about the direction of these ‘direct relationships’.
-
-    \smallskip
-
-    L42. Can you make a directional prediction on how latitude is expected to
-    affect the scaling? Otherwise, the study becomes rather exploratory
-    presenting some phenomenological patterns not grounded in theory that need
-    ad hoc explanations in the discussion. Similarly, can you provide a priori
-    motivations why the relationship may differ among ecosystem types?
-
-  \end{refquote}
-
-  \textbf{R:} The goal of our study was to give support to
-  one of two contrasting hypotheses (narrower niches in the
-  tropics~\cite{Vazquez2004} versus broader niche space in 
-  the tropics~\cite{Davies2007}). Given the limited support
-  available for either hypothesis, we had no~\emph{a priori}
-  expectation that one was more likely than the other-- that
-  is, it was plausible that scaling of specialisation with
-  species richness might be stronger towards the poles or 
-  that scaling would be unaffected by latitude. We have 
-  added to the introduction at lines 22-27 to make these two
-  potential relationships clearer and at lines 37-42 to more
-  explicitly frame our study as a test of these two versions 
-  of the latitude-niche breadth hypothesis. We have also 
-  followed Reviewer 2's suggestion and now provide a 
-  conceptual figure (Fig. 1) that clearly places our study
-  within this context. We also now provide an explanation 
-  for why we included ecosystem type as a covariate at lines
-  42-44.
+  We are pleased that our revised and extended Discussion has met with the Reviewer's approval and appreciate his further minor comments.
+We have followed all of the Reviewer's suggestions and acknowledge his contributions in the manuscript.
+With regard to the slight contradiction in the discussion, we have taken care to soften our statements on page 10 to make it clear that there is no latitudinal gradient in our dataset without implying that there is no latitudinal gradient in the true species richness of these ecosystems.
+We hope that this will remove the apparent contradiction in our discussion.
 
   \begin{quotation} 
-
-    If the latitude-niche breadth hypothesis is correct, 
-    there should also be direct relationships between 
-    latitude and the degree of specialisation (i.e., the 
-    breadth of the Eltonian 
-    niche;~\cite{Elton1927,Leibold2010}) of species within
-    food webs. Specifically, narrower niches in the tropics 
-    would equate to greater specialisation (narrower niches) 
-    while constant niche sizes but greater productivity 
-    would translate to constant specialisation and niche 
-    width across latitude (Fig. 1).
-
-    \smallskip
-
-    If the scaling of specialisation with species richness 
-    is weaker in the  tropics (i.e., if species gain fewer
-    links, predators, or prey as the size  of the network
-    increases), this will indicate narrower niches at the 
-    tropics.  If, however, the scaling of specialisation 
-    with species richness does not vary over latitude, this 
-    will indicate that niches are similarly-sized worldwide 
-    but that there is a broader niche space in the tropics. 
-    Additionally, as food webs describing different 
-    ecosystem types may differ in their 
-    topology~\cite{Dunne2004,Shurin2006}, we also explored 
-    the differences in scaling relationships across 
-    ecosystem types.
-
+  In either case, the lack of a strong association
+  between observed species richness and latitude in any ecosystem type in our dataset
+  means that any effect of latitude on other scaling relationships is not being driven by
+  the scaling of specialisation with species richness in our food webs.
   \end{quotation}
 
-  3) L98-99: explain our model-selection procedure in more detail.
-
-  \begin{refquote}
-
-    L98-99. According to some experts (e.g. the landmark 2002 book by Burnham
-    and Anderson) when models differ less than 2 units in AIC, they have the
-    same support and fit. On what theoretical grounds do you motivate the
-    choice to select the model with the lowest AIC as the best-fit model when
-    models have $\Delta$AIC\textless2? To what extent does this choice affect your
-    conclusions?
-
-  \end{refquote}
-
-  \textbf{R:} We are also aware of the general consensus    that models where
-  $\Delta$AIC\textless2 are roughly equally well-supported. This is why our
-  procedure (as stated in lines 83-86) was to first consider the set of models
-  where $\Delta$AIC\textless2 and select the model with the fewest degrees of
-  freedom. We chose the smallest model where $\Delta$AIC\textless2 in order to
-  avoid over-fitting the models.
-
-  We only used AIC as a deciding factor where
-  there were several models that shared the minimal degrees 
-  of freedom and all had $\Delta$AIC\textless2. In fact, 
-  this scenario did not occur for the models presented in 
-  the previous draft (it does occur when the 
-  by-trophic-level models use counts of species rather than
-  proportions, an analysis which we had explored in an 
-  earlier draft). To avoid confusion we have therefore 
-  removed the description of this step of our analysis from 
-  the main text.
-
-  \begin{quotation}
-
-    Simplified models were obtained by systematically 
-    removing all possible combinations of terms from the 
-    full model. The best-fitting model was then determined 
-    to be the model with the fewest terms where 
-    $\Delta$AIC\textless2, as this model is the least likely 
-    to suffer from over-fitting.
-
-  \end{quotation}
-
-  4) Move by-trophic-level analyses to appendix and/or better-explain our motivations.
-
-  \begin{refquote}
-
-    L100-106. After reading the introduction, it is not clear why you ‘were
-    also interested’ in this topic. I suggest following the advice of reviewer
-    2 and moving this part and the associated results to the appendix. Please
-    also then explain why this is a priori interesting and relevant to
-    investigate in the context of your study.
-
-  \end{refquote}
-
-  \textbf{R:} After carefully considering the Associate 
-  Editor and Reviewer's comments, we have opted to remove
-  the by-trophic-level analyses entirely. Due to length
-  restrictions, we were not able to both expand our 
-  description of the motivations for and implications of
-  these analyses and accommodate the other changes suggested
-  by the Associate Editor and Reviewers. We chose to focus
-  on ensuring that the discussion of the species-richness
-  results is as clear and complete as possible, and believe
-  that our manuscript is stronger and more to-the-point
-  after these changes.
-
-  5) L113: is there any covariance in the network properties?
-
-  \begin{refquote}
-
-    L113. To what extent do the property estimates covary with each other?
-    This may be presented in an appendix.
-
-  \end{refquote}
-
-  \textbf{R:} As the Associate Editor likely suspected, the 
-  property estimates are all strongly positively correlated. 
-  As generality and vulnerability describe the two 
-  components (number of prey and number of predators,
-  respectively) of links per species, this is to be 
-  expected. We have added a brief description of these 
-  correlations to the main text (lines 122-125) as we 
-  believe it will provide some context for the very similar 
-  results for link density and vulnerability.
-
-  \begin{quotation}
-
-    Link density, generality, and vulnerability were strongly and positively
-    correlated ($R^2$=0.891 for link density and generality,
-    $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.890
-    for generality and vulnerability).
-
-  \end{quotation}
-
-  6) L116: missing supporting statistics
-
-  \begin{refquote}
-
-    L116. It seems the stats to support this statement are missing.
-
-  \end{refquote}
-
-  \textbf{R:} We have amended the text (lines 135-138) to support our statement.
-
-  \begin{quotation}
-    In stream food
-    webs, generality increased more rapidly towards the poles
-    ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
-    vulnerability did not vary with latitude (i.e., the interaction term $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
-  \end{quotation}
-
-  7) L187-198: provide citations for an absence of prey-switching in communities other than streams.
-
-  \begin{refquote}
-
-    L187-198. For your explanation why the scaling relationship changes with
-    latitude in lake and stream food webs and not in the other ecosystem types
-    to be convincing it is not enough to cite studies that high-latitude
-    aquatic species tend to switch between different seasonally available
-    prey, you also need to provide evidence from the literature that this is
-    not the case in the other ecosystem types.
-
-  \end{refquote}
-
-  \textbf{R:} Following Reviewer 1's suggestion, we have 
-    restructured our discussion
-    to focus more on seasonality in different ecosystem types than on prey-switching.
-    As we are not aware of any studies explicitly comparing the frequencies of 
-    prey-switching in different ecosystem types, and do not feel qualified to conduct
-    such a review ourselves, we hope that this revised discussion will be satisfactory.
-
-  8) Ensure layout (especially citations) matches journal specifications.
-
-  \begin{refquote}
-
-    Please strictly follow the author guidelines with regard to layout (for
-    example how to cite studies in the text).
-
-  \end{refquote}
-
-  \textbf{R:} We have changed all references to the Vancouver style and have 
-    added sections for author contributions, conflicts of interest, and funding.
-
-  \newpage
-
-% -----------------------------------------------------------------------------
-% -----------------------------------------------------------------------------
-{\Large \bf Reply to Reviewer 1}
-% ---------------------------------------
-
-  The Reviewer was very positive about our manuscript, calling it
-  ``an interesting paper that takes advantage of recent compilations
-  of food webs to test basic theory with respect to latitudinal gradients in
-  niche breadth'', ``exceptionally well written and presented'', ``sophisticated
-  and well thought out''. We thank the Reviewer for their kind words,
-  and also for their suggestions for further improving our manuscript. We
-  have addressed each comment below (in italics), and are confident that our
-  responses (preceded by a \textbf{R}) have further improved the manuscript.
-
-% ---------------------------------------
-  \emph{
-  1) Some trends may be due to differences in sampling effort, especially
-  due to differences between Thompson \& Townsend stream food webs and other
-  stream webs.}
-
-  \begin{refquote}
-
-    My concern here is how much of the pattern can be attributed to true
-    ecological effects – as opposed to the consequences of differences in the
-    effort used to describe different food webs... It could be explored to some extent by
-    analysing for an effect of particular authors (e.g. the Thompson and
-    Townsend food webs which dominate the stream dataset) but ultimately there
-    is every chance that the results here are artefacts of differences in
-    sampling effort between studies. Might it be possible to randomise the
-    datasets, excluding particular food webs (or authors) to determine
-    robustness to this effect??
-
-  \end{refquote}
-
-  \textbf{R:} We share the reviewer's concern that variation in sampling
-  effort could be driving the trends we observe, as it is highly likely that
-  the authors of all 196 webs in our dataset did not follow the same procedures.
-  Following the reviewer's suggestion, we have performed a jackknife analysis by
-  systematically removing each web in turn and then repeating our analysis. We
-  also performed a similar process removing each set of 
-  food webs compiled by a common author (or set of authors
-  where all authors worked on identical sets of food webs).
-  We are happy to report that removing
-  any single web had no significant effect on any model, 
-  nor did removing any set of webs compiled by a common 
-  author. 
-  We have added a description of these methods and summary
-  of their results to the supporting information 
-  (~\emph{Appendix S3}), and we thank the reviewer for 
-  suggesting this validation of our overall results. We 
-  have also added a brief note in the main text to direct 
-  other readers with similar concerns to the supporting 
-  information (lines 111-120).
-
-  We removed webs compiled by Thompson and by 
-  Townsend separately as each author compiled one food
-  web that the other did not. However, as 26/28 of the
-  food webs compiled by Thompson~\emph{or} Townsend were
-  compiled by both together, the results of both jackknife
-  iterations were very similar (as seen in authors 7 and 6, 
-  respectively, in~\emph{Figs. S4-S6, Appendix S3}). 
-  We are particularly reassured by~\emph{Fig. S5}, where
-  the removal of large subsets of the stream food webs
-  had very little impact on the coefficient representing
-  the effect of latitude on the scaling of generality with
-  species richness in streams.
-
-  \begin{quotation}
-
-    As a supplemental check to ensure that variation in sampling effort across
-    food webs was not responsible for the trends we observed, we then repeated
-    our analyses using jackknifed data sets in which we 1) sequentially removed
-    each food web in the dataset and 2) sequentially removed sets of food webs 
-    associated with each author of the food webs in the dataset. Parameter 
-    estimates varied very little across either series of jackknifes (\emph{Appendix S3}).
-
-  \end{quotation}
-
-   2) Emphasise our results for streams, include the possibility that they
-   may be due to greater seasonality in stream food webs.
-
-  \begin{refquote}
-
-    It is particularly interesting in that stream systems (as opposed to
-    estuarine, marine or terrestrial food webs) are more likely to be affected
-    by seasonal variability – and this is the mechanism evoked as underpinning
-    the latitudinal gradient. I am surprised that the authors didn’t make more
-    of this point – to some degree the difference in habitats supports their
-    proposed mechanism, and this could be discussed.
-
-  \end{refquote}
-
-  \textbf{R:} We thank the Reviewer for this suggestion, 
-  and have substantially revised our discussion (lines 
-  182-217) to follow it. The Reviewer will note that our 
-  arguments include lakes as well as streams since both 
-  systems showed effects of latitude on scaling, and both 
-  experience severe seasonal variability as the Reviewer
-  points out for streams. We have also added a brief note 
-  to address the potential that the New Zealand stream food 
-  webs mentioned by the Reviewer above might be affecting 
-  our results. As described below, they are grouped in a 
-  narrow band of latitude; this likely explains their 
-  minimal impact on the trends we observe. We think that 
-  our discussion is much stronger after these changes.
-
-  \begin{quotation}
-
-    That freshwater food webs supported the hypothesis of 
-    narrower niches in the tropics --while other ecosystem 
-    types did not-- is noteworthy given that these
-    ecosystems (especially streams) are known for being 
-    highly variable and that seasonal variability is one of 
-    the proposed drivers of the latitude-niche breadth 
-    hypothesis~\cite{Vazquez2004}. Both streams and lakes
-    can experience severe changes in water temperature and 
-    volume (e.g., floods, drying, freezing) that remove 
-    food or other resources (notably oxygen during
-    freezing events)~\cite{Winterbourn1997,Meding2001}. 
-    These events are often linked to seasonal events such 
-    as snowmelts or summer drought~\cite{Winterbourn1997}). 
-    Further, both temperate streams and lakes tend to 
-    experience seasonal strong pulses of allochthonous 
-    inputs (e.g., fallen leaves, terrestrial
-    invertebrates~\cite{Nakano2001,Lennon2004,Zeng2008}. 
-    These trends combined mean that, relative to estuarine 
-    and marine communities, freshwater food webs may 
-    experience high turnover in both community composition 
-    and productivity~\cite{Tilzer1988,Magalhaes1993,Baird1989}. Notable exceptions from the above
-    trends are New Zealand stream communities (representing 
-    31 of the 71 stream food webs in our dataset), which 
-    experience unpredictable flooding and drying throughout 
-    the year and do not receive seasonally pulsed
-    subsidies~\cite{Winterbourn1997,Winterbourn1981}. 
-    However, as this subset of webs is very tightly grouped 
-    in latitude ($44.64-46.41^{\circ}$S, within an
-    overall range of $23-69.02^{\circ}$ for stream 
-    communities), it is unlikely that they have greatly
-    influenced our results (see also \emph{Appendix S3}). 
-    Moreover, just as in highly-variable communities where 
-    said variation is more seasonal, New Zealand 
-    communities are dominated by ecological
-    generalists~\cite{Winterbourn1997,Winterbourn1981} 
-    implying that they appear to fit the general pattern of 
-    streams worldwide.
-
-    Importantly, while terrestrial communities are also 
-    strongly seasonal at high latitudes and can receive 
-    significant allochthonous inputs~\cite{Nakano2001}, 
-    terrestrial consumers tend to be morphologically 
-    specialised for feeding on particular 
-    prey~\cite{Liem1990}. This means that primarily 
-    gape-limited aquatic consumers tend to be more
-    generalist across all types of aquatic habitats than 
-    terrestrial consumers~\cite{Liem1990,Shurin2006}. The
-    key to this explanation of the differences between 
-    freshwater and marine and estuarine  ecosystems is 
-    whether the former experience more severe seasonal 
-    variation. Although we are not aware of any study 
-    explicitly comparing seasonal variation in freshwater 
-    and saltwater or brackish food webs in a similar 
-    location, we believe that freshwater ecosystems are 
-    indeed likely to  experience more severe changes 
-    because of their small size. While oceans and estuaries 
-    certainly vary in terms of water temperature and
-    nutrients over the course of a year~\cite{Baird1989}, 
-    these changes are likely to be slower and milder than 
-    in freshwaters because marine and estuarine communities 
-    are buffered by being open to the ocean rather than 
-    isolated in the midst of a terrestrial matrix. Net 
-    primary productivity in particular is much more 
-    variable over the course of a year in non-marine 
-    communities~\cite{Field1998}, suggesting that niche 
-    breadths may also be more variable over the course of 
-    the year.
-
-  \end{quotation}
-
-  \newpage
-
-% -----------------------------------------------------------------------------
-% -----------------------------------------------------------------------------
-{\Large \bf Reply to Reviewer 2}
-% ---------------------------------------
-
-  The Reviewer stated that our study is interesting and covers ``a timely and
-  important topic. The core analysis of the paper (scaling relationships of
-  food web metrics with species richness) are convincingly presented and
-  comprehensively discussed.'' Nevertheless, the Reviewer has suggested several
-  ways in which our manuscript could be improved. We have responded to each suggestion
-  in turn, and believe that our replies (preceded by \textbf{R}) have further improved
-  the manuscript.
-
-% ---------------------------------------
-
-  1) Network terminology and methods might be inaccessible to researchers
-  without network background.
-
-  \begin{refquote}
-
-    the accessibility to readers outside the food-web community could be
-    improved by a more detailed explanation of the methods, especially the
-    applied network metrics and underlying scaling relationships; a conceptual
-    figure visualising the expected relationships for different communities
-    according to the latitude-niche breadth hypothesis could be very helpful
-    here
-
-    \smallskip
-
-     For readers outside the field, please explain in more detail the
-     difference between `original species' and `trophic species' in food webs.
-
-  \end{refquote}
-
-  \textbf{R:} We thank the reviewer for their concern that our manuscript
-  should be accessible to as wide a variety of researchers as possible, and
-  have followed the reviewer's suggestions in several places in the manuscript.
-  We now include a conceptual figure to clearly and succinctly link the changes
-  to scaling relationships we expected to these two versions of the latitude-niche
-  breadth hypothesis (Fig. 1).
-
-  We have explained ``trophic species webs" more thoroughly
-  in lines 58-60 and added parenthetical definitions of
-  trophic-species and original webs in lines 62-64. We have also added parenthetical definitions
-  of link density, generality, and vulnerability at the beginning of the results section
-  to remind readers of the biological meaning of these measures.
-
-  \begin{quotation}
-
-    Many analyses of food-web structure attempt to reduce 
-    this variation by using food webs comprised of ``trophic
-    species'' --aggregations of species with identical sets 
-    of predators and prey-- rather than species 
-    \emph{per se}~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}.
-
-    \smallskip
-
-    We therefore analysed both original (i.e., without 
-    aggregating any species) and trophic-species (i.e., 
-    after aggregating species with identical predators and 
-    prey) versions of the dataset ...
-
-    \smallskip
-
-    Link density (mean number of feeding links per 
-    species), generality (mean number of prey per species), 
-    and vulnerability (mean number of predators per 
-    species) were strongly and positively correlated ...
-
-  \end{quotation}
-
-  2) Reconsider by-trophic-level analysis.
-
-  \begin{refquote}
-
-    the additional analyses of scaling relationships by trophic levels and
-    latitude-species richness relationships are not well introduced. If the
-    analysis on scaling relationships by trophic levels was maintained, then
-    it should already be mentioned in the Introduction (including specific
-    expectations for this analysis) and would require a more comprehensive
-    discussion.
-
-    \smallskip
-
-    The abstract is incomplete. Results of the analysis on the scaling
-    relationships by trophic levels are missing.
-
-    \smallskip
-
-    Please justify why you use the proportion of species within a trophic
-    level and not the absolute number of species per trophic level; at a first
-    glance, this would be more intuitive for me given the focus of the study
-    on scaling relationships with species richness.
-
-  \end{refquote}
-
-  \textbf{R:} We appreciate the Reviewer's concerns about 
-  the integration of these results into the main text. Due 
-  to length restrictions, we were unable to explain our 
-  motivations and discuss our results more fully in the main
-  text. Moreover,
-  referring briefly to by-trophic-level results in the supplemental
-  information repeated the problems with lack of justification and
-  poor integration of the by-trophic-level results with the 
-  species-richness results. To that end we have opted to remove
-  these results entirely. Instead, we have prioritised enriching
-  our discussion of the species-richness results, clarifying our
-  methods, and including the latitudinal gradient in species-richness
-  as requested below. We hope that, on balance, this restructuring has
-  resulted in a clearer and more well-integrated manuscript.
-
-  3) Move description of the species-richness gradient to methods and results.
-
-  \begin{refquote}
-
-     Analyses of species richness along latitude should already be mentioned
-     and described in the Methods and should be referred to in the Results
-     section instead of the Discussion.
-
-     \smallskip
-
-      The start of the Discussion confused me since it presents another
-      additional analysis. This analysis on the latitudinal gradient in
-      species richness is interesting and important for the interpretation of
-      the patterns, but should already be presented in Methods and Results
-      section.
-
-  \end{refquote}
-
-  \textbf{R:} Given the lack of significant relationships,
-  we had originally viewed this analysis as a very minor 
-  part of our paper, but are happy to follow the Reviewer's 
-  suggestion and integrate it in the methods and
-  results along with our main analyses. We now describe 
-  the methods for this analysis in lines 74-86 and 
-  summarise our results in lines 125-128.
-
-  \begin{quotation}
-
-    \textbf{Gradients over Latitude}
-
-    To put our dataset in the context of other research on latitudinal gradients in species richness,
-    we first examined simple linear relationships between latitude and each of 
-    species richness, links per species, generality, vulnerability, and proportions
-    of basal resources, intermediate consumers, and top predators. We fit models of the form
-
-    \begin{equation}
-    \label{Latfull}
-    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
-    \end{equation}
-
-    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
-    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
-    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
-    marine, lake, and terrestrial networks with estuarine
-    networks corresponding to $E_{i}=0$) and $\epsilon_{i}$ is a residual error term. 
-    We next calculated the AIC
-    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
-    using the R~\cite{R} function dredge from package MuMIn~\cite{MuMIn}. 
-    Simplified models were obtained by
-    systematically removing all possible combinations of terms from the full model.
-    The best-fitting model was then determined to be the model with the fewest terms 
-    where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
-
-    \smallskip
-
-    Contrary to the expected latitudinal gradient, the 
-    best-fit version of equation (1) did not include a 
-    significant effect of latitude for any ecosystem type. 
-    Further, there were no significant relationships 
-    between link density, generality, or vulnerability with
-    latitude for any ecosystem type.
-
-  \end{quotation}
-
-  4) Explain habitat categories.
-
-  \begin{refquote}
-
-    Please describe in more detail why you used the chosen habitat categories
-    and provide the number of webs per habitat type also in the main
-    manuscript.
-
-  \end{refquote}
-
-  \textbf{R:} We followed the habitat categories given by the publications which
-  aggregated the food webs. Although more detailed descriptions were also provided, 
-  we opted to use the set of five more general habitat types in order to have a 
-  greater number of food webs in each category.
-
-  We have added a brief explanation, and the number of webs in each ecosystem type, at lines 52-55:
-
-  \begin{quotation}
-    We grouped food web by ecosystem type (stream, N=71; lake, N=47; marine, N=28; estuarine, N=18;
-    and terrestrial, N=31) according to their designation in previous aggregations of food webs 
-    (i.e.,~\citet{GlobalWeb,Riede2011,Dunne2013}).
-
-  \end{quotation}
-
-  5) The y-axis of Fig. 1 is unclear, top predators are unlabelled.
-
-  \begin{refquote}
-
-    Please re-label the y-axis on Fig. 1 to improve clarity. The top predators
-    are missing in this figure although they are mentioned in the legend.
-
-  \end{refquote}
-
-  \textbf{R:} We thank the reviewer for pointing this out 
-  and, while the inclusion of top predators specifically
-  is moot since these results have been moved to the 
-  supplemental information, have taken care that all labels
-  are included in all figures. We have also re-labelled the
-  y-axes on Fig. 2 (the old Fig. 1) to improve clarity.
-
-  6) Add generality, vulnerability to Fig. 2 in main text.
-
-  \begin{refquote}
-
-    I would suggest adding generality and vulnerability to Fig. 2 in the main
-    manuscript (instead of showing them in Fig. S2 only).
-
-  \end{refquote}
-
-  \textbf{R:} We have followed the reviewer's suggestion.
-
-  \newpage
-
-\bibliographystyle{prsb} 
-\bibliography{abbreviated}
-
 \end{document}

### 2015-10-09 manuscript/latitudepaper.tex
working on the talk, up to the results more or less

@@
     The version of the dataset used did not qualitatively change the results, suggesting that
-    the scaling relationships between species richness, other food-web properties, and latitude are very 
+    the scaling relationships between species richness and specialisation across ecosystem type and latitude are very 
     similar whether or not species with identical sets of predators and prey are included. For simplicity, 
-    here we present only the results for the original (un-aggregated, original species) webs.
+    here we present only the results for the original webs.
 
@@
     we first examined simple linear relationships between latitude and each of 
-    species richness, links per species, generality, vulnerability, and proportions
-    of basal resources, intermediate consumers, and top predators. We fit models of the form
+    species richness, links per species, generality, and vulnerability. We fit models of the form
 
@@
   equation~(\ref{Latfull}) did not include a significant
-  effect of latitude for any ecosystem type. Further, there were no significant
+  effect of latitude on species richness for any ecosystem type. Further, there were no significant
   relationships between link density, generality, or vulnerability with
@@
   gradient in richness. In either case, the lack of a strong association
-  between species richness and latitude in any ecosystem type means that any
-  effect of latitude on other scaling relationships is not being driven by an
-  underlying latitudinal gradient in species richness. This is fortunate since
+  between observed species richness and latitude in any ecosystem type in our dataset
+  means that any effect of latitude on other scaling relationships is not being driven by
+  the scaling of specialisation with species richness in our food webs. This is fortunate since
   the lack of confounding effects of latitude allows us to more clearly assess
@@
   This means that primarily gape-limited aquatic consumers tend to be more
-  generalist across all types of aquatic habitats than terrestrial consumers~\cite{Liem1990,Shurin2006}. The
-  key to this explanation of the differences between freshwater and
-  marine and estuarine  ecosystems is whether the former experience more
-  severe seasonal variation. Although we are not aware of any study explicitly
-  comparing seasonal variation in freshwater and saltwater or brackish food
-  webs in a similar location, we believe that freshwater ecosystems are indeed
-  likely to  experience more severe changes because of their small size. While
-  oceans and estuaries certainly vary in terms of water temperature and
+  generalist across all types of aquatic habitats than terrestrial 
+  consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data (
+  $\mu_{Aquatic}$=5.47, $\mu_{Terrestrial}$=3.82; $p$=0.007 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$). 
+  The key to this argument is therefore whether freshwater ecosystems experience
+  more severe seasonal variation than marine and estuarine ecosystems. Although
+  we are not aware of any study explicitly comparing seasonal variation in
+  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
+  ecosystems are indeed likely to experience more severe changes because of their small size.
+  While oceans and estuaries certainly vary in terms of water temperature and
   nutrients over the course of a year~\cite{Baird1989}, these changes are likely to be slower
   and milder than in freshwaters because marine and estuarine communities are buffered 
-  by being open to the ocean rather than isolated
-  in the midst of a terrestrial matrix. Net primary productivity in particular is
-  much more variable over the course of a year in non-marine communities~\cite{Field1998},
-  suggesting that niche breadths may also be more variable over the course of the year.
+  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
+  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
+  in non-marine communities~\cite{Field1998}. Thus suggests that niche breadths may also be 
+  more variable over the course of the year.
 
@@
   webs in different habitat types and that freshwater food webs in particular
-  may be strongly affected by seasonal variation. In addition, different
+  may be strongly affected by seasonal variation. Freshwater food webs also
+  appear to have different predator-prey biomass ratios than other ecosystem
+  types~\cite{Riede2011}; although it is not clear whether these ratios are related
+  to seasonality, this could be a promising avenue for future research. In addition, different
   relationships between latitude and niche breadth in different habitat types
-  goes some way towards explaining the equivocal support for the opposing
+  go some way towards explaining the equivocal support for the opposing
   hypotheses of narrower niches in the tropics~\cite{Vazquez2004} and broader
@@
   We thank members of the Romanuk, Stouffer, and Tylianakis labs for their comments on
-  the manuscript. We also thank Angus McIntosh for valuable discussion on stream food webs.
+  the manuscript. We also thank Angus McIntosh for valuable discussion on stream food webs and Matthias Schleuning, Robby Stoks, and one anonymous reviewer for their insightful questions.
 

### 2015-10-09 talk/ABC_2015.tex
working on the talk, up to the results more or less

@@
 \usepackage{multirow}
+\usepackage{pgf}
+\usepackage{tikz}
 
@@
 
-    \textbf{Alyssa R. Cirtwill}, Daniel B. Stouffer, Tamara N. Romanuk
+    \textbf{Alyssa R. Cirtwill},\\ Daniel B. Stouffer \& Tamara N. Romanuk
 
@@
 
-      \vspace{1cm}
+      \vspace{.5cm}
+
+      {\color{white}{\Large Latitude-Niche Breadth Hypothesis}}
+
+      \vspace{.5cm}
 
@@
       \vspace{1cm}
-      {\color{white} 23 October 2015 | ABC 2015}
+
     \end{center}
@@
 
-      \vspace{1cm}
+      \vspace{.5cm}
 
-      \textbf{Envionmental stability?} 
-      \textbf{Productivity?} 
+      {\Large Latitude-Niche Breadth Hypothesis}
+
+      \vspace{.5cm}
+
+      {\color{purple}Envionmental stability? Productivity?}
       Speciation rates?
@@
       \vspace{1cm}
-      {\color{white} 23 October 2015 | ABC 2015}
 
@@
 
-    \footnotesize{Vazquez, D.P. \& Stevens, R.D. 2004. The latitudinal gradient in niche breadth: concepts and evidence. \emph{The American Naturalist} \textbf{164}, E1-19.}
+    \vspace{1.5cm}
+
+    \tiny{Vazquez, D.P. \& Stevens, R.D. 2004. The latitudinal gradient in niche breadth: concepts and evidence. \emph{Am. Nat.}}
   \end{frame}
@@
 
-    \tiny{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology} \textbf{88}, 1940-1947.}
+    \vspace{1.5cm}
+
+    \tiny{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology.}}
   \end{frame}
@@
 \section*{Food Webs}
-  \begin{frame}{Testing The Hypotheses}
-
-    \begin{center}
-      \includegraphics[width=.8\textwidth]{Figures/hypothesis_comparison.eps}
-
-    \end{center}
-
+  \begin{frame}{Does niche breadth vary with latitude?}
     \begin{columns}
@@
     \column{1.75in}
-      - Greater specialisation in the tropics
+      \begin{center}
+      \includegraphics[height=1in]{Figures/version1.eps}\\
+      \vspace{.5cm}
+      Greater specialisation\\in the tropics
+
+      \vspace{.25cm}
+      {\color{white}Fewer links per species\\in the tropics}
+
+      \end{center}
     \column{.5in}
     \column{1.75in}
-      - Similar specialisation at all latitudes
+      \begin{center}
+      \includegraphics[height=1in]{Figures/version1.eps}\\
+      \vspace{.5cm}
+      Similar specialisation\\at all latitudes
+
+      \vspace{.25cm}
+      {\color{white}Equal links per species\\at all latitudes}
+
+      \end{center}
     \column{.5in}
@@
 
-  \begin{frame}{Testing The Hypotheses}
-
-    \begin{center}
-      \includegraphics[width=.8\textwidth]{Figures/hypothesis_comparison.eps}
-
-    \end{center}
-
+  \begin{frame}{Does niche breadth vary with latitude?}
     \begin{columns}
@@
     \column{1.75in}
-      - More feeding links per species in tropics
+      \begin{center}
+      \includegraphics[height=1in]{Figures/version1.eps}\\
+      \vspace{.5cm}
+      Greater specialisation\\in the tropics
+
+      \vspace{.25cm}
+      Fewer links per species\\in the tropics
+
+      \end{center}
     \column{.5in}
     \column{1.75in}
-      - Similar feeding links per species at all latitudes
+      \begin{center}
+      \includegraphics[height=1in]{Figures/version1.eps}\\
+      \vspace{.5cm}
+      Similar specialisation\\at all latitudes
+
+      \vspace{.25cm}
+      Equal links per species\\at all latitudes
+
+      \end{center}
     \column{.5in}
@@
 
-  \begin{frame}{Testing The Hypotheses}
+  \begin{frame}{Does niche breadth vary with latitude?}
 
@@
     195 food webs \\
-    0-78 degrees (absolute latitude) \\
+    0-78$^\circ$ (absolute latitude) \\
     Mean L/S, Generality, Vulnerability
@@
     195 food webs \\
-    0-78 degrees (absolute latitude) \\
+    0-78$^\circ$ (absolute latitude) \\
     Mean \textbf{L/S}, Generality, Vulnerability
@@
 
+\section*{Scaling}
+  \begin{frame}{Does niche breadth vary with latitude?}
+
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/ls_vs_lat_simulated.eps}
+    \end{center}
+
+  \end{frame}
+
+  \begin{frame}{Niche breadth varies with species richness}
+
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
+
+    \vspace{.5cm}
+    {\color{white}... and species richness varies with latitude}
+    \end{center}
+
+  \end{frame}
+
+  \begin{frame}{Niche breadth varies with species richness}
+
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
+
+      \vspace{.5cm}
+    ... and species richness varies with latitude
+    \end{center}
+
+  \end{frame}
+
+  \begin{frame}{Does latitude affect LS vs. S?}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
+
+      \vspace{.5cm}
+    \end{center}
+    \hspace{1in}
+      $B \approx aS^{\color{purple}b}$
+
+  \end{frame}
+
+  \begin{frame}{Does latitude affect LS vs. S?}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
+
+      \vspace{.5cm}
+    \end{center}
+    \hspace{1in}
+      $B \approx aS^{\color{purple}b_0+b_1Latitude}$
+
+  \end{frame}
+
+  \begin{frame}{Does latitude affect LS vs. S?}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
+
+      \vspace{.5cm}
+    \end{center}
+    \hspace{1in}
+      $B \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$
+
+  \end{frame}
+
+\section*{Results}
+  \begin{frame}{Does latitude affect LS vs. S?}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/marginals.eps}
+
+      I want: just LS, maybe 2 columns?
+      Maybe focus on Gen instead of LS? Easier to argue?
+
+    \end{center}
+
+  \end{frame}
+
 \end{document}

### 2015-10-09 talk/ABC_2015.tex
Now talk is done through results. Need to punch up the figures though.

@@
       \vspace{.25cm}
-      {\color{white}Fewer links per species\\in the tropics}
+      {\color{white}Fewer prey per species\\in the tropics}
 
@@
       \vspace{.25cm}
-      {\color{white}Equal links per species\\at all latitudes}
+      {\color{white}Equal prey per species\\at all latitudes}
 
@@
       \vspace{.25cm}
-      Fewer links per species\\in the tropics
+      Fewer prey per species\\in the tropics
 
@@
       \vspace{.25cm}
-      Equal links per species\\at all latitudes
+      Equal prey per species\\at all latitudes
 
@@
     0-78$^\circ$ (absolute latitude) \\
-    Mean L/S, Generality, Vulnerability
+    {\color{white} Mean generality (\textbf{G})}
 
@@
     0-78$^\circ$ (absolute latitude) \\
-    Mean \textbf{L/S}, Generality, Vulnerability
+    Mean generality (\textbf{G})
 
@@
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/ls_vs_lat_simulated.eps}
-    \end{center}
-
-  \end{frame}
-
-  \begin{frame}{Niche breadth varies with species richness}
-
-    \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
+      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_lat_simulated.eps}
 
@@
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
+      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}
+
+    \vspace{.5cm}
+    {\color{white}... and species richness varies with latitude}
+    \end{center}
+
+  \end{frame}
+
+  \begin{frame}{Niche breadth varies with species richness}
+
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}
 
@@
 
-  \begin{frame}{Does latitude affect LS vs. S?}
+  \begin{frame}{Does latitude affect G vs. S?}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}
+
+      \vspace{.5cm}
+    \end{center}
+    \hspace{1in}
+      $G \approx aS^{\color{purple}b}$
+
+  \end{frame}
+
+  \begin{frame}{Does latitude affect G vs. S?}
     \begin{center}
@@
     \hspace{1in}
-      $B \approx aS^{\color{purple}b}$
+      $G \approx aS^{\color{purple}b_0+b_1Latitude}$
 
@@
 
-  \begin{frame}{Does latitude affect LS vs. S?}
+  \begin{frame}{Does latitude affect G vs. S?}
     \begin{center}
@@
     \hspace{1in}
-      $B \approx aS^{\color{purple}b_0+b_1Latitude}$
-
-  \end{frame}
-
-  \begin{frame}{Does latitude affect LS vs. S?}
-    \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
-
-      \vspace{.5cm}
-    \end{center}
-    \hspace{1in}
-      $B \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$
+      $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$
 
@@
 \section*{Results}
-  \begin{frame}{Does latitude affect LS vs. S?}
+  \begin{frame}{Does latitude affect G vs. S?}
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/marginals.eps}
-
-      I want: just LS, maybe 2 columns?
-      Maybe focus on Gen instead of LS? Easier to argue?
+      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal_axis.eps}
 
     \end{center}
-
   \end{frame}
 
+  \begin{frame}{Does latitude affect G vs. S?}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal_one.eps}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Does latitude affect G vs. S?}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal.eps}
+
+    \end{center}
+  \end{frame}
+
+\section*{Discussion}
+
 \end{document}

### 2015-10-10 code/talk_plots.py
Splitting the effect plot

@@ -348,7 +348,6 @@ def marginal_plotter(prop,TL,ecotype,graph):
 
   return graph
 
-
 def dummy_marginal_plotter(plottype,ecotypes,prop):
   grace=MultiPanelGrace(colors=ColorBrewerScheme('Greys'))
 
@@ -456,6 +455,58 @@ def main():
  
   for plottype in ['axis','one']:
     dummy_marginal_plotter(plottype,ecotypes,'Gen')
+
+  prop="Gen" # Split the plot
+
+  Ngrace=MultiPanelGrace(colors=ColorBrewerScheme('Greys'))
+
+  Nnames=['Estuarine','Marine','Terrestrial']
+
+  Ngrace.add_label_scheme('dummy',Nnames)
+  Ngrace.set_label_scheme('dummy')
+  
+  for ecotype in ecotypes[:3]:   
+
+    graph=Ngrace.add_graph(Panel)
+
+    marginal_plotter(prop,TL,ecotype,graph)
+    graph.panel_label.configure(char_size=.75,placement='iul',dy=.02,dx=.03)
+
+  Ngrace.multi(rows=1,cols=3,vgap=.04,hgap=.04)
+
+  Ngrace.hide_redundant_xticklabels()
+  Ngrace.hide_redundant_yticklabels()
+
+  Ngrace.set_col_yaxislabel(col=0,rowspan=(0,0),label='Marginal effect of latitude on scaling',place='normal',just=2,char_size=1,perpendicular_offset=0.07)
+  Ngrace.set_row_xaxislabel(row=0,colspan=(0,2),label='Absolute label',,place='normal',just=2,char_size=1,perpendicular_offset=0.07)
+
+  Ngrace.write_file('../talk/Figures/results/no_effect.eps')
+
+
+  Egrace=MultiPanelGrace(colors=ColorBrewerScheme('Greys'))
+
+  Nnames=['Lake','Stream']
+
+  Egrace.add_label_scheme('dummy',Nnames)
+  Egrace.set_label_scheme('dummy')
+  
+  for ecotype in ecotypes[3:]:   
+
+    graph=Egrace.add_graph(Panel)
+
+    marginal_plotter(prop,TL,ecotype,graph)
+    graph.panel_label.configure(char_size=.75,placement='iul',dy=.02,dx=.03)
+
+  Egrace.multi(rows=1,cols=2,vgap=.04,hgap=.04)
+
+  Egrace.hide_redundant_xticklabels()
[…]

### 2015-10-11 code/talk_plots.py
geasfd

@@ -202,7 +202,6 @@ def S_rawplots(rawdatafile,outfile1,predfolder):
   TL='S'
   prop='Gen'
   outfile=outfile1+prop+'_vs_S_fitline_observed.eps'  
-  print outfile
 
   rawdata=datareader(rawdatafile,TL)
 
@@ -212,7 +211,7 @@ def S_rawplots(rawdatafile,outfile1,predfolder):
 
   obspoints=graph.add_dataset(rawdata[prop])
   obspoints.line.configure(linestyle=0)
-  obspoints.symbol.configure(size=.5,shape=1,fill_color=0,fill_pattern=1,color=8)
+  obspoints.symbol.configure(size=.75,shape=1,fill_color=3,fill_pattern=1,color=8)
 
   predictions=predictionlines(fixed,prop,TL)
   predline=graph.add_dataset(predictions)

### 2015-10-11 talk/ABC_2015.tex
?

@@
 
+  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/no_effect.eps}
+
+      \vspace{1cm}
+      {\color{white} No effect of latitude on scaling\\
+      Similar niche widths at all latitude\\
+      Supports Davies \emph{et. al.}, 2007:\\
+      Broader niche space in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/no_effect.eps}
+
+      \vspace{1cm}
+      No effect of latitude on scaling\\
+      {\color{white}Similar niche widths at all latitude\\
+      Supports Davies \emph{et. al.}, 2007:\\
+      Broader niche space in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/no_effect.eps}
+
+      \vspace{1cm}
+      No effect of latitude on scaling\\
+      Similar niche widths at all latitude\\
+      {\color{white} Supports Davies \emph{et. al.}, 2007:\\
+      Broader niche space in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/no_effect.eps}
+
+      \vspace{1cm}
+      No effect of latitude on scaling\\
+      Similar niche widths at all latitude\\
+      Supports Davies \emph{et. al.}, 2007:\\
+      Broader niche space in the tropics
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Lake \& Stream Food Webs}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/effect.eps}
+
+      \vspace{1cm}
+      {\color{white} Scaling increases with latitude\\
+      Narrower niches in the tropics\\
+      Supports Vazquez \& Stevens 2004\\}
+      {\color{white} narrower niches in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Lake \& Stream Food Webs}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/effect.eps}
+
+      \vspace{1cm}
+      Scaling increases with latitude\\
+      {\color{white} Narrower niches in the tropics\\
+      Supports Vazquez \& Stevens 2004\\}
+      {\color{white} narrower niches in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Lake \& Stream Food Webs}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/effect.eps}
+
+      \vspace{1cm}
+      Scaling increases with latitude\\
+      Narrower niches in the tropics\\
+      {\color{white} Supports Vazquez \& Stevens 2004\\}
+      {\color{white} narrower niches in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Lake \& Stream Food Webs}
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/results/effect.eps}
+
+      \vspace{1cm}
+      Scaling increases with latitude\\
+      Narrower niches in the tropics\\
+      Supports Vazquez \& Stevens 2004\\
+      {\color{white} narrower niches in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{What's different in freshwaters?}
+    Seasonality?\\
+    NZ streams are weird but probably don't affect much\\
+    Gape limitation?\\
+  \end{frame}
+
 \end{document}

### 2015-10-11 talk/ABC_2015.tex
Punched up all the figures

--- 2015-10-09 talk/ABC_2015.tex
@@
       \begin{center}
-      \includegraphics[height=1in]{Figures/version1.eps}\\
+      \includegraphics[height=1in]{Figures/version2.eps}\\
       \vspace{.5cm}
@@
       \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_lat_simulated.eps}
-
-    \vspace{.5cm}
-    {\color{white}... and species richness varies with latitude}
     \end{center}
@@
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}
+      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_dots_vs_S_fitline_observed.eps}
 
-    \vspace{.5cm}
-    {\color{white}... and species richness varies with latitude}
+    \vspace{.3cm}
     \end{center}
-
+      \hspace{.74cm}
+      {\Large      
+      $G \approx aS^{\color{purple}b}$}
   \end{frame}
 
-  \begin{frame}{Niche breadth varies with species richness}
+  \begin{frame}{Does latitude affect scaling?}
 
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}
+      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_dots_vs_S_fitline_observed.eps}
 
-      \vspace{.5cm}
-    ... and species richness varies with latitude
+      \vspace{.3cm}
     \end{center}
-
+      \hspace{.74cm}
+      {\Large
+      $G \approx aS^{\color{purple}b_0+b_1Latitude}$}
   \end{frame}
 
-  \begin{frame}{Does latitude affect G vs. S?}
+  \begin{frame}{Does latitude affect scaling?}
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_fitline_observed.eps}
+      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_dots_vs_S_fitline_observed.eps}
 
-      \vspace{.5cm}
+      \vspace{.3cm}
     \end{center}
-    \hspace{1in}
-      $G \approx aS^{\color{purple}b}$
-
-  \end{frame}
-
-  \begin{frame}{Does latitude affect G vs. S?}
-    \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
-
-      \vspace{.5cm}
-    \end{center}
-    \hspace{1in}
-      $G \approx aS^{\color{purple}b_0+b_1Latitude}$
-
-  \end{frame}
-
-  \begin{frame}{Does latitude affect G vs. S?}
-    \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/LS_vs_S_fitline_observed.eps}
-
-      \vspace{.5cm}
-    \end{center}
-    \hspace{1in}
-      $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$
+      \hspace{.74cm}
+      {\Large
+      $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$}
 
@@
 \section*{Results}
-  \begin{frame}{Does latitude affect G vs. S?}
+  \begin{frame}{Does latitude affect scaling?}
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal_axis.eps}
+      \includegraphics*[width=.9\textwidth]{Figures/results/Gen_vs_S_marginal_axis.eps}
+
+      \vspace{.8cm}
+      ${\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$
 
@@
 
-  \begin{frame}{Does latitude affect G vs. S?}
+  \begin{frame}{Does latitude affect scaling?}
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal_one.eps}
+      \includegraphics*[width=.9\textwidth]{Figures/results/Gen_vs_S_marginal_one.eps}
+
+      \vspace{.8cm}
+      ${\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$
 
@@
 
-  \begin{frame}{Does latitude affect G vs. S?}
+  \begin{frame}{Does latitude affect scaling?}
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/results/Gen_vs_S_marginal.eps}
+      \includegraphics*[width=.9\textwidth]{Figures/results/Gen_vs_S_marginal.eps}
+
+      \vspace{.8cm}
+      ${\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$
 
@@
 
+  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
+    \begin{center}
+      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}
+
+      \vspace{1cm}
+      {\color{white} No effect of latitude on scaling\\
+      Similar niche widths at all latitude\\
+      \vspace{.54cm}        
+      Supports Davies \emph{et. al.}, 2007:\\
+      Broader niche space in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
+    \begin{center}
+      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}
+
+      \vspace{1cm}
+      No effect of latitude on scaling\\
+      {\color{white}Similar niche widths at all latitude\\
+      \vspace{.54cm}      
+      Supports Davies \emph{et. al.}, 2007:\\
+      Broader niche space in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
+    \begin{center}
+      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}
+
+      \vspace{1cm}
+      No effect of latitude on scaling\\
+      Similar niche widths at all latitude\\
+      \vspace{.54cm}
+      {\color{white} Supports Davies \emph{et. al.}, 2007:\\
+      Broader niche space in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
+    \begin{center}
+      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}
+
+      \vspace{1cm}
+      No effect of latitude on scaling\\
+      Similar niche widths at all latitude\\
+      \vspace{.54cm}      
+      Supports Davies \emph{et. al.}, 2007:\\
+      Broader niche space in the tropics
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Lake \& Stream Food Webs}
+    \begin{center}
+      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}
+
+      \vspace{1cm}
+      {\color{white} Scaling increases with latitude\\
+      Narrower niches in the tropics\\
+      \vspace{.54cm}      
+      Supports Vazquez \& Stevens 2004\\}
+      {\color{white} narrower niches in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Lake \& Stream Food Webs}
+    \begin{center}
+      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}
+
+      \vspace{1cm}
+      Scaling increases with latitude\\
+      {\color{white} Narrower niches in the tropics\\
+      \vspace{.54cm}      
+      Supports Vazquez \& Stevens 2004\\}
+      {\color{white} narrower niches in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Lake \& Stream Food Webs}
+    \begin{center}
+      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}
+
+      \vspace{1cm}
+      Scaling increases with latitude\\
+      Narrower niches in the tropics\\
+      \vspace{.54cm}     
+      {\color{white} Supports Vazquez \& Stevens 2004\\}
+      {\color{white} narrower niches in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Lake \& Stream Food Webs}
+    \begin{center}
+      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}
+
+      \vspace{1cm}
+      Scaling increases with latitude\\
+      Narrower niches in the tropics\\
+      \vspace{.54cm}
+      Supports Vazquez \& Stevens 2004\\
+      {\color{white} narrower niches in the tropics}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{What's different in freshwaters?}
+    Seasonality?\\
+    NZ streams are weird but probably don't affect much\\
+    Gape limitation?\\
+  \end{frame}
+
 \end{document}

### 2015-10-11 code/talk_plots.py

@@ -193,39 +193,43 @@ def predictionlines(fixed,prop,TL):
 
   return ecoline
 
-def S_rawplots(rawdatafile,outfile1,predfolder):
+def S_rawplots(rawdatafile,outfile1,predfolder,plottype):
 
   # Lets make clear that these are the original, uncorrected points
 
-  grace=Grace(colors=ColorBrewerScheme("Greys"))
+  grace=Grace(colors=ColorBrewerScheme("PRGn"))
 
   TL='S'
   prop='Gen'
-  outfile=outfile1+prop+'_vs_S_fitline_observed.eps'  
+  outfile=outfile1+prop+'_'+plottype+'_vs_S_fitline_observed.eps'  
 
   rawdata=datareader(rawdatafile,TL)
 
   fixed=fixed_reader('../non_TS/coefficients/'+prop+'_obs.tsv')
 
   graph=grace.add_graph()
-
-  obspoints=graph.add_dataset(rawdata[prop])
+  print plottype
+  if plottype=='dots':
+    obspoints=graph.add_dataset(rawdata[prop])
+  else:
+    obspoints=graph.add_dataset([])
+    graph.add_drawing_object(DrawText,text='Latitude effect on slope?',char_size=1,loc=(0,0),loctype='view')
   obspoints.line.configure(linestyle=0)
-  obspoints.symbol.configure(size=.75,shape=1,fill_color=3,fill_pattern=1,color=8)
+  obspoints.symbol.configure(size=.75,shape=1,fill_color=0,fill_pattern=1,color=2,linewidth=3)
 
   predictions=predictionlines(fixed,prop,TL)
   predline=graph.add_dataset(predictions)
   predline.symbol.shape=0
 
-  predline.line.configure(linestyle=1,color=1,linewidth=2.5)
+  predline.line.configure(linestyle=1,color=3,linewidth=5)
 
   ytex='Species richness'
-  graph.xaxis.label.configure(text=ytex,place='normal',char_size=1)
+  graph.xaxis.label.configure(text=ytex,place='normal',char_size=1.5)
 
   if prop=='LS':
-    graph.yaxis.label.configure(text="Link density",place='normal',char_size=1)
+    graph.yaxis.label.configure(text="Link density",place='normal',char_size=1.5)
   elif prop=='Gen':
[…]

### 2015-10-12 talk/ABC_2015.tex
A few small touches
Ok, just need discussion
we need to fix the ratio on the summer plot

@@
 
-% %%Start Introduction Slides%%
 \section*{Background}
@@
 
+      {\color{white}23 October 2015 | ABC 2015}
+
     \end{center}
@@
       \vspace{1cm}
+
+      {\color{white}23 October 2015 | ABC 2015}
 
@@
     \vspace{.3cm}
+      {\Large      
+      $G \approx aS^b$}
     \end{center}
-      \hspace{.74cm}
-      {\Large      
-      $G \approx aS^{\color{purple}b}$}
+  \end{frame}
+
+ \begin{frame}{Does niche breadth vary with latitude?}
+
+    \begin{center}
+
+      Want to show a dummy negative Gen vs. Lat due to S
+
+    \end{center}
+
   \end{frame}
@@
     \begin{center}
-      \includegraphics*[width=.9\textwidth]{Figures/results/effect_mod.eps}
+      \includegraphics*[width=.75\textwidth]{Figures/results/effect.eps}
 
@@
       Supports Vazquez \& Stevens 2004\\}
-      {\color{white} narrower niches in the tropics}
+      {\color{white} Narrower niches in the tropics}
 
@@
 
+\section*{Freshwaters}
+
   \begin{frame}{What's different in freshwaters?}
-    Seasonality?\\
-    NZ streams are weird but probably don't affect much\\
-    Gape limitation?\\
+    \begin{block}{They're highly seasonal}
+
+      \begin{columns}
+        \column{.5in}
+        \column{2in}
+
+        \begin{center}
+
+        \includegraphics[width=.8\columnwidth]{Figures/spring_stream.eps}
+
+        \vspace{.5cm}
+
+        \includegraphics[width=.8\columnwidth]{Figures/fall_stream.eps}
+
+        \end{center}
+
+        \column{2in}
+
+        \begin{center}
+
+        \includegraphics[width=.8\columnwidth]{Figures/summer_stream.eps}
+
+        \vspace{.5cm}
+
+        \includegraphics[width=.8\columnwidth]{Figures/winter_stream.eps}
+
+        \end{center}
+
+        \column{.5in}
+
+      \end{columns}
+    \end{block}
+  \end{frame}
+
+  \begin{frame}{What's different in freshwaters?}
+    \begin{block}{They're highly seasonal - except in NZ}
+      [same pics]
+    \end{block}
+  \end{frame}
+
+  % Heading off the "but so are terrestrial" issue
+  \begin{frame}{What's different in freshwaters?}
+    \begin{block}{They're aquatic}
+
+      [picture of a fish vs. a land beast]
+      [gape limitation]
+
+    \end{block}
+  \end{frame}
+
+\section*{Conclusion and Acknowledgements}
+  \begin{frame}{So why are there more species in the tropics?}
+    \begin{block}{Estuarine, marine, \& terrestrial}
+      \begin{itemize}
+        \item Broader niche space in the tropics
+        \item Similar specialisation everywhere
+      \end{itemize}
+    \end{block}
+
+    \begin{block}{Lakes \& Streams}
+      \begin{itemize}
+        \item Narrower niches in the tropics
+        \item Generality due to seasonality?
+      \end{itemize}
+    \end{block}
+  \end{frame}
+
+  \begin{frame}{Acknowledgements}
+    \begin{columns}
+      \column{.25in}
+
+      \column{1.5in}
+      \centering
+
+      Daniel B. Stouffer\\
+      \& his lab
+
+      \column{1.5in}
+      \centering
+
+      Tamara N. Romanuk\\
+      \& her lab
+
+      \column{1.5in}
+      \centering
+
+      Angus McIntosh\\
+      Matthias Schleuning
+
+      \column{.25in}
+    \end{columns}
+    \begin{columns}
+     \column{2.5in}
+       \centering
+
+      \vspace{.25cm}
+
+       \includegraphics[width=0.6\columnwidth]{marsden-logo-cmyk-tif.eps}
+
+      \vspace{.25cm}
+
+      \includegraphics[width=0.7\columnwidth]{Dal_logo.eps}
+
+     \column{2.5in}
+       \centering
+
+      \vspace{.25cm}
+
+       \includegraphics[width=0.7\columnwidth]{NSERC_C.eps}
+
+       \vspace{.25cm}
+
+       \includegraphics[width=0.4\columnwidth]{logo-canterbury-color.eps}
+
+       \vspace{.5in}
+
+    \end{columns}
+  \end{frame}
+
+  \begin{frame}{Latitude affects scaling - sometimes}
+
+  [Show the 5-panel plot, the equation.]
+
   \end{frame}

### 2015-10-12 talk/ABC_2015.tex
Ok this will do for the test talk

@@
     \begin{center}
+      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_vs_lat_negative.eps}
 
-      Want to show a dummy negative Gen vs. Lat due to S
-
+    \vspace{.3cm}
+      {\color{white}{\Large      
+      $G \approx aS^b$}}
     \end{center}
 
+  \end{frame}
+
+  \begin{frame}{Does latitude affect scaling?}
+
+    \begin{center}
+      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_dots_vs_S_fitline_observed.eps}
+
+    \vspace{.3cm}
+      {\Large      
+      $G \approx aS^b$}
+    \end{center}
   \end{frame}
@@
         \column{.5in}
-        \column{2in}
+        \column{1.9in}
 
-        \begin{center}
+        \hfill \includegraphics[width=.8\columnwidth]{Figures/spring_stream.eps}
 
-        \includegraphics[width=.8\columnwidth]{Figures/spring_stream.eps}
+        \vspace{.2in}
 
-        \vspace{.5cm}
+        \hfill \includegraphics[width=.8\columnwidth]{Figures/fall_stream.eps}
 
-        \includegraphics[width=.8\columnwidth]{Figures/fall_stream.eps}
+        \column{.2in}
 
-        \end{center}
-
-        \column{2in}
-
-        \begin{center}
+        \column{1.9in}
 
@@
 
-        \vspace{.5cm}
+        \vspace{.2in}
 
         \includegraphics[width=.8\columnwidth]{Figures/winter_stream.eps}
-
-        \end{center}
 
@@
     \end{block}
+
+    \vfill
+
   \end{frame}
@@
     \begin{block}{They're highly seasonal - except in NZ}
-      [same pics]
+
+      \begin{center}
+
+        \includegraphics[width=3in]{Figures/sawcut.eps}
+
+      \end{center}
     \end{block}
@@
 
-  % Heading off the "but so are terrestrial" issue
   \begin{frame}{What's different in freshwaters?}
-    \begin{block}{They're aquatic}
+    \begin{block}{They're dominated by fish}
 
-      [picture of a fish vs. a land beast]
-      [gape limitation]
+      \begin{columns}
+      \column{.5in}
+      \column{1.9in}
+        \hfill
+        \includegraphics[width=.8\columnwidth]{Figures/anteater.eps}
+      \column{.2in}
+      \column{1.9in}
+        \includegraphics[width=.8\columnwidth]{Figures/trout.eps}
+      \column{.5in}
+      \end{columns}
+    \end{block}
 
-    \end{block}
+    \vfill
+
   \end{frame}
@@
   \begin{frame}{So why are there more species in the tropics?}
+    \begin{columns}
+    \column{.5in}
+    \column{2.5in}
       \begin{block}{Estuarine, marine, \& terrestrial}
         \begin{itemize}
-        \item Broader niche space in the tropics
-        \item Similar specialisation everywhere
+          \item Broader niche space\\ in the tropics
+          \item Similar specialisation\\ everywhere
         \end{itemize}
@@
 
+    \vspace{.5cm}
+
     \begin{block}{Lakes \& Streams}
       \begin{itemize}
-        \item Narrower niches in the tropics
+        \item Narrower niches\\ in the tropics
         \item Generality due to seasonality?
@@
     \end{block}
+
+      \column{1.5in}
+        \centering
+        \includegraphics[height=.75in]{Figures/version2.eps}
+
+    \vspace{1cm}
+
+        \includegraphics[height=.75in]{Figures/version1.eps}
+    \column{.5in}
+    \end{columns}
+
   \end{frame}
@@
     \end{columns}
+
+    \vspace{.5cm}
+
     \begin{columns}
-     \column{2.5in}
+    \column{.25in}
+     \column{2.25in}
        \centering
 
-      \vspace{.25cm}
+      \includegraphics[height=.75in]{marsden-logo-cmyk-tif.eps}
 
-       \includegraphics[width=0.6\columnwidth]{marsden-logo-cmyk-tif.eps}
+      \vspace{.5cm}
+      \vspace{.125in}
 
-      \vspace{.25cm}
+      \includegraphics[height=.5in]{Dal_logo.eps}
 
-      \includegraphics[width=0.7\columnwidth]{Dal_logo.eps}
+      \vspace{.125in}
 
-     \column{2.5in}
+     \column{2.25in}
        \centering
 
-      \vspace{.25cm}
+       \includegraphics[height=.75in]{NSERC_C.eps}
 
-       \includegraphics[width=0.7\columnwidth]{NSERC_C.eps}
+       \vspace{.5cm}
 
-       \vspace{.25cm}
+       \includegraphics[height=.75in]{logo-canterbury-color.eps}
 
-       \includegraphics[width=0.4\columnwidth]{logo-canterbury-color.eps}
-
-       \vspace{.5in}
-
+    \column{.25in}
     \end{columns}
@@
 
-  \begin{frame}{Latitude affects scaling - sometimes}
+  \begin{frame}{Latitude affects scaling in freshwaters}
 
-  [Show the 5-panel plot, the equation.]
+    \begin{columns}
+    \column{.5in}
+    \column{2.75in}
+      \begin{center}
+      \includegraphics[height=.8in]{Figures/results/no_effect.eps}
+      \end{center}
+
+    \column{.25in}
+    \column{1in}
+      \begin{center}
+
+        \includegraphics[height=.65in]{Figures/version2.eps}
+        \vspace{.3in}
+
+      \end{center}
+
+    \column{.5in}
+    \end{columns}
+
+    \begin{columns}
+    \column{.5in}
+    \column{2.75in}
+      \begin{center}
+
+      \includegraphics[height=.8in]{Figures/results/effect.eps}
+      \end{center}
+
+    \column{.25in}
+    \column{1in}
+      \begin{center}
+
+        \includegraphics[height=.65in]{Figures/version1.eps}
+        \vspace{.3in}
+
+      \end{center}
+
+    \column{.5in}
+    \end{columns}
+
+    \vspace{.1in}
+
+    \begin{center}
+
+    {\Large $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$}
+
+    \end{center}
 

### 2015-10-15 code/talk_plots.py
embiggened the legend

@@ -201,9 +201,9 @@ def Gen_vs_lat_sim(prop):
 
   graph=grace.add_graph()
 
-  narrowniches=graph.add_dataset([(0,50),(90,2)])
-  narrowniches.symbol.shape=0
-  narrowniches.line.configure(color=2,linewidth=5)
+  # narrowniches=graph.add_dataset([(0,50),(90,2)])
+  # narrowniches.symbol.shape=0
+  # narrowniches.line.configure(color=2,linewidth=5)
 
   ytex='Absolute latitude'
   graph.xaxis.label.configure(text=ytex,place='normal',char_size=1.5)
@@ -213,10 +213,20 @@ def Gen_vs_lat_sim(prop):
   elif prop=='Gen':
     graph.yaxis.label.configure(text="Generality",place='normal',char_size=1.5)
 
-  graph.add_drawing_object(DrawText,text='?',x=45,y=2,just=2,loctype='world',char_size=6,color=11)
+  graph.add_drawing_object(DrawText,text='?',x=25,y=8,just=2,loctype='world',char_size=6,color=11)
+  graph.add_drawing_object(DrawText,text='?',x=65,y=.5,just=2,loctype='world',char_size=6,color=2)
 
+  narrowniches=graph.add_dataset([(100,1),(100,100)])
+  narrowniches.symbol.shape=0
+  narrowniches.line.configure(color=2,linewidth=5)
+  narrowniches.legend="Narrower niches in the tropics"
 
-  graph.legend.configure(char_size=.75,frame=0,loc=(5,.3),loctype='world',box_linestyle=0)
+  sameniches=graph.add_dataset([(100,2),(190,3)])
+  sameniches.symbol.shape=0
+  sameniches.line.configure(color=11,linewidth=5)
+  sameniches.legend="Similar niches everywhere"
+
+  graph.legend.configure(char_size=1.25,frame=0,loc=(5,.4),loctype='world',box_linestyle=0)
 
   graph.world.ymin=.1
   graph.world.ymax=100
@@ -322,7 +332,7 @@ def S_rawplots(rawdatafile,outfile1,predfolder,plottype):
   elif prop=='Gen':
     graph.yaxis.label.configure(text="Generality",place='normal',char_size=1.5)
 
-  graph.legend.configure(char_size=.75,frame=0,loc=(5,.3),loctype='world',box_linestyle=0)
[…]

### 2015-10-16 talk/ABC_2015.tex
revamped talk following confab with DBS

@@
 
-  \begin{frame}{Why are there more species in the tropics?}
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
 
@@
 
-    \textbf{Alyssa R. Cirtwill},\\ Daniel B. Stouffer \& Tamara N. Romanuk
+    \textbf{Alyssa R. Cirtwill}\\ Daniel B. Stouffer \& Tamara N. Romanuk
 
@@
 
-      {\color{white}{\Large Latitude-Niche Breadth Hypothesis}}
-
+      Many groups are more diverse in the tropics\\
       \vspace{.5cm}
-
-      Envionmental stability? 
-      Productivity? 
-      Speciation rates?
+      {\color{white} Environmental stability? Productivity?\\}
 
@@
 
-      {\Large Latitude-Niche Breadth Hypothesis}
-
+      Many groups are more diverse in the tropics\\
       \vspace{.5cm}
-
-      {\color{purple}Envionmental stability? Productivity?}
-      Speciation rates?
+      {\color{white}{Ey}}How?{\color{white}{Ey}}\\
 
@@
 
-  \begin{frame}{Latitude-Niche Breadth Hypothesis}
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
 
+    \begin{center}
+      \includegraphics*[width=.8\textwidth]{Figures/plant_richness.eps}
+
+      \vspace{.5cm}
+
+      Many groups are more diverse in the tropics\\
+      \vspace{.5cm}
+      Environmental stability? Productivity?\\
+
+      \vspace{1cm}
+
+      {\color{white}23 October 2015 | ABC 2015}
+
+    \end{center}
+  \end{frame}
+
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
+
+    \begin{block}{Latitude-niche breadth version 1}
     \begin{center}
@@
 
-    \vspace{1.5cm}
+    \vspace{1cm}
 
     \tiny{Vazquez, D.P. \& Stevens, R.D. 2004. The latitudinal gradient in niche breadth: concepts and evidence. \emph{Am. Nat.}}
+    \end{block}
   \end{frame}
 
-  \begin{frame}{Latitude-Niche Breadth Hypothesis}
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
 
+    \begin{block}{Latitude-niche breadth version 1}
     \begin{center}
@@
 
-    \vspace{1.5cm}
+    \vspace{1cm}
 
     \tiny{Vazquez, D.P. \& Stevens, R.D. 2004. The latitudinal gradient in niche breadth: concepts and evidence. \emph{Am. Nat.}}
+    \end{block}
   \end{frame}
 
-  \begin{frame}{Alternatively ...}
-
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
+    \begin{block}{Latitude-niche breadth version 2}
     \begin{center}
@@
 
-    \vspace{1.5cm}
+    \vspace{1cm}
 
     \tiny{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology.}}
+    \end{block}
   \end{frame}
 
-  \begin{frame}{Alternatively ...}
-
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
+    \begin{block}{Latitude-niche breadth version 2}
     \begin{center}
@@
 
-    \vspace{1.5cm}
+    \vspace{1cm}
 
     \tiny{Davies \emph{et. al.} 2007. Productivity alters the scale dependence of the diversity-invasibility relationship. \emph{Ecology.}}
+    \end{block}
   \end{frame}
@@
 \section*{Food Webs}
-  \begin{frame}{Does niche breadth vary with latitude?}
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
     \begin{columns}
@@
 
+    \vspace{.5cm}
+
+    \begin{center}
+      \color{white}{Generality : mean number of prey per species}
+    \end{center}
   \end{frame}
 
-  \begin{frame}{Does niche breadth vary with latitude?}
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
     \begin{columns}
@@
 
+    \vspace{.5cm}
+
+    \begin{center}
+      \color{white}{Generality : mean number of prey per species}
+    \end{center}
   \end{frame}
 
-  \begin{frame}{Does niche breadth vary with latitude?}
+  \begin{frame}{Testing the latitude-niche breadth hypothesis}
+    \begin{columns}
+    \column{.5in}
+    \column{1.75in}
+      \begin{center}
+      \includegraphics[height=1in]{Figures/version1.eps}\\
+      \vspace{.5cm}
+      Greater specialisation\\in the tropics
+
+      \vspace{.25cm}
+      Lower generality\\in the tropics
+
+      \end{center}
+    \column{.5in}
+    \column{1.75in}
+      \begin{center}
+      \includegraphics[height=1in]{Figures/version2.eps}\\
+      \vspace{.5cm}
+      Similar specialisation\\at all latitudes
+
+      \vspace{.25cm}
+      Equal generality\\at all latitudes
+
+      \end{center}
+    \column{.5in}
+    \end{columns}
+
+    \vspace{.5cm}
 
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/LittleRockLake.eps}
-
-    195 food webs \\
-    0-78$^\circ$ (absolute latitude) \\
-    {\color{white} Mean generality (\textbf{G})}
-
+      \color{DarkGreen}{Generality : mean number of prey per species}
     \end{center}
@@
 
+    \begin{block}{Dataset}
     \begin{center}
-      \includegraphics*[width=.8\textwidth]{Figures/LittleRockLake.eps}
+      \includegraphics*[width=.75\textwidth]{Figures/LittleRockLake.eps}
 
+      \vspace{.4cm}
     195 food webs \\
-    0-78$^\circ$ (absolute latitude) \\
-    Mean generality (\textbf{G})
+    5-188 species \\
 
     \end{center}
+    \end{block}
+  \end{frame}
+
+  \begin{frame}{Does niche breadth vary with latitude?}
+
+    \begin{block}{Dataset}
+    \begin{center}
+      \includegraphics*[width=.75\textwidth]{Figures/results/latitude_hist.eps}
+
+    \end{center}
+    \end{block}
+
+  \end{frame}
+
+  \begin{frame}{Does niche breadth vary with latitude?}
+
+    \begin{block}{Dataset}
+    \begin{center}
+      \includegraphics*[width=.75\textwidth]{Figures/results/generality_hist.eps}
+
+    \end{center}
+    \end{block}
 
@@
 
-  \begin{frame}{Niche breadth varies with species richness}
+  \begin{frame}{Niche breadth scales with species richness}
 
@@
 
- \begin{frame}{Does niche breadth vary with latitude?}
+  \begin{frame}{Niche breadth scales with species richness}
+
+    \begin{center}
+      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_dots_vs_S_fitline_observed.eps}
+
+    \vspace{.3cm}
+      {\Large      
+      log($G$) $\approx b$  log($a$)  log($S$) }
+    \end{center}
+  \end{frame}
+
+ \begin{frame}{Niche breadth scales with species richness}
 
@@
     \vspace{.3cm}
-      {\color{white}{\Large      
-      $G \approx aS^b$}}
+      {\Large      
+      $G \approx aS^b$ \hspace{.5in} $S \approx Latitude$}
     \end{center}
@@
 
-  \begin{frame}{Does latitude affect scaling?}
+  \begin{frame}{Does latitude affect scaling of niche breadth?}
 
@@
     \vspace{.3cm}
+      {\Large      
+      $G \approx aS^{\color{DeepPurple}b}$}
     \end{center}
-      \hspace{.74cm}
-      {\Large
-      $G \approx aS^{\color{purple}b_0+b_1Latitude}$}
   \end{frame}
 
-  \begin{frame}{Does latitude affect scaling?}
+  \begin{frame}{Does latitude affect scaling of niche breadth?}
     \begin{center}
@@
       \vspace{.3cm}
+      {\Large
+      $G \approx aS^{\color{DeepPurple}b_0+b_1Latitude}$}
     \end{center}
-      \hspace{.74cm}
+  \end{frame}
+
+  \begin{frame}{Does latitude affect scaling of niche breadth?}
+    \begin{center}
+      \includegraphics*[width=.654\textwidth]{Figures/results/Gen_vs_S_expectations.eps}
+
+      \vspace{.3cm}
       {\Large
-      $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$}
-
+      $G \approx aS^{\color{DeepPurple}b_0+b_1Latitude}$}
+    \end{center}
   \end{frame}
@@
 \section*{Results}
-  \begin{frame}{Does latitude affect scaling?}
+  \begin{frame}{Does latitude affect scaling of niche breadth?}
     \begin{center}
@@
 
-      \vspace{.8cm}
-      ${\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$
+      \vspace{.3cm}
+      {\Large
+      $G \approx aS^{\color{DeepPurple}b_0+b_1Latitude}$}
 
@@
 
-      \vspace{1cm}
-      {\color{white} No effect of latitude on scaling\\
-      Similar niche widths at all latitude\\
-      \vspace{.54cm}        
-      Supports Davies \emph{et. al.}, 2007:\\
-      Broader niche space in the tropics}
+    \vspace{.5cm}
+
+    \includegraphics*[width=.75\textwidth]{Figures/results/no_effect_interpretations.eps}
 
@@
 
-      \vspace{1cm}
-      No effect of latitude on scaling\\
-      {\color{white}Similar niche widths at all latitude\\
-      \vspace{.54cm}      
-      Supports Davies \emph{et. al.}, 2007:\\
-      Broader niche space in the tropics}
+    \vspace{1.02cm}
 
-    \end{center}
-  \end{frame}
-
-  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
-    \begin{center}
-      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}
-
-      \vspace{1cm}
-      No effect of latitude on scaling\\
-      Similar niche widths at all latitude\\
-      \vspace{.54cm}
-      {\color{white} Supports Davies \emph{et. al.}, 2007:\\
-      Broader niche space in the tropics}
-
-    \end{center}
-  \end{frame}
-
-  \begin{frame}{Estuarine, Marine, \& Terrestrial Food Webs}
-    \begin{center}
-      \includegraphics*[width=.9\textwidth]{Figures/results/no_effect.eps}
-
-      \vspace{1cm}
-      No effect of latitude on scaling\\
-      Similar niche widths at all latitude\\
-      \vspace{.54cm}      
-      Supports Davies \emph{et. al.}, 2007:\\
-      Broader niche space in the tropics
+    \includegraphics*[width=.4\textwidth]{Figures/version2.eps}
 
@@
 
-      \vspace{1cm}
-      {\color{white} Scaling increases with latitude\\
-      Narrower niches in the tropics\\
-      \vspace{.54cm}      
-      Supports Vazquez \& Stevens 2004\\}
-      {\color{white} Narrower niches in the tropics}
+      \vspace{.5cm}
+
+    \includegraphics*[width=.75\textwidth]{Figures/results/effect_interpretations.eps}
 
@@
 
-      \vspace{1cm}
-      Scaling increases with latitude\\
-      {\color{white} Narrower niches in the tropics\\
-      \vspace{.54cm}      
-      Supports Vazquez \& Stevens 2004\\}
-      {\color{white} narrower niches in the tropics}
+    \vspace{1.02cm}
 
-    \end{center}
-  \end{frame}
-
-  \begin{frame}{Lake \& Stream Food Webs}
-    \begin{center}
-      \includegraphics*[width=.75\textwidth]{Figures/results/effect.eps}
-
-      \vspace{1cm}
-      Scaling increases with latitude\\
-      Narrower niches in the tropics\\
-      \vspace{.54cm}     
-      {\color{white} Supports Vazquez \& Stevens 2004\\}
-      {\color{white} narrower niches in the tropics}
-
-    \end{center}
-  \end{frame}
-
-  \begin{frame}{Lake \& Stream Food Webs}
-    \begin{center}
-      \includegraphics*[width=.75\textwidth]{Figures/results/effect.eps}
-
-      \vspace{1cm}
-      Scaling increases with latitude\\
-      Narrower niches in the tropics\\
-      \vspace{.54cm}
-      Supports Vazquez \& Stevens 2004\\
-      {\color{white} narrower niches in the tropics}
+    \includegraphics*[width=.255\textwidth]{Figures/version1.eps}
 
@@
 
-  \begin{frame}{What's different in freshwaters?}
-    \begin{block}{They're highly seasonal}
+  % \begin{frame}{How do lakes and streams differ}
+  %   \begin{block}{from terrestrial food webs?}
+
+  %     \begin{columns}
+  %       \column{.5in}
+
+  %       \column{1.9in}
+  %         \begin{center}
+  %         \includegraphics[width=.8\textwidth]{Figures/anteater.eps}
+  %         \end{center}
+  %       \column{.2in}
+  %       \column{1.9in}
+  %         \begin{center}
+  %         \includegraphics[width=.8\textwidth]{Figures/trout.eps}
+  %         \end{center}
+  %       \column{.5in}
+  %     \end{columns}
+
+  %       \vspace{.5cm}
+
+  %     \begin{columns}
+  %       \column{.5in}
+
+  %       \column{1.9in}
+
+  %        \begin{center}
+
+  %       Gape-limitation!
+
+  %       \vspace{.25cm}
+
+  %       {\tiny Liem 1990, \emph{Am. Zool}}\\
+  %       {\tiny Shurin \emph{et. al.} 2007, \emph{Ecol. Lett.}}
+  %       \end{center}
+
+  %       \column{.2in}
+
+  %       \column{1.9in}
+
+  %         \begin{center}
+  %         \includegraphics[width=.5\columnwidth]{Figures/version1.eps}
+
+  %         \end{center}
+
+  %       \column{.5in}
+
+  %     \end{columns}
+  %   \end{block}
+  % \end{frame}
+
+  \begin{frame}{How do lakes and streams differ}
+    \begin{block}{from estuarine \& marine food webs?}
 
@@
 
-  \begin{frame}{What's different in freshwaters?}
-    \begin{block}{They're highly seasonal - except in NZ}
+\section*{Conclusion and Acknowledgements}
+  \begin{frame}{Evidence for the latitude-niche breadth hypothesis}
+    \begin{block}{Estuarine, marine, \& terrestrial webs}
+      \begin{columns}
+      \column{2.5in}
+        \begin{itemize}
+          \item Broader niche space\\ in the tropics
+          \item Similar specialisation\\ everywhere
+        \end{itemize}
+      \column{1in}
 
@@
 
-        \includegraphics[width=3in]{Figures/sawcut.eps}
+        \includegraphics[height=.75in]{Figures/version2.eps}
 
         \end{center}
-    \end{block}
-  \end{frame}
 
-  \begin{frame}{What's different in freshwaters?}
-    \begin{block}{They're dominated by fish}
-
-      \begin{columns}
-      \column{.5in}
-      \column{1.9in}
-        \hfill
-        \includegraphics[width=.8\columnwidth]{Figures/anteater.eps}
-      \column{.2in}
-      \column{1.9in}
-        \includegraphics[width=.8\columnwidth]{Figures/trout.eps}
       \column{.5in}
@@
 
-    \vfill
-
-  \end{frame}
-
-\section*{Conclusion and Acknowledgements}
-  \begin{frame}{So why are there more species in the tropics?}
+    \begin{block}{Lake \& stream webs}
       \begin{columns}
-    \column{.5in}
       \column{2.5in}
-      \begin{block}{Estuarine, marine, \& terrestrial}
-        \begin{itemize}
-          \item Broader niche space\\ in the tropics
-          \item Similar specialisation\\ everywhere
-        \end{itemize}
-      \end{block}
-
-    \vspace{.5cm}
-
-    \begin{block}{Lakes \& Streams}
       \begin{itemize}
         \item Narrower niches\\ in the tropics
-        \item Generality due to seasonality?
+        \item Specialisation\\ due to stability?
       \end{itemize}
-    \end{block}
+      \column{1in}
 
-      \column{1.5in}
-        \centering
-        \includegraphics[height=.75in]{Figures/version2.eps}
-
-    \vspace{1cm}
+        \begin{center}
 
         \includegraphics[height=.75in]{Figures/version1.eps}
+
+        \end{center}
+
       \column{.5in}
     \end{columns}
-
+    \end{block}
   \end{frame}
@@
 
-  \begin{frame}{Latitude affects scaling in freshwaters}
+  \begin{frame}{Evidence for the latitude-niche breadth hypothesis}
 
@@
 
-    {\Large $G \approx aS^{\color{purple}b_0+b_1Latitude+b_2Ecotype+b_3Latitude:Ecotype}$}
+    {\Large $G \approx aS^{\color{DeepPurple}b_0+b_1Latitude}$}
 

### 2015-10-16 code/talk_plots.py

@@ -471,6 +471,484 @@ def dummy_marginal_plotter(plottype,ecotypes,prop):
 
   print plottype
 
+def lat_histogram_plot(datafile):
+
+	histlist=[]
+
+	a=1
+	b=1
+	c=1
+	d=1
+	e=1
+	f=1
+	g=1
+	h=1
+	i=1
+	j=1
+	k=1
+	l=1
+	m=1
+	n=1
+	o=1
+	p=1
+
+	q=open(datafile,'r')
+	for line in q:
+		web=line.split('\t')[0]
+		if web!='Web':
+			ecotype=line.split('\t')[1]
+			site=line.split('\t')[2]
+			latitude=float(line.split('\t')[3])
+			species=float(line.split('\t')[4])
+			gen=float(line.split('\t')[9])
+
+			if latitude < 5:
+				histlist.append((1,a))
+				a=a+1
+			elif 5 <= latitude <10:
+				histlist.append((2,b))
+				b=b+1
+			elif 10 <= latitude <15:
+				histlist.append((3,c))
+				c=c+1
+			elif 15 <= latitude <20:
+				histlist.append((4,d))
+				d=d+1
+			elif 20 <= latitude <25:
+				histlist.append((5,e))
+				e=e+1
+			elif 25 <= latitude <30:
+				histlist.append((6,f))
+				f=f+1
+			elif 30 <= latitude <35:
+				histlist.append((7,g))
+				g=g+1
+			elif 35 <= latitude < 40:
+				histlist.append((8,h))
+				h=h+1
+			elif 40 <= latitude <45:
+				histlist.append((9,i))
+				i=i+1
+			elif 45 <= latitude <50:
+				histlist.append((10,j))
+				j=j+1
+			elif 50 <= latitude <55:
+				histlist.append((11,k))
+				k=k+1
+			elif 55 <= latitude <60:
+				histlist.append((12,l))
+				l=l+1
+			elif 60 <= latitude <65:
+				histlist.append((13,m))
+				m=m+1
+			elif 65 <= latitude <70:
+				histlist.append((14,n))
+				n=n+1
+			elif 70 <= latitude <75:
+				histlist.append((15,o))
+				o=o+1
+			elif 75 <= latitude:
+				histlist.append((16,p))
+				p=p+1
+
+	q.close()
+
+	grace=Grace(colors=ColorBrewerScheme('PRGn'))
+	graph=grace.add_graph()
+
+	data=graph.add_dataset(histlist)
+	data.line.linestyle=0
[…]

### 2016-09-29 manuscript/latitudepaper.tex

@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
+\centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
 \caption{In A) we show the known scaling relationship between link density (links per species) and 
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
+\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem

### 2017-09-03 code/Models.R
added the rotated version of WEB294, removed the unrotated version

@@ -1,12 +1,14 @@
 
 ## Power analysis function from http://www.esapubs.org/archive/ecol/E092/160/Sup_2_Guidelines.r
 ## Loading required packages. May need to be installed from CRAN.
-library(nlrwr)
+# library(nlrwr) ## Not available for 3.3.1
 library(lmerTest)
 library(boot)
 library(MuMIn)
 
-for(infile in c('../mod_data/summary-properties.tsv','../non_TS/summary-properties.tsv')){
+# Need to re-run with the corrected matrices...
+# for(infile in c('../mod_data/summary-properties.tsv','../non_TS/summary-properties.tsv')){
+for(infile in c('../mod_data/summary-properties_extended_connected.tsv','../non_TS/summary-properties_extended_connected.tsv')){
 
   data=read.delim(infile,sep='\t',header=TRUE,stringsAsFactors=FALSE)
   data$Connectance=as.numeric(as.character(data$Connectance))
@@ -14,8 +16,8 @@ for(infile in c('../mod_data/summary-properties.tsv','../non_TS/summary-properti
   data$Gen=as.numeric(as.character(data$Gen))
   data$Vul=as.numeric(as.character(data$Vul))
   data$Ecotype=as.factor(data$Ecotype)
-  data$Ecotype2=as.factor(data$Ecotype2)
-  data$Humans=as.factor(data$Humans)
+  # data$Ecotype2=as.factor(data$Ecotype2)
+  # data$Humans=as.factor(data$Humans)
   data$Site=as.factor(data$Site)
   data$Basal=as.numeric(as.character(data$Basal))
   data$Herbivores=as.numeric(as.character(data$Herbivores))

### 2017-09-03 code/byTL_Models.R

@@ -1,102 +1,129 @@
 ## Power analysis function from http://www.esapubs.org/archive/ecol/E092/160/Sup_2_Guidelines.r
-## Loading required packages. May need to be installed from CRAN.
 library(nlrwr)
 library(lmerTest)
 library(MuMIn)
 
-infile='../non_TS/summary-properties.tsv'
+infile='../non_TS/summary-properties.tsv' # Versions of webs with species, not trophic species
 # infile='../mod_data/summary-properties.tsv'
 
-format='proportions'
-# format='numbers' # Don't care about numbers actually
+format='proportions' # e.g. Basal is %Basal rather than # of basal resources
+# format='numbers' # I tried both ways initially.
 
 power_analysis=FALSE
 by_TL=FALSE
 # For proportions and numbers, everything is log-normal.
 
-  data=read.delim(infile,sep='\t',header=TRUE,stringsAsFactors=FALSE)
-  data$Connectance=as.numeric(as.character(data$Connectance))
-  data$LS=as.numeric(as.character(data$LS))
-  data$Gen=as.numeric(as.character(data$Gen))
-  data$Vul=as.numeric(as.character(data$Vul))
-  data$Ecotype=as.factor(data$Ecotype)
-  data$Site=as.factor(data$Site)
-  data$Basal=as.numeric(as.character(data$Basal))
-  data$Herbivores=as.numeric(as.character(data$Herbivores))
-  data$Intermediate=as.numeric(as.character(data$Intermediate))
-  data$Intermediate=data$Intermediate+data$Herbivores   # Role herbivores into intermediates
-  data$Toppreds=as.numeric(as.character(data$Toppreds))
+# Format the data file
+data=read.delim(infile,sep='\t',header=TRUE,stringsAsFactors=FALSE)
+data$Connectance=as.numeric(as.character(data$Connectance))
+data$LS=as.numeric(as.character(data$LS))
+data$Gen=as.numeric(as.character(data$Gen))
+data$Vul=as.numeric(as.character(data$Vul))
+data$Ecotype=as.factor(data$Ecotype)
+data$Site=as.factor(data$Site)
+data$Basal=as.numeric(as.character(data$Basal))
+data$Herbivores=as.numeric(as.character(data$Herbivores))
[…]

### 2017-09-03 code/food_web_properties.py

@@ -98,6 +98,7 @@ def clustering(directory,item):
   Clus=float(sum(ratios)/len(ratios))
   return Clus
 
+ 
 def food_web_properties(directory,item,G):
 
   Clus=clustering(directory,item)
@@ -142,6 +143,32 @@ def food_web_properties(directory,item,G):
   herbs=float(float(len(H))/N)
   basal=float(float(len(B))/N)
 
+  TLdict={} # This isn't working so well...
+  for node in B:
+    TLdict[node]=1
+  for node in G.nodes():
+    if node not in B:
+      paths=[]
+      for res in B:
+        try:
+          short=nx.shortest_path_length(G,source=res,target=node)
+          paths.append(short)
+        except nx.exception.NetworkXNoPath:
+          try:
+            short=nx.shortest_path_length(G,source=node,target=res)
+            paths.append(short)
+          except:
+            pass
+      if len(paths)>0:
+        TLdict[node]=sorted(paths)[0] # The shortest path
+      else:
+        pass # Ignoring unconnected nodes
+  if len(TLdict.values())>0:
+    SWTL=sum(TLdict.values())/len(TLdict.values())
+  else:
+    print B, I, T
+    print item, ' has no connected nodes?'
+
   for node in G.nodes():
     pred=len(G.predecessors(node))
     number_predators.append(pred)
@@ -175,17 +202,17 @@ def food_web_properties(directory,item,G):
   try:
     Path=nx.average_shortest_path_length(G,weight=None) #average shortest path length
   except nx.exception.NetworkXError:
+    paths=[]
     for g in nx.connected_component_subgraphs(G.to_undirected()):
-      paths=[]
       try:
         paths.append(nx.average_shortest_path_length(g,weight=None))
       except:
-        paths.append(0)
+        pass
     print item, 'not connected'
     Path=sum(paths)/len(paths)
 
   stroutput=[]
-  outputs = [int(N),int(sum(LinksperS)),float(C),float(LS),float(LinkSD),float(Gen),float(GenSD),float(Vul),float(VulSD),float(Path),float(Clus),basal,herbs,inter,top] 
+  outputs = [int(N),int(sum(LinksperS)),float(C),float(LS),float(LinkSD),float(Gen),float(GenSD),float(Vul),float(VulSD),float(Path),float(SWTL),float(Clus),basal,herbs,inter,top] 
   for thing in outputs:
[…]

### 2017-09-03 code/listcreator.py

@@ -5,42 +5,53 @@ import random
 from decimal import *
 from math import *
 
+backwards_webs=['../mod_data/webs/WEB294.csv']
+# WEB269, WEB296, WEB320 had commas in the headers. Fixed it.
+# And WEB321. And WEB322. And WEB323. And WEB324. And WEB222.
+
 def create_predprey_list(webfile):
+  # print webfile
   rowdict={}
 
   f=open(webfile,'r')
   for line in f:
-    newline=line.split('\n')[0] #Trims off extraneous newline
-    items=newline.split(',')
-    if '' not in items[1:]:
-      rowdict[items[0]]=items[1:]
+    if webfile!='../mod_data/webs/WEB294_rotated.csv':
+      newline=line.split('\n')[0] #Trims off extraneous newline
+      items=newline.split(',')
+      if '' not in items[1:]:
+        if '0' in items[1:] or '1' in items[1:]:
+          rowdict[items[0]]=items[1:]
+        else:
+          predators=items[1:]
+    else:
+      mush=line.split('\r')
+      for newline in mush:
+        items=newline.split(',')
+        if '' not in items[1:]:
+          if '0' in items[1:] or '1' in items[1:]:
+            rowdict[items[0]]=items[1:]
+          else:
+            predators=items[1:]
   f.close()
-
-  for row in rowdict:
-    for item in rowdict[row]:
-      try:
-        item = int(item)
-      except:
-        predators = row
 
   predpreydict={}
   specieslist=set()
 
   # print webfile
 
-  for item in rowdict[predators]:
-    specieslist.add(item)
+  for pred in predators:
+    specieslist.add(pred)
     preylist=[]
-    position = rowdict[predators].index(item)
-    for row in rowdict:
-      specieslist.add(row)
-      if row != predators:
-        try:
-          if rowdict[row][position]!='0':
-            preylist.append(row)
-        except:
-          print webfile, rowdict[predators][position], 'error'
-    predpreydict[item]=preylist
+    position = predators.index(pred)
+    for prey in rowdict:
+      specieslist.add(prey)
+      try:
+        if rowdict[prey][position]!='0':
+          # print pred, prey
+          preylist.append(prey)
+      except:
+        print webfile, pred, 'error'
+    predpreydict[pred]=preylist
 
   numberdict={}
   i = 1
[…]

### 2017-09-03 manuscript/latitudepaper_submitted.tex
Adding a dummy file to try and make a diff
foundup of edited code files

--- 2015-07-01 manuscript/latitudepaper.tex
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
+\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
+\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
 \caption{Changes to the scaling of link density with species richness across ecosystem
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
+\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
 \caption{Changes to the scaling of link density with the proportions of basal resources, intermediate

### 2018-01-30 manuscript/latitudepaper.tex
added updated results

@@
   latitude for any ecosystem type.
+  [[After correction: $R^2$=0.865 for link density and generality, $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.865 for generality and vulnerability.]]
 
@@
   $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
-  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
+  Fig.~\ref{props_v_lat}). 
+  [[After correction: ($\beta_0$=0.689, $p$\textless0.001; $\beta_0$=0.687, $p$\textless0.001; and $\beta_0$=0.690, $p$\textless0.001, respectively).]]
+  For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
@@
   $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). In
+  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). 
+  [[After correction: $\beta_{Latitude}$=-0.0004, $p$=0.890 for link density; $\beta_{Latitude}$=-0.001, $p$=0.640 for generality; and $\beta_{Latitude}$=-0.0004, $p$=0.889 for vulnerability.]]
+  In
   lake food webs, however, the scaling of each property was stronger towards
@@
   $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
+  [[After correction: Link density scaled less strongly with species richness in stream and terrestrial food webs ($\beta_{Stream}$=-0.099, $p$\textless0.001; $\beta_{Terrestrial}$=-0.116, $p$\textless0.001) but there was no scaling of link density with latitude for any property.
+Scaling of generality with latitude, however, was significantly stronger in lake food webs than other ecosystem types and slightly, but not significantly, stronger in stream food webs ($\beta_{Latitude:Lake}$=0.005, $p$=0.001; $\beta_{Latitude:Stream}$=0.003, $p$=0.117).
+Vulnerability, like link density, did not scale with latitude for any property and scaled more weakly with species richness in stream and terrestrial food webs ($\beta_{Stream}$=-0.099, $p$\textless0.001; $\beta_{Terrestrial}$=-0.116, $p$\textless0.001).]]
+
+  [[Note: The trophic species version of the webs changed less with the correction.
+For link density, $\beta_{Latitude:Lake}$=0.005, $p$=0.002.
+For generality, $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001 and $\beta_{Latitude:Stream}$=0.004, $p$=0.009.
+For vulnerability, $\beta_{Latitude:Lake}$=0.005, $p$=0.002.]]
 

### 2018-04-16 manuscript/latitudepaper.tex
updated nonTS versions. Doesn't look so bad, actually

--- 2016-09-29 manuscript/latitudepaper.tex
@@
 \usepackage{setspace}
+\usepackage{soul}
 
@@
   number of prey per species), and vulnerability (mean number of predators per
-  species) were strongly and positively correlated ($R^2$=0.891 for link
+  species) were strongly and positively correlated ($R^2$=\st{0.891}0.890 for link
   density and generality, $R^2$\textgreater0.999 for link density and
-  vulnerability, and $R^2$=0.890 for generality and vulnerability). Contrary
+  vulnerability, and $R^2$=\st{0.890}0.889 for generality and vulnerability). Contrary
   to the expected latitudinal gradient, the best-fit version of
@@
   latitude for any ecosystem type.
+  % [[After correction: $R^2$=0.890 for link density and generality, $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.889 for generality and vulnerability.]]
+
+  % [[Coefficients are from LS_min, etc. Need to re-run for non_TS and TS webs, update with new minimum models.]]
 
   Each measure of specialisation increased with increasing
-  species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
-  $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
-  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
+  species richness ($\beta_0$=\st{0.637}0.668, $p$\textless0.001; $\beta_0$=\st{0.553}0.689,
+  $p$\textless0.001; and $\beta_0$=\st{0.637}0.668, $p$\textless0.001, respectively;
+  Fig.~\ref{props_v_lat}). 
+  % [[After correction: ($\beta_0$=0.668, $p$\textless0.001; $\beta_0$=0.689, $p$\textless0.001; and $\beta_0$=0.668, $p$\textless0.001, respectively).]]
+  For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
-  ($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S}). In
-  lake food webs, however, the scaling of each property was stronger towards
+  (\st{$\beta_{Latitude}$=-0.001, $p$=0.365 for link density;}
+  $\beta_{Latitude}$=\st{-0.001}-0.002, $p$=\st{0.535}0.101 for generality; 
+  latitude was not retained in the best-fit models for link density or vulnerability \st{and
+  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability}; Fig.~\ref{S}). 
+  % [[After correction: latitude not included in LS_min or Vul_min. $\beta_{Latitude}$=-0.002, $p$=0.101 for generality]]
+  \st{In lake food webs, however, the scaling of each property was stronger towards
   the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
@@
   vulnerability did not vary with latitude (i.e., the interaction term 
-  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
+  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).}
+  In lake and stream food webs, however, the scaling of generality was stronger
+  towards the poles. This change in scaling was significant for streams but not for
+  lakes ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively).
+  % [[After correction: Link density and vulnerability scaled more strongly with species richness in lake food webs ($\beta_{Lake}$=0.057, $p$=0.024 and $\beta_{Lake}$=0.059, $p$=0.020, respectively).
+Generality scaled significantly more strongly towards the poles in streams and slightly (not significantly) more strongly towards the poles in lake food webs ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively).
+]]
+
+  [[[[[Need to double-check and update this. Then adjust discussion as needed.]]]]]
+  [[Note: The trophic species version of the webs changed less with the correction.
+For link density, $\beta_{Latitude:Lake}$=0.005, $p$=0.002.
+For generality, $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001 and $\beta_{Latitude:Stream}$=0.004, $p$=0.009.
+For vulnerability, $\beta_{Latitude:Lake}$=0.005, $p$=0.002.]]
 

### 2018-04-16 code/byTL_Models.R

@@ -3,8 +3,7 @@
 library(lmerTest)
 library(MuMIn)
 
-infile='../non_TS/summary-properties_trimmed.tsv' # Versions of webs with species, not trophic species
-# infile='../mod_data/summary-properties_trimmed.tsv'
+for(infile in c('../mod_data/summary-properties_trimmed.tsv','../non_TS/summary-properties_trimmed.tsv')){
 
 format='proportions' # e.g. Basal is %Basal rather than # of basal resources
 # format='numbers' # I tried both ways initially.
@@ -88,6 +87,12 @@ if(format=='proportions'){
 if(power_analysis==TRUE){
   source('power_analyses.R')
 }
+
+if(infile=='../non_TS/summary-properties_trimmed.tsv'){
+  save.image('nonTS_models.Rdata') } else {
+    save.image('TS_models.Rdata')
+  }
+
 
 # Eliminate the redundant authors (those that always and only occur with another author) prior to jackknifing.
 source('redundant_authors.R')
@@ -232,3 +237,4 @@ if(infile=='../non_TS/summary-properties_trimmed.tsv'){
 }
 
 ######### And we're done!!!!!! ###########
+}

### 2018-04-16 code/recreate_with_subset.R

@@ -6,30 +6,29 @@
     +log(Species):Latitude:(Stream+Lakeweb+Marine+Terr)
     ,na.action=na.fail))
   ls_dredge=dredge(LS_full,rank=AIC)
-  if(infile=='../mod_data/summary-properties.tsv'){
-    # TS - updated 29/06/2015
+  if(infile=='../mod_data/summary-properties_trimmed.tsv'){
+    # TS - updated 16/04/2018
     LS_min =with(data,lm(log(LS)~log(Species)
     +log(Species):Lakeweb
-    +log(Species):Latitude
-    +log(Species):Latitude:Lakeweb
-    ,na.action=na.fail))    } else {
-      # non-TS - updated 29/06/2015
+    ,na.action=na.fail))   
+    cutoff<- 4/((nrow(data)-length(LS_min$coefficients)-2)) 
+    plot(LS_min, which=4, cook.levels=cutoff)
+    # Very small changes to parameters, none to sig.
+    subset=data[-c(75,150,161),]
+    subLS_min=(with(subset,lm(log(LS)~log(Species)
+    +log(Species):(Lakeweb),na.action=na.fail)))
+     } else {
+      # non-TS - updated 16/04/2018
     LS_min=with(data,lm(log(LS)~log(Species)
-    +log(Species):(Lakeweb+Terr)
-    +log(Species):Latitude
-    +log(Species):Latitude:Lakeweb,
-    na.action=na.fail))    }
+    +log(Species):(Lakeweb),
+    na.action=na.fail))    
+    cutoff<- 4/((nrow(data)-length(LS_min$coefficients)-2)) 
+    plot(LS_min, which=4, cook.levels=cutoff)
+    # Very small changes to parameters, none to sig.
+    subset=data[-c(62,75,130),]
+    subLS_min=(with(subset,lm(log(LS)~log(Species)
+    +log(Species):(Lakeweb),na.action=na.fail)))
     # Decided on DF
-
-    # cutoff<- 4/((nrow(data)-length(LS_min$coefficients)-2)) 
-    # plot(LS_min, which=4, cook.levels=cutoff)
-    if(infile!='../mod_data/summary-properties.tsv'){
-      # The only change is that the different intercept for terrestrial is not sig.
-      subset=data[-c(60,136,163),]
-      subLS_min=(with(subset,lm(log(LS)~log(Species)
[…]

### 2018-04-16 manuscript/latitudepaper.tex
Still working on the updating:

@@
 
-  [[[[[Need to double-check and update this. Then adjust discussion as needed.]]]]]
-  [[Note: The trophic species version of the webs changed less with the correction.
-For link density, $\beta_{Latitude:Lake}$=0.005, $p$=0.002.
-For generality, $\beta_{Latitude:Lake}$=0.006, $p$\textless0.001 and $\beta_{Latitude:Stream}$=0.004, $p$=0.009.
-For vulnerability, $\beta_{Latitude:Lake}$=0.005, $p$=0.002.]]
+  % [[Very small changes with trophic species versions.]]
 
@@
   species richness. In this dataset, however, we found no evidence to support
-  latitudinal gradients in species richness, links per species, generality, or
-  vulnerability.
+  latitudinal gradients in species richness, links per species, generality, 
+  or vulnerability.
 
@@
   food webs was stronger (i.e., generality increased more steeply with
-  increasing species richness) in higher-latitude food webs. In lake food webs,
+  increasing species richness) in higher-latitude food webs. \st{In lake food webs,
   this trend was echoed in the scaling relationships between species richness
-  and vulnerability and links per species. This means that species in tropical
+  and vulnerability and links per species.} This means that species in tropical
   freshwater communities gain fewer additional feeding links per additional
-  species in the web and that species in tropical lakes also gain fewer
+  species in the web\st{ and that species in tropical lakes also gain fewer
   predators, and fewer links in general, per additional species than species
-  in high-latitude lakes. These trends are consistent with the hypothesis that
+  in high-latitude lakes}. These trends are consistent with the hypothesis that
   greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
@@
   generalist across all types of aquatic habitats than terrestrial 
-  consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data (
-  $\mu_{Aquatic}$=5.47, $\mu_{Terrestrial}$=3.82; $p$=0.007 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$). 
+  consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data, although the difference between generality was not significant (
+  $\mu_{Aquatic}$=\st{5.47}5.71, $\mu_{Terrestrial}$=\st{3.82}4.82; $p$=\st{0.007}0.297 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$). 
   The key to this argument is therefore whether freshwater ecosystems experience

### 2018-04-16 code/TL_observedfits.py

@@ -25,8 +25,9 @@ def datareader(rawdatafile,TL,Bformat):
   points={'LS':[],'Gen':[],'Vul':[]}
 
   f=open(rawdatafile,'r')
+  i=1
   for line in f:
-    if line.split()[0]!='Web':
+    if line.split('\t')[0]!='Web':
       ecotype=line.split('\t')[1]
       ecotype=ecotype.capitalize()
       site=line.split('\t')[2]
@@ -552,7 +553,7 @@ def main():
   for Bformat in ['proportions']:#['numbers','proportions']:
     # for rawdatafile in ['../non_TS/summary-properties.tsv']:#,'../mod_data/summary-properties.tsv']:
     for rawdatafile in ['../non_TS/summary-properties_trimmed.tsv','../mod_data/summary-properties_trimmed.tsv']:
-      if rawdatafile=='../non_TS/summary-properties_connected_extended.tsv':
+      if rawdatafile=='../non_TS/summary-properties_trimmed.tsv':
         outfile1='../manuscript/Figures/by_TL/scaling_with_S/'+Bformat+'/S_fitlines_nonts_new.eps'
         outfile2='../manuscript/Figures/by_TL/scaling_with_S/'+Bformat+'/TL_fitlines_nonts_new.eps'
         # predfolder='../non_TS/'+Bformat
@@ -565,8 +566,10 @@ def main():
 
       S_scaleplots(rawdatafile,outfile1,Bformat,predfolder)
 
+      print 'S okay'
       S_rawplots(rawdatafile,outfile1,Bformat,predfolder)
 
+      print 'Raw okay'
       # # Didn't use these in the final MS, didn't update the TL-specific models.
       # TL_rawplots(rawdatafile,outfile2,Bformat,predfolder)
 

### 2018-04-16 code/byTL_Models.R

@@ -26,6 +26,19 @@ data$Intermediate=as.numeric(as.character(data$Intermediate))
 data$Intermediate=data$Intermediate+data$Herbivores   # Role herbivores into intermediates
 data$Toppreds=as.numeric(as.character(data$Toppreds))
 
+# Remove authors that are no longer relevant
+dead_authors=c("A","Agostinho","Allan","Aloisio","Althaus","Angelini","Antezana","Arreguin_Sanchez","Badcock","Baeta",
+  "Bax","Boit","Briand","Brodeur","Bulman","Carvalho","Catella","Chavez","Chen","Chen_Y","Christian","Cornejo.Donoso",
+  "Cruz.Escalona", "Dai","Darlington","Elton","Emmett","Fang","Fetahi","Flechsig","Gomes","Grigg","He","Hsieh","Hung",
+  "Li_J","Libralato","Lin","Link","Liu","Lo","Luczkovich","Mann","Marshall","Mayse","Mengistou","Morgan","Moriarty_C",
+  "Moriarty_D","Newman","Niering","Niquil","Pearcy","Price","Rasmussen","Ratsirarson","Resende","Ruzicka","Savely",
+  "Schagerl","Shao","Silander","Steele","Su","Tevlin","Thomas","Vaz.Velho","Wainwright","Zamon","Zaret","Zetina_Rejon","de_Morais")
+for(auth in dead_authors){
+  data[,auth]<-NULL
+}
+
+
+
 # Add dummy variables for ecosystem types
 data$Estuary=0
 data$Lakeweb=0
@@ -59,6 +72,7 @@ data=subset(data,data$Basal>0)
 data=subset(data,data$Intermediate>0)
 data=subset(data,data$Toppreds>0)
 data$Latitude = as.numeric(as.character(data$Latitude))
+
 
 # Save the original data to prevent accidents with jackknifing subsets.
 olddata=data
@@ -115,31 +129,31 @@ for(i in 1:nrow(olddata)){
 }
 
 
-# # If an author is only on one web, then I've already checked that in the webwise version :)
-# # Now remove all webs associated with each of the other authors.
-# j=1
-# for(i in 20:222){
-#   if(sum(olddata[,i])>1){
-#     newdata=olddata[which(olddata[,i]==0),]
-#     name=colnames(olddata)[i]
+# If an author is only on one web, then I've already checked that in the webwise version :)
[…]

### 2018-04-16 code/recreate_with_subset.R

@@ -6,12 +6,13 @@
     +log(Species):Latitude:(Stream+Lakeweb+Marine+Terr)
     ,na.action=na.fail))
   ls_dredge=dredge(LS_full,rank=AIC)
+  # Same model for TS and original.
+  LS_min =with(data,lm(log(LS)~log(Species)
+    +log(Species):Lakeweb
+    ,na.action=na.fail))    
+  cutoff<- 4/((nrow(data)-length(LS_min$coefficients)-2)) 
   if(infile=='../mod_data/summary-properties_trimmed.tsv'){
     # TS - updated 16/04/2018
-    LS_min =with(data,lm(log(LS)~log(Species)
-    +log(Species):Lakeweb
-    ,na.action=na.fail))   
-    cutoff<- 4/((nrow(data)-length(LS_min$coefficients)-2)) 
     plot(LS_min, which=4, cook.levels=cutoff)
     # Very small changes to parameters, none to sig.
     subset=data[-c(75,150,161),]
@@ -19,10 +20,6 @@
     +log(Species):(Lakeweb),na.action=na.fail)))
      } else {
       # non-TS - updated 16/04/2018
-    LS_min=with(data,lm(log(LS)~log(Species)
-    +log(Species):(Lakeweb),
-    na.action=na.fail))    
-    cutoff<- 4/((nrow(data)-length(LS_min$coefficients)-2)) 
     plot(LS_min, which=4, cook.levels=cutoff)
     # Very small changes to parameters, none to sig.
     subset=data[-c(62,75,130),]
@@ -40,14 +37,15 @@
     +log(Species):Latitude:(Stream+Lakeweb+Marine+Terr)
     ,na.action=na.fail))
   g_dredge=dredge(Gen_full,rank=AIC)
-  if(infile=='../mod_data/summary-properties_trimmed.tsv'){
-    # TS - updated 16/04/2018
-    Gen_min=with(data,lm(log(Gen)~log(Species)
+  # Same model for TS and original
+  Gen_min=with(data,lm(log(Gen)~log(Species)
       +log(Species):(Lakeweb+Stream)
       +log(Species):Latitude
       +log(Species):Latitude:(Lakeweb+Stream)
       ,na.action=na.fail)) 
-    cutoff<- 4/((nrow(data)-length(Gen_min$coefficients)-2)) 
+  cutoff<- 4/((nrow(data)-length(Gen_min$coefficients)-2)) 
[…]

### 2018-04-16 code/trimmer.py

@@ -10,17 +10,37 @@ dubious_webs=['WEB218.web','WEB220.web','WEB225.web','WEB236.web','WEB238.web','
 # # Taking too long to recalculate. Will be better to just
 # # read in the datafile and trim these.
 
-def removewebs(infile,outfile):
+def read_in_authors(oldfile):
+  authors={}
+  f=open(oldfile,'r')
+  for line in f:
+    web=line.split('\t')[0]
+    auths=line.split('\t')[19:]
+    if web!='Web':
+      authors[web]=auths
+    else:
+      authors['HEAD']=auths
+  return authors
+
+def removewebs(infile,outfile,oldfile):
+  authors=read_in_authors(oldfile)
+
   goodlines=[]
   f=open(infile,'r')
   for line in f:
     if line.split()[0] not in dubious_webs:
-      goodlines.append(line)
+      goodlines.append(line.split('\n')[0])
   f.close()
 
   g=open(outfile,'w')
-  for line in goodlines:
-    g.write(line)
+  g.write(goodlines[0]+'\t'+'\t'.join(authors['HEAD']))
+  for line in goodlines[1:]:
+    web=line.split()[0]
+    if web!='WEB294_rotated.web':
+      g.write(line+'\t'+'\t'.join(authors[web]))
+    else:
+      g.write(line+'\t'+'\t'.join(authors['WEB294.web']))
+
   g.close()
 
 def main():
@@ -29,8 +49,9 @@ def main():
   for indir in ['../mod_data/', '../non_TS/']:
     infile=indir+suffix
     outfile=indir+'summary-properties_trimmed.tsv'
+    oldfile='../non_TS/summary-properties.tsv'
 
-    removewebs(infile,outfile)
+    removewebs(infile,outfile,oldfile)
     print infile, ' done'
 
 if __name__ == '__main__':

### 2018-04-16 code/updated_marginal_CIs_nonTS.R

@@ -7,308 +7,61 @@ S_CIs <- function(model){
 
       if(model=="LS_min" | model=="Vul_min"){ # No latitude terms
 
-        marginal <- betas["log10(Species)"]
+        marginal <- betas["log(Species)"]
 
-        se <- sqrt(covar["log10(Species)","log10(Species)"])
+        se <- sqrt(covar["log(Species)","log(Species)"])
 
         upper <- marginal + 1.64*se
         lower <- marginal - 1.64*se
 
-        terr_m <- marginal + betas["log10(Species):Terr"]
-        terr_se <- sqrt(se^2 +
-          covar["log10(Species):Terr","log10(Species):Terr"] 
-          +2*covar["log10(Species):Terr","log10(Species)"])
-        terr_upper <- terr_m + 1.64*terr_se
-        terr_lower <- terr_m - 1.64*terr_se
+        lake_m <- marginal + betas["log(Species):Lakeweb"]
+        lake_se <- sqrt(se^2 +
+          covar["log(Species):Lakeweb","log(Species):Lakeweb"] 
+          +2*covar["log(Species):Lakeweb","log(Species)"])
+        lake_upper <- lake_m + 1.64*lake_se
+        lake_lower <- lake_m - 1.64*lake_se
 
-        stream_m <- marginal + betas["log10(Species):Stream"]
-        stream_se <- sqrt(se^2 +
-          covar["log10(Species):Stream","log10(Species):Stream"] 
-          +2*covar["log10(Species):Stream","log10(Species)"])
-        stream_upper <- stream_m + 1.64*stream_se
-        stream_lower <- stream_m - 1.64*stream_se
-
-
-        results <- cbind(lat,marginal,upper,lower,terr_m,terr_upper,terr_lower,stream_m,stream_upper,stream_lower)
-        colnames(results)=c("Latitude","Marginal","Upper","Lower","Terrestrial","Terr_upper","Terr_lower","Stream","Stream_upper","Stream_lower")
+        results <- cbind(lat,marginal,upper,lower,lake_m,lake_upper,lake_lower)
+        colnames(results)=c("Latitude","Marginal","Upper","Lower","Lake","Lake_upper","Lake_lower")
       }
 
       if(model=="Gen_min"){
 
-        marginal <- betas["log10(Species)"]+lat*betas["log10(Species):Latitude"]
[…]

### 2018-04-17 manuscript/latitudepaper.tex
updated figs, main text.

@@
   number of prey per species), and vulnerability (mean number of predators per
-  species) were strongly and positively correlated ($R^2$=\st{0.891}0.890 for link
+  species) were strongly and positively correlated ($R^2$=\st{0.891}\textbf{0.890} for link
   density and generality, $R^2$\textgreater0.999 for link density and
-  vulnerability, and $R^2$=\st{0.890}0.889 for generality and vulnerability). Contrary
+  vulnerability, and $R^2$=\st{0.890}\textbf{0.889} for generality and vulnerability). Contrary
   to the expected latitudinal gradient, the best-fit version of
@@
   Each measure of specialisation increased with increasing
-  species richness ($\beta_0$=\st{0.637}0.668, $p$\textless0.001; $\beta_0$=\st{0.553}0.689,
-  $p$\textless0.001; and $\beta_0$=\st{0.637}0.668, $p$\textless0.001, respectively;
+  species richness ($\beta_0$=\st{0.637}\textbf{0.668}, $p$\textless0.001; $\beta_0$=\st{0.553}\textbf{0.689},
+  $p$\textless0.001; and $\beta_0$=\st{0.637}\textbf{0.668}, $p$\textless0.001, respectively;
   Fig.~\ref{props_v_lat}). 
@@
   (\st{$\beta_{Latitude}$=-0.001, $p$=0.365 for link density;}
-  $\beta_{Latitude}$=\st{-0.001}-0.002, $p$=\st{0.535}0.101 for generality; 
-  latitude was not retained in the best-fit models for link density or vulnerability \st{and
+  $\beta_{Latitude}$=\st{-0.001}\textbf{-0.002}, $p$=\st{0.535}\textbf{0.101 for generality; 
+  latitude was not retained in the best-fit models for link density or vulnerability}\st{and
   $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability}; Fig.~\ref{S}). 
@@
   $\beta_{Latitude:Stream}$ was not retained in the best-fit models).}
-  In lake and stream food webs, however, the scaling of generality was stronger
+  In \textbf{lake and} stream food webs, however, the scaling of generality was stronger
   towards the poles. This change in scaling was significant for streams but not for
-  lakes ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively).
+  lakes ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001\textbf{ and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively}).
   % [[After correction: Link density and vulnerability scaled more strongly with species richness in lake food webs ($\beta_{Lake}$=0.057, $p$=0.024 and $\beta_{Lake}$=0.059, $p$=0.020, respectively).
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
+\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_new.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+%\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_updated.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem

### 2018-04-17 code/TL_marginal_latitude.py

@@ -25,7 +25,8 @@ ecotypes=['Estuary','Lake','Marine','Stream','Terrestrial']
 
 def linereader(prop,TL,form):
   # linefile=open('../non_TS/proportions/marginals/'+prop+'_'+TL+'_marginal.tsv','r')
-  linefile=open('../updated/'+form+'/marginals/'+prop+'_'+TL+'_marginal.tsv','r')
+  linefile=open('../updated/'+form+'/proportions/marginals/'+prop+'_'+TL+'_marginal.tsv','r')
+  # ../updated/non_TS/proportions/marginals/LS_S_marginal.tsv  
   lines={}
   for ecotype in ecotypes:
     lines[ecotype]={'main':[],'upper':[],'lower':[]}
@@ -39,17 +40,11 @@ def linereader(prop,TL,form):
 
       if TL=='S':
         if prop!='Gen':
-          terr_m=float(line.split()[5])
-          terr_u=float(line.split()[6])
-          terr_l=float(line.split()[7])
 
-          lake_m=float(line.split()[8])
-          lake_u=float(line.split()[9])
-          lake_l=float(line.split()[10])
+          lake_m=float(line.split()[5])
+          lake_u=float(line.split()[6])
+          lake_l=float(line.split()[7])
 
-          lines['Terrestrial']['main'].append((s0,terr_m))
-          lines['Terrestrial']['upper'].append((s0,terr_u))
-          lines['Terrestrial']['lower'].append((s0,terr_l))
           lines['Lake']['main'].append((s0,lake_m))
           lines['Lake']['upper'].append((s0,lake_u))
           lines['Lake']['lower'].append((s0,lake_l))
@@ -403,7 +398,8 @@ def main():
   names=['','','','','','','','','','','','','','','','','','','','','','','','','','','','','','','','']
 
   # for form in ['proportions']:#,'numbers']: # Always using proportions but want to have updated figs for TS and non-TS
-  for form in ['mod_data','non_TS']:
+  for form in ['non_TS']:
+  # for form in ['mod_data','non_TS']:
     for TL in TLs:
       # Make a separate graph for each TL
       grace=MultiPanelGrace(colors=ColorBrewerScheme('Greys'))

### 2018-04-17 code/TL_observedfits.py

@@ -64,6 +64,7 @@ def datareader(rawdatafile,TL,Bformat):
   return points
 
 def fixed_reader(coefffile):
+  print coefffile
   fixed_effects={}
   f=open(coefffile,'r')
   for line in f:
@@ -234,11 +235,11 @@ def S_scaleplots(rawdatafile,outfile1,Bformat,predfolder):
     rawdata=datareader(rawdatafile,TL,Bformat)
     # if rawdatafile=='../non_TS/summary-properties.tsv':
     if rawdatafile=='../non_TS/summary-properties_trimmed.tsv':
-      # fixed=fixed_reader('../non_TS/coefficients/'+prop+'_co.tsv')
-      fixed=fixed_reader('../updated/non_TS/coefficients/'+prop+'_co.tsv')
+      fixed=fixed_reader('../non_TS/coefficients/'+prop+'_co.tsv')
+      # fixed=fixed_reader('../updated/non_TS/coefficients/'+prop+'_co.tsv')
     else:
-      # fixed=fixed_reader('../mod_data/coefficients/'+prop+'_co.tsv')
-      fixed=fixed_reader('../updated/mod_data/coefficients/'+prop+'_co.tsv')
+      fixed=fixed_reader('../mod_data/coefficients/'+prop+'_co.tsv')
+      # fixed=fixed_reader('../updated/mod_data/coefficients/'+prop+'_co.tsv')
 
     graph=grace.add_graph(Panel)
     for ecotype in ecotypes:

### 2018-04-17 manuscript/supplement.tex
updated SI

@@
   community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
-  describing competitive interactions. Finally, we eliminated 2 webs
+  describing competitive interactions. Additionally, we eliminated 2 webs
   describing  inferred interactions in an extinct community, 10 ``generalised
@@
   food web (and therefore the latitude of the food web could not be
-  included). This left us with 226 webs from~\cite{GlobalWeb}.
+  included). Finally, we eliminated a further 75 food webs which contained one or more formatting errors. This left us with 151 webs from~\cite{GlobalWeb}.
 
@@
   the~\cite{GlobalWeb}  dataset, and the last web was derived from an
-  unpublished source. This gave us a database of 263 webs. As a measure of
+  unpublished source. This gave us a database of 188 webs. All of these 
+  As a measure of
   quality-control, we then eliminated any food web which did not have at least
@@
   which did not meet this requirement tended to be very small and poorly-resolved.
-  Our final sample size was thereby reduced to 196 food webs.
+  Our final sample size was thereby reduced to 161 food webs.
 
@@
         17    & 3 & \cite{Hiatt1960}  & marine & 4,30 - 15 N & No    & Generalised scheme \\
-        18    & 3 & \cite{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & Yes   &       \\
+        18    & 3 & \cite{Niering1963a}  & terrestrial & 1,01,29 - 1,06,23 N & No   &  Formatting errors     \\
         19    & 3 & \cite{Brooks1963}    & lake &       & No    & Could not locate original source \\
@@
         21    & 3 & \cite{Patten1979}  & marine & 70-85 S & Yes   &       \\
-        22    & 3 & \cite{Summerhayes1923}  & terrestrial & 74,27,54 N & Yes   &       \\
-        23    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
-        24    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        22    & 3 & \cite{Summerhayes1923}  & terrestrial & 74,27,54 N & No   &  Formatting errors     \\
+        23    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & No  &  Formatting errors       \\
+        24    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & No  &  Formatting errors     \\
         25    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
-        26    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & Yes   &       \\
+        26    & 3 & \cite{Bird1930}  & terrestrial & 50,25,17 N & No  &  Formatting errors     \\
         27    & 3 & \cite{Varley1970}  & terrestrial &       & No    & Could not locate original source \\
@@
         32    & 3 & \cite{Petipa1970}  & marine &       & No    & Could not locate original source \\
-        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
+        33    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & No  &  Formatting errors     \\
         34    & 3 & \cite{Jones1949}     & stream & 51,41 - 51,55 N & Yes   &       \\
@@
         36    & 3 & \cite{Walsh1967}  & estuary & 21,26,09 N & No    & Could not locate original source \\
-        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & Yes   &       \\
-        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
-        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & Yes   &       \\
+        37    & 3 & \cite{Clarke1967}    & marine & 41,02,49 N & No  &  Formatting errors     \\
+        38    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & No  &  Formatting errors     \\
+        39    & 3 & \cite{Fryer1959} & lake & 11,36,39 S & No  &  Formatting errors     \\
         40    & 3 & \cite{Harrison1962}  & terrestrial &       & No    & Generalised scheme \\
@@
         59    & 3 & \cite{Twomey1945}    & terrestrial & 40,09,47 N & Yes   &       \\
-        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & Yes   &       \\
+        60    & 3 & \cite{Rasmussen1941}    & terrestrial & 36,5-37 N & No  &  Formatting errors     \\
         61    & 3 & \cite{Summerhayes1928}  & terrestrial & 77,52,30 N & Yes   &       \\
@@
         113   & 3 & \cite{Dexter1947}  & marine & 42,38,56 N & Yes   &       \\
-        114   & 3 & \cite{Marshall1982}  & lake  & 17,54,11.90 S & Yes   &       \\
+        114   & 3 & \cite{Marshall1982}  & lake  & 17,54,11.90 S & No  &  Formatting errors     \\
         115   & 3 & \cite{Koepcke1952}  & marine &       & No    & Could not locate original source \\
         116   & 3 & \cite{Hurlbert1972}  & lake  & 35,09,19 S & Yes   &       \\
-        117   & 3 & \cite{Zaret1973}  & lake  & 9,11,31.50 N & Yes   &       \\
+        117   & 3 & \cite{Zaret1973}  & lake  & 9,11,31.50 N & No  &  Formatting errors     \\
         118   & 3 & \cite{Bindloss1972}  & lake  & 56,41,18.71 N & Yes   &       \\
-        119   & 3 & \cite{Mann1972}  & stream & 51,27 N & Yes   &       \\
-        120   & 3 & \cite{Moriarty1973}  & lake  & 0,00,58 N & Yes   &       \\
+        119   & 3 & \cite{Mann1972}  & stream & 51,27 N & No  &  Formatting errors     \\
+        120   & 3 & \cite{Moriarty1973}  & lake  & 0,00,58 N & No  &  Formatting errors     \\
         121   & 3 & \cite{VanEs1977}  & estuary & 53,20 - 53,15 N & Yes   &       \\
@@
         152   & 3 & \cite{Whittaker1984}    & terrestrial &       & No    & Source web \\
-        153   & 3 & \cite{Mayse1978}    & terrestrial & 40,06,38 N & Yes   &       \\
-        154   & 3 & \cite{Mayse1978}    & terrestrial & 39,56,41 N & Yes   &       \\
+        153   & 3 & \cite{Mayse1978}    & terrestrial & 40,06,38 N & No  &  Formatting errors     \\
+        154   & 3 & \cite{Mayse1978}    & terrestrial & 39,56,41 N & No  &  Formatting errors     \\
         155   & 3 & \cite{Askew1975}     & terrestrial &       & No    & Host-parasitoid web \\
@@
         179   & 3 & \cite{Robinson1953}  & terrestrial &       & No    & Source web \\
-        180   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
-        181   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
-        182   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
-        183   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & Yes   &       \\
+        180   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & No  &  Formatting errors     \\
+        181   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & No  &  Formatting errors     \\
+        182   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & No  &  Formatting errors     \\
+        183   & 3 & \cite{Savely1939}    & terrestrial & 36,01,02 N & No  &  Formatting errors     \\
         184   & 3 & \cite{Beaver1972}     & terrestrial &       & No    & Could not locate original source \\
@@
         201   & 3 & \cite{Valiela1974}    & terrestrial &       & No    & Source web \\
-        202   & 3 & \cite{Allan1982}    & stream & 38,50,21 N & Yes   &       \\
+        202   & 3 & \cite{Allan1982}    & stream & 38,50,21 N & No  &  Formatting errors     \\
         203   & 3 & \cite{Collins1976}    & stream & 44,24 N & Yes   &       \\
@@
         212   & 3 & \cite{Ricker1935}  & stream &       & No    & Could not locate original source \\
-        213   & 3 & \cite{Badcock1949}     & stream & 53 N  & Yes   &       \\
-        214   & 3 & \cite{Thompson2003}    & stream & 44,40,44 N & Yes   &       \\
-        215   & 3 & \cite{Thompson2003}    & stream & 40,40,52 N & Yes   &       \\
-        216   & 3 & \cite{Thompson2003}    & stream & 35,02,50 N & Yes   &       \\
-        217   & 3 & \cite{Thompson2003}    & stream & 35,03,50 N & Yes   &       \\
-        218   & 3 & \cite{Thompson2004c}  & stream & 45.79 S & Yes   &       \\
-        219   & 3 & \cite{Thompson2004c}  & stream & 44.64 S & Yes   &       \\
-        220   & 3 & \cite{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
-        221   & 3 & \cite{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
-        222   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
-        223   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        224   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        225   & 3 & \cite{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
+        213   & 3 & \cite{Badcock1949}     & stream & 53 N  & No  &  Formatting errors     \\
+        214   & 3 & \cite{Thompson2003}    & stream & 44,40,44 N & No  &  Formatting errors     \\
+        215   & 3 & \cite{Thompson2003}    & stream & 40,40,52 N & No  &  Formatting errors     \\
+        216   & 3 & \cite{Thompson2003}    & stream & 35,02,50 N & No  &  Formatting errors     \\
+        217   & 3 & \cite{Thompson2003}    & stream & 35,03,50 N & No  &  Formatting errors     \\
+        218   & 3 & \cite{Thompson2004c}  & stream & 45.79 S & No  &  Formatting errors     \\
+        219   & 3 & \cite{Thompson2004c}  & stream & 44.64 S & No  &  Formatting errors     \\
+        220   & 3 & \cite{Thompson2004c}  & stream & 46.29 S & No  &  Formatting errors     \\
+        221   & 3 & \cite{Thompson2004c}  & stream & 46.41 S & No  &  Formatting errors     \\
+        222   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & No  &  Formatting errors     \\
+        223   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & No  &  Formatting errors     \\
+        224   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & No  &  Formatting errors     \\
+        225   & 3 & \cite{Thompson2004c}  & stream & 46.115 S & No  &  Formatting errors     \\
         226   & 3 & \cite{Thompson2004c}  & stream & 45.61 S & Yes   &       \\
@@
         235   & 3 & \cite{Thompson2004c}  & stream & 45.752 S & Yes   &       \\
-        236   & 3 & \cite{Thompson2004c}  & stream & 46.29 S & Yes   &       \\
+        236   & 3 & \cite{Thompson2004c}  & stream & 46.29 S & No  &  Formatting errors     \\
         237   & 3 & \cite{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
-        238   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
+        238   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & No  &  Formatting errors     \\
         239   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        240   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        240   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & No  &  Formatting errors     \\
         241   & 3 & \cite{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
@@
         243   & 3 & \cite{Thompson2004c}  & stream & 46.41 S & Yes   &       \\
-        244   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & Yes   &       \\
+        244   & 3 & \cite{Thompson2004c}  & stream & 45,57,0 S & No  &  Formatting errors     \\
         245   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
-        246   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & Yes   &       \\
+        246   & 3 & \cite{Thompson2004c}  & stream & 46.08 S & No  &  Formatting errors     \\
         247   & 3 & \cite{Thompson2004c}  & stream & 46.115 S & Yes   &       \\
         248   & 3 & \cite{Thompson2004}  & estuary & 45,51,28 S & Yes   &        \\
-        249   & 3 & \cite{Angelini2005}  & stream & 24,30 S & Yes   &       \\
-        250   & 3 & \cite{Angelini2006}  & lake  & 22,57,38 S & Yes   &       \\
-        251   & 3 & \cite{Angelini2006}  & lake  & 22,57,38 S & Yes   &       \\
-        252   & 3 & \cite{Angelini2010}  & stream & 18,40 S & Yes   &       \\
-        253   & 3 & \cite{Angelini2011}  & marine & 5 - 17,15 S & Yes   &       \\
-        254   & 3 & \cite{Angelini2013}  & stream & 21 S  & Yes   &       \\
-        255   & 3 & \cite{Angelini2013}  & stream & 21 S  & Yes   &       \\
+        249   & 3 & \cite{Angelini2005}  & stream & 24,30 S & No  &  Formatting errors     \\
+        250   & 3 & \cite{Angelini2006}  & lake  & 22,57,38 S & No  &  Formatting errors     \\
+        251   & 3 & \cite{Angelini2006}  & lake  & 22,57,38 S & No  &  Formatting errors     \\
+        252   & 3 & \cite{Angelini2010}  & stream & 18,40 S & No  &  Formatting errors     \\
+        253   & 3 & \cite{Angelini2011}  & marine & 5 - 17,15 S & No  &  Formatting errors     \\
+        254   & 3 & \cite{Angelini2013}  & stream & 21 S  & No  &  Formatting errors     \\
+        255   & 3 & \cite{Angelini2013}  & stream & 21 S  & No  &  Formatting errors     \\
         256   & 3 & \cite{Angelini2013}  & stream &       & No    & Could not locate original source \\
-        257   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        258   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        259   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        260   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        261   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
-        262   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & Yes   &       \\
+        257   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & No  &  Formatting errors     \\
+        258   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & No  &  Formatting errors     \\
+        259   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & No  &  Formatting errors     \\
+        260   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & No  &  Formatting errors     \\
+        261   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & No  &  Formatting errors     \\
+        262   & 3 & \cite{Baeta2011}  & estuary & 40,08 N & No  &  Formatting errors     \\
         263   & 3 & \cite{Schneider1997}    & lake  & 45,58,50 N & Yes   &       \\
         264   & 3 & \cite{Stagliano2002}    & terrestrial & 39,06,27 N & Yes   &       \\
-        265   & 3 & \cite{Lin2006}  & marine & 22,27 N & Yes   &       \\
-        266   & 3 & \cite{Cornejo-Donoso2008}  & marine & 60 - 69 S & Yes   &       \\
+        265   & 3 & \cite{Lin2006}  & marine & 22,27 N & No  &  Formatting errors     \\
+        266   & 3 & \cite{Cornejo-Donoso2008}  & marine & 60 - 69 S & No  &  Formatting errors     \\
          \hline
@@
         \hline
-        267   & 3 & \cite{Zetina-Rejon2003}  & marine & 23.15 - 22.9N & Yes   &       \\
-        268   & 3 & \cite{Cruz-Escalona2007}  & marine & 18,45 - 18,50 N & Yes   &       \\
-        269   & 3 & \cite{Liu2007}  & lake  & 29,32,35 N & Yes   &       \\
+        267   & 3 & \cite{Zetina-Rejon2003}  & marine & 23.15 - 22.9N & No  &  Formatting errors     \\
+        268   & 3 & \cite{Cruz-Escalona2007}  & marine & 18,45 - 18,50 N & No  &  Formatting errors     \\
+        269   & 3 & \cite{Liu2007}  & lake  & 29,32,35 N & No  &  Formatting errors     \\
         270   & 3 & \cite{Filgueira2011}  & marine & 42,17,37 - 42,19,29 N & Yes   &       \\
@@
         287   & 3 & \cite{Cromar1996}  & stream & 50,58 N & Yes   &       \\
-        288   & 3 & \cite{Christian1999}    & estuary & 30,05,39 N & Yes   &       \\
-        289   & 3 & \cite{Fetahi2011}  & lake  & 11,15 N & Yes   &       \\
-        290   & 3 & \cite{Brodeur1992}    & marine & 43 - 48 N & Yes   &       \\
-        291   & 3 & \cite{Brodeur1992}    & marine & 44 - 48 N & Yes   &       \\
-        292   & 3 & \cite{Brodeur1992}    & marine & 45 - 48 N & Yes   &       \\
-        293   & 3 & \cite{Brodeur1992}    & marine & 46 - 48 N & Yes   &       \\
+        288   & 3 & \cite{Christian1999}    & estuary & 30,05,39 N & No  &  Formatting errors     \\
+        289   & 3 & \cite{Fetahi2011}  & lake  & 11,15 N & No  &  Formatting errors     \\
+        290   & 3 & \cite{Brodeur1992}    & marine & 43 - 48 N & No  &  Formatting errors     \\
+        291   & 3 & \cite{Brodeur1992}    & marine & 44 - 48 N & No  &  Formatting errors     \\
+        292   & 3 & \cite{Brodeur1992}    & marine & 45 - 48 N & No  &  Formatting errors     \\
+        293   & 3 & \cite{Brodeur1992}    & marine & 46 - 48 N & No  &  Formatting errors     \\
         294   & 3 & \cite{Gaedke1994}  & lake  & 47,37,30 N & Yes   &       \\
         295   & 3 & \cite{Preston2012}    & lake  & 37.66 N & Yes   &        \\
-        296   & 3 & \cite{Ratsirarson1996}  & lake  & 24,55 S & Yes   &       \\
+        296   & 3 & \cite{Ratsirarson1996}  & lake  & 24,55 S & No  &  Formatting errors     \\
         297   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
@@
         306   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
-        307   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
+        307   & 3 & \cite{Closs1994}  & stream & 37,40 S & No  &  Formatting errors     \\
         308   & 3 & \cite{Closs1994}  & stream & 37,40 S & Yes   &       \\
@@
         319   & 3 & \cite{Kaiser-Bunbury2011}  & terrestrial &       & No    & Plant-pollinator web \\
-        320   & 3 & \cite{Ruzicka2012}    & marine & 42 - 49 N & Yes   &       \\
-        321   & 3 & \cite{Ruzicka2012}    & marine & 43 - 49 N & Yes   &       \\
-        322   & 3 & \cite{Ruzicka2012}    & marine & 44 - 49 N & Yes   &       \\
-        323   & 3 & \cite{Ruzicka2012}    & marine & 45 - 49 N & Yes   &       \\
-        324   & 3 & \cite{Ruzicka2012}    & marine & 46 - 49 N & Yes   &       \\
+        320   & 3 & \cite{Ruzicka2012}    & marine & 42 - 49 N & No  &  Formatting errors     \\
+        321   & 3 & \cite{Ruzicka2012}    & marine & 43 - 49 N & No  &  Formatting errors     \\
+        322   & 3 & \cite{Ruzicka2012}    & marine & 44 - 49 N & No  &  Formatting errors     \\
+        323   & 3 & \cite{Ruzicka2012}    & marine & 45 - 49 N & No  &  Formatting errors     \\
+        324   & 3 & \cite{Ruzicka2012}    & marine & 46 - 49 N & No  &  Formatting errors     \\
         325   & 3 & \cite{Lewis2002}  & terrestrial &       & No    & Host-parasitoid web \\
@@
         332   & 3 & \cite{Huang2008}  & stream & 31.70 N & Yes   &       \\
-        333   & 3 & \cite{Link2002}    & marine & 33,51 - 44,49 N & Yes   &       \\
+        333   & 3 & \cite{Link2002}    & marine & 33,51 - 44,49 N & No  &  Formatting errors     \\
         334   & 3 & \cite{Alcorlo2001}  & lake  & 41,26,36 N & Yes   &       \\
@@
         338   & 3 & \cite{Torres2013}  & marine &       & No    & Could not locate original source \\
-        339   & 3 & \cite{Bulman2001}  & marine & 37-39 S & Yes   &       \\
+        339   & 3 & \cite{Bulman2001}  & marine & 37-39 S & No  &  Formatting errors     \\
         340   & 3 & \cite{Smith2007}  & marine & 74-78 S & Yes   &       \\
         341   & 3 & \cite{Lancraft1991}  & marine & 58,20.8 - 60,10.4 S & Yes   &       \\
-        342   & 3 & \cite{Hopkins1993}  & marine & 57,00 - 60,45 S & Yes   &       \\
+        342   & 3 & \cite{Hopkins1993}  & marine & 57,00 - 60,45 S & No  &  Formatting errors     \\
         343   & 3 & \cite{Kitching1987}  & lake  & 28,12 S & Yes   &       \\
         344   & 3 & \cite{Hodkinson2004}  & terrestrial &       & No    & Host-parasitoid web \\
-        345   & 3 & \cite{Boit2012}  & lake  & 47,38,10 N & Yes   &       \\
+        345   & 3 & \cite{Boit2012}  & lake  & 47,38,10 N & No  &  Formatting errors     \\
         346   & 3 & \cite{Rayner2010}  & stream & 17,7 S & Yes   &       \\
@@
         349   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
-        350   & 3 & \cite{Douglass2011}    & marine & 37,13 N & Yes   &       \\
+        350   & 3 & \cite{Douglass2011}    & marine & 37,13 N & No  &  Formatting errors     \\
         351   & 3 & \cite{Warren1989}     & lake  &       & No    & Could not locate original source \\

### 2018-04-17 code/byTL_Models.R

@@ -85,17 +85,17 @@ if(infile=='../mod_data/summary-properties_trimmed.tsv'){
   outdir='../mod_data/'  } else {
     outdir='../non_TS/'     }
 
-# Calculate the by-TL models
-if(by_TL==TRUE){
-if(format=='proportions'){
-  source('property_models_proportions.R')
-  save.image(file=paste(outdir,'proportion_Models.RData',sep=''))
+# # Calculate the by-TL models # Has not been updated.
+# if(by_TL==TRUE){
+# if(format=='proportions'){
+#   source('property_models_proportions.R')
+#   save.image(file=paste(outdir,'proportion_Models.RData',sep=''))
 
-} else {
-  source('property_models_numbers.R')
-  save.image(file=paste(outdir,'number_Models.RData',sep=''))
-}
-}
+# } else {
+#   source('property_models_numbers.R')
+#   save.image(file=paste(outdir,'number_Models.RData',sep=''))
+# }
+# }
 
 # Do the power analyses
 if(power_analysis==TRUE){

### 2018-04-17 code/jackknife_display_figure.py

@@ -16,6 +16,9 @@ from PyGrace.drawing_objects import DrawText, DrawLine
 from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
 from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
 from PyGrace.Extensions.latex_string import LatexString, CONVERT
+colors=ColorBrewerScheme('Paired')
+colors.add_color(120,120,120,'grey')
+
 
 redundants={
   'Egloff':['X38_coauthors','Richardson','Coauthors'],
@@ -107,7 +110,7 @@ def baselines(directory,prop):  # Get non-jackknifed parameters to make red dash
 
   for line in f:
     if line.split()[0]!='"Estimate"':
-      basis[line.split()[0]]=float(line.split()[1])
+      basis[line.split()[0]]=(float(line.split()[1]),float(line.split()[2]))
 
   return basis
 
@@ -116,8 +119,7 @@ def web_coefficient_zoo(directory,webfiles,prop):
   weblist=[]
 
   if prop in ['LS','Vul']:
-    betadict={'"(Intercept)"':{},'"log(Species)"':{},'"log(Species):Lakeweb"':{},
-              '"log(Species):Terr"':{},'"log(Species):Latitude"':{},'"log(Species):Lakeweb:Latitude"':{}}
+    betadict={'"(Intercept)"':{},'"log(Species)"':{},'"log(Species):Lakeweb"':{}}
   elif prop=='Gen':
     betadict={'"(Intercept)"':{},'"log(Species)"':{},'"log(Species):Lakeweb"':{},'"log(Species):Stream"':{},
               '"log(Species):Latitude"':{},'"log(Species):Lakeweb:Latitude"':{},'"log(Species):Stream:Latitude"':{}}
@@ -136,8 +138,7 @@ def author_coefficient_zoo(directory,authorfiles,prop):
   weblist=[]
 
   if prop in ['LS','Vul']:
-    betadict={'"(Intercept)"':{},'"log(Species)"':{},'"log(Species):Lakeweb"':{},
-              '"log(Species):Terr"':{},'"log(Species):Latitude"':{},'"log(Species):Lakeweb:Latitude"':{}}
+    betadict={'"(Intercept)"':{},'"log(Species)"':{},'"log(Species):Lakeweb"':{}}
   elif prop=='Gen':
[…]

### 2018-07-20 manuscript/latitudepaper_submitted.tex
updated to the version that was accepted by PRSB

--- 2015-08-23 manuscript/latitudepaper.tex
@@
 
-% let's get some nature formatted citations
-%\usepackage{overcite}
-\usepackage[round]{natbib}
+\usepackage[numbers,sort&compress]{natbib}
 
-% some cheats to reduce the need to type complicated bits and pieces
 \newcommand{\expect}[1]{\left\langle #1 \right\rangle}
@@
 
-\title{Specialisation in food webs scales with species richness but not with latitude}
-\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1,3}$, Tamara N. Romanuk$^{2}$}
-\date{\small$^1$School of Biological Sciences\\University of Canterbury\\
+\title{Latitudinal gradients in biotic niche breadth vary across ecosystem types.}
+\author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
+\date{\small$^1$Centre for Integrative Ecology\\School of Biological Sciences\\University of Canterbury\\
 Private Bag 4800\\Christchurch 8140, New Zealand \\
@@
 Several properties of food webs---the networks of feeding links between
-species---are known to vary systematically with the species richness of the underlying
-community.  Under the ``latitude-niche breadth hypothesis'', which predicts
-that species in the tropics will tend to evolve narrower niches, one might
-expect that these scaling relationships could also be affected by latitude. To
-test this hypothesis, we analysed the scaling relationships between species
-richness and average generality, vulnerability, and links per species across a
-set of 163 empirical food webs.  We also investigated scaling relationships
-between the three food-web properties and the proportions of the web made up
-by basal resources, intermediate consumers, and top predators. While we
-observed no effect of latitude on scaling relationships with species richness
-in the estuarine, marine, and terrestrial food webs, there were strong effects
-of latitude on scaling relationships in the freshwater food webs. In these
-communities, the latitude-niche breadth hypothesis appears to hold true while
-in other habitat types niche breadth appears to vary little. These contrasting
-findings indicate that it may be more important to account for habitat than
-latitude when exploring gradients in food-web structure.
+species---are known to vary systematically with the species richness of the
+underlying community.  Under the ``latitude-niche breadth hypothesis'', which
+predicts that species in the tropics will tend to evolve narrower niches, one
+might expect that these scaling relationships could also be affected by
+latitude. To test this hypothesis, we analysed the scaling relationships
+between species richness and average generality, vulnerability, and links per
+species across a set of 196 empirical food webs. In estuarine, marine, and 
+terrestrial food webs there was no effect of latitude on any scaling relationship,
+suggesting constant niche breadth in these habitats. In freshwater communities,
+on the other hand, there were strong effects of latitude on scaling relationships,
+supporting the latitude-niche breadth hypothesis. These contrasting findings
+indicate that it may be more important to account for habitat than latitude
+when exploring gradients in food-web structure.
 
@@
 
-\linenumbers
+% \linenumbers
 
@@
 
-  %Food webs are a thing. (Mention gen, vul, LS.) %Food webs have strong scaling structure.
-
   Food webs --networks of feeding links between species-- have been used for
   several decades to summarise the structure of  ecological
-  communities~\citep{Paine1966,Williams2000,Petchey2008} and to understand how
+  communities~\cite{Paine1966,Williams2000,Petchey2008} and to understand how
   that structure relates to environmental variables  such as habitat
-  type~\citep{Briand1983,Shurin2006}, primary
-  productivity~\citep{Townsend1998,Thompson2005a,Vermaat2009}, and
-  climate~\citep{Petchey2010,Baiser2012}. The latter variables in turn have
+  type~\cite{Briand1983,Shurin2006}, primary
+  productivity~\cite{Townsend1998,Thompson2005a,Vermaat2009}, and
+  climate~\cite{Petchey2010,Baiser2012}. The latter variables in turn have
   strong gradients over latitude, with productivity and temperature both being
   higher in the tropics while  climate is more variable at high
-  latitudes~\citep{Field1998}. These variables affect both the resources
+  latitudes~\cite{Field1998}. These variables affect both the resources
   available and species'
-  metabolisms~\citep{White2007,OConnor2009,Hechinger2011,White2011}, and have
+  metabolisms~\cite{White2007,OConnor2009,Hechinger2011,White2011}, and have
   been proposed as determinants of the strength of  interspecific
-  interactions~\citep{Schemske2009,Lang2012,Schleuning2012}.  By modulating
+  interactions~\cite{Schemske2009,Lang2012,Schleuning2012}.  By modulating
   interactions between species, latitudinal gradients may also shape food-web
@@
   richness, one of the most general and robust patterns in
-  ecology~\citep{Kaufman1995,Macpherson2002,Schemske2009}.
+  ecology~\cite{Kaufman1995,Macpherson2002,Schemske2009}.
 
-  % These gradients, together with the strength and generality of associations between biological processes and environmental variables, suggest that variation in network structure 
-  % may also be explained by ecological gradients \citep{Baiser2012}.
+  One proposed link between species richness and latitude is the 
+  ``latitude-niche breadth hypothesis''~\cite{Vazquez2004}.  This hypothesis 
+  predicts that decreased seasonality in the tropics should lead to more stable
+  populations, which in turn should evolve smaller niches~\cite{Vazquez2004}.
+  These narrow niches should therefore allow more species to  coexist in the
+  tropics than at higher latitudes. Alternatively, the higher productivity of
+  the tropics~\cite{Brown2004} may result in a broader niche
+  space~\cite{Davies2007} which could also sustain greater biodiversity even
+  if niche  sizes are globally similar. Although the assumptions of the
+  latitude-niche breadth hypothesis are only equivocally
+  supported~\cite{Vazquez2004}, it remains a compelling potential mechanism
+  for the latitudinal gradient in species
+  richness~\cite{Lappalainen2006,Krasnov2008,Slove2010}.
 
-  One proposed link between species richness and latitude is the ``latitude-niche breadth hypothesis''~\citep{Vazquez2004}. 
-  This hypothesis predicts that decreased seasonality in the tropics should lead to more stable populations, which in
-  turn should evolve smaller niches~\citep{Vazquez2004}. These narrow niches should therefore allow more species to 
-  coexist in the tropics than at higher latitudes. Alternatively, the higher productivity of the tropics~\citep{Brown2004}
-  may result in a broader niche space~\citep{Davies2007} which could also sustain greater biodiversity even if niche 
-  sizes are globally similar. Although the assumptions of the latitude-niche breadth hypothesis are only equivocally 
-  supported~\citep{Vazquez2004}, it remains a compelling potential mechanism for the latitudinal gradient in species 
-  richness~\citep{Lappalainen2006,Krasnov2008,Slove2010}.
+  If the latitude-niche breadth hypothesis is correct, there should also be
+  direct relationships between latitude and the degree of specialisation
+  (i.e., the breadth of the Eltonian niche; ~\cite{Elton1927,Leibold2010}) of
+  species within food webs. Specifically, narrower niches in the tropics would
+  equate to greater specialisation (narrower niches) while constant niche
+  sizes but greater productivity would translate to constant specialisation
+  and niche width across latitude (Fig.~\ref{concept}). Attempts to unravel
+  these effects, however, are complicated by known relationships between
+  species richness and many other network properties~\cite{Riede2010}.  For
+  example, narrower niches imply fewer links per species (i.e., greater
+  specialisation) in the tropics (\cite{Marra1997,Dyer2007}; but
+  see~\cite{Schleuning2012}). However, average numbers of links per species
+  tend to increase in larger food webs~\cite{Dunne2006,Riede2010}. This means
+  that a latitudinal effect on specialisation may be obscured by a latitudinal
+  gradient in species richness.
 
-  If the latitude-niche breadth hypothesis is correct, there should also be direct relationships between latitude and the
-  degree of specialisation (i.e., the breadth of the Eltonian niche; ~\citealp{Elton1927}) of species within food webs.
-  Specifically, narrower niches in the tropics would equate to
-  greater specialisation (narrower niches) while constant niche sizes but
-  greater productivity would translate to constant specialisation and niche
-  width across latitude.
-  Attempts to unravel these effects, however,
-  are complicated by known relationships between species richness and many other network properties~\citep{Riede2010}. 
-  For example,
-  narrower niches imply fewer links per species (i.e., greater specialisation) in the tropics (\citealp{Marra1997,Dyer2007};
-  but see~\citealp{Schleuning2012}). However,
-  average numbers of links per species tend to increase in larger food webs~\citep{Dunne2006,Riede2010}. This means
-  that a latitudinal effect on specialisation may be obscured by a latitudinal gradient in species richness. If this is
-  the case, it may still be possible to uncover effects of latitude on specialisation by examining the shape of the scaling 
-  relationship between specialisation and species richness over changing latitude. Here, we use three measures of specialisation:
-  mean links per species, mean generality (number of prey), and mean vulnerability (number of predators).   By testing whether latitude affects the scaling of each property with
-  species richness, we test for the effects of latitude on specialisation
-  implied by the ``latitude-niche breadth hypothesis''. If the scaling of
-  specialisation with species richness is weaker at the tropics (i.e., if
+  If this is the case, it may still be possible to uncover effects of latitude
+  on specialisation by examining the shape of the scaling relationship between
+  specialisation and species richness over changing latitude.  By testing
+  whether latitude affects the scaling of each property with species richness,
+  we test for the effects of latitude on specialisation predicted by the
+  ``latitude-niche breadth hypothesis'' (Fig.~\ref{concept}).  If the scaling
+  of specialisation with species richness is weaker in the  tropics (i.e., if
   species gain fewer links, predators, or prey as the size  of the network
@@
   the scaling of specialisation with species richness does not  vary over
-  latitude, this will support the hypothesis that niches are similarly-sized
-  worldwide but that there is a broader niche space in the tropics.
+  latitude, this will indicate that niches are similarly-sized worldwide but
+  that there is a broader niche space in the tropics. Additionally, as food
+  webs describing different ecosystem types may differ in their
+  topology~\cite{Dunne2004,Shurin2006}, we also explored the differences in
+  scaling relationships across ecosystem types. Here, we use three measures of
+  specialisation; mean links per species, mean generality (number of prey),
+  and mean vulnerability (number of predators).
 
@@
     possible or, where study sites were described but exact coordinates were not
-    given, obtained estimated coordinates using Google Earth~\citep{GoogleEarth}.
-    We then divided the species in each web into basal resources (those species with
-    consumers but no prey), top predators (those species with prey but no predators),
-    and intermediate consumers (species with both predators and prey, including cannibalistic
-    species).
+    given, obtained estimated coordinates using Google Earth~\cite{GoogleEarth}.
+    If a range of latitudes (e.g. $42-49^{\circ}N$) was provided, we used the midpoint
+    of this range. We grouped food webs by ecosystem type (stream, N=71; lake, N=47; marine, 
+    N=28; estuarine, N=18; and terrestrial, N=31) according to their designation in 
+    previous aggregations of food webs (i.e.,~\cite{GlobalWeb,Riede2011,Dunne2013}).
 
@@
     is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
-    Many analyses of food-web structure attempt to reduce this variation by aggregating species with identical predator and prey
-    sets to form ``trophic species'' webs ~\citep{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
+    Many analyses of food-web structure attempt to reduce this variation by using food webs comprised of ``trophic
+    species'' --aggregations of species with identical sets of predators and prey-- rather than  
+    species \emph{per se}~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
     is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
-    species with identical sets of interactions. We therefore analysed both original and trophic-species versions
+    species with identical sets of interactions. We therefore analysed both original (i.e., without aggregating 
+    any species) and trophic-species (i.e., after aggregating species with identical predators and prey) versions
     of the dataset; in each case using the number of species and 
-    links in each web to calculate the mean link density (number of links per species), mean generality 
+    feeding links in each web to calculate the mean link density (number of links per species), mean generality 
     (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
     The version of the dataset used did not qualitatively change the results, suggesting that
-    the scaling relationships between species richness, other food-web properties, and latitude are very 
-    similar whether or not redundant species are included. For simplicity, here we present only
-    the results for the original webs.
+    the scaling relationships between species richness and specialisation across ecosystem type and latitude are very 
+    similar whether or not species with identical sets of predators and prey are included. For simplicity, 
+    here we present only the results for the original webs.
 
-  \subsection*{Scaling Relationships with S}
+  \subsection*{Gradients over Latitude}
+
+    To put our dataset in the context of other research on latitudinal gradients in species richness,
+    we first examined simple linear relationships between latitude and each of 
+    species richness, links per species, generality, and vulnerability. We fit models of the form
+
+    \begin{equation}
+    \label{Latfull}
+    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
+    \end{equation}
+
+    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
+    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
+    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
+    marine, lake, and terrestrial networks with estuarine
+    networks corresponding to $E_{i}=0$) and $\epsilon_{i}$ is a residual error term. 
+    We next calculated the AIC
+    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
+    using the R~\cite{R} function dredge from package MuMIn~\cite{MuMIn}. 
+    Simplified models were obtained by
+    systematically removing all possible combinations of terms from the full model.
+    The best-fitting model was then determined to be the model with the fewest terms 
+    where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
+
+  \subsection*{Scaling Relationships with Species Richness}
 
     The scaling relationship between link density ($Z$) and species richness ($S$)
-    has been shown to be a power law~\citep{Riede2010} of the form
+    has been shown to be a power law~\cite{Riede2010} of the form
 
@@
 
-    \noindent As the two forms imply a statistical fit to the data to different error 
+    \noindent As the two forms imply a statistical fit of the data to different error 
     distributions, neither of which has strong
-    \emph{a priori} justification in our dataset, we followed the recommendations in~\citet{Xiao2011}
+    \emph{a priori} justification in our dataset, we followed the recommendations in~\cite{Xiao2011}
     to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
@@
 
-    We then simplified each model. To do this, we calculated the AIC of the
-    maximal model as well as the AIC's of a suite of candidate simplified
-    models identified using the R~\citep{R} function dredge from package
-    MuMIn~\citep{MuMIn}.  Simplified models were obtained by systematically
-    removing all possible combinations  of terms from the full model with the
-    restriction that species richness was retained in all reduced models. The
-    best-fitting model was then determined to be the model with the fewest
-    terms  where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
-    % If several models shared the fewest
-    % number of terms  and had $\Delta$AIC\textless2, the model with the lowest
-    % AIC in that set was chosen as the best-fit model.
+    We then simplified versions of model~\ref{LogLat} for link density, generality, and vulnerability following the procedure described above.
+    As a supplemental check to ensure that variation in sampling effort
+    across food webs was not responsible for the trends we observed, we then
+    repeated our analyses using jackknifed data sets in which we 1) sequentially
+    removed each food web in the dataset and 2) sequentially removed sets of food webs
+    that shared a common author. The first jackknife essentially controls for the
+    influence of any single outlier, while the second controls for the influence
+    of particular research groups, some of which contributed large numbers of food
+    webs (up to 27) to the dataset. Parameter estimates for the simplified models 
+    varied very little across either jackknife test (see \emph{Appendix S3} for details),
+    indicating that the trends we observed were not due to either strong outliers or
+    to substantial differences in sampling effort across research groups.
 
@@
 
-  Link density, generality, and vulnerability were strongly and positively
-  correlated ($R^2$=0.891 for link density and generality,
-  $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.890
-  for generality and vulnerability). Each property 
-  increased with increasing
+  Link density (mean number of feeding links per species), generality (mean
+  number of prey per species), and vulnerability (mean number of predators per
+  species) were strongly and positively correlated ($R^2$=0.891 for link
+  density and generality, $R^2$\textgreater0.999 for link density and
+  vulnerability, and $R^2$=0.890 for generality and vulnerability). Contrary
+  to the expected latitudinal gradient, the best-fit version of
+  equation~(\ref{Latfull}) did not include a significant
+  effect of latitude on species richness for any ecosystem type. Further, there were no significant
+  relationships between link density, generality, or vulnerability with
+  latitude for any ecosystem type.
+
+  Each measure of specialisation increased with increasing
   species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
   $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
-  Fig~\ref{props_v_lat}).For estuarine, marine, and terrestrial food webs the
+  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
@@
   The tendency of food-web structure to exhibit scaling relationships with
-  species richness has been well-established~\citep{Dunne2004,Riede2010}. As
+  species richness has been well-established~\cite{Dunne2004,Riede2010}. As
   species richness in particular is also known to vary systematically over
-  latitude~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009},
+  latitude~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009},
   intuitively one might suspect that any relationship between food-web
   properties such as generality might be due to the latitudinal gradient in
-  species richness. In this dataset, however, we did not find overall
-  latitudinal gradients in species richness, links per species,generality,
-  vulnerability, or the proportions of food webs accounted for by basal
-  resources, intermediate consumers, and top predators, except in lake and
-  stream food webs where the proportions of top predators tended to decrease
-  towards the poles  (see \emph{Appendix S3} for details).
+  species richness. In this dataset, however, we found no evidence to support
+  latitudinal gradients in species richness, links per species, generality, or
+  vulnerability.
 
@@
   studies. This could result in food webs describing species-rich tropical
-  communities omitting more species and links than species-poor arctic
-  communities. In addition, it is worth noting that gradients in species
-  richness are generally measured for a single taxonomic group at a
-  time~\citep{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is possible
-  that these taxa are not well-represented in our food webs and that the
-  dominant taxa in them do not have an underlying latitudinal gradient in
-  richness.In either case, the lack of a strong association between species
-  richness and latitude in any ecosystem type means that any effect of
-  latitude on other scaling relationships is not being driven by an underlying
-  latitudinal gradient in species richness. The lack of confounding effects of
-  latitude allows us to more clearly assess effects of latitude on scaling
-  with species richness and proportions of species in different trophic
-  levels.
+  communities omitting more species and links than studies of species-poor
+  arctic communities if research groups spend similar person-hours assembling
+  webs and can observe similar numbers of species and links per person-hour.
+  In addition, it is worth noting that gradients in species richness are
+  generally measured for a single taxonomic group at a
+  time~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is
+  possible that these taxa are not well-represented in our food webs and that
+  the dominant taxa that are represented do not have an underlying latitudinal
+  gradient in richness. In either case, the lack of a strong association
+  between observed species richness and latitude in any ecosystem type in our dataset
+  means that any effect of latitude on other scaling relationships is not being driven by
+  the scaling of specialisation with species richness in our food webs. This is fortunate since
+  the lack of confounding effects of latitude allows us to more clearly assess
+  effects of latitude on scaling with species richness.
 
@@
   systematically with temperature and productivity but that the niche space
-  might be larger in species-rich communities~\citep{Davies2007}. Rather than
+  might be larger in species-rich communities~\cite{Davies2007}. Rather than
   niche space depending on temperature and productivity, it may be that species
-  diversity itself affects the niche space available to species (although climate
-  may affect speciation rates and therefore the diversity in a region~\citep{Currie2004}). 
+  diversity itself affects the biotic niche space available to species (although climate
+  may affect speciation rates and therefore the diversity in a region~\cite{Currie2004}). 
   For example, as the plant diversity of a community increases both the 
@@
   in high-latitude lakes. These trends are consistent with the hypothesis that
-  greater stability in the tropics leads to narrower niches~\citep{Vazquez2004}
-  and a higher proportion of specialists. This may be partly due to high-latitude 
-  species tending to switch between different seasonally-available 
-  prey~\citep{Magalhaes1993,Wilhelm1999,Isaac2012} while tropical
-  freshwater ecosystems may have more stable composition.
+  greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
+  and a higher proportion of specialists.
 
-  The scaling of link density, generality and vulnerability with proportions
-  of species at different trophic levels, however, did not differ between
-  lakes and most other food webs. Indeed, there was comparatively little
-  variation in scaling with the trophic-level breakdown of a web across
-  ecosystem types. Nevertheless, the negative relationships between the
-  proportion of top predators in a web and link density and vulnerability were
-  weaker (i.e., the scaling exponent was more strongly negative) in low-latitude 
-  stream ecosystems. This may imply that top predators in high-latitude 
-  streams tend to be more generalist than their low-latitude
-  equivalents~\citep{Winemiller2008}, perhaps due to prey-switching during
-  seasonal food shortages~\citep{Magalhaes1993}. More generally, the lack of
-  correspondence between the scaling of food-web properties with species
-  richness and with proportions of species at each trophic level suggests that
-  the size and trophic breakdowns of a community can each provide different
-  information~\citep{Downing2002}.
+  That freshwater food webs supported the hypothesis of narrower niches in the
+  tropics --while other ecosystem types did not-- is noteworthy given that
+  these ecosystems (especially streams) are known for being highly variable
+  and that seasonal variability is one of the proposed drivers of the
+  latitude-niche breadth hypothesis~\cite{Vazquez2004}. Both streams and lakes
+  can experience severe changes in water temperature and volume (e.g., floods,
+  drying, freezing) that remove food or other resources (notably oxygen during
+  freezing events)~\cite{Winterbourn1997,Meding2001}. These events are often
+  linked to seasonal events such as snowmelts or summer
+  drought~\cite{Winterbourn1997}). Further, both temperate streams and lakes
+  tend to experience seasonal strong pulses of allochthonous inputs (e.g.,
+  fallen leaves, terrestrial
+  invertebrates~\cite{Nakano2001,Lennon2004,Zeng2008}. These trends combined
+  mean that, relative to estuarine and marine communities, freshwater food 
+  webs may experience high turnover in both community composition and 
+  productivity~\cite{Tilzer1988,Magalhaes1993,Baird1989}. Notable exceptions from the above
+  trends are New Zealand stream communities (representing 31 of the 71 stream
+  food webs in our dataset), which experience unpredictable flooding and
+  drying throughout the year and do not receive seasonally pulsed
+  subsidies~\cite{Winterbourn1997,Winterbourn1981}. However, as this subset of
+  webs is very tightly grouped in latitude ($44.64-46.41^{\circ}$S, within an
+  overall range of $23.00-69.02^{\circ}$ for stream communities), it is unlikely that they have greatly
+  influenced our results (see also \emph{Appendix S3}). Moreover, just as in
+  highly-variable communities where said variation is more seasonal, New
+  Zealand communities are dominated by ecological
+  generalists~\cite{Winterbourn1997,Winterbourn1981} implying that they appear
+  to fit the general pattern of streams worldwide.
+
+  Importantly, while terrestrial communities are also strongly seasonal at
+  high latitudes and can receive significant allochthonous
+  inputs~\cite{Nakano2001}, terrestrial consumers tend to be
+  morphologically specialised for feeding on particular prey~\cite{Liem1990}.
+  This means that primarily gape-limited aquatic consumers tend to be more
+  generalist across all types of aquatic habitats than terrestrial 
+  consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data (
+  $\mu_Aquatic$>=5.47, $\mu_Terrestrial$=3.82; $p$=0.007 for $\mu_Aquatic$\textgreater$\mu_Terrestrial$). 
+  The key to this argument is therefore whether freshwater ecosystems experience
+  more severe seasonal variation than marine and estuarine ecosystems. Although
+  we are not aware of any study explicitly comparing seasonal variation in
+  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
+  ecosystems are indeed likely to experience more severe changes because of their small size.
+  While oceans and estuaries certainly vary in terms of water temperature and
+  nutrients over the course of a year~\cite{Baird1989}, these changes are likely to be slower
+  and milder than in freshwaters because marine and estuarine communities are buffered 
+  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
+  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
+  in non-marine communities~\cite{Field1998}. Thus suggests that niche breadths may also be 
+  more variable over the course of the year.
 
@@
   webs in different habitat types and that freshwater food webs in particular
-  may be strongly affected by seasonal variation. In addition, different
+  may be strongly affected by seasonal variation. Freshwater food webs also
+  appear to have different predator-prey biomass ratios than other ecosystem
+  types~\cite{Riede2011}; although it is not clear whether these ratios are related
+  to seasonality, this could be a promising avenue for future research. In addition, different
   relationships between latitude and niche breadth in different habitat types
-  goes some way towards explaining the equivocal support for the opposing
-  hypotheses of narrower niches in the tropics~\citep{Vazquez2004} and broader
-  niche space in the tropics~\citep{Davies2007}; both have merit but appear to
-  apply to different systems.
+  go some way towards explaining the equivocal support for the opposing
+  hypotheses of narrower niches in the tropics~\cite{Vazquez2004} and broader
+  niche space in the tropics~\cite{Davies2007}. Our study indicates that both 
+  have merit but would appear to apply to different systems.
 
@@
   Food webs used in this study were retrieved from the University of Canberra's 
-  GlobalWeb database (\citealp{GlobalWeb}; \emph{www.globalwebdb.com}) and from
-  two papers (\citealp{Riede2011}; \emph{http://dx.doi.org/10.1111/j.1461-0248.2010.01568.x}
-  and \citealp{Dunne2013}; \emph{http://dx.doi.org/10.1371/journal.pbio.1001579}). Original sources for the
+  GlobalWeb database (\cite{GlobalWeb}; \emph{www.globalwebdb.com}) and from
+  two papers (\cite{Riede2011}; \emph{http://dx.doi.org/10.1111/j.1461-0248.2010.01568.x}
+  and \cite{Dunne2013}; \emph{http://dx.doi.org/10.1371/journal.pbio.1001579}). Original sources for the
   food webs are given in \emph{Appendix S1}.
+
+\section*{Competing interests}
+
+  We have no competing interests.
+
+\section*{Authors' contributions}
+
+  ARC, DBS, and TNR designed the study, ARC collected
+  published data, performed the analyses, and wrote the
+  first draft. DBS and TNR substantially revised the article;
+  all authors approved the final version.
 
@@
   We thank members of the Romanuk, Stouffer, and Tylianakis labs for their comments on
-  the manuscript.
+  the manuscript. We also thank Angus McIntosh for valuable discussion on stream food webs and Matthias Schleuning, Robby Stoks, and one anonymous reviewer for their insightful questions.
+
+\section*{Funding}
   This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
-  graduate scholarship (to ARC).
+  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
+  Rutherford Discovery Fellowship, both administered by the Royal Society of New Zealand 
+  (to DBS), and an NSERC Discovery Grant (to TNR).
 
 \newpage
-\bibliographystyle{jae}%Compile with jae.bst style file
-\bibliography{noISN}% your .bib file(s)
+\bibliographystyle{prsb}
+\bibliography{abbreviated}
 
-% \end{spacing}
 \newpage
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
+% \centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
+\caption{In A) we show the known scaling relationship between link density (links per species) and 
+species richness. This scaling relationship is a power law and therefore linear in a log-log plot.
+In B) we show two versions of the latitudinal-niche breadth hypothesis that have been proposed to
+explain this gradient. Hypothesis 1 posits that greater environmental stability in the tropics will 
+allow species to evolve narrower niches (indicated by parabolas) than those at the poles. Hypothesis 2 
+suggests that species will have constant niche sizes over latitude but that greater primary productivity 
+in the tropics creates a larger niche space such that each species still occupies a smaller proportion 
+of the total niche space. These two hypotheses have different implications for the scaling of food-web 
+properties such as the number of feeding links per species with species richness. C) If hypothesis 1 is 
+true, then the exponent of the scaling relationship between link density and species richness should 
+be larger towards the poles, where each additional species in the food-web will have a larger niche 
+(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this distribution should 
+not vary significantly over latitude.}
+\label{concept}
+\end{figure}
+
+\begin{figure}[h]
+% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts.eps}}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
-relative to species richness and the proportions of basal resources (\% Basal), intermediate 
-consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
+relative to the species richness of a food web. Link density, generality,
 and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
 type. As these relationships take the form of power laws, we did this by dividing the food-web
-property (e.g. link density) by the predictor (e.g. \% Basal) raised to an exponent including the 
+property (e.g. link density) by species richness raised to an exponent including the 
 effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
-type and latitude. Note that in all cases estuarine food webs were used as the baseline 
+type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
 ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
-latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
+latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
 we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
-ecosystems as a baseline (black line, N=166 food webs). For a figure with the uncorrected values,
-see Fig.~\emph{S1}, \emph{Appendix S4}.}
+ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
+see Fig.~\emph{S7}, \emph{Appendix S4}.}
 \label{props_v_lat}
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
-\caption{Changes to the scaling of link density with species richness across ecosystem
+% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
+\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
 types and over latitude. We show the estimated scaling exponent for species richness (black
-line) with its 95\% confidence interval (in grey), based on N=166 empirical food webs.
-Latitude is given in degrees from the equator regardless of direction. The
-behaviour of exponents for the scaling of generality and vulnerability with
-species richness was very  similar to those for link density, except for the
-scaling of generality in streams where  the size of the exponent increased
-towards the poles. See Fig.~\emph{S2, Appendix 5} for  all scaling
-relationships.} \label{S} \end{figure}
-
-\begin{figure}[h]
-% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
-\caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
-consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
-we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
-on N=166 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
-The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
-proportion was very similar to those of the scaling relationships with link density, except for the 
-scaling of generality with the proportion of top predators where there was no effect of latitude on the 
-size of the exponent in any ecosystem type. See Figs.~\emph{S3-S5, Appendix 5} for all scaling relationships.}
-\label{BIT}
-\end{figure}
+line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
+Latitude is given in degrees from the equator regardless of direction.} \label{S} \end{figure}
 

### 2018-07-20 code/TL_marginal_latitude_corrected.py

@@ -1,0 +1,256 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+# import nose
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+#from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+
+# Ranges of the parameters
+weight_min=0.1
+weight_max=2800
+prey_gen_min=0
+prey_gen_max=10
+
+ecotypes=['Estuary','Lake','Marine','Stream','Terrestrial']
+
+def linereader(prop,TL,form):
+  linefile=open('../'+form+'/proportions/marginals/'+prop+'_'+TL+'_marginal_corrected.tsv','r')
+  lines={}
+  for ecotype in ecotypes:
+    lines[ecotype]={'main':[],'upper':[],'lower':[]}
+
+  for line in linefile:
+    if line.split()[0] != '"Latitude"':
+      s0=float(line.split()[1])
+      marginal=float(line.split()[2])
+      upper=float(line.split()[3])
+      lower=float(line.split()[4])
+
+      marine_m=float(line.split()[5])
+      marine_u=float(line.split()[6])
+      marine_l=float(line.split()[7])
+
+      lake_m=float(line.split()[8])
+      lake_u=float(line.split()[9])
+      lake_l=float(line.split()[10])
+
+      lines['Marine']['main'].append((s0,marine_m))
+      lines['Marine']['upper'].append((s0,marine_u))
+      lines['Marine']['lower'].append((s0,marine_l))
+
+      lines['Lake']['main'].append((s0,lake_m))
+      lines['Lake']['upper'].append((s0,lake_u))
+      lines['Lake']['lower'].append((s0,lake_l))
+
+      lines['Estuary']['main'].append((s0,marginal))
+      lines['Estuary']['upper'].append((s0,upper))
+      lines['Estuary']['lower'].append((s0,lower))
+
+
+      if prop=='Gen':
+
+        stream_m=float(line.split()[11])
+        stream_u=float(line.split()[12])
[…]

### 2018-07-20 code/byTL_Models_errorwebs.R

@@ -231,8 +231,8 @@ write.table(summary(obs_Vul)$coefficients,file=paste(outdir,'coefficients/Vul_ob
 ####################   Calculate marginal effect of latitude in each ecotype
 
 if(infile=='../mod_data/summary-properties_corrected_webs.tsv'){
-  outdir='../updated/mod_data/'  } else {
-    outdir=paste('../updated/non_TS/',format,'/',sep='')     }
+  outdir='../mod_data/'  } else {
+    outdir=paste('../non_TS/',format,'/',sep='')     }
 
 source("marginal_CIs_nonTS_errorwebs.R") # Same best-fit models for both web forms 
 

### 2018-07-23 code/TL_observedfits_corrected.py
roundup of changes with corrected LS

@@ -41,12 +41,21 @@ def datareader(rawdatafile,TL,Bformat):
       GenSD=float(line.split('\t')[10])
       Vul=float(line.split('\t')[11])
       VulSD=float(line.split('\t')[12])
-      SWTL=line.split('\t')[13]
-      B=float(line.split('\t')[14])
-      H=float(line.split('\t')[15])
-      I=float(line.split('\t')[16])
+      Path=line.split('\t')[13]
+      Chain=line.split('\t')[14]
+      SWTL=line.split('\t')[15]
+      Clus=line.split('\t')[16]
+      B=float(line.split('\t')[17])
+      H=float(line.split('\t')[18])
+      I=float(line.split('\t')[19])
       I=I+H # Include the herbivores as intermediates
-      T=float(line.split('\t')[17])
+      T=float(line.split('\t')[20])
+
+      # B=float(line.split('\t')[15])
+      # H=float(line.split('\t')[16])
+      # I=float(line.split('\t')[17])
+      # I=I+H # Include the herbivores as intermediates
+      # T=float(line.split('\t')[18])
 
       for response in ['LS','Gen','Vul']:
         points[response].append((eval(TL),eval(response)))
@@ -55,7 +64,7 @@ def datareader(rawdatafile,TL,Bformat):
   return points
 
 def fixed_reader(coefffile):
-  # print coefffile
+  print coefffile
   fixed_effects={}
   f=open(coefffile,'r')
   for line in f:
@@ -96,11 +105,11 @@ def heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat):
       LS=float(line.split('\t')[7])
       Gen=float(line.split('\t')[9])
       Vul=float(line.split('\t')[11])
-      B=float(line.split('\t')[14])
-      H=float(line.split('\t')[15])
-      I=float(line.split('\t')[16])
+      B=float(line.split('\t')[15])
+      H=float(line.split('\t')[16])
+      I=float(line.split('\t')[17])
       I=H+I
-      T=float(line.split('\t')[17])
+      T=float(line.split('\t')[18])
 
       # Correct the observed property based on latitude and ecotype effects
 
[…]

### 2018-07-23 code/byTL_Models_errorwebs.R

@@ -3,13 +3,13 @@
 library(lmerTest)
 library(MuMIn)
 
-for(infile in c('../mod_data/summary-properties_corrected_webs.tsv','../non_TS/summary-properties_corrected_webs.tsv')){
+for(infile in c('../non_TS/summary-properties_corrected_webs.tsv','../mod_data/summary-properties_corrected_webs.tsv')){
 
 format='proportions' # e.g. Basal is %Basal rather than # of basal resources
 # format='numbers' # I tried both ways initially.
 
 power_analysis=FALSE
-by_TL=FALSE
+by_TL=TRUE
 # For proportions and numbers, everything is log-normal.
 
 # Format the data file
@@ -86,17 +86,11 @@ if(infile=='../mod_data/summary-properties_corrected_webs.tsv'){
   outdir='../mod_data/'  } else {
     outdir='../non_TS/'     }
 
-# # Calculate the by-TL models # Has not been updated.
-# if(by_TL==TRUE){
-# if(format=='proportions'){
-#   source('property_models_proportions.R')
-#   save.image(file=paste(outdir,'proportion_Models.RData',sep=''))
-
-# } else {
-#   source('property_models_numbers.R')
-#   save.image(file=paste(outdir,'number_Models.RData',sep=''))
-# }
-# }
+# Calculate the by-TL models # Has not been updated.
+if(by_TL==TRUE){
+  source('property_models_proportions.R')
+  save.image(file=paste(outdir,'proportion_Models.RData',sep=''))
+}
 
 # Do the power analyses - all same as previous files
 if(power_analysis==TRUE){
@@ -112,49 +106,55 @@ if(infile=='../non_TS/summary-properties_corrected_webs.tsv'){
 # Eliminate the redundant authors (those that always and only occur with another author) prior to jackknifing.
 source('redundant_authors.R')
 
-# Jackknifing by authors (slightly harder)
-removals=matrix(nrow=58,ncol=2,data=NA)
+# Only jackknife the non-TS version.
+if(infile=='../non_TS/summary-properties_corrected_webs.tsv'){
+  # Jackknifing by webs (easy)
+  for(i in 1:nrow(olddata)){
+    newdata=olddata[-i,]
+    name=olddata$Web[i]
 
-# Jackknifing by webs (easy)
-for(i in 1:nrow(olddata)){
[…]

### 2018-07-23 code/food_web_properties_errorwebs.py

@@ -141,7 +141,7 @@ def food_web_properties(directory,item,G,predprey,spp,preddict,preydict,linkdict
   I=[]
 
   # Simplest way to get LS
-  LS=Decimal(L)/Decimal(N)
+  LS=2*Decimal(L)/Decimal(N)
   C=Decimal(L)/Decimal(N**2)
 
   a=0
@@ -215,7 +215,7 @@ def food_web_properties(directory,item,G,predprey,spp,preddict,preydict,linkdict
     sys.exit()
 
   stroutput=[]
-  outputs = [int(N),int(L),float(C),float(LS),float(Gen),float(Vul),basal,herbs,inter,top] 
+  outputs = [int(N),int(L),float(C),float(meanL),float(Gen),float(Vul),basal,herbs,inter,top] 
   for thing in outputs:
     stroutput.append(str(thing))
   return stroutput 

### 2018-07-23 code/jackknife_display_figure.py

@@ -543,23 +543,24 @@ def main():
 
   weblist=set()
   for fil in files:
-    if 'web' in fil and 'Lakeweb' not in fil:
-      weblist.add(fil.split('.web')[0])
-      webfiles.append(fil)
-      if 'LS' in fil:
-        LS_webfiles.append(fil)
-      elif 'Gen' in fil:
-        Gen_webfiles.append(fil)
+    if '_corrected' not in fil: # Originals only, please
+      if 'web' in fil and 'Lakeweb' not in fil:
+        weblist.add(fil.split('.web')[0])
+        webfiles.append(fil)
+        if 'LS' in fil:
+          LS_webfiles.append(fil)
+        elif 'Gen' in fil:
+          Gen_webfiles.append(fil)
+        else:
+          Vul_webfiles.append(fil)
       else:
-        Vul_webfiles.append(fil)
-    else:
-      authorfiles.append(fil)
-      if 'LS' in fil:
-        LS_authorfiles.append(fil)
-      elif 'Gen' in fil:
-        Gen_authorfiles.append(fil)
-      else:
-        Vul_authorfiles.append(fil)
+        authorfiles.append(fil)
+        if 'LS' in fil:
+          LS_authorfiles.append(fil)
+        elif 'Gen' in fil:
+          Gen_authorfiles.append(fil)
+        else:
+          Vul_authorfiles.append(fil)
 
   # print sorted(weblist)
   for prop in ['Vul','Gen','LS']:

### 2018-07-23 code/jackknife_display_figure_corrected.py

@@ -1,0 +1,597 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+# import nose
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText, DrawLine
+
+#from PyGrace.Extensions.distribution import CDFGraph, PDFGraph
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+from PyGrace.Extensions.latex_string import LatexString, CONVERT
+colors=ColorBrewerScheme('Paired')
+colors.add_color(120,120,120,'grey')
+
+redundants={
+  'Egloff':['X38_coauthors','Richardson','Coauthors'],
+  'Abele':['Simberloff'],
+  'Ali_Dawah':['Banasek.Richter','Berlow','Bersier','Blanchard','Brey',
+              'Brose','Cushing','Dell','Harper.Smith','Jacob','Knapp',
+              'Ledger','Memmot','Mintenbeck','Pinnegar','Rall','Ruess','Ulrich','Yodzis'],
+  'Aloisio':['Carvalho'],
+  'Althaus':['Bax','Bulman','He','Williams_A'],
+  'Amundsen':['Klemetsen','Knudsen','Kristoffersen','Primicerio'],
+  'Antezana':['Cornejo.Donoso'],
+  'Arreguin_Sanchez':['Zetina_Rejon'],
+  'Baeta':['Niquil'],
+  'Bailey.Watts':['Bindloss','Holden','Smith_I'],
+  'Beaney':['Huxham','Raffaelli'],
+  'Bradstreet':['Cross'],
+  'Bretschko':['Gollmann','Pechlaner','Pfeifer','Tilzer','Weissenbach'],
+  'Briand':['Newman'],
+  'Brittain':['Larsson','Lien','Lillehammer','Tangen'],
+  'Britton':['Kowalczewski','Lack','Matthews','McDonald'],
+  'Brown':['Hechinger'],
+  'Burgis':['Ganf','McGowan','Viner'],
+  'Canuel':['Douglass','Emmett_Duffy'],
[…]

### 2018-07-23 code/marginal_CIs_nonTS_errorwebs.R

@@ -25,6 +25,14 @@ S_CIs <- function(model){
       marine_upper <- marine_m + 1.64*marine_se
       marine_lower <- marine_m - 1.64*marine_se
 
+      terr_m <- marginal + betas["log(Species):Terr"]
+      terr_se <- sqrt(se^2 + 
+          covar["log(Species):Terr","log(Species):Terr"] 
+          +2*covar["log(Species):Terr","log(Species)"]
+          +2*lat*covar["log(Species):Terr","log(Species):Latitude"])
+      terr_upper <- terr_m + 1.64*terr_se
+      terr_lower <- terr_m - 1.64*terr_se
+
       if(model=="LS_min" | model=="Vul_min"){ # No stream terms
 
         if(model=="LS_min"){
@@ -89,3 +97,258 @@ S_CIs <- function(model){
       }
       return(results)
     }
+
+B_CIs <- function(model){
+      modname=eval(as.name(model))
+      betas=summary(modname)$coefficients[,1]
+      covar=vcov(modname)
+    
+      lat=seq(0,90,length.out=200)
+
+      # All have Species:Lakeweb, Species:Marine
+      # All have Species:Latitude:Lakeweb
+      # Gen_min also has Species:Stream, Species:Latitude:Stream
+
+      marginal <- betas["log(Basal)"]+lat*betas["log(Basal):Latitude"]
+
+      se <- sqrt(covar["log(Basal)","log(Basal)"]+2*lat*covar["log(Basal):Latitude","log(Basal)"]
+        +lat^2*covar["log(Basal):Latitude","log(Basal):Latitude"])
+
+      upper <- marginal + 1.64*se
+      lower <- marginal - 1.64*se
+
+      stream_m <- marginal + betas["log(Basal):Stream"]
+      stream_se <- sqrt(se^2 + 
+          covar["log(Basal):Stream","log(Basal):Stream"] 
+          +2*covar["log(Basal):Stream","log(Basal)"]
+          +2*lat*covar["log(Basal):Stream","log(Basal):Latitude"])
+      stream_upper <- stream_m + 1.64*stream_se
+      stream_lower <- stream_m - 1.64*stream_se
+
+      terr_m <- marginal + lat*betas["log(Basal):Latitude:Terr"] + betas["log(Basal):Terr"]
+      terr_se <- sqrt(se^2 + 
+        lat^2*covar["log(Basal):Latitude:Terr","log(Basal):Latitude:Terr"] 
[…]

### 2018-07-23 code/property_models_proportions.R

@@ -13,12 +13,12 @@
     ,na.action=na.fail))
     lbdredge=dredge(LS_B_full,rank=AIC)
     # Same in both infiles :)
-    if(infile=='../non_TS/summary-properties.tsv'){
-      # non-TS - updated 29/06/2015
+    if(infile=='../non_TS/summary-properties_corrected_webs.tsv'){
+      # Updated 22/07/2018
       LS_B_min=with(data,lm(log(LS)~log(Basal)
         +log(Basal):Latitude
-        +log(Basal):(Marine+Stream+Terr)
-        +log(Basal):Latitude:(Marine+Terr)
+        +log(Basal):(Stream+Terr)
+        +log(Basal):Latitude:Terr
         , na.action=na.fail   ))
       } else {       ### Probably wrong
       # TS - updated 29/06/2015
@@ -37,11 +37,11 @@
     +log(Intermediate):Latitude:(Stream+Lakeweb+Marine+Terr)
     ,na.action=na.fail))
     lidredge=dredge(LS_I_full,rank=AIC)
-    if(infile=='../non_TS/summary-properties.tsv'){
-      # TS, updated 29/06/2015
+    if(infile=='../non_TS/summary-properties_corrected_webs.tsv'){
+      # Updated 22/07/2018
       # The only major change so far.
       LS_I_min=with(data,lm(log(LS)~log(Intermediate)
-        +log(Intermediate):Stream, na.action=na.fail   ))
+        +log(Intermediate):(Stream*Latitude), na.action=na.fail   ))
       } else {  #updated 29/06/2015
       LS_I_min=with(data,lm(log(LS)~log(Intermediate)
         +log(Intermediate):Latitude
@@ -58,10 +58,10 @@
     +log(Toppreds):Latitude:(Stream+Lakeweb+Marine+Terr)
     ,na.action=na.fail))
     ltdredge=dredge(LS_T_full,rank=AIC)
-    if(infile=='../non_TS/summary-properties.tsv'){
-      # Updated 29/06/2015
+    if(infile=='../non_TS/summary-properties_corrected_webs.tsv'){
+      # Updated 22/07/2018
       LS_T_min=with(data,lm(log(LS)~log(Toppreds)
-        +log(Toppreds):(Lakeweb+Marine+Stream+Terr)
+        +log(Toppreds):(Lakeweb+Stream+Terr)
[…]

### 2018-07-23 manuscript/latitudepaper.tex
few more changes

@@
   number of prey per species), and vulnerability (mean number of predators per
-  species) were strongly and positively correlated ($R^2$=\st{0.891}\textbf{0.890} for link
+  species) were strongly and positively correlated ($R^2$=\st{0.891}0.915 for link
   density and generality, $R^2$\textgreater0.999 for link density and
-  vulnerability, and $R^2$=\st{0.890}\textbf{0.889} for generality and vulnerability). Contrary
+  vulnerability, and $R^2$=\st{0.890}0.912 for generality and vulnerability). Contrary
   to the expected latitudinal gradient, the best-fit version of
@@
   latitude for any ecosystem type.
-  % [[After correction: $R^2$=0.890 for link density and generality, $R^2$\textgreater0.999 for link density and vulnerability, and $R^2$=0.889 for generality and vulnerability.]]
-
-  % [[Coefficients are from LS_min, etc. Need to re-run for non_TS and TS webs, update with new minimum models.]]
 
   Each measure of specialisation increased with increasing
-  species richness ($\beta_0$=\st{0.637}\textbf{0.668}, $p$\textless0.001; $\beta_0$=\st{0.553}\textbf{0.689},
-  $p$\textless0.001; and $\beta_0$=\st{0.637}\textbf{0.668}, $p$\textless0.001, respectively;
-  Fig.~\ref{props_v_lat}). 
-  % [[After correction: ($\beta_0$=0.668, $p$\textless0.001; $\beta_0$=0.689, $p$\textless0.001; and $\beta_0$=0.668, $p$\textless0.001, respectively).]]
-  For estuarine, marine, and terrestrial food webs the
+  species richness ($\beta_0$=\st{0.637}0.691, $p$\textless0.001; $\beta_0$=\st{0.553}0.663,
+  $p$\textless0.001; and $\beta_0$=\st{0.637}0.698, $p$\textless0.001, respectively;
+  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
-  (\st{$\beta_{Latitude}$=-0.001, $p$=0.365 for link density;}
-  $\beta_{Latitude}$=\st{-0.001}\textbf{-0.002}, $p$=\st{0.535}\textbf{0.101 for generality; 
-  latitude was not retained in the best-fit models for link density or vulnerability}\st{and
-  $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability}; Fig.~\ref{S}). 
-  % [[After correction: latitude not included in LS_min or Vul_min. $\beta_{Latitude}$=-0.002, $p$=0.101 for generality]]
-  \st{In lake food webs, however, the scaling of each property was stronger towards
-  the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
-  $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
-  $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
+  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.212 for link density;
+  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.320 for generality; and
+  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.207 for vulnerability; Fig.~\ref{S}). In
+  lake food webs, however, the scaling of each property was stronger towards
+  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.037;
+  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.007; and
+  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.003, $p$=0.036, respectively). In stream food
   webs, generality increased more rapidly towards the poles
-  ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
+  ($\beta_{Latitude:Stream}$=\st{0.007, $p$=0.001}0.005, $p$=0.008) while link density and
   vulnerability did not vary with latitude (i.e., the interaction term 
-  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).}
-  In \textbf{lake and} stream food webs, however, the scaling of generality was stronger
-  towards the poles. This change in scaling was significant for streams but not for
-  lakes ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001\textbf{ and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively}).
-  % [[After correction: Link density and vulnerability scaled more strongly with species richness in lake food webs ($\beta_{Lake}$=0.057, $p$=0.024 and $\beta_{Lake}$=0.059, $p$=0.020, respectively).
-Generality scaled significantly more strongly towards the poles in streams and slightly (not significantly) more strongly towards the poles in lake food webs ($\beta_{Latitude:Stream}$=0.008, $p$\textless0.001 and $\beta_{Latitude:Lake}$=0.003, $p$=0.100, respectively).
-]]
-
-  % [[Very small changes with trophic species versions.]]
+  $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
 
@@
 \begin{figure}[h]
-\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_new.eps}}
-\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
+% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_new.eps}}
+\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_corrected.eps}}
+% # Zis vun is not korrekt.
+\caption{[[Should have cols for S, B, I, T and rows for LS/Gen/Vul; re-scaled values.]]
+Scaling relationships for re-scaled link density, generality, and vulnerability 
 relative to the species richness of a food web. Link density, generality,
@@
 %\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
-\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_updated.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
+% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_updated.eps}}
+\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_corrected.eps}}
+\caption{[[Also not correct. Should have cols for each env. type, rows for LS/Gen/Vul]]Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
 types and over latitude. We show the estimated scaling exponent for species richness (black

### 2018-07-23 code/combined_linedot_plot.py
recreated Fig. 2 that's in the published version

@@ -1,0 +1,308 @@
+import sys
+import os
+import re
+import random
+from decimal import *
+import math
+
+from PyGrace.grace import Grace
+from PyGrace.colors import RandomColorScheme, MarkovChainColorScheme, ColorBrewerScheme
+from PyGrace.dataset import SYMBOLS
+from PyGrace.Extensions.panel import Panel,MultiPanelGrace
+from PyGrace.drawing_objects import DrawText
+from PyGrace.axis import LINEAR_SCALE, LOGARITHMIC_SCALE
+
+from PyGrace.Extensions.colorbar import SolidRectangle, ColorBar
+from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
+
+# Think I want plots of the raw data (S, LS, G, V vs. lat) with slope lines
+# Plus predictions for LS, G, V vs S (with corrected obs.)
+# [[Redoing this with the new data, old files called are in comments]]
+
+
+def datareader(rawdatafile,TL,Bformat):
+
+  points={'LS':[],'Gen':[],'Vul':[]}
+
+  f=open(rawdatafile,'r')
+  i=1
+  for line in f:
+    if line.split('\t')[0]!='Web':
+      ecotype=line.split('\t')[1]
+      ecotype=ecotype.capitalize()
+      site=line.split('\t')[2]
+      Latitude=float(line.split('\t')[3])
+      S=int(line.split('\t')[4])
+      L=line.split('\t')[5]
+      C=line.split('\t')[6]
+      LS=float(line.split('\t')[7])
+      Gen=float(line.split('\t')[8])
+      Vul=float(line.split('\t')[9])
+      B=float(line.split('\t')[10])
+      H=float(line.split('\t')[11])
+      I=float(line.split('\t')[12])
+      T=float(line.split('\t')[13])
+
+      # B=float(line.split('\t')[15])
+      # H=float(line.split('\t')[16])
+      # I=float(line.split('\t')[17])
+      # I=I+H # Include the herbivores as intermediates
+      # T=float(line.split('\t')[18])
+
+      for response in ['LS','Gen','Vul']:
+        points[response].append((eval(TL),eval(response)))
+
+  f.close()
+  return points
+
+def fixed_reader(coefffile):
+  fixed_effects={}
+  f=open(coefffile,'r')
+  for line in f:
[…]

### 2018-07-23 manuscript/latitudepaper.tex
updated main text and figures

@@
 % \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_new.eps}}
-\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_corrected.eps}}
-% # Zis vun is not korrekt.
-\caption{[[Should have cols for S, B, I, T and rows for LS/Gen/Vul; re-scaled values.]]
+\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/STL_fitlines_nonts.eps}}
+\caption{
 Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_corrected.eps}}
-\caption{[[Also not correct. Should have cols for each env. type, rows for LS/Gen/Vul]]Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
+\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
 types and over latitude. We show the estimated scaling exponent for species richness (black

### 2018-07-23 code/TL_marginal_latitude_corrected.py

@@ -126,57 +126,22 @@ def plotter(prop,TL,ecotype,graph,form):
   main.symbol.shape=0
   main.line.configure(linestyle=1,color=1,linewidth=1)
 
+  return graph
+
+def format_graph(graph,prop,ecotype):
   graph.xaxis.bar.linewidth=1
   graph.yaxis.bar.linewidth=1
   graph.frame.linewidth=1
-
-  # graph.autoscale()
   graph.world.xmin=0
   graph.world.xmax=90
+  graph.world.ymin=0
+  graph.world.ymax=1.5
 
-  if TL=='S':
-    graph.world.ymin=0
-    graph.world.ymax=1.5
-    major=.5
-    prec=1
-  elif TL=='B':
-    prec=0
-    if form=='proportions':
-      graph.world.ymin=-1.25
-      graph.world.ymax=1
-      major=1
-    else:
-      graph.world.ymin=0
-      graph.world.ymax=.60000001
-      major=.2
-  elif TL=='I':
-    if form=='proportions':
-      graph.world.ymin=-1
-      graph.world.ymax=3
-      major=1
-      prec=0
-    else:
-      graph.world.ymin=-.4
-      graph.world.ymax=.80000001
-      major=.4
-      prec=1
-  else:
-    if form=='proportions':
-      graph.world.ymin=-2
-      graph.world.ymax=1
-      major=1
-      prec=0
-    else:
-      graph.world.ymin=-1
-      graph.world.ymax=1
-      major=.5
-      prec=1
-
-  graph.xaxis.ticklabel.configure(char_size=.75)
+  graph.xaxis.ticklabel.configure(char_size=.75,font='Times-Roman')
   graph.xaxis.tick.configure(major_linewidth=.5,minor_linewidth=.5,major_size=.6,minor_size=.4,major=30)
 
-  graph.yaxis.tick.configure(major=major,major_linewidth=.5,minor_linewidth=.5,major_size=.6,minor_size=.4)
-  graph.yaxis.ticklabel.configure(format='decimal',prec=prec,char_size=.75)
+  graph.yaxis.tick.configure(major=.5,major_linewidth=.5,minor_linewidth=.5,major_size=.6,minor_size=.4)
+  graph.yaxis.ticklabel.configure(format='decimal',prec=1,char_size=.75,font='Times-Roman')
 
   # Fancy-pants labelling
   if ecotype=='Estuary':
[…]

### 2018-07-23 code/TL_observedfits_corrected.py

@@ -95,21 +95,18 @@ def heatmappoints(rawdatafile,fixed,prop,ecotype,TL,Bformat):
     key='Species'
   f=open(rawdatafile,'r')
   for line in f:
-    # print line.split()
-    # sys.exit()
     if line.split()[0]!='Web':
       ecotype=line.split('\t')[1]
       ecotype=ecotype.capitalize()
       Latitude=float(line.split('\t')[3])
       S=float(line.split('\t')[4])
       LS=float(line.split('\t')[7])
-      Gen=float(line.split('\t')[9])
-      Vul=float(line.split('\t')[11])
-      B=float(line.split('\t')[15])
-      H=float(line.split('\t')[16])
-      I=float(line.split('\t')[17])
-      I=H+I
-      T=float(line.split('\t')[18])
+      Gen=float(line.split('\t')[8])
+      Vul=float(line.split('\t')[9])
+      B=float(line.split('\t')[10])
+      H=float(line.split('\t')[11])
+      I=float(line.split('\t')[12])
+      T=float(line.split('\t')[13])
 
       # Correct the observed property based on latitude and ecotype effects
 
@@ -235,10 +232,10 @@ def S_scaleplots(rawdatafile,outfile1,Bformat,predfolder):
     rawdata=datareader(rawdatafile,TL,Bformat)
     # if rawdatafile=='../non_TS/summary-properties.tsv':
     if rawdatafile=='../non_TS/summary-properties_corrected_webs.tsv':
-      fixed=fixed_reader('../non_TS/coefficients/'+prop+'_co.tsv')
+      fixed=fixed_reader('../non_TS/coefficients/'+prop+'_co_corrected.tsv')
       # fixed=fixed_reader('../updated/non_TS/coefficients/'+prop+'_co.tsv')
     else:
-      fixed=fixed_reader('../mod_data/coefficients/'+prop+'_co.tsv')
+      fixed=fixed_reader('../mod_data/coefficients/'+prop+'_co_corrected.tsv')
       # fixed=fixed_reader('../updated/mod_data/coefficients/'+prop+'_co.tsv')
 
     graph=grace.add_graph(Panel)
@@ -308,7 +305,7 @@ def S_scaleplots(rawdatafile,outfile1,Bformat,predfolder):
 
 def S_rawplots(rawdatafile,outfile1,Bformat,predfolder):
 
-  outfile=outfile1.split('.eps')[0]+'_observed.eps'  
[…]

### 2018-07-26 manuscript/supplement.tex
fixex figure in Appendix S5

--- 2015-09-08 manuscript/supplement.tex
@@
   and~\cite{Dunne2013}. Of the 358 food webs available
-  from~\cite{GlobalWeb}, 59 were rejected because their original source was
+  from~\cite{GlobalWeb}, 58 were rejected because their original source was
   unpublished or could not be retrieved. We further eliminated 13 source or
@@
   community), 8 plant-pollinator webs, 33 host-parasitoid webs, and 2 networks
-  describing competitive interactions. Finally, we eliminated 2 webs
-  describing  inferred interactions in an extinct community, 10 ``generalised
+  describing competitive interactions. Additionally, we eliminated 2 webs
+  describing  inferred interactions in an extinct community, 2 webs describing compartments rather than particular species,
+  11 ``generalised
   schemes'' that were not based on direct field data, and 4 webs where it was
@@
   the~\cite{GlobalWeb}  dataset, and the last web was derived from an
-  unpublished source. This gave us a database of 263 webs. As a measure of
+  unpublished source. This gave us a database of 263 webs. 
+  Some of these webs, as published, contained errors in species names or other formatting errors.
+We corrected these errors in order to match species arrayed along rows and columns (details in Table~\ref{S2}).
+As a measure of
   quality-control, we then eliminated any food web which did not have at least
@@
   which did not meet this requirement tended to be very small and poorly-resolved.
-  Our final sample size was thereby reduced to 196 food webs.
-
+  Our final sample size was thereby reduced to 225 food webs.
   % Tree hole and pitcher plant webs counted as "lakes", wetlands could be either lakesor streams depending on the study
@@
   exclusion. 
+  \clearpage
 
@@
         152   & 3 & \cite{Whittaker1984}    & terrestrial &       & No    & Source web \\
-        153   & 3 & \cite{Mayse1978}    & terrestrial & 40,06,38 N & Yes   &       \\
-        154   & 3 & \cite{Mayse1978}    & terrestrial & 39,56,41 N & Yes   &       \\
+        153   & 3 & \cite{Mayse1978}    & terrestrial & 40,06,38 N &   &     \\
+        154   & 3 & \cite{Mayse1978}    & terrestrial & 39,56,41 N &   &     \\
         155   & 3 & \cite{Askew1975}     & terrestrial &       & No    & Host-parasitoid web \\
@@
     \end{table}%
-
   \end{landscape}
-\newpage
+
+  \clearpage
+
+  \clearpage
+  \begin{center}
+    \begin{table}[h!]
+      \caption{Networks with corrections.
+Names are as in Table S1.
+All corrected webs were taken from~\cite{GlobalWeb}.
+Some links were coded as negative values, decimal values, or values other than 1 that were intended to convey additional information.
+All were re-coded as 1.
+In a few cases, entries of -1 indicated links that should not be included in the network (e.g., where primary producers would be interpreted as predators).
+These entries were changed to 0.
+Some webs contained missing column or row labels; these were inferred based on species ordering in the complete dimension.
+Some row or column labels contained sample sizes or life stage information missing from the other dimension, or contained typos in either row or column labels.
+These were removed such that row and column labels matched.
+In most webs, predators were given across columns and prey down rows.
+Where this was not the case, rows and columns were flipped.}
+      \label{S2}
+      {\footnotesize
+      \begin{tabular}{l | p{13cm}}
+      Web ID & Type of correction \\
+      \hline
+      18 & Corrected -1 entry to 1 \\
+      22 &  Corrected -1 entries to 1, -2 entries to 0 \\
+      23 & Corrected -1 entries to 1 \\
+      24 &  Corrected -1 entries to 1 \\
+      26 & Corrected decimal entries to 1, -1 entries to 1 \\
+      33 & Corrected decimal entries to 1 \\
+      37 & Corrected -1 entries to 1 \\
+      38 & Converting -1 entries to 1 \\
+      39 & Corrected species names \\
+      41 & Corrected species names \\
+      60 & Corrected species names \\
+      80 & Corrected species names \\
+      114 & Corrected -1 entry to 1 \\
+      117 & Corrected -1 entry to 1 \\
+      119 & Corrected -1 entries to 1 \\
+      120 & Corrected -1 entries to 1 \\
+      153 & Corrected -1 entries to 1 \\
+      154 & Corrected -1 entries to 1  \\
+      180 &  Corrected entries indicating a primary producer as predator to 0 \\
+      181 &  Corrected -1 entries to 1 \\
+      182 &  Corrected -1 entries to 1 \\
+      183 &  Corrected -1 entries to 1 \\
+      202 &  Corrected -1 entries to 1  \\
+      213 &  Corrected -1 entries to 1  \\
+      214 &  Corrected species names \\
+      215 &  Corrected species names \\
+      216 &  Corrected species names \\
+      217 &  Corrected species names \\
+      218 &  Corrected species names \\
+      219 &  Corrected species names \\
+      220 &  Corrected species names \\
+      221 &  Corrected species names \\
+      222 &  Corrected species names \\
+      223 &  Corrected species names \\
+      224 &  Corrected species names \\
+      225 &  Corrected species names \\
+      \hline
+      \end{tabular} }
+      \end{table}
+
+      \begin{table}
+      {\footnotesize
+      \begin{tabular}{l | p{13cm}}
+      Web ID & Type of correction \\
+      \hline
+      236 &  Corrected informative entries to 1; corrected species names \\
+      238 &  Corrected informative entries to 1 \\
+      240 &  Corrected informative entries to 1 \\
+      244 &  Corrected informative entries to 1 \\
+      246 &  Corrected informative entries to 1 \\
+      249 &  Corrected decimal entries to 1 \\
+      250 &  Corrected decimal entries to 1 \\
+      251 &  Corrected decimal entries to 1 \\
+      252 &  Corrected decimal entries to 1 \\
+      253 &  Corrected decimal entries to 1 \\
+      254 &  Corrected decimal entries to 1 \\
+      255 &  Corrected decimal entries to 1 \\
+      256 &  Corrected decimal entries to 1 \\
+      257 &  Corrected decimal entries to 1 \\
+      258 &  Corrected decimal entries to 1 \\
+      259 &  Corrected decimal entries to 1 \\
+      260 &  Corrected decimal entries to 1 \\
+      261 &  Corrected decimal entries to 1 \\
+      262 &  Corrected decimal entries to 1 \\
+      265 &  Corrected decimal entries to 1 \\
+      266 &  Corrected decimal entries to 1 \\
+      267 &  Corrected decimal entries to 1 \\
+      268 &  Corrected decimal entries to 1 \\
+      269 &  Corrected decimal entries to 1 \\
+      288 &  Corrected decimal entries to 1 \\
+      289 &  Corrected decimal entries to 1 \\
+      290 &  Corrected quantitative entries to 1 \\
+      291 &  Corrected quantitative entries to 1 \\
+      292 &  Corrected quantitative entries to 1 \\
+      293 &  Corrected quantitative entries to 1 \\
+      294 &  Corrected decimal entries to 1; flipped rows and columns \\
+      296 &  Corrected decimal entries to 1 \\
+      307 &  Corrected decimal entries to 1 \\
+      320 &  Corrected decimal entries to 1 \\
+      321 &  Corrected decimal entries to 1 \\
+      322 &  Corrected decimal entries to 1 \\
+      323 &  Corrected decimal entries to 1 \\
+      324 &  Corrected decimal entries to 1 \\
+      333 &  Corrected species names; corrected - entries to 1, + entries to 0, +/- entries 10 1; flipped rows and columns \\
+      339 &  Corrected decimal entries to 1; corrected species names \\
+      342 &  Corrected quantitative entries to 1; corrected species names \\
+      345 &  Corrected quantitative entries to 1 \\
+      350 &  Corrected quantitative entries to 1 \\
+      351 &  Corrected quantitative entries to 1 \\
+      357 &  Corrected quantitative entries to 1 \\
+      359 &  Corrected species names \\
+      \hline
+      \end{tabular} }
+    \end{table}
+  \end{center}
+\clearpage
 
@@
 
-% \subsection*{Appendix S4: Scaling relationships by trophic level}
-
-%   \subsubsection*{Methods}
-
-%     We were also interested in the ways that scaling
-%     relationships with species richness might
-%     be affected by changes to the distribution of species 
-%     among trophic levels. [[more justification of why]]
-%     To that end, we repeated our 
-%     analyses replacing species richness with the
-%     proportion of basal resources, proportion of 
-%     intermediate consumers, or proportion of top 
-%     predators. All model fitting procedures were identical 
-%     to those described for species richness. The model 
-%     simplicication procedure was similar to
-%     the procedure described for species richness, except 
-%     that in some cases there were multiple models with 
-%     $\delta$AIC\textless2 that shared the minimal degrees 
-%     of freedom. In these cases, we defined the 
-%     best-fitting model as the model with the lowest AIC in 
-%     the set of models with $\delta$AIC\textless2 and the 
-%     minimal degrees of freedom.
-
-%   \subsubsection*{Results}
-
-%     As with species richness, specialisation scaled with
-%     the numbers and proportions of species at each trophic
-%     level following a lognormal distribution.
-%     The relationships between latitude and the proportions of species at each
-%     trophic level were more complex than the flat relationship between latitude
-%     and species richness in this dataset.  The proportion of basal resources
-%     increased towards the poles in stream webs
-%     ($\beta_{Latitude:stream}$=0.011, $p$\textless0.001)  but did not vary
-%     with latitude in estuarine, marine, lake, or terrestrial  food webs
-%     ($\beta_{Latitude}$=0.001, $p$=0.080), while the proportion of
-%     intermediate consumers decreased towards the poles in all ecosystem types
-%     except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
-%     $\beta_{Latitude:Lake}$=0.005, $p$=0.016). The proportion of top predators
-%     in a food web,  meanwhile, decreased towards the poles in lake and  stream
-%     food webs but did not vary in other ecosystem types
-%     ($\beta_{Latitude}$=0.002, $p$=0.151;  $\beta_{Latitude:Lake}$=-0.006,
-%     $p$=0.001; and $\beta_{Latitude:stream}$=-0.007, $p$=0.006).
-
-%     Unlike species richness, only generality showed an overall increase with
-%     increasing proportions of basal resources in a web ($\beta_0$=0.019,
-%     $p$=0.859; $\beta_0$=0.383, $p$=0.001; and $\beta_0$=0.019, $p$=0.855 for
-%     link density, generality, and vulnerability, respectively;
-%     Fig.~\ref{TL_rescaled}). In each case, however, there were substantial
-%     effects of latitude on the scaling relationships. Thus, the scaling
-%     exponents for link density and vulnerability were negative for estuarine,
-%     lake, and stream communities and became more negative towards the poles
-%     ($\beta_{Latitude}$=-0.008, $p$\textless0.001 and $\beta_{Latitude}$=-0.008,
-%     $p$\textless0.001, respectively; Fig.~\ref{B}). For the scaling of link
-%     density and vulnerability in marine and terrestrial communities, the overall
-%     effect of latitude on scaling was positive ($\beta_{Latitude:Marine}$=0.011,
-%     $p$=0.020; $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001 and
-%     $\beta_{Latitude:Marine}$=0.011, $p$=0.020;
-%     $\beta_{Latitude:Terrestrial}$=0.016, $p$\textless0.001, respectively) such
-%     that there was weak scaling at most latitudes. In contrast, the scaling
-%     exponent of generality with the proportion of basal resources was positive
-%     near the equator and negative near the poles in estuarine, lake, and stream
-%     communities ($\beta_{Latitude}$=-0.010, $p$\textless0.001) while there was
-%     very little change in the scaling exponents for marine and terrestrial
-%     communities ($\beta_{Latitude:Marine}$=0.013, $p$=0.010;
-%     $\beta_{Latitude:Terrestrial}$=0.019, $p$\textless0.001).
-
-%     As with species richness, link density, generality, and vulnerability
-%     generally increased with the proportion of intermediate consumers in a web
-%     ($\beta_0$=0.771, $p$\textless0.001; $\beta_0$=0.349, $p$=0.235; and
-%     $\beta_0$=0.771, $p$\textless0.001 respectively; Fig.~\ref{TL_rescaled}). 
-%     The best-fit models for link density and vulnerability did not include
-%     any effect of latitude. In contrast, the strength of the scaling relationship
-%     for generality increased weakly towards the poles in estuarine, marine, and
-%     terrestrial food webs ($\beta_{Latitude}$=0.008, $p$=0.204) but decreased 
-%     towards the poles in lakes and streams ($\beta_{Latitude:Lake}$=-0.021, $p$=0.018
-%     and $\beta_{Latitude:Stream}$=-0.035, $p$=0.001; Fig~\ref{I}).
-
-%     In contrast to the generally positive scaling relationships above, link
-%     density, generality, and vulnerability decreased as the proportion of top
-%     predators increased ($\beta_0$=-0.532, $p$\textless0.001; $\beta_0$=-0.454,
-%     $p$\textless0.001; and $\beta_0$=-0.532, $p$\textless0.001 respectively;
-%     Fig~\ref{TL_rescaled}). For estuarine, lake, and marine food webs the
-%     strength of this scaling did not vary significantly with latitude
-%     ($\beta_{Latitude}$=-0.001, $p$=0.481 for link density;
-%     $\beta_{Latitude}$=-0.001, $p$=0.472 for vulnerability).
-%     In stream and terrestrial food webs, however, scaling was more strongly negative in the 
-%     tropics and near zero near the poles ($\beta_{Latitude:Stream}$=0.012, $p$=0.001 
-%     and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015 for link density;
-%     $\beta_{Latitude:Stream}$=0.012, $p$=0.001 and $\beta_{Latitude:Terrestrial}$=0.009, $p$=0.015
-%     for vulnerability; Fig.~\ref{T}. The best-fit model for generality did not include any terms
-%     for latitude in any ecosystem type.
-
-\newpage
+\clearpage
 
@@
   \begin{figure}[!h]
-\centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_observed.eps}}
+  \centerline{\includegraphics*[height=.75\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_corrected_observed_corrected.eps}}
   \caption{Scaling relationships for link density, generality, 
@@
 
-% \newpage
-
-% \begin{figure}[!h]
-% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts.eps}}
-% \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
-% relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
-% Link density, generality,
-% and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
-% type. As these relationships take the form of power laws, we did this by dividing the food-web
-% property (e.g. link density) by species richness raised to an exponent including the 
-% effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
-% type and latitude. Note that in all cases estuarine food webs were treated as the baseline 
-% ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
-% latitude retained in the best-fit model (see \emph{Results} for specifics). For each relationship, 
-% we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
-% ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
-% see Fig.~\ref{TL_observed}.}
-% \label{TL_rescaled}
-% \end{figure}
-
-% \newpage
-
-% \begin{figure}[!h]
-% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/scaling_with_S/proportions/TL_fitlines_nonts_observed.eps}}
-% \caption{Scaling relationships for link density, generality, 
-% and vulnerability relative to the proportions of basal resources, intermediate consumers, and top predators in a food web. 
-% For each relationship, we show observed values (white circles) and 
-% a simplified form of the scaling relationship described in equation 2 (\emph{Main Text}), neglecting 
-% any effects of habitat type or latitude (black line, N=196 food webs). See Fig.~\ref{TL_rescaled} to compare with 
-% observed values correcting for the effects of habitat type and latitude. }
-% \label{TL_observed}
-% \end{figure}
-
-% \newpage
-
-% \begin{figure}[!h]
-% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/B_marginal_latitude_proportions.eps}}
-% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-% types and over latitude. For each property we show the scaling exponent for the proportion of
-% basal resources (black line) with its 95\% confidence interval (in grey), based on N=196 
-% empirical food webs. Latitude is given in degrees
-% from the equator regardless of direction.}
-% \label{B}
-% \end{figure}
-
-% \begin{figure}[!h]
-% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/I_marginal_latitude_proportions.eps}}
-% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-% types and over latitude. For each property we show the scaling exponent for the proportion of
-% intermediate consumers (black line) with its 95\% confidence interval (in grey), based on 
-% N=196 empirical food webs. Latitude is given in degrees
-% from the equator regardless of direction.}
-% \label{I}
-% \end{figure}
-
-% \newpage
-
-% \begin{figure}[!h]
-% \centerline{\includegraphics*[width=.8\textwidth]{Figures/by_TL/marginal/T_marginal_latitude_proportions.eps}}
-% \caption{Changes to the scaling of link density, generality, and vulnerability across ecosystem
-% types and over latitude. For each property we show the scaling exponent for the proportion of
-% top predators (black line) with its 95\% confidence interval (in grey), based on N=196 
-% empirical food webs. Latitude is given in degrees
-% from the equator regardless of direction.}
-% \label{T}
-% \end{figure}
-
 \newpage

### 2018-07-26 code/TL_observedfits_corrected.py

@@ -23,7 +23,6 @@ from PyGrace.Styles.el import ElGraph, ElLinColorBar, ElLogColorBar
 def datareader(rawdatafile,TL,Bformat):
 
   points={'LS':[],'Gen':[],'Vul':[]}
-
   f=open(rawdatafile,'r')
   i=1
   for line in f:
@@ -36,27 +35,12 @@ def datareader(rawdatafile,TL,Bformat):
       L=line.split('\t')[5]
       C=line.split('\t')[6]
       LS=float(line.split('\t')[7])
-      LSsd=line.split('\t')[8]
-      Gen=float(line.split('\t')[9])
-      GenSD=float(line.split('\t')[10])
-      Vul=float(line.split('\t')[11])
-      VulSD=float(line.split('\t')[12])
-      Path=line.split('\t')[13]
-      Chain=line.split('\t')[14]
-      SWTL=line.split('\t')[15]
-      Clus=line.split('\t')[16]
-      B=float(line.split('\t')[17])
-      H=float(line.split('\t')[18])
-      I=float(line.split('\t')[19])
-      I=I+H # Include the herbivores as intermediates
-      T=float(line.split('\t')[20])
-
-      # B=float(line.split('\t')[15])
-      # H=float(line.split('\t')[16])
-      # I=float(line.split('\t')[17])
-      # I=I+H # Include the herbivores as intermediates
-      # T=float(line.split('\t')[18])
-
+      Gen=float(line.split('\t')[8])
+      Vul=float(line.split('\t')[9])
+      B=float(line.split('\t')[10])
+      H=float(line.split('\t')[11])
+      I=float(line.split('\t')[12])
+      T=float(line.split('\t')[13])
       for response in ['LS','Gen','Vul']:
         points[response].append((eval(TL),eval(response)))
 
@@ -346,6 +330,8 @@ def S_rawplots(rawdatafile,outfile1,Bformat,predfolder):
     elif prop=='Gen':
       graph.yaxis.label.configure(text="observed generality",place='normal',char_size=1)
     elif prop=='Vul':
+      print sorted(predictions)[0:5], sorted(predictions)[-5:]
+      print sorted(rawdata[prop])[0:5],sorted(rawdata[prop])[-5:]
       graph.yaxis.label.configure(text="observed vulnerability",place='normal',char_size=1)
 
     graph.world.xmin=1
[…]

### 2018-07-26 manuscript/latitudepaper.tex
removed a couple of old strikethroughs in the main text

@@
   food webs was stronger (i.e., generality increased more steeply with
-  increasing species richness) in higher-latitude food webs. \st{In lake food webs,
+  increasing species richness) in higher-latitude food webs. In lake food webs,
   this trend was echoed in the scaling relationships between species richness
-  and vulnerability and links per species.} This means that species in tropical
+  and vulnerability and links per species. This means that species in tropical
   freshwater communities gain fewer additional feeding links per additional
-  species in the web\st{ and that species in tropical lakes also gain fewer
+  species in the web and that species in tropical lakes also gain fewer
   predators, and fewer links in general, per additional species than species
-  in high-latitude lakes}. These trends are consistent with the hypothesis that
+  in high-latitude lakes. These trends are consistent with the hypothesis that
   greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
@@
   consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data, although the difference between generality was not significant (
-  $\mu_{Aquatic}$=\st{5.47}5.71, $\mu_{Terrestrial}$=\st{3.82}4.82; $p$=\st{0.007}0.297 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$). 
+  $\mu_{Aquatic}$=\st{5.47}5.86, $\mu_{Terrestrial}$=\st{3.82}3.75; $p$=\st{0.007}\textless0.001 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$). 
   The key to this argument is therefore whether freshwater ecosystems experience

### 2018-07-26 manuscript/erratum_letter.tex
corrected values after fixing Sri Lanka

--- 2015-06-29 manuscript/coverletter.tex
@@
 %\usepackage[britdate]{canterbury-letter}
-\usepackage[britdate,alyssa-signature]{canterbury-letter}
+\usepackage[britdate]{LiU-letter}
 \usepackage{times}
@@
 
-\position{PhD Candidate}
-\department{School of Biological Sciences}
-\location{Private Bag 4800}
-\telephone{+64 3 364 2729}
-\fax{+64 3 364 2590}
-\email{alyssa.cirtwill@pg.canterbury.ac.nz}
-\url{http://stoufferlab.org}
+\position{Postdoctoral fellow}
+\department{Department of Physics, Chemistry, and Biology (IFM)}
+\location{581 83 Link\"{o}ping, Sweden}
+\cityzip{581 83 Link\"{o}ping, Sweden}
+\telephone{}
+\fax{}
+\email{alyssa.cirtwill@liu.se}
+\url{http://cirtwill.github.io}
 \name{Alyssa R. Cirtwill}
@@
 
-We are happy to invite you to consider our manuscript 
-``\mytitle'' for publication in the Population and Community Ecology section of the \myjournal.
+I am writing regarding my article \emph{Specialisation in food webs scales with species richness but not with latitude} (article ID \#RSPB-2015-1589.R2, doi: 10.1098/rspb.2015.1589, published November, 2015).
+Recently I have revisited the dataset used in this article and noticed that 75  of the webs we used (out of a sample of 263) have irregularities or errors of formatting that caused them to be incorrectly processed by our original code.
+Fortunately, after repeating all analyses with corrected versions of these 75 webs our results were qualitatively identical to those published and our conclusions remain unchanged.
+Unfortunately, the specific values given in the published text are nearly all incorrect.
 
-Our study aims to combine two well-established but disparate ecological
-themes, namely the analysis of macroecological gradients and the search for
-general laws governing the structure of food webs (networks of who eats whom
-within a community). In particular, we explored the possibility of a link
-between the well-known latitudinal gradients in species richness of some taxa
-(e.g., birds, terrestrial plants) and the scaling relationships between
-species richness and food-web structure. With regard to the former, one
-hypothesised mechanism for greater species richness in the tropics is the
-latitude-niche-breadth hypothesis, which predicts that the greater stability
-of temperature and productivity in the tropics will permit species to evolve
-narrower niches and therefore more finely partition habitats. If this
-hypothesis holds true, then tropical species should be more specialised---have
-fewer feeding links---than their high-latitude counterparts. However, the
-number of feeding links in which a species is involved is also known to
-increase with the number of species in the community food web following a
-power law. Therefore we also naively expect that species in tropical food webs
-will participate in relatively many feeding links by virtue of their speciose
-communities. To address this apparent paradox, we tested for an effect of
-latitude on the strength of the relationship between specialisation and species 
-richness.
+I have attached an updated version of the manuscript with the original values struck through and the corrected values provided side-by-side.
+I hope that this demonstrates that our conclusions hold and will be suitable as a corrigendum for our manuscript.
+I have also attached an updated supplemental information document which now includes a table (Table S2) giving details of the webs which required corrections.
 
-In general, we found little evidence of an effect of latitude on the
-relationship between specialisation and species richness, implying that
-latitudinal variation in food-web structure may be driven purely by
-latitudinal gradients in species richness. If diet breadth may be taken as a
-measure of a species' Eltonian (biotic) niche, this means that food webs
-in general do not conform to the latitude-niche-breadth hypothesis. Ecosystem
-type, on the other hand, had a greater impact on scaling exponents, suggesting
-that different processes may structure food webs in different habitats.
-Indeed, freshwater food webs departed from the overall trend and showed strong
-effects of latitude on scaling relationships. Only in these food webs was the
-latitude-niche-breadth hypothesis.
-
-By linking macroecology and food-web ecology, we believe that our study will
-be of interest to ecologists, theory-focused biologists, and to general
-readers of \myjournal. Our results are potentially applicable to researchers
-exploring community structure and specialisation in a variety of different
-systems and also provide a new community-wide perspective on the validity of
-the latitude-niche-breadth hypothesis. We hope you will agree that this broad
-relevance and the novelty of our results justify consideration of our
-manuscript for \myjournal.
-
-Thank you again for your consideration.
+My co-authors and I deeply regret not finding and correcting these errors earlier, and appreciate your kind attention in this matter.
 

### 2018-08-08 manuscript/correction.tex
uploading a shortened correction

--- 2018-07-26 manuscript/latitudepaper.tex
@@
 
-\begin{spacing}{1.0}
-\section*{Abstract}
+% \linenumbers
+\begin{spacing}{2.0}
 
-Several properties of food webs---the networks of feeding links between
-species---are known to vary systematically with the species richness of the
-underlying community.  Under the ``latitude-niche breadth hypothesis'', which
-predicts that species in the tropics will tend to evolve narrower niches, one
-might expect that these scaling relationships could also be affected by
-latitude. To test this hypothesis, we analysed the scaling relationships
-between species richness and average generality, vulnerability, and links per
-species across a set of 196 empirical food webs. In estuarine, marine, and 
-terrestrial food webs there was no effect of latitude on any scaling relationship,
-suggesting constant niche breadth in these habitats. In freshwater communities,
-on the other hand, there were strong effects of latitude on scaling relationships,
-supporting the latitude-niche breadth hypothesis. These contrasting findings
-indicate that it may be more important to account for habitat than latitude
-when exploring gradients in food-web structure.
+\section*{Correction}
 
-\end{spacing}
+  A subset of the food webs (75/263 webs) used in these analyses contained formatting errors or irregularities that meant they were not properly included in the original analyses.
+We have corrected these webs (see \emph{Table S2, Appendix S1} for details) and repeated all analyses.
+The corrected results were very similar to those in the original manuscript: original values (struck-through) and corrected values are provided below.
 
-% \linenumbers
-
-\section*{Introduction}
-
-  Food webs --networks of feeding links between species-- have been used for
-  several decades to summarise the structure of  ecological
-  communities~\cite{Paine1966,Williams2000,Petchey2008} and to understand how
-  that structure relates to environmental variables  such as habitat
-  type~\cite{Briand1983,Shurin2006}, primary
-  productivity~\cite{Townsend1998,Thompson2005a,Vermaat2009}, and
-  climate~\cite{Petchey2010,Baiser2012}. The latter variables in turn have
-  strong gradients over latitude, with productivity and temperature both being
-  higher in the tropics while  climate is more variable at high
-  latitudes~\cite{Field1998}. These variables affect both the resources
-  available and species'
-  metabolisms~\cite{White2007,OConnor2009,Hechinger2011,White2011}, and have
-  been proposed as determinants of the strength of  interspecific
-  interactions~\cite{Schemske2009,Lang2012,Schleuning2012}.  By modulating
-  interactions between species, latitudinal gradients may also shape food-web
-  structure. Indeed, these latitudinal environmental gradients have been put
-  forward as potential drivers for the  latitudinal gradient in species
-  richness, one of the most general and robust patterns in
-  ecology~\cite{Kaufman1995,Macpherson2002,Schemske2009}.
-
-  One proposed link between species richness and latitude is the 
-  ``latitude-niche breadth hypothesis''~\cite{Vazquez2004}.  This hypothesis 
-  predicts that decreased seasonality in the tropics should lead to more stable
-  populations, which in turn should evolve smaller niches~\cite{Vazquez2004}.
-  These narrow niches should therefore allow more species to  coexist in the
-  tropics than at higher latitudes. Alternatively, the higher productivity of
-  the tropics~\cite{Brown2004} may result in a broader niche
-  space~\cite{Davies2007} which could also sustain greater biodiversity even
-  if niche  sizes are globally similar. Although the assumptions of the
-  latitude-niche breadth hypothesis are only equivocally
-  supported~\cite{Vazquez2004}, it remains a compelling potential mechanism
-  for the latitudinal gradient in species
-  richness~\cite{Lappalainen2006,Krasnov2008,Slove2010}.
-
-  If the latitude-niche breadth hypothesis is correct, there should also be
-  direct relationships between latitude and the degree of specialisation
-  (i.e., the breadth of the Eltonian niche; ~\cite{Elton1927,Leibold2010}) of
-  species within food webs. Specifically, narrower niches in the tropics would
-  equate to greater specialisation (narrower niches) while constant niche
-  sizes but greater productivity would translate to constant specialisation
-  and niche width across latitude (Fig.~\ref{concept}). Attempts to unravel
-  these effects, however, are complicated by known relationships between
-  species richness and many other network properties~\cite{Riede2010}.  For
-  example, narrower niches imply fewer links per species (i.e., greater
-  specialisation) in the tropics (\cite{Marra1997,Dyer2007}; but
-  see~\cite{Schleuning2012}). However, average numbers of links per species
-  tend to increase in larger food webs~\cite{Dunne2006,Riede2010}. This means
-  that a latitudinal effect on specialisation may be obscured by a latitudinal
-  gradient in species richness.
-
-  If this is the case, it may still be possible to uncover effects of latitude
-  on specialisation by examining the shape of the scaling relationship between
-  specialisation and species richness over changing latitude.  By testing
-  whether latitude affects the scaling of each property with species richness,
-  we test for the effects of latitude on specialisation predicted by the
-  ``latitude-niche breadth hypothesis'' (Fig.~\ref{concept}).  If the scaling
-  of specialisation with species richness is weaker in the  tropics (i.e., if
-  species gain fewer links, predators, or prey as the size  of the network
-  increases), this will indicate narrower niches at the tropics.  If, however,
-  the scaling of specialisation with species richness does not  vary over
-  latitude, this will indicate that niches are similarly-sized worldwide but
-  that there is a broader niche space in the tropics. Additionally, as food
-  webs describing different ecosystem types may differ in their
-  topology~\cite{Dunne2004,Shurin2006}, we also explored the differences in
-  scaling relationships across ecosystem types. Here, we use three measures of
-  specialisation; mean links per species, mean generality (number of prey),
-  and mean vulnerability (number of predators).
-
-\section*{Methods}
-
-  \subsection*{Data Set}
-
-    We compiled a list of 196 empirical food webs from
-    multiple sources (see \emph{Appendix S1} for web origins and selection
-    criteria). We recorded study site latitude from the original source where
-    possible or, where study sites were described but exact coordinates were not
-    given, obtained estimated coordinates using Google Earth~\cite{GoogleEarth}.
-    If a range of latitudes (e.g. $42-49^{\circ}N$) was provided, we used the midpoint
-    of this range. We grouped food webs by ecosystem type (stream, N=71; lake, N=47; marine, 
-    N=28; estuarine, N=18; and terrestrial, N=31) according to their designation in 
-    previous aggregations of food webs (i.e.,~\cite{GlobalWeb,Riede2011,Dunne2013}).
-
-    As the food webs in this dataset are derived from a variety of sources and were compiled over many decades, it
-    is likely that they vary in their resolution and in the amount of sampling effort invested in their assembly.
-    Many analyses of food-web structure attempt to reduce this variation by using food webs comprised of ``trophic
-    species'' --aggregations of species with identical sets of predators and prey-- rather than  
-    species \emph{per se}~\cite{Martinez1991,Dunne2004,Vermaat2009,Dunne2013}. As our study
-    is concerned directly with the number of species at a particular latitude, however, we did not wish to ignore 
-    species with identical sets of interactions. We therefore analysed both original (i.e., without aggregating 
-    any species) and trophic-species (i.e., after aggregating species with identical predators and prey) versions
-    of the dataset; in each case using the number of species and 
-    feeding links in each web to calculate the mean link density (number of links per species), mean generality 
-    (number of prey per species), and mean vulnerability (number of predators per species) of the web. 
-    The version of the dataset used did not qualitatively change the results, suggesting that
-    the scaling relationships between species richness and specialisation across ecosystem type and latitude are very 
-    similar whether or not species with identical sets of predators and prey are included. For simplicity, 
-    here we present only the results for the original webs.
-
-  \subsection*{Gradients over Latitude}
-
-    To put our dataset in the context of other research on latitudinal gradients in species richness,
-    we first examined simple linear relationships between latitude and each of 
-    species richness, links per species, generality, and vulnerability. We fit models of the form
-
-    \begin{equation}
-    \label{Latfull}
-    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
-    \end{equation}
-
-    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
-    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
-    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
-    marine, lake, and terrestrial networks with estuarine
-    networks corresponding to $E_{i}=0$) and $\epsilon_{i}$ is a residual error term. 
-    We next calculated the AIC
-    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
-    using the R~\cite{R} function dredge from package MuMIn~\cite{MuMIn}. 
-    Simplified models were obtained by
-    systematically removing all possible combinations of terms from the full model.
-    The best-fitting model was then determined to be the model with the fewest terms 
-    where $\Delta$AIC\textless2, as this model is the least likely to suffer from over-fitting.
-
-  \subsection*{Scaling Relationships with Species Richness}
-
-    The scaling relationship between link density ($Z$) and species richness ($S$)
-    has been shown to be a power law~\cite{Riede2010} of the form
-
-    \begin{equation}
-    \label{Power}
-    Z_{i} \sim \alpha S_{i}^{\beta}  ,
-    \end{equation}
-
-    \noindent which is often re-expressed in logarithmic form
-
-    \begin{equation}
-    \label{Loglog}
-    \log{Z_{i}} \sim \log{\alpha} + \beta\log{S_{i}}  .
-    \end{equation}
-
-    \noindent As the two forms imply a statistical fit of the data to different error 
-    distributions, neither of which has strong
-    \emph{a priori} justification in our dataset, we followed the recommendations in~\cite{Xiao2011}
-    to compare the two model formulations explicitly (see \emph{Appendix S2} for details). 
-    The logarithmic form (equation~\ref{Loglog}) provided the better fit to the data,
-    as did the logarithmic forms of similar models for the scaling of generality and vulnerability. 
-    We therefore used and present logarithmic models throughout the rest of the analyses.
-
-  \subsection*{Effect of Latitude on Scaling}
-
-    After determining the appropriate form of the scaling relationship, we
-    then assessed the impact of latitude on the scaling relationships between
-    species richness and link density, generality, vulnerability. In the
-    context of the scaling relationships above, note  that this implies that
-    we wished to determine the effect of latitude on the scaling exponent
-    $\beta$. We included a categorical variable for
-    ecosystem type (stream, lake,  terrestrial, marine, or estuary), as well
-    as interactions between food web type and latitude.
-
-    We therefore began by considering models of the form
-
-    \begin{equation}
-    \label{PowerLat}
-    Z_{i}=\alpha S_{i}^{\beta_{0}+\beta_{1}L_{i}+\beta_{2}E_{i}+\beta_{3}LE_{i}} + \epsilon_{i} ,
-    \end{equation}
-
-    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
-    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
-    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
-    marine, lake, and terrestrial networks with estuarine
-    networks corresponding to $E_{i}=0$) and $\epsilon_{i}$ is a residual error term.
-    The logarithmic formulation of this model is
-
-    \begin{equation}
-    \label{LogLat}
-    \log{Z_{i}} = \log{\alpha}+\beta_{0}\log{S_{i}} + \beta_{1}L\log{S_{i}} +\beta_{2}E\log{S_{i}} +\beta_{3}LE\log{S_{i}} +\epsilon_{i} .
-    \end{equation}
-
-    We then simplified versions of model~\ref{LogLat} for link density, generality, and vulnerability following the procedure described above.
-    As a supplemental check to ensure that variation in sampling effort
-    across food webs was not responsible for the trends we observed, we then
-    repeated our analyses using jackknifed data sets in which we 1) sequentially
-    removed each food web in the dataset and 2) sequentially removed sets of food webs
-    that shared a common author. The first jackknife essentially controls for the
-    influence of any single outlier, while the second controls for the influence
-    of particular research groups, some of which contributed large numbers of food
-    webs (up to 27) to the dataset. Parameter estimates for the simplified models 
-    varied very little across either jackknife test (see \emph{Appendix S3} for details),
-    indicating that the trends we observed were not due to either strong outliers or
-    to substantial differences in sampling effort across research groups.
-
-\section*{Results}
+\subsection*{Results}
 
@@
   to the expected latitudinal gradient, the best-fit version of
-  equation~(\ref{Latfull}) did not include a significant
+  equation (1) did not include a significant
   effect of latitude on species richness for any ecosystem type. Further, there were no significant
@@
   Each measure of specialisation increased with increasing
-  species richness ($\beta_0$=\st{0.637}0.691, $p$\textless0.001; $\beta_0$=\st{0.553}0.663,
-  $p$\textless0.001; and $\beta_0$=\st{0.637}0.698, $p$\textless0.001, respectively;
+  species richness \\($\beta_0$=\st{0.637}0.688, $p$\textless0.001; $\beta_0$=\st{0.553}0.658,
+  $p$\textless0.001; and $\beta_0$=\st{0.637}0.695, $p$\textless0.001, respectively;
   Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
-  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.212 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.320 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.207 for vulnerability; Fig.~\ref{S}). In
+  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.210 for link density;
+  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.315 for generality; and
+  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.205 for vulnerability; Fig.~\ref{S}). In
   lake food webs, however, the scaling of each property was stronger towards
-  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.037;
-  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.007; and
-  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.003, $p$=0.036, respectively). In stream food
+  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.031;
+  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.005; and
+  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.004, $p$=0.030, respectively). In stream food
   webs, generality increased more rapidly towards the poles
@@
 
-\section*{Discussion}
+\subsection*{Discussion}
 
-  The tendency of food-web structure to exhibit scaling relationships with
-  species richness has been well-established~\cite{Dunne2004,Riede2010}. As
-  species richness in particular is also known to vary systematically over
-  latitude~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009},
-  intuitively one might suspect that any relationship between food-web
-  properties such as generality might be due to the latitudinal gradient in
-  species richness. In this dataset, however, we found no evidence to support
-  latitudinal gradients in species richness, links per species, generality, 
-  or vulnerability.
-
-  The lack of a latitudinal gradient in species richness in this dataset
-  contrasts strongly with other
-  studies~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. As
-  numbers of species and links included in a food web vary strongly with
-  sampling effort as well as with the underlying diversity of the study area,
-  it is possible that the lack of latitudinal trends here is a result of
-  researchers tending to expend similar amounts of sampling effort across
-  studies. This could result in food webs describing species-rich tropical
-  communities omitting more species and links than studies of species-poor
-  arctic communities if research groups spend similar person-hours assembling
-  webs and can observe similar numbers of species and links per person-hour.
-  In addition, it is worth noting that gradients in species richness are
-  generally measured for a single taxonomic group at a
-  time~\cite{Kaufman1995,Macpherson2002,Hillebrand2004,Schemske2009}. It is
-  possible that these taxa are not well-represented in our food webs and that
-  the dominant taxa that are represented do not have an underlying latitudinal
-  gradient in richness. In either case, the lack of a strong association
-  between observed species richness and latitude in any ecosystem type in our dataset
-  means that any effect of latitude on other scaling relationships is not being driven by
-  the scaling of specialisation with species richness in our food webs. This is fortunate since
-  the lack of confounding effects of latitude allows us to more clearly assess
-  effects of latitude on scaling with species richness.
-
-  Scaling of links per species, generality, and vulnerability with species
-  richness varied strongly across ecosystem types. In estuarine, marine, and
-  terrestrial food webs scaling of each property varied little with latitude.
-  This is consistent with the idea that species' niche breadths do not vary
-  systematically with temperature and productivity but that the niche space
-  might be larger in species-rich communities~\cite{Davies2007}. Rather than
-  niche space depending on temperature and productivity, it may be that species
-  diversity itself affects the biotic niche space available to species (although climate
-  may affect speciation rates and therefore the diversity in a region~\cite{Currie2004}). 
-  For example, as the plant diversity of a community increases both the 
-  variety of food available to herbivores and the structural variety of the habitat will also increase.
-
-  Unlike other ecosystem types, the scaling of generality in lake and stream
-  food webs was stronger (i.e., generality increased more steeply with
-  increasing species richness) in higher-latitude food webs. In lake food webs,
-  this trend was echoed in the scaling relationships between species richness
-  and vulnerability and links per species. This means that species in tropical
-  freshwater communities gain fewer additional feeding links per additional
-  species in the web and that species in tropical lakes also gain fewer
-  predators, and fewer links in general, per additional species than species
-  in high-latitude lakes. These trends are consistent with the hypothesis that
-  greater stability in the tropics leads to narrower niches~\cite{Vazquez2004}
-  and a higher proportion of specialists.
-
-  That freshwater food webs supported the hypothesis of narrower niches in the
-  tropics --while other ecosystem types did not-- is noteworthy given that
-  these ecosystems (especially streams) are known for being highly variable
-  and that seasonal variability is one of the proposed drivers of the
-  latitude-niche breadth hypothesis~\cite{Vazquez2004}. Both streams and lakes
-  can experience severe changes in water temperature and volume (e.g., floods,
-  drying, freezing) that remove food or other resources (notably oxygen during
-  freezing events)~\cite{Winterbourn1997,Meding2001}. These events are often
-  linked to seasonal events such as snowmelts or summer
-  drought~\cite{Winterbourn1997}). Further, both temperate streams and lakes
-  tend to experience seasonal strong pulses of allochthonous inputs (e.g.,
-  fallen leaves, terrestrial
-  invertebrates~\cite{Nakano2001,Lennon2004,Zeng2008}. These trends combined
-  mean that, relative to estuarine and marine communities, freshwater food 
-  webs may experience high turnover in both community composition and 
-  productivity~\cite{Tilzer1988,Magalhaes1993,Baird1989}. Notable exceptions from the above
-  trends are New Zealand stream communities (representing 31 of the 71 stream
-  food webs in our dataset), which experience unpredictable flooding and
-  drying throughout the year and do not receive seasonally pulsed
-  subsidies~\cite{Winterbourn1997,Winterbourn1981}. However, as this subset of
-  webs is very tightly grouped in latitude ($44.64-46.41^{\circ}$S, within an
-  overall range of $23.00-69.02^{\circ}$ for stream communities), it is unlikely that they have greatly
-  influenced our results (see also \emph{Appendix S3}). Moreover, just as in
-  highly-variable communities where said variation is more seasonal, New
-  Zealand communities are dominated by ecological
-  generalists~\cite{Winterbourn1997,Winterbourn1981} implying that they appear
-  to fit the general pattern of streams worldwide.
-
-  Importantly, while terrestrial communities are also strongly seasonal at
-  high latitudes and can receive significant allochthonous
-  inputs~\cite{Nakano2001}, terrestrial consumers tend to be
-  morphologically specialised for feeding on particular prey~\cite{Liem1990}.
-  This means that primarily gape-limited aquatic consumers tend to be more
+  ... primarily gape-limited aquatic consumers tend to be more
   generalist across all types of aquatic habitats than terrestrial 
   consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data, although the difference between generality was not significant (
-  $\mu_{Aquatic}$=\st{5.47}5.86, $\mu_{Terrestrial}$=\st{3.82}3.75; $p$=\st{0.007}\textless0.001 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$). 
-  The key to this argument is therefore whether freshwater ecosystems experience
-  more severe seasonal variation than marine and estuarine ecosystems. Although
-  we are not aware of any study explicitly comparing seasonal variation in
-  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
-  ecosystems are indeed likely to experience more severe changes because of their small size.
-  While oceans and estuaries certainly vary in terms of water temperature and
-  nutrients over the course of a year~\cite{Baird1989}, these changes are likely to be slower
-  and milder than in freshwaters because marine and estuarine communities are buffered 
-  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
-  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
-  in non-marine communities~\cite{Field1998}. Thus suggests that niche breadths may also be 
-  more variable over the course of the year.
+  $\mu_{Aquatic}$=\st{5.47}5.86, \\$\mu_{Terrestrial}$=\st{3.82}3.75; $p$=\st{0.007}\textless0.001 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$).
 
-\section*{Conclusion}
+\end{spacing}
 
-  Overall, our results were inconsistent with the latitude-niche breadth
-  hypothesis in estuarine, marine, and terrestrial communities but consistent
-  with the hypothesis of greater specialisation in the tropics in stream and
-  lake food webs. This suggests that different mechanisms may structure food
-  webs in different habitat types and that freshwater food webs in particular
-  may be strongly affected by seasonal variation. Freshwater food webs also
-  appear to have different predator-prey biomass ratios than other ecosystem
-  types~\cite{Riede2011}; although it is not clear whether these ratios are related
-  to seasonality, this could be a promising avenue for future research. In addition, different
-  relationships between latitude and niche breadth in different habitat types
-  go some way towards explaining the equivocal support for the opposing
-  hypotheses of narrower niches in the tropics~\cite{Vazquez2004} and broader
-  niche space in the tropics~\cite{Davies2007}. Our study indicates that both 
-  have merit but would appear to apply to different systems.
-
-\section*{Data Accessibility}
-
-  Food webs used in this study were retrieved from the University of Canberra's 
-  GlobalWeb database (\cite{GlobalWeb}; \emph{www.globalwebdb.com}) and from
-  two papers (\cite{Riede2011}; \emph{http://dx.doi.org/10.1111/j.1461-0248.2010.01568.x}
-  and \cite{Dunne2013}; \emph{http://dx.doi.org/10.1371/journal.pbio.1001579}). Original sources for the
-  food webs are given in \emph{Appendix S1}.
-
-\section*{Competing interests}
-
-  We have no competing interests.
-
-\section*{Authors' contributions}
-
-  ARC, DBS, and TNR designed the study, ARC collected
-  published data, performed the analyses, and wrote the
-  first draft. DBS and TNR substantially revised the article;
-  all authors approved the final version.
-
-\section*{Acknowledgements}
-
-  We thank members of the Romanuk, Stouffer, and Tylianakis labs for their comments on
-  the manuscript. We also thank Angus McIntosh for valuable discussion on stream food webs and Matthias Schleuning, Robby Stoks, and one anonymous reviewer for their insightful questions.
-
-\section*{Funding}
-  This research was supported by an NSERC USRA undergraduate scholarship and NSERC PGS-D 
-  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
-  Rutherford Discovery Fellowship, both administered by the Royal Society of New Zealand 
-  (to DBS), and an NSERC Discovery Grant (to TNR).
-
-\newpage
 \bibliographystyle{prsb}
@@
 
-\section*{Figure Captions}
+\section*{Figures}
 
 \begin{figure}[h]
-\centerline{\includegraphics*[height=.5\textheight]{Figures/Other/conceptual_figure.eps}}
-\caption{In A) we show the known scaling relationship between link density (links per species) and 
-species richness. This scaling relationship is a power law and therefore linear in a log-log plot.
-In B) we show two versions of the latitudinal-niche breadth hypothesis that have been proposed to
-explain this gradient. Hypothesis 1 posits that greater environmental stability in the tropics will 
-allow species to evolve narrower niches (indicated by parabolas) than those at the poles. Hypothesis 2 
-suggests that species will have constant niche sizes over latitude but that greater primary productivity 
-in the tropics creates a larger niche space such that each species still occupies a smaller proportion 
-of the total niche space. These two hypotheses have different implications for the scaling of food-web 
-properties such as the number of feeding links per species with species richness. C) If hypothesis 1 is 
-true, then the exponent of the scaling relationship between link density and species richness should 
-be larger towards the poles, where each additional species in the food-web will have a larger niche 
-(i.e., more feeding links). If hypothesis 2 is true, then the exponent of this distribution should 
-not vary significantly over latitude.}
-\label{concept}
-\end{figure}
-
-\begin{figure}[h]
-% \centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/S_fitlines_nonts_new.eps}}
-\centerline{\includegraphics*[height=.5\textheight]{Figures/by_TL/scaling_with_S/proportions/STL_fitlines_nonts.eps}}
+% \centerline{\includegraphics*[width=\textwidth]{Figures/by_TL/scaling_with_S/proportions/STL_fitlines_nonts.eps}}
+% \centerline{\includegraphics*[width=\textwidth]{Figure2_updated.eps}}
 \caption{
@@
 \begin{figure}[h]
-%\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_proportions.eps}}
-% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_updated.eps}}
-\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_corrected.eps}}
+% \centerline{\includegraphics*[width=\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_corrected.eps}}
+% \centerline{\includegraphics*[width=\textwidth]{Figure3_updated.eps}}
 \caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem

### 2018-08-08 manuscript/erratum_letter.tex
uploading a shortened correction

@@
 
-I am writing regarding my article \emph{Specialisation in food webs scales with species richness but not with latitude} (article ID \#RSPB-2015-1589.R2, doi: 10.1098/rspb.2015.1589, published November, 2015).
+I am writing regarding my article \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types.} (article ID \#RSPB-2015-1589.R2).
+The full citation details for this article are: Cirtwill, A.R., Stouffer, D.B., \& Romanuk, T.N.
+(2015) \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types}.
+\textbf{Proceedings of the Royal Society B}: 282(1819), 20151589.
+doi: 10.1098/rspb.2015.1589
+
 Recently I have revisited the dataset used in this article and noticed that 75  of the webs we used (out of a sample of 263) have irregularities or errors of formatting that caused them to be incorrectly processed by our original code.
@@
 
-I have attached an updated version of the manuscript with the original values struck through and the corrected values provided side-by-side.
+I have attached a corrected version of the results and a small portion of the discussion with the original values struck through and the corrected values provided side-by-side.
+No further changes to the manuscript were necessary.
 I hope that this demonstrates that our conclusions hold and will be suitable as a corrigendum for our manuscript.

### 2018-08-09 manuscript/latitudepaper.tex

@@
   Each measure of specialisation increased with increasing
-  species richness ($\beta_0$=\st{0.637}0.691, $p$\textless0.001; $\beta_0$=\st{0.553}0.663,
-  $p$\textless0.001; and $\beta_0$=\st{0.637}0.698, $p$\textless0.001, respectively;
+  species richness ($\beta_0$=\st{0.637}0.688, $p$\textless0.001; $\beta_0$=\st{0.553}0.658,
+  $p$\textless0.001; and $\beta_0$=\st{0.637}0.695, $p$\textless0.001, respectively;
   Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
   strength of this scaling did not vary with latitude
-  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.212 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.320 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.207 for vulnerability; Fig.~\ref{S}). In
+  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.210 for link density;
+  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.315 for generality; and
+  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.205 for vulnerability; Fig.~\ref{S}). In
   lake food webs, however, the scaling of each property was stronger towards
-  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.037;
-  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.007; and
-  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.003, $p$=0.036, respectively). In stream food
+  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.031;
+  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.005; and
+  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.004, $p$=0.030, respectively). In stream food
   webs, generality increased more rapidly towards the poles

### 2018-08-09 manuscript/supplement.tex

@@
       \hline
-      18 & Corrected -1 entry to 1 \\
-      22 &  Corrected -1 entries to 1, -2 entries to 0 \\
-      23 & Corrected -1 entries to 1 \\
-      24 &  Corrected -1 entries to 1 \\
-      26 & Corrected decimal entries to 1, -1 entries to 1 \\
+      #18 & Corrected -1 entry to 1 \\
+      #22 &  Corrected -1 entries to 1, -2 entries to 0 \\
+      #23 & Corrected -1 entries to 1 \\
+      #24 &  Corrected -1 entries to 1 \\
+      #26 & Corrected decimal entries to 1, -1 entries to 1 \\
       33 & Corrected decimal entries to 1 \\
@@
       41 & Corrected species names \\
-      60 & Corrected species names \\
+      #60 & Corrected species names \\
       80 & Corrected species names \\
@@
       120 & Corrected -1 entries to 1 \\
-      153 & Corrected -1 entries to 1 \\
-      154 & Corrected -1 entries to 1  \\
-      180 &  Corrected entries indicating a primary producer as predator to 0 \\
-      181 &  Corrected -1 entries to 1 \\
-      182 &  Corrected -1 entries to 1 \\
-      183 &  Corrected -1 entries to 1 \\
+      #153 & Corrected -1 entries to 1 \\
+      #154 & Corrected -1 entries to 1  \\
+      #180 &  Corrected entries indicating a primary producer as predator to 0 \\
+      #181 &  Corrected -1 entries to 1 \\
+      #182 &  Corrected -1 entries to 1 \\
+      #183 &  Corrected -1 entries to 1 \\
       202 &  Corrected -1 entries to 1  \\

### 2018-08-09 manuscript/correction.tex
fixed the compiling, but figs. 2,3 original are too big.

@@
 
-\title{Latitudinal gradients in biotic niche breadth vary across ecosystem types.}
+\title{Latitudinal gradients in biotic niche breadth vary across ecosystem types}
 \author{Alyssa R. Cirtwill$^{1,2}$, Daniel B. Stouffer$^{1}$, Tamara N. Romanuk$^{2}$}
@@
 
-\section*{Correction}
-
-  A subset of the food webs (75/263 webs) used in these analyses contained formatting errors or irregularities that meant they were not properly included in the original analyses.
-We have corrected these webs (see \emph{Table S2, Appendix S1} for details) and repeated all analyses.
-The corrected results were very similar to those in the original manuscript: original values (struck-through) and corrected values are provided below.
+\section*{Current text}
 
@@
     number of prey per species), and vulnerability (mean number of predators per
-  species) were strongly and positively correlated ($R^2$=\st{0.891}0.915 for link
+    species) were strongly and positively correlated ($R^2$=0.891 for link
     density and generality, $R^2$\textgreater0.999 for link density and
-  vulnerability, and $R^2$=\st{0.890}0.912 for generality and vulnerability). Contrary
+    vulnerability, and $R^2$=0.890 for generality and vulnerability). Contrary
     to the expected latitudinal gradient, the best-fit version of
@@
     Each measure of specialisation increased with increasing
-  species richness \\($\beta_0$=\st{0.637}0.688, $p$\textless0.001; $\beta_0$=\st{0.553}0.658,
-  $p$\textless0.001; and $\beta_0$=\st{0.637}0.695, $p$\textless0.001, respectively;
-  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
+    species richness ($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
+    $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;
+    Fig.~\ref{props_v_lat1}). For estuarine, marine, and terrestrial food webs the
     strength of this scaling did not vary with latitude
-  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.210 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.315 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.205 for vulnerability; Fig.~\ref{S}). In
+    ($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
+    $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
+    $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability; Fig.~\ref{S1}). In
     lake food webs, however, the scaling of each property was stronger towards
-  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.031;
-  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.005; and
-  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.004, $p$=0.030, respectively). In stream food
+    the poles ($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
+    $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
+    $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively). In stream food
     webs, generality increased more rapidly towards the poles
-  ($\beta_{Latitude:Stream}$=\st{0.007, $p$=0.001}0.005, $p$=0.008) while link density and
+    ($\beta_{Latitude:Stream}$=0.007, $p$=0.001) while link density and
     vulnerability did not vary with latitude (i.e., the interaction term 
@@
     generalist across all types of aquatic habitats than terrestrial 
-  consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data, although the difference between generality was not significant (
-  $\mu_{Aquatic}$=\st{5.47}5.86, \\$\mu_{Terrestrial}$=\st{3.82}3.75; $p$=\st{0.007}\textless0.001 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$).
+    consumers [5,53]. This trend also held in our data, although the difference between generality was not significant (
+    $\mu_{Aquatic}$=5.47, $\mu_{Terrestrial}$=3.82; $p$=0.007 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$).
 
-\end{spacing}
+\section*{Corrected text}
 
-\bibliographystyle{prsb}
-\bibliography{abbreviated}
+  \subsection*{Results}
 
-\newpage
+    Link density (mean number of feeding links per species), generality (mean
+    number of prey per species), and vulnerability (mean number of predators per
+    species) were strongly and positively correlated ($R^2$=0.915 for link
+    density and generality, $R^2$\textgreater0.999 for link density and
+    vulnerability, and $R^2$=0.912 for generality and vulnerability). Contrary
+    to the expected latitudinal gradient, the best-fit version of
+    equation (1) did not include a significant
+    effect of latitude on species richness for any ecosystem type. Further, there were no significant
+    relationships between link density, generality, or vulnerability with
+    latitude for any ecosystem type.
 
-\section*{Figures}
+    Each measure of specialisation increased with increasing
+    species richness ($\beta_0$=0.688, $p$\textless0.001; $\beta_0$=0.658,
+    $p$\textless0.001; and $\beta_0$=0.695, $p$\textless0.001, respectively;
+    Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
+    strength of this scaling did not vary with latitude
+    ($\beta_{Latitude}$=-0.001, $p$=0.210 for link density;
+    $\beta_{Latitude}$=-0.001, $p$=0.315 for generality; and
+    $\beta_{Latitude}$=-0.001, $p$=0.205 for vulnerability; Fig.~\ref{S}). In
+    lake food webs, however, the scaling of each property was stronger towards
+    the poles ($\beta_{Latitude:Lake}$=0.003, $p$=0.031;
+    $\beta_{Latitude:Lake}$=0.005, $p$=0.005; and
+    $\beta_{Latitude:Lake}$=0.004, $p$=0.030, respectively). In stream food
+    webs, generality increased more rapidly towards the poles
+    ($\beta_{Latitude:Stream}$=0.005, $p$=0.008) while link density and
+    vulnerability did not vary with latitude (i.e., the interaction term 
+    $\beta_{Latitude:Stream}$ was not retained in the best-fit models).
+
+  \subsection*{Discussion}
+
+    ... primarily gape-limited aquatic consumers tend to be more
+    generalist across all types of aquatic habitats than terrestrial 
+    consumers [5,53]. This trend also held in our data, although the difference between generality was not significant (
+    $\mu_{Aquatic}$=5.86, \\$\mu_{Terrestrial}$=3.75; $p$=\textless0.001 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$).
+
+  \subsection*{Supplemental Information}
+
+    \emph{Table S2} added to Appendix \emph{S1}. All supplemental figures updated.
+
+% \bibliographystyle{prsb}
+% \bibliography{abbreviated}
+
+\clearpage
+
+\section*{Original Figures}
+
+\setcounter{figure}{1}
 
 \begin{figure}[h]
-% \centerline{\includegraphics*[width=\textwidth]{Figures/by_TL/scaling_with_S/proportions/STL_fitlines_nonts.eps}}
-% \centerline{\includegraphics*[width=\textwidth]{Figure2_updated.eps}}
+% \includegraphics*[width=\textwidth]{Figures/Figure2.eps}
+\includegraphics*[width=\textwidth]{Figure2.eps}
 \caption{
@@
 see Fig.~\emph{S7}, \emph{Appendix S4}.}
+\label{props_v_lat1}
+\end{figure}
+
+\begin{figure}[h]
+% \includegraphics*[width=\textwidth]{Figures/Figure3.eps}
+\includegraphics*[width=\textwidth]{Figure3.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
+types and over latitude. We show the estimated scaling exponent for species richness (black
+line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
+Latitude is given in degrees from the equator regardless of direction.} 
+\label{S1} 
+\end{figure}
+
+\clearpage
+
+\section*{Corrected Figures}
+
+\setcounter{figure}{1}
+\begin{figure}[h]
+% \includegraphics*[width=\textwidth]{Figures/Figure2_updated.eps}
+\includegraphics*[width=\textwidth]{Figure2_updated.eps}
+\caption{
+Figure 2 caption correct in original.}
 \label{props_v_lat}
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[width=\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_corrected.eps}}
-% \centerline{\includegraphics*[width=\textwidth]{Figure3_updated.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
-types and over latitude. We show the estimated scaling exponent for species richness (black
-line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
-Latitude is given in degrees from the equator regardless of direction.} \label{S} \end{figure}
+% \includegraphics*[width=\textwidth]{Figures/Figure3_updated.eps}
+\includegraphics*[width=\textwidth]{Figure3_updated.eps}
+\caption{Figure 3 caption correct in original.} \label{S} \end{figure}
+
+\end{spacing}
 

### 2018-08-28 manuscript/correction.tex
reformatted the correction almost to what it was the first time

--- 2018-08-08 manuscript/correction.tex
@@
 
-\section*{Correction}
+\section*{Purpose for correction}
 
-  A subset of the food webs (75/263 webs) used in these analyses contained formatting errors or irregularities that meant they were not properly included in the original analyses.
-We have corrected these webs (see \emph{Table S2, Appendix S1} for details) and repeated all analyses.
-The corrected results were very similar to those in the original manuscript: original values (struck-through) and corrected values are provided below.
+    A subset of food webs analysed for this manuscript (75 out of 263; see \emph{Table S2, Appendix S1} for details) had formatting errors or irregularities that caused them to be incorrectly processed by our original code.
+We have corrected these inconsistencies and repeated our analyses to ensure that our conclusions did not change.
+After re-analysis, our results were qualitatively identical to those originally published and our original conclusions hold.
+However, the specific values given in the results and discussion are now incorrect.
+Below, we present the results and the relevant portion of the discussion with the original values (struck-through) and corrected values (bold) side by side as well as the original and corrected Figures 2-3.
+All supplemental figures have also been updated; as with the main-text figures below, any differences were minor.
+Reference numbers are as in the original main text.
 
-\subsection*{Results}
+\section*{Results}
 
@@
     number of prey per species), and vulnerability (mean number of predators per
-  species) were strongly and positively correlated ($R^2$=\st{0.891}0.915 for link
+    species) were strongly and positively correlated \st{($R^2$=0.891 for link
     density and generality, $R^2$\textgreater0.999 for link density and
-  vulnerability, and $R^2$=\st{0.890}0.912 for generality and vulnerability). Contrary
+    vulnerability, and $R^2$=0.890 for generality and vulnerability)}
+    \textbf{($R^2$=0.915 for link
+    density and generality, $R^2$\textgreater0.999 for link density and
+    vulnerability, and $R^2$=0.912 for generality and vulnerability)}
+    . Contrary
     to the expected latitudinal gradient, the best-fit version of
@@
     Each measure of specialisation increased with increasing
-  species richness \\($\beta_0$=\st{0.637}0.688, $p$\textless0.001; $\beta_0$=\st{0.553}0.658,
-  $p$\textless0.001; and $\beta_0$=\st{0.637}0.695, $p$\textless0.001, respectively;
-  Fig.~\ref{props_v_lat}). For estuarine, marine, and terrestrial food webs the
+    species richness 
+    \st{($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
+    $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;}
+    \textbf{($\beta_0$=0.688, $p$\textless0.001; $\beta_0$=0.658,
+    $p$\textless0.001; and $\beta_0$=0.695, $p$\textless0.001, respectively;}
+    Fig.~\ref{props_v_lat1}). For estuarine, marine, and terrestrial food webs the
     strength of this scaling did not vary with latitude
-  ($\beta_{Latitude}$=-0.001, $p$=\st{0.365}0.210 for link density;
-  $\beta_{Latitude}$=-0.001, $p$=\st{0.535}0.315 for generality; and
-  $\beta_{Latitude}$=-0.001, $p$=\st{0.366}0.205 for vulnerability; Fig.~\ref{S}). In
+    \st{($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
+    $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
+    $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability;}
+    \textbf{($\beta_{Latitude}$=-0.001, $p$=0.210 for link density;
+    $\beta_{Latitude}$=-0.001, $p$=0.315 for generality; and
+    $\beta_{Latitude}$=-0.001, $p$=0.205 for vulnerability;} 
+    Fig.~\ref{S1}). In
     lake food webs, however, the scaling of each property was stronger towards
-  the poles ($\beta_{Latitude:Lake}$=\st{0.004, $p$=0.019}0.003, $p$=0.031;
-  $\beta_{Latitude:Lake}$=0.005, $p$=\st{0.004}0.005; and
-  $\beta_{Latitude:Lake}$=\st{0.004, $p$=0.018}0.004, $p$=0.030, respectively). In stream food
+    the poles 
+    \st{($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
+    $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
+    $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively)}
+    \textbf{($\beta_{Latitude:Lake}$=0.003, $p$=0.031;
+    $\beta_{Latitude:Lake}$=0.005, $p$=0.005; and
+    $\beta_{Latitude:Lake}$=0.004, $p$=0.030, respectively)}
+    . In stream food
     webs, generality increased more rapidly towards the poles
-  ($\beta_{Latitude:Stream}$=\st{0.007, $p$=0.001}0.005, $p$=0.008) while link density and
+    \\\st{($\beta_{Latitude:Stream}$=0.007, $p$=0.001)}
+    \textbf{($\beta_{Latitude:Stream}$=0.005, $p$=0.008)}
+    while link density and
     vulnerability did not vary with latitude (i.e., the interaction term 
@@
 
-\subsection*{Discussion}
+\section*{Discussion}
 
@@
     generalist across all types of aquatic habitats than terrestrial 
-  consumers~\cite{Liem1990,Shurin2006}. This trend also held in our data, although the difference between generality was not significant (
-  $\mu_{Aquatic}$=\st{5.47}5.86, \\$\mu_{Terrestrial}$=\st{3.82}3.75; $p$=\st{0.007}\textless0.001 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$).
+    consumers [5,53]. This trend also held in our data, although the difference between generality was not significant \st{
+    $\mu_{Aquatic}$=5.47, $\mu_{Terrestrial}$=3.82; $p$=0.007 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$)} \textbf{(
+    $\mu_{Aquatic}$=5.86, $\mu_{Terrestrial}$=3.75; $p$\textless0.001 for 
+    \\$\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$)}.
 
-\end{spacing}
+% \bibliographystyle{prsb}
+% \bibliography{abbreviated}
 
-\bibliographystyle{prsb}
-\bibliography{abbreviated}
-
-\newpage
+\clearpage
 
@@
 
+\setcounter{figure}{1}
+
 \begin{figure}[h]
-% \centerline{\includegraphics*[width=\textwidth]{Figures/by_TL/scaling_with_S/proportions/STL_fitlines_nonts.eps}}
-% \centerline{\includegraphics*[width=\textwidth]{Figure2_updated.eps}}
-\caption{
-Scaling relationships for re-scaled link density, generality, and vulnerability 
-relative to the species richness of a food web. Link density, generality,
+% \includegraphics*[width=\textwidth]{Figures/Figure2.eps}
+\includegraphics*[width=.48\textwidth]{Figures/Figure2.eps}
+\hspace{.02\textwidth}
+\includegraphics*[width=.48\textwidth]{Figures/Figure2_updated.eps}
+
+\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
+relative to the species richness of a food web. Here we show the original relationships (left)
+and the relationships after correcting several food webs (right). Link density, generality,
 and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
@@
 ecosystems as a baseline (black line, N=196 food webs). For a figure with the uncorrected values,
-see Fig.~\emph{S7}, \emph{Appendix S4}.}
-\label{props_v_lat}
+see Fig.~\emph{S7}, \emph{Appendix S4}. Note that the corrected and original relationships are 
+very similar, but the re-scaled values for some food webs have changed.
+}
+\label{props_v_lat1}
 \end{figure}
@@
 \begin{figure}[h]
-% \centerline{\includegraphics*[width=\textwidth]{Figures/by_TL/marginal/S_marginal_latitude_non_TS_corrected.eps}}
-% \centerline{\includegraphics*[width=\textwidth]{Figure3_updated.eps}}
-\caption{Changes to the scaling of link density, generality, and vulnerability with species richness across ecosystem
-types and over latitude. We show the estimated scaling exponent for species richness (black
-line) with its 95\% confidence interval (in grey), based on N=196 empirical food webs.
-Latitude is given in degrees from the equator regardless of direction.} \label{S} \end{figure}
+\includegraphics*[width=.48\textwidth]{Figures/Figure3.eps}
+\hspace{.02\textwidth}
+\includegraphics*[width=.48\textwidth]{Figures/Figure3_updated.eps}
+% \includegraphics*[width=\textwidth]{Figure3.eps}
+\caption{Changes to the scaling of link density, generality, and vulnerability with species richness 
+across ecosystem types and over latitude. Here we show these changes for the original dataset (left) 
+and after correcting several food webs (right). We show the estimated scaling exponent for species 
+richness (black line) with its 95\% confidence interval (in grey), based on N=196 empirical food 
+webs. Latitude is given in degrees from the equator regardless of direction. Note that the scaling
+relationships with latitude were very similar for the original and corrected datasets.} 
+\label{S1} 
+\end{figure}
+
+% \clearpage
+
+% \section*{Corrected Figures}
+
+% \setcounter{figure}{1}
+% \begin{figure}[h]
+% % \includegraphics*[width=\textwidth]{Figures/Figure2_updated.eps}
+% \includegraphics*[width=\textwidth]{Figure2_updated.eps}
+% \caption{
+% Figure 2 caption correct in original.}
+% \label{props_v_lat}
+% \end{figure}
+
+% \begin{figure}[h]
+% % \includegraphics*[width=\textwidth]{Figures/Figure3_updated.eps}
+% \includegraphics*[width=\textwidth]{Figure3_updated.eps}
+% \caption{Figure 3 caption correct in original.} \label{S} \end{figure}
+
+\end{spacing}
 

### 2018-08-28 manuscript/correction.tex
going to send the letter back to Daniel

@@
     A subset of food webs analysed for this manuscript (75 out of 263; see \emph{Table S2, Appendix S1} for details) had formatting errors or irregularities that caused them to be incorrectly processed by our original code.
+Some food webs had inconsistent labels that prevented sets of predators and prey from being correctly linked to the same species.
+Others listed interactions using categorical symbols; these interactions were not included in our original analyses.
+
     We have corrected these inconsistencies and repeated our analyses to ensure that our conclusions did not change.
 After re-analysis, our results were qualitatively identical to those originally published and our original conclusions hold.
-However, the specific values given in the results and discussion are now incorrect.
+However, the specific values for correlations and scaling relationships given in the original results and discussion are incorrect.
 Below, we present the results and the relevant portion of the discussion with the original values (struck-through) and corrected values (bold) side by side as well as the original and corrected Figures 2-3.

### 2018-08-28 manuscript/erratum_letter.tex
going to send the letter back to Daniel

@@
 
-Recently I have revisited the dataset used in this article and noticed that 75  of the webs we used (out of a sample of 263) have irregularities or errors of formatting that caused them to be incorrectly processed by our original code.
-Fortunately, after repeating all analyses with corrected versions of these 75 webs our results were qualitatively identical to those published and our conclusions remain unchanged.
-Unfortunately, the specific values given in the published text are nearly all incorrect.
+As requested, we have revised our correction by adding a section to explicitly state the purpose of the correction.
+In this description we refer to \emph{Table S2}, which details the food webs that were corrected and the reason for the correction.
+We agree with the Editor that our previous submission required a lot of effort from a reader; we had used the ''Original text'', ''Revised text'' format in response to a specific request when we first attempted to submit the correction.
+In the absence of any guidelines as to how corrections should be formatted, we hope that our current approach will be more user-friendly.
+We give the results and discussion only once, with original values presented in struck-through font and corrected values immediately following in bold.
+We believe that this will allow readers to see at a glance that the changes to our results are quite minor.
 
-I have attached a corrected version of the results and a small portion of the discussion with the original values struck through and the corrected values provided side-by-side.
-No further changes to the manuscript were necessary.
-I hope that this demonstrates that our conclusions hold and will be suitable as a corrigendum for our manuscript.
-I have also attached an updated supplemental information document which now includes a table (Table S2) giving details of the webs which required corrections.
-
-My co-authors and I deeply regret not finding and correcting these errors earlier, and appreciate your kind attention in this matter.
+Thank you again for considering this correction.
+My co-authors and I are glad to have the opportunity to fix our manuscript and preserve the high quality of research presented in \textbf{Proceedings of the Royal Society B}.
 

### 2018-09-04 manuscript/correction.tex
reformatted correction letter following DBS comments

@@
 However, the specific values for correlations and scaling relationships given in the original results and discussion are incorrect.
-Below, we present the results and the relevant portion of the discussion with the original values (struck-through) and corrected values (bold) side by side as well as the original and corrected Figures 2-3.
+Below, we present the results section and the last paragraph of the discussion (the only portion to require correction) with corrected values in bold.
+The original and corrected values may be compared in Tables~\ref{corr_comparison} and~\ref{beta_comparison}.
+We also show the original and corrected Figures 2-3.
 All supplemental figures have also been updated; as with the main-text figures below, any differences were minor.
@@
     number of prey per species), and vulnerability (mean number of predators per
-    species) were strongly and positively correlated \st{($R^2$=0.891 for link
-    density and generality, $R^2$\textgreater0.999 for link density and
-    vulnerability, and $R^2$=0.890 for generality and vulnerability)}
+    species) were strongly and positively correlated 
     \textbf{($R^2$=0.915 for link
     density and generality, $R^2$\textgreater0.999 for link density and
-    vulnerability, and $R^2$=0.912 for generality and vulnerability)}
+    vulnerability, and $R^2$=0.912 for generality and vulnerability; Table~\ref{corr_comparison})}
     . Contrary
@@
     species richness 
-    \st{($\beta_0$=0.637, $p$\textless0.001; $\beta_0$=0.553,
-    $p$\textless0.001; and $\beta_0$=0.637, $p$\textless0.001, respectively;}
     \textbf{($\beta_0$=0.688, $p$\textless0.001; $\beta_0$=0.658,
-    $p$\textless0.001; and $\beta_0$=0.695, $p$\textless0.001, respectively;}
+    $p$\textless0.001; and $\beta_0$=0.695, $p$\textless0.001, respectively; Table~\ref{beta_comparison}}
     Fig.~\ref{props_v_lat1}). For estuarine, marine, and terrestrial food webs the
     strength of this scaling did not vary with latitude
-    \st{($\beta_{Latitude}$=-0.001, $p$=0.365 for link density;
-    $\beta_{Latitude}$=-0.001, $p$=0.535 for generality; and
-    $\beta_{Latitude}$=-0.001, $p$=0.366 for vulnerability;}
     \textbf{($\beta_{Latitude}$=-0.001, $p$=0.210 for link density;
     $\beta_{Latitude}$=-0.001, $p$=0.315 for generality; and
-    $\beta_{Latitude}$=-0.001, $p$=0.205 for vulnerability;} 
+    $\beta_{Latitude}$=-0.001, $p$=0.205 for vulnerability; Table~\ref{beta_comparison};} 
     Fig.~\ref{S1}). In
@@
     the poles 
-    \st{($\beta_{Latitude:Lake}$=0.004, $p$=0.019;
-    $\beta_{Latitude:Lake}$=0.005, $p$=0.004; and
-    $\beta_{Latitude:Lake}$=0.004, $p$=0.018, respectively)}
     \textbf{($\beta_{Latitude:Lake}$=0.003, $p$=0.031;
     $\beta_{Latitude:Lake}$=0.005, $p$=0.005; and
-    $\beta_{Latitude:Lake}$=0.004, $p$=0.030, respectively)}
+    $\beta_{Latitude:Lake}$=0.004, $p$=0.030, respectively; Table~\ref{beta_comparison})}
     . In stream food
     webs, generality increased more rapidly towards the poles
-    \\\st{($\beta_{Latitude:Stream}$=0.007, $p$=0.001)}
-    \textbf{($\beta_{Latitude:Stream}$=0.005, $p$=0.008)}
+    \textbf{($\beta_{Latitude:Stream}$=0.005, $p$=0.008; Table~\ref{beta_comparison})}
     while link density and
@@
 
-    ... primarily gape-limited aquatic consumers tend to be more
+  Importantly, while terrestrial communities are also strongly seasonal at
+  high latitudes and can receive significant allochthonous
+  inputs [46], terrestrial consumers tend to be
+  morphologically specialised for feeding on particular prey [53].
+  This means that primarily gape-limited aquatic consumers tend to be more
   generalist across all types of aquatic habitats than terrestrial 
-    consumers [5,53]. This trend also held in our data, although the difference between generality was not significant \st{
-    $\mu_{Aquatic}$=5.47, $\mu_{Terrestrial}$=3.82; $p$=0.007 for $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$)} \textbf{(
+  consumers [5, 53]. This trend also held in our data, although the difference between generality was not significant \textbf{(
     $\mu_{Aquatic}$=5.86, $\mu_{Terrestrial}$=3.75; $p$\textless0.001 for 
-    \\$\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$)}.
+    $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$; Table~\ref{corr_comparison})}. 
+  The key to this argument is therefore whether freshwater ecosystems experience
+  more severe seasonal variation than marine and estuarine ecosystems. Although
+  we are not aware of any study explicitly comparing seasonal variation in
+  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
+  ecosystems are indeed likely to experience more severe changes because of their small size.
+  While oceans and estuaries certainly vary in terms of water temperature and
+  nutrients over the course of a year [51], these changes are likely to be slower
+  and milder than in freshwaters because marine and estuarine communities are buffered 
+  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
+  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
+  in non-marine communities [11]. Thus suggests that niche breadths may also be 
+  more variable over the course of the year.
 
@@
 % \bibliography{abbreviated}
+
+\clearpage
+
+\section*{Tables}
+
+\begin{table}[h!]
+\caption{Original and corrected values for correlations, mean generalities, and a student's T-test for differences in mean generalities reported in the main text.
+The 'Location' column indicates the section in which the relationship is described.
+Original values are those given in the original publication of this article.
+Corrected values are those obtained after correcting formatting inconsistencies in several food webs.}
+\label{corr_comparison}
+\small
+\begin{tabular}{l l | r | r}
+Relationship & Location & Original & Corrected \\
+\hline
+$R^2_{link density:generality}$ & Results & 0.891 & 0.915 \\
+$R^2_{link density:vulnerability}$ & Results & \textgreater0.999 & \textgreater0.999 \\
+$R^2_{generality:vulnerability}$ & Results & 0.890 & 0.912 \\
+$\mu_{generality_{Aquatic}}$ & Discussion & 5.47 & 5.86 \\
+$\mu_{generality_{Terrestrial}}$ & Discussion & 3.82 & 3.75 \\
+P($\mu_{generality_{Aquatic}}>\mu_{generality_{Terrestrial}}$) & Discussion & 0.007 & \textless0.001 \\
+\end{tabular}
+\end{table}
+
+\begin{table}[h!]
+\caption{Original and corrected values for scaling relationships between specialisation and species richness and the effect of latitude on the strength of these relationships.
+Original values are those given in the original publication of this article.
+Corrected values are those obtained after correcting formatting inconsistencies in several food webs.
+All values are referred to in the Results section of the main text.}
+\label{beta_comparison}
+\small
+\begin{tabular}{l | r r | r r}
+\multirow{2}{*}{Parameter} & \multicolumn{2}{c|}{Original} & \multicolumn{2}{c}{Corrected} \\
+& $\beta$ & $p$ & $\beta$ & $p$ \\
+\hline
+\multicolumn{5}{c}{Scaling of specialisation with species richness} \\
+\hline
+$\beta_{0_{link density}}$ & 0.637 & \textless0.001 & 0.688 & \textless0.001 \\
+$\beta_{0_{generality}}$ & 0.553 & \textless0.001 & 0.658 & \textless0.001 \\
+$\beta_{0_{vulnerability}}$ & 0.637 & \textless0.001 & 0.695 & \textless0.001 \\
+\hline
+\multicolumn{5}{c}{Strength of scaling and latitude: estuarine, marine, terrestrial} \\
+\hline
+$\beta_{{Latitude}_{link density}}$ & -0.001 & 0.365 & -0.001 & 0.210 \\
+$\beta_{{Latitude}_{generality}}$ & -0.001 & 0.535 & -0.001 & 0.315 \\
+$\beta_{{Latitude}_{vulnerability}}$ & -0.001 & 0.366 & -0.001 & 0.205 \\
+\hline
+\multicolumn{5}{c}{Strength of scaling and latitude: lakes} \\
+\hline
+$\beta_{{Latitude}_{link density}}$ & 0.004 & 0.019 & 0.003 & 0.031 \\
+$\beta_{{Latitude}_{generality}}$ & 0.005 & 0.004 & 0.005 & 0.005 \\
+$\beta_{{Latitude}_{vulnerability}}$ & 0.004 & 0.018 & 0.004 & 0.030 \\
+\hline
+\multicolumn{5}{c}{Strength of scaling and latitude: streams} \\
+\hline
+$\beta_{{Latitude}_{link density}}$ & \multicolumn{2}{c|}{NA} & \multicolumn{2}{c}{NA} \\
+$\beta_{{Latitude}_{generality}}$ & 0.007 & 0.001 & 0.005 & 0.008 \\
+$\beta_{{Latitude}_{vulnerability}}$ & \multicolumn{2}{c|}{NA} & \multicolumn{2}{c}{NA} \\
+\end{tabular}
+\end{table}
 

### 2018-09-04 manuscript/correction.tex
reformatted correction letter following DBS comments

@@
 However, the specific values for correlations and scaling relationships given in the original results and discussion are incorrect.
-Below, we present the results section and the last paragraph of the discussion (the only portion to require correction) with corrected values in bold.
+Below, we present the results section and the beginning of the last paragraph of the discussion (the only portion to require correction).
+All corrections are highlighted in bold.
 The original and corrected values may be compared in Tables~\ref{corr_comparison} and~\ref{beta_comparison}.
@@
   The key to this argument is therefore whether freshwater ecosystems experience
-  more severe seasonal variation than marine and estuarine ecosystems. Although
-  we are not aware of any study explicitly comparing seasonal variation in
-  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
-  ecosystems are indeed likely to experience more severe changes because of their small size.
-  While oceans and estuaries certainly vary in terms of water temperature and
-  nutrients over the course of a year [51], these changes are likely to be slower
-  and milder than in freshwaters because marine and estuarine communities are buffered 
-  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
-  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
-  in non-marine communities [11]. Thus suggests that niche breadths may also be 
-  more variable over the course of the year.
+  more severe seasonal variation than marine and estuarine ecosystems.
 

### 2018-09-04 manuscript/correction.tex
fixed the apostrophe'
fixing figure refs for manuscript central
resubmitted correction'

@@
 
-    A subset of food webs analysed for this manuscript (75 out of 263; see \emph{Table S2, Appendix S1} for details) had formatting errors or irregularities that caused them to be incorrectly processed by our original code.
+    A subset of food webs analysed for the manuscript \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types}; doi: 10.1098/rspb.2015.1589 had formatting errors or irregularities that caused them to be incorrectly processed by our original code (75 out of 263; see \emph{Table S2, Appendix S1} for details).
 Some food webs had inconsistent labels that prevented sets of predators and prey from being correctly linked to the same species.
@@
 \caption{Original and corrected values for correlations, mean generalities, and a student's T-test for differences in mean generalities reported in the main text.
-The 'Location' column indicates the section in which the relationship is described.
+The `Location' column indicates the section in which the relationship is described.
 Original values are those given in the original publication of this article.
@@
 \begin{figure}[h]
-% \includegraphics*[width=\textwidth]{Figures/Figure2.eps}
-\includegraphics*[width=.48\textwidth]{Figures/Figure2.eps}
+\includegraphics*[width=.48\textwidth]{Figure2.eps}
 \hspace{.02\textwidth}
-\includegraphics*[width=.48\textwidth]{Figures/Figure2_updated.eps}
-
+\includegraphics*[width=.48\textwidth]{Figure2_updated.eps}
 \caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
@@
 \begin{figure}[h]
-\includegraphics*[width=.48\textwidth]{Figures/Figure3.eps}
+\includegraphics*[width=.48\textwidth]{Figure3.eps}
 \hspace{.02\textwidth}
-\includegraphics*[width=.48\textwidth]{Figures/Figure3_updated.eps}
-% \includegraphics*[width=\textwidth]{Figure3.eps}
+\includegraphics*[width=.48\textwidth]{Figure3_updated.eps}
 \caption{Changes to the scaling of link density, generality, and vulnerability with species richness 
@@
 
-% \clearpage
-
-% \section*{Corrected Figures}
-
-% \setcounter{figure}{1}
-% \begin{figure}[h]
-% % \includegraphics*[width=\textwidth]{Figures/Figure2_updated.eps}
-% \includegraphics*[width=\textwidth]{Figure2_updated.eps}
-% \caption{
-% Figure 2 caption correct in original.}
-% \label{props_v_lat}
-% \end{figure}
-
-% \begin{figure}[h]
-% % \includegraphics*[width=\textwidth]{Figures/Figure3_updated.eps}
-% \includegraphics*[width=\textwidth]{Figure3_updated.eps}
-% \caption{Figure 3 caption correct in original.} \label{S} \end{figure}
-
 \end{spacing}

### 2018-09-04 manuscript/erratum_letter.tex
resubmitted correction'

@@
 
-\begin{letter}{\bf Professor Spencer C.H. Barrett\\
-               Editor-in-Chief\\
+\begin{letter}{\bf Dr. Daniel Costa\\
+               Associate Editor\\
                Proceedings of the Royal Society B\\
@@
 
-\opening{Dear Prof. Barrett:}
+\opening{Dear Dr. Costa:}
 
-I am writing regarding my article \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types.} (article ID \#RSPB-2015-1589.R2).
+We are pleased to submit a revision to our correction to article \emph{Latitudinal gradients in biotic niche breadth vary across ecosystem types.} (article ID \#RSPB-2015-1589.R2).
 The full citation details for this article are: Cirtwill, A.R., Stouffer, D.B., \& Romanuk, T.N.
@@
 In this description we refer to \emph{Table S2}, which details the food webs that were corrected and the reason for the correction.
+We have also restructured our correction in an effort to be more user-friendly.
 We agree with the Editor that our previous submission required a lot of effort from a reader; we had used the ''Original text'', ''Revised text'' format in response to a specific request when we first attempted to submit the correction.
-In the absence of any guidelines as to how corrections should be formatted, we hope that our current approach will be more user-friendly.
-We give the results and discussion only once, with original values presented in struck-through font and corrected values immediately following in bold.
-We believe that this will allow readers to see at a glance that the changes to our results are quite minor.
+In the absence of any guidelines as to how corrections should be formatted, we now present only the corrected text (with any changes highlighted in bold).
+The original and corrected values for all changes are now presented in two tables which are referred to in the text.
+We hope that this will allow readers to see what has changed with minimal searching.
+We also now show the original and corrected figures side-by-side to illustrate both the minor changes to some data points and the consistency of the overall relationships reported.
+We believe that these changes will make it easy for any reader to see exactly what has changed and that our original conclusions hold.
+If the Editor has any further specific formatting changes that he would like us to implement, we are happy to do so.
 

### 2018-09-04 code/TL_observedfits.py

@@ -233,8 +233,8 @@ def S_scaleplots(rawdatafile,outfile1,Bformat,predfolder):
   TL='S'
   for prop in ['LS','Gen','Vul']:
     rawdata=datareader(rawdatafile,TL,Bformat)
-    # if rawdatafile=='../non_TS/summary-properties.tsv':
-    if rawdatafile=='../non_TS/summary-properties_trimmed.tsv':
+    if rawdatafile=='../non_TS/summary-properties.tsv':
+    # if rawdatafile=='../non_TS/summary-properties_trimmed.tsv':
       fixed=fixed_reader('../non_TS/coefficients/'+prop+'_co.tsv')
       # fixed=fixed_reader('../updated/non_TS/coefficients/'+prop+'_co.tsv')
     else:
@@ -320,13 +320,13 @@ def S_rawplots(rawdatafile,outfile1,Bformat,predfolder):
   for prop in ['LS','Gen','Vul']:
     rawdata=datareader(rawdatafile,TL,Bformat)
 
-    if rawdatafile=='../non_TS/summary-properties_trimmed.tsv':
-    # if rawdatafile=='../non_TS/summary-properties.tsv':
-      # fixed=fixed_reader('../non_TS/coefficients/'+prop+'_obs.tsv')
-      fixed=fixed_reader('../updated/non_TS/coefficients/'+prop+'_obs.tsv')
+    # if rawdatafile=='../non_TS/summary-properties_trimmed.tsv':
+    if rawdatafile=='../non_TS/summary-properties.tsv':
+      fixed=fixed_reader('../non_TS/coefficients/'+prop+'_obs.tsv')
+      # fixed=fixed_reader('../updated/non_TS/coefficients/'+prop+'_obs.tsv')
     else:
-      # fixed=fixed_reader('../mod_data/coefficients/'+prop+'_obs.tsv')
-      fixed=fixed_reader('../updated/mod_data/coefficients/'+prop+'_obs.tsv')
+      fixed=fixed_reader('../mod_data/coefficients/'+prop+'_obs.tsv')
+      # fixed=fixed_reader('../updated/mod_data/coefficients/'+prop+'_obs.tsv')
 
     graph=grace.add_graph(Panel)
 
@@ -396,9 +396,16 @@ def TL_scaleplots(rawdatafile,outfile2,Bformat,predfolder):
   grace=MultiPanelGrace(colors=ColorBrewerScheme("Greys"))
 
[…]
